### 2022-03-04 docs/papers/tex/appendix.tex
refactor(tex,-gitignore): now can compile LaTeX correctly
project structure refactor from vscode projects.

according to my python project template

\documentclass{article}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[a4paper, total={7in, 10in}]{geometry}

\setstretch{1.523}

\newtheorem{ass}{Assumption}
\newtheorem{case}{Case}
%% make sure you have the nature.cls and naturemag.bst files where
%% LaTeX can find them

\bibliographystyle{naturemag}

\title{Supplementary Materials for

Importance of social-ecological fit for water management in large river basins: An analysis of institutional shifts in the Yellow River Basin}

%% Notice placement of commas and superscripts and use of &
%% in the author list

% \author{Shuang Song$^{1,2}$, Huiyu Wen$^3$, *Shuai Wang$^{1,2}$, Graeme S. Cumming$^{4}$ \& Bojie Fu$^{1, 2}$}

\begin{document}

\maketitle
\input{../../drafts/authors.md}

\begin{abstract}
    % 这个补充材料以下述逻辑组织而成：
    The supplementary material is organized logically as follows:
    % 展示流域水资源分配制度在全球的推行情况并详细介绍黄河流域的制度变化，旨在说明黄河流域为什么是一个独一无二的准自然实验。
    (1) Show the implementation of the water resource allocation system in the basin around the world and introduce the institutional changes in the Yellow River Basin in detail, aiming to explain why the Yellow River Basin is a unique quasi-natural experiment.
    % 展示定量分析方法的技术路线图，并详细介绍定量分析方法中的细节部分。
    (2) Show the technical roadmap of quantitative analysis method, and introduce the details of quantitative analysis method in detail.
    % 基于我们建立的一般经济模型，对一些可能的情景进行进一步分析。
    (3) Further extensions based on our general economic model.
\end{abstract}

\section*{S1. Detailed introduction of the institutions}
% 水资源分配方案在全世界范围内都是流域管理的普遍制度。
Water allocation schemes are widespread in large river basin management programs throughout the world (see \textit{Supplementary Material Figure~\ref{fig:world}}) \cite{speedBasinwaterallocation2013}.
% 其中中国的黄河流域以典型的自上而下进行制度改革，这种模式会对制度产生迅速的影响，使我们能够定量地估计高层制度设计变化对用水的净影响。
The Yellow River Basin (YRB) in China has a typical top-down approach to institutional reform, which produces rapid institutional impacts and allows researchers to quantitatively estimate the net impact of changes in high-level institutional design on water use (see \textit{Supplementary Material Figure~\ref{fig:framework}}).
% 作为中国最早实施水资源分配制度的流域，黄河的制度变化可以在几个水利部发布的文件中得以窥见
This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level):
\begin{itemize}
    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}.
    \item \textbf{1987}: Implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
    \item \textbf{1998}: Implementation of unified regulation. (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
    % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
    \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}.
    \item \textbf{2021}: A call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
\end{itemize}

\begin{figure}[!htb]
    \centering
    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/world_institutions}
	\caption{
		Overview of water allocation institutions.
		% 世界已有水资源分配制度的大河流域，其中黄河流域最早于1987年提出资源分配方案，后于1998年更改为统一调度方案。
		\textbf{A.} Major river basins in the world with existing water resource allocation systems (shaded red); the YRB first proposed a resource allocation scheme in 1987 (designed in 1983) and then changed to a unified regulation scheme in 1998 (designed in 1997 but implemented in 1998).
		% 不同的水资源分配制度设计模式，中国黄河流域是典型的自上而下。
		\textbf{B.} Different water resource allocation system design patterns; the YRB is typical of a top-down system with multiple levels.
		% 流域分水制度的演化。这种多层次的制度设计有其历史变化过程。
		\textbf{C.} The four periods of institutional evolution of water allocation of the YRB.
	}
    \label{fig:world}
\end{figure}
% 在上述文件中，1982年的文件标志着设计分水制度尝试的开始，2008年标志着该制度走向成熟（完全建立起流域-省-市区的多级水资源分配和统一调度）。
The 1982 document marked the beginning of the attempt to design a water allocation institution, and the 2008 document marked the maturity of the system (complete establishment of basin-level, provincial, and district water allocation and unified regulation). Currently, a major overhaul is in the planning stages. Major shifts of the institution can be analyzed by using the 1987 and 1998 documents. It is worth noting that, although the essential reason for these institutions was the mismatch between the spatial and temporal distribution of water resources as well as social and economic water demands, the direct reason for their introduction was the drying-up of the Yellow River \cite{wangReviewImplementationYellow2019}.

\textbf{The official documents in 1987 clearly convey the following key points:}
\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today.
\begin{itemize}
	% 该政策面向的目标是各省（区域），黄委会没有被提及
	\item The policy is aimed at related provinces (or regions), and the YRCC is not mentioned.
	% 政策制定的首要考虑是解决断流问题
	\item Drying-up of the river is identified as the first consideration of this institution.
	% 各省被鼓励在此配额下制定自己的用水计划
	\item Provinces are encouraged to develop their own water use plans based on a quota system.
	% 水资源供给无法满足需求对相关省（地区）是普遍现象。
	\item Water in short supply is a common phenomenon in relevant provinces (regions).
\end{itemize}

\textbf{The official documents in 1998 clearly convey the following key points:}
\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today.
\begin{itemize}
	% 除了说明政策针对的各省区之外，明确指出其用水需要黄河水利委员会进行申报，并由其组织和监管
	\item The document clearly points out that not only provinces and autonomous regions involved in water resources management (see \textit{Article 3}), the provinces’ and regions’ water use shall be declared, organized, and supervised by the YRCC (\textit{Article 11 and Chapter III to Chapter V, and Chapter VII}).
	% 本研究(\textit{ Article 1})首先考虑的是上、中、下游用水的总体规划。
	\item Creating the overall plan of water use in the upper, middle, and lower reaches is identified as the first consideration of this institution (\textit{Article 1}).
	% 各省需要
	\item With the same quota as used in the 1987 policy, provinces were encouraged to further distribute their quota into lower-level administrations (see \textit{Article 6 and Article 41}).
	% 强调以总量确定供给，以供给决定需求。
	\item They emphasize that supply is determined by total quantity, and water use should not exceed the quota proposed in 1987 (see \textit{Article 2}).
\end{itemize}

% 基于上述分析，我们抽象出了如正文图2中所展示的流域水资源分配制度的运行结构，并将研究时段选择在1975到2008之间。
On the basis of the above analysis, we abstracted the operational structure of the water resource allocation institution of the YRB as shown in Figure 2 of the main text, focusing on the period between 1975 and 2008. By comparing the net effects of three different institutional structures split by the two institutional shifts, we were able to reach a stronger understanding of the influence of structural alignments under the same basin (previous structure-based analysis usually focus on a certain type of systems but with different geographic contexts).

\begin{figure}[!htb]
    \centering
	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/YRB_scheme}
	\caption{
		% 中国自上而下的水资源分配制度模式（以黄河流域为例）
		A top-down water resources allocation scheme in China (a case study of the YRB).
		% 共有十个省或地区从黄河获取地表水资源，其中8个省的依赖性较强（see Supplementary Material Fig）。
		\textbf{A.} A total of 10 provinces or regions withdraw surface water resources from the Yellow River, of which 8 are highly dependent on the river (see \textit{Supplementary Material S2}).
		% 中国政府是下发流域管理政策的最高权威，其政策常常能够很快自上而下全面推行。
		\textbf{B.} The Chinese government is the ultimate authority in issuing watershed management policies, which are often quickly implemented from top down.
		% 流域管理机构（在黄河是黄河水利委员会）主要负责顺从国家的政策方针来进行流域的日常管理工作。
		\textbf{C.} The basin-level agency (here, the YRCC) is primarily responsible for the river-related management of the basin in accordance with national policy guidelines.
		% 利益相关者是各省
		\textbf{D.} The water management system directly affects the process by which local governments (major stakeholders) plan and use water resources for development. Although only surface water (Sur.) is usually traced and restricted, it can also influence groundwater through related hydro-processes such as recharge.
	}
	\label{fig:framework}
\end{figure}

\section*{S2. The technical roadmap and details of quantitative analyzing}
To quantify and interpret the institutional effects, we followed the technical route illustrated in \textit{Supplementary Material Figure~\ref{fig:roadmap}}. It was a two-step process in which we
% 基于数据使用合成控制法和安慰剂匹配法，创建可比的控制对照和期望（零模型）来分析制度变化对用水产生的影响。
(i) created a comparable control group and an expectation (a “null model”) to analyze the impact of the institutional shifts on water use by using synthetic control and placebo matching methods, and
% 创建一个基于边际收益的一般经济模型，解释我们发现的“冲刺效应”，并设计情景来进一步分析。
(ii) created a general economic model based on marginal revenue to explain the “sprint effect” we observed and designed scenarios for further analysis.

\begin{figure}[!hbt]
    \centering
    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/roadmap}
    \caption{
        Technical roadmap for quantitatively analyzing the “sprint effect”. WU is the the core variable we concerned -total water uses of the Yellow River Basin.
    }
    \label{fig:roadmap}
\end{figure}

% 为了使用合成控制法预测没有制度变化下的用水变化趋势，需要使用影响用水的社会经济数据作为自变量输入。
In order to use the synthetic control method to predict the trend of water use without institutional change, socioeconomic data affecting water use were used as the input independent variables (see the \textit{Methods in the main text}). All variables used are listed in Table~\ref{tab:variables}.
% 这些变量涉及了省级单元在利用水资源时需要考虑的主要经济因素（农业、工业、服务业与居民生活），它们与因变量（水资源使用）的相关性如图所示。
These variables refer to major economic factors (agriculture, industry, service industry, and domestic) that provincial units need to take into account when using water resources; their correlation coefficients with the dependent variable (water resource use) are shown in Figure~\ref{fig:linear} A.

% 此外，合成控制法有一个假设是自变量的线性组合可以有效预测因变量，因此我们还对数据线性拟合的效果进行了测试。
In addition, the synthetic control method assumes that a linear combination of independent variables can effectively predict the dependent variables.
% 将数据集区分为80%的训练样本和20%的测试样本，我们使用训练样本构建了多元线性模型对用水量进行了预测，并使用测试数据集去检验模型拟合效果。
We therefore divided the dataset into two groups, training samples $(80\%)$ and test samples $(20\%)$, and used the training samples to build a multivariate linear model to predict the water consumption. We then used the test dataset to test the model-fitting effect.
% 结果表明拟合优度R2超过了0.8，因变量可以很好的被自变量的线性组合所解释，该数据集可以用于控制合成法。
Results show that the goodness of fit $R^2$ exceeded $0.8$; thus, the dependent variable is well-explained by the linear combination of independent variables, and the dataset can be used in the synthetic control method (Figure~\ref{fig:linear}B).
% 为了估计用水量变化的期望值，我们对黄河流域各省用各自变量最接近的三个其它省（最近邻法）匹配了一个用作安慰剂实验的数据集
To estimate the expected water use changes, we used the placebo test method as a null model (see the \textit{Methods}), which gives a comparable baseline for matched datasets.
% 从图可以看出，匹配的数据集无论是数值还是变化趋势都与实际数据相似。
Figure~\ref{fig:placebo} indicates that the matched dataset is similar to the actual data both in values and change trends. This means that the differences between the predictions made from actual data and from the matched data by the synthetic control method are more likely to be result of the impacts of institutional shifts.

\begin{table}[!h]
	\caption{Variables and their categories for water use predictions}
	\scriptsize
	\label{tab:variables}
	\begin{tabular}{lllll}
	\hline
	Economic sector &
	  Category &
	  Unit &
	  Description &
	  Variables \\ \hline
	Agriculture &
	  Irrigation Area &
	  thousand ha &
	  \begin{tabular}[c]{@{}l@{}}Area equipped for irrgiation by different \\ crop:\end{tabular} &
	  \begin{tabular}[c]{@{}l@{}}Rice, \\ Wheat, \\ Maize, \\ Fruits, \\ Others.\end{tabular} \\ \hline
	Industry &
	  \begin{tabular}[c]{@{}l@{}}Industrial gross \\ value added\end{tabular} &
	  Billion Yuan &
	  Industrial GVA by industries &
	  \begin{tabular}[c]{@{}l@{}}Textile, \\ Papermaking, \\ Petrochemicals, \\ Metallurgy, \\ Mining, \\ Food, \\ Cements, \\ Machinery, \\ Electronics, \\ Thermal electrivity, \\ Others.\end{tabular} \\
	 &
	  \begin{tabular}[c]{@{}l@{}}Industrial water \\ use efficiency\end{tabular} &
	  \% &
	  \begin{tabular}[c]{@{}l@{}}The ratio of recycled water and evaporated \\ water to total industrial water use\end{tabular} &
	  \begin{tabular}[c]{@{}l@{}}Ratio of industrial water recycling, \\ Ratio of industrial water evaporated.\end{tabular} \\ \hline
	Services &
	  \begin{tabular}[c]{@{}l@{}}Services gross \\ value added\end{tabular} &
	  Billion Yuan &
	  GVA of service activities &
	  Services GVA \\ \hline
	Domestic &
	  Urban population &
	  Million Capita &
	  Population living in urban regions. &
	  Urban pop \\
	 &
	  Rural population &
	  Million Capita &
	  Population living in rural regions. &
	  Rural pop \\
	 &
	  Livestock population &
	  Billion KJ &
	  \begin{tabular}[c]{@{}l@{}}Livestock commodity calories summed from \\ 7 types of animal.\end{tabular} &
	  Livestock \\ \hline
	\end{tabular}
\end{table}

\begin{figure}[!thb]
	\centering
	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/linear}
	\caption{
		\textbf{A.} Correlation between independent variables and the dependent variable (water use).
		\textbf{B.} Linear relationship between the independent variables and the dependent variable trained by a linear model.
	}
\label{fig:linear}
\end{figure}

\begin{figure}[!thb]
	\centering
	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/compared_placebo}
	\caption{
		\textbf{A.} A comparison of the matched placebo dataset and the actual YRB dataset for each province.
		\textbf{B.} Trend of total water use $(10^8 m^3)$ for the matched placebo and actual datasets.
	}
\label{fig:placebo}
\end{figure}

\section*{S3. Further analysis regarding the general economic model}

% 基于构建的一般经济学模型，我们对利益相关者面对用水配额政策的响应做了进一步探讨
Using the general economic model (see the \textit{Methods in the main text}), we also explored the response of stakeholders to water quota policies. We considered two additional scenarios for stakeholders, one that considered technology growth and one that considered different valuations through time (via the discount rate) of economic benefits and ecological costs. In the following scenarios, the cost is assumed to be untransferable, which could be fully allocated to the one incurring the water use. Explaining plausible scenarios for these stakeholders will help us better understand the causes of the sprint effect and potential solutions. We argue that the sprint effect of water use remains robust even if a complete and equitable system.

\subsection*{Growth in technology}

Assume that there is an exogenous technology growth rate of $g$ in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$ and discount factor $\beta$. For simplicity, consider the following finite-period water use optimization:

$ max \quad P \cdot (1+g)^t ln(1+x_{i,0})-\frac{C}{N}+\beta^t \begin{matrix} \sum_{t=1}^T [P \cdot (1+g)^t ln(x_{i,t}+1)-C \cdot x_{i,t}] \end{matrix}$

$s.t. \quad x_{i,t} \leq Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \quad for \quad \forall t$

We depict the relation between multi-period benefits and water use $x_{i0}$ in Figure~\ref{fig:tech_growth}to illustrate the optimal water use pattern under technology growth. The higher marginal benefits of water might create enough incentive to offset the untransferable costs of water overuse at $t=0$, because a higher allocated quota provides growth option value. Because provincial decisions are under a longer time horizon, there is a greater sprint effect due to the higher accumulated yield.

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.7\linewidth]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/tech_growth}
	\caption{Multi-period benefits and optimal water use under technology growth and a quota system. The figure depicts the relationship of multi-period benefits of province $i$ and water use under Case 3 with technology growth under $T$ periods. Assume $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta=0.7$, $g=0.2$, and $Q=8$. The horizontal axis coordinates of $*$ denotes optimal water use at $t=0$ under each time horizon in decision-making.}
	\label{fig:tech_growth}
\end{figure}

\subsection*{Economic benefits and ecological costs with different discount rate}

Assume that there is high discount rate for economic benefits and a low discount rate for ecological costs, in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$, discount factor $\beta^{ecolomy}$ and $\beta^{ecology}$. It means that present economic profits are significantly concerned but future ecological costs are widely ignored. (In fact, if GDP are the core standard to judge officers’ performance, this is an assumption cloth to the reality.) For simplicity, consider the following finite-period water use optimization, notes the water use of province $i$ at period $t$:

$$ max \quad P \cdot ln(1+x_{i,0})-\frac{C}{N}+\beta_{economy}^t \begin{matrix} \sum_{t=1}^T [P \cdot ln(x_{i,t}+1)]  \end{matrix} - \beta_{ecology}^t \begin{matrix} \sum_{t=1}^T [C \cdot x_{i,t}] \end{matrix}$$

$$s.t. \quad x_{i,t} \leq Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \quad for \quad \forall t$$

We depict the relation between multi-period benefits and water use xi0 in different time horizons in Figure~\ref{fig:remote_cost}, Using a higher discount rate for ecological costs might create enough incentive to set off the untransferable unit cost of $C$. Because the provincial decision is often under a longer horizon than that in baseline results in Figure 4 of the main text, there is a greater sprint effect as a result of higher accumulated yields.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\linewidth]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/remote_ecological_cost}
	\caption{Multi-period benefits and optimal water use when economic benefits have a high discount rate, ecological costs have a low discount rate, and a quota is implemented. The figure depicts the relation between multi-period benefits of province $i$ and water use under Case 3 under $T$ periods. Assume $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta_{economy}=0.7$, $\beta_{ecology}=0.3$, and $Q=8$. The horizontal axis coordinates of $*$ denotes optimal water use at $t=0$ under each time horizon in decision-making.
	}
	\label{fig:remote_cost}
\end{figure}

\bibliography{WAInstitution_YRB_2021}
\end{document}

### 2022-03-04 docs/papers/tex/main.tex
refactor(tex,-gitignore): now can compile LaTeX correctly
project structure refactor from vscode projects.

according to my python project template

%% Template for a preprint Letter or Article for submission
%% to the journal Nature.
%% Written by Peter Czoschke, 26 February 2004
%%
\documentclass{article}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage[a4paper, total={7in, 10in}]{geometry}

\setstretch{1.523}

\newtheorem{ass}{Assumption}
\newtheorem{case}{Case}
%% make sure you have the nature.cls and naturemag.bst files where
%% LaTeX can find them

\bibliographystyle{naturemag}

%\usepackage{biblatex}
%% make sure you have the nature.cls and naturemag.bst files where
%% LaTeX can find them

\title{Importance of social-ecological fit for water management in large river basins: An analysis of institutional shifts in the Yellow River Basin}

%% Notice placement of commas and superscripts and use of &
%% in the author list

\author{Shuang Song$^{1,2}$, Huiyu Wen$^3$, *Shuai Wang$^{1,2}$, Graeme S. Cumming$^{4}$ \& Bojie Fu$^{1, 2}$}

\begin{document}

\maketitle
\input{../../drafts/authors.md}

\begin{abstract}
    \input{../../drafts/abstract.md}
\end{abstract}

% Then the body of the main text appears after the intro paragraph.
% Figure environments can be left in place in the document.
% \verb|\includegraphics| commands are ignored since Nature wants
% the figures sent as separate files and the captions are
% automatically moved to the end of the document (they are printed
% out with the \verb|\end{document}| command. However, tables must
% be manually moved to the end of the document, after the addendum.
% 表需要手动移到文末
% water use; water management; social-ecological system; common pool resources; institutional analysis; collaborative governance

\section{Introduction}
Emerging competition for water is an urgent problem in water governance, with widespread water scarcity and overuse resulting in huge impacts on economies, societies, and ecosystems \cite{gleickPeakwaterlimits2010,dolanEvaluatingeconomicimpact2021,siwiCompetitionWaterGetting,ziolkowskaCompetitionWaterResources2016,distefanoArewedeep2017}.
Water is the key exclusive and competitive resource that couples socioeconomic and ecological systems (known as common-pool resources, CPRs) \cite{wutichWaterScarcitySustainability2009,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017,castilla-rhoGroundwaterCommonPool2020}.
Conflicts of interest often occur in allocation and competitions of water resources, with water governance policies often leading to long-term changes in human–water relationships and the redistribution of benefits \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013,chingManagingsocioecologyvery2015}.
Although governments in many of the world’s large river basins have tried to resolve competition for water through the deliberate design of new institutions, general principles underlying the successes and failures of these initiatives are poorly documented and understood.

Institutions (such as policies, laws, and norms) can influence regional sustainability by changing social-ecological system (SES) structure and dynamics \cite{youngInstitutionsenvironmentalchange2008,cummingAdvancingunderstandingnatural2020,lieninstitutionalgrammartool2020}.
These include inter-relationships and interactions between social actors, between ecological units, or between social and ecological system elements \cite{bodinCollaborativeenvironmentalgovernance2017,barnesSocialecologicalalignmentecological2019}.
Effective (“matched”) institutions operate at appropriate spatial, temporal, and functional scales to manage and balance these different relationships and interactions \cite{heWateringEnvironmentalRegulation2020,kellenbergempiricalinvestigationpollution2009}.
From the perspective of SES outcomes, matched institutions support (but do not guarantee) sustainability \cite{epsteinInstitutionalfitsustainability2015,wangAlignmentsocialecological2019}.

Some kinds of institutions have been shown to support desirable outcomes in water-centered SESs (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wangAlignmentsocialecological2019} and in collaborative water governance systems in Europe \cite{greenEUWaterGovernance2013}).
At the same time, undesired and unsustainable outcomes (e.g., failures in environmental regulation of highly polluting industries or the development of “tragedy of the commons” situations when pursuing more water resources), with considerable ecological degradation, have attracted much attention \cite{saylesSocialecologicalnetworkanalysis2019,caiPollutingthyneighbor2016,castilla-rhoSocialtippingpoints2017}.
Despite widespread recognition of the rising importance of integrated water resource management in solving water competition in the world’s large river basins, relatively few studies have explored the mechanisms by which SESs respond to new institutions \cite{agrawalSustainableGovernanceCommonPool2003,pershaSocialEcologicalSynergy2011,agrawalCommonPropertyInstitutions2001}.
Two particular weaknesses in existing knowledge include understanding (1) the causal links between SES structures and outcomes; and (2) details of the underlying processes, especially the coordination of the incentives of different participants, that result from an institutional lack of fit. These weaknesses limit our understanding of institutional design, and they may reduce the speed and transfer of new knowledge and experience related to improving the sustainability of comprehensive water resources management.

In order to disentangle the relationship between SES structure and outcomes, we analyzed a case study to show how an institutional shift led to a structural mismatch that triggered unsustainable water use and unintended ecological deterioration. Two rapid shifts in institutional structure that occurred in 1987 and 1998 (see Supplementary Material S1) provide unique settings to exploit quasi-natural experiments of a large river basin, the Yellow River Basin (YRB) in China \cite{xiaDevelopmentWaterAllocation2012}. After a period of severe drying up, an institutional shift implemented in 1987 represented the beginning of attempts to control water use in the YRB through the use of quotas, with the goals of alleviating conflicts between supply and demand and achieving sustainable development.

Our results show that this initiative actually accelerated water withdrawals, resulting in an unintended “sprint effect”, where institutional mismatches created an even stronger incentive for each resource user to withdraw resources until the next major institutional shift in 1998. Our analysis contributes to a deeper understanding of the mechanisms underlying the relationships among institutions, SES structures, and outcomes. By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings are consistent with the urgent calls for a more dynamic design for water use allocation to achieve sustainability.

\section{Institutions and SES structures}
% 机构可以塑造社会经济体系的结构，对其进行抽象是机械地理解结构和结果之间联系的第一步。
Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{fig:framework}A).
% 例如，机构可以创建一种被确定为与良好的社会经济效益相关联的水平匹配结构，如果它鼓励管理相连生态成分的不同行动者之间的协作(图1B)。
For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{fig:framework}B), leading to sustainable outcomes.
% 例如，机构可以创建一个结构，鼓励不同行为者之间的合作，管理相连的生态成分
Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{fig:framework}C and D).
% 在实践中，一个大型、复杂的河流流域的制度变化将创造或摧毁数百种不同的联系。这些局部变化的更广泛影响可以从系统的整体行为中看到。
In practice, institutional changes in a large, complex river basin will create or destroy hundreds of different connections. The broader impacts of these local changes can be seen in the overall behavior of the system.
% 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
We thus explored the causal linkages between the SES structures and sustainability (outcomes) in quasi-natural experiments of the YRB, which provides an informative case study for two main reasons.
% 首先，长江流域管理的急剧结构变化使我们能够定量估计高层制度设计变化对用水的净影响。决定水分配的制度包括自下而上的协议或社会规范，以及自上而下的配额或法规，它们对社会经济结构有不同的影响;自上而下的监管可能会立即引发制度转变和SES的剧烈结构性变化。通过与由自下而上的制度转变引起的更渐进的变化相比，探索自上而下变化的影响，在对社会经济地位的定量分析中，极大地减少了来自不可观测因素的潜在干扰，提高了社会经济地位结构和结果之间因果关系的清晰度。
First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use. Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013}; top-down regulations can trigger immediate institutional shifts and sharp SES structural changes \cite{speedBasinwaterallocation2013,rolandUnderstandinginstitutionalchange2004}.
In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and improves the clarity of the causal link between SES structure and outcome.
% 其次，通过比较长江流域两次制度变迁所分裂的三种不同制度结构的净效应，我们也可以更深入地理解“盆地固定效应”下结构格局的影响。尽管流域内的社会经济单位从世界各地的大型河流流域和许多地区的水资源中受益，但很少有流域多次经历过如此激进的社会经济结构变化。
Second, by comparing the net effects of three different institutional structures split by two institutional shifts in the YRB, we can also reach a stronger understanding of the influence of structural alignments under a fixed basin. Although socioeconomic units within a basin benefit from water resources in large river basins all over the world and many locations have shown increased levels of regulation, few basins have experienced such radical SES structural changes several times (see \textit{Supplementary Material} S1). Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in SES institutional structure.
% 因此，黄河流域的“流域固定效应”为SES结构的自我比较提供了宝贵的机会。
% Thus, the YRB provides valuable settings for understanding the direct impacts of changes in SES institutional structure.

\begin{figure}
	\centering
	\includegraphics[width=8.3cm]{../../../figs/diagrams/framework.jpg}
	\caption{
		Framework for understanding linkages between SES structures and outcomes.
		\textbf{a.} The general framework for analyzing social-ecological systems (SESs) (adapted from Ostrom \cite{ostromGeneralFrameworkAnalyzing2009}). Institutions embedded in SESs may reshape structures by changing the interactions between core subsystems, resulting in different outcomes.
        Three typical types of abstracted SES structures are shown as \textbf{b.}, \textbf{c.} and \textbf{d.} (adapted from Bodin, 2017)\cite{bodinCollaborativeenvironmentalgovernance2017}. Red circles indicate social actors, and green ones indicate ecological components. Connection (ties between two ecological components), collaboration (ties between two social actors), or management (ties between a social actor and an ecological component) exist when two units are linked by gray lines. The gray dashed lines show aligned SES structures that are more likely to result in a desirable outcome according to empirical evidence.
	}
    \label{fig:framework}
\end{figure}

\section{Context of institutional shifts}
% 黄河是世界第五长河，它的流域也是中国文明的摇篮。
The Yellow River, whose basin is the cradle of Chinese civilization, is the fifth-longest river in the world. It supports $9.7\%$ of China’s irrigation, with only $2.6\%$ of its total water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021).
% 然而，经过沿江各省多年的免费取水(图~\ref{fig:structure} A和B)，到20世纪80年代，黄河地表水耗水量接近径流量的10倍，并不断上升
However, after years of free access to water by provinces along the river (Figure~\ref{fig:structure} A and B), surface water consumption of the Yellow River was close to $80\%$ of its runoff by the 1980s and rising
\cite{wangYellowRiverwater2019,songSedimenttransportincreasing2020}.
% 自1972年以来，黄河径流量的减少破坏了黄河的生态，制约了黄河的经济发展
Reductions in runoff after 1972 damaged the ecology of the YRB and restricted its economic development \cite{wangYellowRiverwater2019}.
% 因此，在中国典型的自上而下的制度结构下(附录图S1-B)，黄河流域不同层次提出了相对完整的水资源分配规定(图1a)。
Therefore, through typical top-down institutional structures in China (see \textit{Supplementary Material S1}), relatively integrated water allocation regulations were successively proposed across different levels in the YRB.
% 这些机构包括国家政府、流域管理机构、省、市，甚至地区(见图1 B-D)。
These include the national government, the basin management agency, provinces, cities, and even districts.
% 这些在不同制度发展阶段相继出台的政策，引发了长江经济带经济发展结构的突变，并产生了不同的结果(见附录A和图S1-C)。
These policies at different stages of institutional development triggered abrupt changes in the SES structure of the YRB with different outcomes.

% 0世纪70年代以来，中国政府向黄河水利委员会下达指令，要求黄河水利委员会设计配水方案，同时要求黄河沿岸各省进行水资源规划
In 1982, the Chinese government issued instructions to the Yellow River Water Conservancy Commission (YRCC), the basin agency of the YRB, requiring it to design a water allocation scheme and at the same time requiring the provinces along the Yellow River to carry out water resources planning (see \textit{Supplementary Material S1})
\cite{wangReviewImplementationYellow2019}.
% 经过多方讨论与权衡，中国政府于1987年为相关省份分配了水资源配额，要求沿黄各省(区)贯彻执行
The Chinese government started to assign water quotas to the relevant provinces in 1987, but did not create a unit to coordinate water division between them (Figure~\ref{fig:structure} \textbf{A} and \textbf{C}).
% 这一时期长江水利枢纽的监督任务是编制长江水利枢纽用水量统计公报，并与定额进行对比分析。
The mandate of the YRCC during this period was only to report on and analyze water consumption in the YRB
\cite{wangReviewImplementationYellow2019}.
% 随着断流的进一步恶化，1998年中国政府推进了相关政策的改革，要求所有省份在取用水资源时必须向黄委会申请许可，黄委会得以直接对各省的用水实施监管。
However, since reductions in river flow indicated an unintended SES outcome (Figure~\ref{fig:structure} E), the Chinese government pushed for a policy reform in 1998 that required all provinces to apply for licenses to use water from the YRCC, allowing the council to directly regulate their water use (see \textit{Supplementary Material S1} and Figure~\ref{fig:structure} A and D).
% 由于革新后的政策成功遏制了断流，2008年该分配政策被进一步细化，相关各省都进一步设置了更细致的分配方案，并最终形成了黄河流域如今的水资源分配格局。
The 1998 policy succeeded in curbing water extraction (Figure~\ref{fig:structure} E), and it was further refined in 2008.
The relevant provinces created a more detailed allocation plan and finally formed the present water allocation institutions of the YRB (see \textit{Supplementary Material S1}).
% 因此，在1975-2008长达33年的时间里，从没有分水政策到以两种不同模式监管下的分水政策，黄河流域实际上先后存在着三种不同的社会-生态结构（Fig 1）。
Therefore, in our study period (from 1975 to 2008), the system shifted between three different SES structures (Figure~\ref{fig:structure} \textbf{B} to \textbf{D}).
% 在它们之中，与预期相反地，1987年至1998年的流域SES结构下黄河的生态急剧恶化，表明了制度的失配。
The sharp and unintended decline in the ecological condition of the Yellow River from 1987 to 1998 indicates an institutional mismatch during this period (Figure~\ref{fig:structure} the shadowed time periods).

\begin{figure}[!ht]
    \centering
    \includegraphics[width=12cm]{../../../figs/diagrams/structure.jpg}
	\caption{
		% 黄河流域的制度变迁与经济社会结构差异。
		Institutional shifts and related SES structures in the Yellow River Basin (YRB). See \textit{Supplementary Material S1} for detailed introduction for the institutions.
		% 国家政府在1987年和1998年先后两次出台了改变流域制度的政策，而黄河水利委员会、利益攸关的各省在不同制度时期具备的功能是不同的。
		\textbf{A.} The national government changed YRB management policies and institutions in 1987 and 1998. As a result, the Yellow River Conservancy Commission (YRCC) and the provinces acted differently in different periods. Three different SES structures existed successively in the YRB.
		% 没有任何政策限制，各利益相关者此时期可以从单向但联通的河流生态单元内自由取水
		\textbf{B.} 1975–1987: Without any constraints, water resources were freely accessible to each stakeholder (the provinces in this case, denoted by red circles) from a one-way but connected ecological unit (the Yellow River, denoted by the blue rectangle).
		% 在政策1之后，每个使用者都被分配了能够开采河流地表水资源的配额，而黄委会的工作是对配额的使用进行统计与汇报。
		\textbf{C.} 1987–1998: After the implementation of policy 1 in 1987, each user was assigned a quota to withdraw surface water resources, and the YRCC (yellow triangle) was tasked with reporting on water quota use.
		% 第二个政策之后，利益相关者取水需要向黄委会申请，黄委会则根据用水配额来批发许可。因此此时黄委会与利益相关者之间产生了直接的双向联系，监督他们对资源配额的取用。
		\textbf{D.} 1998–2008: After the implementation of policy 2, stakeholders had to apply for water resources from the YRCC, which then licensed water use according to the quota. Under this institution, the YRCC had direct two-way connections between provinces and ecological components.
		% 由于政策1与政策2都是为了解决黄河断流的生态问题而提出的，因此在结果与政策预期严重相反的第二时期（灰色阴影时段），是制度导致了错配的社会-生态系统结构。
		\textbf{E.} A timeline of the Yellow River and drying conditions. The size of the circles indicates the length of section that dried up (km), and the y-axis indicates the length of the drying period. Both policy 1 and policy 2 were put forward to solve this ecological crisis. The mismatch created by policy 1 is clearly correlated with the unintended outcomes shown in the second (gray-shaded) period.
	}
	\label{fig:structure}
\end{figure}

\section{Sprint effect induced by an institutional mismatch}
% % 这里，我们使用合成控制模型创建了假设不存在政策变化的虚拟对照组（see \textit{Methods}-1），同时用K-近临算法找到经济状况与黄河流域各省“类似”的安慰剂对照（see \textit{Methods}-2），反复对比表明两次社会-生态系统结构变迁对流域的水资源利用及分配产生了明显不同的影响。
% Here, we use synthetic control method to create a control group assuming that there is no water use constraints (\textbf{methods}), at the same time with K-nearest algorithm to match an economic state and the YRB provinces ``similar'' placebo-controlled (\textbf{methods}).
% % 然后，我们反复比较了两个SES结构(分别自1987年和1998年)，以量化是否有显著不同的影响，YRB用水或分配。
% Then we repeatedly compared between two SES structures (since 1987 and 1998, respectively) to quantify if there were significantly different impacts on water uses or allocation (\textbf{methods}).
% % 我们的结果表明，1987年的结构变化刺激各省使用了远超模型预测的没有政策影响下的用水量，其增量超出安慰剂对照组xx\%，但对水资源的分配的均匀程度没有改变（see fig）。
Our results suggest that the institutional shift in 1987 stimulated the provinces to use far more water than would have been used without policy effects (Figure~\ref{fig:main_results}A), with an observed increase of $164\%$ over the expectation(Figure~\ref{fig:main_results}B).
% 然而，水资源分配的均匀性并没有改变，区域间的用水量在相同规模下增加(图~\ref{fig:main_results}C)。
However, the relative share of water use was not changed, denoting proportionally similar water use increases among the different regions (Figure~\ref{fig:main_results}C).
% 在1998年出台的政策再次改变社会-生态结构之后，用水量显著下降，总量仅为安慰剂对照组的xx%。
After the SES structure changed again in 1998, the trend of increasing water use appeared to be effectively suppressed (Figure~\ref{fig:main_results} D), with total observed water consumption decreasing by $260\%$ relative to expectations(Figure~\ref{fig:main_results} E).
% 但此阶段主要是xx，xx，xx等黄河流域的用水大省受到了遏制，因此水资源在各个省之间的比例分配变得更均匀了。
At this stage, however, the reduction in water use came mainly from the provinces with large water consumption, such as Henan and Shandong (Figure~\ref{fig:main_results} E),  so the proportion of water used by regions became more similar (Figure~\ref{fig:main_results} F).
% 上述结果表明，1998年各省之间由黄委会统一监管后分水政策才真正达到了其遏制用水、解决断流的预期。
In conclusion, the water allocation policy curbed water use in 1998, whereas the 1987–1998 institutional mismatch stimulated a notable increase in total water use in all related provinces.
% 在过去的十年里，对制度变革的“冲刺”反应似乎创造了一场竞赛，每个省份都开始使用超过他们需要的水。
Over this decade, “sprint” responses (i.e., rapid increases in resource use \cite{lueckPreemptiveHabitatDestruction2003}) to institutional change appear to have created a race in which each province began to use more water than they needed.

\begin{figure}
    \centering
    \includegraphics[width=12cm]{../../../figs/outputs/main_results.jpg}
    \caption{
        Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB). (\textbf{A} to \textbf{C}: Entering the mismatched SES structure in 1987; \textbf{D} to \textbf{E}: exiting the mismatch in 1998. \textbf{A} and \textbf{D}: Impact of the first institutional shift on water use trends in the YRB. Blue points are actual water use, and gray points are predicted use under a scenario without any institutional shift (see \textit{Methods}). \textbf{B} and \textbf{E}: Impact of the institutional shift on total water use. Dark bars indicate the difference between the actual and predicted water use in specific study periods. Gray bars are the expected water use, simulated by setting up placebo experiments (null models, see \textit{Methods}). \textbf{C} and \textbf{F}: Impact of institutional shift on water allocation equity (see \textit{Methods}). Red lines indicate the index calculated from actual water use data; gray lines indicate predicted water use under a scenario with unconstrained water use.
    }
    \label{fig:main_results}
\end{figure}

\section{Incentive distortion causes the sprint effect}
Theoretically, our economic model suggests that different kinds of institutional shifts should lead to different optimal water uses (Figure~\ref{fig:economic_model}).
Furthermore, our analysis indicated that the cause of the sprint effect in this case was incentive distortion.
Compared with the decentralized water allocation institution in place before 1987, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs (see Table~\ref{tab:cases} the \textbf{methods} for a detailed mathematical formula).
% 在不匹配条件下，边际成本减去边际收益增加，导致用水量增加，xx的差异反映了水配额模拟的非预期冲刺效应。
The unintended sprint effect (from 1987 to 1998) was caused by both declining marginal costs (a shift from a fixed unit cost to an irrelevant cost) and increasing marginal returns due to future water use benefits (see Table~\ref{tab:cases} the \textbf{methods} for a detailed mathematical formula).
% 因此，这种制度引发了一种与可持续用水意图背道而驰的激励扭曲。
The institution thus triggered an incentive distortion that ran counter to the intention of sustainable water use. Further, the strength of the sprint effect was positively correlated with the size and time horizon of the water use quota (Figure~\ref{fig:economic_model} \textbf{Panel B}).
% 这些理论上的预测正如我们在黄河流域所观察到的一样，不匹配的配额制度导致了短跑效应的出现，而中心化的制度结构结束了这一非预期的现象。
% These theoretical predictions, in line with phenomenon observed in the YRB, indicating the mismatched institution leads to incentive distortion of provinces for pre-empting resources by `sprinting', according to their expectations for the future.
% 这些理论预测进一步从YRB观察到的现象出发，表明不匹配的配额制度通过提高边际效益来刺激用水量，而边际效益与放宽限制带来的未来潜在用水量的影子值有关。
% These theoretical predictions, further from the phenomenon observed in the YRB, indicating the mismatched institution with quota stimulates water use by raising marginal benefits, which is related to the shadow value of potential future water use from relaxing the constraints.
% 温博推荐的版本：
% These theoretical predictions, further from the phenomenon observed in the YRB, attributing ``sprint effect'' into raising marginal benefits -by pursuing indirectly generating shadow value of water use while converting fixed marginal costs to irrelevant cost for each individual province.

\begin{table}[!ht]
	\centering
	\caption{Summary of marginal returns and marginal costs for each case }
	%\footnotesize
    \setlength{\tabcolsep}{1mm}{
       \begin{tabular}{lccc}
		\hline
		& Case 1: Decentralized Ins. & Case 2: Mismatched Ins. & Case 3: Matched Ins. \\ \hline
		Marginal return & $P*F'(X)$                & $P*F'(X)+V(X)^*$            & $P*F'(X)$              \\
		Marginal cost   & $C/N$                    & $Irrelevant$              & $C$                   \\ \hline
	\end{tabular}
    }
	\centering
	\footnotesize{\leftline{$^*$Note: $V(X)$ denotes a shadow value.}}
	\label{tab:cases}
\end{table}

\begin{figure}[!ht]
    \centering
    \includegraphics[width=12cm]{../../../figs/outputs/economic_model.jpg}
	\caption{
		% \textbf{Assumption 1:} \textit{(Production)} Assuming that water is the only input of the homogenous production function F(x) of each province. Under diminishing marginal returns assumption, and $F(x)$ is continuous, $F'(0)=\infty$, $ F'(\infty)=0$. The production output is under perfect competition, with constant unit price of P.
		% \textbf{Assumption 2:} \textit{(Cost function)} Assuming that the ecology is a unity for the whole basin, the cost of water use is equally assigned to each province under any water use. The unit cost of water is a constant C.
		% \textbf{Assumption 3:} \textit{(Multi-period setting)} There are infinite periods with constant discount factor $\beta$ lying in (0,1) with no cross-period smoothing in water uses.
		\textbf{A.} The relationship of marginal benefits and water use of province i at t = 0 for three different cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}, assuming $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, and $\beta=0.4$ as an example  (see \textit{Methods}In Case 3, water use by others is taken as a given, equal to the optimal water use for Case 2. The horizontal coordinate of each intersection of marginal benefits and the break-even line represents the optimal water use under each case.
		\textbf{Panel B.} The relation between optimal water use of province i and total quota for Case 3, under time horizon of $T=5$, $T=10$, and an infinite $T$, respectively. The settings are the same as in \textbf{A}.
	}
	\label{fig:economic_model}
\end{figure}

\section{Discussion}
% 我们展示了不匹配的分配制度是如何导致激励失真导致水资源加速耗竭的(即“冲刺效应”)。“冲刺效应”是CPR系统面临的一种特殊情况，在这种情况下，制度的不匹配为每个资源使用者创造了更强的动机(扭曲)，促使他们收回资源
We have shown how a mismatched allocation institution can lead to an accelerated depletion of water resources (i.e., the “sprint effect”) caused by incentive distortion. The sprint effect is a special case faced by CPR systems, where institutional mismatches create an even stronger incentive (with distortion) for each resource user to withdraw resources
\cite{ostromRevisitingCommonsLocal1999,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017}.
% 过往研究指出制度常常是避免公共池塘资源系统的崩溃的关键，但“短跑效应”的出现表明在自上而下进行制度设计所形成的错配SES结构中，制度也可以成为系统加速崩溃的触发者。
Previous studies have suggested that institutions are often the key to avoid the collapse of a CPR system, but the emergence of a sprint effect shows that an institution with structural mismatches can also be the trigger that accelerates system collapse \cite{bodinConservationSuccessFunction2014,bodinCollaborativeenvironmentalgovernance2017,wangAlignmentsocialecological2019}.
The initial formulation of the water quota in our case studies went through a stage of “bargaining” among stakeholders (from 1982 to 1987) \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}, where each province attempted to demonstrate its development potential related to water use.
% 在高层决策者与低层利益相关者之间存在信息不对称的用水分配中，当前用水量越大的利益相关者议价能力越大。1987年以后，对各省来说，合乎逻辑的下一步是试图证明争取更大配额的合理性，而不是立即采取资源节约型改革。在实践中，尽管受影响的省份可能没有直接鼓励过度使用资源，但由于激励扭曲，他们有更大的动机对资源提取开绿灯。因此，在争夺潜在的水资源配额时，各省往往将生态成本隐藏在经济发展背后。
In water use allocation with information asymmetry between upper-level decision-makers and lower-level stakeholders, those with more current water use might have greater bargaining power. After 1987, the logical next step for provinces was to attempt to justify bargaining for larger quotas rather than immediately adopt resource-conserving transformations. In practice, although the affected provinces may not have directly encouraged excessive resource use, they had a greater incentive to give the green light to resource withdrawals because of incentive distortions \cite{kriegerProgressGroundWater1955, ostromGoverningCommonsEvolution1990}. As a result, while competing for potential water quotas, the provinces tended to hide the ecological costs behind economic development.

% 毫无疑问，随着资源竞争的日趋激烈，越来越多的SES正依赖着不同形式的制度进行资源分配（如自组织和政府干预），避免“短跑效应”的出现或将成为制度设计的关键。
There is no doubt that with increasingly fierce competition for water, more and more SESs are developing new institutions for water allocation (whether through self-organization or government intervention) \cite{anderssonVoluntaryleadershipemergence2020, wutichWaterScarcitySustainability2009}.
% 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
Adoption of an overall quota plays an important role in preventing overuse of CPRs \cite{tilmanLocalizedprosocialpreferences2019}.
However, the negative effects of incentive distortion imply a trade-off between long-term SES benefits and current stability, and the proportion of available resources allocated under quota schemes matters when institutions change \cite{ladeRegimeshiftssocialecological2013}.
According to our analysis of plausible scenario assumptions based on our general economic model, the sprint effect will be reinforced when stakeholders anticipate that technological advances will amplify the benefits of water quotas in the future (see \textit{Supplementary Material S3}).
% 然而，如果有水权转换机制允许利益相关者之间通过交易来弥补 shadow value，当前这种错乱的动机就不会那么强。
However, if an institution allowed stakeholders to compensate for the shadow value (i.e., potential returns sacrificed due to water constraints and water scarcity) \cite{howarthAccountingvalueecosystem2002} of future water use, incentive distortion would be less devastating (e.g., through water rights transfer).
Policymakers can also weaken the sprint effect by increasing the frequency of quota updates, supporting the idea that a more dynamic institution that responds to changing conditions (see \textit{Supplementary Material S3}) will adapt more effectively to its social-ecological context.

% 近年来黄河流域面临的分水制度调整问题也说明了动态设置配额的重要性。
Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of dynamic quota setting (see \textit{Supplementary Material S1}) \cite{yuAdaptabilityassessmentpromotion2019}. Following the institutional reforms of 1998, the Yellow River has not dried up since 1999. However, given recent changes in the YRB, its rigid resource allocation scheme can no longer meet the new demands of economic development \cite{wangThingsCurrentSignificance2019}. The Chinese government has embarked on an ambitious plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}). Other SESs around the world face similar problems in establishing successful resource allocation institutions \cite{cummingQuantifyingSocialEcologicalScale2020, muneepeerakulStrategicbehaviorsgovernance2017, cummingAdvancingunderstandingnatural2020, leslieOperationalizingsocialecologicalsystems2015}. These initiatives can benefit from our analysis by actively considering and incorporating social-ecological complexity and incentive structures when developing new approaches that avoid unsustainable outcomes. Our research provides a cautionary tale of how institutions can act as a double-edged sword when trying to attain sustainability.

\section{Methods}
% 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程
We estimated and analyzed the net effects of two SES structural changes of water use. The actual water use of the Yellow River Basin was peroxided by the sum of the water use of the target group provinces. To quantify water use, we used synthetic control methods to estimate possible trends of water use in the absence of institutional shifts. In addition, as a robustness test, we conducted a matched placebo test (creating a “null model”) to exclude the effects of other factors that were contemporaneous with the institutional shifts. Finally, we created an economic model based on marginal revenue to provide a theoretical explanation for the observed “sprint effect” phenomenon. A brief technical overview is given in \textit{Supplementary Material S2}.

\subsection{Dataset and variables}
% 我们使用中国1978年至2012年各省的年度用水量数据集，这个公开的数据集由全国水资源利用调查得到，详细可查看。
We used China’s provincial annual water consumption dataset from 1978 to 2012. This publicly available dataset was obtained from the National Water Resources Utilization Survey; details are accessible from Zhou (2020)
\cite{zhouDecelerationChinahuman2020}.
A total of 10 provinces or regions have been directly affected by the water allocation institutional shifts in the YRB, accounting for $8.6\%$ of the total population of China (in 1990). Eight provinces have been particularly affected because of their greater dependence on the water resources from the Yellow River (see \textit{Supplementary Material S2}). Therefore, we divided the dataset into a “target group” and a “control group”, treating provinces that were greatly affected as the target group $(n=8)$ and provinces that were not affected by the institutional shifts as the potential control group $(n=20)$.

We focused on two features of water use in the YRB: total water use and diversification of water allocation. The actual water uses are given by the dataset, but when the synthetic control method is used to predict the water use of the control group, other independent influences need to be considered. Thus, we used economic features that are highly related to water use to extrapolate demand (e.g., agriculture, industry, service industry, and domestics, see \textit{Supplementary Material S2, Table 1} To measure resource allocation diversification between the upper, middle, and lower reaches, we used “entropy” as a simple index,

$$ Index_{entropy} = \sum_i{p_i *log(p_i)} $$

% 式子中的p是每个使用的水占流域总用水的比例
Where $p_i$ is the proportion of water uses for region $i$ to the total water uses in the basin. A larger index value indicates the proportion of water resources actually used is closer to the average among the upper, middle, and lower reaches.

\subsection{Synthetic Control}
Synthetic control is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadieSyntheticControlMethods2010}.
In this study, we used a comparative event approach and compared actual post-institutional shift induced water use changes with an appropriate counterfactual of what the water use change would have been.
The counterfactual was built as the optimally weighted average of provinces not exposed to the institutional shifts.
The synthetic control method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity \cite{billmeierAssessingEconomicLiberalization2013, smithresourcecurseexorcised2015}.
In practice, each of the units (i.e., provinces) in the treated group were affected by institutional shifts in 1987 and 1998, each of which was taken as the “shifted” point $t_0$ and the two steady institutions as $t$ for analyzing in each shift. The synthetic control method generates the control unit by assigning a weight matrix $W$ to units of the potential control group, so that the treated unit and its control unit are similar in each variable before $t_0$, i.e.,

$$\min(V_{i}^{t<t_0} - W_i * F_{control}^{t<t_0})$$

where $V_i$ is a vector that indicates all features of a unit $i$ of the treated group, and $F_{control}$ is a matrix that consists of all features and units of the potential control group. $W_i$ is the weight matrix for target unit $i$. We minimized the root mean square error (RMSE) by using the Synth package in R \cite{abadieSynthPackageSynthetic2011, abadieComparativePoliticsSynthetic2015}. All codes are accessible in the repository.

% 这样一来，基于降维的思想，我们构建出了一系列特征上与实验组最为接近的可比对照。
In accordance with the idea of dimensionality reduction, we constructed a series of comparable control units that were most similar in characteristics to the treated units. Because the units of the control group were not affected by the institutional shifts, after giving the same weight to the total water use of the control group $M_i * WU_{control}$, the result $W_i*WU_{control}$ could be considered a reasonable estimation of the untreated situation. The net effect of the water allocation institutional shift was then estimated by calculating the difference of water uses after the institutional shift between the treated group and the control group, compared with the water use difference before the shift.

\subsection{Placebo Test}
% 作为一种稳健性检验，安慰剂测试的必要性体现在两个原因上。
For robustness, we conducted a placebo test because the synthetic control method neglects the influences of overall changes in factors in the same year by simply dividing time periods according to institutional shifts. Three steps were required to apply the placebo test:
% (1) 对目标组中的每个省份$i$，计算所有潜在控制组与它之间特征向量的欧氏距离
(1) For each province in the target group, we calculated the Euclidean distance of vectors between all provinces in the potential control group.
% (2) 将距离由小到大排序后，选取特征向量最相似的三个省份，所有特征的均值作为 $i$ 的替代
(2) After ranking the distances, the three provinces with the most similar economic context were used to generate an average paired treatment target unit.
% (3) 对这个配对目标同样实施控制合成法（潜在控制组排除构成它的三个省）
(3) We performed the same synthetic control analysis for this paired target (i.e., the potential control group excluding the three provinces in step 2).
% 经过上述步骤，我们在理论上构建了一个相似的“区域”并实施了同样的控制合成实验。
In this way, we theoretically constructed a pseudo-treated unit and performed the same synthetic control treatments. Because these placebo tests were directed at units unaffected by the institutional shifts, the results can be regarded as a reasonable baseline expectation or null model from which to assess the changes caused by other factors.

\subsection{Economic model}
In order to understand the mechanisms underlying the empirical results, we developed a dynamic economic model to analyze how institutional change could have led to the sprint effect in water use. Specifically, we modeled individual provincial decision-making in water resources before quota execution. The analysis result implied that the underlying driver of CPR overuse was incentive distortion.

In developing the model, we highlighted the main features of the YRB, as well as the water use institutions of 1987 and 1998. We proposed three intuitive and general assumptions.

\begin{ass}
    % (生产)为了简化，由于不可替代性，水是每个省的同质生产函数10的唯一投入。$F(x)$是连续的，满足Inada条件，即$F'(x)>0, F''(x)<0$(边际收益递减假设)，$F'(0)=\infty$,$ F'(\infty)=0$。产品产量处于完全竞争状态，单位价格为15。
    (Water-dependent production) For simplicity, water is assumed to be the only input of the homogenous production function $F(x)$ of each province because of its irreplaceability. $F(x)$ is continuous and satisfies the Inada Conditions, i.e., $F'(x)>0, F''(x)<0$ (the diminishing marginal returns assumption), $F'(0)=\infty$,$ F'(\infty)=0$. The production output is under perfect competition, with a constant unit price of $P$.
\end{ass}
\begin{ass}
    (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in N provinces, the cost of water use is equally assigned to each province under any water use. The unit cost of water is a constant $C$.
\end{ass}
\begin{ass}
    (Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water uses.
\end{ass}

Under the above assumptions, we can demonstrate three cases consisting of local governments in YRB to simulate their water use decision-making and water use patterns.

\begin{case} Decentralized institution:
    This case corresponds to a situation without any high-level water allocation institution (i.e., before 1987, see Figure~\ref{fig:structure} B).

    When each province independently decides on its water use, the optimal water use $\hat x_i^*$ in province $i$ satisfies:
    $$F'(x)=\frac{C}{P \cdot N}$$

    When the decisions in different periods are independent, for $t=0,1,2 \ldots$, then:
    $$\hat x_{it}^*=\hat x_i^*$$

\end{case}

\begin{case} Mismatched institution
    This case corresponds to a mismatched institution (i.e., $1987\sim1998$, see Figure~\ref{fig:structure} C).

    The water quota is determined at $t=0$ and imposed in $t=1,2,\ldots$ The total quota is a constant denoted as $Q$, and the quota for province $i$ is determined in a proportional form:
    $$Q_i=Q \cdot \frac{x_i}{x_i + \begin{matrix} \sum x_{-i} \end{matrix}}$$

    Under a scenario with decentralized decision-making with a water quota institution, given other provinces’ water use decisions remain unchanged, the optimal water use $\widetilde x_{i0}^*$ of province $i$ at $t=0$ satisfies:

    $F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot f(Q \cdot \frac{x_{i,0}}{\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix})^2}$.

    When future water use is constrained by a water quota, the dynamic optimization problem of province $i$ is shown as follows:

    $max  \quad P \cdot F(x_{i,0})-\frac{C \cdot \begin{matrix} \sum x_{i,0} + x_{-i,0} \end{matrix}}{N}+\beta P \cdot F(x_{i,1})+\beta^2 P \cdot F(x_{i,2})+...$

    $=P \cdot F(x_{i,0})-C \cdot \frac{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}{N}+\frac{\beta}{1-\beta} P \cdot F(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}})$

    First-order condition: $P \cdot F'(x_{i,0})-\frac{C}{N}+\frac{\beta}{1-\beta}[P \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0}+\begin{matrix} \sum  x_{-i,0} \end{matrix})^2}]=0$

    where $f(\cdot)$ is the differential function of $F(\cdot)$.

    The optimal water use in province i at t=0 $\widetilde x_{i,0}^*$ satisfies $P \cdot F'(x_{i,0})=\frac{C}{N}-\frac{\beta}{1-\beta} \cdot P \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$, i.e., $F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$.

\end{case}

\begin{case} Matched institution

    This case corresponds to the institution under which the YRCC centrally managed water allocation between provinces (i.e., $1998\sim2008$, see Figure~\ref{fig:structure} D).

    When the $N$ provinces decide on water uses as unified whole (e.g., the central government completely decides and controls on the water use in each province), the optimal water use $x_i^*$ of province $i$ satisfies:

    $$F'(x)=\frac{C}{P}$$

\end{case}

We propose Proposition 1 and Proposition 2:

\textbf{Proposition 1}: Compared with the decentralized institution, a matched institution with unified management decreases total water use.

Because $F’$ is monotonically decreasing, based on a comparison of costs and benefits for stakeholders (provinces) in the three cases,

$$\widetilde x_i^*>\hat x_i^*>x_i^*$$

The result of $\hat x_i^*>x_i^*$ indicates that individual rationality would deviate from collective rationality when property rights are unclear \cite{hardinTragedyCommons2009}, because of the common-pool characteristics of water
\cite{castilla-rhoGroundwaterCommonPool2020,ostromGeneralFrameworkAnalyzing2009}.

The difference of $\widetilde x_i^*$ and $\hat x_i^*$ stems from two parts: the marginal returns effect and the marginal costs effect. First, the “shadow value” provides additional marginal returns of water use in $t=0$, wwhich increases the incentives of water overuse by encouraging bargaining for a larger quota. Second, the future cost of water use would be degraded from $\frac{P}{N}$ to an irrelevant cost.

The optimal water use under the three cases implies that mismatched institutions cause incentive distortions and lead to resource overuse.

\textbf{Proposition 2}: The quota determination of the mismatched institution increases the incentives of current water use.

The intuition for this proposition is straight-forward in that all provinces would use up their allocated quota under a relatively small $Q$. As $Q$ increases, the quota would provide higher future benefits for a pre-emptive water use strategy. Since the provincial water use decisions are exactly symmetric, total water use would increase when each province has higher incentives for current water use. This situation corresponds to a “sprint” effect, where the total water use dramatically increases in the “sprint” period.

Extensions of the model are shown in \textit{Supplementary Material S3}.

\section{Info.}
Funding was provided by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007).

[Competing Interests] The authors declare that they have no competing interests.

[Correspondence] Correspondence and requests for materials should be addressed to Shuai Wang.~(email: shuaiwang@bnu.edu.cn).

[Author contributions]Shuai Wang and Bojie Fu designed this research, Shuang Song performed the research and analyzed data, and Huiyu Wen designed the economic model. Shuang Song and Huiyu Wen wrote the paper, and Graeme S. Cumming revised the manuscript and offered important advice.

[Code availability] All codes and datasets used in this research are accessible at https://github.com/SongshGeo/sochyd-transboundary-HESS. They will be made open source after this project is completed.

%% Put the bibliography here, most people will use BiBTeX in
%% which case the environment below should be replaced with
%% the \bibliography{} command.
\bibliography{WAInstitution_YRB_2021}

%% Here is the endmatter stuff: Supplementary Info, etc.
%% Use \item's to separate, default label is "Acknowledgements"

\end{document}

### 2022-03-04 func/experiment.py

@@ -9,16 +9,11 @@
 import logging
 import os
 import pickle
-import ssl
-from tkinter.messagebox import NO
 
-import numpy as np
 import pandas as pd
 import yaml
-from matplotlib import pyplot as plt
 from qcloudsms_py import SmsSingleSender
 from qcloudsms_py.httpclient import HTTPError
-from SyntheticControlMethods import DiffSynth, Synth
 
 # BASIC testing settings.
 LOG_FORMAT = logging.Formatter(
@@ -31,7 +26,7 @@ def send_finish_message(name):
     # 短信应用SDK AppID
     appid = 1400630042  # SDK AppID是1400开头
     # 短信应用SDK AppKey
-    appkey = "ad30ec46aa617263813ca8996e1a0113"
+    app_key = "ad30ec46aa617263813ca8996e1a0113"
     # 需要发送短信的手机号码
     phone_numbers = ["18500685922"]
     # 短信模板ID，需要在短信应用中申请
@@ -39,12 +34,10 @@ def send_finish_message(name):
     # 签名
     sms_sign = "隅地公众号"
 
-    ssl._create_default_https_context = ssl._create_unverified_context
-
-    ssender = SmsSingleSender(appid, appkey)
+    s_sender = SmsSingleSender(appid, app_key)
     params = [name]  # 当模板没有参数时，`params = []`
     try:
-        result = ssender.send_with_param(
+        result = s_sender.send_with_param(
             86,
             phone_numbers[0],
             template_id,
@@ -54,11 +47,11 @@ def send_finish_message(name):
             ext="",
         )  # 签名参数不允许为空串
         print(result)
+        return result
     except HTTPError as e:
         print(e)
     except Exception as e:
         print(e)
-    return result
 
 
 class Experiment:

### 2022-03-04 func/model.py

@@ -1,3 +1,11 @@
+#!/usr/bin/env python 3.83
+# -*-coding:utf-8 -*-
+# Created date: 2022-02-10
+# @Author  : Shuang Song
+# @Contact   : SongshGeo@gmail.com
+# GitHub   : https://github.com/SongshGeo
+# Research Gate: https://www.researchgate.net/profile/Song_Shuang9
+
 import os
 import pickle
 
@@ -9,6 +17,11 @@ from tqdm import tqdm
 
 
 def do_synth_model(p):
+    """
+    Do a synth control modelling.
+    :param p:
+    :return:
+    """
     # 加载数据，排除所有的省份
     data = pd.read_csv(p["data_input"], index_col=0)
     if "province_exclude" in p:

### 2022-03-04 func/experiment.py
docs(docs): enrich docs of class and functions

@@ -12,6 +12,7 @@ import pickle
 
 import pandas as pd
 import yaml
+from attrs import define, field
 from qcloudsms_py import SmsSingleSender
 from qcloudsms_py.httpclient import HTTPError
 
@@ -22,7 +23,12 @@ LOG_FORMAT = logging.Formatter(
 DATE_FORMAT = "%Y-%m-%d  %H:%M:%S %a "
 
 
-def send_finish_message(name):
+def send_finish_message(num):
+    """
+    Send message to myself as notification.
+    :param num: experiment num
+    :return: dict, sending result from the network.
+    """
     # 短信应用SDK AppID
     appid = 1400630042  # SDK AppID是1400开头
     # 短信应用SDK AppKey
@@ -35,7 +41,7 @@ def send_finish_message(name):
     sms_sign = "隅地公众号"
 
     s_sender = SmsSingleSender(appid, app_key)
-    params = [name]  # 当模板没有参数时，`params = []`
+    params = [num]  # 当模板没有参数时，`params = []`
     try:
         result = s_sender.send_with_param(
             86,
@@ -54,15 +60,27 @@ def send_finish_message(name):
         print(e)
 
 
+@define
 class Experiment:
+    model = field(repr=False)
+    yaml_path: str = field(repr=False)
+    name: str = field(default=None, repr=True)
+    other_path: str = field(default=None, repr=False)
+    result: dict = field(default=None, repr=False)
+    state: str = field(default="Initialized", repr=True)
+
     def __init__(
         self,
         model,
         yaml_path,
         other_path=False,
-        output=None,
-        notification=False,
     ) -> None:
+        """
+        Initiate an experiment.
+        :param model: how to calculate the result.
+        :param yaml_path: parameters input.
+        :param other_path: save to another output path? default False.
+        """
         # 实验存储的路径
         if not other_path:
             experiment_path = os.path.dirname(yaml_path)  # 父级目录
@@ -78,25 +96,33 @@ class Experiment:
         self.p = p
         self.path = experiment_path
         self.log = None
-        self.name = p["name"]
+        if "name" in p:
+            self.name = p["name"]
+        else:
+            self.name = None
         self.model = model
-        self.output = output
         self.state = "Initialized"
         self.result = None
 
     def set_log_file(
         self, file_level=logging.DEBUG, cmd_level=logging.WARNING
     ):
+        """
+        set up log file
+        :param file_level: file logging level, default DEBUG (all).
[…]

### 2022-03-04 func/model.py

@@ -19,8 +19,8 @@ from tqdm import tqdm
 def do_synth_model(p):
     """
     Do a synth control modelling.
-    :param p:
-    :return:
+    :param p: parameters import from html
+    :return: results of experiment, dict of results
     """
     # 加载数据，排除所有的省份
     data = pd.read_csv(p["data_input"], index_col=0)
@@ -62,6 +62,11 @@ def do_synth_model(p):
 
 
 def transfer_exp_pickle_to_data(yaml_path):
+    """
+    Transform a pickle experiment result to comparable csv data.
+    :param yaml_path: YAML parameters data as a file path.
+    :return: transformed dataset.
+    """
     # open parameters
     with open(yaml_path, "r", encoding="utf-8") as file:
         params = yaml.load(file.read(), Loader=yaml.FullLoader)

### 2022-03-05 func/plots.py
feat(plots.py): add plot and style to ax by a beauty dict
seperate plot, data, and style

@@ -1,0 +1,60 @@
+#!/usr/bin/env python
+# -*-coding:utf-8 -*-
+# Created date: 2022/3/4
+# @Author  : Shuang Song
+# @Contact   : SongshGeo@gmail.com
+# GitHub   : https://github.com/SongshGeo
+# Research Gate: https://www.researchgate.net/profile/Song_Shuang9
+
+
+from attrs import define, field
+from matplotlib import pyplot as plt
+
+from func.tools import get_optimal_fit_linear
+
+# 自定义配色
+NATURE_PALETTE = {
+    "NS": "#c83c1c",
+    "Nature": "#29303c",
+    "NCC": "#0889a6",
+    "NC": "#f1801f",
+    "NG": "#006c43",
+    "NHB": "#1951A0",
+    "NEE": "#C7D530",
+}
+
+
+@define
+class BeautyPlot(object):
+    elements: dict = field(factory=dict, repr=True)
+    beauty_dicts: dict = field(factory=dict, repr=False)
+
+    def add_beauty_dict(self, label, beauty_dict):
+        self.beauty_dicts[label] = beauty_dict
+        return f"{beauty_dict} added."
+
+    def get_beauty_dict(self, label):
+        return self.beauty_dicts.get(label)
+
+    def add_element(self, data, ax, how, label):
+        beauty_dict = self.get_beauty_dict(label)
+        if hasattr(self, how):
+            func_ = getattr(self, how)
+            new_elements = func_(ax=ax, data=data, label=label)
+        elif not hasattr(ax, how):
+            raise "Incorrect plotting way."
+        else:
+            func_ = getattr(ax, how)
+            element = func_(*data, **beauty_dict)
+            new_elements = label, how, element
+            self.elements[label] = element
+        return new_elements
+
+    def linear_fit(self, ax, data, label):
+        beauty_points = self.get_beauty_dict(f"{label}_points")
+        beauty_line = self.get_beauty_dict(f"{label}_line")
+        scatter = ax.scatter(*data, **beauty_points)
+        y_sim = get_optimal_fit_linear(*data)
+        line = ax.plot(data[0], y_sim, **beauty_line, label=label)
+        self.elements[label] = (scatter, line)
+        return label, "linear_fit", line

### 2022-03-05 func/tools.py
feat(plot-tools): some tool functions for plotting

@@ -1,0 +1,33 @@
+#!/usr/bin/env python
+# -*-coding:utf-8 -*-
+# Created date: 2022/3/4
+# @Author  : Shuang Song
+# @Contact   : SongshGeo@gmail.com
+# GitHub   : https://github.com/SongshGeo
+# Research Gate: https://www.researchgate.net/profile/Song_Shuang9
+
+
+# 使用图片的比例来定位
+def get_position_by_ratio(ax, x_ratio, y_ratio):
+    """
+    使用图片的比例来返回定位，从而更好的控制说明文字的位置
+    ax: 一个 matplotlib 的画图轴对象
+    x_ratio: 横坐标的比例位置
+    y_ratio: 纵坐标的比例位置
+    """
+    x_min, x_max = ax.get_xlim()
+    y_min, y_max = ax.get_ylim()
+    x = (x_max - x_min) * x_ratio + x_min
+    y = (y_max - y_min) * y_ratio + y_min
+    return x, y
+
+
+def get_optimal_fit_linear(x_arr, y_arr):
+    from scipy import optimize
+
+    def linear(x, slope, intercept):
+        return slope * x + intercept
+
+    k, b = optimize.curve_fit(linear, x_arr, y_arr)[0]  # optimize
+    y_sim = linear(x_arr, k, b)  # simulated y
+    return y_sim

### 2022-03-06 config.py
feat(log): project logger

@@ -6,5 +6,77 @@
 # GitHub   : https://github.com/SongshGeo
 # Research Gate: https://www.researchgate.net/profile/Song_Shuang9
 
+import logging
+import os
 
+PROJECT_NAME = "WAInstitution_YRB_2021"
 ROOT = "/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021"
+
+# BASIC logging settings.
+LOG_FORMAT = "%(asctime)s %(levelname)s %(filename)s %(message)s "
+DATE_FORMAT = "%Y-%m-%d  %H:%M:%S %a "
+FILE_LEVEL = "debug"
+CMD_LEVEL = "warn"
+
+
+def set_logger(
+    name,
+    path=None,
+    reset=False,
+    log_format=None,
+    file_level="debug",
+    cmd_level="info",
+):
+    """
+    Setup a log file for my project.
+    :param name: logger's name
+    :param path: sub-folder path of the log file
+    :param reset: remove the old log file and refresh new one?
+    :param log_format: format of file message.
+    :param file_level: message save level in file.
+    :param cmd_level: message level print in CMD
+    :return: a logger.
+    """
+    logger = logging.getLogger(name)
+    logger.setLevel(logging.DEBUG)
+
+    file_level = getattr(logging, file_level.upper())
+    cmd_level = getattr(logging, cmd_level.upper())
+
+    if path:
+        file_path = os.path.join(ROOT, path, f"{name}.log")
+    else:
+        file_path = os.path.join(ROOT, f"{name}.log")
+    if not log_format:
+        log_format = LOG_FORMAT
+    if reset:
+        if not os.path.exists(file_path):
+            raise FileNotFoundError(
+                f"Logging file not found in {file_path}, no need of reset."
+            )
+        else:
+            os.remove(file_path)
+
+    # 建立一个 FileHandler 来把日志记录在文件里
+    file_handler = logging.FileHandler(file_path)
+    file_handler.setLevel(file_level)
+    file_handler.setFormatter(logging.Formatter(log_format))
+
+    # 建立一个 StreamHandler 来把日志打在CMD窗口上
+    cmd_handler = logging.StreamHandler()
+    cmd_handler.setLevel(cmd_level)
+    cmd_handler.setFormatter(logging.Formatter(log_format))
+
+    logger.addHandler(file_handler)
+    logger.addHandler(cmd_handler)
[…]

### 2022-03-06 config.py
refactor(experiment.py-and-config.py): restructure experiment class and yaml

@@ -69,7 +69,6 @@ def set_logger(
 
     logger.addHandler(file_handler)
     logger.addHandler(cmd_handler)
-    logger.info(f"{name} starts logging.")
     return logger
 
 

### 2022-03-06 func/experiment.py

@@ -6,219 +6,217 @@
 # GitHub   : https://github.com/SongshGeo
 # Research Gate: https://www.researchgate.net/profile/Song_Shuang9
 
-import logging
+import datetime
 import os
 import pickle
+import pprint
+import sys
 
-import pandas as pd
 import yaml
 from attrs import define, field
-from qcloudsms_py import SmsSingleSender
-from qcloudsms_py.httpclient import HTTPError
 
-# BASIC testing settings.
-LOG_FORMAT = logging.Formatter(
-    "%(asctime)s %(name)s %(levelname)s %(pathname)s %(message)s "
-)
-DATE_FORMAT = "%Y-%m-%d  %H:%M:%S %a "
+from config import ROOT
+from config import log as logger
+from config import set_logger
+from func.model import do_synth_model
+from func.tools import send_finish_message
 
-
-def send_finish_message(num):
-    """
-    Send message to myself as notification.
-    :param num: experiment num
-    :return: dict, sending result from the network.
-    """
-    # 短信应用SDK AppID
-    appid = 1400630042  # SDK AppID是1400开头
-    # 短信应用SDK AppKey
-    app_key = "ad30ec46aa617263813ca8996e1a0113"
-    # 需要发送短信的手机号码
-    phone_numbers = ["18500685922"]
-    # 短信模板ID，需要在短信应用中申请
-    template_id = 1299444
-    # 签名
-    sms_sign = "隅地公众号"
-
-    s_sender = SmsSingleSender(appid, app_key)
-    params = [num]  # 当模板没有参数时，`params = []`
-    try:
-        result = s_sender.send_with_param(
-            86,
-            phone_numbers[0],
-            template_id,
-            params,
-            sign=sms_sign,
-            extend="",
-            ext="",
-        )  # 签名参数不允许为空串
-        print(result)
-        return result
-    except HTTPError as e:
-        print(e)
-    except Exception as e:
-        print(e)
+# base_path = os.getcwd()
+# sys.path.append(base_path)
 
 
 @define
-class Experiment:
+class Experiment(object):
     model = field(repr=False)
-    yaml_path: str = field(repr=False)
     name: str = field(default=None, repr=True)
-    other_path: str = field(default=None, repr=False)
+    paths = field(factory=dict, repr=False)
     result: dict = field(default=None, repr=False)
     state: str = field(default="Initialized", repr=True)
+    datasets: dict = field(factory=dict, repr=False)
[…]

### 2022-03-06 func/experiment.py
refactor(tools,-*.yaml,-experiment.py): restructure experiment

@@ -21,9 +21,6 @@ from config import set_logger
 from func.model import do_synth_model
 from func.tools import send_finish_message
 
-# base_path = os.getcwd()
-# sys.path.append(base_path)
-
 
 @define
 class Experiment(object):
@@ -36,6 +33,8 @@ class Experiment(object):
     parameters: dict = field(factory=dict, repr=False)
     analysis: dict = field(factory=dict, repr=False)
     log = field(default=None, repr=False)
+    authors = field(factory=list, repr=False)
+    description: str = field(default=None, repr=True)
     _updated_time = field(default=None, repr=True)
     _strftime = field(default="%Y-%m-%d, %H:%M:%S", repr=False)
     _run_time = field(default="", repr=False)
@@ -83,6 +82,8 @@ class Experiment(object):
             self.parameters = parameters.get("parameters")
             self.analysis = parameters.get("analysis")
             self.datasets = parameters.get("datasets")
+            self.description = parameters.get("description")
+            self.authors = parameters.get("author")
 
             # root path: from yaml > default project root
             root = parameters.get("root")
@@ -216,7 +217,7 @@ if __name__ == "__main__":
     YAML_PATH = sys.argv[1]
     exp = Experiment(do_synth_model, YAML_PATH)
 
-    # sc_result = exp.do_experiment(notification=True)
+    sc_result = exp.do_experiment(notification=True)
     exp.drop_exp_to_pickle()
     logger.info(exp.state)
     pprint.pprint(exp.paths)

### 2022-03-06 func/tools.py

@@ -6,6 +6,46 @@
 # GitHub   : https://github.com/SongshGeo
 # Research Gate: https://www.researchgate.net/profile/Song_Shuang9
 
+from qcloudsms_py import SmsSingleSender
+from qcloudsms_py.httpclient import HTTPError
+
+
+def send_finish_message(num):
+    """
+    Send message to myself as notification.
+    :param num: experiment num
+    :return: dict, sending result from the network.
+    """
+    # 短信应用SDK AppID
+    appid = 1400630042  # SDK AppID是1400开头
+    # 短信应用SDK AppKey
+    app_key = "ad30ec46aa617263813ca8996e1a0113"
+    # 需要发送短信的手机号码
+    phone_numbers = ["18500685922"]
+    # 短信模板ID，需要在短信应用中申请
+    template_id = 1299444
+    # 签名
+    sms_sign = "隅地公众号"
+
+    s_sender = SmsSingleSender(appid, app_key)
+    params = [num]  # 当模板没有参数时，`params = []`
+    try:
+        result = s_sender.send_with_param(
+            86,
+            phone_numbers[0],
+            template_id,
+            params,
+            sign=sms_sign,
+            extend="",
+            ext="",
+        )  # 签名参数不允许为空串
+        print(result)
+        return result
+    except HTTPError as e:
+        print(e)
+    except Exception as e:
+        print(e)
+
 
 # 使用图片的比例来定位
 def get_position_by_ratio(ax, x_ratio, y_ratio):

### 2022-03-07 config.py
feat(handle-experiment): experiment with yaml parameters, well structured, easy to handle
now structure like this: model and handler -> experiment <- data and parameter

BREAKING CHANGE:

@@ -12,6 +12,19 @@ import os
 PROJECT_NAME = "WAInstitution_YRB_2021"
 ROOT = "/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021"
 
+SCHEME_87 = {
+    "Qinghai": 1.41,
+    # 'Sichuan': 0.04,
+    "Gansu": 3.04,
+    "Ningxia": 4.00,
+    "Neimeng": 5.86,
+    "Shanxi": 3.80,
+    "Shaanxi": 4.31,
+    "Henan": 5.54,
+    "Shandong": 7,
+    # 'Jinji': 2
+}
+
 # BASIC logging settings.
 LOG_FORMAT = "%(asctime)s %(levelname)s %(filename)s %(message)s "
 DATE_FORMAT = "%Y-%m-%d  %H:%M:%S %a "

### 2022-03-07 func/experiment.py

@@ -21,6 +21,10 @@ from config import set_logger
 from func.model import do_synth_model
 from func.tools import send_finish_message
 
+# # If needed in cmd:
+# base = os.getcwd()
+# sys.path.append(base)
+
 
 @define
 class Experiment(object):
@@ -123,9 +127,10 @@ class Experiment(object):
         self.paths["log"] = os.path.join(root, f"{logger.name}.log")
 
         for dataset in self.datasets.keys():
-            self.paths[dataset] = os.path.join(
-                root, self.datasets.get(dataset)
-            )
+            full_dataset_path = os.path.join(root, self.datasets.get(dataset))
+            self.paths[dataset] = full_dataset_path
+            self.datasets[dataset] = full_dataset_path
+
         for key, path in self.paths.items():
             if not os.path.exists(path):
                 os.mkdir(path)

### 2022-03-07 func/handle.py

@@ -1,0 +1,129 @@
+#!/usr/bin/env python
+# -*-coding:utf-8 -*-
+# Created date: 2022/3/4
+# @Author  : Shuang Song
+# @Contact   : SongshGeo@gmail.com
+# GitHub   : https://github.com/SongshGeo
+# Research Gate: https://www.researchgate.net/profile/Song_Shuang9
+
+import os
+import pickle
+
+import numpy as np
+import pandas as pd
+import yaml
+from attrs import define
+
+
+@define
+class ExpResultsHandler(object):
+    """
+    Experiment handler, for exploring results easier.
+    """
+
+    def correlation_stimulation(self):
+        pass
+
+    def original_plots(self, province, save=True):
+        # TODO put this functions into handle class.
+        if save:
+            # 储存图像路径
+            figs_folder = os.path.join(self.exp_path, "figs")
+            if not os.path.exists(figs_folder):
+                os.mkdir(figs_folder)
+
+            # 图像展示
+            self.result[province].plot(
+                ["original", "pointwise", "cumulative"],
+                treated_label=province,
+                synth_label=f"Synthetic {province}",
+                treatment_label=f"Treatment in {self.parameters['treat_year']}",
+                save_path=os.path.join(figs_folder, f"{province}.jpg"),
+            )
+        else:
+            # 图像展示
+            self.result[province].plot(
+                ["original", "pointwise", "cumulative"],
+                treated_label=province,
+                synth_label=f"Synthetic {province}",
+                treatment_label=f"Treatment in {self.parameters['treat_year']}",
+            )
+
+    def weight_df(self, province="all"):
+        if province == "all":
+            weights = {}
+            for p in self.result.keys():
+                weights[p] = self.result[p].original_data.weight_df
+        else:
+            weights = self.result[province].original_data.weight_df
+        return weights
+
+    def original_comparison(self, province="all"):
+        if province == "all":
+            comparison = pd.DataFrame()
+            for p in self.result.keys():
+                comparison_df = self.result[p].original_data.comparison_df
+                # 把获取的结果储存到同一个表中
+                for col in comparison_df:
+                    # WMAPE is a indicator to stimulation of Synth Control.
+                    if col == "WMAPE":
+                        comparison[col + "_" + p] = comparison_df[col]
+                    else:
+                        comparison[col] = comparison_df[col]
+        else:
[…]

### 2022-03-07 func/model.py

@@ -6,98 +6,152 @@
 # GitHub   : https://github.com/SongshGeo
 # Research Gate: https://www.researchgate.net/profile/Song_Shuang9
 
-import os
-import pickle
-
-import numpy as np
 import pandas as pd
-import yaml
+from attrs import define, field
 from SyntheticControlMethods import Synth
 from tqdm import tqdm
 
+from config import log
 
-def do_synth_model(p):
+
+@define
+class ProvinceSynth(Synth):
+    """Data input"""
+
+    province: str = field(default=None, repr=True)
+
+    def __init__(
+        self,
+        dataset,
+        outcome_var,
+        id_var,
+        time_var,
+        treatment_period,
+        treated_unit,
+        n_optim=10,
+        pen=0,
+        exclude_columns=None,
+        random_seed=0,
+        **kwargs,
+    ):
+        if exclude_columns is None:
+            exclude_columns = []
+        super().__init__(
+            dataset,
+            outcome_var,
+            id_var,
+            time_var,
+            treatment_period,
+            treated_unit,
+            n_optim,
+            pen,
+            exclude_columns,
+            random_seed,
+            verbose=False,
+            **kwargs,
+        )
+        self.province = treated_unit
+
+    def diff_plot(self, ax, bp):
+        data = self.original_data
+        time = data.dataset[data.time].unique()
+        treat = data.treatment_period
+        synthetic = data.synth_outcome.T  # Synthetic
+        original = data.treated_outcome_all  # Original
+        temp_data = pd.DataFrame(
+            data={
+                "time": time,
+                "origin": original,
+                "synth": synthetic,
+            }
+        )
+        before = temp_data[temp_data["time"] <= treat]
+        after = temp_data[temp_data["time"] > treat]
+        bp.add_element(
+            data=(before["time"], before["origin"]),
+            ax=ax,
+            how="plot",
+            label="before_observation",
+        )
+        bp.add_element(
+            data=(before["time"], before["synth"]),
+            ax=ax,
+            how="plot",
+            label="before_prediction",
+        )
+        bp.add_element(
+            data=(after["time"], after["origin"]),
+            ax=ax,
+            how="linear_fit",
+            label="after_observation",
+        )
+        bp.add_element(
+            data=(after["time"], after["synth"]),
+            ax=ax,
+            how="linear_fit",
+            label="after_prediction",
+        )
+        bp.add_element(
[…]

### 2022-03-09 config.py
feat(handle.py-experiment.py-model.py-config.py): now handle experiment smoothly, by loading pickle files
BREAKING CHANGE:

@@ -37,8 +37,28 @@ PROVINCES_CHN2ENG = {
     "山东": "Shandong",
     "河北": "Hebei",
     "天津": "Tianjin",
+    "北京": "Beijing",
     "河北和天津": "Jinji",
     "津冀": "Jinji",
+    "辽宁": "Liaoning",
+    "吉林": "Jilin",
+    "黑龙江": "Heilongjiang",
+    "上海": "Shanghai",
+    "江苏": "Jiangsu",
+    "云南": "Yunnan",
+    "安徽": "Anhui",
+    "广东": "Guangdong",
+    "广西": "Guangxi",
+    "新疆": "Xinjiang",
+    "江西": "Jiangxi",
+    "浙江": "Zhejiang",
+    "海南": "Hainan",
+    "湖北": "Hubei",
+    "湖南": "Hunan",
+    "福建": "Fujian",
+    "西藏": "Tibet",
+    "贵州": "Guizhou",
+    "重庆": "Chongqing",
 }
 
 # BASIC logging settings.

### 2022-03-09 func/experiment.py

@@ -21,10 +21,6 @@ from config import set_logger
 from func.model import do_synth_model
 from func.tools import send_finish_message
 
-# # If needed in cmd:
-# base = os.getcwd()
-# sys.path.append(base)
-
 
 @define
 class Experiment(object):
@@ -45,9 +41,9 @@ class Experiment(object):
 
     def __init__(
         self,
-        model,
         yaml_file,
         name="exp",
+        model=None,
         experiment_path=None,
         results_path=None,
     ):
@@ -91,8 +87,6 @@ class Experiment(object):
 
             # root path: from yaml > default project root
             root = parameters.get("root")
-            if not root:
-                root = ROOT
             os.chdir(root)
             if not results_path:
                 results_path = os.path.join(
@@ -165,13 +159,16 @@ class Experiment(object):
         self.paths["log"] = os.path.join(exp_path, f"{self.name}.log")
         return exp_log
 
-    def do_experiment(self, notification=False):
+    def do_experiment(self, model=None, notification=False):
         """
         Main func, do experiment.
+        :param model: how to do the experiment.
         :param notification: send message to user.
         :return: state of the experiment.
         """
         log = self.log
+        if model:
+            self.model = model
         # Do experiment
         log.info(f"Start experiment, model: {self.model.__name__}.")
         start_time = datetime.datetime.now()
@@ -214,13 +211,81 @@ class Experiment(object):
             self.log.info(f"Saved as pickle file {file_path}")
         self.paths["experiment_pickle"] = file_path
 
+    def load_from_pickle(self):
+        with open(self.paths.get("yaml"), "r", encoding="utf-8") as file:
+            params = yaml.load(file.read(), Loader=yaml.FullLoader)
+            root = params.get("root")
+            result_path = params.get("results_path")
+            file.close()
+        path = os.path.join(root, result_path, "exp_experiment.pkl")
+        with open(path, "rb") as pkl:
+            obj = pickle.load(pkl)
+        return obj
+
+    def list_datasets(self):
+        names = self.datasets.keys()
+        categories = []
+        for name in names:
+            if "processed" in self.datasets.get(name):
+                category = "processed"
+            elif "result" in self.datasets.get(name):
+                category = "result"
+            else:
+                category = "Unknown"
+            categories.append(category)
+        return [(n, c) for n, c in zip(names, categories)]
+
+    def update(self, attr=None, val=None, msg="Nothing."):
[…]

### 2022-03-09 func/handle.py

@@ -6,23 +6,155 @@
 # GitHub   : https://github.com/SongshGeo
 # Research Gate: https://www.researchgate.net/profile/Song_Shuang9
 
+import inspect
 import os
-import pickle
 
 import numpy as np
 import pandas as pd
-import yaml
-from attrs import define
+import pingouin as pg
+from attrs import define, field
+from experiment import Experiment
+from matplotlib import pyplot as plt
+from tools import extract_mean_std
 
 
 @define
-class ExpResultsHandler(object):
+class ExpResultsHandler(Experiment):
     """
     Experiment handler, for exploring results easier.
     """
 
-    def correlation_stimulation(self):
-        pass
+    dfs: dict = field(factory=dict, repr=False)
+    provinces: list = field(factory=list, repr=False)
+
+    def __init__(self, yaml_file):
+        super().__init__(yaml_file)
+        self.dfs = {}
+        self.provinces = []
+
+    def load_processed_datasets(self):
+        """Load processed datasets from disk."""
+        for key in self.datasets.keys():
+            data = pd.read_csv(self.datasets.get(key), index_col=0)
+            self.dfs[key] = data
+            self.log.info(f"{key} dataset loaded from disk.")
+        return self.dfs.keys()
+
+    def load_from_pickle(self):
+        """Load exp results from pickle."""
+        checks = [inspect.ismethod, inspect.isbuiltin]
+        experiment = super().load_from_pickle()
+        for attr in dir(experiment):
+            obj = getattr(experiment, attr)
+            if attr.startswith("__"):
+                continue
+            if any([check(obj) for check in checks]):
+                continue
+            val = getattr(experiment, attr)
+            setattr(self, attr, val)
+        self.state = "loaded"
+        self.load_processed_datasets()
+        self.provinces = list(self.result.keys())
+        return self
+
+    def transfer_exp_pickle_to_data(self, save=False):
+        """
+        Transform a pickle experiment result to comparable csv data.
+        """
+        params = self.parameters
+
+        # save datasets
+        dataset = pd.DataFrame(
+            index=np.arange(params["start"], params["end"] + 1)
+        )  # time
+        for province, synth_result in self.result.items():
+            synth_data = (
+                synth_result.original_data.synth_outcome.T
+            )  # Synth label
+            actual_data = (
[…]

### 2022-03-09 func/model.py

@@ -11,8 +11,6 @@ from attrs import define, field
 from SyntheticControlMethods import Synth
 from tqdm import tqdm
 
-from config import log
-
 
 @define
 class ProvinceSynth(Synth):
@@ -107,7 +105,7 @@ def do_synth_once(province, data, outside_data, used_variables, parameters):
     ]
     used_data = used_period[used_variables]
 
-    sc = ProvinceSynth(
+    sc = Synth(
         used_data,
         parameters["Y_inputs"],
         "Province",

### 2022-03-09 func/tools.py

@@ -71,3 +71,8 @@ def get_optimal_fit_linear(x_arr, y_arr):
     k, b = optimize.curve_fit(linear, x_arr, y_arr)[0]  # optimize
     y_sim = linear(x_arr, k, b)  # simulated y
     return y_sim
+
+
+def extract_mean_std(data, start, end):
+    data = data.loc[start:end, :]
+    return data.mean(), data.std()

### 2022-03-10 config.py
feat(placebo-plots,-panel-plots): now plow placebo and other plots by panel
make it easier to handle exp results.

BREAKING CHANGE:

@@ -45,7 +45,7 @@ PROVINCES_CHN2ENG = {
     "黑龙江": "Heilongjiang",
     "上海": "Shanghai",
     "江苏": "Jiangsu",
-    "云南": "Yunnan",
+    "云南": "Yunan",
     "安徽": "Anhui",
     "广东": "Guangdong",
     "广西": "Guangxi",
@@ -59,6 +59,9 @@ PROVINCES_CHN2ENG = {
     "西藏": "Tibet",
     "贵州": "Guizhou",
     "重庆": "Chongqing",
+    "中国": "China",
+    "内蒙": "Neimeng",
+    "黑龙": "Heilongjiang",
 }
 
 # BASIC logging settings.

### 2022-03-10 func/experiment.py

@@ -172,7 +172,7 @@ class Experiment(object):
         # Do experiment
         log.info(f"Start experiment, model: {self.model.__name__}.")
         start_time = datetime.datetime.now()
-        result = self.model(self.datasets, self.parameters)
+        result = self.model(self.datasets, self.parameters, self.analysis)
         self.state = "finished"
         log.info("End experiment.")
 

### 2022-03-10 func/handle.py

@@ -12,9 +12,11 @@ import os
 import numpy as np
 import pandas as pd
 import pingouin as pg
+import seaborn as sns
 from attrs import define, field
 from experiment import Experiment
 from matplotlib import pyplot as plt
+from plots import basic_plot
 from tools import extract_mean_std
 
 
@@ -62,21 +64,15 @@ class ExpResultsHandler(Experiment):
         Transform a pickle experiment result to comparable csv data.
         """
         params = self.parameters
-
-        # save datasets
-        dataset = pd.DataFrame(
-            index=np.arange(params["start"], params["end"] + 1)
-        )  # time
+        years = np.arange(params["start"], params["end"] + 1)
+        dataset = pd.DataFrame(index=years)
         for province, synth_result in self.result.items():
-            synth_data = (
-                synth_result.original_data.synth_outcome.T
-            )  # Synth label
-            actual_data = (
-                synth_result.original_data.treated_outcome_all
-            )  # original data
+            data = synth_result.original_data
+            synth_data = data.synth_outcome.T.ravel()  # Synth label
+            actual_data = data.treated_outcome_all.ravel()  # original data
+
             dataset[f"{province}_synth"] = synth_data
             dataset[f"{province}_actual"] = actual_data
-
         if save:
             path = os.path.join(
                 self.paths.get("results"),
@@ -156,6 +152,83 @@ class ExpResultsHandler(Experiment):
         ax.set_ylabel(f"Partial Corr to {y}")
         return r_results, p_val
 
+    def plot(self, panels, province):
+        sc = self.result.get(province)
+        sc.plot(panels)
+
+    def panel_plots(self, how="original", save_path=None):
+        fig, (axs1, axs2) = plt.subplots(2, 4, figsize=(16, 8))
+        axs = []
+        axs.extend(axs1)
+        axs.extend(axs2)
+        for province, ax in zip(self.provinces, axs):
+            sc = self.result.get(province)
+            basic_plot(how=how, ax=ax, sc=sc)
+        pass
+
+    def outcome_panel_data(self, outcome_var, save=False, plot=False):
+        params = self.parameters
+        datasets = []
+        for province in self.provinces:
+            sc = self.result.get(province)
+            data = sc.original_data
+            years = np.arange(params["start"], params["end"] + 1)
+            synth_data = data.synth_outcome.T.ravel()  # Synth label
+            actual_data = data.treated_outcome_all.ravel()  # original data
+            df = pd.DataFrame(
+                {
+                    "Year": years,
[…]

### 2022-03-10 func/model.py

@@ -119,11 +119,12 @@ def do_synth_once(province, data, outside_data, used_variables, parameters):
     return sc
 
 
-def do_synth_model(datasets, parameters):
+def do_synth_model(datasets, parameters, analysis):
     """
     Do a synth control modelling.
     :param datasets: {name: path} dictionary of necessary input datasets.
     :param parameters: necessary parameters import from html.
+    :param analysis:
     :return: results of experiment, dict of results.
     """
     # 加载数据，排除所有的省份
@@ -142,13 +143,19 @@ def do_synth_model(datasets, parameters):
     sc_results = {}
     for province in tqdm(parameters["province_include"]):
         print(f"solving {province}!...")
-        sc_results[province] = do_synth_once(
+        sc = do_synth_once(
             province=province,
             data=data,
             outside_data=outside_data,
             used_variables=used_variables,
             parameters=parameters,
         )
+        if analysis["placebo"]:
+            sc.in_time_placebo(
+                parameters["placebo_time"], n_optim=parameters["placebo_optim"]
+            )
+            sc.in_space_placebo(parameters["placebo_optim"])
+        sc_results[province] = sc
     return sc_results
 
 

### 2022-03-10 func/plots.py

@@ -6,8 +6,8 @@
 # GitHub   : https://github.com/SongshGeo
 # Research Gate: https://www.researchgate.net/profile/Song_Shuang9
 
-import inspect
 
+import numpy as np
 from attrs import define, field
 
 from func.tools import get_optimal_fit_linear
@@ -58,3 +58,245 @@ class BeautyPlot(object):
         line = ax.plot(data[0], y_sim, **beauty_line, label=label)
         self.elements[label] = (scatter, line)
         return label, "linear_fit", line
+
+
+def basic_plot(
+    how,
+    sc,
+    ax,
+    treated_label="Treated Unit",
+    synth_label="Synthetic Treated Unit",
+    treatment_label="Treatment",
+    in_space_exclusion_multiple=5,
+):
+    """
+    Supported plots:
+      original:
+        Outcome of the treated unit and the synthetic control unit for all time periods
+
+      pointwise:
+        Difference between the outcome of the treated and synthetic control unit
+        I.e. same as original but normalized wrt. the treated unit
+
+      cumulative:
+        Sum of pointwise differences in the post treatment period
+        I.e. the cumulative treatment effect
+
+      in-space placebo:
+        Pointwise plot of synthetic control and in-space placebos
+
+        Procedure:
+        Fits a synthetic control to every control unit.
+        These synthetic controls are referred to "in-space placebos"
+
+      pre/post rmspe:
+        Histogram showing
+        (post-treatment rmspe) / (pre-treatment rmspe)
+        for real synthetic control and all placebos
+
+        Extreme values indicates small difference in pre-period with
+        large difference (estimated treatment effect) in the post-period
+        Treated unit should be more extreme than placebos to indicate significance
+
+
+    Arguments:
+      panels : list of strings
+        list of the plots to be generated
+
+      figsize : tuple (int, int)
+        argument to plt.figure
+        First value indicated desired width of plot, second the height
+        The height height is divided evenly between each subplot, whereas each subplot has full width
+        E.g. three plots: each subplot will have figure size (width, height/3)
+
+      treated_label : str
+        Label for treated unit in plot title and legend
+
+      synth_label : str
+        Label for synthetic control unit in plot title and legend
+
[…]

### 2022-03-10 config.py
refactor(config.py-model.py-handle.py-experiment.py): now run config.py to do experiment. analysis automatically, and analysis by yzr data
guangdong is a special outline data.

BREAKING CHANGE:

@@ -8,6 +8,11 @@
 
 import logging
 import os
+import sys
+
+from func.experiment import Experiment
+from func.handle import ExpResultsHandler
+from func.model import do_synth_analysis, do_synth_model
 
 PROJECT_NAME = "WAInstitution_YRB_2021"
 ROOT = "/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021"
@@ -127,7 +132,22 @@ def set_logger(
 log = set_logger(PROJECT_NAME, file_level=FILE_LEVEL, cmd_level=CMD_LEVEL)
 
 if __name__ == "__main__":
-    log = set_logger(
-        PROJECT_NAME, reset=True, file_level="info", cmd_level="warn"
-    )
-    log.info("LOG reset.")
+    # Do experiment model and analysis from CMD.
+    YAML_PATH = sys.argv[1]
+    exp = ExpResultsHandler(yaml_file=YAML_PATH)
+
+    # Change to a special logger.
+    exp_rel_path = exp.get_path("experiment", absolute=False)
+    exp_log = set_logger(exp.name, path=exp_rel_path)
+    exp.change_experiment_logger(exp_log)
+
+    # modelling
+    sc_result = exp.do_experiment(model=do_synth_model, notification=True)
+    exp.drop_exp_to_pickle()
+
+    # analysis
+    exp.do_analysis(model=do_synth_analysis)
+    exp.drop_exp_to_pickle()
+
+    exp.log.info(exp.state)
+    pass

### 2022-03-10 func/experiment.py

@@ -7,18 +7,13 @@
 # Research Gate: https://www.researchgate.net/profile/Song_Shuang9
 
 import datetime
+import logging
 import os
 import pickle
-import pprint
-import sys
 
 import yaml
 from attrs import define, field
 
-from config import ROOT
-from config import log as logger
-from config import set_logger
-from func.model import do_synth_model
 from func.tools import send_finish_message
 
 
@@ -46,6 +41,7 @@ class Experiment(object):
         model=None,
         experiment_path=None,
         results_path=None,
+        log=None,
     ):
         """
         Initiate an experiment, as the following structure.
@@ -100,7 +96,9 @@ class Experiment(object):
 
         # basic attributions
         self.name = name
-        self.log = logger
+        if not log:
+            log = logging.getLogger(__file__)
+        self.log = log
         self.model = model
         self.state = "Initialized"
         self.paths = {}
@@ -118,7 +116,7 @@ class Experiment(object):
         self.paths["results"] = os.path.abspath(
             os.path.join(root, results_path)
         )
-        self.paths["log"] = os.path.join(root, f"{logger.name}.log")
+        self.paths["log"] = os.path.join(root, f"{self.log.name}.log")
 
         for dataset in self.datasets.keys():
             full_dataset_path = os.path.join(root, self.datasets.get(dataset))
@@ -126,9 +124,11 @@ class Experiment(object):
             self.datasets[dataset] = full_dataset_path
 
         for key, path in self.paths.items():
+            if key == "log":
+                continue
             if not os.path.exists(path):
                 os.mkdir(path)
-                logger.warning(
+                self.log.warning(
                     f"{key} folder made in {os.path.dirname(path)}."
                 )
 
@@ -140,7 +140,7 @@ class Experiment(object):
         else:
             return os.path.relpath(path, root)
 
-    def set_experiment_log(self, **kwargs):
+    def change_experiment_logger(self, exp_log):
         """
         Set up log file to this experiment and switch the default logger.
         :return: The new exp logger.
@@ -148,11 +148,10 @@ class Experiment(object):
         # Default project logger
         exp_path = self.get_path("experiment")
         exp_rel_path = self.get_path("experiment", absolute=False)
-        logger.warning(
+        self.log.warning(
             f"Experiment {self.name} log file will be set under {exp_rel_path}."
         )
         # Change logger
[…]

### 2022-03-10 func/handle.py

@@ -5,7 +5,7 @@
 # @Contact   : SongshGeo@gmail.com
 # GitHub   : https://github.com/SongshGeo
 # Research Gate: https://www.researchgate.net/profile/Song_Shuang9
-
+import copy
 import inspect
 import os
 
@@ -14,10 +14,11 @@ import pandas as pd
 import pingouin as pg
 import seaborn as sns
 from attrs import define, field
-from experiment import Experiment
 from matplotlib import pyplot as plt
-from plots import basic_plot
-from tools import extract_mean_std
+
+from func.experiment import Experiment
+from func.plots import basic_plot
+from func.tools import extract_mean_std
 
 
 @define
@@ -28,11 +29,16 @@ class ExpResultsHandler(Experiment):
 
     dfs: dict = field(factory=dict, repr=False)
     provinces: list = field(factory=list, repr=False)
+    time_placebo_results: dict = field(factory=dict, repr=False)
 
-    def __init__(self, yaml_file):
-        super().__init__(yaml_file)
+    def __init__(self, experiment=None, yaml_file=None):
+        if experiment:
+            yaml_file = experiment.paths.get("yaml")
+        if yaml_file:
+            super().__init__(yaml_file)
         self.dfs = {}
         self.provinces = []
+        self.time_placebo_results = {}
 
     def load_processed_datasets(self):
         """Load processed datasets from disk."""
@@ -88,7 +94,9 @@ class ExpResultsHandler(Experiment):
     def get_statistic_df(self, save=False):
         provinces = self.result.keys()
         data = self.transfer_exp_pickle_to_data()
-        start, end = self.parameters.get("start"), self.parameters.get("end")
+        start, end = self.parameters.get("treat_year"), self.parameters.get(
+            "end"
+        )
         statistic = pd.DataFrame(index=provinces)
         for province in provinces:
             diff = data[f"{province}_actual"] - data[f"{province}_synth"]
@@ -164,6 +172,9 @@ class ExpResultsHandler(Experiment):
         for province, ax in zip(self.provinces, axs):
             sc = self.result.get(province)
             basic_plot(how=how, ax=ax, sc=sc)
+        if save_path:
+            self.log.info(f"Panel plots saved in {save_path}.")
+            fig.save(save_path, dpi=300)
         pass
 
     def outcome_panel_data(self, outcome_var, save=False, plot=False):
@@ -292,15 +303,29 @@ class ExpResultsHandler(Experiment):
             self.result[province].in_time_placebo(
[…]

### 2022-03-10 func/model.py

@@ -119,12 +119,11 @@ def do_synth_once(province, data, outside_data, used_variables, parameters):
     return sc
 
 
-def do_synth_model(datasets, parameters, analysis):
+def do_synth_model(datasets, parameters):
     """
     Do a synth control modelling.
     :param datasets: {name: path} dictionary of necessary input datasets.
     :param parameters: necessary parameters import from html.
-    :param analysis:
     :return: results of experiment, dict of results.
     """
     # 加载数据，排除所有的省份
@@ -150,13 +149,17 @@ def do_synth_model(datasets, parameters, analysis):
             used_variables=used_variables,
             parameters=parameters,
         )
-        if analysis["placebo"]:
-            sc.in_time_placebo(
-                parameters["placebo_time"], n_optim=parameters["placebo_optim"]
-            )
-            sc.in_space_placebo(parameters["placebo_optim"])
         sc_results[province] = sc
     return sc_results
+
+
+def do_synth_analysis(exp, parameters, analysis):
+    if analysis["placebo"]:
+        exp.do_in_place_placebo()
+        exp.do_in_time_placebo()
+    if analysis["iter_placebo"]:
+        span = parameters.get("placebo_iter_span")
+        exp.iter_time_placebo(span=span)
 
 
 if __name__ == "__main__":

### 2022-03-10 docs/papers/elements/abstract.tex
docs(paper): initialize paper in LaTeX, prepared to refactor it

%! Abstract
Increasing competition for water is challenging management institutions of large river basins around the world.
Institutions that successfully support sustainable water resource use are structurally well-aligned with water provisioning and social-ecological demands.
However, what constitutes a well-aligned institution in this context is poorly understood.
We analyzed institutional shifts in water resource allocation, exploiting two quasi-natural experiments of the Yellow River Basin, China.
Using a synthetic control identification strategy, we analyzed an institution that was intended to prevent water overuse but instead resulted in a social-ecological structural mismatch, leading to a 164\% increase beyond the expected total water use.
We applied a novel economic model that suggested that this “sprint effect” (i.e., rapid competing in resource use) and the resulting ecological crisis were driven by incentive distortions in water allocation bargaining, which in turn, led to each province trying to pre-emptively increase their water quotas for long-term gain.
Our analysis highlights the need to carefully evaluate institutional fit in the management of water in large river basins, particularly to avoid the possibility of incentive distortion.

### 2022-03-10 docs/papers/elements/info.tex
docs(paper): initialize paper in LaTeX, prepared to refactor it

--- 2022-03-04 docs/papers/tex/main.tex
@@
-%% Template for a preprint Letter or Article for submission
-%% to the journal Nature.
-%% Written by Peter Czoschke, 26 February 2004
-%%
-\documentclass{article}
-\usepackage{hyperref}
-\usepackage{graphicx}
-\usepackage{setspace}
-\usepackage[a4paper, total={7in, 10in}]{geometry}
+%! Author = songshgeo
+%! Date = 2022/3/10
 
-\setstretch{1.523}
-
-\newtheorem{ass}{Assumption}
-\newtheorem{case}{Case}
-%% make sure you have the nature.cls and naturemag.bst files where
-%% LaTeX can find them
-
-\bibliographystyle{naturemag}
-
-%\usepackage{biblatex}
-%% make sure you have the nature.cls and naturemag.bst files where
-%% LaTeX can find them
-
-\title{Importance of social-ecological fit for water management in large river basins: An analysis of institutional shifts in the Yellow River Basin}
-
-%% Notice placement of commas and superscripts and use of &
-%% in the author list
-
-\author{Shuang Song$^{1,2}$, Huiyu Wen$^3$, *Shuai Wang$^{1,2}$, Graeme S. Cumming$^{4}$ \& Bojie Fu$^{1, 2}$}
-
-\begin{document}
-
-\maketitle
-\input{../../drafts/authors.md}
-
-\begin{abstract}
-    \input{../../drafts/abstract.md}
-\end{abstract}
-
-% Then the body of the main text appears after the intro paragraph.
-% Figure environments can be left in place in the document.
-% \verb|\includegraphics| commands are ignored since Nature wants
-% the figures sent as separate files and the captions are
-% automatically moved to the end of the document (they are printed
-% out with the \verb|\end{document}| command. However, tables must
-% be manually moved to the end of the document, after the addendum.
-% 表需要手动移到文末
-% water use; water management; social-ecological system; common pool resources; institutional analysis; collaborative governance
-
-\section{Introduction}
-Emerging competition for water is an urgent problem in water governance, with widespread water scarcity and overuse resulting in huge impacts on economies, societies, and ecosystems \cite{gleickPeakwaterlimits2010,dolanEvaluatingeconomicimpact2021,siwiCompetitionWaterGetting,ziolkowskaCompetitionWaterResources2016,distefanoArewedeep2017}.
-Water is the key exclusive and competitive resource that couples socioeconomic and ecological systems (known as common-pool resources, CPRs) \cite{wutichWaterScarcitySustainability2009,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017,castilla-rhoGroundwaterCommonPool2020}.
-Conflicts of interest often occur in allocation and competitions of water resources, with water governance policies often leading to long-term changes in human–water relationships and the redistribution of benefits \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013,chingManagingsocioecologyvery2015}.
-Although governments in many of the world’s large river basins have tried to resolve competition for water through the deliberate design of new institutions, general principles underlying the successes and failures of these initiatives are poorly documented and understood.
-
-Institutions (such as policies, laws, and norms) can influence regional sustainability by changing social-ecological system (SES) structure and dynamics \cite{youngInstitutionsenvironmentalchange2008,cummingAdvancingunderstandingnatural2020,lieninstitutionalgrammartool2020}.
-These include inter-relationships and interactions between social actors, between ecological units, or between social and ecological system elements \cite{bodinCollaborativeenvironmentalgovernance2017,barnesSocialecologicalalignmentecological2019}.
-Effective (“matched”) institutions operate at appropriate spatial, temporal, and functional scales to manage and balance these different relationships and interactions \cite{heWateringEnvironmentalRegulation2020,kellenbergempiricalinvestigationpollution2009}.
-From the perspective of SES outcomes, matched institutions support (but do not guarantee) sustainability \cite{epsteinInstitutionalfitsustainability2015,wangAlignmentsocialecological2019}.
-
-Some kinds of institutions have been shown to support desirable outcomes in water-centered SESs (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wangAlignmentsocialecological2019} and in collaborative water governance systems in Europe \cite{greenEUWaterGovernance2013}).
-At the same time, undesired and unsustainable outcomes (e.g., failures in environmental regulation of highly polluting industries or the development of “tragedy of the commons” situations when pursuing more water resources), with considerable ecological degradation, have attracted much attention \cite{saylesSocialecologicalnetworkanalysis2019,caiPollutingthyneighbor2016,castilla-rhoSocialtippingpoints2017}.
-Despite widespread recognition of the rising importance of integrated water resource management in solving water competition in the world’s large river basins, relatively few studies have explored the mechanisms by which SESs respond to new institutions \cite{agrawalSustainableGovernanceCommonPool2003,pershaSocialEcologicalSynergy2011,agrawalCommonPropertyInstitutions2001}.
-Two particular weaknesses in existing knowledge include understanding (1) the causal links between SES structures and outcomes; and (2) details of the underlying processes, especially the coordination of the incentives of different participants, that result from an institutional lack of fit.
-These weaknesses limit our understanding of institutional design, and they may reduce the speed and transfer of new knowledge and experience related to improving the sustainability of comprehensive water resources management.
-
-In order to disentangle the relationship between SES structure and outcomes, we analyzed a case study to show how an institutional shift led to a structural mismatch that triggered unsustainable water use and unintended ecological deterioration.
-Two rapid shifts in institutional structure that occurred in 1987 and 1998 (see Supplementary Material S1) provide unique settings to exploit quasi-natural experiments of a large river basin, the Yellow River Basin (YRB) in China \cite{xiaDevelopmentWaterAllocation2012}.
-After a period of severe drying up, an institutional shift implemented in 1987 represented the beginning of attempts to control water use in the YRB through the use of quotas, with the goals of alleviating conflicts between supply and demand and achieving sustainable development.
-
-Our results show that this initiative actually accelerated water withdrawals, resulting in an unintended “sprint effect”, where institutional mismatches created an even stronger incentive for each resource user to withdraw resources until the next major institutional shift in 1998.
-Our analysis contributes to a deeper understanding of the mechanisms underlying the relationships among institutions, SES structures, and outcomes.
-By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings are consistent with the urgent calls for a more dynamic design for water use allocation to achieve sustainability.
-
-\section{Institutions and SES structures}
-% 机构可以塑造社会经济体系的结构，对其进行抽象是机械地理解结构和结果之间联系的第一步。
-Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{fig:framework}A).
-% 例如，机构可以创建一种被确定为与良好的社会经济效益相关联的水平匹配结构，如果它鼓励管理相连生态成分的不同行动者之间的协作(图1B)。
-For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{fig:framework}B), leading to sustainable outcomes.
-% 例如，机构可以创建一个结构，鼓励不同行为者之间的合作，管理相连的生态成分
-Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{fig:framework}C and D).
-% 在实践中，一个大型、复杂的河流流域的制度变化将创造或摧毁数百种不同的联系。这些局部变化的更广泛影响可以从系统的整体行为中看到。
-In practice, institutional changes in a large, complex river basin will create or destroy hundreds of different connections.
-The broader impacts of these local changes can be seen in the overall behavior of the system.
-% 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
-We thus explored the causal linkages between the SES structures and sustainability (outcomes) in quasi-natural experiments of the YRB, which provides an informative case study for two main reasons.
-% 首先，长江流域管理的急剧结构变化使我们能够定量估计高层制度设计变化对用水的净影响。决定水分配的制度包括自下而上的协议或社会规范，以及自上而下的配额或法规，它们对社会经济结构有不同的影响;自上而下的监管可能会立即引发制度转变和SES的剧烈结构性变化。通过与由自下而上的制度转变引起的更渐进的变化相比，探索自上而下变化的影响，在对社会经济地位的定量分析中，极大地减少了来自不可观测因素的潜在干扰，提高了社会经济地位结构和结果之间因果关系的清晰度。
-First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use.
-Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013}; top-down regulations can trigger immediate institutional shifts and sharp SES structural changes \cite{speedBasinwaterallocation2013,rolandUnderstandinginstitutionalchange2004}.
-In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and improves the clarity of the causal link between SES structure and outcome.
-% 其次，通过比较长江流域两次制度变迁所分裂的三种不同制度结构的净效应，我们也可以更深入地理解“盆地固定效应”下结构格局的影响。尽管流域内的社会经济单位从世界各地的大型河流流域和许多地区的水资源中受益，但很少有流域多次经历过如此激进的社会经济结构变化。
-Second, by comparing the net effects of three different institutional structures split by two institutional shifts in the YRB, we can also reach a stronger understanding of the influence of structural alignments under a fixed basin.
-Although socioeconomic units within a basin benefit from water resources in large river basins all over the world and many locations have shown increased levels of regulation, few basins have experienced such radical SES structural changes several times (see \textit{Supplementary Material} S1).
-Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in SES institutional structure.
-% 因此，黄河流域的“流域固定效应”为SES结构的自我比较提供了宝贵的机会。
-% Thus, the YRB provides valuable settings for understanding the direct impacts of changes in SES institutional structure.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=8.3cm]{../../../figs/diagrams/framework.jpg}
-	\caption{
-		Framework for understanding linkages between SES structures and outcomes.
-		\textbf{a.} The general framework for analyzing social-ecological systems (SESs) (adapted from Ostrom \cite{ostromGeneralFrameworkAnalyzing2009}).
-Institutions embedded in SESs may reshape structures by changing the interactions between core subsystems, resulting in different outcomes.
-        Three typical types of abstracted SES structures are shown as \textbf{b.}, \textbf{c.} and \textbf{d.} (adapted from Bodin, 2017)\cite{bodinCollaborativeenvironmentalgovernance2017}.
-Red circles indicate social actors, and green ones indicate ecological components.
-Connection (ties between two ecological components), collaboration (ties between two social actors), or management (ties between a social actor and an ecological component) exist when two units are linked by gray lines.
-The gray dashed lines show aligned SES structures that are more likely to result in a desirable outcome according to empirical evidence.
-	}
-    \label{fig:framework}
-\end{figure}
-
-\section{Context of institutional shifts}
-% 黄河是世界第五长河，它的流域也是中国文明的摇篮。
-The Yellow River, whose basin is the cradle of Chinese civilization, is the fifth-longest river in the world.
-It supports $9.7\%$ of China’s irrigation, with only $2.6\%$ of its total water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021).
-% 然而，经过沿江各省多年的免费取水(图~\ref{fig:structure} A和B)，到20世纪80年代，黄河地表水耗水量接近径流量的10倍，并不断上升
-However, after years of free access to water by provinces along the river (Figure~\ref{fig:structure} A and B), surface water consumption of the Yellow River was close to $80\%$ of its runoff by the 1980s and rising
-\cite{wangYellowRiverwater2019,songSedimenttransportincreasing2020}.
-% 自1972年以来，黄河径流量的减少破坏了黄河的生态，制约了黄河的经济发展
-Reductions in runoff after 1972 damaged the ecology of the YRB and restricted its economic development \cite{wangYellowRiverwater2019}.
-% 因此，在中国典型的自上而下的制度结构下(附录图S1-B)，黄河流域不同层次提出了相对完整的水资源分配规定(图1a)。
-Therefore, through typical top-down institutional structures in China (see \textit{Supplementary Material S1}), relatively integrated water allocation regulations were successively proposed across different levels in the YRB.
-% 这些机构包括国家政府、流域管理机构、省、市，甚至地区(见图1 B-D)。
-These include the national government, the basin management agency, provinces, cities, and even districts.
-% 这些在不同制度发展阶段相继出台的政策，引发了长江经济带经济发展结构的突变，并产生了不同的结果(见附录A和图S1-C)。
-These policies at different stages of institutional development triggered abrupt changes in the SES structure of the YRB with different outcomes.
-
-% 0世纪70年代以来，中国政府向黄河水利委员会下达指令，要求黄河水利委员会设计配水方案，同时要求黄河沿岸各省进行水资源规划
-In 1982, the Chinese government issued instructions to the Yellow River Water Conservancy Commission (YRCC), the basin agency of the YRB, requiring it to design a water allocation scheme and at the same time requiring the provinces along the Yellow River to carry out water resources planning (see \textit{Supplementary Material S1})
-\cite{wangReviewImplementationYellow2019}.
-% 经过多方讨论与权衡，中国政府于1987年为相关省份分配了水资源配额，要求沿黄各省(区)贯彻执行
-The Chinese government started to assign water quotas to the relevant provinces in 1987, but did not create a unit to coordinate water division between them (Figure~\ref{fig:structure} \textbf{A} and \textbf{C}).
-% 这一时期长江水利枢纽的监督任务是编制长江水利枢纽用水量统计公报，并与定额进行对比分析。
-The mandate of the YRCC during this period was only to report on and analyze water consumption in the YRB
-\cite{wangReviewImplementationYellow2019}.
-% 随着断流的进一步恶化，1998年中国政府推进了相关政策的改革，要求所有省份在取用水资源时必须向黄委会申请许可，黄委会得以直接对各省的用水实施监管。
-However, since reductions in river flow indicated an unintended SES outcome (Figure~\ref{fig:structure} E), the Chinese government pushed for a policy reform in 1998 that required all provinces to apply for licenses to use water from the YRCC, allowing the council to directly regulate their water use (see \textit{Supplementary Material S1} and Figure~\ref{fig:structure} A and D).
-% 由于革新后的政策成功遏制了断流，2008年该分配政策被进一步细化，相关各省都进一步设置了更细致的分配方案，并最终形成了黄河流域如今的水资源分配格局。
-The 1998 policy succeeded in curbing water extraction (Figure~\ref{fig:structure} E), and it was further refined in 2008.
-The relevant provinces created a more detailed allocation plan and finally formed the present water allocation institutions of the YRB (see \textit{Supplementary Material S1}).
-% 因此，在1975-2008长达33年的时间里，从没有分水政策到以两种不同模式监管下的分水政策，黄河流域实际上先后存在着三种不同的社会-生态结构（Fig 1）。
-Therefore, in our study period (from 1975 to 2008), the system shifted between three different SES structures (Figure~\ref{fig:structure} \textbf{B} to \textbf{D}).
-% 在它们之中，与预期相反地，1987年至1998年的流域SES结构下黄河的生态急剧恶化，表明了制度的失配。
-The sharp and unintended decline in the ecological condition of the Yellow River from 1987 to 1998 indicates an institutional mismatch during this period (Figure~\ref{fig:structure} the shadowed time periods).
-
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=12cm]{../../../figs/diagrams/structure.jpg}
-	\caption{
-		% 黄河流域的制度变迁与经济社会结构差异。
-		Institutional shifts and related SES structures in the Yellow River Basin (YRB). See \textit{Supplementary Material S1} for detailed introduction for the institutions.
-		% 国家政府在1987年和1998年先后两次出台了改变流域制度的政策，而黄河水利委员会、利益攸关的各省在不同制度时期具备的功能是不同的。
-		\textbf{A.} The national government changed YRB management policies and institutions in 1987 and 1998.
-As a result, the Yellow River Conservancy Commission (YRCC) and the provinces acted differently in different periods.
-Three different SES structures existed successively in the YRB.
-		% 没有任何政策限制，各利益相关者此时期可以从单向但联通的河流生态单元内自由取水
-		\textbf{B.} 1975–1987: Without any constraints, water resources were freely accessible to each stakeholder (the provinces in this case, denoted by red circles) from a one-way but connected ecological unit (the Yellow River, denoted by the blue rectangle).
-		% 在政策1之后，每个使用者都被分配了能够开采河流地表水资源的配额，而黄委会的工作是对配额的使用进行统计与汇报。
-		\textbf{C.} 1987–1998: After the implementation of policy 1 in 1987, each user was assigned a quota to withdraw surface water resources, and the YRCC (yellow triangle) was tasked with reporting on water quota use.
-		% 第二个政策之后，利益相关者取水需要向黄委会申请，黄委会则根据用水配额来批发许可。因此此时黄委会与利益相关者之间产生了直接的双向联系，监督他们对资源配额的取用。
-		\textbf{D.} 1998–2008: After the implementation of policy 2, stakeholders had to apply for water resources from the YRCC, which then licensed water use according to the quota.
-Under this institution, the YRCC had direct two-way connections between provinces and ecological components.
-		% 由于政策1与政策2都是为了解决黄河断流的生态问题而提出的，因此在结果与政策预期严重相反的第二时期（灰色阴影时段），是制度导致了错配的社会-生态系统结构。
-		\textbf{E.} A timeline of the Yellow River and drying conditions.
-The size of the circles indicates the length of section that dried up (km), and the y-axis indicates the length of the drying period.
-Both policy 1 and policy 2 were put forward to solve this ecological crisis.
-The mismatch created by policy 1 is clearly correlated with the unintended outcomes shown in the second (gray-shaded) period.
-	}
-	\label{fig:structure}
-\end{figure}
-
-\section{Sprint effect induced by an institutional mismatch}
-% % 这里，我们使用合成控制模型创建了假设不存在政策变化的虚拟对照组（see \textit{Methods}-1），同时用K-近临算法找到经济状况与黄河流域各省“类似”的安慰剂对照（see \textit{Methods}-2），反复对比表明两次社会-生态系统结构变迁对流域的水资源利用及分配产生了明显不同的影响。
-% Here, we use synthetic control method to create a control group assuming that there is no water use constraints (\textbf{methods}), at the same time with K-nearest algorithm to match an economic state and the YRB provinces ``similar'' placebo-controlled (\textbf{methods}).
-% % 然后，我们反复比较了两个SES结构(分别自1987年和1998年)，以量化是否有显著不同的影响，YRB用水或分配。
-% Then we repeatedly compared between two SES structures (since 1987 and 1998, respectively) to quantify if there were significantly different impacts on water uses or allocation (\textbf{methods}).
-% % 我们的结果表明，1987年的结构变化刺激各省使用了远超模型预测的没有政策影响下的用水量，其增量超出安慰剂对照组xx\%，但对水资源的分配的均匀程度没有改变（see fig）。
-Our results suggest that the institutional shift in 1987 stimulated the provinces to use far more water than would have been used without policy effects (Figure~\ref{fig:main_results}A), with an observed increase of $164\%$ over the expectation(Figure~\ref{fig:main_results}B).
-% 然而，水资源分配的均匀性并没有改变，区域间的用水量在相同规模下增加(图~\ref{fig:main_results}C)。
-However, the relative share of water use was not changed, denoting proportionally similar water use increases among the different regions (Figure~\ref{fig:main_results}C).
-% 在1998年出台的政策再次改变社会-生态结构之后，用水量显著下降，总量仅为安慰剂对照组的xx%。
-After the SES structure changed again in 1998, the trend of increasing water use appeared to be effectively suppressed (Figure~\ref{fig:main_results} D), with total observed water consumption decreasing by $260\%$ relative to expectations(Figure~\ref{fig:main_results} E).
-% 但此阶段主要是xx，xx，xx等黄河流域的用水大省受到了遏制，因此水资源在各个省之间的比例分配变得更均匀了。
-At this stage, however, the reduction in water use came mainly from the provinces with large water consumption, such as Henan and Shandong (Figure~\ref{fig:main_results} E),  so the proportion of water used by regions became more similar (Figure~\ref{fig:main_results} F).
-% 上述结果表明，1998年各省之间由黄委会统一监管后分水政策才真正达到了其遏制用水、解决断流的预期。
-In conclusion, the water allocation policy curbed water use in 1998, whereas the 1987–1998 institutional mismatch stimulated a notable increase in total water use in all related provinces.
-% 在过去的十年里，对制度变革的“冲刺”反应似乎创造了一场竞赛，每个省份都开始使用超过他们需要的水。
-Over this decade, “sprint” responses (i.e., rapid increases in resource use \cite{lueckPreemptiveHabitatDestruction2003}) to institutional change appear to have created a race in which each province began to use more water than they needed.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=12cm]{../../../figs/outputs/main_results.jpg}
-    \caption{
-        Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
-(\textbf{A} to \textbf{C}: Entering the mismatched SES structure in 1987; \textbf{D} to \textbf{E}: exiting the mismatch in 1998.
-\textbf{A} and \textbf{D}: Impact of the first institutional shift on water use trends in the YRB.
-Blue points are actual water use, and gray points are predicted use under a scenario without any institutional shift (see \textit{Methods}).
-\textbf{B} and \textbf{E}: Impact of the institutional shift on total water use.
-Dark bars indicate the difference between the actual and predicted water use in specific study periods.
-Gray bars are the expected water use, simulated by setting up placebo experiments (null models, see \textit{Methods}).
-\textbf{C} and \textbf{F}: Impact of institutional shift on water allocation equity (see \textit{Methods}).
-Red lines indicate the index calculated from actual water use data; gray lines indicate predicted water use under a scenario with unconstrained water use.
-    }
-    \label{fig:main_results}
-\end{figure}
-
-\section{Incentive distortion causes the sprint effect}
-Theoretically, our economic model suggests that different kinds of institutional shifts should lead to different optimal water uses (Figure~\ref{fig:economic_model}).
-Furthermore, our analysis indicated that the cause of the sprint effect in this case was incentive distortion.
-Compared with the decentralized water allocation institution in place before 1987, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs (see Table~\ref{tab:cases} the \textbf{methods} for a detailed mathematical formula).
-% 在不匹配条件下，边际成本减去边际收益增加，导致用水量增加，xx的差异反映了水配额模拟的非预期冲刺效应。
-The unintended sprint effect (from 1987 to 1998) was caused by both declining marginal costs (a shift from a fixed unit cost to an irrelevant cost) and increasing marginal returns due to future water use benefits (see Table~\ref{tab:cases} the \textbf{methods} for a detailed mathematical formula).
-% 因此，这种制度引发了一种与可持续用水意图背道而驰的激励扭曲。
-The institution thus triggered an incentive distortion that ran counter to the intention of sustainable water use.
-Further, the strength of the sprint effect was positively correlated with the size and time horizon of the water use quota (Figure~\ref{fig:economic_model} \textbf{Panel B}).
-% 这些理论上的预测正如我们在黄河流域所观察到的一样，不匹配的配额制度导致了短跑效应的出现，而中心化的制度结构结束了这一非预期的现象。
-% These theoretical predictions, in line with phenomenon observed in the YRB, indicating the mismatched institution leads to incentive distortion of provinces for pre-empting resources by `sprinting', according to their expectations for the future.
-% 这些理论预测进一步从YRB观察到的现象出发，表明不匹配的配额制度通过提高边际效益来刺激用水量，而边际效益与放宽限制带来的未来潜在用水量的影子值有关。
-% These theoretical predictions, further from the phenomenon observed in the YRB, indicating the mismatched institution with quota stimulates water use by raising marginal benefits, which is related to the shadow value of potential future water use from relaxing the constraints.
-% 温博推荐的版本：
-% These theoretical predictions, further from the phenomenon observed in the YRB, attributing ``sprint effect'' into raising marginal benefits -by pursuing indirectly generating shadow value of water use while converting fixed marginal costs to irrelevant cost for each individual province.
-
-\begin{table}[!ht]
-	\centering
-	\caption{Summary of marginal returns and marginal costs for each case }
-	%\footnotesize
-    \setlength{\tabcolsep}{1mm}{
-       \begin{tabular}{lccc}
-		\hline
-		& Case 1: Decentralized Ins. & Case 2: Mismatched Ins. & Case 3: Matched Ins. \\ \hline
-		Marginal return & $P*F'(X)$                & $P*F'(X)+V(X)^*$            & $P*F'(X)$              \\
-		Marginal cost   & $C/N$                    & $Irrelevant$              & $C$                   \\ \hline
-	\end{tabular}
-    }
-	\centering
-	\footnotesize{\leftline{$^*$Note: $V(X)$ denotes a shadow value.}}
-	\label{tab:cases}
-\end{table}
-
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=12cm]{../../../figs/outputs/economic_model.jpg}
-	\caption{
-		% \textbf{Assumption 1:} \textit{(Production)} Assuming that water is the only input of the homogenous production function F(x) of each province.
-Under diminishing marginal returns assumption, and $F(x)$ is continuous, $F'(0)=\infty$, $ F'(\infty)=0$.
-The production output is under perfect competition, with constant unit price of P.
-		% \textbf{Assumption 2:} \textit{(Cost function)} Assuming that the ecology is a unity for the whole basin, the cost of water use is equally assigned to each province under any water use.
-The unit cost of water is a constant C.
-		% \textbf{Assumption 3:} \textit{(Multi-period setting)} There are infinite periods with constant discount factor $\beta$ lying in (0,1) with no cross-period smoothing in water uses.
-		\textbf{A.} The relationship of marginal benefits and water use of province i at t = 0 for three different cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}, assuming $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, and $\beta=0.4$ as an example  (see \textit{Methods}In Case 3, water use by others is taken as a given, equal to the optimal water use for Case 2.
-The horizontal coordinate of each intersection of marginal benefits and the break-even line represents the optimal water use under each case.
-		\textbf{Panel B.} The relation between optimal water use of province i and total quota for Case 3, under time horizon of $T=5$, $T=10$, and an infinite $T$, respectively.
-The settings are the same as in \textbf{A}.
-	}
-	\label{fig:economic_model}
-\end{figure}
-
-\section{Discussion}
-% 我们展示了不匹配的分配制度是如何导致激励失真导致水资源加速耗竭的(即“冲刺效应”)。“冲刺效应”是CPR系统面临的一种特殊情况，在这种情况下，制度的不匹配为每个资源使用者创造了更强的动机(扭曲)，促使他们收回资源
-We have shown how a mismatched allocation institution can lead to an accelerated depletion of water resources (i.e., the “sprint effect”) caused by incentive distortion.
-The sprint effect is a special case faced by CPR systems, where institutional mismatches create an even stronger incentive (with distortion) for each resource user to withdraw resources
-\cite{ostromRevisitingCommonsLocal1999,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017}.
-% 过往研究指出制度常常是避免公共池塘资源系统的崩溃的关键，但“短跑效应”的出现表明在自上而下进行制度设计所形成的错配SES结构中，制度也可以成为系统加速崩溃的触发者。
-Previous studies have suggested that institutions are often the key to avoid the collapse of a CPR system, but the emergence of a sprint effect shows that an institution with structural mismatches can also be the trigger that accelerates system collapse \cite{bodinConservationSuccessFunction2014,bodinCollaborativeenvironmentalgovernance2017,wangAlignmentsocialecological2019}.
-The initial formulation of the water quota in our case studies went through a stage of “bargaining” among stakeholders (from 1982 to 1987) \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}, where each province attempted to demonstrate its development potential related to water use.
-% 在高层决策者与低层利益相关者之间存在信息不对称的用水分配中，当前用水量越大的利益相关者议价能力越大。1987年以后，对各省来说，合乎逻辑的下一步是试图证明争取更大配额的合理性，而不是立即采取资源节约型改革。在实践中，尽管受影响的省份可能没有直接鼓励过度使用资源，但由于激励扭曲，他们有更大的动机对资源提取开绿灯。因此，在争夺潜在的水资源配额时，各省往往将生态成本隐藏在经济发展背后。
-In water use allocation with information asymmetry between upper-level decision-makers and lower-level stakeholders, those with more current water use might have greater bargaining power.
-After 1987, the logical next step for provinces was to attempt to justify bargaining for larger quotas rather than immediately adopt resource-conserving transformations.
-In practice, although the affected provinces may not have directly encouraged excessive resource use, they had a greater incentive to give the green light to resource withdrawals because of incentive distortions \cite{kriegerProgressGroundWater1955, ostromGoverningCommonsEvolution1990}.
-As a result, while competing for potential water quotas, the provinces tended to hide the ecological costs behind economic development.
-
-% 毫无疑问，随着资源竞争的日趋激烈，越来越多的SES正依赖着不同形式的制度进行资源分配（如自组织和政府干预），避免“短跑效应”的出现或将成为制度设计的关键。
-There is no doubt that with increasingly fierce competition for water, more and more SESs are developing new institutions for water allocation (whether through self-organization or government intervention) \cite{anderssonVoluntaryleadershipemergence2020, wutichWaterScarcitySustainability2009}.
-% 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
-Adoption of an overall quota plays an important role in preventing overuse of CPRs \cite{tilmanLocalizedprosocialpreferences2019}.
-However, the negative effects of incentive distortion imply a trade-off between long-term SES benefits and current stability, and the proportion of available resources allocated under quota schemes matters when institutions change \cite{ladeRegimeshiftssocialecological2013}.
-According to our analysis of plausible scenario assumptions based on our general economic model, the sprint effect will be reinforced when stakeholders anticipate that technological advances will amplify the benefits of water quotas in the future (see \textit{Supplementary Material S3}).
-% 然而，如果有水权转换机制允许利益相关者之间通过交易来弥补 shadow value，当前这种错乱的动机就不会那么强。
-However, if an institution allowed stakeholders to compensate for the shadow value (i.e., potential returns sacrificed due to water constraints and water scarcity) \cite{howarthAccountingvalueecosystem2002} of future water use, incentive distortion would be less devastating (e.g., through water rights transfer).
-Policymakers can also weaken the sprint effect by increasing the frequency of quota updates, supporting the idea that a more dynamic institution that responds to changing conditions (see \textit{Supplementary Material S3}) will adapt more effectively to its social-ecological context.
-
-% 近年来黄河流域面临的分水制度调整问题也说明了动态设置配额的重要性。
-Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of dynamic quota setting (see \textit{Supplementary Material S1}) \cite{yuAdaptabilityassessmentpromotion2019}.
-Following the institutional reforms of 1998, the Yellow River has not dried up since 1999.
-However, given recent changes in the YRB, its rigid resource allocation scheme can no longer meet the new demands of economic development \cite{wangThingsCurrentSignificance2019}.
-The Chinese government has embarked on an ambitious plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}).
-Other SESs around the world face similar problems in establishing successful resource allocation institutions \cite{cummingQuantifyingSocialEcologicalScale2020, muneepeerakulStrategicbehaviorsgovernance2017, cummingAdvancingunderstandingnatural2020, leslieOperationalizingsocialecologicalsystems2015}.
-These initiatives can benefit from our analysis by actively considering and incorporating social-ecological complexity and incentive structures when developing new approaches that avoid unsustainable outcomes.
-Our research provides a cautionary tale of how institutions can act as a double-edged sword when trying to attain sustainability.
-
-\section{Methods}
-% 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程
-We estimated and analyzed the net effects of two SES structural changes of water use.
-The actual water use of the Yellow River Basin was peroxided by the sum of the water use of the target group provinces.
-To quantify water use, we used synthetic control methods to estimate possible trends of water use in the absence of institutional shifts.
-In addition, as a robustness test, we conducted a matched placebo test (creating a “null model”) to exclude the effects of other factors that were contemporaneous with the institutional shifts.
-Finally, we created an economic model based on marginal revenue to provide a theoretical explanation for the observed “sprint effect” phenomenon.
-A brief technical overview is given in \textit{Supplementary Material S2}.
-
-\subsection{Dataset and variables}
-% 我们使用中国1978年至2012年各省的年度用水量数据集，这个公开的数据集由全国水资源利用调查得到，详细可查看。
-We used China’s provincial annual water consumption dataset from 1978 to 2012.
-This publicly available dataset was obtained from the National Water Resources Utilization Survey; details are accessible from Zhou (2020)
-\cite{zhouDecelerationChinahuman2020}.
-A total of 10 provinces or regions have been directly affected by the water allocation institutional shifts in the YRB, accounting for $8.6\%$ of the total population of China (in 1990).
-Eight provinces have been particularly affected because of their greater dependence on the water resources from the Yellow River (see \textit{Supplementary Material S2}).
-Therefore, we divided the dataset into a “target group” and a “control group”, treating provinces that were greatly affected as the target group $(n=8)$ and provinces that were not affected by the institutional shifts as the potential control group $(n=20)$.
-
-We focused on two features of water use in the YRB: total water use and diversification of water allocation.
-The actual water uses are given by the dataset, but when the synthetic control method is used to predict the water use of the control group, other independent influences need to be considered.
-Thus, we used economic features that are highly related to water use to extrapolate demand (e.g., agriculture, industry, service industry, and domestics, see \textit{Supplementary Material S2, Table 1} To measure resource allocation diversification between the upper, middle, and lower reaches, we used “entropy” as a simple index,
-
-$$ Index_{entropy} = \sum_i{p_i *log(p_i)} $$
-
-% 式子中的p是每个使用的水占流域总用水的比例
-Where $p_i$ is the proportion of water uses for region $i$ to the total water uses in the basin.
-A larger index value indicates the proportion of water resources actually used is closer to the average among the upper, middle, and lower reaches.
-
-\subsection{Synthetic Control}
-Synthetic control is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadieSyntheticControlMethods2010}.
-In this study, we used a comparative event approach and compared actual post-institutional shift induced water use changes with an appropriate counterfactual of what the water use change would have been.
-The counterfactual was built as the optimally weighted average of provinces not exposed to the institutional shifts.
-The synthetic control method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity \cite{billmeierAssessingEconomicLiberalization2013, smithresourcecurseexorcised2015}.
-In practice, each of the units (i.e., provinces) in the treated group were affected by institutional shifts in 1987 and 1998, each of which was taken as the “shifted” point $t_0$ and the two steady institutions as $t$ for analyzing in each shift.
-The synthetic control method generates the control unit by assigning a weight matrix $W$ to units of the potential control group, so that the treated unit and its control unit are similar in each variable before $t_0$, i.e.,
-
-$$\min(V_{i}^{t<t_0} - W_i * F_{control}^{t<t_0})$$
-
-where $V_i$ is a vector that indicates all features of a unit $i$ of the treated group, and $F_{control}$ is a matrix that consists of all features and units of the potential control group.
-$W_i$ is the weight matrix for target unit $i$.
-We minimized the root mean square error (RMSE) by using the Synth package in R \cite{abadieSynthPackageSynthetic2011, abadieComparativePoliticsSynthetic2015}.
-All codes are accessible in the repository.
-
-% 这样一来，基于降维的思想，我们构建出了一系列特征上与实验组最为接近的可比对照。
-In accordance with the idea of dimensionality reduction, we constructed a series of comparable control units that were most similar in characteristics to the treated units.
-Because the units of the control group were not affected by the institutional shifts, after giving the same weight to the total water use of the control group $M_i * WU_{control}$, the result $W_i*WU_{control}$ could be considered a reasonable estimation of the untreated situation.
-The net effect of the water allocation institutional shift was then estimated by calculating the difference of water uses after the institutional shift between the treated group and the control group, compared with the water use difference before the shift.
-
-\subsection{Placebo Test}
-% 作为一种稳健性检验，安慰剂测试的必要性体现在两个原因上。
-For robustness, we conducted a placebo test because the synthetic control method neglects the influences of overall changes in factors in the same year by simply dividing time periods according to institutional shifts.
-Three steps were required to apply the placebo test:
-% (1) 对目标组中的每个省份$i$，计算所有潜在控制组与它之间特征向量的欧氏距离
-(1) For each province in the target group, we calculated the Euclidean distance of vectors between all provinces in the potential control group.
-% (2) 将距离由小到大排序后，选取特征向量最相似的三个省份，所有特征的均值作为 $i$ 的替代
-(2) After ranking the distances, the three provinces with the most similar economic context were used to generate an average paired treatment target unit.
-% (3) 对这个配对目标同样实施控制合成法（潜在控制组排除构成它的三个省）
-(3) We performed the same synthetic control analysis for this paired target (i.e., the potential control group excluding the three provinces in step 2).
-% 经过上述步骤，我们在理论上构建了一个相似的“区域”并实施了同样的控制合成实验。
-In this way, we theoretically constructed a pseudo-treated unit and performed the same synthetic control treatments.
-Because these placebo tests were directed at units unaffected by the institutional shifts, the results can be regarded as a reasonable baseline expectation or null model from which to assess the changes caused by other factors.
-
-\subsection{Economic model}
-In order to understand the mechanisms underlying the empirical results, we developed a dynamic economic model to analyze how institutional change could have led to the sprint effect in water use.
-Specifically, we modeled individual provincial decision-making in water resources before quota execution.
-The analysis result implied that the underlying driver of CPR overuse was incentive distortion.
-
-In developing the model, we highlighted the main features of the YRB, as well as the water use institutions of 1987 and 1998. We proposed three intuitive and general assumptions.
-
-\begin{ass}
-    % (生产)为了简化，由于不可替代性，水是每个省的同质生产函数10的唯一投入。$F(x)$是连续的，满足Inada条件，即$F'(x)>0, F''(x)<0$(边际收益递减假设)，$F'(0)=\infty$,$ F'(\infty)=0$。产品产量处于完全竞争状态，单位价格为15。
-    (Water-dependent production) For simplicity, water is assumed to be the only input of the homogenous production function $F(x)$ of each province because of its irreplaceability.
-$F(x)$ is continuous and satisfies the Inada Conditions, i.e., $F'(x)>0, F''(x)<0$ (the diminishing marginal returns assumption), $F'(0)=\infty$,$ F'(\infty)=0$.
-The production output is under perfect competition, with a constant unit price of $P$.
-\end{ass}
-\begin{ass}
-    (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in N provinces, the cost of water use is equally assigned to each province under any water use.
-The unit cost of water is a constant $C$.
-\end{ass}
-\begin{ass}
-    (Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water uses.
-\end{ass}
-
-Under the above assumptions, we can demonstrate three cases consisting of local governments in YRB to simulate their water use decision-making and water use patterns.
-
-\begin{case} Decentralized institution:
-    This case corresponds to a situation without any high-level water allocation institution (i.e., before 1987, see Figure~\ref{fig:structure} B).
-
-    When each province independently decides on its water use, the optimal water use $\hat x_i^*$ in province $i$ satisfies:
-    $$F'(x)=\frac{C}{P \cdot N}$$
-
-    When the decisions in different periods are independent, for $t=0,1,2 \ldots$, then:
-    $$\hat x_{it}^*=\hat x_i^*$$
-
-\end{case}
-
-\begin{case} Mismatched institution
-    This case corresponds to a mismatched institution (i.e., $1987\sim1998$, see Figure~\ref{fig:structure} C).
-
-    The water quota is determined at $t=0$ and imposed in $t=1,2,\ldots$ The total quota is a constant denoted as $Q$, and the quota for province $i$ is determined in a proportional form:
-    $$Q_i=Q \cdot \frac{x_i}{x_i + \begin{matrix} \sum x_{-i} \end{matrix}}$$
-
-    Under a scenario with decentralized decision-making with a water quota institution, given other provinces’ water use decisions remain unchanged, the optimal water use $\widetilde x_{i0}^*$ of province $i$ at $t=0$ satisfies:
-
-    $F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot f(Q \cdot \frac{x_{i,0}}{\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix})^2}$.
-
-    When future water use is constrained by a water quota, the dynamic optimization problem of province $i$ is shown as follows:
-
-    $max  \quad P \cdot F(x_{i,0})-\frac{C \cdot \begin{matrix} \sum x_{i,0} + x_{-i,0} \end{matrix}}{N}+\beta P \cdot F(x_{i,1})+\beta^2 P \cdot F(x_{i,2})+...$
-
-    $=P \cdot F(x_{i,0})-C \cdot \frac{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}{N}+\frac{\beta}{1-\beta} P \cdot F(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}})$
-
-    First-order condition: $P \cdot F'(x_{i,0})-\frac{C}{N}+\frac{\beta}{1-\beta}[P \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0}+\begin{matrix} \sum  x_{-i,0} \end{matrix})^2}]=0$
-
-    where $f(\cdot)$ is the differential function of $F(\cdot)$.
-
-    The optimal water use in province i at t=0 $\widetilde x_{i,0}^*$ satisfies $P \cdot F'(x_{i,0})=\frac{C}{N}-\frac{\beta}{1-\beta} \cdot P \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$, i.e., $F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$.
-
-\end{case}
-
-\begin{case} Matched institution
-
-    This case corresponds to the institution under which the YRCC centrally managed water allocation between provinces (i.e., $1998\sim2008$, see Figure~\ref{fig:structure} D).
-
-    When the $N$ provinces decide on water uses as unified whole (e.g., the central government completely decides and controls on the water use in each province), the optimal water use $x_i^*$ of province $i$ satisfies:
-
-    $$F'(x)=\frac{C}{P}$$
-
-\end{case}
-
-We propose Proposition 1 and Proposition 2:
-
-\textbf{Proposition 1}: Compared with the decentralized institution, a matched institution with unified management decreases total water use.
-
-Because $F’$ is monotonically decreasing, based on a comparison of costs and benefits for stakeholders (provinces) in the three cases,
-
-$$\widetilde x_i^*>\hat x_i^*>x_i^*$$
-
-The result of $\hat x_i^*>x_i^*$ indicates that individual rationality would deviate from collective rationality when property rights are unclear \cite{hardinTragedyCommons2009}, because of the common-pool characteristics of water
-\cite{castilla-rhoGroundwaterCommonPool2020,ostromGeneralFrameworkAnalyzing2009}.
-
-The difference of $\widetilde x_i^*$ and $\hat x_i^*$ stems from two parts: the marginal returns effect and the marginal costs effect.
-First, the “shadow value” provides additional marginal returns of water use in $t=0$, wwhich increases the incentives of water overuse by encouraging bargaining for a larger quota.
-Second, the future cost of water use would be degraded from $\frac{P}{N}$ to an irrelevant cost.
-
-The optimal water use under the three cases implies that mismatched institutions cause incentive distortions and lead to resource overuse.
-
-\textbf{Proposition 2}: The quota determination of the mismatched institution increases the incentives of current water use.
-
-The intuition for this proposition is straight-forward in that all provinces would use up their allocated quota under a relatively small $Q$.
-As $Q$ increases, the quota would provide higher future benefits for a pre-emptive water use strategy.
-Since the provincial water use decisions are exactly symmetric, total water use would increase when each province has higher incentives for current water use.
-This situation corresponds to a “sprint” effect, where the total water use dramatically increases in the “sprint” period.
-
-Extensions of the model are shown in \textit{Supplementary Material S3}.
-
-\section{Info.}
 Funding was provided by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007).
@@
 They will be made open source after this project is completed.
-
-%% Put the bibliography here, most people will use BiBTeX in
-%% which case the environment below should be replaced with
-%% the \bibliography{} command.
-\bibliography{WAInstitution_YRB_2021}
-
-%% Here is the endmatter stuff: Supplementary Info, etc.
-%% Use \item's to separate, default label is "Acknowledgements"
-
-\end{document}

### 2022-03-10 docs/papers/elements/institution.tex
docs(paper): initialize paper in LaTeX, prepared to refactor it

--- 2022-03-04 docs/papers/tex/main.tex
@@
-%% Template for a preprint Letter or Article for submission
-%% to the journal Nature.
-%% Written by Peter Czoschke, 26 February 2004
-%%
-\documentclass{article}
-\usepackage{hyperref}
-\usepackage{graphicx}
-\usepackage{setspace}
-\usepackage[a4paper, total={7in, 10in}]{geometry}
-
-\setstretch{1.523}
-
-\newtheorem{ass}{Assumption}
-\newtheorem{case}{Case}
-%% make sure you have the nature.cls and naturemag.bst files where
-%% LaTeX can find them
-
-\bibliographystyle{naturemag}
-
-%\usepackage{biblatex}
-%% make sure you have the nature.cls and naturemag.bst files where
-%% LaTeX can find them
-
-\title{Importance of social-ecological fit for water management in large river basins: An analysis of institutional shifts in the Yellow River Basin}
-
-%% Notice placement of commas and superscripts and use of &
-%% in the author list
-
-\author{Shuang Song$^{1,2}$, Huiyu Wen$^3$, *Shuai Wang$^{1,2}$, Graeme S. Cumming$^{4}$ \& Bojie Fu$^{1, 2}$}
-
-\begin{document}
-
-\maketitle
-\input{../../drafts/authors.md}
-
-\begin{abstract}
-    \input{../../drafts/abstract.md}
-\end{abstract}
-
-% Then the body of the main text appears after the intro paragraph.
-% Figure environments can be left in place in the document.
-% \verb|\includegraphics| commands are ignored since Nature wants
-% the figures sent as separate files and the captions are
-% automatically moved to the end of the document (they are printed
-% out with the \verb|\end{document}| command. However, tables must
-% be manually moved to the end of the document, after the addendum.
-% 表需要手动移到文末
-% water use; water management; social-ecological system; common pool resources; institutional analysis; collaborative governance
-
-\section{Introduction}
-Emerging competition for water is an urgent problem in water governance, with widespread water scarcity and overuse resulting in huge impacts on economies, societies, and ecosystems \cite{gleickPeakwaterlimits2010,dolanEvaluatingeconomicimpact2021,siwiCompetitionWaterGetting,ziolkowskaCompetitionWaterResources2016,distefanoArewedeep2017}.
-Water is the key exclusive and competitive resource that couples socioeconomic and ecological systems (known as common-pool resources, CPRs) \cite{wutichWaterScarcitySustainability2009,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017,castilla-rhoGroundwaterCommonPool2020}.
-Conflicts of interest often occur in allocation and competitions of water resources, with water governance policies often leading to long-term changes in human–water relationships and the redistribution of benefits \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013,chingManagingsocioecologyvery2015}.
-Although governments in many of the world’s large river basins have tried to resolve competition for water through the deliberate design of new institutions, general principles underlying the successes and failures of these initiatives are poorly documented and understood.
-
-Institutions (such as policies, laws, and norms) can influence regional sustainability by changing social-ecological system (SES) structure and dynamics \cite{youngInstitutionsenvironmentalchange2008,cummingAdvancingunderstandingnatural2020,lieninstitutionalgrammartool2020}.
-These include inter-relationships and interactions between social actors, between ecological units, or between social and ecological system elements \cite{bodinCollaborativeenvironmentalgovernance2017,barnesSocialecologicalalignmentecological2019}.
-Effective (“matched”) institutions operate at appropriate spatial, temporal, and functional scales to manage and balance these different relationships and interactions \cite{heWateringEnvironmentalRegulation2020,kellenbergempiricalinvestigationpollution2009}.
-From the perspective of SES outcomes, matched institutions support (but do not guarantee) sustainability \cite{epsteinInstitutionalfitsustainability2015,wangAlignmentsocialecological2019}.
-
-Some kinds of institutions have been shown to support desirable outcomes in water-centered SESs (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wangAlignmentsocialecological2019} and in collaborative water governance systems in Europe \cite{greenEUWaterGovernance2013}).
-At the same time, undesired and unsustainable outcomes (e.g., failures in environmental regulation of highly polluting industries or the development of “tragedy of the commons” situations when pursuing more water resources), with considerable ecological degradation, have attracted much attention \cite{saylesSocialecologicalnetworkanalysis2019,caiPollutingthyneighbor2016,castilla-rhoSocialtippingpoints2017}.
-Despite widespread recognition of the rising importance of integrated water resource management in solving water competition in the world’s large river basins, relatively few studies have explored the mechanisms by which SESs respond to new institutions \cite{agrawalSustainableGovernanceCommonPool2003,pershaSocialEcologicalSynergy2011,agrawalCommonPropertyInstitutions2001}.
-Two particular weaknesses in existing knowledge include understanding (1) the causal links between SES structures and outcomes; and (2) details of the underlying processes, especially the coordination of the incentives of different participants, that result from an institutional lack of fit.
-These weaknesses limit our understanding of institutional design, and they may reduce the speed and transfer of new knowledge and experience related to improving the sustainability of comprehensive water resources management.
-
-In order to disentangle the relationship between SES structure and outcomes, we analyzed a case study to show how an institutional shift led to a structural mismatch that triggered unsustainable water use and unintended ecological deterioration.
-Two rapid shifts in institutional structure that occurred in 1987 and 1998 (see Supplementary Material S1) provide unique settings to exploit quasi-natural experiments of a large river basin, the Yellow River Basin (YRB) in China \cite{xiaDevelopmentWaterAllocation2012}.
-After a period of severe drying up, an institutional shift implemented in 1987 represented the beginning of attempts to control water use in the YRB through the use of quotas, with the goals of alleviating conflicts between supply and demand and achieving sustainable development.
-
-Our results show that this initiative actually accelerated water withdrawals, resulting in an unintended “sprint effect”, where institutional mismatches created an even stronger incentive for each resource user to withdraw resources until the next major institutional shift in 1998.
-Our analysis contributes to a deeper understanding of the mechanisms underlying the relationships among institutions, SES structures, and outcomes.
-By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings are consistent with the urgent calls for a more dynamic design for water use allocation to achieve sustainability.
-
-\section{Institutions and SES structures}
-% 机构可以塑造社会经济体系的结构，对其进行抽象是机械地理解结构和结果之间联系的第一步。
-Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{fig:framework}A).
-% 例如，机构可以创建一种被确定为与良好的社会经济效益相关联的水平匹配结构，如果它鼓励管理相连生态成分的不同行动者之间的协作(图1B)。
-For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{fig:framework}B), leading to sustainable outcomes.
-% 例如，机构可以创建一个结构，鼓励不同行为者之间的合作，管理相连的生态成分
-Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{fig:framework}C and D).
-% 在实践中，一个大型、复杂的河流流域的制度变化将创造或摧毁数百种不同的联系。这些局部变化的更广泛影响可以从系统的整体行为中看到。
-In practice, institutional changes in a large, complex river basin will create or destroy hundreds of different connections.
-The broader impacts of these local changes can be seen in the overall behavior of the system.
-% 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
-We thus explored the causal linkages between the SES structures and sustainability (outcomes) in quasi-natural experiments of the YRB, which provides an informative case study for two main reasons.
-% 首先，长江流域管理的急剧结构变化使我们能够定量估计高层制度设计变化对用水的净影响。决定水分配的制度包括自下而上的协议或社会规范，以及自上而下的配额或法规，它们对社会经济结构有不同的影响;自上而下的监管可能会立即引发制度转变和SES的剧烈结构性变化。通过与由自下而上的制度转变引起的更渐进的变化相比，探索自上而下变化的影响，在对社会经济地位的定量分析中，极大地减少了来自不可观测因素的潜在干扰，提高了社会经济地位结构和结果之间因果关系的清晰度。
-First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use.
-Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013}; top-down regulations can trigger immediate institutional shifts and sharp SES structural changes \cite{speedBasinwaterallocation2013,rolandUnderstandinginstitutionalchange2004}.
-In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and improves the clarity of the causal link between SES structure and outcome.
-% 其次，通过比较长江流域两次制度变迁所分裂的三种不同制度结构的净效应，我们也可以更深入地理解“盆地固定效应”下结构格局的影响。尽管流域内的社会经济单位从世界各地的大型河流流域和许多地区的水资源中受益，但很少有流域多次经历过如此激进的社会经济结构变化。
-Second, by comparing the net effects of three different institutional structures split by two institutional shifts in the YRB, we can also reach a stronger understanding of the influence of structural alignments under a fixed basin.
-Although socioeconomic units within a basin benefit from water resources in large river basins all over the world and many locations have shown increased levels of regulation, few basins have experienced such radical SES structural changes several times (see \textit{Supplementary Material} S1).
-Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in SES institutional structure.
-% 因此，黄河流域的“流域固定效应”为SES结构的自我比较提供了宝贵的机会。
-% Thus, the YRB provides valuable settings for understanding the direct impacts of changes in SES institutional structure.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=8.3cm]{../../../figs/diagrams/framework.jpg}
-	\caption{
-		Framework for understanding linkages between SES structures and outcomes.
-		\textbf{a.} The general framework for analyzing social-ecological systems (SESs) (adapted from Ostrom \cite{ostromGeneralFrameworkAnalyzing2009}).
-Institutions embedded in SESs may reshape structures by changing the interactions between core subsystems, resulting in different outcomes.
-        Three typical types of abstracted SES structures are shown as \textbf{b.}, \textbf{c.} and \textbf{d.} (adapted from Bodin, 2017)\cite{bodinCollaborativeenvironmentalgovernance2017}.
-Red circles indicate social actors, and green ones indicate ecological components.
-Connection (ties between two ecological components), collaboration (ties between two social actors), or management (ties between a social actor and an ecological component) exist when two units are linked by gray lines.
-The gray dashed lines show aligned SES structures that are more likely to result in a desirable outcome according to empirical evidence.
-	}
-    \label{fig:framework}
-\end{figure}
-
-\section{Context of institutional shifts}
+%! Author = songshgeo
+%! Date = 2022/3/10
 % 黄河是世界第五长河，它的流域也是中国文明的摇篮。
@@
 % 然而，经过沿江各省多年的免费取水(图~\ref{fig:structure} A和B)，到20世纪80年代，黄河地表水耗水量接近径流量的10倍，并不断上升
-However, after years of free access to water by provinces along the river (Figure~\ref{fig:structure} A and B), surface water consumption of the Yellow River was close to $80\%$ of its runoff by the 1980s and rising
-\cite{wangYellowRiverwater2019,songSedimenttransportincreasing2020}.
+However, after years of free access to water by provinces along the river (Figure~\ref{fig:structure} A and B), surface water consumption of the Yellow River was close to $80\%$ of its runoff by the 1980s and rising~\cite{wangYellowRiverwater2019,songSedimenttransportincreasing2020}.
 % 自1972年以来，黄河径流量的减少破坏了黄河的生态，制约了黄河的经济发展
-Reductions in runoff after 1972 damaged the ecology of the YRB and restricted its economic development \cite{wangYellowRiverwater2019}.
+Reductions in runoff after 1972 damaged the ecology of the YRB and restricted its economic development~\cite{wangYellowRiverwater2019}.
 % 因此，在中国典型的自上而下的制度结构下(附录图S1-B)，黄河流域不同层次提出了相对完整的水资源分配规定(图1a)。
@@
 % 0世纪70年代以来，中国政府向黄河水利委员会下达指令，要求黄河水利委员会设计配水方案，同时要求黄河沿岸各省进行水资源规划
-In 1982, the Chinese government issued instructions to the Yellow River Water Conservancy Commission (YRCC), the basin agency of the YRB, requiring it to design a water allocation scheme and at the same time requiring the provinces along the Yellow River to carry out water resources planning (see \textit{Supplementary Material S1})
-\cite{wangReviewImplementationYellow2019}.
+In 1982, the Chinese government issued instructions to the Yellow River Water Conservancy Commission (YRCC), the basin agency of the YRB, requiring it to design a water allocation scheme and at the same time requiring the provinces along the Yellow River to carry out water resources planning (see \textit{Supplementary Material S1})~\cite{wangReviewImplementationYellow2019}.
 % 经过多方讨论与权衡，中国政府于1987年为相关省份分配了水资源配额，要求沿黄各省(区)贯彻执行
@@
 % 这一时期长江水利枢纽的监督任务是编制长江水利枢纽用水量统计公报，并与定额进行对比分析。
-The mandate of the YRCC during this period was only to report on and analyze water consumption in the YRB
-\cite{wangReviewImplementationYellow2019}.
+The mandate of the YRCC during this period was only to report on and analyze water consumption in the YRB~\cite{wangReviewImplementationYellow2019}.
 % 随着断流的进一步恶化，1998年中国政府推进了相关政策的改革，要求所有省份在取用水资源时必须向黄委会申请许可，黄委会得以直接对各省的用水实施监管。
@@
 The sharp and unintended decline in the ecological condition of the Yellow River from 1987 to 1998 indicates an institutional mismatch during this period (Figure~\ref{fig:structure} the shadowed time periods).
-
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=12cm]{../../../figs/diagrams/structure.jpg}
-	\caption{
-		% 黄河流域的制度变迁与经济社会结构差异。
-		Institutional shifts and related SES structures in the Yellow River Basin (YRB). See \textit{Supplementary Material S1} for detailed introduction for the institutions.
-		% 国家政府在1987年和1998年先后两次出台了改变流域制度的政策，而黄河水利委员会、利益攸关的各省在不同制度时期具备的功能是不同的。
-		\textbf{A.} The national government changed YRB management policies and institutions in 1987 and 1998.
-As a result, the Yellow River Conservancy Commission (YRCC) and the provinces acted differently in different periods.
-Three different SES structures existed successively in the YRB.
-		% 没有任何政策限制，各利益相关者此时期可以从单向但联通的河流生态单元内自由取水
-		\textbf{B.} 1975–1987: Without any constraints, water resources were freely accessible to each stakeholder (the provinces in this case, denoted by red circles) from a one-way but connected ecological unit (the Yellow River, denoted by the blue rectangle).
-		% 在政策1之后，每个使用者都被分配了能够开采河流地表水资源的配额，而黄委会的工作是对配额的使用进行统计与汇报。
-		\textbf{C.} 1987–1998: After the implementation of policy 1 in 1987, each user was assigned a quota to withdraw surface water resources, and the YRCC (yellow triangle) was tasked with reporting on water quota use.
-		% 第二个政策之后，利益相关者取水需要向黄委会申请，黄委会则根据用水配额来批发许可。因此此时黄委会与利益相关者之间产生了直接的双向联系，监督他们对资源配额的取用。
-		\textbf{D.} 1998–2008: After the implementation of policy 2, stakeholders had to apply for water resources from the YRCC, which then licensed water use according to the quota.
-Under this institution, the YRCC had direct two-way connections between provinces and ecological components.
-		% 由于政策1与政策2都是为了解决黄河断流的生态问题而提出的，因此在结果与政策预期严重相反的第二时期（灰色阴影时段），是制度导致了错配的社会-生态系统结构。
-		\textbf{E.} A timeline of the Yellow River and drying conditions.
-The size of the circles indicates the length of section that dried up (km), and the y-axis indicates the length of the drying period.
-Both policy 1 and policy 2 were put forward to solve this ecological crisis.
-The mismatch created by policy 1 is clearly correlated with the unintended outcomes shown in the second (gray-shaded) period.
-	}
-	\label{fig:structure}
-\end{figure}
-
-\section{Sprint effect induced by an institutional mismatch}
-% % 这里，我们使用合成控制模型创建了假设不存在政策变化的虚拟对照组（see \textit{Methods}-1），同时用K-近临算法找到经济状况与黄河流域各省“类似”的安慰剂对照（see \textit{Methods}-2），反复对比表明两次社会-生态系统结构变迁对流域的水资源利用及分配产生了明显不同的影响。
-% Here, we use synthetic control method to create a control group assuming that there is no water use constraints (\textbf{methods}), at the same time with K-nearest algorithm to match an economic state and the YRB provinces ``similar'' placebo-controlled (\textbf{methods}).
-% % 然后，我们反复比较了两个SES结构(分别自1987年和1998年)，以量化是否有显著不同的影响，YRB用水或分配。
-% Then we repeatedly compared between two SES structures (since 1987 and 1998, respectively) to quantify if there were significantly different impacts on water uses or allocation (\textbf{methods}).
-% % 我们的结果表明，1987年的结构变化刺激各省使用了远超模型预测的没有政策影响下的用水量，其增量超出安慰剂对照组xx\%，但对水资源的分配的均匀程度没有改变（see fig）。
-Our results suggest that the institutional shift in 1987 stimulated the provinces to use far more water than would have been used without policy effects (Figure~\ref{fig:main_results}A), with an observed increase of $164\%$ over the expectation(Figure~\ref{fig:main_results}B).
-% 然而，水资源分配的均匀性并没有改变，区域间的用水量在相同规模下增加(图~\ref{fig:main_results}C)。
-However, the relative share of water use was not changed, denoting proportionally similar water use increases among the different regions (Figure~\ref{fig:main_results}C).
-% 在1998年出台的政策再次改变社会-生态结构之后，用水量显著下降，总量仅为安慰剂对照组的xx%。
-After the SES structure changed again in 1998, the trend of increasing water use appeared to be effectively suppressed (Figure~\ref{fig:main_results} D), with total observed water consumption decreasing by $260\%$ relative to expectations(Figure~\ref{fig:main_results} E).
-% 但此阶段主要是xx，xx，xx等黄河流域的用水大省受到了遏制，因此水资源在各个省之间的比例分配变得更均匀了。
-At this stage, however, the reduction in water use came mainly from the provinces with large water consumption, such as Henan and Shandong (Figure~\ref{fig:main_results} E),  so the proportion of water used by regions became more similar (Figure~\ref{fig:main_results} F).
-% 上述结果表明，1998年各省之间由黄委会统一监管后分水政策才真正达到了其遏制用水、解决断流的预期。
-In conclusion, the water allocation policy curbed water use in 1998, whereas the 1987–1998 institutional mismatch stimulated a notable increase in total water use in all related provinces.
-% 在过去的十年里，对制度变革的“冲刺”反应似乎创造了一场竞赛，每个省份都开始使用超过他们需要的水。
-Over this decade, “sprint” responses (i.e., rapid increases in resource use \cite{lueckPreemptiveHabitatDestruction2003}) to institutional change appear to have created a race in which each province began to use more water than they needed.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=12cm]{../../../figs/outputs/main_results.jpg}
-    \caption{
-        Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
-(\textbf{A} to \textbf{C}: Entering the mismatched SES structure in 1987; \textbf{D} to \textbf{E}: exiting the mismatch in 1998.
-\textbf{A} and \textbf{D}: Impact of the first institutional shift on water use trends in the YRB.
-Blue points are actual water use, and gray points are predicted use under a scenario without any institutional shift (see \textit{Methods}).
-\textbf{B} and \textbf{E}: Impact of the institutional shift on total water use.
-Dark bars indicate the difference between the actual and predicted water use in specific study periods.
-Gray bars are the expected water use, simulated by setting up placebo experiments (null models, see \textit{Methods}).
-\textbf{C} and \textbf{F}: Impact of institutional shift on water allocation equity (see \textit{Methods}).
-Red lines indicate the index calculated from actual water use data; gray lines indicate predicted water use under a scenario with unconstrained water use.
-    }
-    \label{fig:main_results}
-\end{figure}
-
-\section{Incentive distortion causes the sprint effect}
-Theoretically, our economic model suggests that different kinds of institutional shifts should lead to different optimal water uses (Figure~\ref{fig:economic_model}).
-Furthermore, our analysis indicated that the cause of the sprint effect in this case was incentive distortion.
-Compared with the decentralized water allocation institution in place before 1987, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs (see Table~\ref{tab:cases} the \textbf{methods} for a detailed mathematical formula).
-% 在不匹配条件下，边际成本减去边际收益增加，导致用水量增加，xx的差异反映了水配额模拟的非预期冲刺效应。
-The unintended sprint effect (from 1987 to 1998) was caused by both declining marginal costs (a shift from a fixed unit cost to an irrelevant cost) and increasing marginal returns due to future water use benefits (see Table~\ref{tab:cases} the \textbf{methods} for a detailed mathematical formula).
-% 因此，这种制度引发了一种与可持续用水意图背道而驰的激励扭曲。
-The institution thus triggered an incentive distortion that ran counter to the intention of sustainable water use.
-Further, the strength of the sprint effect was positively correlated with the size and time horizon of the water use quota (Figure~\ref{fig:economic_model} \textbf{Panel B}).
-% 这些理论上的预测正如我们在黄河流域所观察到的一样，不匹配的配额制度导致了短跑效应的出现，而中心化的制度结构结束了这一非预期的现象。
-% These theoretical predictions, in line with phenomenon observed in the YRB, indicating the mismatched institution leads to incentive distortion of provinces for pre-empting resources by `sprinting', according to their expectations for the future.
-% 这些理论预测进一步从YRB观察到的现象出发，表明不匹配的配额制度通过提高边际效益来刺激用水量，而边际效益与放宽限制带来的未来潜在用水量的影子值有关。
-% These theoretical predictions, further from the phenomenon observed in the YRB, indicating the mismatched institution with quota stimulates water use by raising marginal benefits, which is related to the shadow value of potential future water use from relaxing the constraints.
-% 温博推荐的版本：
-% These theoretical predictions, further from the phenomenon observed in the YRB, attributing ``sprint effect'' into raising marginal benefits -by pursuing indirectly generating shadow value of water use while converting fixed marginal costs to irrelevant cost for each individual province.
-
-\begin{table}[!ht]
-	\centering
-	\caption{Summary of marginal returns and marginal costs for each case }
-	%\footnotesize
-    \setlength{\tabcolsep}{1mm}{
-       \begin{tabular}{lccc}
-		\hline
-		& Case 1: Decentralized Ins. & Case 2: Mismatched Ins. & Case 3: Matched Ins. \\ \hline
-		Marginal return & $P*F'(X)$                & $P*F'(X)+V(X)^*$            & $P*F'(X)$              \\
-		Marginal cost   & $C/N$                    & $Irrelevant$              & $C$                   \\ \hline
-	\end{tabular}
-    }
-	\centering
-	\footnotesize{\leftline{$^*$Note: $V(X)$ denotes a shadow value.}}
-	\label{tab:cases}
-\end{table}
-
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=12cm]{../../../figs/outputs/economic_model.jpg}
-	\caption{
-		% \textbf{Assumption 1:} \textit{(Production)} Assuming that water is the only input of the homogenous production function F(x) of each province.
-Under diminishing marginal returns assumption, and $F(x)$ is continuous, $F'(0)=\infty$, $ F'(\infty)=0$.
-The production output is under perfect competition, with constant unit price of P.
-		% \textbf{Assumption 2:} \textit{(Cost function)} Assuming that the ecology is a unity for the whole basin, the cost of water use is equally assigned to each province under any water use.
-The unit cost of water is a constant C.
-		% \textbf{Assumption 3:} \textit{(Multi-period setting)} There are infinite periods with constant discount factor $\beta$ lying in (0,1) with no cross-period smoothing in water uses.
-		\textbf{A.} The relationship of marginal benefits and water use of province i at t = 0 for three different cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}, assuming $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, and $\beta=0.4$ as an example  (see \textit{Methods}In Case 3, water use by others is taken as a given, equal to the optimal water use for Case 2.
-The horizontal coordinate of each intersection of marginal benefits and the break-even line represents the optimal water use under each case.
-		\textbf{Panel B.} The relation between optimal water use of province i and total quota for Case 3, under time horizon of $T=5$, $T=10$, and an infinite $T$, respectively.
-The settings are the same as in \textbf{A}.
-	}
-	\label{fig:economic_model}
-\end{figure}
-
-\section{Discussion}
-% 我们展示了不匹配的分配制度是如何导致激励失真导致水资源加速耗竭的(即“冲刺效应”)。“冲刺效应”是CPR系统面临的一种特殊情况，在这种情况下，制度的不匹配为每个资源使用者创造了更强的动机(扭曲)，促使他们收回资源
-We have shown how a mismatched allocation institution can lead to an accelerated depletion of water resources (i.e., the “sprint effect”) caused by incentive distortion.
-The sprint effect is a special case faced by CPR systems, where institutional mismatches create an even stronger incentive (with distortion) for each resource user to withdraw resources
-\cite{ostromRevisitingCommonsLocal1999,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017}.
-% 过往研究指出制度常常是避免公共池塘资源系统的崩溃的关键，但“短跑效应”的出现表明在自上而下进行制度设计所形成的错配SES结构中，制度也可以成为系统加速崩溃的触发者。
-Previous studies have suggested that institutions are often the key to avoid the collapse of a CPR system, but the emergence of a sprint effect shows that an institution with structural mismatches can also be the trigger that accelerates system collapse \cite{bodinConservationSuccessFunction2014,bodinCollaborativeenvironmentalgovernance2017,wangAlignmentsocialecological2019}.
-The initial formulation of the water quota in our case studies went through a stage of “bargaining” among stakeholders (from 1982 to 1987) \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}, where each province attempted to demonstrate its development potential related to water use.
-% 在高层决策者与低层利益相关者之间存在信息不对称的用水分配中，当前用水量越大的利益相关者议价能力越大。1987年以后，对各省来说，合乎逻辑的下一步是试图证明争取更大配额的合理性，而不是立即采取资源节约型改革。在实践中，尽管受影响的省份可能没有直接鼓励过度使用资源，但由于激励扭曲，他们有更大的动机对资源提取开绿灯。因此，在争夺潜在的水资源配额时，各省往往将生态成本隐藏在经济发展背后。
-In water use allocation with information asymmetry between upper-level decision-makers and lower-level stakeholders, those with more current water use might have greater bargaining power.
-After 1987, the logical next step for provinces was to attempt to justify bargaining for larger quotas rather than immediately adopt resource-conserving transformations.
-In practice, although the affected provinces may not have directly encouraged excessive resource use, they had a greater incentive to give the green light to resource withdrawals because of incentive distortions \cite{kriegerProgressGroundWater1955, ostromGoverningCommonsEvolution1990}.
-As a result, while competing for potential water quotas, the provinces tended to hide the ecological costs behind economic development.
-
-% 毫无疑问，随着资源竞争的日趋激烈，越来越多的SES正依赖着不同形式的制度进行资源分配（如自组织和政府干预），避免“短跑效应”的出现或将成为制度设计的关键。
-There is no doubt that with increasingly fierce competition for water, more and more SESs are developing new institutions for water allocation (whether through self-organization or government intervention) \cite{anderssonVoluntaryleadershipemergence2020, wutichWaterScarcitySustainability2009}.
-% 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
-Adoption of an overall quota plays an important role in preventing overuse of CPRs \cite{tilmanLocalizedprosocialpreferences2019}.
-However, the negative effects of incentive distortion imply a trade-off between long-term SES benefits and current stability, and the proportion of available resources allocated under quota schemes matters when institutions change \cite{ladeRegimeshiftssocialecological2013}.
-According to our analysis of plausible scenario assumptions based on our general economic model, the sprint effect will be reinforced when stakeholders anticipate that technological advances will amplify the benefits of water quotas in the future (see \textit{Supplementary Material S3}).
-% 然而，如果有水权转换机制允许利益相关者之间通过交易来弥补 shadow value，当前这种错乱的动机就不会那么强。
-However, if an institution allowed stakeholders to compensate for the shadow value (i.e., potential returns sacrificed due to water constraints and water scarcity) \cite{howarthAccountingvalueecosystem2002} of future water use, incentive distortion would be less devastating (e.g., through water rights transfer).
-Policymakers can also weaken the sprint effect by increasing the frequency of quota updates, supporting the idea that a more dynamic institution that responds to changing conditions (see \textit{Supplementary Material S3}) will adapt more effectively to its social-ecological context.
-
-% 近年来黄河流域面临的分水制度调整问题也说明了动态设置配额的重要性。
-Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of dynamic quota setting (see \textit{Supplementary Material S1}) \cite{yuAdaptabilityassessmentpromotion2019}.
-Following the institutional reforms of 1998, the Yellow River has not dried up since 1999.
-However, given recent changes in the YRB, its rigid resource allocation scheme can no longer meet the new demands of economic development \cite{wangThingsCurrentSignificance2019}.
-The Chinese government has embarked on an ambitious plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}).
-Other SESs around the world face similar problems in establishing successful resource allocation institutions \cite{cummingQuantifyingSocialEcologicalScale2020, muneepeerakulStrategicbehaviorsgovernance2017, cummingAdvancingunderstandingnatural2020, leslieOperationalizingsocialecologicalsystems2015}.
-These initiatives can benefit from our analysis by actively considering and incorporating social-ecological complexity and incentive structures when developing new approaches that avoid unsustainable outcomes.
-Our research provides a cautionary tale of how institutions can act as a double-edged sword when trying to attain sustainability.
-
-\section{Methods}
-% 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程
-We estimated and analyzed the net effects of two SES structural changes of water use.
-The actual water use of the Yellow River Basin was peroxided by the sum of the water use of the target group provinces.
-To quantify water use, we used synthetic control methods to estimate possible trends of water use in the absence of institutional shifts.
-In addition, as a robustness test, we conducted a matched placebo test (creating a “null model”) to exclude the effects of other factors that were contemporaneous with the institutional shifts.
-Finally, we created an economic model based on marginal revenue to provide a theoretical explanation for the observed “sprint effect” phenomenon.
-A brief technical overview is given in \textit{Supplementary Material S2}.
-
-\subsection{Dataset and variables}
-% 我们使用中国1978年至2012年各省的年度用水量数据集，这个公开的数据集由全国水资源利用调查得到，详细可查看。
-We used China’s provincial annual water consumption dataset from 1978 to 2012.
-This publicly available dataset was obtained from the National Water Resources Utilization Survey; details are accessible from Zhou (2020)
-\cite{zhouDecelerationChinahuman2020}.
-A total of 10 provinces or regions have been directly affected by the water allocation institutional shifts in the YRB, accounting for $8.6\%$ of the total population of China (in 1990).
-Eight provinces have been particularly affected because of their greater dependence on the water resources from the Yellow River (see \textit{Supplementary Material S2}).
-Therefore, we divided the dataset into a “target group” and a “control group”, treating provinces that were greatly affected as the target group $(n=8)$ and provinces that were not affected by the institutional shifts as the potential control group $(n=20)$.
-
-We focused on two features of water use in the YRB: total water use and diversification of water allocation.
-The actual water uses are given by the dataset, but when the synthetic control method is used to predict the water use of the control group, other independent influences need to be considered.
-Thus, we used economic features that are highly related to water use to extrapolate demand (e.g., agriculture, industry, service industry, and domestics, see \textit{Supplementary Material S2, Table 1} To measure resource allocation diversification between the upper, middle, and lower reaches, we used “entropy” as a simple index,
-
-$$ Index_{entropy} = \sum_i{p_i *log(p_i)} $$
-
-% 式子中的p是每个使用的水占流域总用水的比例
-Where $p_i$ is the proportion of water uses for region $i$ to the total water uses in the basin.
-A larger index value indicates the proportion of water resources actually used is closer to the average among the upper, middle, and lower reaches.
-
-\subsection{Synthetic Control}
-Synthetic control is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadieSyntheticControlMethods2010}.
-In this study, we used a comparative event approach and compared actual post-institutional shift induced water use changes with an appropriate counterfactual of what the water use change would have been.
-The counterfactual was built as the optimally weighted average of provinces not exposed to the institutional shifts.
-The synthetic control method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity \cite{billmeierAssessingEconomicLiberalization2013, smithresourcecurseexorcised2015}.
-In practice, each of the units (i.e., provinces) in the treated group were affected by institutional shifts in 1987 and 1998, each of which was taken as the “shifted” point $t_0$ and the two steady institutions as $t$ for analyzing in each shift.
-The synthetic control method generates the control unit by assigning a weight matrix $W$ to units of the potential control group, so that the treated unit and its control unit are similar in each variable before $t_0$, i.e.,
-
-$$\min(V_{i}^{t<t_0} - W_i * F_{control}^{t<t_0})$$
-
-where $V_i$ is a vector that indicates all features of a unit $i$ of the treated group, and $F_{control}$ is a matrix that consists of all features and units of the potential control group.
-$W_i$ is the weight matrix for target unit $i$.
-We minimized the root mean square error (RMSE) by using the Synth package in R \cite{abadieSynthPackageSynthetic2011, abadieComparativePoliticsSynthetic2015}.
-All codes are accessible in the repository.
-
-% 这样一来，基于降维的思想，我们构建出了一系列特征上与实验组最为接近的可比对照。
-In accordance with the idea of dimensionality reduction, we constructed a series of comparable control units that were most similar in characteristics to the treated units.
-Because the units of the control group were not affected by the institutional shifts, after giving the same weight to the total water use of the control group $M_i * WU_{control}$, the result $W_i*WU_{control}$ could be considered a reasonable estimation of the untreated situation.
-The net effect of the water allocation institutional shift was then estimated by calculating the difference of water uses after the institutional shift between the treated group and the control group, compared with the water use difference before the shift.
-
-\subsection{Placebo Test}
-% 作为一种稳健性检验，安慰剂测试的必要性体现在两个原因上。
-For robustness, we conducted a placebo test because the synthetic control method neglects the influences of overall changes in factors in the same year by simply dividing time periods according to institutional shifts.
-Three steps were required to apply the placebo test:
-% (1) 对目标组中的每个省份$i$，计算所有潜在控制组与它之间特征向量的欧氏距离
-(1) For each province in the target group, we calculated the Euclidean distance of vectors between all provinces in the potential control group.
-% (2) 将距离由小到大排序后，选取特征向量最相似的三个省份，所有特征的均值作为 $i$ 的替代
-(2) After ranking the distances, the three provinces with the most similar economic context were used to generate an average paired treatment target unit.
-% (3) 对这个配对目标同样实施控制合成法（潜在控制组排除构成它的三个省）
-(3) We performed the same synthetic control analysis for this paired target (i.e., the potential control group excluding the three provinces in step 2).
-% 经过上述步骤，我们在理论上构建了一个相似的“区域”并实施了同样的控制合成实验。
-In this way, we theoretically constructed a pseudo-treated unit and performed the same synthetic control treatments.
-Because these placebo tests were directed at units unaffected by the institutional shifts, the results can be regarded as a reasonable baseline expectation or null model from which to assess the changes caused by other factors.
-
-\subsection{Economic model}
-In order to understand the mechanisms underlying the empirical results, we developed a dynamic economic model to analyze how institutional change could have led to the sprint effect in water use.
-Specifically, we modeled individual provincial decision-making in water resources before quota execution.
-The analysis result implied that the underlying driver of CPR overuse was incentive distortion.
-
-In developing the model, we highlighted the main features of the YRB, as well as the water use institutions of 1987 and 1998. We proposed three intuitive and general assumptions.
-
-\begin{ass}
-    % (生产)为了简化，由于不可替代性，水是每个省的同质生产函数10的唯一投入。$F(x)$是连续的，满足Inada条件，即$F'(x)>0, F''(x)<0$(边际收益递减假设)，$F'(0)=\infty$,$ F'(\infty)=0$。产品产量处于完全竞争状态，单位价格为15。
-    (Water-dependent production) For simplicity, water is assumed to be the only input of the homogenous production function $F(x)$ of each province because of its irreplaceability.
-$F(x)$ is continuous and satisfies the Inada Conditions, i.e., $F'(x)>0, F''(x)<0$ (the diminishing marginal returns assumption), $F'(0)=\infty$,$ F'(\infty)=0$.
-The production output is under perfect competition, with a constant unit price of $P$.
-\end{ass}
-\begin{ass}
-    (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in N provinces, the cost of water use is equally assigned to each province under any water use.
-The unit cost of water is a constant $C$.
-\end{ass}
-\begin{ass}
-    (Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water uses.
-\end{ass}
-
-Under the above assumptions, we can demonstrate three cases consisting of local governments in YRB to simulate their water use decision-making and water use patterns.
-
-\begin{case} Decentralized institution:
-    This case corresponds to a situation without any high-level water allocation institution (i.e., before 1987, see Figure~\ref{fig:structure} B).
-
-    When each province independently decides on its water use, the optimal water use $\hat x_i^*$ in province $i$ satisfies:
-    $$F'(x)=\frac{C}{P \cdot N}$$
-
-    When the decisions in different periods are independent, for $t=0,1,2 \ldots$, then:
-    $$\hat x_{it}^*=\hat x_i^*$$
-
-\end{case}
-
-\begin{case} Mismatched institution
-    This case corresponds to a mismatched institution (i.e., $1987\sim1998$, see Figure~\ref{fig:structure} C).
-
-    The water quota is determined at $t=0$ and imposed in $t=1,2,\ldots$ The total quota is a constant denoted as $Q$, and the quota for province $i$ is determined in a proportional form:
-    $$Q_i=Q \cdot \frac{x_i}{x_i + \begin{matrix} \sum x_{-i} \end{matrix}}$$
-
-    Under a scenario with decentralized decision-making with a water quota institution, given other provinces’ water use decisions remain unchanged, the optimal water use $\widetilde x_{i0}^*$ of province $i$ at $t=0$ satisfies:
-
-    $F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot f(Q \cdot \frac{x_{i,0}}{\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix})^2}$.
-
-    When future water use is constrained by a water quota, the dynamic optimization problem of province $i$ is shown as follows:
-
-    $max  \quad P \cdot F(x_{i,0})-\frac{C \cdot \begin{matrix} \sum x_{i,0} + x_{-i,0} \end{matrix}}{N}+\beta P \cdot F(x_{i,1})+\beta^2 P \cdot F(x_{i,2})+...$
-
-    $=P \cdot F(x_{i,0})-C \cdot \frac{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}{N}+\frac{\beta}{1-\beta} P \cdot F(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}})$
-
-    First-order condition: $P \cdot F'(x_{i,0})-\frac{C}{N}+\frac{\beta}{1-\beta}[P \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0}+\begin{matrix} \sum  x_{-i,0} \end{matrix})^2}]=0$
-
-    where $f(\cdot)$ is the differential function of $F(\cdot)$.
-
-    The optimal water use in province i at t=0 $\widetilde x_{i,0}^*$ satisfies $P \cdot F'(x_{i,0})=\frac{C}{N}-\frac{\beta}{1-\beta} \cdot P \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$, i.e., $F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$.
-
-\end{case}
-
-\begin{case} Matched institution
-
-    This case corresponds to the institution under which the YRCC centrally managed water allocation between provinces (i.e., $1998\sim2008$, see Figure~\ref{fig:structure} D).
-
-    When the $N$ provinces decide on water uses as unified whole (e.g., the central government completely decides and controls on the water use in each province), the optimal water use $x_i^*$ of province $i$ satisfies:
-
-    $$F'(x)=\frac{C}{P}$$
-
-\end{case}
-
-We propose Proposition 1 and Proposition 2:
-
-\textbf{Proposition 1}: Compared with the decentralized institution, a matched institution with unified management decreases total water use.
-
-Because $F’$ is monotonically decreasing, based on a comparison of costs and benefits for stakeholders (provinces) in the three cases,
-
-$$\widetilde x_i^*>\hat x_i^*>x_i^*$$
-
-The result of $\hat x_i^*>x_i^*$ indicates that individual rationality would deviate from collective rationality when property rights are unclear \cite{hardinTragedyCommons2009}, because of the common-pool characteristics of water
-\cite{castilla-rhoGroundwaterCommonPool2020,ostromGeneralFrameworkAnalyzing2009}.
-
-The difference of $\widetilde x_i^*$ and $\hat x_i^*$ stems from two parts: the marginal returns effect and the marginal costs effect.
-First, the “shadow value” provides additional marginal returns of water use in $t=0$, wwhich increases the incentives of water overuse by encouraging bargaining for a larger quota.
-Second, the future cost of water use would be degraded from $\frac{P}{N}$ to an irrelevant cost.
-
-The optimal water use under the three cases implies that mismatched institutions cause incentive distortions and lead to resource overuse.
-
-\textbf{Proposition 2}: The quota determination of the mismatched institution increases the incentives of current water use.
-
-The intuition for this proposition is straight-forward in that all provinces would use up their allocated quota under a relatively small $Q$.
-As $Q$ increases, the quota would provide higher future benefits for a pre-emptive water use strategy.
-Since the provincial water use decisions are exactly symmetric, total water use would increase when each province has higher incentives for current water use.
-This situation corresponds to a “sprint” effect, where the total water use dramatically increases in the “sprint” period.
-
-Extensions of the model are shown in \textit{Supplementary Material S3}.
-
-\section{Info.}
-Funding was provided by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007).
-
-[Competing Interests] The authors declare that they have no competing interests.
-
-[Correspondence] Correspondence and requests for materials should be addressed to Shuai Wang.~(email: shuaiwang@bnu.edu.cn).
-
-[Author contributions]Shuai Wang and Bojie Fu designed this research, Shuang Song performed the research and analyzed data, and Huiyu Wen designed the economic model.
-Shuang Song and Huiyu Wen wrote the paper, and Graeme S.
-Cumming revised the manuscript and offered important advice.
-
-[Code availability] All codes and datasets used in this research are accessible at https://github.com/SongshGeo/sochyd-transboundary-HESS.
-They will be made open source after this project is completed.
-
-%% Put the bibliography here, most people will use BiBTeX in
-%% which case the environment below should be replaced with
-%% the \bibliography{} command.
-\bibliography{WAInstitution_YRB_2021}
-
-%% Here is the endmatter stuff: Supplementary Info, etc.
-%% Use \item's to separate, default label is "Acknowledgements"
-
-\end{document}

### 2022-03-10 docs/papers/elements/model.tex
docs(paper): initialize paper in LaTeX, prepared to refactor it

--- 2022-03-04 docs/papers/tex/main.tex
@@
-%% Template for a preprint Letter or Article for submission
-%% to the journal Nature.
-%% Written by Peter Czoschke, 26 February 2004
-%%
-\documentclass{article}
-\usepackage{hyperref}
-\usepackage{graphicx}
-\usepackage{setspace}
-\usepackage[a4paper, total={7in, 10in}]{geometry}
-
-\setstretch{1.523}
-
-\newtheorem{ass}{Assumption}
-\newtheorem{case}{Case}
-%% make sure you have the nature.cls and naturemag.bst files where
-%% LaTeX can find them
-
-\bibliographystyle{naturemag}
-
-%\usepackage{biblatex}
-%% make sure you have the nature.cls and naturemag.bst files where
-%% LaTeX can find them
-
-\title{Importance of social-ecological fit for water management in large river basins: An analysis of institutional shifts in the Yellow River Basin}
-
-%% Notice placement of commas and superscripts and use of &
-%% in the author list
-
-\author{Shuang Song$^{1,2}$, Huiyu Wen$^3$, *Shuai Wang$^{1,2}$, Graeme S. Cumming$^{4}$ \& Bojie Fu$^{1, 2}$}
-
-\begin{document}
-
-\maketitle
-\input{../../drafts/authors.md}
-
-\begin{abstract}
-    \input{../../drafts/abstract.md}
-\end{abstract}
-
-% Then the body of the main text appears after the intro paragraph.
-% Figure environments can be left in place in the document.
-% \verb|\includegraphics| commands are ignored since Nature wants
-% the figures sent as separate files and the captions are
-% automatically moved to the end of the document (they are printed
-% out with the \verb|\end{document}| command. However, tables must
-% be manually moved to the end of the document, after the addendum.
-% 表需要手动移到文末
-% water use; water management; social-ecological system; common pool resources; institutional analysis; collaborative governance
-
-\section{Introduction}
-Emerging competition for water is an urgent problem in water governance, with widespread water scarcity and overuse resulting in huge impacts on economies, societies, and ecosystems \cite{gleickPeakwaterlimits2010,dolanEvaluatingeconomicimpact2021,siwiCompetitionWaterGetting,ziolkowskaCompetitionWaterResources2016,distefanoArewedeep2017}.
-Water is the key exclusive and competitive resource that couples socioeconomic and ecological systems (known as common-pool resources, CPRs) \cite{wutichWaterScarcitySustainability2009,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017,castilla-rhoGroundwaterCommonPool2020}.
-Conflicts of interest often occur in allocation and competitions of water resources, with water governance policies often leading to long-term changes in human–water relationships and the redistribution of benefits \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013,chingManagingsocioecologyvery2015}.
-Although governments in many of the world’s large river basins have tried to resolve competition for water through the deliberate design of new institutions, general principles underlying the successes and failures of these initiatives are poorly documented and understood.
-
-Institutions (such as policies, laws, and norms) can influence regional sustainability by changing social-ecological system (SES) structure and dynamics \cite{youngInstitutionsenvironmentalchange2008,cummingAdvancingunderstandingnatural2020,lieninstitutionalgrammartool2020}.
-These include inter-relationships and interactions between social actors, between ecological units, or between social and ecological system elements \cite{bodinCollaborativeenvironmentalgovernance2017,barnesSocialecologicalalignmentecological2019}.
-Effective (“matched”) institutions operate at appropriate spatial, temporal, and functional scales to manage and balance these different relationships and interactions \cite{heWateringEnvironmentalRegulation2020,kellenbergempiricalinvestigationpollution2009}.
-From the perspective of SES outcomes, matched institutions support (but do not guarantee) sustainability \cite{epsteinInstitutionalfitsustainability2015,wangAlignmentsocialecological2019}.
-
-Some kinds of institutions have been shown to support desirable outcomes in water-centered SESs (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wangAlignmentsocialecological2019} and in collaborative water governance systems in Europe \cite{greenEUWaterGovernance2013}).
-At the same time, undesired and unsustainable outcomes (e.g., failures in environmental regulation of highly polluting industries or the development of “tragedy of the commons” situations when pursuing more water resources), with considerable ecological degradation, have attracted much attention \cite{saylesSocialecologicalnetworkanalysis2019,caiPollutingthyneighbor2016,castilla-rhoSocialtippingpoints2017}.
-Despite widespread recognition of the rising importance of integrated water resource management in solving water competition in the world’s large river basins, relatively few studies have explored the mechanisms by which SESs respond to new institutions \cite{agrawalSustainableGovernanceCommonPool2003,pershaSocialEcologicalSynergy2011,agrawalCommonPropertyInstitutions2001}.
-Two particular weaknesses in existing knowledge include understanding (1) the causal links between SES structures and outcomes; and (2) details of the underlying processes, especially the coordination of the incentives of different participants, that result from an institutional lack of fit.
-These weaknesses limit our understanding of institutional design, and they may reduce the speed and transfer of new knowledge and experience related to improving the sustainability of comprehensive water resources management.
-
-In order to disentangle the relationship between SES structure and outcomes, we analyzed a case study to show how an institutional shift led to a structural mismatch that triggered unsustainable water use and unintended ecological deterioration.
-Two rapid shifts in institutional structure that occurred in 1987 and 1998 (see Supplementary Material S1) provide unique settings to exploit quasi-natural experiments of a large river basin, the Yellow River Basin (YRB) in China \cite{xiaDevelopmentWaterAllocation2012}.
-After a period of severe drying up, an institutional shift implemented in 1987 represented the beginning of attempts to control water use in the YRB through the use of quotas, with the goals of alleviating conflicts between supply and demand and achieving sustainable development.
-
-Our results show that this initiative actually accelerated water withdrawals, resulting in an unintended “sprint effect”, where institutional mismatches created an even stronger incentive for each resource user to withdraw resources until the next major institutional shift in 1998.
-Our analysis contributes to a deeper understanding of the mechanisms underlying the relationships among institutions, SES structures, and outcomes.
-By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings are consistent with the urgent calls for a more dynamic design for water use allocation to achieve sustainability.
-
-\section{Institutions and SES structures}
-% 机构可以塑造社会经济体系的结构，对其进行抽象是机械地理解结构和结果之间联系的第一步。
-Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{fig:framework}A).
-% 例如，机构可以创建一种被确定为与良好的社会经济效益相关联的水平匹配结构，如果它鼓励管理相连生态成分的不同行动者之间的协作(图1B)。
-For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{fig:framework}B), leading to sustainable outcomes.
-% 例如，机构可以创建一个结构，鼓励不同行为者之间的合作，管理相连的生态成分
-Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{fig:framework}C and D).
-% 在实践中，一个大型、复杂的河流流域的制度变化将创造或摧毁数百种不同的联系。这些局部变化的更广泛影响可以从系统的整体行为中看到。
-In practice, institutional changes in a large, complex river basin will create or destroy hundreds of different connections.
-The broader impacts of these local changes can be seen in the overall behavior of the system.
-% 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
-We thus explored the causal linkages between the SES structures and sustainability (outcomes) in quasi-natural experiments of the YRB, which provides an informative case study for two main reasons.
-% 首先，长江流域管理的急剧结构变化使我们能够定量估计高层制度设计变化对用水的净影响。决定水分配的制度包括自下而上的协议或社会规范，以及自上而下的配额或法规，它们对社会经济结构有不同的影响;自上而下的监管可能会立即引发制度转变和SES的剧烈结构性变化。通过与由自下而上的制度转变引起的更渐进的变化相比，探索自上而下变化的影响，在对社会经济地位的定量分析中，极大地减少了来自不可观测因素的潜在干扰，提高了社会经济地位结构和结果之间因果关系的清晰度。
-First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use.
-Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013}; top-down regulations can trigger immediate institutional shifts and sharp SES structural changes \cite{speedBasinwaterallocation2013,rolandUnderstandinginstitutionalchange2004}.
-In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and improves the clarity of the causal link between SES structure and outcome.
-% 其次，通过比较长江流域两次制度变迁所分裂的三种不同制度结构的净效应，我们也可以更深入地理解“盆地固定效应”下结构格局的影响。尽管流域内的社会经济单位从世界各地的大型河流流域和许多地区的水资源中受益，但很少有流域多次经历过如此激进的社会经济结构变化。
-Second, by comparing the net effects of three different institutional structures split by two institutional shifts in the YRB, we can also reach a stronger understanding of the influence of structural alignments under a fixed basin.
-Although socioeconomic units within a basin benefit from water resources in large river basins all over the world and many locations have shown increased levels of regulation, few basins have experienced such radical SES structural changes several times (see \textit{Supplementary Material} S1).
-Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in SES institutional structure.
-% 因此，黄河流域的“流域固定效应”为SES结构的自我比较提供了宝贵的机会。
-% Thus, the YRB provides valuable settings for understanding the direct impacts of changes in SES institutional structure.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=8.3cm]{../../../figs/diagrams/framework.jpg}
-	\caption{
-		Framework for understanding linkages between SES structures and outcomes.
-		\textbf{a.} The general framework for analyzing social-ecological systems (SESs) (adapted from Ostrom \cite{ostromGeneralFrameworkAnalyzing2009}).
-Institutions embedded in SESs may reshape structures by changing the interactions between core subsystems, resulting in different outcomes.
-        Three typical types of abstracted SES structures are shown as \textbf{b.}, \textbf{c.} and \textbf{d.} (adapted from Bodin, 2017)\cite{bodinCollaborativeenvironmentalgovernance2017}.
-Red circles indicate social actors, and green ones indicate ecological components.
-Connection (ties between two ecological components), collaboration (ties between two social actors), or management (ties between a social actor and an ecological component) exist when two units are linked by gray lines.
-The gray dashed lines show aligned SES structures that are more likely to result in a desirable outcome according to empirical evidence.
-	}
-    \label{fig:framework}
-\end{figure}
-
-\section{Context of institutional shifts}
-% 黄河是世界第五长河，它的流域也是中国文明的摇篮。
-The Yellow River, whose basin is the cradle of Chinese civilization, is the fifth-longest river in the world.
-It supports $9.7\%$ of China’s irrigation, with only $2.6\%$ of its total water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021).
-% 然而，经过沿江各省多年的免费取水(图~\ref{fig:structure} A和B)，到20世纪80年代，黄河地表水耗水量接近径流量的10倍，并不断上升
-However, after years of free access to water by provinces along the river (Figure~\ref{fig:structure} A and B), surface water consumption of the Yellow River was close to $80\%$ of its runoff by the 1980s and rising
-\cite{wangYellowRiverwater2019,songSedimenttransportincreasing2020}.
-% 自1972年以来，黄河径流量的减少破坏了黄河的生态，制约了黄河的经济发展
-Reductions in runoff after 1972 damaged the ecology of the YRB and restricted its economic development \cite{wangYellowRiverwater2019}.
-% 因此，在中国典型的自上而下的制度结构下(附录图S1-B)，黄河流域不同层次提出了相对完整的水资源分配规定(图1a)。
-Therefore, through typical top-down institutional structures in China (see \textit{Supplementary Material S1}), relatively integrated water allocation regulations were successively proposed across different levels in the YRB.
-% 这些机构包括国家政府、流域管理机构、省、市，甚至地区(见图1 B-D)。
-These include the national government, the basin management agency, provinces, cities, and even districts.
-% 这些在不同制度发展阶段相继出台的政策，引发了长江经济带经济发展结构的突变，并产生了不同的结果(见附录A和图S1-C)。
-These policies at different stages of institutional development triggered abrupt changes in the SES structure of the YRB with different outcomes.
-
-% 0世纪70年代以来，中国政府向黄河水利委员会下达指令，要求黄河水利委员会设计配水方案，同时要求黄河沿岸各省进行水资源规划
-In 1982, the Chinese government issued instructions to the Yellow River Water Conservancy Commission (YRCC), the basin agency of the YRB, requiring it to design a water allocation scheme and at the same time requiring the provinces along the Yellow River to carry out water resources planning (see \textit{Supplementary Material S1})
-\cite{wangReviewImplementationYellow2019}.
-% 经过多方讨论与权衡，中国政府于1987年为相关省份分配了水资源配额，要求沿黄各省(区)贯彻执行
-The Chinese government started to assign water quotas to the relevant provinces in 1987, but did not create a unit to coordinate water division between them (Figure~\ref{fig:structure} \textbf{A} and \textbf{C}).
-% 这一时期长江水利枢纽的监督任务是编制长江水利枢纽用水量统计公报，并与定额进行对比分析。
-The mandate of the YRCC during this period was only to report on and analyze water consumption in the YRB
-\cite{wangReviewImplementationYellow2019}.
-% 随着断流的进一步恶化，1998年中国政府推进了相关政策的改革，要求所有省份在取用水资源时必须向黄委会申请许可，黄委会得以直接对各省的用水实施监管。
-However, since reductions in river flow indicated an unintended SES outcome (Figure~\ref{fig:structure} E), the Chinese government pushed for a policy reform in 1998 that required all provinces to apply for licenses to use water from the YRCC, allowing the council to directly regulate their water use (see \textit{Supplementary Material S1} and Figure~\ref{fig:structure} A and D).
-% 由于革新后的政策成功遏制了断流，2008年该分配政策被进一步细化，相关各省都进一步设置了更细致的分配方案，并最终形成了黄河流域如今的水资源分配格局。
-The 1998 policy succeeded in curbing water extraction (Figure~\ref{fig:structure} E), and it was further refined in 2008.
-The relevant provinces created a more detailed allocation plan and finally formed the present water allocation institutions of the YRB (see \textit{Supplementary Material S1}).
-% 因此，在1975-2008长达33年的时间里，从没有分水政策到以两种不同模式监管下的分水政策，黄河流域实际上先后存在着三种不同的社会-生态结构（Fig 1）。
-Therefore, in our study period (from 1975 to 2008), the system shifted between three different SES structures (Figure~\ref{fig:structure} \textbf{B} to \textbf{D}).
-% 在它们之中，与预期相反地，1987年至1998年的流域SES结构下黄河的生态急剧恶化，表明了制度的失配。
-The sharp and unintended decline in the ecological condition of the Yellow River from 1987 to 1998 indicates an institutional mismatch during this period (Figure~\ref{fig:structure} the shadowed time periods).
-
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=12cm]{../../../figs/diagrams/structure.jpg}
-	\caption{
-		% 黄河流域的制度变迁与经济社会结构差异。
-		Institutional shifts and related SES structures in the Yellow River Basin (YRB). See \textit{Supplementary Material S1} for detailed introduction for the institutions.
-		% 国家政府在1987年和1998年先后两次出台了改变流域制度的政策，而黄河水利委员会、利益攸关的各省在不同制度时期具备的功能是不同的。
-		\textbf{A.} The national government changed YRB management policies and institutions in 1987 and 1998.
-As a result, the Yellow River Conservancy Commission (YRCC) and the provinces acted differently in different periods.
-Three different SES structures existed successively in the YRB.
-		% 没有任何政策限制，各利益相关者此时期可以从单向但联通的河流生态单元内自由取水
-		\textbf{B.} 1975–1987: Without any constraints, water resources were freely accessible to each stakeholder (the provinces in this case, denoted by red circles) from a one-way but connected ecological unit (the Yellow River, denoted by the blue rectangle).
-		% 在政策1之后，每个使用者都被分配了能够开采河流地表水资源的配额，而黄委会的工作是对配额的使用进行统计与汇报。
-		\textbf{C.} 1987–1998: After the implementation of policy 1 in 1987, each user was assigned a quota to withdraw surface water resources, and the YRCC (yellow triangle) was tasked with reporting on water quota use.
-		% 第二个政策之后，利益相关者取水需要向黄委会申请，黄委会则根据用水配额来批发许可。因此此时黄委会与利益相关者之间产生了直接的双向联系，监督他们对资源配额的取用。
-		\textbf{D.} 1998–2008: After the implementation of policy 2, stakeholders had to apply for water resources from the YRCC, which then licensed water use according to the quota.
-Under this institution, the YRCC had direct two-way connections between provinces and ecological components.
-		% 由于政策1与政策2都是为了解决黄河断流的生态问题而提出的，因此在结果与政策预期严重相反的第二时期（灰色阴影时段），是制度导致了错配的社会-生态系统结构。
-		\textbf{E.} A timeline of the Yellow River and drying conditions.
-The size of the circles indicates the length of section that dried up (km), and the y-axis indicates the length of the drying period.
-Both policy 1 and policy 2 were put forward to solve this ecological crisis.
-The mismatch created by policy 1 is clearly correlated with the unintended outcomes shown in the second (gray-shaded) period.
-	}
-	\label{fig:structure}
-\end{figure}
-
-\section{Sprint effect induced by an institutional mismatch}
-% % 这里，我们使用合成控制模型创建了假设不存在政策变化的虚拟对照组（see \textit{Methods}-1），同时用K-近临算法找到经济状况与黄河流域各省“类似”的安慰剂对照（see \textit{Methods}-2），反复对比表明两次社会-生态系统结构变迁对流域的水资源利用及分配产生了明显不同的影响。
-% Here, we use synthetic control method to create a control group assuming that there is no water use constraints (\textbf{methods}), at the same time with K-nearest algorithm to match an economic state and the YRB provinces ``similar'' placebo-controlled (\textbf{methods}).
-% % 然后，我们反复比较了两个SES结构(分别自1987年和1998年)，以量化是否有显著不同的影响，YRB用水或分配。
-% Then we repeatedly compared between two SES structures (since 1987 and 1998, respectively) to quantify if there were significantly different impacts on water uses or allocation (\textbf{methods}).
-% % 我们的结果表明，1987年的结构变化刺激各省使用了远超模型预测的没有政策影响下的用水量，其增量超出安慰剂对照组xx\%，但对水资源的分配的均匀程度没有改变（see fig）。
-Our results suggest that the institutional shift in 1987 stimulated the provinces to use far more water than would have been used without policy effects (Figure~\ref{fig:main_results}A), with an observed increase of $164\%$ over the expectation(Figure~\ref{fig:main_results}B).
-% 然而，水资源分配的均匀性并没有改变，区域间的用水量在相同规模下增加(图~\ref{fig:main_results}C)。
-However, the relative share of water use was not changed, denoting proportionally similar water use increases among the different regions (Figure~\ref{fig:main_results}C).
-% 在1998年出台的政策再次改变社会-生态结构之后，用水量显著下降，总量仅为安慰剂对照组的xx%。
-After the SES structure changed again in 1998, the trend of increasing water use appeared to be effectively suppressed (Figure~\ref{fig:main_results} D), with total observed water consumption decreasing by $260\%$ relative to expectations(Figure~\ref{fig:main_results} E).
-% 但此阶段主要是xx，xx，xx等黄河流域的用水大省受到了遏制，因此水资源在各个省之间的比例分配变得更均匀了。
-At this stage, however, the reduction in water use came mainly from the provinces with large water consumption, such as Henan and Shandong (Figure~\ref{fig:main_results} E),  so the proportion of water used by regions became more similar (Figure~\ref{fig:main_results} F).
-% 上述结果表明，1998年各省之间由黄委会统一监管后分水政策才真正达到了其遏制用水、解决断流的预期。
-In conclusion, the water allocation policy curbed water use in 1998, whereas the 1987–1998 institutional mismatch stimulated a notable increase in total water use in all related provinces.
-% 在过去的十年里，对制度变革的“冲刺”反应似乎创造了一场竞赛，每个省份都开始使用超过他们需要的水。
-Over this decade, “sprint” responses (i.e., rapid increases in resource use \cite{lueckPreemptiveHabitatDestruction2003}) to institutional change appear to have created a race in which each province began to use more water than they needed.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=12cm]{../../../figs/outputs/main_results.jpg}
-    \caption{
-        Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
-(\textbf{A} to \textbf{C}: Entering the mismatched SES structure in 1987; \textbf{D} to \textbf{E}: exiting the mismatch in 1998.
-\textbf{A} and \textbf{D}: Impact of the first institutional shift on water use trends in the YRB.
-Blue points are actual water use, and gray points are predicted use under a scenario without any institutional shift (see \textit{Methods}).
-\textbf{B} and \textbf{E}: Impact of the institutional shift on total water use.
-Dark bars indicate the difference between the actual and predicted water use in specific study periods.
-Gray bars are the expected water use, simulated by setting up placebo experiments (null models, see \textit{Methods}).
-\textbf{C} and \textbf{F}: Impact of institutional shift on water allocation equity (see \textit{Methods}).
-Red lines indicate the index calculated from actual water use data; gray lines indicate predicted water use under a scenario with unconstrained water use.
-    }
-    \label{fig:main_results}
-\end{figure}
-
-\section{Incentive distortion causes the sprint effect}
+%! Author = songshgeo
+%! Date = 2022/3/10
 Theoretically, our economic model suggests that different kinds of institutional shifts should lead to different optimal water uses (Figure~\ref{fig:economic_model}).
@@
 % These theoretical predictions, further from the phenomenon observed in the YRB, attributing ``sprint effect'' into raising marginal benefits -by pursuing indirectly generating shadow value of water use while converting fixed marginal costs to irrelevant cost for each individual province.
-
-\begin{table}[!ht]
-	\centering
-	\caption{Summary of marginal returns and marginal costs for each case }
-	%\footnotesize
-    \setlength{\tabcolsep}{1mm}{
-       \begin{tabular}{lccc}
-		\hline
-		& Case 1: Decentralized Ins. & Case 2: Mismatched Ins. & Case 3: Matched Ins. \\ \hline
-		Marginal return & $P*F'(X)$                & $P*F'(X)+V(X)^*$            & $P*F'(X)$              \\
-		Marginal cost   & $C/N$                    & $Irrelevant$              & $C$                   \\ \hline
-	\end{tabular}
-    }
-	\centering
-	\footnotesize{\leftline{$^*$Note: $V(X)$ denotes a shadow value.}}
-	\label{tab:cases}
-\end{table}
-
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=12cm]{../../../figs/outputs/economic_model.jpg}
-	\caption{
-		% \textbf{Assumption 1:} \textit{(Production)} Assuming that water is the only input of the homogenous production function F(x) of each province.
-Under diminishing marginal returns assumption, and $F(x)$ is continuous, $F'(0)=\infty$, $ F'(\infty)=0$.
-The production output is under perfect competition, with constant unit price of P.
-		% \textbf{Assumption 2:} \textit{(Cost function)} Assuming that the ecology is a unity for the whole basin, the cost of water use is equally assigned to each province under any water use.
-The unit cost of water is a constant C.
-		% \textbf{Assumption 3:} \textit{(Multi-period setting)} There are infinite periods with constant discount factor $\beta$ lying in (0,1) with no cross-period smoothing in water uses.
-		\textbf{A.} The relationship of marginal benefits and water use of province i at t = 0 for three different cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}, assuming $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, and $\beta=0.4$ as an example  (see \textit{Methods}In Case 3, water use by others is taken as a given, equal to the optimal water use for Case 2.
-The horizontal coordinate of each intersection of marginal benefits and the break-even line represents the optimal water use under each case.
-		\textbf{Panel B.} The relation between optimal water use of province i and total quota for Case 3, under time horizon of $T=5$, $T=10$, and an infinite $T$, respectively.
-The settings are the same as in \textbf{A}.
-	}
-	\label{fig:economic_model}
-\end{figure}
-
-\section{Discussion}
-% 我们展示了不匹配的分配制度是如何导致激励失真导致水资源加速耗竭的(即“冲刺效应”)。“冲刺效应”是CPR系统面临的一种特殊情况，在这种情况下，制度的不匹配为每个资源使用者创造了更强的动机(扭曲)，促使他们收回资源
-We have shown how a mismatched allocation institution can lead to an accelerated depletion of water resources (i.e., the “sprint effect”) caused by incentive distortion.
-The sprint effect is a special case faced by CPR systems, where institutional mismatches create an even stronger incentive (with distortion) for each resource user to withdraw resources
-\cite{ostromRevisitingCommonsLocal1999,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017}.
-% 过往研究指出制度常常是避免公共池塘资源系统的崩溃的关键，但“短跑效应”的出现表明在自上而下进行制度设计所形成的错配SES结构中，制度也可以成为系统加速崩溃的触发者。
-Previous studies have suggested that institutions are often the key to avoid the collapse of a CPR system, but the emergence of a sprint effect shows that an institution with structural mismatches can also be the trigger that accelerates system collapse \cite{bodinConservationSuccessFunction2014,bodinCollaborativeenvironmentalgovernance2017,wangAlignmentsocialecological2019}.
-The initial formulation of the water quota in our case studies went through a stage of “bargaining” among stakeholders (from 1982 to 1987) \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}, where each province attempted to demonstrate its development potential related to water use.
-% 在高层决策者与低层利益相关者之间存在信息不对称的用水分配中，当前用水量越大的利益相关者议价能力越大。1987年以后，对各省来说，合乎逻辑的下一步是试图证明争取更大配额的合理性，而不是立即采取资源节约型改革。在实践中，尽管受影响的省份可能没有直接鼓励过度使用资源，但由于激励扭曲，他们有更大的动机对资源提取开绿灯。因此，在争夺潜在的水资源配额时，各省往往将生态成本隐藏在经济发展背后。
-In water use allocation with information asymmetry between upper-level decision-makers and lower-level stakeholders, those with more current water use might have greater bargaining power.
-After 1987, the logical next step for provinces was to attempt to justify bargaining for larger quotas rather than immediately adopt resource-conserving transformations.
-In practice, although the affected provinces may not have directly encouraged excessive resource use, they had a greater incentive to give the green light to resource withdrawals because of incentive distortions \cite{kriegerProgressGroundWater1955, ostromGoverningCommonsEvolution1990}.
-As a result, while competing for potential water quotas, the provinces tended to hide the ecological costs behind economic development.
-
-% 毫无疑问，随着资源竞争的日趋激烈，越来越多的SES正依赖着不同形式的制度进行资源分配（如自组织和政府干预），避免“短跑效应”的出现或将成为制度设计的关键。
-There is no doubt that with increasingly fierce competition for water, more and more SESs are developing new institutions for water allocation (whether through self-organization or government intervention) \cite{anderssonVoluntaryleadershipemergence2020, wutichWaterScarcitySustainability2009}.
-% 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
-Adoption of an overall quota plays an important role in preventing overuse of CPRs \cite{tilmanLocalizedprosocialpreferences2019}.
-However, the negative effects of incentive distortion imply a trade-off between long-term SES benefits and current stability, and the proportion of available resources allocated under quota schemes matters when institutions change \cite{ladeRegimeshiftssocialecological2013}.
-According to our analysis of plausible scenario assumptions based on our general economic model, the sprint effect will be reinforced when stakeholders anticipate that technological advances will amplify the benefits of water quotas in the future (see \textit{Supplementary Material S3}).
-% 然而，如果有水权转换机制允许利益相关者之间通过交易来弥补 shadow value，当前这种错乱的动机就不会那么强。
-However, if an institution allowed stakeholders to compensate for the shadow value (i.e., potential returns sacrificed due to water constraints and water scarcity) \cite{howarthAccountingvalueecosystem2002} of future water use, incentive distortion would be less devastating (e.g., through water rights transfer).
-Policymakers can also weaken the sprint effect by increasing the frequency of quota updates, supporting the idea that a more dynamic institution that responds to changing conditions (see \textit{Supplementary Material S3}) will adapt more effectively to its social-ecological context.
-
-% 近年来黄河流域面临的分水制度调整问题也说明了动态设置配额的重要性。
-Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of dynamic quota setting (see \textit{Supplementary Material S1}) \cite{yuAdaptabilityassessmentpromotion2019}.
-Following the institutional reforms of 1998, the Yellow River has not dried up since 1999.
-However, given recent changes in the YRB, its rigid resource allocation scheme can no longer meet the new demands of economic development \cite{wangThingsCurrentSignificance2019}.
-The Chinese government has embarked on an ambitious plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}).
-Other SESs around the world face similar problems in establishing successful resource allocation institutions \cite{cummingQuantifyingSocialEcologicalScale2020, muneepeerakulStrategicbehaviorsgovernance2017, cummingAdvancingunderstandingnatural2020, leslieOperationalizingsocialecologicalsystems2015}.
-These initiatives can benefit from our analysis by actively considering and incorporating social-ecological complexity and incentive structures when developing new approaches that avoid unsustainable outcomes.
-Our research provides a cautionary tale of how institutions can act as a double-edged sword when trying to attain sustainability.
-
-\section{Methods}
-% 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程
-We estimated and analyzed the net effects of two SES structural changes of water use.
-The actual water use of the Yellow River Basin was peroxided by the sum of the water use of the target group provinces.
-To quantify water use, we used synthetic control methods to estimate possible trends of water use in the absence of institutional shifts.
-In addition, as a robustness test, we conducted a matched placebo test (creating a “null model”) to exclude the effects of other factors that were contemporaneous with the institutional shifts.
-Finally, we created an economic model based on marginal revenue to provide a theoretical explanation for the observed “sprint effect” phenomenon.
-A brief technical overview is given in \textit{Supplementary Material S2}.
-
-\subsection{Dataset and variables}
-% 我们使用中国1978年至2012年各省的年度用水量数据集，这个公开的数据集由全国水资源利用调查得到，详细可查看。
-We used China’s provincial annual water consumption dataset from 1978 to 2012.
-This publicly available dataset was obtained from the National Water Resources Utilization Survey; details are accessible from Zhou (2020)
-\cite{zhouDecelerationChinahuman2020}.
-A total of 10 provinces or regions have been directly affected by the water allocation institutional shifts in the YRB, accounting for $8.6\%$ of the total population of China (in 1990).
-Eight provinces have been particularly affected because of their greater dependence on the water resources from the Yellow River (see \textit{Supplementary Material S2}).
-Therefore, we divided the dataset into a “target group” and a “control group”, treating provinces that were greatly affected as the target group $(n=8)$ and provinces that were not affected by the institutional shifts as the potential control group $(n=20)$.
-
-We focused on two features of water use in the YRB: total water use and diversification of water allocation.
-The actual water uses are given by the dataset, but when the synthetic control method is used to predict the water use of the control group, other independent influences need to be considered.
-Thus, we used economic features that are highly related to water use to extrapolate demand (e.g., agriculture, industry, service industry, and domestics, see \textit{Supplementary Material S2, Table 1} To measure resource allocation diversification between the upper, middle, and lower reaches, we used “entropy” as a simple index,
-
-$$ Index_{entropy} = \sum_i{p_i *log(p_i)} $$
-
-% 式子中的p是每个使用的水占流域总用水的比例
-Where $p_i$ is the proportion of water uses for region $i$ to the total water uses in the basin.
-A larger index value indicates the proportion of water resources actually used is closer to the average among the upper, middle, and lower reaches.
-
-\subsection{Synthetic Control}
-Synthetic control is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadieSyntheticControlMethods2010}.
-In this study, we used a comparative event approach and compared actual post-institutional shift induced water use changes with an appropriate counterfactual of what the water use change would have been.
-The counterfactual was built as the optimally weighted average of provinces not exposed to the institutional shifts.
-The synthetic control method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity \cite{billmeierAssessingEconomicLiberalization2013, smithresourcecurseexorcised2015}.
-In practice, each of the units (i.e., provinces) in the treated group were affected by institutional shifts in 1987 and 1998, each of which was taken as the “shifted” point $t_0$ and the two steady institutions as $t$ for analyzing in each shift.
-The synthetic control method generates the control unit by assigning a weight matrix $W$ to units of the potential control group, so that the treated unit and its control unit are similar in each variable before $t_0$, i.e.,
-
-$$\min(V_{i}^{t<t_0} - W_i * F_{control}^{t<t_0})$$
-
-where $V_i$ is a vector that indicates all features of a unit $i$ of the treated group, and $F_{control}$ is a matrix that consists of all features and units of the potential control group.
-$W_i$ is the weight matrix for target unit $i$.
-We minimized the root mean square error (RMSE) by using the Synth package in R \cite{abadieSynthPackageSynthetic2011, abadieComparativePoliticsSynthetic2015}.
-All codes are accessible in the repository.
-
-% 这样一来，基于降维的思想，我们构建出了一系列特征上与实验组最为接近的可比对照。
-In accordance with the idea of dimensionality reduction, we constructed a series of comparable control units that were most similar in characteristics to the treated units.
-Because the units of the control group were not affected by the institutional shifts, after giving the same weight to the total water use of the control group $M_i * WU_{control}$, the result $W_i*WU_{control}$ could be considered a reasonable estimation of the untreated situation.
-The net effect of the water allocation institutional shift was then estimated by calculating the difference of water uses after the institutional shift between the treated group and the control group, compared with the water use difference before the shift.
-
-\subsection{Placebo Test}
-% 作为一种稳健性检验，安慰剂测试的必要性体现在两个原因上。
-For robustness, we conducted a placebo test because the synthetic control method neglects the influences of overall changes in factors in the same year by simply dividing time periods according to institutional shifts.
-Three steps were required to apply the placebo test:
-% (1) 对目标组中的每个省份$i$，计算所有潜在控制组与它之间特征向量的欧氏距离
-(1) For each province in the target group, we calculated the Euclidean distance of vectors between all provinces in the potential control group.
-% (2) 将距离由小到大排序后，选取特征向量最相似的三个省份，所有特征的均值作为 $i$ 的替代
-(2) After ranking the distances, the three provinces with the most similar economic context were used to generate an average paired treatment target unit.
-% (3) 对这个配对目标同样实施控制合成法（潜在控制组排除构成它的三个省）
-(3) We performed the same synthetic control analysis for this paired target (i.e., the potential control group excluding the three provinces in step 2).
-% 经过上述步骤，我们在理论上构建了一个相似的“区域”并实施了同样的控制合成实验。
-In this way, we theoretically constructed a pseudo-treated unit and performed the same synthetic control treatments.
-Because these placebo tests were directed at units unaffected by the institutional shifts, the results can be regarded as a reasonable baseline expectation or null model from which to assess the changes caused by other factors.
-
-\subsection{Economic model}
-In order to understand the mechanisms underlying the empirical results, we developed a dynamic economic model to analyze how institutional change could have led to the sprint effect in water use.
-Specifically, we modeled individual provincial decision-making in water resources before quota execution.
-The analysis result implied that the underlying driver of CPR overuse was incentive distortion.
-
-In developing the model, we highlighted the main features of the YRB, as well as the water use institutions of 1987 and 1998. We proposed three intuitive and general assumptions.
-
-\begin{ass}
-    % (生产)为了简化，由于不可替代性，水是每个省的同质生产函数10的唯一投入。$F(x)$是连续的，满足Inada条件，即$F'(x)>0, F''(x)<0$(边际收益递减假设)，$F'(0)=\infty$,$ F'(\infty)=0$。产品产量处于完全竞争状态，单位价格为15。
-    (Water-dependent production) For simplicity, water is assumed to be the only input of the homogenous production function $F(x)$ of each province because of its irreplaceability.
-$F(x)$ is continuous and satisfies the Inada Conditions, i.e., $F'(x)>0, F''(x)<0$ (the diminishing marginal returns assumption), $F'(0)=\infty$,$ F'(\infty)=0$.
-The production output is under perfect competition, with a constant unit price of $P$.
-\end{ass}
-\begin{ass}
-    (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in N provinces, the cost of water use is equally assigned to each province under any water use.
-The unit cost of water is a constant $C$.
-\end{ass}
-\begin{ass}
-    (Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water uses.
-\end{ass}
-
-Under the above assumptions, we can demonstrate three cases consisting of local governments in YRB to simulate their water use decision-making and water use patterns.
-
-\begin{case} Decentralized institution:
-    This case corresponds to a situation without any high-level water allocation institution (i.e., before 1987, see Figure~\ref{fig:structure} B).
-
-    When each province independently decides on its water use, the optimal water use $\hat x_i^*$ in province $i$ satisfies:
-    $$F'(x)=\frac{C}{P \cdot N}$$
-
-    When the decisions in different periods are independent, for $t=0,1,2 \ldots$, then:
-    $$\hat x_{it}^*=\hat x_i^*$$
-
-\end{case}
-
-\begin{case} Mismatched institution
-    This case corresponds to a mismatched institution (i.e., $1987\sim1998$, see Figure~\ref{fig:structure} C).
-
-    The water quota is determined at $t=0$ and imposed in $t=1,2,\ldots$ The total quota is a constant denoted as $Q$, and the quota for province $i$ is determined in a proportional form:
-    $$Q_i=Q \cdot \frac{x_i}{x_i + \begin{matrix} \sum x_{-i} \end{matrix}}$$
-
-    Under a scenario with decentralized decision-making with a water quota institution, given other provinces’ water use decisions remain unchanged, the optimal water use $\widetilde x_{i0}^*$ of province $i$ at $t=0$ satisfies:
-
-    $F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot f(Q \cdot \frac{x_{i,0}}{\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix})^2}$.
-
-    When future water use is constrained by a water quota, the dynamic optimization problem of province $i$ is shown as follows:
-
-    $max  \quad P \cdot F(x_{i,0})-\frac{C \cdot \begin{matrix} \sum x_{i,0} + x_{-i,0} \end{matrix}}{N}+\beta P \cdot F(x_{i,1})+\beta^2 P \cdot F(x_{i,2})+...$
-
-    $=P \cdot F(x_{i,0})-C \cdot \frac{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}{N}+\frac{\beta}{1-\beta} P \cdot F(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}})$
-
-    First-order condition: $P \cdot F'(x_{i,0})-\frac{C}{N}+\frac{\beta}{1-\beta}[P \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0}+\begin{matrix} \sum  x_{-i,0} \end{matrix})^2}]=0$
-
-    where $f(\cdot)$ is the differential function of $F(\cdot)$.
-
-    The optimal water use in province i at t=0 $\widetilde x_{i,0}^*$ satisfies $P \cdot F'(x_{i,0})=\frac{C}{N}-\frac{\beta}{1-\beta} \cdot P \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$, i.e., $F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$.
-
-\end{case}
-
-\begin{case} Matched institution
-
-    This case corresponds to the institution under which the YRCC centrally managed water allocation between provinces (i.e., $1998\sim2008$, see Figure~\ref{fig:structure} D).
-
-    When the $N$ provinces decide on water uses as unified whole (e.g., the central government completely decides and controls on the water use in each province), the optimal water use $x_i^*$ of province $i$ satisfies:
-
-    $$F'(x)=\frac{C}{P}$$
-
-\end{case}
-
-We propose Proposition 1 and Proposition 2:
-
-\textbf{Proposition 1}: Compared with the decentralized institution, a matched institution with unified management decreases total water use.
-
-Because $F’$ is monotonically decreasing, based on a comparison of costs and benefits for stakeholders (provinces) in the three cases,
-
-$$\widetilde x_i^*>\hat x_i^*>x_i^*$$
-
-The result of $\hat x_i^*>x_i^*$ indicates that individual rationality would deviate from collective rationality when property rights are unclear \cite{hardinTragedyCommons2009}, because of the common-pool characteristics of water
-\cite{castilla-rhoGroundwaterCommonPool2020,ostromGeneralFrameworkAnalyzing2009}.
-
-The difference of $\widetilde x_i^*$ and $\hat x_i^*$ stems from two parts: the marginal returns effect and the marginal costs effect.
-First, the “shadow value” provides additional marginal returns of water use in $t=0$, wwhich increases the incentives of water overuse by encouraging bargaining for a larger quota.
-Second, the future cost of water use would be degraded from $\frac{P}{N}$ to an irrelevant cost.
-
-The optimal water use under the three cases implies that mismatched institutions cause incentive distortions and lead to resource overuse.
-
-\textbf{Proposition 2}: The quota determination of the mismatched institution increases the incentives of current water use.
-
-The intuition for this proposition is straight-forward in that all provinces would use up their allocated quota under a relatively small $Q$.
-As $Q$ increases, the quota would provide higher future benefits for a pre-emptive water use strategy.
-Since the provincial water use decisions are exactly symmetric, total water use would increase when each province has higher incentives for current water use.
-This situation corresponds to a “sprint” effect, where the total water use dramatically increases in the “sprint” period.
-
-Extensions of the model are shown in \textit{Supplementary Material S3}.
-
-\section{Info.}
-Funding was provided by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007).
-
-[Competing Interests] The authors declare that they have no competing interests.
-
-[Correspondence] Correspondence and requests for materials should be addressed to Shuai Wang.~(email: shuaiwang@bnu.edu.cn).
-
-[Author contributions]Shuai Wang and Bojie Fu designed this research, Shuang Song performed the research and analyzed data, and Huiyu Wen designed the economic model.
-Shuang Song and Huiyu Wen wrote the paper, and Graeme S.
-Cumming revised the manuscript and offered important advice.
-
-[Code availability] All codes and datasets used in this research are accessible at https://github.com/SongshGeo/sochyd-transboundary-HESS.
-They will be made open source after this project is completed.
-
-%% Put the bibliography here, most people will use BiBTeX in
-%% which case the environment below should be replaced with
-%% the \bibliography{} command.
-\bibliography{WAInstitution_YRB_2021}
-
-%% Here is the endmatter stuff: Supplementary Info, etc.
-%% Use \item's to separate, default label is "Acknowledgements"
-
-\end{document}

### 2022-03-10 docs/papers/elements/results.tex
docs(paper): initialize paper in LaTeX, prepared to refactor it

--- 2022-03-04 docs/papers/tex/main.tex
@@
-%% Template for a preprint Letter or Article for submission
-%% to the journal Nature.
-%% Written by Peter Czoschke, 26 February 2004
-%%
-\documentclass{article}
-\usepackage{hyperref}
-\usepackage{graphicx}
-\usepackage{setspace}
-\usepackage[a4paper, total={7in, 10in}]{geometry}
+%! Author = songshgeo
+%! Date = 2022/3/10
 
-\setstretch{1.523}
-
-\newtheorem{ass}{Assumption}
-\newtheorem{case}{Case}
-%% make sure you have the nature.cls and naturemag.bst files where
-%% LaTeX can find them
-
-\bibliographystyle{naturemag}
-
-%\usepackage{biblatex}
-%% make sure you have the nature.cls and naturemag.bst files where
-%% LaTeX can find them
-
-\title{Importance of social-ecological fit for water management in large river basins: An analysis of institutional shifts in the Yellow River Basin}
-
-%% Notice placement of commas and superscripts and use of &
-%% in the author list
-
-\author{Shuang Song$^{1,2}$, Huiyu Wen$^3$, *Shuai Wang$^{1,2}$, Graeme S. Cumming$^{4}$ \& Bojie Fu$^{1, 2}$}
-
-\begin{document}
-
-\maketitle
-\input{../../drafts/authors.md}
-
-\begin{abstract}
-    \input{../../drafts/abstract.md}
-\end{abstract}
-
-% Then the body of the main text appears after the intro paragraph.
-% Figure environments can be left in place in the document.
-% \verb|\includegraphics| commands are ignored since Nature wants
-% the figures sent as separate files and the captions are
-% automatically moved to the end of the document (they are printed
-% out with the \verb|\end{document}| command. However, tables must
-% be manually moved to the end of the document, after the addendum.
-% 表需要手动移到文末
-% water use; water management; social-ecological system; common pool resources; institutional analysis; collaborative governance
-
-\section{Introduction}
-Emerging competition for water is an urgent problem in water governance, with widespread water scarcity and overuse resulting in huge impacts on economies, societies, and ecosystems \cite{gleickPeakwaterlimits2010,dolanEvaluatingeconomicimpact2021,siwiCompetitionWaterGetting,ziolkowskaCompetitionWaterResources2016,distefanoArewedeep2017}.
-Water is the key exclusive and competitive resource that couples socioeconomic and ecological systems (known as common-pool resources, CPRs) \cite{wutichWaterScarcitySustainability2009,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017,castilla-rhoGroundwaterCommonPool2020}.
-Conflicts of interest often occur in allocation and competitions of water resources, with water governance policies often leading to long-term changes in human–water relationships and the redistribution of benefits \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013,chingManagingsocioecologyvery2015}.
-Although governments in many of the world’s large river basins have tried to resolve competition for water through the deliberate design of new institutions, general principles underlying the successes and failures of these initiatives are poorly documented and understood.
-
-Institutions (such as policies, laws, and norms) can influence regional sustainability by changing social-ecological system (SES) structure and dynamics \cite{youngInstitutionsenvironmentalchange2008,cummingAdvancingunderstandingnatural2020,lieninstitutionalgrammartool2020}.
-These include inter-relationships and interactions between social actors, between ecological units, or between social and ecological system elements \cite{bodinCollaborativeenvironmentalgovernance2017,barnesSocialecologicalalignmentecological2019}.
-Effective (“matched”) institutions operate at appropriate spatial, temporal, and functional scales to manage and balance these different relationships and interactions \cite{heWateringEnvironmentalRegulation2020,kellenbergempiricalinvestigationpollution2009}.
-From the perspective of SES outcomes, matched institutions support (but do not guarantee) sustainability \cite{epsteinInstitutionalfitsustainability2015,wangAlignmentsocialecological2019}.
-
-Some kinds of institutions have been shown to support desirable outcomes in water-centered SESs (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wangAlignmentsocialecological2019} and in collaborative water governance systems in Europe \cite{greenEUWaterGovernance2013}).
-At the same time, undesired and unsustainable outcomes (e.g., failures in environmental regulation of highly polluting industries or the development of “tragedy of the commons” situations when pursuing more water resources), with considerable ecological degradation, have attracted much attention \cite{saylesSocialecologicalnetworkanalysis2019,caiPollutingthyneighbor2016,castilla-rhoSocialtippingpoints2017}.
-Despite widespread recognition of the rising importance of integrated water resource management in solving water competition in the world’s large river basins, relatively few studies have explored the mechanisms by which SESs respond to new institutions \cite{agrawalSustainableGovernanceCommonPool2003,pershaSocialEcologicalSynergy2011,agrawalCommonPropertyInstitutions2001}.
-Two particular weaknesses in existing knowledge include understanding (1) the causal links between SES structures and outcomes; and (2) details of the underlying processes, especially the coordination of the incentives of different participants, that result from an institutional lack of fit.
-These weaknesses limit our understanding of institutional design, and they may reduce the speed and transfer of new knowledge and experience related to improving the sustainability of comprehensive water resources management.
-
-In order to disentangle the relationship between SES structure and outcomes, we analyzed a case study to show how an institutional shift led to a structural mismatch that triggered unsustainable water use and unintended ecological deterioration.
-Two rapid shifts in institutional structure that occurred in 1987 and 1998 (see Supplementary Material S1) provide unique settings to exploit quasi-natural experiments of a large river basin, the Yellow River Basin (YRB) in China \cite{xiaDevelopmentWaterAllocation2012}.
-After a period of severe drying up, an institutional shift implemented in 1987 represented the beginning of attempts to control water use in the YRB through the use of quotas, with the goals of alleviating conflicts between supply and demand and achieving sustainable development.
-
-Our results show that this initiative actually accelerated water withdrawals, resulting in an unintended “sprint effect”, where institutional mismatches created an even stronger incentive for each resource user to withdraw resources until the next major institutional shift in 1998.
-Our analysis contributes to a deeper understanding of the mechanisms underlying the relationships among institutions, SES structures, and outcomes.
-By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings are consistent with the urgent calls for a more dynamic design for water use allocation to achieve sustainability.
-
-\section{Institutions and SES structures}
-% 机构可以塑造社会经济体系的结构，对其进行抽象是机械地理解结构和结果之间联系的第一步。
-Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{fig:framework}A).
-% 例如，机构可以创建一种被确定为与良好的社会经济效益相关联的水平匹配结构，如果它鼓励管理相连生态成分的不同行动者之间的协作(图1B)。
-For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{fig:framework}B), leading to sustainable outcomes.
-% 例如，机构可以创建一个结构，鼓励不同行为者之间的合作，管理相连的生态成分
-Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{fig:framework}C and D).
-% 在实践中，一个大型、复杂的河流流域的制度变化将创造或摧毁数百种不同的联系。这些局部变化的更广泛影响可以从系统的整体行为中看到。
-In practice, institutional changes in a large, complex river basin will create or destroy hundreds of different connections.
-The broader impacts of these local changes can be seen in the overall behavior of the system.
-% 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
-We thus explored the causal linkages between the SES structures and sustainability (outcomes) in quasi-natural experiments of the YRB, which provides an informative case study for two main reasons.
-% 首先，长江流域管理的急剧结构变化使我们能够定量估计高层制度设计变化对用水的净影响。决定水分配的制度包括自下而上的协议或社会规范，以及自上而下的配额或法规，它们对社会经济结构有不同的影响;自上而下的监管可能会立即引发制度转变和SES的剧烈结构性变化。通过与由自下而上的制度转变引起的更渐进的变化相比，探索自上而下变化的影响，在对社会经济地位的定量分析中，极大地减少了来自不可观测因素的潜在干扰，提高了社会经济地位结构和结果之间因果关系的清晰度。
-First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use.
-Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013}; top-down regulations can trigger immediate institutional shifts and sharp SES structural changes \cite{speedBasinwaterallocation2013,rolandUnderstandinginstitutionalchange2004}.
-In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and improves the clarity of the causal link between SES structure and outcome.
-% 其次，通过比较长江流域两次制度变迁所分裂的三种不同制度结构的净效应，我们也可以更深入地理解“盆地固定效应”下结构格局的影响。尽管流域内的社会经济单位从世界各地的大型河流流域和许多地区的水资源中受益，但很少有流域多次经历过如此激进的社会经济结构变化。
-Second, by comparing the net effects of three different institutional structures split by two institutional shifts in the YRB, we can also reach a stronger understanding of the influence of structural alignments under a fixed basin.
-Although socioeconomic units within a basin benefit from water resources in large river basins all over the world and many locations have shown increased levels of regulation, few basins have experienced such radical SES structural changes several times (see \textit{Supplementary Material} S1).
-Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in SES institutional structure.
-% 因此，黄河流域的“流域固定效应”为SES结构的自我比较提供了宝贵的机会。
-% Thus, the YRB provides valuable settings for understanding the direct impacts of changes in SES institutional structure.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=8.3cm]{../../../figs/diagrams/framework.jpg}
-	\caption{
-		Framework for understanding linkages between SES structures and outcomes.
-		\textbf{a.} The general framework for analyzing social-ecological systems (SESs) (adapted from Ostrom \cite{ostromGeneralFrameworkAnalyzing2009}).
-Institutions embedded in SESs may reshape structures by changing the interactions between core subsystems, resulting in different outcomes.
-        Three typical types of abstracted SES structures are shown as \textbf{b.}, \textbf{c.} and \textbf{d.} (adapted from Bodin, 2017)\cite{bodinCollaborativeenvironmentalgovernance2017}.
-Red circles indicate social actors, and green ones indicate ecological components.
-Connection (ties between two ecological components), collaboration (ties between two social actors), or management (ties between a social actor and an ecological component) exist when two units are linked by gray lines.
-The gray dashed lines show aligned SES structures that are more likely to result in a desirable outcome according to empirical evidence.
-	}
-    \label{fig:framework}
-\end{figure}
-
-\section{Context of institutional shifts}
-% 黄河是世界第五长河，它的流域也是中国文明的摇篮。
-The Yellow River, whose basin is the cradle of Chinese civilization, is the fifth-longest river in the world.
-It supports $9.7\%$ of China’s irrigation, with only $2.6\%$ of its total water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021).
-% 然而，经过沿江各省多年的免费取水(图~\ref{fig:structure} A和B)，到20世纪80年代，黄河地表水耗水量接近径流量的10倍，并不断上升
-However, after years of free access to water by provinces along the river (Figure~\ref{fig:structure} A and B), surface water consumption of the Yellow River was close to $80\%$ of its runoff by the 1980s and rising
-\cite{wangYellowRiverwater2019,songSedimenttransportincreasing2020}.
-% 自1972年以来，黄河径流量的减少破坏了黄河的生态，制约了黄河的经济发展
-Reductions in runoff after 1972 damaged the ecology of the YRB and restricted its economic development \cite{wangYellowRiverwater2019}.
-% 因此，在中国典型的自上而下的制度结构下(附录图S1-B)，黄河流域不同层次提出了相对完整的水资源分配规定(图1a)。
-Therefore, through typical top-down institutional structures in China (see \textit{Supplementary Material S1}), relatively integrated water allocation regulations were successively proposed across different levels in the YRB.
-% 这些机构包括国家政府、流域管理机构、省、市，甚至地区(见图1 B-D)。
-These include the national government, the basin management agency, provinces, cities, and even districts.
-% 这些在不同制度发展阶段相继出台的政策，引发了长江经济带经济发展结构的突变，并产生了不同的结果(见附录A和图S1-C)。
-These policies at different stages of institutional development triggered abrupt changes in the SES structure of the YRB with different outcomes.
-
-% 0世纪70年代以来，中国政府向黄河水利委员会下达指令，要求黄河水利委员会设计配水方案，同时要求黄河沿岸各省进行水资源规划
-In 1982, the Chinese government issued instructions to the Yellow River Water Conservancy Commission (YRCC), the basin agency of the YRB, requiring it to design a water allocation scheme and at the same time requiring the provinces along the Yellow River to carry out water resources planning (see \textit{Supplementary Material S1})
-\cite{wangReviewImplementationYellow2019}.
-% 经过多方讨论与权衡，中国政府于1987年为相关省份分配了水资源配额，要求沿黄各省(区)贯彻执行
-The Chinese government started to assign water quotas to the relevant provinces in 1987, but did not create a unit to coordinate water division between them (Figure~\ref{fig:structure} \textbf{A} and \textbf{C}).
-% 这一时期长江水利枢纽的监督任务是编制长江水利枢纽用水量统计公报，并与定额进行对比分析。
-The mandate of the YRCC during this period was only to report on and analyze water consumption in the YRB
-\cite{wangReviewImplementationYellow2019}.
-% 随着断流的进一步恶化，1998年中国政府推进了相关政策的改革，要求所有省份在取用水资源时必须向黄委会申请许可，黄委会得以直接对各省的用水实施监管。
-However, since reductions in river flow indicated an unintended SES outcome (Figure~\ref{fig:structure} E), the Chinese government pushed for a policy reform in 1998 that required all provinces to apply for licenses to use water from the YRCC, allowing the council to directly regulate their water use (see \textit{Supplementary Material S1} and Figure~\ref{fig:structure} A and D).
-% 由于革新后的政策成功遏制了断流，2008年该分配政策被进一步细化，相关各省都进一步设置了更细致的分配方案，并最终形成了黄河流域如今的水资源分配格局。
-The 1998 policy succeeded in curbing water extraction (Figure~\ref{fig:structure} E), and it was further refined in 2008.
-The relevant provinces created a more detailed allocation plan and finally formed the present water allocation institutions of the YRB (see \textit{Supplementary Material S1}).
-% 因此，在1975-2008长达33年的时间里，从没有分水政策到以两种不同模式监管下的分水政策，黄河流域实际上先后存在着三种不同的社会-生态结构（Fig 1）。
-Therefore, in our study period (from 1975 to 2008), the system shifted between three different SES structures (Figure~\ref{fig:structure} \textbf{B} to \textbf{D}).
-% 在它们之中，与预期相反地，1987年至1998年的流域SES结构下黄河的生态急剧恶化，表明了制度的失配。
-The sharp and unintended decline in the ecological condition of the Yellow River from 1987 to 1998 indicates an institutional mismatch during this period (Figure~\ref{fig:structure} the shadowed time periods).
-
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=12cm]{../../../figs/diagrams/structure.jpg}
-	\caption{
-		% 黄河流域的制度变迁与经济社会结构差异。
-		Institutional shifts and related SES structures in the Yellow River Basin (YRB). See \textit{Supplementary Material S1} for detailed introduction for the institutions.
-		% 国家政府在1987年和1998年先后两次出台了改变流域制度的政策，而黄河水利委员会、利益攸关的各省在不同制度时期具备的功能是不同的。
-		\textbf{A.} The national government changed YRB management policies and institutions in 1987 and 1998.
-As a result, the Yellow River Conservancy Commission (YRCC) and the provinces acted differently in different periods.
-Three different SES structures existed successively in the YRB.
-		% 没有任何政策限制，各利益相关者此时期可以从单向但联通的河流生态单元内自由取水
-		\textbf{B.} 1975–1987: Without any constraints, water resources were freely accessible to each stakeholder (the provinces in this case, denoted by red circles) from a one-way but connected ecological unit (the Yellow River, denoted by the blue rectangle).
-		% 在政策1之后，每个使用者都被分配了能够开采河流地表水资源的配额，而黄委会的工作是对配额的使用进行统计与汇报。
-		\textbf{C.} 1987–1998: After the implementation of policy 1 in 1987, each user was assigned a quota to withdraw surface water resources, and the YRCC (yellow triangle) was tasked with reporting on water quota use.
-		% 第二个政策之后，利益相关者取水需要向黄委会申请，黄委会则根据用水配额来批发许可。因此此时黄委会与利益相关者之间产生了直接的双向联系，监督他们对资源配额的取用。
-		\textbf{D.} 1998–2008: After the implementation of policy 2, stakeholders had to apply for water resources from the YRCC, which then licensed water use according to the quota.
-Under this institution, the YRCC had direct two-way connections between provinces and ecological components.
-		% 由于政策1与政策2都是为了解决黄河断流的生态问题而提出的，因此在结果与政策预期严重相反的第二时期（灰色阴影时段），是制度导致了错配的社会-生态系统结构。
-		\textbf{E.} A timeline of the Yellow River and drying conditions.
-The size of the circles indicates the length of section that dried up (km), and the y-axis indicates the length of the drying period.
-Both policy 1 and policy 2 were put forward to solve this ecological crisis.
-The mismatch created by policy 1 is clearly correlated with the unintended outcomes shown in the second (gray-shaded) period.
-	}
-	\label{fig:structure}
-\end{figure}
-
-\section{Sprint effect induced by an institutional mismatch}
 % % 这里，我们使用合成控制模型创建了假设不存在政策变化的虚拟对照组（see \textit{Methods}-1），同时用K-近临算法找到经济状况与黄河流域各省“类似”的安慰剂对照（see \textit{Methods}-2），反复对比表明两次社会-生态系统结构变迁对流域的水资源利用及分配产生了明显不同的影响。
@@
 Over this decade, “sprint” responses (i.e., rapid increases in resource use \cite{lueckPreemptiveHabitatDestruction2003}) to institutional change appear to have created a race in which each province began to use more water than they needed.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=12cm]{../../../figs/outputs/main_results.jpg}
-    \caption{
-        Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
-(\textbf{A} to \textbf{C}: Entering the mismatched SES structure in 1987; \textbf{D} to \textbf{E}: exiting the mismatch in 1998.
-\textbf{A} and \textbf{D}: Impact of the first institutional shift on water use trends in the YRB.
-Blue points are actual water use, and gray points are predicted use under a scenario without any institutional shift (see \textit{Methods}).
-\textbf{B} and \textbf{E}: Impact of the institutional shift on total water use.
-Dark bars indicate the difference between the actual and predicted water use in specific study periods.
-Gray bars are the expected water use, simulated by setting up placebo experiments (null models, see \textit{Methods}).
-\textbf{C} and \textbf{F}: Impact of institutional shift on water allocation equity (see \textit{Methods}).
-Red lines indicate the index calculated from actual water use data; gray lines indicate predicted water use under a scenario with unconstrained water use.
-    }
-    \label{fig:main_results}
-\end{figure}
-
-\section{Incentive distortion causes the sprint effect}
-Theoretically, our economic model suggests that different kinds of institutional shifts should lead to different optimal water uses (Figure~\ref{fig:economic_model}).
-Furthermore, our analysis indicated that the cause of the sprint effect in this case was incentive distortion.
-Compared with the decentralized water allocation institution in place before 1987, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs (see Table~\ref{tab:cases} the \textbf{methods} for a detailed mathematical formula).
-% 在不匹配条件下，边际成本减去边际收益增加，导致用水量增加，xx的差异反映了水配额模拟的非预期冲刺效应。
-The unintended sprint effect (from 1987 to 1998) was caused by both declining marginal costs (a shift from a fixed unit cost to an irrelevant cost) and increasing marginal returns due to future water use benefits (see Table~\ref{tab:cases} the \textbf{methods} for a detailed mathematical formula).
-% 因此，这种制度引发了一种与可持续用水意图背道而驰的激励扭曲。
-The institution thus triggered an incentive distortion that ran counter to the intention of sustainable water use.
-Further, the strength of the sprint effect was positively correlated with the size and time horizon of the water use quota (Figure~\ref{fig:economic_model} \textbf{Panel B}).
-% 这些理论上的预测正如我们在黄河流域所观察到的一样，不匹配的配额制度导致了短跑效应的出现，而中心化的制度结构结束了这一非预期的现象。
-% These theoretical predictions, in line with phenomenon observed in the YRB, indicating the mismatched institution leads to incentive distortion of provinces for pre-empting resources by `sprinting', according to their expectations for the future.
-% 这些理论预测进一步从YRB观察到的现象出发，表明不匹配的配额制度通过提高边际效益来刺激用水量，而边际效益与放宽限制带来的未来潜在用水量的影子值有关。
-% These theoretical predictions, further from the phenomenon observed in the YRB, indicating the mismatched institution with quota stimulates water use by raising marginal benefits, which is related to the shadow value of potential future water use from relaxing the constraints.
-% 温博推荐的版本：
-% These theoretical predictions, further from the phenomenon observed in the YRB, attributing ``sprint effect'' into raising marginal benefits -by pursuing indirectly generating shadow value of water use while converting fixed marginal costs to irrelevant cost for each individual province.
-
-\begin{table}[!ht]
-	\centering
-	\caption{Summary of marginal returns and marginal costs for each case }
-	%\footnotesize
-    \setlength{\tabcolsep}{1mm}{
-       \begin{tabular}{lccc}
-		\hline
-		& Case 1: Decentralized Ins. & Case 2: Mismatched Ins. & Case 3: Matched Ins. \\ \hline
-		Marginal return & $P*F'(X)$                & $P*F'(X)+V(X)^*$            & $P*F'(X)$              \\
-		Marginal cost   & $C/N$                    & $Irrelevant$              & $C$                   \\ \hline
-	\end{tabular}
-    }
-	\centering
-	\footnotesize{\leftline{$^*$Note: $V(X)$ denotes a shadow value.}}
-	\label{tab:cases}
-\end{table}
-
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=12cm]{../../../figs/outputs/economic_model.jpg}
-	\caption{
-		% \textbf{Assumption 1:} \textit{(Production)} Assuming that water is the only input of the homogenous production function F(x) of each province.
-Under diminishing marginal returns assumption, and $F(x)$ is continuous, $F'(0)=\infty$, $ F'(\infty)=0$.
-The production output is under perfect competition, with constant unit price of P.
-		% \textbf{Assumption 2:} \textit{(Cost function)} Assuming that the ecology is a unity for the whole basin, the cost of water use is equally assigned to each province under any water use.
-The unit cost of water is a constant C.
-		% \textbf{Assumption 3:} \textit{(Multi-period setting)} There are infinite periods with constant discount factor $\beta$ lying in (0,1) with no cross-period smoothing in water uses.
-		\textbf{A.} The relationship of marginal benefits and water use of province i at t = 0 for three different cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}, assuming $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, and $\beta=0.4$ as an example  (see \textit{Methods}In Case 3, water use by others is taken as a given, equal to the optimal water use for Case 2.
-The horizontal coordinate of each intersection of marginal benefits and the break-even line represents the optimal water use under each case.
-		\textbf{Panel B.} The relation between optimal water use of province i and total quota for Case 3, under time horizon of $T=5$, $T=10$, and an infinite $T$, respectively.
-The settings are the same as in \textbf{A}.
-	}
-	\label{fig:economic_model}
-\end{figure}
-
-\section{Discussion}
-% 我们展示了不匹配的分配制度是如何导致激励失真导致水资源加速耗竭的(即“冲刺效应”)。“冲刺效应”是CPR系统面临的一种特殊情况，在这种情况下，制度的不匹配为每个资源使用者创造了更强的动机(扭曲)，促使他们收回资源
-We have shown how a mismatched allocation institution can lead to an accelerated depletion of water resources (i.e., the “sprint effect”) caused by incentive distortion.
-The sprint effect is a special case faced by CPR systems, where institutional mismatches create an even stronger incentive (with distortion) for each resource user to withdraw resources
-\cite{ostromRevisitingCommonsLocal1999,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017}.
-% 过往研究指出制度常常是避免公共池塘资源系统的崩溃的关键，但“短跑效应”的出现表明在自上而下进行制度设计所形成的错配SES结构中，制度也可以成为系统加速崩溃的触发者。
-Previous studies have suggested that institutions are often the key to avoid the collapse of a CPR system, but the emergence of a sprint effect shows that an institution with structural mismatches can also be the trigger that accelerates system collapse \cite{bodinConservationSuccessFunction2014,bodinCollaborativeenvironmentalgovernance2017,wangAlignmentsocialecological2019}.
-The initial formulation of the water quota in our case studies went through a stage of “bargaining” among stakeholders (from 1982 to 1987) \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}, where each province attempted to demonstrate its development potential related to water use.
-% 在高层决策者与低层利益相关者之间存在信息不对称的用水分配中，当前用水量越大的利益相关者议价能力越大。1987年以后，对各省来说，合乎逻辑的下一步是试图证明争取更大配额的合理性，而不是立即采取资源节约型改革。在实践中，尽管受影响的省份可能没有直接鼓励过度使用资源，但由于激励扭曲，他们有更大的动机对资源提取开绿灯。因此，在争夺潜在的水资源配额时，各省往往将生态成本隐藏在经济发展背后。
-In water use allocation with information asymmetry between upper-level decision-makers and lower-level stakeholders, those with more current water use might have greater bargaining power.
-After 1987, the logical next step for provinces was to attempt to justify bargaining for larger quotas rather than immediately adopt resource-conserving transformations.
-In practice, although the affected provinces may not have directly encouraged excessive resource use, they had a greater incentive to give the green light to resource withdrawals because of incentive distortions \cite{kriegerProgressGroundWater1955, ostromGoverningCommonsEvolution1990}.
-As a result, while competing for potential water quotas, the provinces tended to hide the ecological costs behind economic development.
-
-% 毫无疑问，随着资源竞争的日趋激烈，越来越多的SES正依赖着不同形式的制度进行资源分配（如自组织和政府干预），避免“短跑效应”的出现或将成为制度设计的关键。
-There is no doubt that with increasingly fierce competition for water, more and more SESs are developing new institutions for water allocation (whether through self-organization or government intervention) \cite{anderssonVoluntaryleadershipemergence2020, wutichWaterScarcitySustainability2009}.
-% 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
-Adoption of an overall quota plays an important role in preventing overuse of CPRs \cite{tilmanLocalizedprosocialpreferences2019}.
-However, the negative effects of incentive distortion imply a trade-off between long-term SES benefits and current stability, and the proportion of available resources allocated under quota schemes matters when institutions change \cite{ladeRegimeshiftssocialecological2013}.
-According to our analysis of plausible scenario assumptions based on our general economic model, the sprint effect will be reinforced when stakeholders anticipate that technological advances will amplify the benefits of water quotas in the future (see \textit{Supplementary Material S3}).
-% 然而，如果有水权转换机制允许利益相关者之间通过交易来弥补 shadow value，当前这种错乱的动机就不会那么强。
-However, if an institution allowed stakeholders to compensate for the shadow value (i.e., potential returns sacrificed due to water constraints and water scarcity) \cite{howarthAccountingvalueecosystem2002} of future water use, incentive distortion would be less devastating (e.g., through water rights transfer).
-Policymakers can also weaken the sprint effect by increasing the frequency of quota updates, supporting the idea that a more dynamic institution that responds to changing conditions (see \textit{Supplementary Material S3}) will adapt more effectively to its social-ecological context.
-
-% 近年来黄河流域面临的分水制度调整问题也说明了动态设置配额的重要性。
-Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of dynamic quota setting (see \textit{Supplementary Material S1}) \cite{yuAdaptabilityassessmentpromotion2019}.
-Following the institutional reforms of 1998, the Yellow River has not dried up since 1999.
-However, given recent changes in the YRB, its rigid resource allocation scheme can no longer meet the new demands of economic development \cite{wangThingsCurrentSignificance2019}.
-The Chinese government has embarked on an ambitious plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}).
-Other SESs around the world face similar problems in establishing successful resource allocation institutions \cite{cummingQuantifyingSocialEcologicalScale2020, muneepeerakulStrategicbehaviorsgovernance2017, cummingAdvancingunderstandingnatural2020, leslieOperationalizingsocialecologicalsystems2015}.
-These initiatives can benefit from our analysis by actively considering and incorporating social-ecological complexity and incentive structures when developing new approaches that avoid unsustainable outcomes.
-Our research provides a cautionary tale of how institutions can act as a double-edged sword when trying to attain sustainability.
-
-\section{Methods}
-% 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程
-We estimated and analyzed the net effects of two SES structural changes of water use.
-The actual water use of the Yellow River Basin was peroxided by the sum of the water use of the target group provinces.
-To quantify water use, we used synthetic control methods to estimate possible trends of water use in the absence of institutional shifts.
-In addition, as a robustness test, we conducted a matched placebo test (creating a “null model”) to exclude the effects of other factors that were contemporaneous with the institutional shifts.
-Finally, we created an economic model based on marginal revenue to provide a theoretical explanation for the observed “sprint effect” phenomenon.
-A brief technical overview is given in \textit{Supplementary Material S2}.
-
-\subsection{Dataset and variables}
-% 我们使用中国1978年至2012年各省的年度用水量数据集，这个公开的数据集由全国水资源利用调查得到，详细可查看。
-We used China’s provincial annual water consumption dataset from 1978 to 2012.
-This publicly available dataset was obtained from the National Water Resources Utilization Survey; details are accessible from Zhou (2020)
-\cite{zhouDecelerationChinahuman2020}.
-A total of 10 provinces or regions have been directly affected by the water allocation institutional shifts in the YRB, accounting for $8.6\%$ of the total population of China (in 1990).
-Eight provinces have been particularly affected because of their greater dependence on the water resources from the Yellow River (see \textit{Supplementary Material S2}).
-Therefore, we divided the dataset into a “target group” and a “control group”, treating provinces that were greatly affected as the target group $(n=8)$ and provinces that were not affected by the institutional shifts as the potential control group $(n=20)$.
-
-We focused on two features of water use in the YRB: total water use and diversification of water allocation.
-The actual water uses are given by the dataset, but when the synthetic control method is used to predict the water use of the control group, other independent influences need to be considered.
-Thus, we used economic features that are highly related to water use to extrapolate demand (e.g., agriculture, industry, service industry, and domestics, see \textit{Supplementary Material S2, Table 1} To measure resource allocation diversification between the upper, middle, and lower reaches, we used “entropy” as a simple index,
-
-$$ Index_{entropy} = \sum_i{p_i *log(p_i)} $$
-
-% 式子中的p是每个使用的水占流域总用水的比例
-Where $p_i$ is the proportion of water uses for region $i$ to the total water uses in the basin.
-A larger index value indicates the proportion of water resources actually used is closer to the average among the upper, middle, and lower reaches.
-
-\subsection{Synthetic Control}
-Synthetic control is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadieSyntheticControlMethods2010}.
-In this study, we used a comparative event approach and compared actual post-institutional shift induced water use changes with an appropriate counterfactual of what the water use change would have been.
-The counterfactual was built as the optimally weighted average of provinces not exposed to the institutional shifts.
-The synthetic control method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity \cite{billmeierAssessingEconomicLiberalization2013, smithresourcecurseexorcised2015}.
-In practice, each of the units (i.e., provinces) in the treated group were affected by institutional shifts in 1987 and 1998, each of which was taken as the “shifted” point $t_0$ and the two steady institutions as $t$ for analyzing in each shift.
-The synthetic control method generates the control unit by assigning a weight matrix $W$ to units of the potential control group, so that the treated unit and its control unit are similar in each variable before $t_0$, i.e.,
-
-$$\min(V_{i}^{t<t_0} - W_i * F_{control}^{t<t_0})$$
-
-where $V_i$ is a vector that indicates all features of a unit $i$ of the treated group, and $F_{control}$ is a matrix that consists of all features and units of the potential control group.
-$W_i$ is the weight matrix for target unit $i$.
-We minimized the root mean square error (RMSE) by using the Synth package in R \cite{abadieSynthPackageSynthetic2011, abadieComparativePoliticsSynthetic2015}.
-All codes are accessible in the repository.
-
-% 这样一来，基于降维的思想，我们构建出了一系列特征上与实验组最为接近的可比对照。
-In accordance with the idea of dimensionality reduction, we constructed a series of comparable control units that were most similar in characteristics to the treated units.
-Because the units of the control group were not affected by the institutional shifts, after giving the same weight to the total water use of the control group $M_i * WU_{control}$, the result $W_i*WU_{control}$ could be considered a reasonable estimation of the untreated situation.
-The net effect of the water allocation institutional shift was then estimated by calculating the difference of water uses after the institutional shift between the treated group and the control group, compared with the water use difference before the shift.
-
-\subsection{Placebo Test}
-% 作为一种稳健性检验，安慰剂测试的必要性体现在两个原因上。
-For robustness, we conducted a placebo test because the synthetic control method neglects the influences of overall changes in factors in the same year by simply dividing time periods according to institutional shifts.
-Three steps were required to apply the placebo test:
-% (1) 对目标组中的每个省份$i$，计算所有潜在控制组与它之间特征向量的欧氏距离
-(1) For each province in the target group, we calculated the Euclidean distance of vectors between all provinces in the potential control group.
-% (2) 将距离由小到大排序后，选取特征向量最相似的三个省份，所有特征的均值作为 $i$ 的替代
-(2) After ranking the distances, the three provinces with the most similar economic context were used to generate an average paired treatment target unit.
-% (3) 对这个配对目标同样实施控制合成法（潜在控制组排除构成它的三个省）
-(3) We performed the same synthetic control analysis for this paired target (i.e., the potential control group excluding the three provinces in step 2).
-% 经过上述步骤，我们在理论上构建了一个相似的“区域”并实施了同样的控制合成实验。
-In this way, we theoretically constructed a pseudo-treated unit and performed the same synthetic control treatments.
-Because these placebo tests were directed at units unaffected by the institutional shifts, the results can be regarded as a reasonable baseline expectation or null model from which to assess the changes caused by other factors.
-
-\subsection{Economic model}
-In order to understand the mechanisms underlying the empirical results, we developed a dynamic economic model to analyze how institutional change could have led to the sprint effect in water use.
-Specifically, we modeled individual provincial decision-making in water resources before quota execution.
-The analysis result implied that the underlying driver of CPR overuse was incentive distortion.
-
-In developing the model, we highlighted the main features of the YRB, as well as the water use institutions of 1987 and 1998. We proposed three intuitive and general assumptions.
-
-\begin{ass}
-    % (生产)为了简化，由于不可替代性，水是每个省的同质生产函数10的唯一投入。$F(x)$是连续的，满足Inada条件，即$F'(x)>0, F''(x)<0$(边际收益递减假设)，$F'(0)=\infty$,$ F'(\infty)=0$。产品产量处于完全竞争状态，单位价格为15。
-    (Water-dependent production) For simplicity, water is assumed to be the only input of the homogenous production function $F(x)$ of each province because of its irreplaceability.
-$F(x)$ is continuous and satisfies the Inada Conditions, i.e., $F'(x)>0, F''(x)<0$ (the diminishing marginal returns assumption), $F'(0)=\infty$,$ F'(\infty)=0$.
-The production output is under perfect competition, with a constant unit price of $P$.
-\end{ass}
-\begin{ass}
-    (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in N provinces, the cost of water use is equally assigned to each province under any water use.
-The unit cost of water is a constant $C$.
-\end{ass}
-\begin{ass}
-    (Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water uses.
-\end{ass}
-
-Under the above assumptions, we can demonstrate three cases consisting of local governments in YRB to simulate their water use decision-making and water use patterns.
-
-\begin{case} Decentralized institution:
-    This case corresponds to a situation without any high-level water allocation institution (i.e., before 1987, see Figure~\ref{fig:structure} B).
-
-    When each province independently decides on its water use, the optimal water use $\hat x_i^*$ in province $i$ satisfies:
-    $$F'(x)=\frac{C}{P \cdot N}$$
-
-    When the decisions in different periods are independent, for $t=0,1,2 \ldots$, then:
-    $$\hat x_{it}^*=\hat x_i^*$$
-
-\end{case}
-
-\begin{case} Mismatched institution
-    This case corresponds to a mismatched institution (i.e., $1987\sim1998$, see Figure~\ref{fig:structure} C).
-
-    The water quota is determined at $t=0$ and imposed in $t=1,2,\ldots$ The total quota is a constant denoted as $Q$, and the quota for province $i$ is determined in a proportional form:
-    $$Q_i=Q \cdot \frac{x_i}{x_i + \begin{matrix} \sum x_{-i} \end{matrix}}$$
-
-    Under a scenario with decentralized decision-making with a water quota institution, given other provinces’ water use decisions remain unchanged, the optimal water use $\widetilde x_{i0}^*$ of province $i$ at $t=0$ satisfies:
-
-    $F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot f(Q \cdot \frac{x_{i,0}}{\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix})^2}$.
-
-    When future water use is constrained by a water quota, the dynamic optimization problem of province $i$ is shown as follows:
-
-    $max  \quad P \cdot F(x_{i,0})-\frac{C \cdot \begin{matrix} \sum x_{i,0} + x_{-i,0} \end{matrix}}{N}+\beta P \cdot F(x_{i,1})+\beta^2 P \cdot F(x_{i,2})+...$
-
-    $=P \cdot F(x_{i,0})-C \cdot \frac{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}{N}+\frac{\beta}{1-\beta} P \cdot F(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}})$
-
-    First-order condition: $P \cdot F'(x_{i,0})-\frac{C}{N}+\frac{\beta}{1-\beta}[P \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0}+\begin{matrix} \sum  x_{-i,0} \end{matrix})^2}]=0$
-
-    where $f(\cdot)$ is the differential function of $F(\cdot)$.
-
-    The optimal water use in province i at t=0 $\widetilde x_{i,0}^*$ satisfies $P \cdot F'(x_{i,0})=\frac{C}{N}-\frac{\beta}{1-\beta} \cdot P \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$, i.e., $F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$.
-
-\end{case}
-
-\begin{case} Matched institution
-
-    This case corresponds to the institution under which the YRCC centrally managed water allocation between provinces (i.e., $1998\sim2008$, see Figure~\ref{fig:structure} D).
-
-    When the $N$ provinces decide on water uses as unified whole (e.g., the central government completely decides and controls on the water use in each province), the optimal water use $x_i^*$ of province $i$ satisfies:
-
-    $$F'(x)=\frac{C}{P}$$
-
-\end{case}
-
-We propose Proposition 1 and Proposition 2:
-
-\textbf{Proposition 1}: Compared with the decentralized institution, a matched institution with unified management decreases total water use.
-
-Because $F’$ is monotonically decreasing, based on a comparison of costs and benefits for stakeholders (provinces) in the three cases,
-
-$$\widetilde x_i^*>\hat x_i^*>x_i^*$$
-
-The result of $\hat x_i^*>x_i^*$ indicates that individual rationality would deviate from collective rationality when property rights are unclear \cite{hardinTragedyCommons2009}, because of the common-pool characteristics of water
-\cite{castilla-rhoGroundwaterCommonPool2020,ostromGeneralFrameworkAnalyzing2009}.
-
-The difference of $\widetilde x_i^*$ and $\hat x_i^*$ stems from two parts: the marginal returns effect and the marginal costs effect.
-First, the “shadow value” provides additional marginal returns of water use in $t=0$, wwhich increases the incentives of water overuse by encouraging bargaining for a larger quota.
-Second, the future cost of water use would be degraded from $\frac{P}{N}$ to an irrelevant cost.
-
-The optimal water use under the three cases implies that mismatched institutions cause incentive distortions and lead to resource overuse.
-
-\textbf{Proposition 2}: The quota determination of the mismatched institution increases the incentives of current water use.
-
-The intuition for this proposition is straight-forward in that all provinces would use up their allocated quota under a relatively small $Q$.
-As $Q$ increases, the quota would provide higher future benefits for a pre-emptive water use strategy.
-Since the provincial water use decisions are exactly symmetric, total water use would increase when each province has higher incentives for current water use.
-This situation corresponds to a “sprint” effect, where the total water use dramatically increases in the “sprint” period.
-
-Extensions of the model are shown in \textit{Supplementary Material S3}.
-
-\section{Info.}
-Funding was provided by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007).
-
-[Competing Interests] The authors declare that they have no competing interests.
-
-[Correspondence] Correspondence and requests for materials should be addressed to Shuai Wang.~(email: shuaiwang@bnu.edu.cn).
-
-[Author contributions]Shuai Wang and Bojie Fu designed this research, Shuang Song performed the research and analyzed data, and Huiyu Wen designed the economic model.
-Shuang Song and Huiyu Wen wrote the paper, and Graeme S.
-Cumming revised the manuscript and offered important advice.
-
-[Code availability] All codes and datasets used in this research are accessible at https://github.com/SongshGeo/sochyd-transboundary-HESS.
-They will be made open source after this project is completed.
-
-%% Put the bibliography here, most people will use BiBTeX in
-%% which case the environment below should be replaced with
-%% the \bibliography{} command.
-\bibliography{WAInstitution_YRB_2021}
-
-%% Here is the endmatter stuff: Supplementary Info, etc.
-%% Use \item's to separate, default label is "Acknowledgements"
-
-\end{document}

### 2022-03-10 docs/papers/tex/main.tex
docs(paper): initialize paper in LaTeX, prepared to refactor it

@@
-%% Template for a preprint Letter or Article for submission
-%% to the journal Nature.
-%% Written by Peter Czoschke, 26 February 2004
+\documentclass{nsr}
+
+\usepackage{amsmath,graphicx,array}
+\usepackage{dcolumn,soul}%
+\let\openbox\relax
+\usepackage{amsthm}
+\usepackage[figuresright]{rotating}%
+\usepackage{algorithm, algorithmicx, algpseudocode}
+\usepackage{listings}%
+\usepackage{hyperref}
+
+\makeatletter
 %%
-\documentclass{article}
-\usepackage{hyperref}
-\usepackage{graphicx}
-\usepackage{setspace}
-\usepackage[a4paper, total={7in, 10in}]{geometry}
+\def\uns{\ifmmode\,\else$\,$\fi}%
+\newtheorem{theorem}{Theorem}
+\newtheorem{construction}{Construction}
+\newtheorem{estimate}{Estimate}
+\newtheorem{lemma}{Lemma}
+\newtheorem{corollary}{Corollary}
+\newtheorem{result}{Result}
+\newtheorem{algth}{Algorithm}
+\newtheorem{proposition}{Proposition}
+\newtheorem{hypothesis}{Hypothesis}
+\newtheorem{experiment}{Experiment}
+\newtheorem{definition}{Definition}
+\newtheorem{condition}{Condition}
+\newtheorem{property}{Property}
+\newtheorem{problem}{Problem}
+\newtheorem{fact}{Fact}
+\newtheorem{assumption}{Assumption}
+\newtheorem{eexample}{Example}
+\newtheorem{model}{Model}
+%%
+\makeatother
 
-\setstretch{1.523}
+\jvol{XX}
+\jnum{X}
+\jyear{Year}
+\doi{10.1093/nsr/XXXX}
+\received{XX XX Year}
+\revised{XX XX Year}
+\accepted{XX XX Year}
 
-\newtheorem{ass}{Assumption}
-\newtheorem{case}{Case}
-%% make sure you have the nature.cls and naturemag.bst files where
-%% LaTeX can find them
-
-\bibliographystyle{naturemag}
-
-%\usepackage{biblatex}
-%% make sure you have the nature.cls and naturemag.bst files where
-%% LaTeX can find them
-
-\title{Importance of social-ecological fit for water management in large river basins: An analysis of institutional shifts in the Yellow River Basin}
-
-%% Notice placement of commas and superscripts and use of &
-%% in the author list
-
-\author{Shuang Song$^{1,2}$, Huiyu Wen$^3$, *Shuai Wang$^{1,2}$, Graeme S. Cumming$^{4}$ \& Bojie Fu$^{1, 2}$}
+\markboth{One, Two, and Three}{One, Two, and Three}
 
@@
 
+\dhead{RESEARCH ARTICLE}
+\subhead{EARTH SCIENCES}
+\newtheorem{ass}{Assumption}   % My command. Assumptions.
+\newtheorem{case}{Case}  % My command. Cases
+
+\bibliographystyle{nsr}
+
+\title{\input{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/docs/papers/elements/title.md}}
+
+\author{Shuang Song$^{1,2}$}
+\author{Huiyu Wen$^3$}
+\author{*Shuai Wang$^{1,2}$}
+\author{Xutong Wu$^{1,2}$}
+\author{Graeme S. Cumming$^{4}$}
+\author{Bojie Fu$^{1,2,5}$}
+
+\affil{$^1$State Key Laboratory of Earth Surface Processes and Resource Ecology,
+     Faculty of Geographical Science,
+     Beijing Normal University,
+     Beijing 100875,
+     P.R. China}
+
+\affil{$^2$Institute of Land Surface System and Sustainability,
+     Faculty of Geographical Science,
+     Beijing Normal University,
+     Beijing 100875,
+     P.R. China}
+
+\affil{$^3$School of Finance,
+     Renmin University of China,
+     Beijing 100875,
+     P.R. China}
+
+\affil{$^4$ARC Centre of Excellence for Coral Reef Studies,
+     James Cook University,
+     Townsville 4811,
+     QLD, Australia}
+
+\affil{$^5$The research for this article was financed by.......
+The authors thank.......
+for insightful comments and .......
+for expert research assistance.
+A supplementary online appendix is available with this article at the \em{National Science Review} website.}
+
+\authornote{\textbf{Corresponding authors.} Email: shuaiwang@bnu.edu.cn}
+\authornote{Shuang Song and Huiyu Wen equally contributed to this work.}
+
+\abstract[ABSTRACT]{\input{../elements/abstract}}
+
+\keywords{\input{../elements/keywords}}
 \maketitle
-\input{../../drafts/authors.md}
 
-\begin{abstract}
-    \input{../../drafts/abstract.md}
-\end{abstract}
-
-% Then the body of the main text appears after the intro paragraph.
-% Figure environments can be left in place in the document.
-% \verb|\includegraphics| commands are ignored since Nature wants
-% the figures sent as separate files and the captions are
-% automatically moved to the end of the document (they are printed
-% out with the \verb|\end{document}| command. However, tables must
-% be manually moved to the end of the document, after the addendum.
-% 表需要手动移到文末
-% water use; water management; social-ecological system; common pool resources; institutional analysis; collaborative governance
-
-\section{Introduction}
-Emerging competition for water is an urgent problem in water governance, with widespread water scarcity and overuse resulting in huge impacts on economies, societies, and ecosystems \cite{gleickPeakwaterlimits2010,dolanEvaluatingeconomicimpact2021,siwiCompetitionWaterGetting,ziolkowskaCompetitionWaterResources2016,distefanoArewedeep2017}.
-Water is the key exclusive and competitive resource that couples socioeconomic and ecological systems (known as common-pool resources, CPRs) \cite{wutichWaterScarcitySustainability2009,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017,castilla-rhoGroundwaterCommonPool2020}.
-Conflicts of interest often occur in allocation and competitions of water resources, with water governance policies often leading to long-term changes in human–water relationships and the redistribution of benefits \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013,chingManagingsocioecologyvery2015}.
-Although governments in many of the world’s large river basins have tried to resolve competition for water through the deliberate design of new institutions, general principles underlying the successes and failures of these initiatives are poorly documented and understood.
-
-Institutions (such as policies, laws, and norms) can influence regional sustainability by changing social-ecological system (SES) structure and dynamics \cite{youngInstitutionsenvironmentalchange2008,cummingAdvancingunderstandingnatural2020,lieninstitutionalgrammartool2020}.
-These include inter-relationships and interactions between social actors, between ecological units, or between social and ecological system elements \cite{bodinCollaborativeenvironmentalgovernance2017,barnesSocialecologicalalignmentecological2019}.
-Effective (“matched”) institutions operate at appropriate spatial, temporal, and functional scales to manage and balance these different relationships and interactions \cite{heWateringEnvironmentalRegulation2020,kellenbergempiricalinvestigationpollution2009}.
-From the perspective of SES outcomes, matched institutions support (but do not guarantee) sustainability \cite{epsteinInstitutionalfitsustainability2015,wangAlignmentsocialecological2019}.
-
-Some kinds of institutions have been shown to support desirable outcomes in water-centered SESs (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wangAlignmentsocialecological2019} and in collaborative water governance systems in Europe \cite{greenEUWaterGovernance2013}).
-At the same time, undesired and unsustainable outcomes (e.g., failures in environmental regulation of highly polluting industries or the development of “tragedy of the commons” situations when pursuing more water resources), with considerable ecological degradation, have attracted much attention \cite{saylesSocialecologicalnetworkanalysis2019,caiPollutingthyneighbor2016,castilla-rhoSocialtippingpoints2017}.
-Despite widespread recognition of the rising importance of integrated water resource management in solving water competition in the world’s large river basins, relatively few studies have explored the mechanisms by which SESs respond to new institutions \cite{agrawalSustainableGovernanceCommonPool2003,pershaSocialEcologicalSynergy2011,agrawalCommonPropertyInstitutions2001}.
-Two particular weaknesses in existing knowledge include understanding (1) the causal links between SES structures and outcomes; and (2) details of the underlying processes, especially the coordination of the incentives of different participants, that result from an institutional lack of fit.
-These weaknesses limit our understanding of institutional design, and they may reduce the speed and transfer of new knowledge and experience related to improving the sustainability of comprehensive water resources management.
-
-In order to disentangle the relationship between SES structure and outcomes, we analyzed a case study to show how an institutional shift led to a structural mismatch that triggered unsustainable water use and unintended ecological deterioration.
-Two rapid shifts in institutional structure that occurred in 1987 and 1998 (see Supplementary Material S1) provide unique settings to exploit quasi-natural experiments of a large river basin, the Yellow River Basin (YRB) in China \cite{xiaDevelopmentWaterAllocation2012}.
-After a period of severe drying up, an institutional shift implemented in 1987 represented the beginning of attempts to control water use in the YRB through the use of quotas, with the goals of alleviating conflicts between supply and demand and achieving sustainable development.
-
-Our results show that this initiative actually accelerated water withdrawals, resulting in an unintended “sprint effect”, where institutional mismatches created an even stronger incentive for each resource user to withdraw resources until the next major institutional shift in 1998.
-Our analysis contributes to a deeper understanding of the mechanisms underlying the relationships among institutions, SES structures, and outcomes.
-By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings are consistent with the urgent calls for a more dynamic design for water use allocation to achieve sustainability.
-
-\section{Institutions and SES structures}
-% 机构可以塑造社会经济体系的结构，对其进行抽象是机械地理解结构和结果之间联系的第一步。
-Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{fig:framework}A).
-% 例如，机构可以创建一种被确定为与良好的社会经济效益相关联的水平匹配结构，如果它鼓励管理相连生态成分的不同行动者之间的协作(图1B)。
-For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{fig:framework}B), leading to sustainable outcomes.
-% 例如，机构可以创建一个结构，鼓励不同行为者之间的合作，管理相连的生态成分
-Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{fig:framework}C and D).
-% 在实践中，一个大型、复杂的河流流域的制度变化将创造或摧毁数百种不同的联系。这些局部变化的更广泛影响可以从系统的整体行为中看到。
-In practice, institutional changes in a large, complex river basin will create or destroy hundreds of different connections.
-The broader impacts of these local changes can be seen in the overall behavior of the system.
-% 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
-We thus explored the causal linkages between the SES structures and sustainability (outcomes) in quasi-natural experiments of the YRB, which provides an informative case study for two main reasons.
-% 首先，长江流域管理的急剧结构变化使我们能够定量估计高层制度设计变化对用水的净影响。决定水分配的制度包括自下而上的协议或社会规范，以及自上而下的配额或法规，它们对社会经济结构有不同的影响;自上而下的监管可能会立即引发制度转变和SES的剧烈结构性变化。通过与由自下而上的制度转变引起的更渐进的变化相比，探索自上而下变化的影响，在对社会经济地位的定量分析中，极大地减少了来自不可观测因素的潜在干扰，提高了社会经济地位结构和结果之间因果关系的清晰度。
-First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use.
-Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013}; top-down regulations can trigger immediate institutional shifts and sharp SES structural changes \cite{speedBasinwaterallocation2013,rolandUnderstandinginstitutionalchange2004}.
-In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and improves the clarity of the causal link between SES structure and outcome.
-% 其次，通过比较长江流域两次制度变迁所分裂的三种不同制度结构的净效应，我们也可以更深入地理解“盆地固定效应”下结构格局的影响。尽管流域内的社会经济单位从世界各地的大型河流流域和许多地区的水资源中受益，但很少有流域多次经历过如此激进的社会经济结构变化。
-Second, by comparing the net effects of three different institutional structures split by two institutional shifts in the YRB, we can also reach a stronger understanding of the influence of structural alignments under a fixed basin.
-Although socioeconomic units within a basin benefit from water resources in large river basins all over the world and many locations have shown increased levels of regulation, few basins have experienced such radical SES structural changes several times (see \textit{Supplementary Material} S1).
-Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in SES institutional structure.
-% 因此，黄河流域的“流域固定效应”为SES结构的自我比较提供了宝贵的机会。
-% Thus, the YRB provides valuable settings for understanding the direct impacts of changes in SES institutional structure.
+\section{INTRODUCTION}\label{intro}
+\input{../elements/introduction}
 
@@
 	\centering
-	\includegraphics[width=8.3cm]{../../../figs/diagrams/framework.jpg}
+	\includegraphics[width=16pc]{../../../figs/diagrams/framework.jpg}
 	\caption{
@@
 
-\section{Context of institutional shifts}
-% 黄河是世界第五长河，它的流域也是中国文明的摇篮。
-The Yellow River, whose basin is the cradle of Chinese civilization, is the fifth-longest river in the world.
-It supports $9.7\%$ of China’s irrigation, with only $2.6\%$ of its total water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021).
-% 然而，经过沿江各省多年的免费取水(图~\ref{fig:structure} A和B)，到20世纪80年代，黄河地表水耗水量接近径流量的10倍，并不断上升
-However, after years of free access to water by provinces along the river (Figure~\ref{fig:structure} A and B), surface water consumption of the Yellow River was close to $80\%$ of its runoff by the 1980s and rising
-\cite{wangYellowRiverwater2019,songSedimenttransportincreasing2020}.
-% 自1972年以来，黄河径流量的减少破坏了黄河的生态，制约了黄河的经济发展
-Reductions in runoff after 1972 damaged the ecology of the YRB and restricted its economic development \cite{wangYellowRiverwater2019}.
-% 因此，在中国典型的自上而下的制度结构下(附录图S1-B)，黄河流域不同层次提出了相对完整的水资源分配规定(图1a)。
-Therefore, through typical top-down institutional structures in China (see \textit{Supplementary Material S1}), relatively integrated water allocation regulations were successively proposed across different levels in the YRB.
-% 这些机构包括国家政府、流域管理机构、省、市，甚至地区(见图1 B-D)。
-These include the national government, the basin management agency, provinces, cities, and even districts.
-% 这些在不同制度发展阶段相继出台的政策，引发了长江经济带经济发展结构的突变，并产生了不同的结果(见附录A和图S1-C)。
-These policies at different stages of institutional development triggered abrupt changes in the SES structure of the YRB with different outcomes.
-
-% 0世纪70年代以来，中国政府向黄河水利委员会下达指令，要求黄河水利委员会设计配水方案，同时要求黄河沿岸各省进行水资源规划
-In 1982, the Chinese government issued instructions to the Yellow River Water Conservancy Commission (YRCC), the basin agency of the YRB, requiring it to design a water allocation scheme and at the same time requiring the provinces along the Yellow River to carry out water resources planning (see \textit{Supplementary Material S1})
-\cite{wangReviewImplementationYellow2019}.
-% 经过多方讨论与权衡，中国政府于1987年为相关省份分配了水资源配额，要求沿黄各省(区)贯彻执行
-The Chinese government started to assign water quotas to the relevant provinces in 1987, but did not create a unit to coordinate water division between them (Figure~\ref{fig:structure} \textbf{A} and \textbf{C}).
-% 这一时期长江水利枢纽的监督任务是编制长江水利枢纽用水量统计公报，并与定额进行对比分析。
-The mandate of the YRCC during this period was only to report on and analyze water consumption in the YRB
-\cite{wangReviewImplementationYellow2019}.
-% 随着断流的进一步恶化，1998年中国政府推进了相关政策的改革，要求所有省份在取用水资源时必须向黄委会申请许可，黄委会得以直接对各省的用水实施监管。
-However, since reductions in river flow indicated an unintended SES outcome (Figure~\ref{fig:structure} E), the Chinese government pushed for a policy reform in 1998 that required all provinces to apply for licenses to use water from the YRCC, allowing the council to directly regulate their water use (see \textit{Supplementary Material S1} and Figure~\ref{fig:structure} A and D).
-% 由于革新后的政策成功遏制了断流，2008年该分配政策被进一步细化，相关各省都进一步设置了更细致的分配方案，并最终形成了黄河流域如今的水资源分配格局。
-The 1998 policy succeeded in curbing water extraction (Figure~\ref{fig:structure} E), and it was further refined in 2008.
-The relevant provinces created a more detailed allocation plan and finally formed the present water allocation institutions of the YRB (see \textit{Supplementary Material S1}).
-% 因此，在1975-2008长达33年的时间里，从没有分水政策到以两种不同模式监管下的分水政策，黄河流域实际上先后存在着三种不同的社会-生态结构（Fig 1）。
-Therefore, in our study period (from 1975 to 2008), the system shifted between three different SES structures (Figure~\ref{fig:structure} \textbf{B} to \textbf{D}).
-% 在它们之中，与预期相反地，1987年至1998年的流域SES结构下黄河的生态急剧恶化，表明了制度的失配。
-The sharp and unintended decline in the ecological condition of the Yellow River from 1987 to 1998 indicates an institutional mismatch during this period (Figure~\ref{fig:structure} the shadowed time periods).
+\section{Context of institutional shifts}\label{institution}
+\input{../elements/institution.tex}
 
@@
     \centering
-    \includegraphics[width=12cm]{../../../figs/diagrams/structure.jpg}
+    \includegraphics[width=16pc]{../../../figs/diagrams/structure.jpg}
 	\caption{
@@
 
-\section{Sprint effect induced by an institutional mismatch}
-% % 这里，我们使用合成控制模型创建了假设不存在政策变化的虚拟对照组（see \textit{Methods}-1），同时用K-近临算法找到经济状况与黄河流域各省“类似”的安慰剂对照（see \textit{Methods}-2），反复对比表明两次社会-生态系统结构变迁对流域的水资源利用及分配产生了明显不同的影响。
-% Here, we use synthetic control method to create a control group assuming that there is no water use constraints (\textbf{methods}), at the same time with K-nearest algorithm to match an economic state and the YRB provinces ``similar'' placebo-controlled (\textbf{methods}).
-% % 然后，我们反复比较了两个SES结构(分别自1987年和1998年)，以量化是否有显著不同的影响，YRB用水或分配。
-% Then we repeatedly compared between two SES structures (since 1987 and 1998, respectively) to quantify if there were significantly different impacts on water uses or allocation (\textbf{methods}).
-% % 我们的结果表明，1987年的结构变化刺激各省使用了远超模型预测的没有政策影响下的用水量，其增量超出安慰剂对照组xx\%，但对水资源的分配的均匀程度没有改变（see fig）。
-Our results suggest that the institutional shift in 1987 stimulated the provinces to use far more water than would have been used without policy effects (Figure~\ref{fig:main_results}A), with an observed increase of $164\%$ over the expectation(Figure~\ref{fig:main_results}B).
-% 然而，水资源分配的均匀性并没有改变，区域间的用水量在相同规模下增加(图~\ref{fig:main_results}C)。
-However, the relative share of water use was not changed, denoting proportionally similar water use increases among the different regions (Figure~\ref{fig:main_results}C).
-% 在1998年出台的政策再次改变社会-生态结构之后，用水量显著下降，总量仅为安慰剂对照组的xx%。
-After the SES structure changed again in 1998, the trend of increasing water use appeared to be effectively suppressed (Figure~\ref{fig:main_results} D), with total observed water consumption decreasing by $260\%$ relative to expectations(Figure~\ref{fig:main_results} E).
-% 但此阶段主要是xx，xx，xx等黄河流域的用水大省受到了遏制，因此水资源在各个省之间的比例分配变得更均匀了。
-At this stage, however, the reduction in water use came mainly from the provinces with large water consumption, such as Henan and Shandong (Figure~\ref{fig:main_results} E),  so the proportion of water used by regions became more similar (Figure~\ref{fig:main_results} F).
-% 上述结果表明，1998年各省之间由黄委会统一监管后分水政策才真正达到了其遏制用水、解决断流的预期。
-In conclusion, the water allocation policy curbed water use in 1998, whereas the 1987–1998 institutional mismatch stimulated a notable increase in total water use in all related provinces.
-% 在过去的十年里，对制度变革的“冲刺”反应似乎创造了一场竞赛，每个省份都开始使用超过他们需要的水。
-Over this decade, “sprint” responses (i.e., rapid increases in resource use \cite{lueckPreemptiveHabitatDestruction2003}) to institutional change appear to have created a race in which each province began to use more water than they needed.
+\section{RESULTS}\label{results}
+\subsection{SPRINT EFFECT}\label{phenomenon}
+\input{../elements/results.tex}
 
@@
     \centering
-    \includegraphics[width=12cm]{../../../figs/outputs/main_results.jpg}
+    \includegraphics[width=16pc]{../../../figs/outputs/main_results.jpg}
     \caption{
@@
 
-\section{Incentive distortion causes the sprint effect}
-Theoretically, our economic model suggests that different kinds of institutional shifts should lead to different optimal water uses (Figure~\ref{fig:economic_model}).
-Furthermore, our analysis indicated that the cause of the sprint effect in this case was incentive distortion.
-Compared with the decentralized water allocation institution in place before 1987, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs (see Table~\ref{tab:cases} the \textbf{methods} for a detailed mathematical formula).
-% 在不匹配条件下，边际成本减去边际收益增加，导致用水量增加，xx的差异反映了水配额模拟的非预期冲刺效应。
-The unintended sprint effect (from 1987 to 1998) was caused by both declining marginal costs (a shift from a fixed unit cost to an irrelevant cost) and increasing marginal returns due to future water use benefits (see Table~\ref{tab:cases} the \textbf{methods} for a detailed mathematical formula).
-% 因此，这种制度引发了一种与可持续用水意图背道而驰的激励扭曲。
-The institution thus triggered an incentive distortion that ran counter to the intention of sustainable water use.
-Further, the strength of the sprint effect was positively correlated with the size and time horizon of the water use quota (Figure~\ref{fig:economic_model} \textbf{Panel B}).
-% 这些理论上的预测正如我们在黄河流域所观察到的一样，不匹配的配额制度导致了短跑效应的出现，而中心化的制度结构结束了这一非预期的现象。
-% These theoretical predictions, in line with phenomenon observed in the YRB, indicating the mismatched institution leads to incentive distortion of provinces for pre-empting resources by `sprinting', according to their expectations for the future.
-% 这些理论预测进一步从YRB观察到的现象出发，表明不匹配的配额制度通过提高边际效益来刺激用水量，而边际效益与放宽限制带来的未来潜在用水量的影子值有关。
-% These theoretical predictions, further from the phenomenon observed in the YRB, indicating the mismatched institution with quota stimulates water use by raising marginal benefits, which is related to the shadow value of potential future water use from relaxing the constraints.
-% 温博推荐的版本：
-% These theoretical predictions, further from the phenomenon observed in the YRB, attributing ``sprint effect'' into raising marginal benefits -by pursuing indirectly generating shadow value of water use while converting fixed marginal costs to irrelevant cost for each individual province.
-
-\begin{table}[!ht]
-	\centering
-	\caption{Summary of marginal returns and marginal costs for each case }
-	%\footnotesize
-    \setlength{\tabcolsep}{1mm}{
-       \begin{tabular}{lccc}
-		\hline
-		& Case 1: Decentralized Ins. & Case 2: Mismatched Ins. & Case 3: Matched Ins. \\ \hline
-		Marginal return & $P*F'(X)$                & $P*F'(X)+V(X)^*$            & $P*F'(X)$              \\
-		Marginal cost   & $C/N$                    & $Irrelevant$              & $C$                   \\ \hline
-	\end{tabular}
-    }
-	\centering
-	\footnotesize{\leftline{$^*$Note: $V(X)$ denotes a shadow value.}}
-	\label{tab:cases}
-\end{table}
+\subsection{CAUSES}\label{causes}
+\input{../elements/model}
+\input{../elements/table.tex}
 
@@
     \centering
-    \includegraphics[width=12cm]{../../../figs/outputs/economic_model.jpg}
+    \includegraphics[width=16pc]{../../../figs/outputs/economic_model.jpg}
 	\caption{
@@
 
-\section{Discussion}
-% 我们展示了不匹配的分配制度是如何导致激励失真导致水资源加速耗竭的(即“冲刺效应”)。“冲刺效应”是CPR系统面临的一种特殊情况，在这种情况下，制度的不匹配为每个资源使用者创造了更强的动机(扭曲)，促使他们收回资源
-We have shown how a mismatched allocation institution can lead to an accelerated depletion of water resources (i.e., the “sprint effect”) caused by incentive distortion.
-The sprint effect is a special case faced by CPR systems, where institutional mismatches create an even stronger incentive (with distortion) for each resource user to withdraw resources
-\cite{ostromRevisitingCommonsLocal1999,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017}.
-% 过往研究指出制度常常是避免公共池塘资源系统的崩溃的关键，但“短跑效应”的出现表明在自上而下进行制度设计所形成的错配SES结构中，制度也可以成为系统加速崩溃的触发者。
-Previous studies have suggested that institutions are often the key to avoid the collapse of a CPR system, but the emergence of a sprint effect shows that an institution with structural mismatches can also be the trigger that accelerates system collapse \cite{bodinConservationSuccessFunction2014,bodinCollaborativeenvironmentalgovernance2017,wangAlignmentsocialecological2019}.
-The initial formulation of the water quota in our case studies went through a stage of “bargaining” among stakeholders (from 1982 to 1987) \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}, where each province attempted to demonstrate its development potential related to water use.
-% 在高层决策者与低层利益相关者之间存在信息不对称的用水分配中，当前用水量越大的利益相关者议价能力越大。1987年以后，对各省来说，合乎逻辑的下一步是试图证明争取更大配额的合理性，而不是立即采取资源节约型改革。在实践中，尽管受影响的省份可能没有直接鼓励过度使用资源，但由于激励扭曲，他们有更大的动机对资源提取开绿灯。因此，在争夺潜在的水资源配额时，各省往往将生态成本隐藏在经济发展背后。
-In water use allocation with information asymmetry between upper-level decision-makers and lower-level stakeholders, those with more current water use might have greater bargaining power.
-After 1987, the logical next step for provinces was to attempt to justify bargaining for larger quotas rather than immediately adopt resource-conserving transformations.
-In practice, although the affected provinces may not have directly encouraged excessive resource use, they had a greater incentive to give the green light to resource withdrawals because of incentive distortions \cite{kriegerProgressGroundWater1955, ostromGoverningCommonsEvolution1990}.
-As a result, while competing for potential water quotas, the provinces tended to hide the ecological costs behind economic development.
-
-% 毫无疑问，随着资源竞争的日趋激烈，越来越多的SES正依赖着不同形式的制度进行资源分配（如自组织和政府干预），避免“短跑效应”的出现或将成为制度设计的关键。
-There is no doubt that with increasingly fierce competition for water, more and more SESs are developing new institutions for water allocation (whether through self-organization or government intervention) \cite{anderssonVoluntaryleadershipemergence2020, wutichWaterScarcitySustainability2009}.
-% 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
-Adoption of an overall quota plays an important role in preventing overuse of CPRs \cite{tilmanLocalizedprosocialpreferences2019}.
-However, the negative effects of incentive distortion imply a trade-off between long-term SES benefits and current stability, and the proportion of available resources allocated under quota schemes matters when institutions change \cite{ladeRegimeshiftssocialecological2013}.
-According to our analysis of plausible scenario assumptions based on our general economic model, the sprint effect will be reinforced when stakeholders anticipate that technological advances will amplify the benefits of water quotas in the future (see \textit{Supplementary Material S3}).
-% 然而，如果有水权转换机制允许利益相关者之间通过交易来弥补 shadow value，当前这种错乱的动机就不会那么强。
-However, if an institution allowed stakeholders to compensate for the shadow value (i.e., potential returns sacrificed due to water constraints and water scarcity) \cite{howarthAccountingvalueecosystem2002} of future water use, incentive distortion would be less devastating (e.g., through water rights transfer).
-Policymakers can also weaken the sprint effect by increasing the frequency of quota updates, supporting the idea that a more dynamic institution that responds to changing conditions (see \textit{Supplementary Material S3}) will adapt more effectively to its social-ecological context.
-
-% 近年来黄河流域面临的分水制度调整问题也说明了动态设置配额的重要性。
-Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of dynamic quota setting (see \textit{Supplementary Material S1}) \cite{yuAdaptabilityassessmentpromotion2019}.
-Following the institutional reforms of 1998, the Yellow River has not dried up since 1999.
-However, given recent changes in the YRB, its rigid resource allocation scheme can no longer meet the new demands of economic development \cite{wangThingsCurrentSignificance2019}.
-The Chinese government has embarked on an ambitious plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}).
-Other SESs around the world face similar problems in establishing successful resource allocation institutions \cite{cummingQuantifyingSocialEcologicalScale2020, muneepeerakulStrategicbehaviorsgovernance2017, cummingAdvancingunderstandingnatural2020, leslieOperationalizingsocialecologicalsystems2015}.
-These initiatives can benefit from our analysis by actively considering and incorporating social-ecological complexity and incentive structures when developing new approaches that avoid unsustainable outcomes.
-Our research provides a cautionary tale of how institutions can act as a double-edged sword when trying to attain sustainability.
+\section{DISCUSSION}\label{discussion}
+\input{../elements/discussion}
 
@@
 
-\section{Info.}
-Funding was provided by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007).
+\section{CONCLUSION}\label{conclusion}
+\input{../elements/conclusion}
 
-[Competing Interests] The authors declare that they have no competing interests.
-
-[Correspondence] Correspondence and requests for materials should be addressed to Shuai Wang.~(email: shuaiwang@bnu.edu.cn).
-
-[Author contributions]Shuai Wang and Bojie Fu designed this research, Shuang Song performed the research and analyzed data, and Huiyu Wen designed the economic model.
-Shuang Song and Huiyu Wen wrote the paper, and Graeme S.
-Cumming revised the manuscript and offered important advice.
-
-[Code availability] All codes and datasets used in this research are accessible at https://github.com/SongshGeo/sochyd-transboundary-HESS.
-They will be made open source after this project is completed.
+\appendix
+\label{appendix}
+%%%%%%%% -----  appendix -------- %%%%%%%%%%
 

### 2022-03-11 config.py
fix(iter-placebo-fix): some experiment didn't correctly have the parameter iter placebo in analysis, now fixed

@@ -140,10 +140,11 @@ if __name__ == "__main__":
     exp_rel_path = exp.get_path("experiment", absolute=False)
     exp_log = set_logger(exp.name, path=exp_rel_path)
     exp.change_experiment_logger(exp_log)
+    exp.load_from_pickle()
 
     # modelling
-    sc_result = exp.do_experiment(model=do_synth_model, notification=True)
-    exp.drop_exp_to_pickle()
+    # sc_result = exp.do_experiment(model=do_synth_model, notification=True)
+    # exp.drop_exp_to_pickle()
 
     # analysis
     exp.do_analysis(model=do_synth_analysis)

### 2022-03-11 func/model.py

@@ -8,7 +8,7 @@
 
 import pandas as pd
 from attrs import define, field
-from SyntheticControlMethods import Synth
+from SyntheticControlMethods import DiffSynth, Synth
 from tqdm import tqdm
 
 
@@ -105,7 +105,12 @@ def do_synth_once(province, data, outside_data, used_variables, parameters):
     ]
     used_data = used_period[used_variables]
 
-    sc = Synth(
+    if parameters.get("synth") == "DSC":
+        # DSC = Diff Synth Control
+        synth = DiffSynth
+    else:
+        synth = Synth
+    sc = synth(
         used_data,
         parameters["Y_inputs"],
         "Province",

### 2022-03-20 docs/papers/tex/appendix/institution_context.tex
feat(paper): paper structure

--- 2022-03-04 docs/papers/tex/appendix.tex
@@
-\documentclass{article}
-\usepackage{hyperref}
-\usepackage{graphicx}
-\usepackage{setspace}
-\usepackage[a4paper, total={7in, 10in}]{geometry}
+%! Author = songshgeo
+%! Date = 2022/3/10
 
-\setstretch{1.523}
-
-\newtheorem{ass}{Assumption}
-\newtheorem{case}{Case}
-%% make sure you have the nature.cls and naturemag.bst files where
-%% LaTeX can find them
-
-\bibliographystyle{naturemag}
-
-\title{Supplementary Materials for
-
-Importance of social-ecological fit for water management in large river basins: An analysis of institutional shifts in the Yellow River Basin}
-
-%% Notice placement of commas and superscripts and use of &
-%% in the author list
-
-% \author{Shuang Song$^{1,2}$, Huiyu Wen$^3$, *Shuai Wang$^{1,2}$, Graeme S. Cumming$^{4}$ \& Bojie Fu$^{1, 2}$}
-
-\begin{document}
-
-\maketitle
-\input{../../drafts/authors.md}
-
-\begin{abstract}
-    % 这个补充材料以下述逻辑组织而成：
-    The supplementary material is organized logically as follows:
-    % 展示流域水资源分配制度在全球的推行情况并详细介绍黄河流域的制度变化，旨在说明黄河流域为什么是一个独一无二的准自然实验。
-    (1) Show the implementation of the water resource allocation system in the basin around the world and introduce the institutional changes in the Yellow River Basin in detail, aiming to explain why the Yellow River Basin is a unique quasi-natural experiment.
-    % 展示定量分析方法的技术路线图，并详细介绍定量分析方法中的细节部分。
-    (2) Show the technical roadmap of quantitative analysis method, and introduce the details of quantitative analysis method in detail.
-    % 基于我们建立的一般经济模型，对一些可能的情景进行进一步分析。
-    (3) Further extensions based on our general economic model.
-\end{abstract}
-
-\section*{S1. Detailed introduction of the institutions}
 % 水资源分配方案在全世界范围内都是流域管理的普遍制度。
@@
 
-\begin{figure}[!htb]
-    \centering
-    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/world_institutions}
-	\caption{
-		Overview of water allocation institutions.
-		% 世界已有水资源分配制度的大河流域，其中黄河流域最早于1987年提出资源分配方案，后于1998年更改为统一调度方案。
-		\textbf{A.} Major river basins in the world with existing water resource allocation systems (shaded red); the YRB first proposed a resource allocation scheme in 1987 (designed in 1983) and then changed to a unified regulation scheme in 1998 (designed in 1997 but implemented in 1998).
-		% 不同的水资源分配制度设计模式，中国黄河流域是典型的自上而下。
-		\textbf{B.} Different water resource allocation system design patterns; the YRB is typical of a top-down system with multiple levels.
-		% 流域分水制度的演化。这种多层次的制度设计有其历史变化过程。
-		\textbf{C.} The four periods of institutional evolution of water allocation of the YRB.
-	}
-    \label{fig:world}
-\end{figure}
 % 在上述文件中，1982年的文件标志着设计分水制度尝试的开始，2008年标志着该制度走向成熟（完全建立起流域-省-市区的多级水资源分配和统一调度）。
@@
     \centering
+    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/world_institutions}
+	\caption{
+		Overview of water allocation institutions.
+		% 世界已有水资源分配制度的大河流域，其中黄河流域最早于1987年提出资源分配方案，后于1998年更改为统一调度方案。
+		\textbf{A.} Major river basins in the world with existing water resource allocation systems (shaded red); the YRB first proposed a resource allocation scheme in 1987 (designed in 1983) and then changed to a unified regulation scheme in 1998 (designed in 1997 but implemented in 1998).
+		% 不同的水资源分配制度设计模式，中国黄河流域是典型的自上而下。
+		\textbf{B.} Different water resource allocation system design patterns; the YRB is typical of a top-down system with multiple levels.
+		% 流域分水制度的演化。这种多层次的制度设计有其历史变化过程。
+		\textbf{C.} The four periods of institutional evolution of water allocation of the YRB.
+	}
+    \label{fig:world}
+\end{figure}
+
+\begin{figure}[!htb]
+    \centering
 	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/YRB_scheme}
@@
 \end{figure}
-
-\section*{S2. The technical roadmap and details of quantitative analyzing}
-To quantify and interpret the institutional effects, we followed the technical route illustrated in \textit{Supplementary Material Figure~\ref{fig:roadmap}}. It was a two-step process in which we
-% 基于数据使用合成控制法和安慰剂匹配法，创建可比的控制对照和期望（零模型）来分析制度变化对用水产生的影响。
-(i) created a comparable control group and an expectation (a “null model”) to analyze the impact of the institutional shifts on water use by using synthetic control and placebo matching methods, and
-% 创建一个基于边际收益的一般经济模型，解释我们发现的“冲刺效应”，并设计情景来进一步分析。
-(ii) created a general economic model based on marginal revenue to explain the “sprint effect” we observed and designed scenarios for further analysis.
-
-\begin{figure}[!hbt]
-    \centering
-    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/roadmap}
-    \caption{
-        Technical roadmap for quantitatively analyzing the “sprint effect”. WU is the the core variable we concerned -total water uses of the Yellow River Basin.
-    }
-    \label{fig:roadmap}
-\end{figure}
-
-% 为了使用合成控制法预测没有制度变化下的用水变化趋势，需要使用影响用水的社会经济数据作为自变量输入。
-In order to use the synthetic control method to predict the trend of water use without institutional change, socioeconomic data affecting water use were used as the input independent variables (see the \textit{Methods in the main text}).
-All variables used are listed in Table~\ref{tab:variables}.
-% 这些变量涉及了省级单元在利用水资源时需要考虑的主要经济因素（农业、工业、服务业与居民生活），它们与因变量（水资源使用）的相关性如图所示。
-These variables refer to major economic factors (agriculture, industry, service industry, and domestic) that provincial units need to take into account when using water resources; their correlation coefficients with the dependent variable (water resource use) are shown in Figure~\ref{fig:linear} A.
-
-% 此外，合成控制法有一个假设是自变量的线性组合可以有效预测因变量，因此我们还对数据线性拟合的效果进行了测试。
-In addition, the synthetic control method assumes that a linear combination of independent variables can effectively predict the dependent variables.
-% 将数据集区分为80%的训练样本和20%的测试样本，我们使用训练样本构建了多元线性模型对用水量进行了预测，并使用测试数据集去检验模型拟合效果。
-We therefore divided the dataset into two groups, training samples $(80\%)$ and test samples $(20\%)$, and used the training samples to build a multivariate linear model to predict the water consumption.
-We then used the test dataset to test the model-fitting effect.
-% 结果表明拟合优度R2超过了0.8，因变量可以很好的被自变量的线性组合所解释，该数据集可以用于控制合成法。
-Results show that the goodness of fit $R^2$ exceeded $0.8$; thus, the dependent variable is well-explained by the linear combination of independent variables, and the dataset can be used in the synthetic control method (Figure~\ref{fig:linear}B).
-% 为了估计用水量变化的期望值，我们对黄河流域各省用各自变量最接近的三个其它省（最近邻法）匹配了一个用作安慰剂实验的数据集
-To estimate the expected water use changes, we used the placebo test method as a null model (see the \textit{Methods}), which gives a comparable baseline for matched datasets.
-% 从图可以看出，匹配的数据集无论是数值还是变化趋势都与实际数据相似。
-Figure~\ref{fig:placebo} indicates that the matched dataset is similar to the actual data both in values and change trends.
-This means that the differences between the predictions made from actual data and from the matched data by the synthetic control method are more likely to be result of the impacts of institutional shifts.
-
-\begin{table}[!h]
-	\caption{Variables and their categories for water use predictions}
-	\scriptsize
-	\label{tab:variables}
-	\begin{tabular}{lllll}
-	\hline
-	Economic sector &
-	  Category &
-	  Unit &
-	  Description &
-	  Variables \\ \hline
-	Agriculture &
-	  Irrigation Area &
-	  thousand ha &
-	  \begin{tabular}[c]{@{}l@{}}Area equipped for irrgiation by different \\ crop:\end{tabular} &
-	  \begin{tabular}[c]{@{}l@{}}Rice, \\ Wheat, \\ Maize, \\ Fruits, \\ Others.\end{tabular} \\ \hline
-	Industry &
-	  \begin{tabular}[c]{@{}l@{}}Industrial gross \\ value added\end{tabular} &
-	  Billion Yuan &
-	  Industrial GVA by industries &
-	  \begin{tabular}[c]{@{}l@{}}Textile, \\ Papermaking, \\ Petrochemicals, \\ Metallurgy, \\ Mining, \\ Food, \\ Cements, \\ Machinery, \\ Electronics, \\ Thermal electrivity, \\ Others.\end{tabular} \\
-	 &
-	  \begin{tabular}[c]{@{}l@{}}Industrial water \\ use efficiency\end{tabular} &
-	  \% &
-	  \begin{tabular}[c]{@{}l@{}}The ratio of recycled water and evaporated \\ water to total industrial water use\end{tabular} &
-	  \begin{tabular}[c]{@{}l@{}}Ratio of industrial water recycling, \\ Ratio of industrial water evaporated.\end{tabular} \\ \hline
-	Services &
-	  \begin{tabular}[c]{@{}l@{}}Services gross \\ value added\end{tabular} &
-	  Billion Yuan &
-	  GVA of service activities &
-	  Services GVA \\ \hline
-	Domestic &
-	  Urban population &
-	  Million Capita &
-	  Population living in urban regions. &
-	  Urban pop \\
-	 &
-	  Rural population &
-	  Million Capita &
-	  Population living in rural regions. &
-	  Rural pop \\
-	 &
-	  Livestock population &
-	  Billion KJ &
-	  \begin{tabular}[c]{@{}l@{}}Livestock commodity calories summed from \\ 7 types of animal.\end{tabular} &
-	  Livestock \\ \hline
-	\end{tabular}
-\end{table}
-
-\begin{figure}[!thb]
-	\centering
-	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/linear}
-	\caption{
-		\textbf{A.} Correlation between independent variables and the dependent variable (water use).
-		\textbf{B.} Linear relationship between the independent variables and the dependent variable trained by a linear model.
-	}
-\label{fig:linear}
-\end{figure}
-
-\begin{figure}[!thb]
-	\centering
-	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/compared_placebo}
-	\caption{
-		\textbf{A.} A comparison of the matched placebo dataset and the actual YRB dataset for each province.
-		\textbf{B.} Trend of total water use $(10^8 m^3)$ for the matched placebo and actual datasets.
-	}
-\label{fig:placebo}
-\end{figure}
-
-\section*{S3. Further analysis regarding the general economic model}
-
-% 基于构建的一般经济学模型，我们对利益相关者面对用水配额政策的响应做了进一步探讨
-Using the general economic model (see the \textit{Methods in the main text}), we also explored the response of stakeholders to water quota policies.
-We considered two additional scenarios for stakeholders, one that considered technology growth and one that considered different valuations through time (via the discount rate) of economic benefits and ecological costs.
-In the following scenarios, the cost is assumed to be untransferable, which could be fully allocated to the one incurring the water use.
-Explaining plausible scenarios for these stakeholders will help us better understand the causes of the sprint effect and potential solutions.
-We argue that the sprint effect of water use remains robust even if a complete and equitable system.
-
-\subsection*{Growth in technology}
-
-Assume that there is an exogenous technology growth rate of $g$ in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$ and discount factor $\beta$.
-For simplicity, consider the following finite-period water use optimization:
-
-$ max \quad P \cdot (1+g)^t ln(1+x_{i,0})-\frac{C}{N}+\beta^t \begin{matrix} \sum_{t=1}^T [P \cdot (1+g)^t ln(x_{i,t}+1)-C \cdot x_{i,t}] \end{matrix}$
-
-$s.t. \quad x_{i,t} \leq Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \quad for \quad \forall t$
-
-We depict the relation between multi-period benefits and water use $x_{i0}$ in Figure~\ref{fig:tech_growth}to illustrate the optimal water use pattern under technology growth.
-The higher marginal benefits of water might create enough incentive to offset the untransferable costs of water overuse at $t=0$, because a higher allocated quota provides growth option value.
-Because provincial decisions are under a longer time horizon, there is a greater sprint effect due to the higher accumulated yield.
-
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=0.7\linewidth]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/tech_growth}
-	\caption{Multi-period benefits and optimal water use under technology growth and a quota system.
-The figure depicts the relationship of multi-period benefits of province $i$ and water use under Case 3 with technology growth under $T$ periods.
-Assume $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta=0.7$, $g=0.2$, and $Q=8$.
-The horizontal axis coordinates of $*$ denotes optimal water use at $t=0$ under each time horizon in decision-making.}
-	\label{fig:tech_growth}
-\end{figure}
-
-\subsection*{Economic benefits and ecological costs with different discount rate}
-
-Assume that there is high discount rate for economic benefits and a low discount rate for ecological costs, in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$, discount factor $\beta^{ecolomy}$ and $\beta^{ecology}$.
-It means that present economic profits are significantly concerned but future ecological costs are widely ignored.
-(In fact, if GDP are the core standard to judge officers’ performance, this is an assumption cloth to the reality.) For simplicity, consider the following finite-period water use optimization, notes the water use of province $i$ at period $t$:
-
-$$ max \quad P \cdot ln(1+x_{i,0})-\frac{C}{N}+\beta_{economy}^t \begin{matrix} \sum_{t=1}^T [P \cdot ln(x_{i,t}+1)]  \end{matrix} - \beta_{ecology}^t \begin{matrix} \sum_{t=1}^T [C \cdot x_{i,t}] \end{matrix}$$
-
-$$s.t. \quad x_{i,t} \leq Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \quad for \quad \forall t$$
-
-We depict the relation between multi-period benefits and water use xi0 in different time horizons in Figure~\ref{fig:remote_cost}, Using a higher discount rate for ecological costs might create enough incentive to set off the untransferable unit cost of $C$.
-Because the provincial decision is often under a longer horizon than that in baseline results in Figure 4 of the main text, there is a greater sprint effect as a result of higher accumulated yields.
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=0.7\linewidth]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/remote_ecological_cost}
-	\caption{Multi-period benefits and optimal water use when economic benefits have a high discount rate, ecological costs have a low discount rate, and a quota is implemented.
-The figure depicts the relation between multi-period benefits of province $i$ and water use under Case 3 under $T$ periods.
-Assume $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta_{economy}=0.7$, $\beta_{ecology}=0.3$, and $Q=8$.
-The horizontal axis coordinates of $*$ denotes optimal water use at $t=0$ under each time horizon in decision-making.
-	}
-	\label{fig:remote_cost}
-\end{figure}
-
-\bibliography{WAInstitution_YRB_2021}
-\end{document}

### 2022-03-20 docs/papers/tex/appendix/theoretical_model.tex
feat(paper): paper structure

--- 2022-03-04 docs/papers/tex/appendix.tex
@@
-\documentclass{article}
-\usepackage{hyperref}
-\usepackage{graphicx}
-\usepackage{setspace}
-\usepackage[a4paper, total={7in, 10in}]{geometry}
-
-\setstretch{1.523}
-
-\newtheorem{ass}{Assumption}
-\newtheorem{case}{Case}
-%% make sure you have the nature.cls and naturemag.bst files where
-%% LaTeX can find them
-
-\bibliographystyle{naturemag}
-
-\title{Supplementary Materials for
-
-Importance of social-ecological fit for water management in large river basins: An analysis of institutional shifts in the Yellow River Basin}
-
-%% Notice placement of commas and superscripts and use of &
-%% in the author list
-
-% \author{Shuang Song$^{1,2}$, Huiyu Wen$^3$, *Shuai Wang$^{1,2}$, Graeme S. Cumming$^{4}$ \& Bojie Fu$^{1, 2}$}
-
-\begin{document}
-
-\maketitle
-\input{../../drafts/authors.md}
-
-\begin{abstract}
-    % 这个补充材料以下述逻辑组织而成：
-    The supplementary material is organized logically as follows:
-    % 展示流域水资源分配制度在全球的推行情况并详细介绍黄河流域的制度变化，旨在说明黄河流域为什么是一个独一无二的准自然实验。
-    (1) Show the implementation of the water resource allocation system in the basin around the world and introduce the institutional changes in the Yellow River Basin in detail, aiming to explain why the Yellow River Basin is a unique quasi-natural experiment.
-    % 展示定量分析方法的技术路线图，并详细介绍定量分析方法中的细节部分。
-    (2) Show the technical roadmap of quantitative analysis method, and introduce the details of quantitative analysis method in detail.
-    % 基于我们建立的一般经济模型，对一些可能的情景进行进一步分析。
-    (3) Further extensions based on our general economic model.
-\end{abstract}
-
-\section*{S1. Detailed introduction of the institutions}
-% 水资源分配方案在全世界范围内都是流域管理的普遍制度。
-Water allocation schemes are widespread in large river basin management programs throughout the world (see \textit{Supplementary Material Figure~\ref{fig:world}}) \cite{speedBasinwaterallocation2013}.
-% 其中中国的黄河流域以典型的自上而下进行制度改革，这种模式会对制度产生迅速的影响，使我们能够定量地估计高层制度设计变化对用水的净影响。
-The Yellow River Basin (YRB) in China has a typical top-down approach to institutional reform, which produces rapid institutional impacts and allows researchers to quantitatively estimate the net impact of changes in high-level institutional design on water use (see \textit{Supplementary Material Figure~\ref{fig:framework}}).
-% 作为中国最早实施水资源分配制度的流域，黄河的制度变化可以在几个水利部发布的文件中得以窥见
-This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level):
-\begin{itemize}
-    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}.
-    \item \textbf{1987}: Implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
-    \item \textbf{1998}: Implementation of unified regulation.
-(\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
-    % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
-    \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}.
-    \item \textbf{2021}: A call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
-\end{itemize}
-
-\begin{figure}[!htb]
-    \centering
-    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/world_institutions}
-	\caption{
-		Overview of water allocation institutions.
-		% 世界已有水资源分配制度的大河流域，其中黄河流域最早于1987年提出资源分配方案，后于1998年更改为统一调度方案。
-		\textbf{A.} Major river basins in the world with existing water resource allocation systems (shaded red); the YRB first proposed a resource allocation scheme in 1987 (designed in 1983) and then changed to a unified regulation scheme in 1998 (designed in 1997 but implemented in 1998).
-		% 不同的水资源分配制度设计模式，中国黄河流域是典型的自上而下。
-		\textbf{B.} Different water resource allocation system design patterns; the YRB is typical of a top-down system with multiple levels.
-		% 流域分水制度的演化。这种多层次的制度设计有其历史变化过程。
-		\textbf{C.} The four periods of institutional evolution of water allocation of the YRB.
-	}
-    \label{fig:world}
-\end{figure}
-% 在上述文件中，1982年的文件标志着设计分水制度尝试的开始，2008年标志着该制度走向成熟（完全建立起流域-省-市区的多级水资源分配和统一调度）。
-The 1982 document marked the beginning of the attempt to design a water allocation institution, and the 2008 document marked the maturity of the system (complete establishment of basin-level, provincial, and district water allocation and unified regulation).
-Currently, a major overhaul is in the planning stages.
-Major shifts of the institution can be analyzed by using the 1987 and 1998 documents.
-It is worth noting that, although the essential reason for these institutions was the mismatch between the spatial and temporal distribution of water resources as well as social and economic water demands, the direct reason for their introduction was the drying-up of the Yellow River \cite{wangReviewImplementationYellow2019}.
-
-\textbf{The official documents in 1987 clearly convey the following key points:}
-\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today.
-\begin{itemize}
-	% 该政策面向的目标是各省（区域），黄委会没有被提及
-	\item The policy is aimed at related provinces (or regions), and the YRCC is not mentioned.
-	% 政策制定的首要考虑是解决断流问题
-	\item Drying-up of the river is identified as the first consideration of this institution.
-	% 各省被鼓励在此配额下制定自己的用水计划
-	\item Provinces are encouraged to develop their own water use plans based on a quota system.
-	% 水资源供给无法满足需求对相关省（地区）是普遍现象。
-	\item Water in short supply is a common phenomenon in relevant provinces (regions).
-\end{itemize}
-
-\textbf{The official documents in 1998 clearly convey the following key points:}
-\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today.
-\begin{itemize}
-	% 除了说明政策针对的各省区之外，明确指出其用水需要黄河水利委员会进行申报，并由其组织和监管
-	\item The document clearly points out that not only provinces and autonomous regions involved in water resources management (see \textit{Article 3}), the provinces’ and regions’ water use shall be declared, organized, and supervised by the YRCC (\textit{Article 11 and Chapter III to Chapter V, and Chapter VII}).
-	% 本研究(\textit{ Article 1})首先考虑的是上、中、下游用水的总体规划。
-	\item Creating the overall plan of water use in the upper, middle, and lower reaches is identified as the first consideration of this institution (\textit{Article 1}).
-	% 各省需要
-	\item With the same quota as used in the 1987 policy, provinces were encouraged to further distribute their quota into lower-level administrations (see \textit{Article 6 and Article 41}).
-	% 强调以总量确定供给，以供给决定需求。
-	\item They emphasize that supply is determined by total quantity, and water use should not exceed the quota proposed in 1987 (see \textit{Article 2}).
-\end{itemize}
-
-% 基于上述分析，我们抽象出了如正文图2中所展示的流域水资源分配制度的运行结构，并将研究时段选择在1975到2008之间。
-On the basis of the above analysis, we abstracted the operational structure of the water resource allocation institution of the YRB as shown in Figure 2 of the main text, focusing on the period between 1975 and 2008.
-By comparing the net effects of three different institutional structures split by the two institutional shifts, we were able to reach a stronger understanding of the influence of structural alignments under the same basin (previous structure-based analysis usually focus on a certain type of systems but with different geographic contexts).
-
-\begin{figure}[!htb]
-    \centering
-	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/YRB_scheme}
-	\caption{
-		% 中国自上而下的水资源分配制度模式（以黄河流域为例）
-		A top-down water resources allocation scheme in China (a case study of the YRB).
-		% 共有十个省或地区从黄河获取地表水资源，其中8个省的依赖性较强（see Supplementary Material Fig）。
-		\textbf{A.} A total of 10 provinces or regions withdraw surface water resources from the Yellow River, of which 8 are highly dependent on the river (see \textit{Supplementary Material S2}).
-		% 中国政府是下发流域管理政策的最高权威，其政策常常能够很快自上而下全面推行。
-		\textbf{B.} The Chinese government is the ultimate authority in issuing watershed management policies, which are often quickly implemented from top down.
-		% 流域管理机构（在黄河是黄河水利委员会）主要负责顺从国家的政策方针来进行流域的日常管理工作。
-		\textbf{C.} The basin-level agency (here, the YRCC) is primarily responsible for the river-related management of the basin in accordance with national policy guidelines.
-		% 利益相关者是各省
-		\textbf{D.} The water management system directly affects the process by which local governments (major stakeholders) plan and use water resources for development.
-Although only surface water (Sur.) is usually traced and restricted, it can also influence groundwater through related hydro-processes such as recharge.
-	}
-	\label{fig:framework}
-\end{figure}
-
-\section*{S2. The technical roadmap and details of quantitative analyzing}
-To quantify and interpret the institutional effects, we followed the technical route illustrated in \textit{Supplementary Material Figure~\ref{fig:roadmap}}. It was a two-step process in which we
-% 基于数据使用合成控制法和安慰剂匹配法，创建可比的控制对照和期望（零模型）来分析制度变化对用水产生的影响。
-(i) created a comparable control group and an expectation (a “null model”) to analyze the impact of the institutional shifts on water use by using synthetic control and placebo matching methods, and
-% 创建一个基于边际收益的一般经济模型，解释我们发现的“冲刺效应”，并设计情景来进一步分析。
-(ii) created a general economic model based on marginal revenue to explain the “sprint effect” we observed and designed scenarios for further analysis.
-
-\begin{figure}[!hbt]
-    \centering
-    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/roadmap}
-    \caption{
-        Technical roadmap for quantitatively analyzing the “sprint effect”. WU is the the core variable we concerned -total water uses of the Yellow River Basin.
-    }
-    \label{fig:roadmap}
-\end{figure}
-
-% 为了使用合成控制法预测没有制度变化下的用水变化趋势，需要使用影响用水的社会经济数据作为自变量输入。
-In order to use the synthetic control method to predict the trend of water use without institutional change, socioeconomic data affecting water use were used as the input independent variables (see the \textit{Methods in the main text}).
-All variables used are listed in Table~\ref{tab:variables}.
-% 这些变量涉及了省级单元在利用水资源时需要考虑的主要经济因素（农业、工业、服务业与居民生活），它们与因变量（水资源使用）的相关性如图所示。
-These variables refer to major economic factors (agriculture, industry, service industry, and domestic) that provincial units need to take into account when using water resources; their correlation coefficients with the dependent variable (water resource use) are shown in Figure~\ref{fig:linear} A.
-
-% 此外，合成控制法有一个假设是自变量的线性组合可以有效预测因变量，因此我们还对数据线性拟合的效果进行了测试。
-In addition, the synthetic control method assumes that a linear combination of independent variables can effectively predict the dependent variables.
-% 将数据集区分为80%的训练样本和20%的测试样本，我们使用训练样本构建了多元线性模型对用水量进行了预测，并使用测试数据集去检验模型拟合效果。
-We therefore divided the dataset into two groups, training samples $(80\%)$ and test samples $(20\%)$, and used the training samples to build a multivariate linear model to predict the water consumption.
-We then used the test dataset to test the model-fitting effect.
-% 结果表明拟合优度R2超过了0.8，因变量可以很好的被自变量的线性组合所解释，该数据集可以用于控制合成法。
-Results show that the goodness of fit $R^2$ exceeded $0.8$; thus, the dependent variable is well-explained by the linear combination of independent variables, and the dataset can be used in the synthetic control method (Figure~\ref{fig:linear}B).
-% 为了估计用水量变化的期望值，我们对黄河流域各省用各自变量最接近的三个其它省（最近邻法）匹配了一个用作安慰剂实验的数据集
-To estimate the expected water use changes, we used the placebo test method as a null model (see the \textit{Methods}), which gives a comparable baseline for matched datasets.
-% 从图可以看出，匹配的数据集无论是数值还是变化趋势都与实际数据相似。
-Figure~\ref{fig:placebo} indicates that the matched dataset is similar to the actual data both in values and change trends.
-This means that the differences between the predictions made from actual data and from the matched data by the synthetic control method are more likely to be result of the impacts of institutional shifts.
-
-\begin{table}[!h]
-	\caption{Variables and their categories for water use predictions}
-	\scriptsize
-	\label{tab:variables}
-	\begin{tabular}{lllll}
-	\hline
-	Economic sector &
-	  Category &
-	  Unit &
-	  Description &
-	  Variables \\ \hline
-	Agriculture &
-	  Irrigation Area &
-	  thousand ha &
-	  \begin{tabular}[c]{@{}l@{}}Area equipped for irrgiation by different \\ crop:\end{tabular} &
-	  \begin{tabular}[c]{@{}l@{}}Rice, \\ Wheat, \\ Maize, \\ Fruits, \\ Others.\end{tabular} \\ \hline
-	Industry &
-	  \begin{tabular}[c]{@{}l@{}}Industrial gross \\ value added\end{tabular} &
-	  Billion Yuan &
-	  Industrial GVA by industries &
-	  \begin{tabular}[c]{@{}l@{}}Textile, \\ Papermaking, \\ Petrochemicals, \\ Metallurgy, \\ Mining, \\ Food, \\ Cements, \\ Machinery, \\ Electronics, \\ Thermal electrivity, \\ Others.\end{tabular} \\
-	 &
-	  \begin{tabular}[c]{@{}l@{}}Industrial water \\ use efficiency\end{tabular} &
-	  \% &
-	  \begin{tabular}[c]{@{}l@{}}The ratio of recycled water and evaporated \\ water to total industrial water use\end{tabular} &
-	  \begin{tabular}[c]{@{}l@{}}Ratio of industrial water recycling, \\ Ratio of industrial water evaporated.\end{tabular} \\ \hline
-	Services &
-	  \begin{tabular}[c]{@{}l@{}}Services gross \\ value added\end{tabular} &
-	  Billion Yuan &
-	  GVA of service activities &
-	  Services GVA \\ \hline
-	Domestic &
-	  Urban population &
-	  Million Capita &
-	  Population living in urban regions. &
-	  Urban pop \\
-	 &
-	  Rural population &
-	  Million Capita &
-	  Population living in rural regions. &
-	  Rural pop \\
-	 &
-	  Livestock population &
-	  Billion KJ &
-	  \begin{tabular}[c]{@{}l@{}}Livestock commodity calories summed from \\ 7 types of animal.\end{tabular} &
-	  Livestock \\ \hline
-	\end{tabular}
-\end{table}
-
-\begin{figure}[!thb]
-	\centering
-	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/linear}
-	\caption{
-		\textbf{A.} Correlation between independent variables and the dependent variable (water use).
-		\textbf{B.} Linear relationship between the independent variables and the dependent variable trained by a linear model.
-	}
-\label{fig:linear}
-\end{figure}
-
-\begin{figure}[!thb]
-	\centering
-	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/compared_placebo}
-	\caption{
-		\textbf{A.} A comparison of the matched placebo dataset and the actual YRB dataset for each province.
-		\textbf{B.} Trend of total water use $(10^8 m^3)$ for the matched placebo and actual datasets.
-	}
-\label{fig:placebo}
-\end{figure}
-
-\section*{S3. Further analysis regarding the general economic model}
+%! Author = songshgeo
+%! Date = 2022/3/19
 
@@
 We considered two additional scenarios for stakeholders, one that considered technology growth and one that considered different valuations through time (via the discount rate) of economic benefits and ecological costs.
-In the following scenarios, the cost is assumed to be untransferable, which could be fully allocated to the one incurring the water use.
+In the following scenarios, the cost is assumed to be Nontransferable, which could be fully allocated to the one incurring the water use.
 Explaining plausible scenarios for these stakeholders will help us better understand the causes of the sprint effect and potential solutions.
@@
 
-$ max \quad P \cdot (1+g)^t ln(1+x_{i,0})-\frac{C}{N}+\beta^t \begin{matrix} \sum_{t=1}^T [P \cdot (1+g)^t ln(x_{i,t}+1)-C \cdot x_{i,t}] \end{matrix}$
+$ \max \quad P \cdot (1+g)^t \ln(1+x_{i,0})-\frac{C}{N}+\beta^t \begin{matrix} \sum_{t=1}^T [P \cdot (1+g)^t \ln(x_{i,t}+1)-C \cdot x_{i,t}] \end{matrix}$
 
@@
 We depict the relation between multi-period benefits and water use $x_{i0}$ in Figure~\ref{fig:tech_growth}to illustrate the optimal water use pattern under technology growth.
-The higher marginal benefits of water might create enough incentive to offset the untransferable costs of water overuse at $t=0$, because a higher allocated quota provides growth option value.
+The higher marginal benefits of water might create enough incentive to offset the nontransferable costs of water overuse at $t=0$, because a higher allocated quota provides growth option value.
 Because provincial decisions are under a longer time horizon, there is a greater sprint effect due to the higher accumulated yield.
@@
 The figure depicts the relationship of multi-period benefits of province $i$ and water use under Case 3 with technology growth under $T$ periods.
-Assume $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta=0.7$, $g=0.2$, and $Q=8$.
+Assume $F(x)=\ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta=0.7$, $g=0.2$, and $Q=8$.
 The horizontal axis coordinates of $*$ denotes optimal water use at $t=0$ under each time horizon in decision-making.}
@@
 
-Assume that there is high discount rate for economic benefits and a low discount rate for ecological costs, in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$, discount factor $\beta^{ecolomy}$ and $\beta^{ecology}$.
+Assume that there is high discount rate for economic benefits and a low discount rate for ecological costs, in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$, discount factor $\beta^{ecology}$ and $\beta^{ecology}$.
 It means that present economic profits are significantly concerned but future ecological costs are widely ignored.
@@
 
-$$ max \quad P \cdot ln(1+x_{i,0})-\frac{C}{N}+\beta_{economy}^t \begin{matrix} \sum_{t=1}^T [P \cdot ln(x_{i,t}+1)]  \end{matrix} - \beta_{ecology}^t \begin{matrix} \sum_{t=1}^T [C \cdot x_{i,t}] \end{matrix}$$
+\[ \max \quad P \cdot \ln(1+x_{i,0})-\frac{C}{N}+\beta_{economy}^t \begin{matrix} \sum_{t=1}^T [P \cdot \ln(x_{i,t}+1)]  \end{matrix} - \beta_{ecology}^t \begin{matrix} \sum_{t=1}^T [C \cdot x_{i,t}] \end{matrix}\]
 
-$$s.t. \quad x_{i,t} \leq Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \quad for \quad \forall t$$
+\[s.t. \quad x_{i,t} \leq Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \quad for \quad \forall t\]
 
-We depict the relation between multi-period benefits and water use xi0 in different time horizons in Figure~\ref{fig:remote_cost}, Using a higher discount rate for ecological costs might create enough incentive to set off the untransferable unit cost of $C$.
+We depict the relation between multi-period benefits and water use xi0 in different time horizons in Figure~\ref{fig:remote_cost}, Using a higher discount rate for ecological costs might create enough incentive to set off the nontransferable unit cost of $C$.
 Because the provincial decision is often under a longer horizon than that in baseline results in Figure 4 of the main text, there is a greater sprint effect as a result of higher accumulated yields.
@@
 The figure depicts the relation between multi-period benefits of province $i$ and water use under Case 3 under $T$ periods.
-Assume $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta_{economy}=0.7$, $\beta_{ecology}=0.3$, and $Q=8$.
+Assume $F(x)=\ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta_{economy}=0.7$, $\beta_{ecology}=0.3$, and $Q=8$.
 The horizontal axis coordinates of $*$ denotes optimal water use at $t=0$ under each time horizon in decision-making.
@@
 \end{figure}
-
-\bibliography{WAInstitution_YRB_2021}
-\end{document}

### 2022-03-20 docs/papers/tex/previous_appendix.tex
feat(paper): paper structure

--- 2022-03-04 docs/papers/tex/appendix.tex
@@
 \usepackage[a4paper, total={7in, 10in}]{geometry}
+\usepackage{amsmath}
 
@@
 
-Importance of social-ecological fit for water management in large river basins: An analysis of institutional shifts in the Yellow River Basin}
+\input{../title.tex}}
 
@@
 \maketitle
-\input{../../drafts/authors.md}
+\input{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/docs/papers/authors.md}
 
@@
 \section*{S1. Detailed introduction of the institutions}
-% 水资源分配方案在全世界范围内都是流域管理的普遍制度。
-Water allocation schemes are widespread in large river basin management programs throughout the world (see \textit{Supplementary Material Figure~\ref{fig:world}}) \cite{speedBasinwaterallocation2013}.
-% 其中中国的黄河流域以典型的自上而下进行制度改革，这种模式会对制度产生迅速的影响，使我们能够定量地估计高层制度设计变化对用水的净影响。
-The Yellow River Basin (YRB) in China has a typical top-down approach to institutional reform, which produces rapid institutional impacts and allows researchers to quantitatively estimate the net impact of changes in high-level institutional design on water use (see \textit{Supplementary Material Figure~\ref{fig:framework}}).
-% 作为中国最早实施水资源分配制度的流域，黄河的制度变化可以在几个水利部发布的文件中得以窥见
-This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level):
-\begin{itemize}
-    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}.
-    \item \textbf{1987}: Implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
-    \item \textbf{1998}: Implementation of unified regulation.
-(\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
-    % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
-    \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}.
-    \item \textbf{2021}: A call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
-\end{itemize}
-
-\begin{figure}[!htb]
-    \centering
-    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/world_institutions}
-	\caption{
-		Overview of water allocation institutions.
-		% 世界已有水资源分配制度的大河流域，其中黄河流域最早于1987年提出资源分配方案，后于1998年更改为统一调度方案。
-		\textbf{A.} Major river basins in the world with existing water resource allocation systems (shaded red); the YRB first proposed a resource allocation scheme in 1987 (designed in 1983) and then changed to a unified regulation scheme in 1998 (designed in 1997 but implemented in 1998).
-		% 不同的水资源分配制度设计模式，中国黄河流域是典型的自上而下。
-		\textbf{B.} Different water resource allocation system design patterns; the YRB is typical of a top-down system with multiple levels.
-		% 流域分水制度的演化。这种多层次的制度设计有其历史变化过程。
-		\textbf{C.} The four periods of institutional evolution of water allocation of the YRB.
-	}
-    \label{fig:world}
-\end{figure}
-% 在上述文件中，1982年的文件标志着设计分水制度尝试的开始，2008年标志着该制度走向成熟（完全建立起流域-省-市区的多级水资源分配和统一调度）。
-The 1982 document marked the beginning of the attempt to design a water allocation institution, and the 2008 document marked the maturity of the system (complete establishment of basin-level, provincial, and district water allocation and unified regulation).
-Currently, a major overhaul is in the planning stages.
-Major shifts of the institution can be analyzed by using the 1987 and 1998 documents.
-It is worth noting that, although the essential reason for these institutions was the mismatch between the spatial and temporal distribution of water resources as well as social and economic water demands, the direct reason for their introduction was the drying-up of the Yellow River \cite{wangReviewImplementationYellow2019}.
-
-\textbf{The official documents in 1987 clearly convey the following key points:}
-\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today.
-\begin{itemize}
-	% 该政策面向的目标是各省（区域），黄委会没有被提及
-	\item The policy is aimed at related provinces (or regions), and the YRCC is not mentioned.
-	% 政策制定的首要考虑是解决断流问题
-	\item Drying-up of the river is identified as the first consideration of this institution.
-	% 各省被鼓励在此配额下制定自己的用水计划
-	\item Provinces are encouraged to develop their own water use plans based on a quota system.
-	% 水资源供给无法满足需求对相关省（地区）是普遍现象。
-	\item Water in short supply is a common phenomenon in relevant provinces (regions).
-\end{itemize}
-
-\textbf{The official documents in 1998 clearly convey the following key points:}
-\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today.
-\begin{itemize}
-	% 除了说明政策针对的各省区之外，明确指出其用水需要黄河水利委员会进行申报，并由其组织和监管
-	\item The document clearly points out that not only provinces and autonomous regions involved in water resources management (see \textit{Article 3}), the provinces’ and regions’ water use shall be declared, organized, and supervised by the YRCC (\textit{Article 11 and Chapter III to Chapter V, and Chapter VII}).
-	% 本研究(\textit{ Article 1})首先考虑的是上、中、下游用水的总体规划。
-	\item Creating the overall plan of water use in the upper, middle, and lower reaches is identified as the first consideration of this institution (\textit{Article 1}).
-	% 各省需要
-	\item With the same quota as used in the 1987 policy, provinces were encouraged to further distribute their quota into lower-level administrations (see \textit{Article 6 and Article 41}).
-	% 强调以总量确定供给，以供给决定需求。
-	\item They emphasize that supply is determined by total quantity, and water use should not exceed the quota proposed in 1987 (see \textit{Article 2}).
-\end{itemize}
-
-% 基于上述分析，我们抽象出了如正文图2中所展示的流域水资源分配制度的运行结构，并将研究时段选择在1975到2008之间。
-On the basis of the above analysis, we abstracted the operational structure of the water resource allocation institution of the YRB as shown in Figure 2 of the main text, focusing on the period between 1975 and 2008.
-By comparing the net effects of three different institutional structures split by the two institutional shifts, we were able to reach a stronger understanding of the influence of structural alignments under the same basin (previous structure-based analysis usually focus on a certain type of systems but with different geographic contexts).
-
-\begin{figure}[!htb]
-    \centering
-	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/YRB_scheme}
-	\caption{
-		% 中国自上而下的水资源分配制度模式（以黄河流域为例）
-		A top-down water resources allocation scheme in China (a case study of the YRB).
-		% 共有十个省或地区从黄河获取地表水资源，其中8个省的依赖性较强（see Supplementary Material Fig）。
-		\textbf{A.} A total of 10 provinces or regions withdraw surface water resources from the Yellow River, of which 8 are highly dependent on the river (see \textit{Supplementary Material S2}).
-		% 中国政府是下发流域管理政策的最高权威，其政策常常能够很快自上而下全面推行。
-		\textbf{B.} The Chinese government is the ultimate authority in issuing watershed management policies, which are often quickly implemented from top down.
-		% 流域管理机构（在黄河是黄河水利委员会）主要负责顺从国家的政策方针来进行流域的日常管理工作。
-		\textbf{C.} The basin-level agency (here, the YRCC) is primarily responsible for the river-related management of the basin in accordance with national policy guidelines.
-		% 利益相关者是各省
-		\textbf{D.} The water management system directly affects the process by which local governments (major stakeholders) plan and use water resources for development.
-Although only surface water (Sur.) is usually traced and restricted, it can also influence groundwater through related hydro-processes such as recharge.
-	}
-	\label{fig:framework}
-\end{figure}
+\input{../appendix/institution_context.tex}
 
 \section*{S2. The technical roadmap and details of quantitative analyzing}
-To quantify and interpret the institutional effects, we followed the technical route illustrated in \textit{Supplementary Material Figure~\ref{fig:roadmap}}. It was a two-step process in which we
-% 基于数据使用合成控制法和安慰剂匹配法，创建可比的控制对照和期望（零模型）来分析制度变化对用水产生的影响。
-(i) created a comparable control group and an expectation (a “null model”) to analyze the impact of the institutional shifts on water use by using synthetic control and placebo matching methods, and
-% 创建一个基于边际收益的一般经济模型，解释我们发现的“冲刺效应”，并设计情景来进一步分析。
-(ii) created a general economic model based on marginal revenue to explain the “sprint effect” we observed and designed scenarios for further analysis.
-
-\begin{figure}[!hbt]
-    \centering
-    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/roadmap}
-    \caption{
-        Technical roadmap for quantitatively analyzing the “sprint effect”. WU is the the core variable we concerned -total water uses of the Yellow River Basin.
-    }
-    \label{fig:roadmap}
-\end{figure}
-
-% 为了使用合成控制法预测没有制度变化下的用水变化趋势，需要使用影响用水的社会经济数据作为自变量输入。
-In order to use the synthetic control method to predict the trend of water use without institutional change, socioeconomic data affecting water use were used as the input independent variables (see the \textit{Methods in the main text}).
-All variables used are listed in Table~\ref{tab:variables}.
-% 这些变量涉及了省级单元在利用水资源时需要考虑的主要经济因素（农业、工业、服务业与居民生活），它们与因变量（水资源使用）的相关性如图所示。
-These variables refer to major economic factors (agriculture, industry, service industry, and domestic) that provincial units need to take into account when using water resources; their correlation coefficients with the dependent variable (water resource use) are shown in Figure~\ref{fig:linear} A.
-
-% 此外，合成控制法有一个假设是自变量的线性组合可以有效预测因变量，因此我们还对数据线性拟合的效果进行了测试。
-In addition, the synthetic control method assumes that a linear combination of independent variables can effectively predict the dependent variables.
-% 将数据集区分为80%的训练样本和20%的测试样本，我们使用训练样本构建了多元线性模型对用水量进行了预测，并使用测试数据集去检验模型拟合效果。
-We therefore divided the dataset into two groups, training samples $(80\%)$ and test samples $(20\%)$, and used the training samples to build a multivariate linear model to predict the water consumption.
-We then used the test dataset to test the model-fitting effect.
-% 结果表明拟合优度R2超过了0.8，因变量可以很好的被自变量的线性组合所解释，该数据集可以用于控制合成法。
-Results show that the goodness of fit $R^2$ exceeded $0.8$; thus, the dependent variable is well-explained by the linear combination of independent variables, and the dataset can be used in the synthetic control method (Figure~\ref{fig:linear}B).
-% 为了估计用水量变化的期望值，我们对黄河流域各省用各自变量最接近的三个其它省（最近邻法）匹配了一个用作安慰剂实验的数据集
-To estimate the expected water use changes, we used the placebo test method as a null model (see the \textit{Methods}), which gives a comparable baseline for matched datasets.
-% 从图可以看出，匹配的数据集无论是数值还是变化趋势都与实际数据相似。
-Figure~\ref{fig:placebo} indicates that the matched dataset is similar to the actual data both in values and change trends.
-This means that the differences between the predictions made from actual data and from the matched data by the synthetic control method are more likely to be result of the impacts of institutional shifts.
-
-\begin{table}[!h]
-	\caption{Variables and their categories for water use predictions}
-	\scriptsize
-	\label{tab:variables}
-	\begin{tabular}{lllll}
-	\hline
-	Economic sector &
-	  Category &
-	  Unit &
-	  Description &
-	  Variables \\ \hline
-	Agriculture &
-	  Irrigation Area &
-	  thousand ha &
-	  \begin{tabular}[c]{@{}l@{}}Area equipped for irrgiation by different \\ crop:\end{tabular} &
-	  \begin{tabular}[c]{@{}l@{}}Rice, \\ Wheat, \\ Maize, \\ Fruits, \\ Others.\end{tabular} \\ \hline
-	Industry &
-	  \begin{tabular}[c]{@{}l@{}}Industrial gross \\ value added\end{tabular} &
-	  Billion Yuan &
-	  Industrial GVA by industries &
-	  \begin{tabular}[c]{@{}l@{}}Textile, \\ Papermaking, \\ Petrochemicals, \\ Metallurgy, \\ Mining, \\ Food, \\ Cements, \\ Machinery, \\ Electronics, \\ Thermal electrivity, \\ Others.\end{tabular} \\
-	 &
-	  \begin{tabular}[c]{@{}l@{}}Industrial water \\ use efficiency\end{tabular} &
-	  \% &
-	  \begin{tabular}[c]{@{}l@{}}The ratio of recycled water and evaporated \\ water to total industrial water use\end{tabular} &
-	  \begin{tabular}[c]{@{}l@{}}Ratio of industrial water recycling, \\ Ratio of industrial water evaporated.\end{tabular} \\ \hline
-	Services &
-	  \begin{tabular}[c]{@{}l@{}}Services gross \\ value added\end{tabular} &
-	  Billion Yuan &
-	  GVA of service activities &
-	  Services GVA \\ \hline
-	Domestic &
-	  Urban population &
-	  Million Capita &
-	  Population living in urban regions. &
-	  Urban pop \\
-	 &
-	  Rural population &
-	  Million Capita &
-	  Population living in rural regions. &
-	  Rural pop \\
-	 &
-	  Livestock population &
-	  Billion KJ &
-	  \begin{tabular}[c]{@{}l@{}}Livestock commodity calories summed from \\ 7 types of animal.\end{tabular} &
-	  Livestock \\ \hline
-	\end{tabular}
-\end{table}
-
-\begin{figure}[!thb]
-	\centering
-	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/linear}
-	\caption{
-		\textbf{A.} Correlation between independent variables and the dependent variable (water use).
-		\textbf{B.} Linear relationship between the independent variables and the dependent variable trained by a linear model.
-	}
-\label{fig:linear}
-\end{figure}
-
-\begin{figure}[!thb]
-	\centering
-	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/compared_placebo}
-	\caption{
-		\textbf{A.} A comparison of the matched placebo dataset and the actual YRB dataset for each province.
-		\textbf{B.} Trend of total water use $(10^8 m^3)$ for the matched placebo and actual datasets.
-	}
-\label{fig:placebo}
-\end{figure}
+\input{../appendix/method_details.tex}
 
 \section*{S3. Further analysis regarding the general economic model}
-
-% 基于构建的一般经济学模型，我们对利益相关者面对用水配额政策的响应做了进一步探讨
-Using the general economic model (see the \textit{Methods in the main text}), we also explored the response of stakeholders to water quota policies.
-We considered two additional scenarios for stakeholders, one that considered technology growth and one that considered different valuations through time (via the discount rate) of economic benefits and ecological costs.
-In the following scenarios, the cost is assumed to be untransferable, which could be fully allocated to the one incurring the water use.
-Explaining plausible scenarios for these stakeholders will help us better understand the causes of the sprint effect and potential solutions.
-We argue that the sprint effect of water use remains robust even if a complete and equitable system.
-
-\subsection*{Growth in technology}
-
-Assume that there is an exogenous technology growth rate of $g$ in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$ and discount factor $\beta$.
-For simplicity, consider the following finite-period water use optimization:
-
-$ max \quad P \cdot (1+g)^t ln(1+x_{i,0})-\frac{C}{N}+\beta^t \begin{matrix} \sum_{t=1}^T [P \cdot (1+g)^t ln(x_{i,t}+1)-C \cdot x_{i,t}] \end{matrix}$
-
-$s.t. \quad x_{i,t} \leq Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \quad for \quad \forall t$
-
-We depict the relation between multi-period benefits and water use $x_{i0}$ in Figure~\ref{fig:tech_growth}to illustrate the optimal water use pattern under technology growth.
-The higher marginal benefits of water might create enough incentive to offset the untransferable costs of water overuse at $t=0$, because a higher allocated quota provides growth option value.
-Because provincial decisions are under a longer time horizon, there is a greater sprint effect due to the higher accumulated yield.
-
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=0.7\linewidth]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/tech_growth}
-	\caption{Multi-period benefits and optimal water use under technology growth and a quota system.
-The figure depicts the relationship of multi-period benefits of province $i$ and water use under Case 3 with technology growth under $T$ periods.
-Assume $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta=0.7$, $g=0.2$, and $Q=8$.
-The horizontal axis coordinates of $*$ denotes optimal water use at $t=0$ under each time horizon in decision-making.}
-	\label{fig:tech_growth}
-\end{figure}
-
-\subsection*{Economic benefits and ecological costs with different discount rate}
-
-Assume that there is high discount rate for economic benefits and a low discount rate for ecological costs, in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$, discount factor $\beta^{ecolomy}$ and $\beta^{ecology}$.
-It means that present economic profits are significantly concerned but future ecological costs are widely ignored.
-(In fact, if GDP are the core standard to judge officers’ performance, this is an assumption cloth to the reality.) For simplicity, consider the following finite-period water use optimization, notes the water use of province $i$ at period $t$:
-
-$$ max \quad P \cdot ln(1+x_{i,0})-\frac{C}{N}+\beta_{economy}^t \begin{matrix} \sum_{t=1}^T [P \cdot ln(x_{i,t}+1)]  \end{matrix} - \beta_{ecology}^t \begin{matrix} \sum_{t=1}^T [C \cdot x_{i,t}] \end{matrix}$$
-
-$$s.t. \quad x_{i,t} \leq Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \quad for \quad \forall t$$
-
-We depict the relation between multi-period benefits and water use xi0 in different time horizons in Figure~\ref{fig:remote_cost}, Using a higher discount rate for ecological costs might create enough incentive to set off the untransferable unit cost of $C$.
-Because the provincial decision is often under a longer horizon than that in baseline results in Figure 4 of the main text, there is a greater sprint effect as a result of higher accumulated yields.
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=0.7\linewidth]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/remote_ecological_cost}
-	\caption{Multi-period benefits and optimal water use when economic benefits have a high discount rate, ecological costs have a low discount rate, and a quota is implemented.
-The figure depicts the relation between multi-period benefits of province $i$ and water use under Case 3 under $T$ periods.
-Assume $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta_{economy}=0.7$, $\beta_{ecology}=0.3$, and $Q=8$.
-The horizontal axis coordinates of $*$ denotes optimal water use at $t=0$ under each time horizon in decision-making.
-	}
-	\label{fig:remote_cost}
-\end{figure}
+\input{../appendix/theoretical_model.tex}
 

### 2022-03-20 docs/papers/01_manuscript/01_introduction.tex
testing

Emerging competition for water is an urgent problem in water governance, with widespread water scarcity and overuse resulting in huge impacts on economies, societies, and ecosystems \cite{gleickPeakwaterlimits2010,dolanEvaluatingeconomicimpact2021,siwiCompetitionWaterGetting,ziolkowskaCompetitionWaterResources2016,distefanoArewedeep2017}.
Water is the key exclusive and competitive resource that couples socioeconomic and ecological systems (known as common-pool resources, CPRs) \cite{wutichWaterScarcitySustainability2009,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017,castilla-rhoGroundwaterCommonPool2020}.
Conflicts of interest often occur in allocation and competitions of water resources, with water governance policies often leading to long-term changes in human–water relationships and the redistribution of benefits \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013,chingManagingsocioecologyvery2015}.
Although governments in many of the world’s large river basins have tried to resolve competition for water through the deliberate design of new institutions, general principles underlying the successes and failures of these initiatives are poorly documented and understood.

Institutions (such as policies, laws, and norms) can influence regional sustainability by changing social-ecological system (SES) structure and dynamics \cite{youngInstitutionsenvironmentalchange2008,cummingAdvancingunderstandingnatural2020,lieninstitutionalgrammartool2020}.
These include inter-relationships and interactions between social actors, between ecological units, or between social and ecological system elements \cite{bodinCollaborativeenvironmentalgovernance2017,barnesSocialecologicalalignmentecological2019}.
Effective (“matched”) institutions operate at appropriate spatial, temporal, and functional scales to manage and balance these different relationships and interactions \cite{heWateringEnvironmentalRegulation2020,kellenbergempiricalinvestigationpollution2009}.
From the perspective of SES outcomes, matched institutions support (but do not guarantee) sustainability \cite{epsteinInstitutionalfitsustainability2015,wangAlignmentsocialecological2019}.

Some kinds of institutions have been shown to support desirable outcomes in water-centered SESs (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wangAlignmentsocialecological2019} and in collaborative water governance systems in Europe \cite{greenEUWaterGovernance2013}).
At the same time, undesired and unsustainable outcomes (e.g., failures in environmental regulation of highly polluting industries or the development of “tragedy of the commons” situations when pursuing more water resources), with considerable ecological degradation, have attracted much attention \cite{saylesSocialecologicalnetworkanalysis2019,caiPollutingthyneighbor2016,castilla-rhoSocialtippingpoints2017}.
Despite widespread recognition of the rising importance of integrated water resource management in solving water competition in the world’s large river basins, relatively few studies have explored the mechanisms by which SESs respond to new institutions \cite{agrawalSustainableGovernanceCommonPool2003,pershaSocialEcologicalSynergy2011,agrawalCommonPropertyInstitutions2001}.
Two particular weaknesses in existing knowledge include understanding (1) the causal links between SES structures and outcomes; and (2) details of the underlying processes, especially the coordination of the incentives of different participants, that result from an institutional lack of fit. These weaknesses limit our understanding of institutional design, and they may reduce the speed and transfer of new knowledge and experience related to improving the sustainability of comprehensive water resources management.

In order to disentangle the relationship between SES structure and outcomes, we analyzed a case study to show how an institutional shift led to a structural mismatch that triggered unsustainable water use and unintended ecological deterioration. Two rapid shifts in institutional structure that occurred in 1987 and 1998 (see Supplementary Material S1) provide unique settings to exploit quasi-natural experiments of a large river basin, the Yellow River Basin (YRB) in China \cite{xiaDevelopmentWaterAllocation2012}. After a period of severe drying up, an institutional shift implemented in 1987 represented the beginning of attempts to control water use in the YRB through the use of quotas, with the goals of alleviating conflicts between supply and demand and achieving sustainable development.

Our results show that this initiative actually accelerated water withdrawals, resulting in an unintended “sprint effect”, where institutional mismatches created an even stronger incentive for each resource user to withdraw resources until the next major institutional shift in 1998. Our analysis contributes to a deeper understanding of the mechanisms underlying the relationships among institutions, SES structures, and outcomes. By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings are consistent with the urgent calls for a more dynamic design for water use allocation to achieve sustainability.

\section{Institutions and SES structures}
% 机构可以塑造社会经济体系的结构，对其进行抽象是机械地理解结构和结果之间联系的第一步。
Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{fig:framework}A).
% 例如，机构可以创建一种被确定为与良好的社会经济效益相关联的水平匹配结构，如果它鼓励管理相连生态成分的不同行动者之间的协作(图1B)。
For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{fig:framework}B), leading to sustainable outcomes.
% 例如，机构可以创建一个结构，鼓励不同行为者之间的合作，管理相连的生态成分
Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{fig:framework}C and D).
% 在实践中，一个大型、复杂的河流流域的制度变化将创造或摧毁数百种不同的联系。这些局部变化的更广泛影响可以从系统的整体行为中看到。
In practice, institutional changes in a large, complex river basin will create or destroy hundreds of different connections. The broader impacts of these local changes can be seen in the overall behavior of the system.
% 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
We thus explored the causal linkages between the SES structures and sustainability (outcomes) in quasi-natural experiments of the YRB, which provides an informative case study for two main reasons.
% 首先，长江流域管理的急剧结构变化使我们能够定量估计高层制度设计变化对用水的净影响。决定水分配的制度包括自下而上的协议或社会规范，以及自上而下的配额或法规，它们对社会经济结构有不同的影响;自上而下的监管可能会立即引发制度转变和SES的剧烈结构性变化。通过与由自下而上的制度转变引起的更渐进的变化相比，探索自上而下变化的影响，在对社会经济地位的定量分析中，极大地减少了来自不可观测因素的潜在干扰，提高了社会经济地位结构和结果之间因果关系的清晰度。
First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use. Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013}; top-down regulations can trigger immediate institutional shifts and sharp SES structural changes \cite{speedBasinwaterallocation2013,rolandUnderstandinginstitutionalchange2004}.
In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and improves the clarity of the causal link between SES structure and outcome.
% 其次，通过比较长江流域两次制度变迁所分裂的三种不同制度结构的净效应，我们也可以更深入地理解“盆地固定效应”下结构格局的影响。尽管流域内的社会经济单位从世界各地的大型河流流域和许多地区的水资源中受益，但很少有流域多次经历过如此激进的社会经济结构变化。
Second, by comparing the net effects of three different institutional structures split by two institutional shifts in the YRB, we can also reach a stronger understanding of the influence of structural alignments under a fixed basin. Although socioeconomic units within a basin benefit from water resources in large river basins all over the world and many locations have shown increased levels of regulation, few basins have experienced such radical SES structural changes several times (see \textit{Supplementary Material} S1). Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in SES institutional structure.
% 因此，黄河流域的“流域固定效应”为SES结构的自我比较提供了宝贵的机会。
% Thus, the YRB provides valuable settings for understanding the direct impacts of changes in SES institutional structure.

### 2022-03-20 docs/papers/01_manuscript/04_discussion.tex
testing

%! Author = songshgeo
%! Date = 2022/3/10
% 我们展示了不匹配的分配制度是如何导致激励失真导致水资源加速耗竭的(即“冲刺效应”)。“冲刺效应”是CPR系统面临的一种特殊情况，在这种情况下，制度的不匹配为每个资源使用者创造了更强的动机(扭曲)，促使他们收回资源
We have shown how a mismatched allocation institution can lead to an accelerated depletion of water resources (i.e., the “sprint effect”) caused by incentive distortion. The sprint effect is a special case faced by CPR systems, where institutional mismatches create an even stronger incentive (with distortion) for each resource user to withdraw resources
\cite{ostromRevisitingCommonsLocal1999,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017}.
% 过往研究指出制度常常是避免公共池塘资源系统的崩溃的关键，但“短跑效应”的出现表明在自上而下进行制度设计所形成的错配SES结构中，制度也可以成为系统加速崩溃的触发者。
Previous studies have suggested that institutions are often the key to avoid the collapse of a CPR system, but the emergence of a sprint effect shows that an institution with structural mismatches can also be the trigger that accelerates system collapse \cite{bodinConservationSuccessFunction2014,bodinCollaborativeenvironmentalgovernance2017,wangAlignmentsocialecological2019}.
The initial formulation of the water quota in our case studies went through a stage of “bargaining” among stakeholders (from 1982 to 1987) \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}, where each province attempted to demonstrate its development potential related to water use.
% 在高层决策者与低层利益相关者之间存在信息不对称的用水分配中，当前用水量越大的利益相关者议价能力越大。1987年以后，对各省来说，合乎逻辑的下一步是试图证明争取更大配额的合理性，而不是立即采取资源节约型改革。在实践中，尽管受影响的省份可能没有直接鼓励过度使用资源，但由于激励扭曲，他们有更大的动机对资源提取开绿灯。因此，在争夺潜在的水资源配额时，各省往往将生态成本隐藏在经济发展背后。
In water use allocation with information asymmetry between upper-level decision-makers and lower-level stakeholders, those with more current water use might have greater bargaining power. After 1987, the logical next step for provinces was to attempt to justify bargaining for larger quotas rather than immediately adopt resource-conserving transformations. In practice, although the affected provinces may not have directly encouraged excessive resource use, they had a greater incentive to give the green light to resource withdrawals because of incentive distortions \cite{kriegerProgressGroundWater1955, ostromGoverningCommonsEvolution1990}. As a result, while competing for potential water quotas, the provinces tended to hide the ecological costs behind economic development.

% 毫无疑问，随着资源竞争的日趋激烈，越来越多的SES正依赖着不同形式的制度进行资源分配（如自组织和政府干预），避免“短跑效应”的出现或将成为制度设计的关键。
There is no doubt that with increasingly fierce competition for water, more and more SESs are developing new institutions for water allocation (whether through self-organization or government intervention) \cite{anderssonVoluntaryleadershipemergence2020, wutichWaterScarcitySustainability2009}.
% 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
Adoption of an overall quota plays an important role in preventing overuse of CPRs \cite{tilmanLocalizedprosocialpreferences2019}.
However, the negative effects of incentive distortion imply a trade-off between long-term SES benefits and current stability, and the proportion of available resources allocated under quota schemes matters when institutions change \cite{ladeRegimeshiftssocialecological2013}.
According to our analysis of plausible scenario assumptions based on our general economic model, the sprint effect will be reinforced when stakeholders anticipate that technological advances will amplify the benefits of water quotas in the future (see \textit{Supplementary Material S3}).
% 然而，如果有水权转换机制允许利益相关者之间通过交易来弥补 shadow value，当前这种错乱的动机就不会那么强。
However, if an institution allowed stakeholders to compensate for the shadow value (i.e., potential returns sacrificed due to water constraints and water scarcity) \cite{howarthAccountingvalueecosystem2002} of future water use, incentive distortion would be less devastating (e.g., through water rights transfer).
Policymakers can also weaken the sprint effect by increasing the frequency of quota updates, supporting the idea that a more dynamic institution that responds to changing conditions (see \textit{Supplementary Material S3}) will adapt more effectively to its social-ecological context.

% 近年来黄河流域面临的分水制度调整问题也说明了动态设置配额的重要性。
Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of dynamic quota setting (see \textit{Supplementary Material S1}) \cite{yuAdaptabilityassessmentpromotion2019}. Following the institutional reforms of 1998, the Yellow River has not dried up since 1999. However, given recent changes in the YRB, its rigid resource allocation scheme can no longer meet the new demands of economic development \cite{wangThingsCurrentSignificance2019}. The Chinese government has embarked on an ambitious plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}). Other SESs around the world face similar problems in establishing successful resource allocation institutions \cite{cummingQuantifyingSocialEcologicalScale2020, muneepeerakulStrategicbehaviorsgovernance2017, cummingAdvancingunderstandingnatural2020, leslieOperationalizingsocialecologicalsystems2015}. These initiatives can benefit from our analysis by actively considering and incorporating social-ecological complexity and incentive structures when developing new approaches that avoid unsustainable outcomes. Our research provides a cautionary tale of how institutions can act as a double-edged sword when trying to attain sustainability.

### 2022-03-20 docs/papers/02_appendix/02_method_details.tex
testing

--- 2022-03-04 docs/papers/tex/appendix.tex
@@
-\documentclass{article}
-\usepackage{hyperref}
-\usepackage{graphicx}
-\usepackage{setspace}
-\usepackage[a4paper, total={7in, 10in}]{geometry}
+%! Author = songshgeo
+%! Date = 2022/3/19
 
-\setstretch{1.523}
-
-\newtheorem{ass}{Assumption}
-\newtheorem{case}{Case}
-%% make sure you have the nature.cls and naturemag.bst files where
-%% LaTeX can find them
-
-\bibliographystyle{naturemag}
-
-\title{Supplementary Materials for
-
-Importance of social-ecological fit for water management in large river basins: An analysis of institutional shifts in the Yellow River Basin}
-
-%% Notice placement of commas and superscripts and use of &
-%% in the author list
-
-% \author{Shuang Song$^{1,2}$, Huiyu Wen$^3$, *Shuai Wang$^{1,2}$, Graeme S. Cumming$^{4}$ \& Bojie Fu$^{1, 2}$}
-
-\begin{document}
-
-\maketitle
-\input{../../drafts/authors.md}
-
-\begin{abstract}
-    % 这个补充材料以下述逻辑组织而成：
-    The supplementary material is organized logically as follows:
-    % 展示流域水资源分配制度在全球的推行情况并详细介绍黄河流域的制度变化，旨在说明黄河流域为什么是一个独一无二的准自然实验。
-    (1) Show the implementation of the water resource allocation system in the basin around the world and introduce the institutional changes in the Yellow River Basin in detail, aiming to explain why the Yellow River Basin is a unique quasi-natural experiment.
-    % 展示定量分析方法的技术路线图，并详细介绍定量分析方法中的细节部分。
-    (2) Show the technical roadmap of quantitative analysis method, and introduce the details of quantitative analysis method in detail.
-    % 基于我们建立的一般经济模型，对一些可能的情景进行进一步分析。
-    (3) Further extensions based on our general economic model.
-\end{abstract}
-
-\section*{S1. Detailed introduction of the institutions}
-% 水资源分配方案在全世界范围内都是流域管理的普遍制度。
-Water allocation schemes are widespread in large river basin management programs throughout the world (see \textit{Supplementary Material Figure~\ref{fig:world}}) \cite{speedBasinwaterallocation2013}.
-% 其中中国的黄河流域以典型的自上而下进行制度改革，这种模式会对制度产生迅速的影响，使我们能够定量地估计高层制度设计变化对用水的净影响。
-The Yellow River Basin (YRB) in China has a typical top-down approach to institutional reform, which produces rapid institutional impacts and allows researchers to quantitatively estimate the net impact of changes in high-level institutional design on water use (see \textit{Supplementary Material Figure~\ref{fig:framework}}).
-% 作为中国最早实施水资源分配制度的流域，黄河的制度变化可以在几个水利部发布的文件中得以窥见
-This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level):
-\begin{itemize}
-    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}.
-    \item \textbf{1987}: Implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
-    \item \textbf{1998}: Implementation of unified regulation.
-(\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
-    % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
-    \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}.
-    \item \textbf{2021}: A call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
-\end{itemize}
-
-\begin{figure}[!htb]
-    \centering
-    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/world_institutions}
-	\caption{
-		Overview of water allocation institutions.
-		% 世界已有水资源分配制度的大河流域，其中黄河流域最早于1987年提出资源分配方案，后于1998年更改为统一调度方案。
-		\textbf{A.} Major river basins in the world with existing water resource allocation systems (shaded red); the YRB first proposed a resource allocation scheme in 1987 (designed in 1983) and then changed to a unified regulation scheme in 1998 (designed in 1997 but implemented in 1998).
-		% 不同的水资源分配制度设计模式，中国黄河流域是典型的自上而下。
-		\textbf{B.} Different water resource allocation system design patterns; the YRB is typical of a top-down system with multiple levels.
-		% 流域分水制度的演化。这种多层次的制度设计有其历史变化过程。
-		\textbf{C.} The four periods of institutional evolution of water allocation of the YRB.
-	}
-    \label{fig:world}
-\end{figure}
-% 在上述文件中，1982年的文件标志着设计分水制度尝试的开始，2008年标志着该制度走向成熟（完全建立起流域-省-市区的多级水资源分配和统一调度）。
-The 1982 document marked the beginning of the attempt to design a water allocation institution, and the 2008 document marked the maturity of the system (complete establishment of basin-level, provincial, and district water allocation and unified regulation).
-Currently, a major overhaul is in the planning stages.
-Major shifts of the institution can be analyzed by using the 1987 and 1998 documents.
-It is worth noting that, although the essential reason for these institutions was the mismatch between the spatial and temporal distribution of water resources as well as social and economic water demands, the direct reason for their introduction was the drying-up of the Yellow River \cite{wangReviewImplementationYellow2019}.
-
-\textbf{The official documents in 1987 clearly convey the following key points:}
-\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today.
-\begin{itemize}
-	% 该政策面向的目标是各省（区域），黄委会没有被提及
-	\item The policy is aimed at related provinces (or regions), and the YRCC is not mentioned.
-	% 政策制定的首要考虑是解决断流问题
-	\item Drying-up of the river is identified as the first consideration of this institution.
-	% 各省被鼓励在此配额下制定自己的用水计划
-	\item Provinces are encouraged to develop their own water use plans based on a quota system.
-	% 水资源供给无法满足需求对相关省（地区）是普遍现象。
-	\item Water in short supply is a common phenomenon in relevant provinces (regions).
-\end{itemize}
-
-\textbf{The official documents in 1998 clearly convey the following key points:}
-\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today.
-\begin{itemize}
-	% 除了说明政策针对的各省区之外，明确指出其用水需要黄河水利委员会进行申报，并由其组织和监管
-	\item The document clearly points out that not only provinces and autonomous regions involved in water resources management (see \textit{Article 3}), the provinces’ and regions’ water use shall be declared, organized, and supervised by the YRCC (\textit{Article 11 and Chapter III to Chapter V, and Chapter VII}).
-	% 本研究(\textit{ Article 1})首先考虑的是上、中、下游用水的总体规划。
-	\item Creating the overall plan of water use in the upper, middle, and lower reaches is identified as the first consideration of this institution (\textit{Article 1}).
-	% 各省需要
-	\item With the same quota as used in the 1987 policy, provinces were encouraged to further distribute their quota into lower-level administrations (see \textit{Article 6 and Article 41}).
-	% 强调以总量确定供给，以供给决定需求。
-	\item They emphasize that supply is determined by total quantity, and water use should not exceed the quota proposed in 1987 (see \textit{Article 2}).
-\end{itemize}
-
-% 基于上述分析，我们抽象出了如正文图2中所展示的流域水资源分配制度的运行结构，并将研究时段选择在1975到2008之间。
-On the basis of the above analysis, we abstracted the operational structure of the water resource allocation institution of the YRB as shown in Figure 2 of the main text, focusing on the period between 1975 and 2008.
-By comparing the net effects of three different institutional structures split by the two institutional shifts, we were able to reach a stronger understanding of the influence of structural alignments under the same basin (previous structure-based analysis usually focus on a certain type of systems but with different geographic contexts).
-
-\begin{figure}[!htb]
-    \centering
-	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/YRB_scheme}
-	\caption{
-		% 中国自上而下的水资源分配制度模式（以黄河流域为例）
-		A top-down water resources allocation scheme in China (a case study of the YRB).
-		% 共有十个省或地区从黄河获取地表水资源，其中8个省的依赖性较强（see Supplementary Material Fig）。
-		\textbf{A.} A total of 10 provinces or regions withdraw surface water resources from the Yellow River, of which 8 are highly dependent on the river (see \textit{Supplementary Material S2}).
-		% 中国政府是下发流域管理政策的最高权威，其政策常常能够很快自上而下全面推行。
-		\textbf{B.} The Chinese government is the ultimate authority in issuing watershed management policies, which are often quickly implemented from top down.
-		% 流域管理机构（在黄河是黄河水利委员会）主要负责顺从国家的政策方针来进行流域的日常管理工作。
-		\textbf{C.} The basin-level agency (here, the YRCC) is primarily responsible for the river-related management of the basin in accordance with national policy guidelines.
-		% 利益相关者是各省
-		\textbf{D.} The water management system directly affects the process by which local governments (major stakeholders) plan and use water resources for development.
-Although only surface water (Sur.) is usually traced and restricted, it can also influence groundwater through related hydro-processes such as recharge.
-	}
-	\label{fig:framework}
-\end{figure}
-
-\section*{S2. The technical roadmap and details of quantitative analyzing}
 To quantify and interpret the institutional effects, we followed the technical route illustrated in \textit{Supplementary Material Figure~\ref{fig:roadmap}}. It was a two-step process in which we
@@
 \end{figure}
-
-\section*{S3. Further analysis regarding the general economic model}
-
-% 基于构建的一般经济学模型，我们对利益相关者面对用水配额政策的响应做了进一步探讨
-Using the general economic model (see the \textit{Methods in the main text}), we also explored the response of stakeholders to water quota policies.
-We considered two additional scenarios for stakeholders, one that considered technology growth and one that considered different valuations through time (via the discount rate) of economic benefits and ecological costs.
-In the following scenarios, the cost is assumed to be untransferable, which could be fully allocated to the one incurring the water use.
-Explaining plausible scenarios for these stakeholders will help us better understand the causes of the sprint effect and potential solutions.
-We argue that the sprint effect of water use remains robust even if a complete and equitable system.
-
-\subsection*{Growth in technology}
-
-Assume that there is an exogenous technology growth rate of $g$ in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$ and discount factor $\beta$.
-For simplicity, consider the following finite-period water use optimization:
-
-$ max \quad P \cdot (1+g)^t ln(1+x_{i,0})-\frac{C}{N}+\beta^t \begin{matrix} \sum_{t=1}^T [P \cdot (1+g)^t ln(x_{i,t}+1)-C \cdot x_{i,t}] \end{matrix}$
-
-$s.t. \quad x_{i,t} \leq Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \quad for \quad \forall t$
-
-We depict the relation between multi-period benefits and water use $x_{i0}$ in Figure~\ref{fig:tech_growth}to illustrate the optimal water use pattern under technology growth.
-The higher marginal benefits of water might create enough incentive to offset the untransferable costs of water overuse at $t=0$, because a higher allocated quota provides growth option value.
-Because provincial decisions are under a longer time horizon, there is a greater sprint effect due to the higher accumulated yield.
-
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=0.7\linewidth]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/tech_growth}
-	\caption{Multi-period benefits and optimal water use under technology growth and a quota system.
-The figure depicts the relationship of multi-period benefits of province $i$ and water use under Case 3 with technology growth under $T$ periods.
-Assume $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta=0.7$, $g=0.2$, and $Q=8$.
-The horizontal axis coordinates of $*$ denotes optimal water use at $t=0$ under each time horizon in decision-making.}
-	\label{fig:tech_growth}
-\end{figure}
-
-\subsection*{Economic benefits and ecological costs with different discount rate}
-
-Assume that there is high discount rate for economic benefits and a low discount rate for ecological costs, in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$, discount factor $\beta^{ecolomy}$ and $\beta^{ecology}$.
-It means that present economic profits are significantly concerned but future ecological costs are widely ignored.
-(In fact, if GDP are the core standard to judge officers’ performance, this is an assumption cloth to the reality.) For simplicity, consider the following finite-period water use optimization, notes the water use of province $i$ at period $t$:
-
-$$ max \quad P \cdot ln(1+x_{i,0})-\frac{C}{N}+\beta_{economy}^t \begin{matrix} \sum_{t=1}^T [P \cdot ln(x_{i,t}+1)]  \end{matrix} - \beta_{ecology}^t \begin{matrix} \sum_{t=1}^T [C \cdot x_{i,t}] \end{matrix}$$
-
-$$s.t. \quad x_{i,t} \leq Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \quad for \quad \forall t$$
-
-We depict the relation between multi-period benefits and water use xi0 in different time horizons in Figure~\ref{fig:remote_cost}, Using a higher discount rate for ecological costs might create enough incentive to set off the untransferable unit cost of $C$.
-Because the provincial decision is often under a longer horizon than that in baseline results in Figure 4 of the main text, there is a greater sprint effect as a result of higher accumulated yields.
-
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=0.7\linewidth]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/remote_ecological_cost}
-	\caption{Multi-period benefits and optimal water use when economic benefits have a high discount rate, ecological costs have a low discount rate, and a quota is implemented.
-The figure depicts the relation between multi-period benefits of province $i$ and water use under Case 3 under $T$ periods.
-Assume $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta_{economy}=0.7$, $\beta_{ecology}=0.3$, and $Q=8$.
-The horizontal axis coordinates of $*$ denotes optimal water use at $t=0$ under each time horizon in decision-making.
-	}
-	\label{fig:remote_cost}
-\end{figure}
-
-\bibliography{WAInstitution_YRB_2021}
-\end{document}

### 2022-03-20 docs/papers/manuscript.tex
testing

--- 2022-03-10 docs/papers/tex/main.tex
@@
 
-\title{\input{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/docs/papers/elements/title.md}}
+\title{\input{title.tex}}  %! Notice Input
 
@@
 
-\abstract[ABSTRACT]{\input{../elements/abstract}}
+\abstract[ABSTRACT]{
+    \input{abstract}
+}  %! Notice input
 
-\keywords{\input{../elements/keywords}}
+\keywords{\input{keywords}}  %! Notice input
 \maketitle
@@
 \section{INTRODUCTION}\label{intro}
-\input{../elements/introduction}
+\input{01_manuscript/01_introduction.tex}
 
@@
 	\centering
-	\includegraphics[width=16pc]{../../../figs/diagrams/framework.jpg}
+	\includegraphics[width=16pc]{../../figs/diagrams/framework.jpg}
 	\caption{
@@
 \section{Context of institutional shifts}\label{institution}
-\input{../elements/institution.tex}
+\input{01_manuscript/02_institution.tex}
 
@@
     \centering
-    \includegraphics[width=16pc]{../../../figs/diagrams/structure.jpg}
+    \includegraphics[width=16pc]{../../figs/diagrams/structure.jpg}
 	\caption{
@@
 \subsection{SPRINT EFFECT}\label{phenomenon}
-\input{../elements/results.tex}
+\input{01_manuscript/03_results.tex}
 
@@
     \centering
-    \includegraphics[width=16pc]{../../../figs/outputs/main_results.jpg}
+    \includegraphics[width=16pc]{../../figs/outputs/main_results.jpg}
     \caption{
@@
 \subsection{CAUSES}\label{causes}
-\input{../elements/model}
-\input{../elements/table.tex}
+\input{01_manuscript/model}
+\input{01_manuscript/table.tex}
 
@@
     \centering
-    \includegraphics[width=16pc]{../../../figs/outputs/economic_model.jpg}
+    \includegraphics[width=16pc]{../../figs/outputs/economic_model.jpg}
 	\caption{
@@
 \section{DISCUSSION}\label{discussion}
-\input{../elements/discussion}
+\input{01_manuscript/04_discussion.tex}
 
@@
 \section{CONCLUSION}\label{conclusion}
-\input{../elements/conclusion}
+\input{01_manuscript/05_conclusion.tex}
 
@@
 \label{appendix}
-%%%%%%%% -----  appendix -------- %%%%%%%%%%
+%%%%%%%% -----  02_appendix -------- %%%%%%%%%%
 

### 2022-03-20 docs/papers/make.sh

@@ -1,0 +1,4 @@
+pdflatex -halt-on-error -output-directory=01_manuscript/out manuscript.tex
+biblatex -halt-on-error -output-directory=out 01_manuscript/outmanuscript.aux
+pdflatex -halt-on-error -output-directory=01_manuscript/out manuscript.tex
+pdflatex -halt-on-error -output-directory=01_manuscript/out manuscript.tex

### 2022-03-20 docs/papers/paper.py

@@ -1,0 +1,55 @@
+#!/usr/bin/env python
+# -*-coding:utf-8 -*-
+# Created date: 2022/3/20
+# @Author  : Shuang Song
+# @Contact   : SongshGeo@gmail.com
+# GitHub   : https://github.com/SongshGeo
+# Research Gate: https://www.researchgate.net/profile/Song_Shuang9
+import sys
+
+import yaml
+import os
+
+YAML_PATH = "metadata.yaml"
+with open(YAML_PATH, "r", encoding="utf-8") as file:
+    params = yaml.load(file.read(), Loader=yaml.FullLoader)
+    file.close()
+
+
+class SciPaper(dict):
+    def __init__(self):
+        super().__init__()
+
+
+if __name__ == '__main__':
+    print(os.getcwd())
+    os.chdir(os.getcwd())
+    title = params.get("title")
+    abstract = params.get("abstract")
+    authors = params.get("authors").keys()
+    keywords = params.get("keywords")
+    keywords = ", ".join(keywords)
+    print(title, abstract, authors, keywords)
+    # for folder in ('00_cover_letter', '01_manuscript', '02_appendix'):
+    #     os.system(f"cd {folder}")
+    #     for name, element in zip(
+    #             ['title', 'abstract', 'keyword'],
+    #             [title, abstract, keywords]
+    #     ):
+    #         os.system(f"echo '{element}' > {name}.tex")
+    #         os.system("cp ../*.sh .")
+    #         os.system("zsh *.sh")
+        # for name in ['title', 'abstract', 'keyword']:
+        #     os.system(f"rm '{name}.tex'")
+    for name, element in zip(
+            ['title', 'abstract', 'keywords'],
+            [title, abstract, keywords]
+    ):
+        os.system(f"echo '{element}' > 00_cover_letter/{name}.tex")
+        os.system(f"echo '{element}' > 01_manuscript/{name}.tex")
+        os.system(f"echo '{element}' > 02_appendix/{name}.tex")
+        os.system(f"echo '{element}' > {name}.tex")
+    # os.system(f'zsh make.sh')
+    # for name in ['title', 'abstract', 'keyword']:
+    #     os.system(f"rm '{name}.tex'")
+    pass

### 2022-03-22 docs/papers/01_manuscript/manuscript.tex
refactor(.tex-structure): refactor LaTeX project, now a well-structured project set
BREAKING CHANGE:

--- 2022-03-20 docs/papers/manuscript.tex
@@
-\documentclass{nsr}
+\documentclass{../nsr}
 
@@
 \markboth{One, Two, and Three}{One, Two, and Three}
+\graphicspath{{../../../figs/}}
 
@@
 
-\bibliographystyle{nsr}
+\bibliographystyle{../nsr}
 
@@
 \section{INTRODUCTION}\label{intro}
-\input{01_manuscript/01_introduction.tex}
+\input{01_introduction.tex}
 
@@
 	\centering
-	\includegraphics[width=16pc]{../../figs/diagrams/framework.jpg}
+	\includegraphics[width=16pc]{diagrams/framework.jpg}
 	\caption{
@@
 \section{Context of institutional shifts}\label{institution}
-\input{01_manuscript/02_institution.tex}
+\input{02_institution.tex}
 
@@
     \centering
-    \includegraphics[width=16pc]{../../figs/diagrams/structure.jpg}
+    \includegraphics[width=16pc]{diagrams/structure.jpg}
 	\caption{
@@
 \subsection{SPRINT EFFECT}\label{phenomenon}
-\input{01_manuscript/03_results.tex}
+\input{03_results.tex}
 
@@
     \centering
-    \includegraphics[width=16pc]{../../figs/outputs/main_results.jpg}
+    \includegraphics[width=16pc]{outputs/main_results.jpg}
     \caption{
@@
 \subsection{CAUSES}\label{causes}
-\input{01_manuscript/model}
-\input{01_manuscript/table.tex}
+\input{model}
+\input{table.tex}
 
@@
     \centering
-    \includegraphics[width=16pc]{../../figs/outputs/economic_model.jpg}
+    \includegraphics[width=16pc]{outputs/economic_model.jpg}
 	\caption{
@@
 \section{DISCUSSION}\label{discussion}
-\input{01_manuscript/04_discussion.tex}
+\input{04_discussion.tex}
 
@@
 \section{CONCLUSION}\label{conclusion}
-\input{01_manuscript/05_conclusion.tex}
+\input{05_conclusion.tex}
 
@@
 %% the \bibliography{} command.
-\bibliography{WAInstitution_YRB_2021}
+\bibliography{../WAInstitution_YRB_2021}
 

### 2022-03-22 docs/papers/make.sh

@@ -1,4 +1,4 @@
-pdflatex -halt-on-error -output-directory=01_manuscript/out manuscript.tex
-biblatex -halt-on-error -output-directory=out 01_manuscript/outmanuscript.aux
-pdflatex -halt-on-error -output-directory=01_manuscript/out manuscript.tex
-pdflatex -halt-on-error -output-directory=01_manuscript/out manuscript.tex
+pdflatex -halt-on-error -output-directory=01_manuscript/out 01_manuscript/manuscript.tex
+bibtex 01_manuscript/out/manuscript.aux
+pdflatex -halt-on-error -output-directory=01_manuscript/out 01_manuscript/manuscript.tex
+pdflatex -halt-on-error -output-directory=01_manuscript/out 01_manuscript/manuscript.tex

### 2022-03-22 docs/papers/paper.py

@@ -5,10 +5,10 @@
 # @Contact   : SongshGeo@gmail.com
 # GitHub   : https://github.com/SongshGeo
 # Research Gate: https://www.researchgate.net/profile/Song_Shuang9
-import sys
+
+import os
 
 import yaml
-import os
 
 YAML_PATH = "metadata.yaml"
 with open(YAML_PATH, "r", encoding="utf-8") as file:
@@ -21,7 +21,7 @@ class SciPaper(dict):
         super().__init__()
 
 
-if __name__ == '__main__':
+if __name__ == "__main__":
     print(os.getcwd())
     os.chdir(os.getcwd())
     title = params.get("title")
@@ -30,26 +30,12 @@ if __name__ == '__main__':
     keywords = params.get("keywords")
     keywords = ", ".join(keywords)
     print(title, abstract, authors, keywords)
-    # for folder in ('00_cover_letter', '01_manuscript', '02_appendix'):
-    #     os.system(f"cd {folder}")
-    #     for name, element in zip(
-    #             ['title', 'abstract', 'keyword'],
-    #             [title, abstract, keywords]
-    #     ):
-    #         os.system(f"echo '{element}' > {name}.tex")
-    #         os.system("cp ../*.sh .")
-    #         os.system("zsh *.sh")
-        # for name in ['title', 'abstract', 'keyword']:
-        #     os.system(f"rm '{name}.tex'")
+
     for name, element in zip(
-            ['title', 'abstract', 'keywords'],
-            [title, abstract, keywords]
+        ["title", "abstract", "keywords"], [title, abstract, keywords]
     ):
-        os.system(f"echo '{element}' > 00_cover_letter/{name}.tex")
-        os.system(f"echo '{element}' > 01_manuscript/{name}.tex")
-        os.system(f"echo '{element}' > 02_appendix/{name}.tex")
         os.system(f"echo '{element}' > {name}.tex")
     # os.system(f'zsh make.sh')
-    # for name in ['title', 'abstract', 'keyword']:
+    # for name in ['title', 'abstract', 'keywords']:
     #     os.system(f"rm '{name}.tex'")
     pass

### 2022-03-26 docs/papers/01_manuscript/01_introduction.tex
docs(introduction): rewrite introduction section

@@
-Emerging competition for water is an urgent problem in water governance, with widespread water scarcity and overuse resulting in huge impacts on economies, societies, and ecosystems \cite{gleickPeakwaterlimits2010,dolanEvaluatingeconomicimpact2021,siwiCompetitionWaterGetting,ziolkowskaCompetitionWaterResources2016,distefanoArewedeep2017}.
-Water is the key exclusive and competitive resource that couples socioeconomic and ecological systems (known as common-pool resources, CPRs) \cite{wutichWaterScarcitySustainability2009,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017,castilla-rhoGroundwaterCommonPool2020}.
-Conflicts of interest often occur in allocation and competitions of water resources, with water governance policies often leading to long-term changes in human–water relationships and the redistribution of benefits \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013,chingManagingsocioecologyvery2015}.
-Although governments in many of the world’s large river basins have tried to resolve competition for water through the deliberate design of new institutions, general principles underlying the successes and failures of these initiatives are poorly documented and understood.
+% 水竞争的重要性
+Widespread freshwater scarcity and overuse, resulting in systematic risks on economies, societies, and ecosystems globally, are critical environmental challenges to sustainable development \cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
+With steadily increasing demand, competition for water is an urgent problem in water governance, where policies often lead to long-term changes in human–water relationships and the redistribution of benefits \cite{gleick2010, ziolkowska2016, wang2019d}.
+Despite governments worldwide trying to resolve competition for water through deliberate institutions at large river basins, cascading effects of these initiatives are poorly understood, underlying the coupled human-nature systems \cite{giuliani2013, falkenmark2019, jaeger2019}.
 
-Institutions (such as policies, laws, and norms) can influence regional sustainability by changing social-ecological system (SES) structure and dynamics \cite{youngInstitutionsenvironmentalchange2008,cummingAdvancingunderstandingnatural2020,lieninstitutionalgrammartool2020}.
-These include inter-relationships and interactions between social actors, between ecological units, or between social and ecological system elements \cite{bodinCollaborativeenvironmentalgovernance2017,barnesSocialecologicalalignmentecological2019}.
-Effective (“matched”) institutions operate at appropriate spatial, temporal, and functional scales to manage and balance these different relationships and interactions \cite{heWateringEnvironmentalRegulation2020,kellenbergempiricalinvestigationpollution2009}.
-From the perspective of SES outcomes, matched institutions support (but do not guarantee) sustainability \cite{epsteinInstitutionalfitsustainability2015,wangAlignmentsocialecological2019}.
+% 制度的意义
+Institutions (such as policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled system, including interplays between social actors, between ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
+Effective (“matched”) institutions operate at appropriate spatial, temporal, and functional scales to manage and balance these different relationships and interactions, therefore, supporting (but do not guarantee) sustainability \cite{epstein2015, wang2019d}.
+Some institutional shifts were reported to have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and in collaborative water governance systems in Europe \cite{green2013}).
+However, shifting institutions in a large, complex river basin may create or destroy hundreds of different connections, where matched human-water relationships are not universal.
+Therefore, despite widespread recognition of the rising importance of institutions as an approach to water sustainable use within large river (especially transboundary river) basins, broader cascading effects of these changes are still in open discussion \cite{agrawal2003, persha2011, agrawal2001}.
 
-Some kinds of institutions have been shown to support desirable outcomes in water-centered SESs (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wangAlignmentsocialecological2019} and in collaborative water governance systems in Europe \cite{greenEUWaterGovernance2013}).
-At the same time, undesired and unsustainable outcomes (e.g., failures in environmental regulation of highly polluting industries or the development of “tragedy of the commons” situations when pursuing more water resources), with considerable ecological degradation, have attracted much attention \cite{saylesSocialecologicalnetworkanalysis2019,caiPollutingthyneighbor2016,castilla-rhoSocialtippingpoints2017}.
-Despite widespread recognition of the rising importance of integrated water resource management in solving water competition in the world’s large river basins, relatively few studies have explored the mechanisms by which SESs respond to new institutions \cite{agrawalSustainableGovernanceCommonPool2003,pershaSocialEcologicalSynergy2011,agrawalCommonPropertyInstitutions2001}.
-Two particular weaknesses in existing knowledge include understanding (1) the causal links between SES structures and outcomes; and (2) details of the underlying processes, especially the coordination of the incentives of different participants, that result from an institutional lack of fit.
-These weaknesses limit our understanding of institutional design, and they may reduce the speed and transfer of new knowledge and experience related to improving the sustainability of comprehensive water resources management.
+% 黄河的制度介绍
+Supporting $35.63\%$ irrigation and $xx\%$ population with only $2.66\%$ of water resources in China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021), the overburdened Yellow River (YR) once dried up in consecutive years but successfully recovered through an institutional solution since 1998.
+Before the remarkable achievement in the restoration of river depletion, on the contrary, the first temptation to restrict water uses in the YR in 1987 (known as the ``87 Water Allocation Scheme, 87-WAS'') was recognized as a not fulfilling expectations institutional shift.
+Until the 87-WAS, stakeholders have free access to the YR water resources, with geographic and temporal differences between freshwater demand and availability.
+As mismatch between demands and supply kept increasing, national authorities proposed in 87-WAS allocating certain water quota between $10$ provinces (or regions) along the YR basin.
+However, this controversial scheme helped little in turn water depletion around until a different strategy (Unified Basinal Regulation, 98-UBR) expanded responsibilities of basinal authorities in integrated water management, 1998, and started progress in the restoration.
 
-In order to disentangle the relationship between SES structure and outcomes, we analyzed a case study to show how an institutional shift led to a structural mismatch that triggered unsustainable water use and unintended ecological deterioration.
-Two rapid shifts in institutional structure that occurred in 1987 and 1998 (see Supplementary Material S1) provide unique settings to exploit quasi-natural experiments of a large river basin, the Yellow River Basin (YRB) in China \cite{xiaDevelopmentWaterAllocation2012}.
-After a period of severe drying up, an institutional shift implemented in 1987 represented the beginning of attempts to control water use in the YRB through the use of quotas, with the goals of alleviating conflicts between supply and demand and achieving sustainable development.
-
-Our results show that this initiative actually accelerated water withdrawals, resulting in an unintended “sprint effect”, where institutional mismatches created an even stronger incentive for each resource user to withdraw resources until the next major institutional shift in 1998.
-Our analysis contributes to a deeper understanding of the mechanisms underlying the relationships among institutions, SES structures, and outcomes.
-By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings are consistent with the urgent calls for a more dynamic design for water use allocation to achieve sustainability.
-
-\section{Institutions and SES structures}
-% 机构可以塑造社会经济体系的结构，对其进行抽象是机械地理解结构和结果之间联系的第一步。
-Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{fig:framework}A).
-% 例如，机构可以创建一种被确定为与良好的社会经济效益相关联的水平匹配结构，如果它鼓励管理相连生态成分的不同行动者之间的协作(图1B)。
-For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{fig:framework}B), leading to sustainable outcomes.
-% 例如，机构可以创建一个结构，鼓励不同行为者之间的合作，管理相连的生态成分
-Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{fig:framework}C and D).
-% 在实践中，一个大型、复杂的河流流域的制度变化将创造或摧毁数百种不同的联系。这些局部变化的更广泛影响可以从系统的整体行为中看到。
-In practice, institutional changes in a large, complex river basin will create or destroy hundreds of different connections.
-The broader impacts of these local changes can be seen in the overall behavior of the system.
-% 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
-We thus explored the causal linkages between the SES structures and sustainability (outcomes) in quasi-natural experiments of the YRB, which provides an informative case study for two main reasons.
-% 首先，长江流域管理的急剧结构变化使我们能够定量估计高层制度设计变化对用水的净影响。决定水分配的制度包括自下而上的协议或社会规范，以及自上而下的配额或法规，它们对社会经济结构有不同的影响;自上而下的监管可能会立即引发制度转变和SES的剧烈结构性变化。通过与由自下而上的制度转变引起的更渐进的变化相比，探索自上而下变化的影响，在对社会经济地位的定量分析中，极大地减少了来自不可观测因素的潜在干扰，提高了社会经济地位结构和结果之间因果关系的清晰度。
-First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use.
-Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013}; top-down regulations can trigger immediate institutional shifts and sharp SES structural changes \cite{speedBasinwaterallocation2013,rolandUnderstandinginstitutionalchange2004}.
-In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and improves the clarity of the causal link between SES structure and outcome.
-% 其次，通过比较长江流域两次制度变迁所分裂的三种不同制度结构的净效应，我们也可以更深入地理解“盆地固定效应”下结构格局的影响。尽管流域内的社会经济单位从世界各地的大型河流流域和许多地区的水资源中受益，但很少有流域多次经历过如此激进的社会经济结构变化。
-Second, by comparing the net effects of three different institutional structures split by two institutional shifts in the YRB, we can also reach a stronger understanding of the influence of structural alignments under a fixed basin.
-Although socioeconomic units within a basin benefit from water resources in large river basins all over the world and many locations have shown increased levels of regulation, few basins have experienced such radical SES structural changes several times (see \textit{Supplementary Material} S1).
-Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in SES institutional structure.
-% 因此，黄河流域的“流域固定效应”为SES结构的自我比较提供了宝贵的机会。
-% Thus, the YRB provides valuable settings for understanding the direct impacts of changes in SES institutional structure.
+% 我们的研究
+The shifts of the water governance institution of YR refactored the interplays between humans and water with long-term cascading effects, leaving two quasi-natural experiments for understanding the interactions.
+By Differenced Synthetic Control method, our analysis on net effects of institutional shift shows that institutional mismatches contributed to acceleration water withdrawals for resource users after 98-WAS.
+As few large river basins have experienced such radical structural changes several times, our quantitative analysis of institutional shifts in the YR induces a valuable understanding of water sustainable governance by decoupling natural and human interferences.
+By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings align with the urgent calls for a more dynamic design for water governance institutions to achieve sustainability.

### 2022-03-28 docs/papers/01_manuscript/01_introduction.tex
docs(introduction-rectification-and-results-part1-finished): embed results and discussions to make the novel more fluent
BREAKING CHANGE:

@@
 With steadily increasing demand, competition for water is an urgent problem in water governance, where policies often lead to long-term changes in human–water relationships and the redistribution of benefits \cite{gleick2010, ziolkowska2016, wang2019d}.
-Despite governments worldwide trying to resolve competition for water through deliberate institutions at large river basins, cascading effects of these initiatives are poorly understood, underlying the coupled human-nature systems \cite{giuliani2013, falkenmark2019, jaeger2019}.
+Despite governments worldwide trying to resolve competition for water through deliberate institutions at large river basins, cascading effects of these initiatives are poorly understood \cite{giuliani2013, falkenmark2019, jaeger2019}.
 
@@
 Institutions (such as policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled system, including interplays between social actors, between ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
-Effective (“matched”) institutions operate at appropriate spatial, temporal, and functional scales to manage and balance these different relationships and interactions, therefore, supporting (but do not guarantee) sustainability \cite{epstein2015, wang2019d}.
+Understanding the complex interlinkages is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
+Effective (“matched”) institutions operate at appropriate spatial, temporal, and functional scales to manage and balance these different relationships and interactions, therefore, supporting (but do not guarantee) sustainability of SES \cite{epstein2015, wang2019d}.
+Water governance tends to shift for institutional solutions within a complex basinal system, where societal drivers impact through water use and related technical interventions \cite{fischer2020}.
 Some institutional shifts were reported to have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and in collaborative water governance systems in Europe \cite{green2013}).

### 2022-03-28 docs/papers/01_manuscript/03_results.tex
docs(introduction-rectification-and-results-part1-finished): embed results and discussions to make the novel more fluent
BREAKING CHANGE:

%! Author = songshgeo
%! Date = 2022/3/10
% \MakeUppercase{\subsection{Cascading effects of the institutional shifts}}
\subsection{Cascading effects of the institutional shifts}
\label{effects}
% 从国家官员到流域管理官员，从省、市到区，长江流域自上而下的制度结构开始演变至今
Including the national authorities, the basin management authorities, provinces, cities, and even districts, top-down institutional structures of the YRB started to evolve up to now (\textit{S1 in Supplementary Material}).
% 从70年代黄河断流开始摸索87-WAS的初步治理方案，到98-UBR成功解决断流后于2008年强化该制度，黄河一直是中国水治理制度转变的先行者。
As a pioneer in water governance shifting in China, the YRB started to explore the initial water allocating scheme in the 1970s, then found a successful solution of dring-up in 1998, and promoted completely since 2008.
% 1987年(87-WAS)和1998年(98-UBR)的制度变迁是YRB中两个被广泛认可的制度演变里程碑(图~\ref{fig:structure} \textit{S1 in  Supplementary  Methods})。
Throughout, the institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones of water governance (Figure~\ref{fig:structure} and \textit{S1 in Supplementary Material}).
Our analysis period, therefore, spans from 1975 to 2008, with the human-water system shifted between three different institutional structures (Figure~\ref{fig:structure}).

Here, we use Differenced Synthetic Control method, which considers economic growth and natural background, to estimate theoretical water uses scenarios without these policy interferences (\textbf{Methods}; \textit{S2 in Supplementary Material}).
% 我们的结果表明，1987年(87-WAS)的制度转变实际上刺激了各省比没有干扰时使用更多的水，观测到比预期增加了10(图~\ref{fig:main_results}A和B)。
Our results suggest that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without the interference (Figure~\ref{fig:main_results}A).
% 在1998年制度再次改变后，用水量增加的趋势似乎被有效地抑制了，观察到的总用水量比预期减少了10(图~\ref{fig:main_results} C和D)。
However, after the institution shifted again in 1998 (98-UBR), the trend of increasing water use appeared to be effectively suppressed, with total observed water consumption decreasing by $260\%$ relative to the estimation (Figure~\ref{fig:main_results} B).
% 87-WAS后用水量的增加与1987 - 1998年地表径流严重干涸的事实相吻合，这是河流退化和环境危机的一个明显的试金石
The increased water uses after 87-WAS align with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{fig:main_results}C).
% 尽管在1998年制度转变后的十年内，干旱程度有增无减，但断流的环境危机却得到了有效解决。
On the other hand, although the density of droughts increased in the decade after the 98-UBR, the environmental crisis of river drying-up was effectively resolved (Figure~\ref{fig:main_results}C).
% 正如许多研究指出的，这主要是大规模制度变迁的成功
As literature has suggested, this institution shift contributed a lot to the successful water governance.

\begin{figure*}[!h]
    \centering
    \includegraphics[width=32pc]{outputs/main_results2.jpg}
    \caption{
        Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
        \textbf{A.} water uses of the YRB before and after the institutional shift in 1987 (87-WAS);
        \textbf{B.} water uses of the YRB before and after the institutional shift in 1998 (98-UBR). While the blue lines are statistic water use data, grey ones are the estimation from the Differenced Synthetic Control method with economic and environmental background controlled.
        \textbf{C.}
    }
    \label{fig:main_results}
\end{figure*}

% 然而，87-WAS 也非大多分析报告所认为的“没有起到效果”，因为制度变化完全没有产生影响时，流域的用水量将更接近我们的模型预测。
Furthermore, 87-WAS did not ``have no effect'' as previous analyses suggested because water uses will be closer to what our models predicted when the shift was a blank policy.
% 除了环境背景外，我们的预测还考虑了经济因素，假设经济总量与用水量之间的生产函数保持不变。
Besides environmental background, our forecast takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textit{S2 in Supplementary Material}).
% 由于单位水资源的生产效率在这一时期实际上保持了相似的趋势，这意味着流域用水量的加速增长不是经济增长的必然结果。
However, the production efficiency of unit water resources kept similar trends between provinces of the YRB and others (Figure \textit{S3 in Supplementary Material}), which means that the accelerated growth of basinal water uses was not the inevitable result of economic growth.
% 但实际上，我们的结果表明相对于正常的经济发展进程来说，黄河流域的水资源利用反而更像是受到了刺激。
However, our results suggest that water use (especially for irrigation) in the YRB was more likely to be partly stimulated by the shift in 1987 besides economic growth.
% 这种用水量的加速增长与制度设计时遏制用水、保护黄河流域有限的水资源的初衷相悖。
This accelerated growth in water use was contrary to the original intention of the 87-WAS in conserving the limited water.

% 两次制度转变带来的级联效应存在巨大差异
The cascading effects of the two institutional shifts were very different, while their reframed SES structures have direct differences.
% 在我们的研究期间(从1975年到2008年)，机构在三种不同的结构之间转换:免费访问、87-WAS和98-UBR。
In our study period, the institution shifted between three different structures (XXX, XXX, and XXX) (Figure~\ref{fig:structure}).
%! 这里还是需要名字的
% 长江水利委员会是长江流域的主要负责人，其任务是报告和分析1998年以前长江流域的用水量(87-WAS之后)。
However, the YRCC, whose primary official response to the river before 1998, the mandate was to conserve the riverway environment, construct and maintain infrastructures, and report on and analyze water consumption (after the 87-WAS) in the YRB, i.e., connecting the ecological nodes (different river reaches) horizontally ~\cite{wang2019a}.
% 这意味着，而与生态节点直接联系的各利益相关者之间没有横向连接。
Thus, until the institutional shift of 98-UBR, with no necessity to apply for a water permit from YRCC, there were no horizontal connections (cooperations or agreements) between the various stakeholders (provinces) directly connected to the ecological sections.
% 许多不同领域的经验研究指出这种结构很可能是错配的，因为这些利益相关者难以从全局出发维护好互相联系的生态系统。
Empirical studies in many different fields indicate that this structure is likely to be mismatched, as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
% 87-WAS带来的效果再一次说明了这种阻碍可持续性的治理结构需要得到重视。
The cascading effect of the 87-WAS once again demonstrates that the more stakeholders, the more difficult it is to have a win-win situation of environment and interests \cite{hegwood2021} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.

### 2022-03-28 docs/papers/01_manuscript/04_discussion.tex
docs(introduction-rectification-and-results-part1-finished): embed results and discussions to make the novel more fluent
BREAKING CHANGE:

@@
 %! Date = 2022/3/10
+
+% \MakeUppercase{\subsection{Mechanism of institutional shift effects}}
+\subsection{Mechanism of institutional shift effects}
+\label{reason}
+Next, we explored the mechanisms linking the structures and the outcomes.
+% 87-WAS 后各省响应的差异是理解制度影响机制的关键
+Differences in provincial responses to 87-WAS are vital to understanding the mechanism of institutional shifts' impacts.
+% 我们的结果表明，各省加速用水的比例（实际用水量超出模型预测用水量的比例）与各省黄河水取用量呈现显著正相关
+Our results show that the proportion of accelerated water consumption in each province (the proportion of actual water consumption exceeding the predicted water consumption by the model) has a significant correlation to the Yellow River water consumption in each province (Figure~\ref{fig:upset}A).
+% 但明显的加速效应仅突出体现在主要用水省份上，对大多数省份来说，87-WAS 带来的影响并不大，
+However, the apparent acceleration effect of the 87-WAS was only prominent in the significant water-using provinces (Neimeng, Henan, and Shandong), and there were no evident impacts for most provinces (Figure~\ref{fig:upset}B).
+% 尤其是常年超指标用水的山东与内蒙，分别在1987到1998年的十年间使用了高于模型预测值的xx%和xx%的用水量。
+In particular, Shandong and Inner Mongolia, both of which exceed the prescribed water uses of the 87-WAS, used xx\% and XX\% more water uses than predicted by the model from 1987 to 1998, respectively.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=16pc]{outputs/upset.jpg}
+    \caption{
+        \textbf{A.} The partial correlation coefficient between wate uses (WU) of Yellow River (YR), unsatisfied ratio (compared with requirements in water plan and supply in the 87-WAS), and the average accelerated ratio.
+        \textbf{B.} Average accelerated ratio of water uses for each province in the YRB during the decade after 87-WAS (from 1987 to 1998).
+        \textbf{Mian users:} Major water consumption provinces (over the median).
+        \textbf{Overused:} violate the 87-WAS in average water uses.
+    }
+    \label{fig:upset}
+\end{figure}
+
+Then, we analyzed mathematically why the mismatched structure made win-wins elusive in the institution shift of 87-WAS (\textit{method} and \textit{Supplementary Material S4}).
+Theoretically, our model suggests that different kinds of institutional shifts should lead to different optimal water uses (Figure~\ref{fig:economic_model}).
+% 在不匹配条件下，边际成本减去边际收益增加，导致用水量增加，xx的差异反映了水配额模拟的非预期冲刺效应。
+The unintended accelerations from 1987 to 1998 was caused by both declining marginal costs (a shift from a fixed unit cost to an irrelevant cost) and increasing marginal returns due to future water use benefits (\textit{Supplementary Material S4}).
+% 对于已经拥有较高经济效率的用水者（如这里的黄河用水大户），更大的边际收益诱使他们为了未来的经济增长而开采资源的“冲刺效应”
+For users who are already economically efficient, the "sprint effect" of extracting resources for future economic growth is is induced by greater marginal returns.
+% 因此，这种制度引发了一种与可持续用水意图背道而驰的激励扭曲。
+The institution (87-WAS) thus triggered an incentive distortion that ran counter to the intention of sustainable water use.
+% 中央管理的存在(1998年后由YRCC进行管理)可以有效降低边际生态成本(详细的数学公式见表~\ref{tab:cases}的\textbf{methods})。
+On the contrary, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs (\textit{Supplementary Material S4}).
+
+% 制度失效背后的资源竞争
+Linking structures to outcomes are in need of advancement when understanding a SES.
 % 我们展示了不匹配的分配制度是如何导致激励失真导致水资源加速耗竭的(即“冲刺效应”)。“冲刺效应”是CPR系统面临的一种特殊情况，在这种情况下，制度的不匹配为每个资源使用者创造了更强的动机(扭曲)，促使他们收回资源
-We have shown how a mismatched allocation institution can lead to an accelerated depletion of water resources (i.e., the “sprint effect”) caused by incentive distortion.
-The sprint effect is a special case faced by CPR systems, where institutional mismatches create an even stronger incentive (with distortion) for each resource user to withdraw resources
+Here, we have shown how a mismatched structure induced by institutional shift can lead to accelerated depletion of water resources (i.e., the "sprint effect") caused by incentive distortion.
+The ``sprint effect'' is a particular case faced by CPR systems, where institutional mismatches create an even stronger incentive (with distortion) for each resource user to withdraw resources
 \cite{ostromRevisitingCommonsLocal1999,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017}.
 % 过往研究指出制度常常是避免公共池塘资源系统的崩溃的关键，但“短跑效应”的出现表明在自上而下进行制度设计所形成的错配SES结构中，制度也可以成为系统加速崩溃的触发者。
-Previous studies have suggested that institutions are often the key to avoid the collapse of a CPR system, but the emergence of a sprint effect shows that an institution with structural mismatches can also be the trigger that accelerates system collapse \cite{bodinConservationSuccessFunction2014,bodinCollaborativeenvironmentalgovernance2017,wangAlignmentsocialecological2019}.
-The initial formulation of the water quota in our case studies went through a stage of “bargaining” among stakeholders (from 1982 to 1987) \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}, where each province attempted to demonstrate its development potential related to water use.
+Previous studies have suggested that institutions are often the key to avoiding the collapse of a CPR system, but the emergence of a sprint effect shows that an institution with structural mismatches can also be the trigger that accelerates system collapse \cite{bodinConservationSuccessFunction2014,bodinCollaborativeenvironmentalgovernance2017,wangAlignmentsocialecological2019}.
+The initial formulation of the water quota in our case studies went through a stage of "bargaining" among stakeholders (from 1982 to 1987) \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}, where each province attempted to demonstrate its development potential related to water use.
 % 在高层决策者与低层利益相关者之间存在信息不对称的用水分配中，当前用水量越大的利益相关者议价能力越大。1987年以后，对各省来说，合乎逻辑的下一步是试图证明争取更大配额的合理性，而不是立即采取资源节约型改革。在实践中，尽管受影响的省份可能没有直接鼓励过度使用资源，但由于激励扭曲，他们有更大的动机对资源提取开绿灯。因此，在争夺潜在的水资源配额时，各省往往将生态成本隐藏在经济发展背后。
-In water use allocation with information asymmetry between upper-level decision-makers and lower-level stakeholders, those with more current water use might have greater bargaining power.
+With information asymmetry between upper-level decision-makers and lower-level stakeholders in water use allocation, those with more current water use might have greater bargaining power.
 After 1987, the logical next step for provinces was to attempt to justify bargaining for larger quotas rather than immediately adopt resource-conserving transformations.
@@
 % 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
-Adoption of an overall quota plays an important role in preventing overuse of CPRs \cite{tilmanLocalizedprosocialpreferences2019}.
-However, the negative effects of incentive distortion imply a trade-off between long-term SES benefits and current stability, and the proportion of available resources allocated under quota schemes matters when institutions change \cite{ladeRegimeshiftssocialecological2013}.
-According to our analysis of plausible scenario assumptions based on our general economic model, the sprint effect will be reinforced when stakeholders anticipate that technological advances will amplify the benefits of water quotas in the future (see \textit{Supplementary Material S3}).
+Adoption of an overall quota plays a vital role in preventing overuse of CPRs \cite{tilmanLocalizedprosocialpreferences2019}.
+However, the adverse effects of incentive distortion imply a trade-off between long-term SES benefits and current stability, and the proportion of available resources allocated under quota schemes matters when institutions change \cite{ladeRegimeshiftssocialecological2013}.
+According to our analysis of plausible scenario assumptions based on our general economic model, the ``sprint effect'' will be reinforced when stakeholders anticipate that technological advances will amplify the benefits of water quotas in the future (see \textit{Supplementary Material S3}).
+
+\subsection{Novel insights and policy implications}
+\label{insights}
+
 % 然而，如果有水权转换机制允许利益相关者之间通过交易来弥补 shadow value，当前这种错乱的动机就不会那么强。
@@
 
+% 重视制度的影响，人水耦合
+% 机构可以塑造社会经济体系的结构，对其进行抽象是机械地理解结构和结果之间联系的第一步。
+Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{fig:framework}A).
+% 例如，机构可以创建一种被确定为与良好的社会经济效益相关联的水平匹配结构，如果它鼓励管理相连生态成分的不同行动者之间的协作(图1B)。
+For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{fig:framework}B), leading to sustainable outcomes.
+% 例如，机构可以创建一个结构，鼓励不同行为者之间的合作，管理相连的生态成分
+Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{fig:framework}C and D).
+% 在实践中，一个大型、复杂的河流流域的制度变化将创造或摧毁数百种不同的联系。这些局部变化的更广泛影响可以从系统的整体行为中看到。
+% 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
+We thus explored the causal linkages between the SES structures and sustainability (outcomes) in quasi-natural experiments of the YRB, which provides an informative case study for two main reasons.
+% 首先，长江流域管理的急剧结构变化使我们能够定量估计高层制度设计变化对用水的净影响。决定水分配的制度包括自下而上的协议或社会规范，以及自上而下的配额或法规，它们对社会经济结构有不同的影响;自上而下的监管可能会立即引发制度转变和SES的剧烈结构性变化。通过与由自下而上的制度转变引起的更渐进的变化相比，探索自上而下变化的影响，在对社会经济地位的定量分析中，极大地减少了来自不可观测因素的潜在干扰，提高了社会经济地位结构和结果之间因果关系的清晰度。
+First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use.
+Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013}; top-down regulations can trigger immediate institutional shifts, and sharp SES structural changes \cite{speedBasinwaterallocation2013,rolandUnderstandinginstitutionalchange2004}.
+In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and improves the clarity of the causal link between SES structure and outcome.
+% 其次，通过比较长江流域两次制度变迁所分裂的三种不同制度结构的净效应，我们也可以更深入地理解“盆地固定效应”下结构格局的影响。尽管流域内的社会经济单位从世界各地的大型河流流域和许多地区的水资源中受益，但很少有流域多次经历过如此激进的社会经济结构变化。
+Second, by comparing the net effects of three different institutional structures split by two institutional shifts in the YRB, we can also better understand of the influence of structural alignments under a fixed basin.
+Although socioeconomic units within a basin benefit from water resources in large river basins all over the world and many locations have shown increased levels of regulation, few basins have experienced such radical SES structural changes several times (see \textit{Supplementary Material} S1).
+Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in SES institutional structure.
+% 因此，黄河流域的“流域固定效应”为SES结构的自我比较提供了宝贵的机会。
+% Thus, the YRB provides valuable settings for understanding the direct impacts of changes in SES institutional structure.
+
+% 未来的政策建议
 % 近年来黄河流域面临的分水制度调整问题也说明了动态设置配额的重要性。

### 2022-03-28 docs/papers/01_manuscript/drafs.tex
docs(introduction-rectification-and-results-part1-finished): embed results and discussions to make the novel more fluent
BREAKING CHANGE:

--- 2022-03-20 docs/papers/01_manuscript/04_discussion.tex
@@
-%! Author = songshgeo
-%! Date = 2022/3/10
+drafs.tex
+
+\section{introduction}
+% At the same time, undesired and unsustainable outcomes (e.g., failures in environmental regulation of highly polluting industries or the development of “tragedy of the commons” situations when pursuing more water resources), with considerable ecological degradation, have attracted much attention \cite{saylesSocialecologicalnetworkanalysis2019,caiPollutingthyneighbor2016,castilla-rhoSocialtippingpoints2017}.
+Two particular weaknesses in existing knowledge include understanding (1) the causal links between SES structures and outcomes; and (2) details of the underlying processes, especially the coordination of the incentives of different participants, that result from an institutional lack of fit.
+These weaknesses limit our understanding of institutional design, and they may reduce the speed and transfer of new knowledge and experience related to improving the sustainability of comprehensive water resources management.
+
+% In order to disentangle the relationship between SES structure and outcomes, we analyzed a case study to show how an institutional shift led to a structural mismatch that triggered unsustainable water use and unintended ecological deterioration.
+% Water is the key exclusive and competitive resource that couples socioeconomic and ecological systems (known as common-pool resources, CPRs) \cite{wutichWaterScarcitySustainability2009,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017,castilla-rhoGroundwaterCommonPool2020}.
+% Conflicts of interest often occur in allocation and competitions of water resources, with water governance policies often leading to long-term changes in human–water relationships and the redistribution of benefits \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013,chingManagingsocioecologyvery2015}.
+
+% Two rapid shifts in institutional structure that occurred in 1987 and 1998 (see Supplementary Material S1) provide unique settings to exploit quasi-natural experiments of a large river basin, the Yellow River Basin (YRB) in China \cite{xiaDevelopmentWaterAllocation2012}.
+
+% After a period of severe drying up, an institutional shift implemented in 1987 represented the beginning of attempts to control water use in the YRB through the use of quotas, with the goals of alleviating conflicts between supply and demand and achieving sustainable development.
+
+% Our results show that this initiative actually accelerated water withdrawals, resulting in an unintended “sprint effect”, where institutional mismatches created an even stronger incentive for each resource user to withdraw resources until the next major institutional shift in 1998.
+% Our analysis contributes to a deeper understanding of the mechanisms underlying the relationships among institutions, SES structures, and outcomes.
+By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings are consistent with the urgent calls for a more dynamic design for water use allocation to achieve sustainability.
+
+\section{Institutions and SES structures}
+% 机构可以塑造社会经济体系的结构，对其进行抽象是机械地理解结构和结果之间联系的第一步。
+Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{fig:framework}A).
+% 例如，机构可以创建一种被确定为与良好的社会经济效益相关联的水平匹配结构，如果它鼓励管理相连生态成分的不同行动者之间的协作(图1B)。
+For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{fig:framework}B), leading to sustainable outcomes.
+% 例如，机构可以创建一个结构，鼓励不同行为者之间的合作，管理相连的生态成分
+Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{fig:framework}C and D).
+% 在实践中，一个大型、复杂的河流流域的制度变化将创造或摧毁数百种不同的联系。这些局部变化的更广泛影响可以从系统的整体行为中看到。
+% 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
+We thus explored the causal linkages between the SES structures and sustainability (outcomes) in quasi-natural experiments of the YRB, which provides an informative case study for two main reasons.
+% 首先，长江流域管理的急剧结构变化使我们能够定量估计高层制度设计变化对用水的净影响。决定水分配的制度包括自下而上的协议或社会规范，以及自上而下的配额或法规，它们对社会经济结构有不同的影响;自上而下的监管可能会立即引发制度转变和SES的剧烈结构性变化。通过与由自下而上的制度转变引起的更渐进的变化相比，探索自上而下变化的影响，在对社会经济地位的定量分析中，极大地减少了来自不可观测因素的潜在干扰，提高了社会经济地位结构和结果之间因果关系的清晰度。
+First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use.
+Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013}; top-down regulations can trigger immediate institutional shifts, and sharp SES structural changes \cite{speedBasinwaterallocation2013,rolandUnderstandinginstitutionalchange2004}.
+In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and improves the clarity of the causal link between SES structure and outcome.
+% 其次，通过比较长江流域两次制度变迁所分裂的三种不同制度结构的净效应，我们也可以更深入地理解“盆地固定效应”下结构格局的影响。尽管流域内的社会经济单位从世界各地的大型河流流域和许多地区的水资源中受益，但很少有流域多次经历过如此激进的社会经济结构变化。
+Second, by comparing the net effects of three different institutional structures split by two institutional shifts in the YRB, we can also better understand of the influence of structural alignments under a fixed basin.
+Although socioeconomic units within a basin benefit from water resources in large river basins all over the world and many locations have shown increased levels of regulation, few basins have experienced such radical SES structural changes several times (see \textit{Supplementary Material} S1).
+Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in SES institutional structure.
+% 因此，黄河流域的“流域固定效应”为SES结构的自我比较提供了宝贵的机会。
+% Thus, the YRB provides valuable settings for understanding the direct impacts of changes in SES institutional structure.
+
+\section{results}
+% % 然后，我们反复比较了两个SES结构(分别自1987年和1998年)，以量化是否有显著不同的影响，YRB用水或分配。
+% Then we repeatedly compared between two SES structures (since 1987 and 1998, respectively) to quantify if there were significantly different impacts on water uses or allocation (\textbf{methods}).
+
+\section{discussion}
 % 我们展示了不匹配的分配制度是如何导致激励失真导致水资源加速耗竭的(即“冲刺效应”)。“冲刺效应”是CPR系统面临的一种特殊情况，在这种情况下，制度的不匹配为每个资源使用者创造了更强的动机(扭曲)，促使他们收回资源

### 2022-03-28 docs/papers/01_manuscript/manuscript.tex
docs(introduction-rectification-and-results-part1-finished): embed results and discussions to make the novel more fluent
BREAKING CHANGE:

@@
 \author{Xutong Wu$^{1,2}$}
+
 \author{Graeme S. Cumming$^{4}$}
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=16pc]{diagrams/framework.jpg}
-	\caption{
-		Framework for understanding linkages between SES structures and outcomes.
-		\textbf{a.} The general framework for analyzing social-ecological systems (SESs) (adapted from Ostrom \cite{ostromGeneralFrameworkAnalyzing2009}).
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=16pc]{diagrams/framework.jpg}
+%	\caption{
+%		Framework for understanding linkages between SES structures and outcomes.
+%		\textbf{a.} The general framework for analyzing social-ecological systems (SESs) (adapted from Ostrom \cite{ostromGeneralFrameworkAnalyzing2009}).
 Institutions embedded in SESs may reshape structures by changing the interactions between core subsystems, resulting in different outcomes.
-        Three typical types of abstracted SES structures are shown as \textbf{b.}, \textbf{c.} and \textbf{d.} (adapted from Bodin, 2017)\cite{bodinCollaborativeenvironmentalgovernance2017}.
+%        Three typical types of abstracted SES structures are shown as \textbf{b.}, \textbf{c.} and \textbf{d.} (adapted from Bodin, 2017)\cite{bodinCollaborativeenvironmentalgovernance2017}.
 Red circles indicate social actors, and green ones indicate ecological components.
@@
 The gray dashed lines show aligned SES structures that are more likely to result in a desirable outcome according to empirical evidence.
-	}
-    \label{fig:framework}
-\end{figure}
+%	}
+%    \label{fig:framework}
+%\end{figure}
 
-\section{Context of institutional shifts}\label{institution}
-\input{02_institution.tex}
+%\section{Context of institutional shifts}\label{institution}
+%\input{02_institution.tex}
 
@@
 
-\section{RESULTS}\label{results}
-\subsection{SPRINT EFFECT}\label{phenomenon}
+\section{RESULTS AND DISCUSSION}\label{results}
+%\begin{figure*}[!h]
+%    \centering
+%    \includegraphics[width=32pc]{outputs/main_results2.jpg}
+%    \caption{
+%        Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
+\textbf{A}: water uses of the YRB before and after the institutional shift in 1987 (87-WAS); \textbf{A}: water uses of the YRB before and after the institutional shift in 1998 (98-UBR).
+While the blue lines are observed data, gray ones are estimated by the Differenced Synthetic Control method with economic and environmental background controlled.
+\textbf{C}
+%    }
+%    \label{fig:main_results}
+%\end{figure*}
+
 \input{03_results.tex}
+\input{04_discussion.tex}
+%\subsection{CAUSES}\label{causes}
+%\input{model}
+%\input{table.tex}
 
-\begin{figure}
-    \centering
-    \includegraphics[width=16pc]{outputs/main_results.jpg}
-    \caption{
-        Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
-(\textbf{A} to \textbf{C}: Entering the mismatched SES structure in 1987; \textbf{D} to \textbf{E}: exiting the mismatch in 1998.
-\textbf{A} and \textbf{D}: Impact of the first institutional shift on water use trends in the YRB.
-Blue points are actual water use, and gray points are predicted use under a scenario without any institutional shift (see \textit{Methods}).
-\textbf{B} and \textbf{E}: Impact of the institutional shift on total water use.
-Dark bars indicate the difference between the actual and predicted water use in specific study periods.
-Gray bars are the expected water use, simulated by setting up placebo experiments (null models, see \textit{Methods}).
-\textbf{C} and \textbf{F}: Impact of institutional shift on water allocation equity (see \textit{Methods}).
-Red lines indicate the index calculated from actual water use data; gray lines indicate predicted water use under a scenario with unconstrained water use.
-    }
-    \label{fig:main_results}
-\end{figure}
-
-\subsection{CAUSES}\label{causes}
-\input{model}
-\input{table.tex}
-
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=16pc]{outputs/economic_model.jpg}
-	\caption{
-		% \textbf{Assumption 1:} \textit{(Production)} Assuming that water is the only input of the homogenous production function F(x) of each province.
+%\begin{figure}[!ht]
+%    \centering
+%    \includegraphics[width=16pc]{outputs/economic_model.jpg}
+%	\caption{
+%		% \textbf{Assumption 1:} \textit{(Production)} Assuming that water is the only input of the homogenous production function F(x) of each province.
 Under diminishing marginal returns assumption, and $F(x)$ is continuous, $F'(0)=\infty$, $ F'(\infty)=0$.
 The production output is under perfect competition, with constant unit price of P.
-		% \textbf{Assumption 2:} \textit{(Cost function)} Assuming that the ecology is a unity for the whole basin, the cost of water use is equally assigned to each province under any water use.
+%		% \textbf{Assumption 2:} \textit{(Cost function)} Assuming that the ecology is a unity for the whole basin, the cost of water use is equally assigned to each province under any water use.
 The unit cost of water is a constant C.
-		% \textbf{Assumption 3:} \textit{(Multi-period setting)} There are infinite periods with constant discount factor $\beta$ lying in (0,1) with no cross-period smoothing in water uses.
-		\textbf{A.} The relationship of marginal benefits and water use of province i at t = 0 for three different cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}, assuming $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, and $\beta=0.4$ as an example  (see \textit{Methods}In Case 3, water use by others is taken as a given, equal to the optimal water use for Case 2.
+%		% \textbf{Assumption 3:} \textit{(Multi-period setting)} There are infinite periods with constant discount factor $\beta$ lying in (0,1) with no cross-period smoothing in water uses.
+%		\textbf{A.} The relationship of marginal benefits and water use of province i at t = 0 for three different cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}, assuming $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, and $\beta=0.4$ as an example  (see \textit{Methods}In Case 3, water use by others is taken as a given, equal to the optimal water use for Case 2.
 The horizontal coordinate of each intersection of marginal benefits and the break-even line represents the optimal water use under each case.
-		\textbf{Panel B.} The relation between optimal water use of province i and total quota for Case 3, under time horizon of $T=5$, $T=10$, and an infinite $T$, respectively.
+%		\textbf{Panel B.} The relation between optimal water use of province i and total quota for Case 3, under time horizon of $T=5$, $T=10$, and an infinite $T$, respectively.
 The settings are the same as in \textbf{A}.
-	}
-	\label{fig:economic_model}
-\end{figure}
+%	}
+%	\label{fig:economic_model}
+%\end{figure}
 
-\section{DISCUSSION}\label{discussion}
-\input{04_discussion.tex}
+%\section{DISCUSSION}\label{discussion}
+%\input{04_discussion.tex}
 
-\section{Methods}
+\section{MATERIALS AND METHODS}
+Detailed methods are given inthe online supplementary material.
+
 % 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程

### 2022-03-28 func/handle.py

@@ -363,7 +363,18 @@ class ExpResultsHandler(Experiment):
         # TODO finish this
         pass
 
-    def plot_pre_post(self, actual, synth, ylabel, ax=None, figsize=(4, 3)):
+    def plot_pre_post(
+        self,
+        ylabel=None,
+        actual=None,
+        synth=None,
+        ax=None,
+        figsize=(4, 3),
+        axvline=True,
+    ):
+        if not actual and not synth:
+            synth, actual = self.summarize_analysis()
+            ylabel = self.parameters.get("Y_inputs")
         treat = self.parameters.get("treat_year")
         if not ax:
             _, ax = plt.subplots(figsize=figsize)
@@ -429,13 +440,14 @@ class ExpResultsHandler(Experiment):
         # ax.axvspan(x_min, treat, color=NATURE_PALETTE['NG'], alpha=0.4)
         ax.set_xticks([(treat + x_min) / 2, (x_max + treat) / 2])
         ax.set_xticklabels(["Before", "After"])
-        ax.axvline(
-            treat,
-            ls=":",
-            lw=4,
-            color=NATURE_PALETTE["NG"],
-            label="Policy: {}".format(treat),
-        )
+        if axvline:
+            ax.axvline(
+                treat,
+                ls=":",
+                lw=4,
+                color=NATURE_PALETTE["NG"],
+                label="Policy: {}".format(treat),
+            )
         ax.set_xlabel("")
 
         # spines visibility
@@ -558,6 +570,7 @@ class ExpResultsHandler(Experiment):
                 color=point_color,
             )
             ax2.text(
+                # TODO 查看一下为什么
                 s=note,
                 x=(max(true) + min(true)) / 2,
                 y=index - 0.5,

### 2022-03-29 docs/papers/00_cover_letter/abstract.tex
docs(paper-nsr-v1.1.0): primary manuscript for nsr, v-1.1.0
BREAKING CHANGE:

Increasing competition for water is challenging management institutions of large river basins worldwide. Institutions that successfully support sustainable water resource use are structurally well-aligned with water provisioning and social-ecological demands. However, what constitutes a well-aligned institution in this context is poorly understood. We analyzed institutional shifts in water governance, exploiting two quasi-natural experiments of the Yellow River Basin. First, using a Differenced Synthetic Control method to control economic and environmental contexts, we found the Water Allocation Scheme (87-WAS), which intended to limit water use, unexpectedly resulting in a structural mismatch of the social-ecological system (SES) with increased water use. We then applied a mathematical model to suggest that incentive distortions contributed to the rapid water use under the typical mismatched SES structure. Our analysis highlights the need to evaluate institutional fit in coupled human and natural systems carefully.

### 2022-03-29 docs/papers/01_manuscript/01_introduction.tex
docs(paper-nsr-v1.1.0): primary manuscript for nsr, v-1.1.0
BREAKING CHANGE:

@@
 Some institutional shifts were reported to have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and in collaborative water governance systems in Europe \cite{green2013}).
-However, shifting institutions in a large, complex river basin may create or destroy hundreds of different connections, where matched human-water relationships are not universal.
+However, shifting institutions in a large, complex river basin may create or destroy hundreds of different connections, where matched human-water relationships are not ubiquitous.
 Therefore, despite widespread recognition of the rising importance of institutions as an approach to water sustainable use within large river (especially transboundary river) basins, broader cascading effects of these changes are still in open discussion \cite{agrawal2003, persha2011, agrawal2001}.

### 2022-03-29 docs/papers/01_manuscript/02_results.tex
docs(paper-nsr-v1.1.0): primary manuscript for nsr, v-1.1.0
BREAKING CHANGE:

--- 2022-03-28 docs/papers/01_manuscript/03_results.tex
@@
 % \MakeUppercase{\subsection{Cascading effects of the institutional shifts}}
-\subsection{Cascading effects of the institutional shifts}
+\subsection{Institutional shifts effect on water use}
 \label{effects}
@@
 % 从70年代黄河断流开始摸索87-WAS的初步治理方案，到98-UBR成功解决断流后于2008年强化该制度，黄河一直是中国水治理制度转变的先行者。
-As a pioneer in water governance shifting in China, the YRB started to explore the initial water allocating scheme in the 1970s, then found a successful solution of dring-up in 1998, and promoted completely since 2008.
-% 1987年(87-WAS)和1998年(98-UBR)的制度变迁是YRB中两个被广泛认可的制度演变里程碑(图~\ref{fig:structure} \textit{S1 in  Supplementary  Methods})。
-Throughout, the institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones of water governance (Figure~\ref{fig:structure} and \textit{S1 in Supplementary Material}).
-Our analysis period, therefore, spans from 1975 to 2008, with the human-water system shifted between three different institutional structures (Figure~\ref{fig:structure}).
+As a pioneer in water governance shifting in China, the YRB started to explore the initial water allocating scheme in the 1970s, then found a successful solution of dring-up in 1998, and promoted entirely since 2008.
+% 1987年(87-WAS)和1998年(98-UBR)的制度变迁是YRB中两个被广泛认可的制度演变里程碑(图~\ref{structure} \textit{S1 in  Supplementary  Methods})。
+Throughout, the institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones of water governance (Figure~\ref{structure} and \textit{S1 in Supplementary Material}).
+Our analysis period, therefore, spans from 1975 to 2008, with the human-water system shifted between three different institutional structures (Figure~\ref{structure}).
 
 Here, we use Differenced Synthetic Control method, which considers economic growth and natural background, to estimate theoretical water uses scenarios without these policy interferences (\textbf{Methods}; \textit{S2 in Supplementary Material}).
-% 我们的结果表明，1987年(87-WAS)的制度转变实际上刺激了各省比没有干扰时使用更多的水，观测到比预期增加了10(图~\ref{fig:main_results}A和B)。
-Our results suggest that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without the interference (Figure~\ref{fig:main_results}A).
-% 在1998年制度再次改变后，用水量增加的趋势似乎被有效地抑制了，观察到的总用水量比预期减少了10(图~\ref{fig:main_results} C和D)。
-However, after the institution shifted again in 1998 (98-UBR), the trend of increasing water use appeared to be effectively suppressed, with total observed water consumption decreasing by $260\%$ relative to the estimation (Figure~\ref{fig:main_results} B).
+% 我们的结果表明，1987年(87-WAS)的制度转变实际上刺激了各省比没有干扰时使用更多的水，观测到比预期增加了10(图~\ref{main_results}A和B)。
+Our results suggest that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without the interference (Figure~\ref{main_results}A).
+% 在1998年制度再次改变后，用水量增加的趋势似乎被有效地抑制了，观察到的总用水量比预期减少了10(图~\ref{main_results} C和D)。
+However, after the institution shifted again in 1998 (98-UBR), the trend of increasing water use appeared to be effectively suppressed, with total observed water consumption decreasing by $260\%$ relative to the estimation (Figure~\ref{main_results} B).
 % 87-WAS后用水量的增加与1987 - 1998年地表径流严重干涸的事实相吻合，这是河流退化和环境危机的一个明显的试金石
-The increased water uses after 87-WAS align with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{fig:main_results}C).
+The increased water uses after 87-WAS align with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{main_results}C).
 % 尽管在1998年制度转变后的十年内，干旱程度有增无减，但断流的环境危机却得到了有效解决。
-On the other hand, although the density of droughts increased in the decade after the 98-UBR, the environmental crisis of river drying-up was effectively resolved (Figure~\ref{fig:main_results}C).
+On the other hand, although the density of droughts increased in the decade after the 98-UBR, the environmental crisis of river drying up was effectively resolved (Figure~\ref{main_results}C).
 % 正如许多研究指出的，这主要是大规模制度变迁的成功
@@
         \textbf{B.} water uses of the YRB before and after the institutional shift in 1998 (98-UBR).
-While the blue lines are statistic water use data, grey ones are the estimation from the Differenced Synthetic Control method with economic and environmental background controlled.
-        \textbf{C.}
+While the blue lines are statistic water use data, the grey ones are the estimation from the Differenced Synthetic Control method with economic and environmental background controlled.
+        \textbf{C.} Drought intensity in the YRB and drying up events of the Yellow River. Size of the grey bubbles denotes the length of a drying up stream.
     }
-    \label{fig:main_results}
+    \label{main_results}
 \end{figure*}
@@
 % 然而，87-WAS 也非大多分析报告所认为的“没有起到效果”，因为制度变化完全没有产生影响时，流域的用水量将更接近我们的模型预测。
-Furthermore, 87-WAS did not ``have no effect'' as previous analyses suggested because water uses will be closer to what our models predicted when the shift was a blank policy.
+Furthermore, 87-WAS did not ``have no effect'' as previous analyses suggested because water use will be closer to what our models predicted when the shift was a blank policy.
 % 除了环境背景外，我们的预测还考虑了经济因素，假设经济总量与用水量之间的生产函数保持不变。
@@
 % 在我们的研究期间(从1975年到2008年)，机构在三种不同的结构之间转换:免费访问、87-WAS和98-UBR。
-In our study period, the institution shifted between three different structures (XXX, XXX, and XXX) (Figure~\ref{fig:structure}).
-%! 这里还是需要名字的
+In our study period, the institution shifted between three different structures (Figure~\ref{structure} A to C).
 % 长江水利委员会是长江流域的主要负责人，其任务是报告和分析1998年以前长江流域的用水量(87-WAS之后)。
@@
 % 87-WAS带来的效果再一次说明了这种阻碍可持续性的治理结构需要得到重视。
-The cascading effect of the 87-WAS once again demonstrates that the more stakeholders, the more difficult it is to have a win-win situation of environment and interests \cite{hegwood2021} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.
+The cascading effect of the 87-WAS once again demonstrates that the more stakeholders, the more difficult it is to have a win-win situation of environment and interests \cite{hegwood2022} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.

### 2022-03-29 docs/papers/01_manuscript/03_causes.tex
docs(paper-nsr-v1.1.0): primary manuscript for nsr, v-1.1.0
BREAKING CHANGE:

%! Author = songshgeo
%! Date = 2022/3/10

% \MakeUppercase{\subsection{Mechanism of institutional shift effects}}
\subsection{Mechanism of institutional shift effects}
\label{reason}
Next, we explored the mechanisms linking the structures and the outcomes.
% 87-WAS 后各省响应的差异是理解制度影响机制的关键
Differences in provincial responses to 87-WAS are vital to understanding the mechanism of institutional shifts' impacts.
% 我们的结果表明，各省加速用水的比例（实际用水量超出模型预测用水量的比例）与各省黄河水取用量呈现显著正相关
Our results show that the proportion of accelerated water consumption in each province (the proportion of actual water consumption exceeding the predicted water consumption by the model) has a significant correlation to the Yellow River water consumption in each province (Figure~\ref{upset}A).
% 但明显的加速效应仅突出体现在主要用水省份上，对大多数省份来说，87-WAS 带来的影响并不大，
However, the apparent acceleration effect of the 87-WAS was only prominent in the significant water-using provinces (Neimeng, Henan, and Shandong), and there were no evident impacts for most provinces (Figure~\ref{upset}B).
% 尤其是常年超指标用水的山东与内蒙，分别在1987到1998年的十年间使用了高于模型预测值的xx%和xx%的用水量。
In particular, Shandong and Inner Mongolia, both provinces that exceeded the prescribed water uses of the 87-WAS, used xx\% and XX\% more water uses than predicted by the model from 1987 to 1998, respectively.

\begin{figure*}[!h]
    \centering
    \includegraphics[width=32pc]{outputs/upset.jpg}
    \caption{
        \textbf{A.} The partial correlation coefficient between wate uses (WU) of Yellow River (YR), unsatisfied ratio (compared with requirements in water plan and supply in the 87-WAS), and the average accelerated ratio.
        \textbf{B.} Average accelerated ratio of water uses for each province in the YRB during the decade after 87-WAS (from 1987 to 1998).
        \textbf{Mian users:} Major water consumption provinces (over the median).
        \textbf{Overused:} violate the 87-WAS in average water uses.
    }
    \label{upset}
\end{figure*}

We analyzed mathematically why the mismatched structure made win-wins holistically elusive in the institution shift of 87-WAS (\textit{method} and \textit{Supplementary Material S4}).
% 我们的模型表明，对于已经具有经济效率的用户来说，为了未来的经济增长而加速开采资源是由更大的边际收益引起的
Our model suggests that for users who are already economically efficient, greater marginal returns from water induce the acceleration of extracting resources for future economic growth (Figure~\ref{economic_model}).
% 因此，这种制度引发了一种与可持续用水意图背道而驰的激励扭曲。
Therefore, isolated stakeholders reacted variety to the similar marginal cost, and the institution of 87-WAS thus triggered an incentive distortion besides the initial intention of sustainable water use.
% 相反，中央管理(1998年以后的YRCC)能够有效降低边际生态成本
On the contrary, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs as stakeholders take corresponding responsibilities to the YRCC (\textit{Supplementary Material S4}).
% 制度结构和结果的差异呼应了SES成功治理的前景，通过间接(或垂直)在不同的利益相关者之间建立联系(在这种情况下是通过管理)
The alignments of differences in institutional structures and outcomes echo the hypothesis of successful governance in SES by indirectly (or vertically) creating links between different stakeholders (in the YRB cases, through administration).
%! citation

\begin{figure*}[!ht]
    \centering
    \includegraphics[width=24pc]{outputs/economic_model.jpg}
	\caption{
		% \textbf{Assumption 1:} \textit{(Production)} Assuming that water is the only input of the homogenous production function F(x) of each province. Under diminishing marginal returns assumption, and $F(x)$ is continuous, $F'(0)=\infty$, $ F'(\infty)=0$. The production output is under perfect competition, with constant unit price of P.
		% \textbf{Assumption 2:} \textit{(Cost function)} Assuming that the ecology is a unity for the whole basin, the cost of water use is equally assigned to each province under any water use. The unit cost of water is a constant C.
		% \textbf{Assumption 3:} \textit{(Multi-period setting)} There are infinite periods with constant discount factor $\beta$ lying in (0,1) with no cross-period smoothing in water uses.
		\textbf{A.} The relationship of marginal benefits and water use of province i at t = 0 for three different cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{structure}, assuming $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, and $\beta=0.4$ as an example  (see \textit{Methods}In Case 3, water use by others is taken as a given, equal to the optimal water use for Case 2. The horizontal coordinate of each intersection of marginal benefits and the break-even line represents the optimal water use under each case.
		\textbf{Panel B.} The relation between optimal water use of province i and total quota for Case 3, under time horizon of $T=5$, $T=10$, and an infinite $T$, respectively. The settings are the same as in \textbf{A}.
	}
	\label{economic_model}
\end{figure*}

Authentic the water quota (or the initial water rights) in our case studies went through a stage of "bargaining" among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
% 在水资源分配过程中，上下级决策者与利益相关者之间存在信息不对称，当前用水量越大的决策者议价能力越强。
With information asymmetry between upper-level decision-makers and lower-level stakeholders in water use allocation, those with more current water use might have greater bargaining power.
After 1987, the logical next step for provinces was to attempt to justify bargaining for larger quotas rather than immediately adopt resource-conserving transformations, as the trend of the water consumption intensity denotes (\textit{Supplementary Material S4}).
% 研究表明，如果仅考虑经济因素，用水量大户的体量与效率需要超出其配额的水资源
Studies show that the volume and efficiency of large water users need more water than their quota (in the 87-WAS) if only considering the economic factors when designing the institution.
In practice, therefore, although the affected provinces may not have directly encouraged excessive resource use because of the institutional shift, they had a larger incentive to show their economic potential
\cite{krieger1955, ostrom1990}.
As a result, while competing for potential water quotas, the provinces tended to hide the ecological costs behind economic development.

% 毫无疑问，随着资源竞争的日趋激烈，越来越多的SES正依赖着不同形式的制度进行资源分配（如自组织和政府干预），避免“短跑效应”的出现或将成为制度设计的关键。
With increasingly fierce competition for water, worldwide basins are developing institutions for governance (whether through self-organization or government intervention) \cite{andersson2020, wutich2009, cumming2020b}.
% 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
Adoption of an overall quota plays a vital role in preventing overuse of Common-pool Resources, like exclusive and competitive water resources.
However, various outcomes following institutional shifts of YRB demonstrates that stakeholders may react to quota with distortion when pursuing returns isolated under mismatched SES structures.
% 历史也证明，在87-WAS之后，各省、尤其是用水大省均对提出了异议，并持续上诉以寻求更大的配额。
History also shows that, after 87-WAS, provinces, especially water-intensive ones, challenged it and continued to appeal for larger quotas.
% 而在用水许可制度之后，这种寻求更大配额的外在诉求转变成了提升用水效率的内部革新。
After YRCC as governing agent coordinated between stakeholders since 98-UBR, the external appeal of provinces for larger quotas turned into internal innovation to improve water efficiency.
% 与生态尺度相匹配的代理人在成功治理的SES中作为 motif 反复出现，无论是在渔业、森林、还是在地下水治理中，表明减少与割裂生态fragment直接相连的独立利益相关者是结构产生良好效果的重要普遍性机制。
Agents matching the ecological scale appear widespread as motifs in SES of successful governance, whether in fisheries, forests, or groundwater management, suggesting that reducing independent stakeholders linked to fragmentation is an essential primary mechanism for a structure to produce good results.

### 2022-03-29 docs/papers/01_manuscript/04_discussion.tex
docs(paper-nsr-v1.1.0): primary manuscript for nsr, v-1.1.0
BREAKING CHANGE:

--- 2022-03-20 docs/papers/01_manuscript/04_discussion.tex
@@
 %! Date = 2022/3/10
-% 我们展示了不匹配的分配制度是如何导致激励失真导致水资源加速耗竭的(即“冲刺效应”)。“冲刺效应”是CPR系统面临的一种特殊情况，在这种情况下，制度的不匹配为每个资源使用者创造了更强的动机(扭曲)，促使他们收回资源
-We have shown how a mismatched allocation institution can lead to an accelerated depletion of water resources (i.e., the “sprint effect”) caused by incentive distortion.
-The sprint effect is a special case faced by CPR systems, where institutional mismatches create an even stronger incentive (with distortion) for each resource user to withdraw resources
-\cite{ostromRevisitingCommonsLocal1999,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017}.
-% 过往研究指出制度常常是避免公共池塘资源系统的崩溃的关键，但“短跑效应”的出现表明在自上而下进行制度设计所形成的错配SES结构中，制度也可以成为系统加速崩溃的触发者。
-Previous studies have suggested that institutions are often the key to avoid the collapse of a CPR system, but the emergence of a sprint effect shows that an institution with structural mismatches can also be the trigger that accelerates system collapse \cite{bodinConservationSuccessFunction2014,bodinCollaborativeenvironmentalgovernance2017,wangAlignmentsocialecological2019}.
-The initial formulation of the water quota in our case studies went through a stage of “bargaining” among stakeholders (from 1982 to 1987) \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}, where each province attempted to demonstrate its development potential related to water use.
-% 在高层决策者与低层利益相关者之间存在信息不对称的用水分配中，当前用水量越大的利益相关者议价能力越大。1987年以后，对各省来说，合乎逻辑的下一步是试图证明争取更大配额的合理性，而不是立即采取资源节约型改革。在实践中，尽管受影响的省份可能没有直接鼓励过度使用资源，但由于激励扭曲，他们有更大的动机对资源提取开绿灯。因此，在争夺潜在的水资源配额时，各省往往将生态成本隐藏在经济发展背后。
-In water use allocation with information asymmetry between upper-level decision-makers and lower-level stakeholders, those with more current water use might have greater bargaining power.
-After 1987, the logical next step for provinces was to attempt to justify bargaining for larger quotas rather than immediately adopt resource-conserving transformations.
-In practice, although the affected provinces may not have directly encouraged excessive resource use, they had a greater incentive to give the green light to resource withdrawals because of incentive distortions \cite{kriegerProgressGroundWater1955, ostromGoverningCommonsEvolution1990}.
-As a result, while competing for potential water quotas, the provinces tended to hide the ecological costs behind economic development.
 
-% 毫无疑问，随着资源竞争的日趋激烈，越来越多的SES正依赖着不同形式的制度进行资源分配（如自组织和政府干预），避免“短跑效应”的出现或将成为制度设计的关键。
-There is no doubt that with increasingly fierce competition for water, more and more SESs are developing new institutions for water allocation (whether through self-organization or government intervention) \cite{anderssonVoluntaryleadershipemergence2020, wutichWaterScarcitySustainability2009}.
-% 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
-Adoption of an overall quota plays an important role in preventing overuse of CPRs \cite{tilmanLocalizedprosocialpreferences2019}.
-However, the negative effects of incentive distortion imply a trade-off between long-term SES benefits and current stability, and the proportion of available resources allocated under quota schemes matters when institutions change \cite{ladeRegimeshiftssocialecological2013}.
-According to our analysis of plausible scenario assumptions based on our general economic model, the sprint effect will be reinforced when stakeholders anticipate that technological advances will amplify the benefits of water quotas in the future (see \textit{Supplementary Material S3}).
-% 然而，如果有水权转换机制允许利益相关者之间通过交易来弥补 shadow value，当前这种错乱的动机就不会那么强。
-However, if an institution allowed stakeholders to compensate for the shadow value (i.e., potential returns sacrificed due to water constraints and water scarcity) \cite{howarthAccountingvalueecosystem2002} of future water use, incentive distortion would be less devastating (e.g., through water rights transfer).
-Policymakers can also weaken the sprint effect by increasing the frequency of quota updates, supporting the idea that a more dynamic institution that responds to changing conditions (see \textit{Supplementary Material S3}) will adapt more effectively to its social-ecological context.
+\subsection{Novel insights and policy implications}
+\label{insights}
 
+% 由于87-WAS和98-UBR分别带来的两种结构在很多的SES中都是反复出现的构件，我们提出的机制对理解这类耦合系统至关重要
+Since the structures introduced by 87-WAS and 98-UBR are recurring motifs in many SES, our proposed mechanism is crucial to understanding such coupled systems.
+% 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
+Furthermore, we explored the causal linkages between the SES structures and sustainability (outcomes) in quasi-natural experiments of the YRB, which provides an informative case study for two main reasons.
+% 首先，长江流域管理的急剧结构变化使我们能够定量估计高层制度设计变化对用水的净影响。
+First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use.
+Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wang2019d,speed2013}; top-down regulations can trigger immediate institutional shifts, and sharp SES structural changes \cite{speed2013,roland2004}.
+In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and clarifies the causal link between SES structure and outcome.
+% 其次，通过比较长江流域两次制度变迁所分裂的三种不同制度结构的净效应，我们也可以更深入地理解“盆地固定效应”下结构格局的影响。尽管流域内的社会经济单位从世界各地的大型河流流域和许多地区的水资源中受益，但很少有流域多次经历过如此激进的社会经济结构变化。
+Second, we can better understand the influence of structural alignments under a fixed basin by comparing the net effects of three different institutional structures split by two institutional shifts in the YRB.
+Although socioeconomic units within a basin benefit from water resources in large river basins all over the world, and many locations have shown increased levels of regulation, few basins have experienced such radical SES structural changes several times (see \textit{Supplementary Material} S1).
+Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in the SES institutional structure.
+% 最后，我们的研究也存在一定局限性，那就是很难排除同期其他政策的效应。
+Finally, one of the limitations of our method is that it is difficult to rule out the effects of other policies over the same time breakpoints.
+% 然而，鉴于学者对于87-WAS与98-UBR两次制度转变的重要性基本达成共识，其结果差异仍对理解水治理有重要借鉴意义。
+However, since scholars have reached a consensus on the importance of the two institutional shifts of 87-WAS and 98-UBR, the differences in their results still provide important references for understanding water governance.
+
+% 我们的模型结果与机制探讨加深了SES结构的理解，强化了孤立利益相关者形成的结构不利于制度解决环境问题的基本认识
+Our results and discussion deepen the understanding of SES structure and strengthen the basic understanding that the mismatched structure formed by isolated stakeholders is not conducive to institutional solutions to environmental sustainability.
+% 而随后 98-UBR 的成功从理论和实际上都佐证了制度尺度匹配的重要性，即需要强调与生态单元的尺度（这里是流域尺度）相符的代理人建立利益相关者之间的横向联系。
+Moreover, the subsequent success of 98-UBR has proved the importance of institutional scale matching both theoretically and practically; that is, it is necessary to emphasize the establishment of potential connections between stakeholders by agents consistent with the scale of the ecological system (in this case, basinal scale and the YRCC).
+Furthermore, according to our analysis of plausible scenario assumptions based on our model, when stakeholders anticipate that technological advances will amplify the benefits of water quotas in the future, the incentive distortion will be reinforced (see \textit{Supplementary Material S4}).
+However, an institution allowed stakeholders to compensate for the shadow value (i.e., potential returns sacrificed due to water constraints and water scarcity) \cite{howarth2002} of future water use would weaken incentive distortion (e.g., through water rights transfer) (see \textit{Supplementary Material S4}).
+Policymakers can also propose a more dynamic institution by increasing the frequency of quota updates that responds to changing conditions will adapt more effectively to its social-ecological context (see \textit{Supplementary Material S4}).
+
+% 未来的政策建议
 % 近年来黄河流域面临的分水制度调整问题也说明了动态设置配额的重要性。
-Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of dynamic quota setting (see \textit{Supplementary Material S1}) \cite{yuAdaptabilityassessmentpromotion2019}.
+Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of dynamic quota setting (see \textit{Supplementary Material S1}) \cite{yu2019}.
 Following the institutional reforms of 1998, the Yellow River has not dried up since 1999.
-However, given recent changes in the YRB, its rigid resource allocation scheme can no longer meet the new demands of economic development \cite{wangThingsCurrentSignificance2019}.
-The Chinese government has embarked on an ambitious plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}).
-Other SESs around the world face similar problems in establishing successful resource allocation institutions \cite{cummingQuantifyingSocialEcologicalScale2020, muneepeerakulStrategicbehaviorsgovernance2017, cummingAdvancingunderstandingnatural2020, leslieOperationalizingsocialecologicalsystems2015}.
+However, given recent changes in the YRB, its rigid resource allocation scheme can no longer meet the new demands of economic development \cite{wang2019a}.
+As a result, the Chinese government has embarked on an ambitious plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}).
+Other SESs around the world face similar problems in establishing successful institutions for governance \cite{cumming2020b, muneepeerakul2017, cumming2020a, leslie2015}.
 These initiatives can benefit from our analysis by actively considering and incorporating social-ecological complexity and incentive structures when developing new approaches that avoid unsustainable outcomes.
-Our research provides a cautionary tale of how institutions can act as a double-edged sword when trying to attain sustainability.
+Our research provides a cautionary tale of how a mismatched structure of institutions can be a double-edged sword when attaining sustainability.

### 2022-03-29 docs/papers/01_manuscript/drafs.tex
docs(paper-nsr-v1.1.0): primary manuscript for nsr, v-1.1.0
BREAKING CHANGE:

@@
 These weaknesses limit our understanding of institutional design, and they may reduce the speed and transfer of new knowledge and experience related to improving the sustainability of comprehensive water resources management.
+
+% 机构可以塑造社会经济体系的结构，对其进行抽象是机械地理解结构和结果之间联系的第一步。
+Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{framework} A).
+% 例如，机构可以创建一种被确定为与良好的社会经济效益相关联的水平匹配结构，如果它鼓励管理相连生态成分的不同行动者之间的协作(图1B)。
+For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{framework} B), leading to sustainable outcomes.
+% 例如，机构可以创建一个结构，鼓励不同行为者之间的合作，管理相连的生态成分
+Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{framework} C and D).
 
@@
 The initial formulation of the water quota in our case studies went through a stage of “bargaining” among stakeholders (from 1982 to 1987) \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}, where each province attempted to demonstrate its development potential related to water use.
-% 在高层决策者与低层利益相关者之间存在信息不对称的用水分配中，当前用水量越大的利益相关者议价能力越大。1987年以后，对各省来说，合乎逻辑的下一步是试图证明争取更大配额的合理性，而不是立即采取资源节约型改革。在实践中，尽管受影响的省份可能没有直接鼓励过度使用资源，但由于激励扭曲，他们有更大的动机对资源提取开绿灯。因此，在争夺潜在的水资源配额时，各省往往将生态成本隐藏在经济发展背后。
-In water use allocation with information asymmetry between upper-level decision-makers and lower-level stakeholders, those with more current water use might have greater bargaining power.
-After 1987, the logical next step for provinces was to attempt to justify bargaining for larger quotas rather than immediately adopt resource-conserving transformations.
-In practice, although the affected provinces may not have directly encouraged excessive resource use, they had a greater incentive to give the green light to resource withdrawals because of incentive distortions \cite{kriegerProgressGroundWater1955, ostromGoverningCommonsEvolution1990}.
-As a result, while competing for potential water quotas, the provinces tended to hide the ecological costs behind economic development.
-
-% 毫无疑问，随着资源竞争的日趋激烈，越来越多的SES正依赖着不同形式的制度进行资源分配（如自组织和政府干预），避免“短跑效应”的出现或将成为制度设计的关键。
-There is no doubt that with increasingly fierce competition for water, more and more SESs are developing new institutions for water allocation (whether through self-organization or government intervention) \cite{anderssonVoluntaryleadershipemergence2020, wutichWaterScarcitySustainability2009}.
 % 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
@@
 Our research provides a cautionary tale of how institutions can act as a double-edged sword when trying to attain sustainability.
+
+% 我们展示了不匹配的分配制度是如何导致激励失真导致水资源加速耗竭的(即“冲刺效应”)。“冲刺效应”是CPR系统面临的一种特殊情况，在这种情况下，制度的不匹配为每个资源使用者创造了更强的动机(扭曲)，促使他们收回资源
+\cite{ostromRevisitingCommonsLocal1999,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017}.
+% 过往研究指出制度常常是避免公共池塘资源系统的崩溃的关键，但“短跑效应”的出现表明在自上而下进行制度设计所形成的错配SES结构中，制度也可以成为系统加速崩溃的触发者。
+Previous studies have suggested that institutions are often the key to avoiding the collapse of a CPR system, but the emergence of a sprint effect shows that an institution with structural mismatches can also be the trigger that accelerates system collapse \cite{bodinConservationSuccessFunction2014,bodinCollaborativeenvironmentalgovernance2017,wangAlignmentsocialecological2019}.
+
+##
+% Linking structures to outcomes need advancement when understanding an SES.
+Two particular weaknesses in existing knowledge include understanding (1) the causal links between SES structures and outcomes; and (2) details of the underlying processes, especially the coordination of the incentives of different participants, that result from an institutional lack of fit.
+These weaknesses limit our understanding of institutional design, and they may reduce the speed and transfer of new knowledge and experience related to improving the sustainability of comprehensive water resources management.
+
+The adverse effects of incentive distortion imply a trade-off between long-term SES benefits and current stability, and the proportion of available resources allocated under quota schemes matters when institutions change \cite{lade2013}

### 2022-03-29 docs/papers/01_manuscript/manuscript.tex
docs(paper-nsr-v1.1.0): primary manuscript for nsr, v-1.1.0
BREAKING CHANGE:

@@
 \authornote{\textbf{Corresponding authors.} Email: shuaiwang@bnu.edu.cn}
-\authornote{Shuang Song and Huiyu Wen equally contributed to this work.}
+%\authornote{Shuang Song and Huiyu Wen equally contributed to this work.}
 
@@
 %	}
-%    \label{fig:framework}
+%    \label{framework}
 %\end{figure}
@@
 
-\begin{figure}[!ht]
+\begin{figure*}[!ht]
     \centering
-    \includegraphics[width=16pc]{diagrams/structure.jpg}
+    \includegraphics[width=32pc]{diagrams/structure.png}
 	\caption{
@@
 		% 由于政策1与政策2都是为了解决黄河断流的生态问题而提出的，因此在结果与政策预期严重相反的第二时期（灰色阴影时段），是制度导致了错配的社会-生态系统结构。
-		\textbf{E.} A timeline of the Yellow River and drying conditions.
+%		\textbf{E.} A timeline of the Yellow River and drying conditions.
 The size of the circles indicates the length of section that dried up (km), and the y-axis indicates the length of the drying period.
@@
 	}
-	\label{fig:structure}
-\end{figure}
+	\label{structure}
+\end{figure*}
 
@@
 %    }
-%    \label{fig:main_results}
+%    \label{main_results}
 %\end{figure*}
-
-\input{03_results.tex}
+\input{02_results.tex}
+\input{03_causes.tex}
 \input{04_discussion.tex}
@@
 
-%\begin{figure}[!ht]
-%    \centering
-%    \includegraphics[width=16pc]{outputs/economic_model.jpg}
-%	\caption{
-%		% \textbf{Assumption 1:} \textit{(Production)} Assuming that water is the only input of the homogenous production function F(x) of each province.
-Under diminishing marginal returns assumption, and $F(x)$ is continuous, $F'(0)=\infty$, $ F'(\infty)=0$.
-The production output is under perfect competition, with constant unit price of P.
-%		% \textbf{Assumption 2:} \textit{(Cost function)} Assuming that the ecology is a unity for the whole basin, the cost of water use is equally assigned to each province under any water use.
-The unit cost of water is a constant C.
-%		% \textbf{Assumption 3:} \textit{(Multi-period setting)} There are infinite periods with constant discount factor $\beta$ lying in (0,1) with no cross-period smoothing in water uses.
-%		\textbf{A.} The relationship of marginal benefits and water use of province i at t = 0 for three different cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}, assuming $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, and $\beta=0.4$ as an example  (see \textit{Methods}In Case 3, water use by others is taken as a given, equal to the optimal water use for Case 2.
-The horizontal coordinate of each intersection of marginal benefits and the break-even line represents the optimal water use under each case.
-%		\textbf{Panel B.} The relation between optimal water use of province i and total quota for Case 3, under time horizon of $T=5$, $T=10$, and an infinite $T$, respectively.
-The settings are the same as in \textbf{A}.
-%	}
-%	\label{fig:economic_model}
-%\end{figure}
-
 %\section{DISCUSSION}\label{discussion}
@@
 \section{MATERIALS AND METHODS}
-Detailed methods are given inthe online supplementary material.
+%Detailed methods are given inthe online supplementary material.
 
@@
 This publicly available dataset was obtained from the National Water Resources Utilization Survey; details are accessible from Zhou (2020)
-\cite{zhouDecelerationChinahuman2020}.
+\cite{zhou2020}.
 A total of 10 provinces or regions have been directly affected by the water allocation institutional shifts in the YRB, accounting for $8.6\%$ of the total population of China (in 1990).
@@
 \subsection{Synthetic Control}
-Synthetic control is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadieSyntheticControlMethods2010}.
+Synthetic control is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadie2010, abadie2015, hill2021}.
 In this study, we used a comparative event approach and compared actual post-institutional shift induced water use changes with an appropriate counterfactual of what the water use change would have been.
 The counterfactual was built as the optimally weighted average of provinces not exposed to the institutional shifts.
-The synthetic control method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity \cite{billmeierAssessingEconomicLiberalization2013, smithresourcecurseexorcised2015}.
+The synthetic control method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity \cite{billmeier2013, smith2015}.
 In practice, each of the units (i.e., provinces) in the treated group were affected by institutional shifts in 1987 and 1998, each of which was taken as the “shifted” point $t_0$ and the two steady institutions as $t$ for analyzing in each shift.
@@
 \begin{case} Decentralized institution:
-    This case corresponds to a situation without any high-level water allocation institution (i.e., before 1987, see Figure~\ref{fig:structure} B).
+    This case corresponds to a situation without any high-level water allocation institution (i.e., before 1987, see Figure~\ref{structure} B).
 
@@
 \begin{case} Mismatched institution
-    This case corresponds to a mismatched institution (i.e., $1987\sim1998$, see Figure~\ref{fig:structure} C).
+    This case corresponds to a mismatched institution (i.e., $1987\sim1998$, see Figure~\ref{structure} C).
 
@@
 
-    This case corresponds to the institution under which the YRCC centrally managed water allocation between provinces (i.e., $1998\sim2008$, see Figure~\ref{fig:structure} D).
+    This case corresponds to the institution under which the YRCC centrally managed water allocation between provinces (i.e., $1998\sim2008$, see Figure~\ref{structure} D).
 

### 2022-03-29 docs/papers/paper.py

@@ -23,6 +23,7 @@ class SciPaper(dict):
 
 if __name__ == "__main__":
     print(os.getcwd())
+    root = os.getcwd()
     os.chdir(os.getcwd())
     title = params.get("title")
     abstract = params.get("abstract")
@@ -31,10 +32,12 @@ if __name__ == "__main__":
     keywords = ", ".join(keywords)
     print(title, abstract, authors, keywords)
 
-    for name, element in zip(
-        ["title", "abstract", "keywords"], [title, abstract, keywords]
-    ):
-        os.system(f"echo '{element}' > {name}.tex")
+    for folder in ["00_cover_letter", "01_manuscript", "02_appendix"]:
+        os.chdir(os.path.join(root, folder))
+        for name, element in zip(
+            ["title", "abstract", "keywords"], [title, abstract, keywords]
+        ):
+            os.system(f"echo '{element}' > {name}.tex")
     # os.system(f'zsh make.sh')
     # for name in ['title', 'abstract', 'keywords']:
     #     os.system(f"rm '{name}.tex'")

### 2022-04-04 docs/papers/01_manuscript/01_introduction.tex
docs(rectification-followed-grammarly.): Grammarly checking

@@
 % 水竞争的重要性
-Widespread freshwater scarcity and overuse, resulting in systematic risks on economies, societies, and ecosystems globally, are critical environmental challenges to sustainable development \cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
+Widespread freshwater scarcity and overuse, resulting in systematic risks to economies, societies, and ecosystems globally, are critical environmental challenges to sustainable development \cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
 With steadily increasing demand, competition for water is an urgent problem in water governance, where policies often lead to long-term changes in human–water relationships and the redistribution of benefits \cite{gleick2010, ziolkowska2016, wang2019d}.
@@
 % 制度的意义
-Institutions (such as policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled system, including interplays between social actors, between ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
+Institutions (such as policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled system, including interplays between social actors, ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
 Understanding the complex interlinkages is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
 Effective (“matched”) institutions operate at appropriate spatial, temporal, and functional scales to manage and balance these different relationships and interactions, therefore, supporting (but do not guarantee) sustainability of SES \cite{epstein2015, wang2019d}.
-Water governance tends to shift for institutional solutions within a complex basinal system, where societal drivers impact through water use and related technical interventions \cite{fischer2020}.
-Some institutional shifts were reported to have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and in collaborative water governance systems in Europe \cite{green2013}).
+Water governance tends to shift to institutional solutions within a complex basinal system, where societal drivers impact through water use and related technical interventions \cite{fischer2020}.
+Some institutional shifts, however, have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and collaborative water governance systems in Europe \cite{green2013}).
 However, shifting institutions in a large, complex river basin may create or destroy hundreds of different connections, where matched human-water relationships are not ubiquitous.
@@
 Supporting $35.63\%$ irrigation and $xx\%$ population with only $2.66\%$ of water resources in China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021), the overburdened Yellow River (YR) once dried up in consecutive years but successfully recovered through an institutional solution since 1998.
-Before the remarkable achievement in the restoration of river depletion, on the contrary, the first temptation to restrict water uses in the YR in 1987 (known as the ``87 Water Allocation Scheme, 87-WAS'') was recognized as a not fulfilling expectations institutional shift.
+Before the remarkable achievement in the restoration of river depletion, on the contrary, the first temptation to restrict water uses in the YR in 1987 (known as the ``87 Water Allocation Scheme, 87-WAS'') was recognized as a not fulfilling expectations of institutional shift.
 Until the 87-WAS, stakeholders have free access to the YR water resources, with geographic and temporal differences between freshwater demand and availability.
-As mismatch between demands and supply kept increasing, national authorities proposed in 87-WAS allocating certain water quota between $10$ provinces (or regions) along the YR basin.
-However, this controversial scheme helped little in turn water depletion around until a different strategy (Unified Basinal Regulation, 98-UBR) expanded responsibilities of basinal authorities in integrated water management, 1998, and started progress in the restoration.
+As the mismatch between demands and supply kept increasing, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin.
+However, this controversial scheme helped little in turning water depletion around until a different strategy (Unified Basinal Regulation, 98-UBR) expanded the responsibilities of basinal authorities in integrated water management in 1998 and started progress in the restoration.
 
 % 我们的研究
-The shifts of the water governance institution of YR refactored the interplays between humans and water with long-term cascading effects, leaving two quasi-natural experiments for understanding the interactions.
-By Differenced Synthetic Control method, our analysis on net effects of institutional shift shows that institutional mismatches contributed to acceleration water withdrawals for resource users after 98-WAS.
+The shifts in the water governance institution of YR refactored the interplays between humans and water with long-term cascading effects, leaving two quasi-natural experiments for understanding the interactions.
+By Differenced Synthetic Control method, our analysis of the net effects of institutional shift shows that institutional mismatches contributed to the acceleration of water withdrawals for resource users after 98-WAS.
 As few large river basins have experienced such radical structural changes several times, our quantitative analysis of institutional shifts in the YR induces a valuable understanding of water sustainable governance by decoupling natural and human interferences.

### 2022-04-04 docs/papers/01_manuscript/02_results.tex
docs(rectification-followed-grammarly.): Grammarly checking

@@
 % 87-WAS后用水量的增加与1987 - 1998年地表径流严重干涸的事实相吻合，这是河流退化和环境危机的一个明显的试金石
-The increased water uses after 87-WAS align with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{main_results}C).
+The increased water uses after 87-WAS aligns with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{main_results}C).
 % 尽管在1998年制度转变后的十年内，干旱程度有增无减，但断流的环境危机却得到了有效解决。
@@
 While the blue lines are statistic water use data, the grey ones are the estimation from the Differenced Synthetic Control method with economic and environmental background controlled.
-        \textbf{C.} Drought intensity in the YRB and drying up events of the Yellow River. Size of the grey bubbles denotes the length of a drying up stream.
+        \textbf{C.} Drought intensity in the YRB and drying up events of the Yellow River. The size of the grey bubbles denotes the length of a drying upstream.
     }

### 2022-04-04 docs/papers/01_manuscript/03_causes.tex
docs(rectification-followed-grammarly.): Grammarly checking

@@
 The horizontal coordinate of each intersection of marginal benefits and the break-even line represents the optimal water use under each case.
-		\textbf{Panel B.} The relation between optimal water use of province i and total quota for Case 3, under time horizon of $T=5$, $T=10$, and an infinite $T$, respectively.
+		\textbf{Panel B.} The relation between optimal water use of province $i$ and total quota for Case 3, under time horizon of $T=5$, $T=10$, and an infinite $T$, respectively.
 The settings are the same as in \textbf{A}.
@@
 % 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
-Adoption of an overall quota plays a vital role in preventing overuse of Common-pool Resources, like exclusive and competitive water resources.
-However, various outcomes following institutional shifts of YRB demonstrates that stakeholders may react to quota with distortion when pursuing returns isolated under mismatched SES structures.
+Adopting an overall quota plays a vital role in preventing the overuse of Common-pool Resources, like exclusive and competitive water resources.
+However, various outcomes following institutional shifts of YRB demonstrate that stakeholders may react to quota with distortion when pursuing returns isolated under mismatched SES structures.
 % 历史也证明，在87-WAS之后，各省、尤其是用水大省均对提出了异议，并持续上诉以寻求更大的配额。

### 2022-04-04 docs/papers/01_manuscript/04_discussion.tex
docs(rectification-followed-grammarly.): Grammarly checking

@@
 However, an institution allowed stakeholders to compensate for the shadow value (i.e., potential returns sacrificed due to water constraints and water scarcity) \cite{howarth2002} of future water use would weaken incentive distortion (e.g., through water rights transfer) (see \textit{Supplementary Material S4}).
-Policymakers can also propose a more dynamic institution by increasing the frequency of quota updates that responds to changing conditions will adapt more effectively to its social-ecological context (see \textit{Supplementary Material S4}).
+Policymakers can also propose a more dynamic institution by increasing the frequency of quota updates that responds to changing conditions and will adapt more effectively to its social-ecological context (see \textit{Supplementary Material S4}).
 

### 2022-04-05 docs/papers/01_manuscript/01_introduction.tex
docs(results1-analysis-section-2): appendix S3 and results1-section2
BREAKING CHANGE:

@@
 With steadily increasing demand, competition for water is an urgent problem in water governance, where policies often lead to long-term changes in human–water relationships and the redistribution of benefits \cite{gleick2010, ziolkowska2016, wang2019d}.
-Despite governments worldwide trying to resolve competition for water through deliberate institutions at large river basins, cascading effects of these initiatives are poorly understood \cite{giuliani2013, falkenmark2019, jaeger2019}.
+Despite governments worldwide trying to resolve competition for water through deliberate institutions at large river basins, cascading effects of these initiatives are poorly understood
+\cite{giuliani2013, falkenmark2019, jaeger2019}.
 
@@
 Water governance tends to shift to institutional solutions within a complex basinal system, where societal drivers impact through water use and related technical interventions \cite{fischer2020}.
-Some institutional shifts, however, have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and collaborative water governance systems in Europe \cite{green2013}).
+Some institutional shifts have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and collaborative water governance systems in Europe \cite{green2013}).
 However, shifting institutions in a large, complex river basin may create or destroy hundreds of different connections, where matched human-water relationships are not ubiquitous.
+%TODO 这里应该梳理 Institutional shift --> structures / building blocks.
 Therefore, despite widespread recognition of the rising importance of institutions as an approach to water sustainable use within large river (especially transboundary river) basins, broader cascading effects of these changes are still in open discussion \cite{agrawal2003, persha2011, agrawal2001}.
+% TODO 根据武老师的意见，这个KG应该再明确
+
+%! 这一段梳理一下 building blocks 的作用机制
+% Among
 
 % 黄河的制度介绍
-Supporting $35.63\%$ irrigation and $xx\%$ population with only $2.66\%$ of water resources in China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021), the overburdened Yellow River (YR) once dried up in consecutive years but successfully recovered through an institutional solution since 1998.
-Before the remarkable achievement in the restoration of river depletion, on the contrary, the first temptation to restrict water uses in the YR in 1987 (known as the ``87 Water Allocation Scheme, 87-WAS'') was recognized as a not fulfilling expectations of institutional shift.
+Supporting $35.63\%$ irrigation and $xx\%$ population with only $2.66\%$ of water resources in China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021), the overburdened Yellow River (YR) once dried up in consecutive years.
+For that, as a pioneer in water governance shifting in China, the YRB started to explore the initial water allocating scheme in the 1970s, then found a successful solution of dring-up in 1998, and promoted entirely since 2008.
+The institutional shifts in 1987 (known as the ``87 Water Allocation Scheme, 87-WAS'') and 1998 (Unified Basinal Regulation, 98-UBR) were two widely recognized milestones of water governance.
+Before the remarkable achievement in the restoration of river depletion since the 98-UBR, on the contrary, the first temptation to restrict water uses in the 87-WAS was recognized as a not fulfilling expectation of institutional shift.
 Until the 87-WAS, stakeholders have free access to the YR water resources, with geographic and temporal differences between freshwater demand and availability.
 As the mismatch between demands and supply kept increasing, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin.
-However, this controversial scheme helped little in turning water depletion around until a different strategy (Unified Basinal Regulation, 98-UBR) expanded the responsibilities of basinal authorities in integrated water management in 1998 and started progress in the restoration.
+However, this controversial scheme helped little in turning water depletion around until a different strategy expanded the responsibilities of basinal authorities in integrated water management in 1998 and started progress in the restoration.
 
@@
 As few large river basins have experienced such radical structural changes several times, our quantitative analysis of institutional shifts in the YR induces a valuable understanding of water sustainable governance by decoupling natural and human interferences.
+%! 这还要继续凝练我们的贡献
 By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings align with the urgent calls for a more dynamic design for water governance institutions to achieve sustainability.

### 2022-04-05 docs/papers/01_manuscript/02_results.tex
docs(results1-analysis-section-2): appendix S3 and results1-section2
BREAKING CHANGE:

@@
 \subsection{Institutional shifts effect on water use}
-\label{effects}
-% 从国家官员到流域管理官员，从省、市到区，长江流域自上而下的制度结构开始演变至今
-Including the national authorities, the basin management authorities, provinces, cities, and even districts, top-down institutional structures of the YRB started to evolve up to now (\textit{S1 in Supplementary Material}).
-% 从70年代黄河断流开始摸索87-WAS的初步治理方案，到98-UBR成功解决断流后于2008年强化该制度，黄河一直是中国水治理制度转变的先行者。
-As a pioneer in water governance shifting in China, the YRB started to explore the initial water allocating scheme in the 1970s, then found a successful solution of dring-up in 1998, and promoted entirely since 2008.
-% 1987年(87-WAS)和1998年(98-UBR)的制度变迁是YRB中两个被广泛认可的制度演变里程碑(图~\ref{structure} \textit{S1 in  Supplementary  Methods})。
-Throughout, the institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones of water governance (Figure~\ref{structure} and \textit{S1 in Supplementary Material}).
-Our analysis period, therefore, spans from 1975 to 2008, with the human-water system shifted between three different institutional structures (Figure~\ref{structure}).
+\label{result-1}
+% 结果一：
+% 1. 展示制度转变带来的用水量变化
+% 2. 解释结果的意义、合理性、
+% 3. 建立结果与结构之间的联系
 
-Here, we use Differenced Synthetic Control method, which considers economic growth and natural background, to estimate theoretical water uses scenarios without these policy interferences (\textbf{Methods}; \textit{S2 in Supplementary Material}).
-% 我们的结果表明，1987年(87-WAS)的制度转变实际上刺激了各省比没有干扰时使用更多的水，观测到比预期增加了10(图~\ref{main_results}A和B)。
+\label{result-1-p2}
+Here, we use Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without basinal policy interferences (\textbf{Methods}; \textit{S2 in Supplementary Material}).
 Our results suggest that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without the interference (Figure~\ref{main_results}A).
-% 在1998年制度再次改变后，用水量增加的趋势似乎被有效地抑制了，观察到的总用水量比预期减少了10(图~\ref{main_results} C和D)。
-However, after the institution shifted again in 1998 (98-UBR), the trend of increasing water use appeared to be effectively suppressed, with total observed water consumption decreasing by $260\%$ relative to the estimation (Figure~\ref{main_results} B).
-% 87-WAS后用水量的增加与1987 - 1998年地表径流严重干涸的事实相吻合，这是河流退化和环境危机的一个明显的试金石
+From 1988 to 1998, while the estimation of water use only suggests $956.38 km^3$, the observed water use of the YRB provinces reached $1038.36 km^3$ in sum, $8.57\%$ increased.
+However, after the institution shifted again in 1998 (98-UBR), the trend of increasing water use appeared to be effectively suppressed.
+From 1998 to 2008, the total observed water use decreased by $0.49 km^3$ per year, while the estimation of water use still suggests $1.03 km^3$ increases (Figure~\ref{main_results} B).
 The increased water uses after 87-WAS aligns with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{main_results}C).
-% 尽管在1998年制度转变后的十年内，干旱程度有增无减，但断流的环境危机却得到了有效解决。
-On the other hand, although the density of droughts increased in the decade after the 98-UBR, the environmental crisis of river drying up was effectively resolved (Figure~\ref{main_results}C).
-% 正如许多研究指出的，这主要是大规模制度变迁的成功
-As literature has suggested, this institution shift contributed a lot to the successful water governance.
+On the other hand, the environmental crisis of river drying up was effectively resolved after the 98-UBR, though the density of droughts still increased for decades (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{main_results}C).
+In line with previous literature had reported; therefore, the institution shift of 98-UBR contributed a lot to the successful water governance. %! citation
 
@@
     \centering
-    \includegraphics[width=32pc]{outputs/main_results2.jpg}
+    \includegraphics[width=32pc]{outputs/main_results2.pdf}
     \caption{
@@
 
-% 然而，87-WAS 也非大多分析报告所认为的“没有起到效果”，因为制度变化完全没有产生影响时，流域的用水量将更接近我们的模型预测。
-Furthermore, 87-WAS did not ``have no effect'' as previous analyses suggested because water use will be closer to what our models predicted when the shift was a blank policy.
-% 除了环境背景外，我们的预测还考虑了经济因素，假设经济总量与用水量之间的生产函数保持不变。
-Besides environmental background, our forecast takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textit{S2 in Supplementary Material}).
-% 由于单位水资源的生产效率在这一时期实际上保持了相似的趋势，这意味着流域用水量的加速增长不是经济增长的必然结果。
-However, the production efficiency of unit water resources kept similar trends between provinces of the YRB and others (Figure \textit{S3 in Supplementary Material}), which means that the accelerated growth of basinal water uses was not the inevitable result of economic growth.
-% 但实际上，我们的结果表明相对于正常的经济发展进程来说，黄河流域的水资源利用反而更像是受到了刺激。
-However, our results suggest that water use (especially for irrigation) in the YRB was more likely to be partly stimulated by the shift in 1987 besides economic growth.
-% 这种用水量的加速增长与制度设计时遏制用水、保护黄河流域有限的水资源的初衷相悖。
-This accelerated growth in water use was contrary to the original intention of the 87-WAS in conserving the limited water.
+% P2: 主要介绍结果的意义、合理性
+\label{result-1-p2}
+Besides environmental background, our forecast by DSC takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textit{S2 in Supplementary Material}).
+It means the forecast of water use includes the part caused by the increased economic volume, while the outcomes of the economy (GDP in different sectors) of the YRB maintained a parallel trend with other regions during the period (\textit{S3 in Supplementary Material} Figure~\ref{S3-1}).
+Therefore, 87-WAS did not ``have little effect'' as previous analyses suggested (cites) but led to increased water use because the difference between prediction and observation will be trivial when the shift was just a blank policy by applying the DSC method.
+%!
+Citation
+Water use efficiency is another crucial factor in interpreting the differences besides the economic factors (e.g., irrigated areas and industrial outcomes) considered and controlled by the method.
+In addition to the expansion of irrigation area after the 87-WAS, water uses per unit of irrigation area also rapidly widened the gap with the average level of the rest provinces.
+However, the industry water use intensity hardly changed (\textit{S3 in Supplementary Material} Figure~\ref{S3-2}).
+As a previous report sigh: although the key to alleviating the drought is saving water in the irrigated areas, the tragedy of scrambling for water appeared in provinces and irrigated areas %!
+\cite{mao2000}.
+In terms of the average ratio of water-saving irrigation area (refer to drip or sprinkler irrigation systems and canal lining), although there was a significant increase in the whole country after 1987, the YRB did not rapidly open a noticeable gap until about 1994 (Figure~\ref{S3-3}).
+As a result, despite the irrigation area expanding, scrambling for water resources without any incentive to optimize water efficiency accelerated holistic water use.
+This accelerated growth in water use was contrary to the original intention of the 87-WAS in conserving the limited water, and this failure of the institution was a major barrier to the sustainability of the Yellow River %!
+\cite{huangang2002}.
+
+% 过去的研究总结出87-WAS收效甚微的几个因素，然而我们发现的机制
 

### 2022-04-05 docs/papers/01_manuscript/03_causes.tex
docs(results1-analysis-section-2): appendix S3 and results1-section2
BREAKING CHANGE:

@@
 \subsection{Mechanism of institutional shift effects}
-\label{reason}
-Next, we explored the mechanisms linking the structures and the outcomes.
+\label{result-2}
+% 结果2部分：
+% 1. 加速用水增长的结果 for each province.
+% 2. Potential benefits for each stakeholder (economic model - assumption & results), and social-ecological fit holistically. 结合经济模型
+% 3. Why some building blocks fits for good outcomes. 结合 building block
+
+Next, we explored the mechanisms linking the structures and the outcomes by analyzing regional disparity in influenced water use for each province by institutional shifts.
 % 87-WAS 后各省响应的差异是理解制度影响机制的关键
@@
 In particular, Shandong and Inner Mongolia, both provinces that exceeded the prescribed water uses of the 87-WAS, used xx\% and XX\% more water uses than predicted by the model from 1987 to 1998, respectively.
+% 与黄河水取用量相比，各省对制度规定的分水配额的满意度（用各省实际分水与规划预期的差值表示）反而与这个加速效应的相关性并不显著。
+On the contrary, the satisfaction of each province with the water allocation stipulated by the 87-WAS (expressed by the difference between the actual water allocation of each province and the expected planning value) is not significantly correlated with this acceleration effect.
 
@@
 
+% 经济模型与理论解释
+%! 这里可以指出他们过去的经济发展路径
 We analyzed mathematically why the mismatched structure made win-wins holistically elusive in the institution shift of 87-WAS (\textit{method} and \textit{Supplementary Material S4}).
@@
 %! citation
-
-\begin{figure*}[!ht]
-    \centering
-    \includegraphics[width=24pc]{outputs/economic_model.jpg}
-	\caption{
-		% \textbf{Assumption 1:} \textit{(Production)} Assuming that water is the only input of the homogenous production function F(x) of each province.
-Under diminishing marginal returns assumption, and $F(x)$ is continuous, $F'(0)=\infty$, $ F'(\infty)=0$.
-The production output is under perfect competition, with constant unit price of P.
-		% \textbf{Assumption 2:} \textit{(Cost function)} Assuming that the ecology is a unity for the whole basin, the cost of water use is equally assigned to each province under any water use.
-The unit cost of water is a constant C.
-		% \textbf{Assumption 3:} \textit{(Multi-period setting)} There are infinite periods with constant discount factor $\beta$ lying in (0,1) with no cross-period smoothing in water uses.
-		\textbf{A.} The relationship of marginal benefits and water use of province i at t = 0 for three different cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{structure}, assuming $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, and $\beta=0.4$ as an example  (see \textit{Methods}In Case 3, water use by others is taken as a given, equal to the optimal water use for Case 2.
-The horizontal coordinate of each intersection of marginal benefits and the break-even line represents the optimal water use under each case.
-		\textbf{Panel B.} The relation between optimal water use of province $i$ and total quota for Case 3, under time horizon of $T=5$, $T=10$, and an infinite $T$, respectively.
-The settings are the same as in \textbf{A}.
-        }
-	\label{economic_model}
-\end{figure*}
 

### 2022-04-05 docs/papers/01_manuscript/drafs.tex
docs(results1-analysis-section-2): appendix S3 and results1-section2
BREAKING CHANGE:

@@
 Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{framework} C and D).
+
+% 从国家官员到流域管理官员，从省、市到区，长江流域自上而下的制度结构开始演变至今
+Including the national authorities, the basin management authorities, provinces, cities, and even districts, top-down institutional structures of the YRB started to evolve up to now (\textit{S1 in Supplementary Material}).
+
+Our analysis period, therefore, spans from 1975 to 2008, with the human-water system shifted between three different institutional structures (Figure~\ref{structure}).
 

### 2022-04-05 docs/papers/01_manuscript/model.tex
docs(results1-analysis-section-2): appendix S3 and results1-section2
BREAKING CHANGE:

--- 2022-03-10 docs/papers/elements/model.tex
@@
 % These theoretical predictions, further from the phenomenon observed in the YRB, attributing ``sprint effect'' into raising marginal benefits -by pursuing indirectly generating shadow value of water use while converting fixed marginal costs to irrelevant cost for each individual province.
+
+\begin{figure*}[!ht]
+    \centering
+    \includegraphics[width=24pc]{outputs/economic_model.jpg}
+	\caption{
+		% \textbf{Assumption 1:} \textit{(Production)} Assuming that water is the only input of the homogenous production function F(x) of each province.
+Under diminishing marginal returns assumption, and $F(x)$ is continuous, $F'(0)=\infty$, $ F'(\infty)=0$.
+The production output is under perfect competition, with constant unit price of P.
+		% \textbf{Assumption 2:} \textit{(Cost function)} Assuming that the ecology is a unity for the whole basin, the cost of water use is equally assigned to each province under any water use.
+The unit cost of water is a constant C.
+		% \textbf{Assumption 3:} \textit{(Multi-period setting)} There are infinite periods with constant discount factor $\beta$ lying in (0,1) with no cross-period smoothing in water uses.
+		\textbf{A.} The relationship of marginal benefits and water use of province i at t = 0 for three different cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{structure}, assuming $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, and $\beta=0.4$ as an example  (see \textit{Methods}In Case 3, water use by others is taken as a given, equal to the optimal water use for Case 2.
+The horizontal coordinate of each intersection of marginal benefits and the break-even line represents the optimal water use under each case.
+		\textbf{Panel B.} The relation between optimal water use of province $i$ and total quota for Case 3, under time horizon of $T=5$, $T=10$, and an infinite $T$, respectively.
+The settings are the same as in \textbf{A}.
+        }
+	\label{economic_model}
+\end{figure*}

### 2022-04-05 docs/papers/02_appendix/03_results_appendix.tex
docs(results1-analysis-section-2): appendix S3 and results1-section2
BREAKING CHANGE:

\graphicspath{{../../../figs/}}

\begin{figure*}
    \includegraphics[width=0.7\linewidth]{outputs/economy.pdf}
    \centering
    \caption{test}
    \label{S3-1}
\end{figure*}

\begin{figure*}
    \includegraphics[width=0.7\linewidth]{outputs/S3_WUI.pdf}
    \centering
    \caption{test}
    \label{S3-2}
\end{figure*}

\begin{figure*}
    \includegraphics[width=0.7\linewidth]{outputs/S3_wci.pdf}
    \centering
    \caption{test}
    \label{S3-3}
\end{figure*}

### 2022-04-05 func/handle.py
feat(appendix-S3-analyze-economic-and-wui-factors-to-explain-the-increasement): add gam in tool, compare provinces in the YRB and others in gdp, wui, wci
BREAKING CHANGE:

@@ -420,16 +420,22 @@ class ExpResultsHandler(Experiment):
             s=50,
             alpha=0.4,
         )
+        y_sim_obs, k_obs = get_optimal_fit_linear(
+            obs_post.index, obs_post.values
+        )
         ax.plot(
             obs_post.index,
-            get_optimal_fit_linear(obs_post.index, obs_post.values),
+            y_sim_obs,
             color=NATURE_PALETTE["NCC"],
             lw=2,
             ls="--",
         )
+        y_sim_syn, k_syn = get_optimal_fit_linear(
+            syn_post.index, syn_post.values
+        )
         ax.plot(
             syn_post.index,
-            get_optimal_fit_linear(syn_post.index, syn_post.values),
+            y_sim_syn,
             color="gray",
             lw=2,
             ls="--",
@@ -458,7 +464,7 @@ class ExpResultsHandler(Experiment):
         ax.spines["bottom"].set_visible(True)
         ax.set_ylabel(ylabel=ylabel)
         ax.set_xlabel("")
-        return ax
+        return {"k_obs": k_obs, "k_syn": k_syn}
 
     def plot_upset(
         self, items, threshold=0.05, figszie=(8, 4), height_ratio=(3, 1.5)

### 2022-04-05 func/tools.py

@@ -13,6 +13,7 @@ import numpy as np
 import pandas as pd
 import xarray as xr
 from affine import Affine
+from matplotlib import pyplot as plt
 from qcloudsms_py import SmsSingleSender
 from qcloudsms_py.httpclient import HTTPError
 from rasterio import features
@@ -78,7 +79,7 @@ def get_optimal_fit_linear(x_arr, y_arr):
 
     k, b = optimize.curve_fit(linear, x_arr, y_arr)[0]  # optimize
     y_sim = linear(x_arr, k, b)  # simulated y
-    return y_sim
+    return y_sim, k
 
 
 def extract_mean_std(data, start, end):
@@ -240,3 +241,53 @@ def show_files(path, all_files=None, full_path=False, suffix=None):
             else:
                 all_files.append(file)
     return all_files
+
+
+def plot_gam_and_interval(
+    x,
+    y,
+    main_color="#29303C",
+    err_color="gray",
+    width=0.95,
+    ax=None,
+    err_space=True,
+    alpha=0.1,
+    scatter_alpha=0.8,
+    y_label="Y",
+):
+    if not ax:
+        fig, ax = plt.subplots()
+
+    import pygam
+
+    X = x.reshape(-1, 1)
+
+    gam = pygam.LinearGAM(n_splines=25).gridsearch(X, y)
+    XX = gam.generate_X_grid(term=0, n=500)
+
+    ax.plot(
+        XX,
+        gam.predict(XX),
+        color=main_color,
+        label="{} GAM Fitted".format(y_label),
+    )  # 拟合曲线
+    ax.scatter(X, y, facecolor=main_color, alpha=scatter_alpha, label="")  # 散点
+
+    if err_space:
+        err = gam.prediction_intervals(XX, width=width)
+        ax.plot(
+            XX,
+            gam.prediction_intervals(XX, width=width),
+            color=err_color,
+            ls="--",
+        )  # 置信区间
+        ax.fill_between(
+            XX.reshape(
+                -1,
+            ),
+            err[:, 0],
+            err[:, 1],
+            color=err_color,
+            alpha=alpha,
+            label="{} Confidence interval".format(y_label),
+        )

### 2022-04-06 docs/papers/01_manuscript/02_results.tex
docs(analyze-results-in-discussion): results analysis

@@
 
-% 过去的研究总结出87-WAS收效甚微的几个因素，然而我们发现的机制
-
-% 两次制度转变带来的级联效应存在巨大差异
-The cascading effects of the two institutional shifts were very different, while their reframed SES structures have direct differences.
-% 在我们的研究期间(从1975年到2008年)，机构在三种不同的结构之间转换:免费访问、87-WAS和98-UBR。
-In our study period, the institution shifted between three different structures (Figure~\ref{structure} A to C).
-% 长江水利委员会是长江流域的主要负责人，其任务是报告和分析1998年以前长江流域的用水量(87-WAS之后)。
-However, the YRCC, whose primary official response to the river before 1998, the mandate was to conserve the riverway environment, construct and maintain infrastructures, and report on and analyze water consumption (after the 87-WAS) in the YRB, i.e., connecting the ecological nodes (different river reaches) horizontally ~\cite{wang2019a}.
-% 这意味着，而与生态节点直接联系的各利益相关者之间没有横向连接。
-Thus, until the institutional shift of 98-UBR, with no necessity to apply for a water permit from YRCC, there were no horizontal connections (cooperations or agreements) between the various stakeholders (provinces) directly connected to the ecological sections.
-% 许多不同领域的经验研究指出这种结构很可能是错配的，因为这些利益相关者难以从全局出发维护好互相联系的生态系统。
-Empirical studies in many different fields indicate that this structure is likely to be mismatched, as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
+% 过去的研究总结出87-WAS收效甚微的几个因素：
+Previous studies have summarised factors that contribute to the non-ideal effect of 87-WAS: (1) The YRCC had no right to punish the provinces for over-exploitation; (2) the water quotas were annual values, causing provinces to rob water in the dry season; (3) The YRCC can make statistics on water use in the mainstream but cannot on the tributaries, so provinces water use underreport %!
+\cite{huangang2002}.
+However, the effects of the two institutional shifts (the 87-WAS and the 98-UBR) were significantly different, which the above reasons cannot fully explain.
+Between the 98-UBR and the further refinement of the unified regulation in 2008, there was still a lack of a temporary water allocation scheme and effective monitoring of tributaries.
+Moreover, without any actual punishment, provinces with high water consumption (such as Inner Mongolia and Shandong) continued to exceed the quota after 98-UBR.
+As we have analyzed (Figure~\ref{structure}), the difference between the two institutional shifts is mainly reflected in the structure of linkages between social actors.
+Until the institutional shift of 98-UBR, with no necessity to apply for a water permit from YRCC, there were no horizontal connections (cooperations or agreements) between the various stakeholders (provinces) directly connected to the ecological units.
+Make it clear that the YRCC was responsible for regulating provincial water use; that is, each province has made it clear that in the long run, water resources are not ``internal'' but ``dependent''.
+By taking the structure before and after the two institutional shifts as different basic assumptions (before 87-WAS: free access to water; after 87-WAS but before 98-UBR: decisions on water use under quotas; after 98-UBR: unified regulation), we use the marginal benefit model to analyze the theoretical optimal water consumption of stakeholders in each scenario.
+The analysis of the model also shows that 98-UBR can reduce the overall water use of the basin while 87-WAS can increase the water use of the basin when the same parameters are guaranteed but the institutional structure changes.
+Empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
 \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
-% 87-WAS带来的效果再一次说明了这种阻碍可持续性的治理结构需要得到重视。
-The cascading effect of the 87-WAS once again demonstrates that the more stakeholders, the more difficult it is to have a win-win situation of environment and interests \cite{hegwood2022} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.
+The effect of the institutional shifts once again demonstrated that it is not easy to have a win-win situation of environment and interests in complex coupled human-nature systems \cite{hegwood2022} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.

### 2022-04-06 func/handle.py
fix(upset-plot-could-not-sort-index-in-ax2,-ax3): handle upset plot now plot correctly

@@ -103,7 +103,7 @@ class ExpResultsHandler(Experiment):
             diff_sum = diff.loc[start:end].sum()
             statistic.loc[province, "diff_sum"] = diff_sum
             synth_sum = data[f"{province}_synth"].loc[start:end].sum()
-            statistic.loc[province, "diff_ratio"] = diff_sum / synth_sum
+            statistic.loc[province, "diff_ratio"] = diff_sum / abs(synth_sum)
 
         wu_total = self.dfs.get("wu_all")
         wu_yr = self.dfs.get("wu_yr")
@@ -122,8 +122,8 @@ class ExpResultsHandler(Experiment):
         statistic["unsatisfied"] = 1 - statistic["satisfied"]
         statistic["stress"] = statistic["unsatisfied"] * statistic["YR_WU"]
 
-        statistic["diff_ratio"] = (
-            statistic["diff_sum"] / statistic["diff_sum"].sum()
+        statistic["diff_ratio"] = statistic["diff_sum"] / abs(
+            statistic["diff_sum"].sum()
         )
         statistic["punished"] = statistic["scheme83"] - statistic["scheme87"]
 
@@ -537,6 +537,7 @@ class ExpResultsHandler(Experiment):
         point_color = NATURE_PALETTE["NS"]
         labels = []
         for index, (label, bools, note, corr, p_val) in enumerate(items):
+            bools = bools[ratio.index]
             true = []
             colors = [point_color if i else "gray" for i in bools]
             ax2.scatter(
@@ -576,7 +577,6 @@ class ExpResultsHandler(Experiment):
                 color=point_color,
             )
             ax2.text(
-                # TODO 查看一下为什么
                 s=note,
                 x=(max(true) + min(true)) / 2,
                 y=index - 0.5,

### 2022-04-06 docs/papers/01_manuscript/03_causes.tex
docs(results2-section1-show-results): describe upset plots

@@
 
-Next, we explored the mechanisms linking the structures and the outcomes by analyzing regional disparity in influenced water use for each province by institutional shifts.
-% 87-WAS 后各省响应的差异是理解制度影响机制的关键
-Differences in provincial responses to 87-WAS are vital to understanding the mechanism of institutional shifts' impacts.
-% 我们的结果表明，各省加速用水的比例（实际用水量超出模型预测用水量的比例）与各省黄河水取用量呈现显著正相关
-Our results show that the proportion of accelerated water consumption in each province (the proportion of actual water consumption exceeding the predicted water consumption by the model) has a significant correlation to the Yellow River water consumption in each province (Figure~\ref{upset}A).
-% 但明显的加速效应仅突出体现在主要用水省份上，对大多数省份来说，87-WAS 带来的影响并不大，
-However, the apparent acceleration effect of the 87-WAS was only prominent in the significant water-using provinces (Neimeng, Henan, and Shandong), and there were no evident impacts for most provinces (Figure~\ref{upset}B).
-% 尤其是常年超指标用水的山东与内蒙，分别在1987到1998年的十年间使用了高于模型预测值的xx%和xx%的用水量。
-In particular, Shandong and Inner Mongolia, both provinces that exceeded the prescribed water uses of the 87-WAS, used xx\% and XX\% more water uses than predicted by the model from 1987 to 1998, respectively.
-% 与黄河水取用量相比，各省对制度规定的分水配额的满意度（用各省实际分水与规划预期的差值表示）反而与这个加速效应的相关性并不显著。
-On the contrary, the satisfaction of each province with the water allocation stipulated by the 87-WAS (expressed by the difference between the actual water allocation of each province and the expected planning value) is not significantly correlated with this acceleration effect.
+Differences between stakeholders in responses to institutional shifts are vital to understanding the mechanism between structures and outcomes.
+Our results show that the proportion of accelerated water use in each province after the decade of 87-WAS (the proportion of actual water use exceeding the predicted water use by the model) has a significant correlation ($p<0.05$, see \textbf{Methods}) to the Yellow River water use in each province (Figure~\ref{upset}A).
+Furthermore, while no evident impacts for most provinces (no more than $10\%$ differences, the apparent acceleration effects were only prominent in the big water-using provinces (e.g., Neimeng, Henan, and Shandong.
+Figure~\ref{upset}B).
+In particular, Neimeng and Shandong, both provinces that exceeded the prescribed water uses of the 87-WAS, used $44.25\%$ and $25.69\%$ more water uses than the prediction from 1987 to 1998, respectively.
+Furthermore, the satisfaction of each province with the water allocation stipulated by the 87-WAS (expressed by the difference between the actual water allocation of each province and the expected planning value) is not significantly correlated with the acceleration.
+By contrast, after the 98-UBR, with the exception of Shaanxi (which has always been abundant in water quota) had evident ($17.53\%$) increasd water use, almost all provinces have seen significant declines in water use ($-12.5\%$ on average).
+Neither the satisfaction nor Yellow River water use, however, have correlation with the declines.
 
@@
 We analyzed mathematically why the mismatched structure made win-wins holistically elusive in the institution shift of 87-WAS (\textit{method} and \textit{Supplementary Material S4}).
-% 我们的模型表明，对于已经具有经济效率的用户来说，为了未来的经济增长而加速开采资源是由更大的边际收益引起的
 Our model suggests that for users who are already economically efficient, greater marginal returns from water induce the acceleration of extracting resources for future economic growth (Figure~\ref{economic_model}).
-% 因此，这种制度引发了一种与可持续用水意图背道而驰的激励扭曲。
 Therefore, isolated stakeholders reacted variety to the similar marginal cost, and the institution of 87-WAS thus triggered an incentive distortion besides the initial intention of sustainable water use.
-% 相反，中央管理(1998年以后的YRCC)能够有效降低边际生态成本
 On the contrary, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs as stakeholders take corresponding responsibilities to the YRCC (\textit{Supplementary Material S4}).
-% 制度结构和结果的差异呼应了SES成功治理的前景，通过间接(或垂直)在不同的利益相关者之间建立联系(在这种情况下是通过管理)
 The alignments of differences in institutional structures and outcomes echo the hypothesis of successful governance in SES by indirectly (or vertically) creating links between different stakeholders (in the YRB cases, through administration).

### 2022-04-06 docs/papers/01_manuscript/drafs.tex
docs(results2-section1-show-results): describe upset plots

@@
 The adverse effects of incentive distortion imply a trade-off between long-term SES benefits and current stability, and the proportion of available resources allocated under quota schemes matters when institutions change \cite{lade2013}
+
+% 在我们的研究期间(从1975年到2008年)，机构在三种不同的结构之间转换:免费访问、87-WAS和98-UBR。
+In our study period, the institution shifted between three different structures (Figure~\ref{structure} A to C).
+% 长江水利委员会是长江流域的主要负责人，其任务是报告和分析1998年以前长江流域的用水量(87-WAS之后)。
+However, the YRCC, whose primary official response to the river before 1998, the mandate was to conserve the riverway environment, construct and maintain infrastructures, and report on and analyze water consumption (after the 87-WAS) in the YRB, i.e., connecting the ecological nodes (different river reaches) horizontally ~\cite{wang2019a}.

### 2022-04-11 docs/papers/01_manuscript/01_introduction.tex
docs(introduction-refactor): introduction re-write according to Shuai Wang's suggestions. 03_causes changed by grammly, drafts added. metadata title and version updated
Now, we focus more on water governance in the yellow river basin, to make reader curious about how institution effect on that.

BREAKING CHANGE: Writing logic totally changed.

@@
 % 水竞争的重要性
-Widespread freshwater scarcity and overuse, resulting in systematic risks to economies, societies, and ecosystems globally, are critical environmental challenges to sustainable development \cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
-With steadily increasing demand, competition for water is an urgent problem in water governance, where policies often lead to long-term changes in human–water relationships and the redistribution of benefits \cite{gleick2010, ziolkowska2016, wang2019d}.
-Despite governments worldwide trying to resolve competition for water through deliberate institutions at large river basins, cascading effects of these initiatives are poorly understood
+Widespread freshwater scarcity and overuse, resulting in systematic risks to economies, societies, and ecosystems globally, are critical environmental challenges to sustainability \cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
+With steadily increasing demand, competition for water causes depletion of freshwater globally and calls for an urgent transformation of governance system by considering water use conservation \cite{gleick2010, ziolkowska2016, wang2019d}.
+Despite worldwide trying to govern water, however, degredation of large river basins is not easily reversable because of few alignments between practice and theory in successful water governance cases.
 \cite{giuliani2013, falkenmark2019, jaeger2019}.
 
-% 制度的意义
-Institutions (such as policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled system, including interplays between social actors, ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
+% 黄河的介绍
+The Yellow River Basin (YRB), the fifth large river worldwide, is known for irreplacable role in the social-economic development of China, and thus also drastically interferend by anthropotic stress.
+Supporting $35.63\%$ irrigation and $30\%$ population with only $2.66\%$ water resources of China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021), the overburdened Yellow River dried up in consecutive years, resulting huge ecological, economic and social crisis (e.g., wetland shrink, agriculture reduction, and scramble for water).
+Intense water use, accounting for about $80\%$ of Yellow River surface runoff in 1980s, was remarked as the major reason of the degradation.
+Furthermore, human interferences such as soil conservation and water conservancy project boosted water withdraw then stressed the water scarcity of the Yellow River.
+To balance between ecological and developing demands in such a human-dominated basin, therefore, is not only a problem for China in water governance throughout, but also for large rivers worldwide.
+
+% 第三段 过去管理的经验，断流的严重程度，连续多少没有断流，少有的解决断流的大河。治理成功的流域？分析背后的机制，基础。往用水上靠。
+In China, several ambitious water management practices were proposed since the last centery, such as reservoir regulating, South-to-north Water Diversion Project (WDP), Water Allocation Scheme since 1987 (87-WAS), and the Unified Basinal Regulation since 1998 (98-UBR), to solve the water stress of the YRB.
+Contributed by those efforts, ecological restoration of wetland and estuary delta in the YRB without drying-up for over $20$ years is widely considered as a achievement in large river management.
+Different from engineering of WDP provides further water supply or reservoir matches water supply and demands, however, institutional strategies like the 87-WAS (assign water quotas for provinces in the YRB) and the 98-UBR (the provinces had to be allowed for using water by the Yellow River Conservancy Commission, YRCC) mainly focused on limiting demands of water use.
+Such institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human and natural system, including interplays between social actors, ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
 Understanding the complex interlinkages is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
-Effective (“matched”) institutions operate at appropriate spatial, temporal, and functional scales to manage and balance these different relationships and interactions, therefore, supporting (but do not guarantee) sustainability of SES \cite{epstein2015, wang2019d}.
-Water governance tends to shift to institutional solutions within a complex basinal system, where societal drivers impact through water use and related technical interventions \cite{fischer2020}.
+However, while effects of engineering solutions are well evaluated and quantified beforehand, there are few attempts on assessment of institutional contributions to an successful water governance.
+
+% 第四段 目标 制度变化。是不是制度变化产生的，如果是的话怎么影响。
+Despite widespread recognition of the rising importance of institutions as an approach to water sustainable use within large river (especially transboundary river) basins, their specific effects are still in open discussion \cite{agrawal2003, persha2011, agrawal2001}.
+Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water system, therefore, supporting (but do not guarantee) sustainability of SES \cite{epstein2015, wang2019d}.
 Some institutional shifts have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and collaborative water governance systems in Europe \cite{green2013}).
 However, shifting institutions in a large, complex river basin may create or destroy hundreds of different connections, where matched human-water relationships are not ubiquitous.
-%TODO 这里应该梳理 Institutional shift --> structures / building blocks.
-Therefore, despite widespread recognition of the rising importance of institutions as an approach to water sustainable use within large river (especially transboundary river) basins, broader cascading effects of these changes are still in open discussion \cite{agrawal2003, persha2011, agrawal2001}.
-% TODO 根据武老师的意见，这个KG应该再明确
-
-%! 这一段梳理一下 building blocks 的作用机制
-% Among
-
-% 黄河的制度介绍
-Supporting $35.63\%$ irrigation and $xx\%$ population with only $2.66\%$ of water resources in China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021), the overburdened Yellow River (YR) once dried up in consecutive years.
-For that, as a pioneer in water governance shifting in China, the YRB started to explore the initial water allocating scheme in the 1970s, then found a successful solution of dring-up in 1998, and promoted entirely since 2008.
-The institutional shifts in 1987 (known as the ``87 Water Allocation Scheme, 87-WAS'') and 1998 (Unified Basinal Regulation, 98-UBR) were two widely recognized milestones of water governance.
-Before the remarkable achievement in the restoration of river depletion since the 98-UBR, on the contrary, the first temptation to restrict water uses in the 87-WAS was recognized as a not fulfilling expectation of institutional shift.
-Until the 87-WAS, stakeholders have free access to the YR water resources, with geographic and temporal differences between freshwater demand and availability.
-As the mismatch between demands and supply kept increasing, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin.
-However, this controversial scheme helped little in turning water depletion around until a different strategy expanded the responsibilities of basinal authorities in integrated water management in 1998 and started progress in the restoration.
-
-% 我们的研究
-The shifts in the water governance institution of YR refactored the interplays between humans and water with long-term cascading effects, leaving two quasi-natural experiments for understanding the interactions.
-By Differenced Synthetic Control method, our analysis of the net effects of institutional shift shows that institutional mismatches contributed to the acceleration of water withdrawals for resource users after 98-WAS.
-As few large river basins have experienced such radical structural changes several times, our quantitative analysis of institutional shifts in the YR induces a valuable understanding of water sustainable governance by decoupling natural and human interferences.
-%! 这还要继续凝练我们的贡献
-By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings align with the urgent calls for a more dynamic design for water governance institutions to achieve sustainability.
+How did and how important the institutional shifts played an role in the water governance achievement of the YRB, therefore, are still uncertain.
+Here, we quantitatively analyzed impacts of two significant institutional shifts (the 87-WAS and the 98-UBR) on water uses of the YRB.
+By linking structures and outcomes within the coupled human and natural system, we further explored mechanisms of institutional effects in the YRB, for deeper understanding of institutions role in water governance worldwide.

### 2022-04-11 docs/papers/01_manuscript/03_causes.tex
docs(introduction-refactor): introduction re-write according to Shuai Wang's suggestions. 03_causes changed by grammly, drafts added. metadata title and version updated
Now, we focus more on water governance in the yellow river basin, to make reader curious about how institution effect on that.

BREAKING CHANGE: Writing logic totally changed.

@@
 % \MakeUppercase{\subsection{Mechanism of institutional shift effects}}
-\subsection{Mechanism of institutional shift effects}
+\subsection{Mechanism of institutional effects}
 \label{result-2}
@@
 In particular, Neimeng and Shandong, both provinces that exceeded the prescribed water uses of the 87-WAS, used $44.25\%$ and $25.69\%$ more water uses than the prediction from 1987 to 1998, respectively.
-Furthermore, the satisfaction of each province with the water allocation stipulated by the 87-WAS (expressed by the difference between the actual water allocation of each province and the expected planning value) is not significantly correlated with the acceleration.
-By contrast, after the 98-UBR, with the exception of Shaanxi (which has always been abundant in water quota) had evident ($17.53\%$) increasd water use, almost all provinces have seen significant declines in water use ($-12.5\%$ on average).
-Neither the satisfaction nor Yellow River water use, however, have correlation with the declines.
+Furthermore, the satisfaction of each province with the water allocation stipulated by the 87-WAS (expressed by the difference between the actual water allocation of each province and the expected planning value) has little significant correlation to the acceleration.
+By contrast, after the 98-UBR, except Shaanxi (which has always been abundant in water quota) had an evident ($17.53\%$) increase in water use, almost all provinces have seen significant declines in water use ($-12.5\%$ on average).
+However, neither the satisfaction nor Yellow River water use correlates with the declines.
 
@@
     \centering
-    \includegraphics[width=32pc]{outputs/upset.jpg}
+    \includegraphics[width=32pc]{outputs/upset_87.pdf}
     \caption{

### 2022-04-11 docs/papers/01_manuscript/drafs.tex
docs(introduction-refactor): introduction re-write according to Shuai Wang's suggestions. 03_causes changed by grammly, drafts added. metadata title and version updated
Now, we focus more on water governance in the yellow river basin, to make reader curious about how institution effect on that.

BREAKING CHANGE: Writing logic totally changed.

@@
 However, the YRCC, whose primary official response to the river before 1998, the mandate was to conserve the riverway environment, construct and maintain infrastructures, and report on and analyze water consumption (after the 87-WAS) in the YRB, i.e., connecting the ecological nodes (different river reaches) horizontally ~\cite{wang2019a}.
+
+% 为此，长江流域作为中国水治理转型的先驱者，从上世纪70年代开始探索初步的配水方案，到1998年找到了解决水资源枯竭问题的成功方案，并从2008年开始全面推广。
+% 1987年(被称为“87年水分配计划，87- was”)和1998年(统一流域管理，98-UBR)的制度转变是水治理的两个被广泛认可的里程碑。
+% 相反，在自98-UBR以来在恢复河流枯竭方面取得显著成就之前，第一个限制87-WAS用水的诱惑被认为是对体制转变的不满足的期望。
+% 在87-WAS之前，利益攸关方可以免费使用YR水资源，但淡水需求和可用性之间存在地理和时间差异。
+% 由于需求和供应之间的不匹配不断增加，国家当局在87-WAS中建议在YR盆地沿线10个省(或区域)之间分配具体的水配额。
+% 然而，这个有争议的计划在扭转水资源枯竭方面帮助不大，直到1998年一项不同的战略扩大了流域当局在综合水资源管理方面的责任，并开始在恢复方面取得进展。
+For that, as a pioneer in water governance shifting in China, the YRB started to explore the initial water allocating scheme in the 1970s, then found a successful solution of dring-up in 1998, and promoted entirely since 2008.
+The institutional shifts in 1987 (known as the ``87 Water Allocation Scheme, 87-WAS'') and 1998 (Unified Basinal Regulation, 98-UBR) were two widely recognized milestones of water governance.
+Before the remarkable achievement in the restoration of river depletion since the 98-UBR, on the contrary, the first temptation to restrict water uses in the 87-WAS was recognized as a not fulfilling expectation of institutional shift.
+Until the 87-WAS, stakeholders have free access to the YR water resources, with geographic and temporal differences between freshwater demand and availability.
+As the mismatch between demands and supply kept increasing, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin.
+However, this controversial scheme helped little in turning water depletion around until a different strategy expanded the responsibilities of basinal authorities in integrated water management in 1998 and started progress in the restoration.
+
+Water governance tends to shift to institutional solutions within a complex basinal system, where societal drivers impact through water use and related technical interventions \cite{fischer2020}.
+
+% YR水治理机构的转变重构了人与水之间的相互作用，并产生了长期的级联效应，为理解这种相互作用留下了两个准自然实验。
+% 利用差分综合控制方法，对制度变迁的净效应进行了分析，结果表明:制度不匹配促进了98-WAS后资源使用者的取水速度。
+% 由于很少有大型河流流域经历过如此剧烈的结构变化，我们对年度制度变迁的定量分析，通过将自然和人类干预脱钩，促使我们对水的可持续治理有了宝贵的理解。
+% % !这还要继续凝练我们的贡献
+% 通过强调结构不匹配下生态系统崩溃的潜在担忧，我们的研究结果与迫切需要为水治理机构提供更动态的设计以实现可持续性的呼吁相一致。
+The shifts in the water governance institution of YR refactored the interplays between humans and water with long-term cascading effects, leaving two quasi-natural experiments for understanding the interactions.
+By Differenced Synthetic Control method, our analysis of the net effects of institutional shift shows that institutional mismatches contributed to the acceleration of water withdrawals for resource users after 98-WAS.
+As few large river basins have experienced such radical structural changes several times, our quantitative analysis of institutional shifts in the YR induces a valuable understanding of water sustainable governance by decoupling natural and human interferences.
+%! 这还要继续凝练我们的贡献
+By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings align with the urgent calls for a more dynamic design for water governance institutions to achieve sustainability.

### 2022-04-11 docs/papers/01_manuscript/01_introduction.tex
fix(grammar): correct grammar in the introduction section by grammarly suggestions

@@
 Widespread freshwater scarcity and overuse, resulting in systematic risks to economies, societies, and ecosystems globally, are critical environmental challenges to sustainability \cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
-With steadily increasing demand, competition for water causes depletion of freshwater globally and calls for an urgent transformation of governance system by considering water use conservation \cite{gleick2010, ziolkowska2016, wang2019d}.
-Despite worldwide trying to govern water, however, degredation of large river basins is not easily reversable because of few alignments between practice and theory in successful water governance cases.
+With steadily increasing demand, competition for water causes depletion of freshwater globally and calls for an urgent transformation of the governance system by considering water use conservation \cite{gleick2010, ziolkowska2016, wang2019d}.
+Despite worldwide trying to govern water, however, degradation of large river basins is not easily reversible because of few alignments between practice and theory in successful water governance cases.
 \cite{giuliani2013, falkenmark2019, jaeger2019}.
@@
 % 黄河的介绍
-The Yellow River Basin (YRB), the fifth large river worldwide, is known for irreplacable role in the social-economic development of China, and thus also drastically interferend by anthropotic stress.
-Supporting $35.63\%$ irrigation and $30\%$ population with only $2.66\%$ water resources of China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021), the overburdened Yellow River dried up in consecutive years, resulting huge ecological, economic and social crisis (e.g., wetland shrink, agriculture reduction, and scramble for water).
-Intense water use, accounting for about $80\%$ of Yellow River surface runoff in 1980s, was remarked as the major reason of the degradation.
-Furthermore, human interferences such as soil conservation and water conservancy project boosted water withdraw then stressed the water scarcity of the Yellow River.
-To balance between ecological and developing demands in such a human-dominated basin, therefore, is not only a problem for China in water governance throughout, but also for large rivers worldwide.
+The Yellow River Basin (YRB), the fifth large river worldwide, is known for its irreplaceable role in the social-economic development of China, and thus also drastically interference by anthropogenic stress.
+Supporting $35.63\%$ irrigation and $30\%$ population with only $2.66\%$ water resources of China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021), the overburdened Yellow River dried up in consecutive years, resulting in substantial ecological, economic and social crisis (e.g., wetland shrink, agriculture reduction, and scramble for water).
+Intense water use, accounting for about $80\%$ of Yellow River surface runoff in the 1980s, was remarked as the significant reason for the degradation.
+Furthermore, human interferences such as soil conservation and water conservancy project boosted water withdrawal and then stressed the water scarcity of the Yellow River.
+To balance ecological and developing demands in such a human-dominated basin, therefore, is a problem for China in terms of water governance throughout and for large rivers worldwide.
 
 % 第三段 过去管理的经验，断流的严重程度，连续多少没有断流，少有的解决断流的大河。治理成功的流域？分析背后的机制，基础。往用水上靠。
-In China, several ambitious water management practices were proposed since the last centery, such as reservoir regulating, South-to-north Water Diversion Project (WDP), Water Allocation Scheme since 1987 (87-WAS), and the Unified Basinal Regulation since 1998 (98-UBR), to solve the water stress of the YRB.
-Contributed by those efforts, ecological restoration of wetland and estuary delta in the YRB without drying-up for over $20$ years is widely considered as a achievement in large river management.
-Different from engineering of WDP provides further water supply or reservoir matches water supply and demands, however, institutional strategies like the 87-WAS (assign water quotas for provinces in the YRB) and the 98-UBR (the provinces had to be allowed for using water by the Yellow River Conservancy Commission, YRCC) mainly focused on limiting demands of water use.
-Such institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human and natural system, including interplays between social actors, ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
+In China, there were several ambitious water management practices in the last century, such as reservoir regulation, South-to-north Water Diversion Project (WDP), Water Allocation Scheme since 1987 (87-WAS), and the Unified Basinal Regulation since 1998 (98-UBR), to solve the water stress of the YRB.
+Through those efforts, ecological restoration of wetland and estuary delta in the YRB without drying up for over $20$ is widely considered a considerable river management achievement.
+Different from the engineering of WDP provides further water supply or reservoir matches water supply and demands, institutional strategies like the 87-WAS (assign water quotas for provinces in the YRB) and the 98-UBR (the provinces had to be allowed for using water by the Yellow River Conservancy Commission, YRCC) mainly focused on limiting demands of water use.
+Such institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human, and natural system, including interplays between social actors, ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
 Understanding the complex interlinkages is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
-However, while effects of engineering solutions are well evaluated and quantified beforehand, there are few attempts on assessment of institutional contributions to an successful water governance.
+However, while literature had well evaluated and quantified the effects of engineering solutions beforehand, there are few attempts to assess institutional contributions to successful water governance.
 
 % 第四段 目标 制度变化。是不是制度变化产生的，如果是的话怎么影响。
-Despite widespread recognition of the rising importance of institutions as an approach to water sustainable use within large river (especially transboundary river) basins, their specific effects are still in open discussion \cite{agrawal2003, persha2011, agrawal2001}.
-Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water system, therefore, supporting (but do not guarantee) sustainability of SES \cite{epstein2015, wang2019d}.
+In addition to widespread recognition of the rising importance of institutions as an approach to water sustainable use within large river (especially transboundary river) basins, their specific effects are still in open discussion \cite{agrawal2003, persha2011, agrawal2001}.
+Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, therefore, supporting (but do not guarantee) sustainability of SES \cite{epstein2015, wang2019d}.
 Some institutional shifts have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and collaborative water governance systems in Europe \cite{green2013}).
 However, shifting institutions in a large, complex river basin may create or destroy hundreds of different connections, where matched human-water relationships are not ubiquitous.
-How did and how important the institutional shifts played an role in the water governance achievement of the YRB, therefore, are still uncertain.
-Here, we quantitatively analyzed impacts of two significant institutional shifts (the 87-WAS and the 98-UBR) on water uses of the YRB.
-By linking structures and outcomes within the coupled human and natural system, we further explored mechanisms of institutional effects in the YRB, for deeper understanding of institutions role in water governance worldwide.
+How and how important the institutional shifts played a role in the water governance achievement of the YRB, therefore, are still uncertain.
+Here, we quantitatively analyzed the impacts of two significant institutional shifts (the 87-WAS and the 98-UBR) on water uses of the YRB.
+By linking structures and outcomes within the coupled human and natural system, we further explored mechanisms of institutional effects in the YRB for a deeper understanding of institutions' role in water governance worldwide.

### 2022-04-11 docs/papers/01_manuscript/02_results.tex
docs(analysis-results-2): re-analyze the result-2 section
BREAKING CHANGE:

@@
 Citation
-Water use efficiency is another crucial factor in interpreting the differences besides the economic factors (e.g., irrigated areas and industrial outcomes) considered and controlled by the method.
+Water use intensity is another crucial factor in interpreting the differences besides the economic factors (e.g., irrigated areas and industrial outcomes) considered and controlled by the method.
 In addition to the expansion of irrigation area after the 87-WAS, water uses per unit of irrigation area also rapidly widened the gap with the average level of the rest provinces.
@@
 In terms of the average ratio of water-saving irrigation area (refer to drip or sprinkler irrigation systems and canal lining), although there was a significant increase in the whole country after 1987, the YRB did not rapidly open a noticeable gap until about 1994 (Figure~\ref{S3-3}).
-As a result, despite the irrigation area expanding, scrambling for water resources without any incentive to optimize water efficiency accelerated holistic water use.
-This accelerated growth in water use was contrary to the original intention of the 87-WAS in conserving the limited water, and this failure of the institution was a major barrier to the sustainability of the Yellow River %!
+As a result, despite the irrigation area expanding, scrambling for water resources without any incentive to optimize production in per unit water resources accelerated holistic water use.
+This accelerated growth in water use was contrary to the original intention of the 87-WAS in conserving the limited water, and this failure of the institution played as a barrier to the sustainability of the Yellow River %!
 \cite{huangang2002}.
@@
 Until the institutional shift of 98-UBR, with no necessity to apply for a water permit from YRCC, there were no horizontal connections (cooperations or agreements) between the various stakeholders (provinces) directly connected to the ecological units.
-Make it clear that the YRCC was responsible for regulating provincial water use; that is, each province has made it clear that in the long run, water resources are not ``internal'' but ``dependent''.
-By taking the structure before and after the two institutional shifts as different basic assumptions (before 87-WAS: free access to water; after 87-WAS but before 98-UBR: decisions on water use under quotas; after 98-UBR: unified regulation), we use the marginal benefit model to analyze the theoretical optimal water consumption of stakeholders in each scenario.
-The analysis of the model also shows that 98-UBR can reduce the overall water use of the basin while 87-WAS can increase the water use of the basin when the same parameters are guaranteed but the institutional structure changes.
+Make it clear that the YRCC was responsible for regulating provincial water use; that is, each province has made it clear that in the long run, water resources are not ``internal'' but ``dependent'' on YRCC.
+In that way, the YRCC, whose authority scale matches to the whole river basin, also took the main responsibilities to the river, and the structure like this was widly recongnized as a social-ecological fit usually led to good outcomes.
 Empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems

### 2022-04-11 docs/papers/01_manuscript/03_causes.tex
docs(analysis-results-2): re-analyze the result-2 section
BREAKING CHANGE:

@@
 % 结果2部分：
-% 1. 加速用水增长的结果 for each province.
-% 2. Potential benefits for each stakeholder (economic model - assumption & results), and social-ecological fit holistically. 结合经济模型
-% 3. Why some building blocks fits for good outcomes. 结合 building block
 
@@
 By contrast, after the 98-UBR, except Shaanxi (which has always been abundant in water quota) had an evident ($17.53\%$) increase in water use, almost all provinces have seen significant declines in water use ($-12.5\%$ on average).
-However, neither the satisfaction nor Yellow River water use correlates with the declines.
+However, neither the satisfaction nor Yellow River water use correlates with the declines after the 98-UBR.
 
@@
 % 经济模型与理论解释
-%! 这里可以指出他们过去的经济发展路径
-We analyzed mathematically why the mismatched structure made win-wins holistically elusive in the institution shift of 87-WAS (\textit{method} and \textit{Supplementary Material S4}).
-Our model suggests that for users who are already economically efficient, greater marginal returns from water induce the acceleration of extracting resources for future economic growth (Figure~\ref{economic_model}).
-Therefore, isolated stakeholders reacted variety to the similar marginal cost, and the institution of 87-WAS thus triggered an incentive distortion besides the initial intention of sustainable water use.
-On the contrary, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs as stakeholders take corresponding responsibilities to the YRCC (\textit{Supplementary Material S4}).
-The alignments of differences in institutional structures and outcomes echo the hypothesis of successful governance in SES by indirectly (or vertically) creating links between different stakeholders (in the YRB cases, through administration).
-%! citation
+Differences between the responses pattern by provinces can demonstrate the influence of social-ecological structures led by the institutional shifts.
+We analyzed mathematically why the mismatched structure made limited water use holistically elusive in the institution shift of the 87-WAS but finally achieved by the 98-UBR (\textit{method} and \textit{Supplementary Material S4}).
+By taking the structure before and after the two institutional shifts as different basic assumptions (before 87-WAS: free access to water; after 87-WAS but before 98-UBR: decisions on water use under quotas; after 98-UBR: unified regulation), we use the marginal benefit model to analyze the theoretical optimal water consumption of stakeholders in each scenario.
+The analysis of the model also shows that 98-UBR can reduce the overall water use of the basin while 87-WAS can increase the water use of the basin when the same parameters are guaranteed but the institutional structure changes.
+Before the 98-UBR, model assumes that the seperated ecological units (river reaches) are linking to stakeholders (related provinces) who use water for persing their own marginal benefits but have a potential political cost if over the quota after the 87-WAS.
+Our model suggests that for users who are already economically efficient (who are already using more water), greater marginal returns from water induce the acceleration of extracting resources for future economic growth (Figure~\ref{economic_model}).
+Therefore, isolated stakeholders reacted variety to the similar marginal cost, and smaller water users have a threshold because of the political cost, so 87-WAS triggered an increased water use for big users.
+On the contrary, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs holistically as stakeholders only take corresponding responsibilities (follow the quota as possible as they can) to the YRCC (\textit{Supplementary Material S4}).
+As a result, unified regulating acted the core role after the 98-UBR and reduced water use of all stakeholders (provinces) by irregular ratios.
 
-Authentic the water quota (or the initial water rights) in our case studies went through a stage of "bargaining" among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
-% 在水资源分配过程中，上下级决策者与利益相关者之间存在信息不对称，当前用水量越大的决策者议价能力越强。
-With information asymmetry between upper-level decision-makers and lower-level stakeholders in water use allocation, those with more current water use might have greater bargaining power.
-After 1987, the logical next step for provinces was to attempt to justify bargaining for larger quotas rather than immediately adopt resource-conserving transformations, as the trend of the water consumption intensity denotes (\textit{Supplementary Material S4}).
-% 研究表明，如果仅考虑经济因素，用水量大户的体量与效率需要超出其配额的水资源
-Studies show that the volume and efficiency of large water users need more water than their quota (in the 87-WAS) if only considering the economic factors when designing the institution.
+The alignments of differences in institutional structures and outcomes here echo the hypothesis that successful governance of SES emerged by indirectly (or vertically) creating links between different stakeholders (in the YRB cases, through administration).
+When links The water quotas of 87-WAS (or the initial water rights) in our case studies went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
+The bargaining itself was also can a process towards matches between their economic volume and water shares, as studies show that the large water users (like Shandong and Henan) need more water than their quota (in the 87-WAS) if only considering the economic equity when designing the institution.
+Furthermore, with information asymmetry between upper-level decision-makers and lower-level stakeholders in water use allocation, those with more current water use might have greater bargaining power.
 In practice, therefore, although the affected provinces may not have directly encouraged excessive resource use because of the institutional shift, they had a larger incentive to show their economic potential
+That keeps in line with the historical records that, even after the 87-WAS had already confirmed the quotas, provinces, especially water-intensive ones, challenged it by appear to the higher central government for larger quotas.
+On contrary, after YRCC as governing agent coordinated between stakeholders since 98-UBR, the external appeal of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically incrased water conserving equipments, \textit{Supplementary Material S3})
 \cite{krieger1955, ostrom1990}.
-As a result, while competing for potential water quotas, the provinces tended to hide the ecological costs behind economic development.
-
-% 毫无疑问，随着资源竞争的日趋激烈，越来越多的SES正依赖着不同形式的制度进行资源分配（如自组织和政府干预），避免“短跑效应”的出现或将成为制度设计的关键。
-With increasingly fierce competition for water, worldwide basins are developing institutions for governance (whether through self-organization or government intervention) \cite{andersson2020, wutich2009, cumming2020b}.
-% 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
-Adopting an overall quota plays a vital role in preventing the overuse of Common-pool Resources, like exclusive and competitive water resources.
-However, various outcomes following institutional shifts of YRB demonstrate that stakeholders may react to quota with distortion when pursuing returns isolated under mismatched SES structures.
-% 历史也证明，在87-WAS之后，各省、尤其是用水大省均对提出了异议，并持续上诉以寻求更大的配额。
-History also shows that, after 87-WAS, provinces, especially water-intensive ones, challenged it and continued to appeal for larger quotas.
-% 而在用水许可制度之后，这种寻求更大配额的外在诉求转变成了提升用水效率的内部革新。
-After YRCC as governing agent coordinated between stakeholders since 98-UBR, the external appeal of provinces for larger quotas turned into internal innovation to improve water efficiency.
-% 与生态尺度相匹配的代理人在成功治理的SES中作为 motif 反复出现，无论是在渔业、森林、还是在地下水治理中，表明减少与割裂生态fragment直接相连的独立利益相关者是结构产生良好效果的重要普遍性机制。
-Agents matching the ecological scale appear widespread as motifs in SES of successful governance, whether in fisheries, forests, or groundwater management, suggesting that reducing independent stakeholders linked to fragmentation is an essential primary mechanism for a structure to produce good results.
+Then, the YRCC, authority of approving water applications for all stakeholders, could adjusted water use quotas according to the river conditions of the whole basin.
+The 98-UBR led to incentive towards social-ecological fits in both basin (between YRCC and the YRB) and regions (between provincial economy and their water shares).

### 2022-04-11 docs/papers/01_manuscript/drafs.tex
docs(analysis-results-2): re-analyze the result-2 section
BREAKING CHANGE:

@@
 By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings align with the urgent calls for a more dynamic design for water governance institutions to achieve sustainability.
+
+% 毫无疑问，随着资源竞争的日趋激烈，越来越多的SES正依赖着不同形式的制度进行资源分配（如自组织和政府干预），避免“短跑效应”的出现或将成为制度设计的关键。
+With increasingly fierce competition for water, worldwide basins are developing institutions for governance (whether through self-organization or government intervention) \cite{andersson2020, wutich2009, cumming2020b}.
+% 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
+Adopting an overall quota plays a vital role in preventing the overuse of Common-pool Resources, like exclusive and competitive water resources.
+However, various outcomes following institutional shifts of YRB demonstrate that stakeholders may react to quota with distortion when pursuing returns isolated under mismatched SES structures.
+% 与生态尺度相匹配的代理人在成功治理的SES中作为 motif 反复出现，无论是在渔业、森林、还是在地下水治理中，表明减少与割裂生态fragment直接相连的独立利益相关者是结构产生良好效果的重要普遍性机制。
+Agents matching the ecological scale appear widespread as motifs in SES of successful governance, whether in fisheries, forests, or groundwater management, suggesting that reducing independent stakeholders linked to fragmentation is an essential primary mechanism for a structure to produce good results.

### 2022-04-11 docs/papers/01_manuscript/02_results.tex
fix(grammar): check according to grammarly

@@
 Citation
-Water use intensity is another crucial factor in interpreting the differences besides the economic factors (e.g., irrigated areas and industrial outcomes) considered and controlled by the method.
+Water-use intensity is another crucial factor in interpreting the differences besides the economic factors (e.g., irrigated areas and industrial outcomes) considered and controlled by the method.
 In addition to the expansion of irrigation area after the 87-WAS, water uses per unit of irrigation area also rapidly widened the gap with the average level of the rest provinces.
@@
 In terms of the average ratio of water-saving irrigation area (refer to drip or sprinkler irrigation systems and canal lining), although there was a significant increase in the whole country after 1987, the YRB did not rapidly open a noticeable gap until about 1994 (Figure~\ref{S3-3}).
-As a result, despite the irrigation area expanding, scrambling for water resources without any incentive to optimize production in per unit water resources accelerated holistic water use.
-This accelerated growth in water use was contrary to the original intention of the 87-WAS in conserving the limited water, and this failure of the institution played as a barrier to the sustainability of the Yellow River %!
-\cite{huangang2002}.
+As a result, despite the irrigation area expanding, scrambling for water resources without any incentive to optimize production per unit of water resources accelerated holistic water use.
+This accelerated water use was contrary to the original intention of the 87-WAS in conserving the limited water, and the failure was a barrier to the sustainability %! \cite{huangang2002}.
 
@@
 Make it clear that the YRCC was responsible for regulating provincial water use; that is, each province has made it clear that in the long run, water resources are not ``internal'' but ``dependent'' on YRCC.
-In that way, the YRCC, whose authority scale matches to the whole river basin, also took the main responsibilities to the river, and the structure like this was widly recongnized as a social-ecological fit usually led to good outcomes.
+In that way, the YRCC, whose authority scale matches the whole river basin, also took the primary responsibilities to the river, and literature recognized the structure as a social-ecological fit that usually led to good outcomes.
 Empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems

### 2022-04-11 docs/papers/01_manuscript/03_causes.tex
fix(grammar): check according to grammarly

@@
 % 经济模型与理论解释
-Differences between the responses pattern by provinces can demonstrate the influence of social-ecological structures led by the institutional shifts.
+Differences in the pattern of the response by provinces can demonstrate the influence of social-ecological structures led by the institutional shifts.
 We analyzed mathematically why the mismatched structure made limited water use holistically elusive in the institution shift of the 87-WAS but finally achieved by the 98-UBR (\textit{method} and \textit{Supplementary Material S4}).
@@
 The analysis of the model also shows that 98-UBR can reduce the overall water use of the basin while 87-WAS can increase the water use of the basin when the same parameters are guaranteed but the institutional structure changes.
-Before the 98-UBR, model assumes that the seperated ecological units (river reaches) are linking to stakeholders (related provinces) who use water for persing their own marginal benefits but have a potential political cost if over the quota after the 87-WAS.
+Before the 98-UBR, the model assumes that the separated ecological units (river reaches) link to stakeholders (related provinces) who use water to pursue their marginal benefits but have a potential political cost if they exceed the quota 87-WAS.
 Our model suggests that for users who are already economically efficient (who are already using more water), greater marginal returns from water induce the acceleration of extracting resources for future economic growth (Figure~\ref{economic_model}).
-Therefore, isolated stakeholders reacted variety to the similar marginal cost, and smaller water users have a threshold because of the political cost, so 87-WAS triggered an increased water use for big users.
+Therefore, isolated stakeholders reacted to the similar marginal cost, and smaller water users have a threshold because of the political cost, so 87-WAS triggered an increased water use for the significant users.
 On the contrary, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs holistically as stakeholders only take corresponding responsibilities (follow the quota as possible as they can) to the YRCC (\textit{Supplementary Material S4}).
@@
 When links The water quotas of 87-WAS (or the initial water rights) in our case studies went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
-The bargaining itself was also can a process towards matches between their economic volume and water shares, as studies show that the large water users (like Shandong and Henan) need more water than their quota (in the 87-WAS) if only considering the economic equity when designing the institution.
+The bargaining itself was also a process towards matches between their economic volume and water shares, as studies show that the large water users (like Shandong and Henan) need more water than their quota (in the 87-WAS) if only considering the economic equity when designing the institution.
 Furthermore, with information asymmetry between upper-level decision-makers and lower-level stakeholders in water use allocation, those with more current water use might have greater bargaining power.
-In practice, therefore, although the affected provinces may not have directly encouraged excessive resource use because of the institutional shift, they had a larger incentive to show their economic potential
-That keeps in line with the historical records that, even after the 87-WAS had already confirmed the quotas, provinces, especially water-intensive ones, challenged it by appear to the higher central government for larger quotas.
-On contrary, after YRCC as governing agent coordinated between stakeholders since 98-UBR, the external appeal of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically incrased water conserving equipments, \textit{Supplementary Material S3})
+In practice, therefore, although the affected provinces may not have directly encouraged excessive resource use because of the institutional shift, they had a more considerable incentive to show their economic potential
+That aligns with the historical records that, even after the 87-WAS had already confirmed the quotas, provinces, especially water-intensive ones, challenged it by appearing to the higher central government for larger quotas.
+On the contrary, after YRCC as governing agent coordinated between stakeholders since 98-UBR, the external appeal of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment, \textit{Supplementary Material S3})
 \cite{krieger1955, ostrom1990}.
-Then, the YRCC, authority of approving water applications for all stakeholders, could adjusted water use quotas according to the river conditions of the whole basin.
-The 98-UBR led to incentive towards social-ecological fits in both basin (between YRCC and the YRB) and regions (between provincial economy and their water shares).
+Then, the YRCC, the authority for approving water applications from all stakeholders, could adjust water use quotas according to the river conditions of the whole basin.
+The 98-UBR led to a structure for achieving social-ecological fits in both basins (between YRCC and the YRB) and regions (between provincial economy and their water shares).

### 2022-04-12 docs/papers/01_manuscript/02_structures.tex
docs(structures): add abstracting structures as a new section
BREAKING CHANGE: according to discussion

--- 2022-04-06 docs/papers/01_manuscript/drafs.tex
@@
-drafs.tex
+\subsection{Shifts of institution and SES structure in the YRB}
+\label{result-0}
 
-\section{introduction}
-% At the same time, undesired and unsustainable outcomes (e.g., failures in environmental regulation of highly polluting industries or the development of “tragedy of the commons” situations when pursuing more water resources), with considerable ecological degradation, have attracted much attention \cite{saylesSocialecologicalnetworkanalysis2019,caiPollutingthyneighbor2016,castilla-rhoSocialtippingpoints2017}.
-Two particular weaknesses in existing knowledge include understanding (1) the causal links between SES structures and outcomes; and (2) details of the underlying processes, especially the coordination of the incentives of different participants, that result from an institutional lack of fit.
-These weaknesses limit our understanding of institutional design, and they may reduce the speed and transfer of new knowledge and experience related to improving the sustainability of comprehensive water resources management.
+% 制度变动综述
+Including the national authorities, the basin management authorities, provinces, cities, and even districts, top-down institutional structures of the YRB started to evolve up to now (\textit{S1 in Supplementary Material}).
+As a pioneer in water governance shifting in China, the YRB started to explore the initial water allocating scheme in the 1970s.
+The institutional shifts in 1987 (known as the ``87 Water Allocation Scheme, 87-WAS'') and 1998 (Unified Basinal Regulation, 98-UBR) were two widely recognized milestones of water governance.
+Until the 87-WAS, stakeholders have free access to the YR water resources, with geographic and temporal differences between freshwater demand and availability.
+As the mismatch between demands and supply kept increasing, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin.
+However, this controversial scheme helped slight turn water depletion around until a different strategy expanded the responsibilities of basinal authorities in integrated water management in 1998 (the 98-UBR).
+Ten years later, the YRB authorities require to further divide the provinces' quota into cities, counties, and districts.
+Therefore, our analysis period spans from 1975 to 2008, with the human-water system shifted between three different institutions, which were different from other large river basins in China.
 
-% 机构可以塑造社会经济体系的结构，对其进行抽象是机械地理解结构和结果之间联系的第一步。
+% 制度结构关系抽象
 Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{framework} A).
-% 例如，机构可以创建一种被确定为与良好的社会经济效益相关联的水平匹配结构，如果它鼓励管理相连生态成分的不同行动者之间的协作(图1B)。
 For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{framework} B), leading to sustainable outcomes.
-% 例如，机构可以创建一个结构，鼓励不同行为者之间的合作，管理相连的生态成分
 Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{framework} C and D).
+Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures, and a network model is a widely used way to depict them by abstracting links and nodes.
+We thus selected institutional regulatory documents on water use issued by national ministries (for validation to both watershed and regional agents) and extracted the interactions between the agents involved (\textit{Supplementary Material S2}).
 
-% 从国家官员到流域管理官员，从省、市到区，长江流域自上而下的制度结构开始演变至今
-Including the national authorities, the basin management authorities, provinces, cities, and even districts, top-down institutional structures of the YRB started to evolve up to now (\textit{S1 in Supplementary Material}).
-
-Our analysis period, therefore, spans from 1975 to 2008, with the human-water system shifted between three different institutional structures (Figure~\ref{structure}).
-
-% In order to disentangle the relationship between SES structure and outcomes, we analyzed a case study to show how an institutional shift led to a structural mismatch that triggered unsustainable water use and unintended ecological deterioration.
-% Water is the key exclusive and competitive resource that couples socioeconomic and ecological systems (known as common-pool resources, CPRs) \cite{wutichWaterScarcitySustainability2009,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017,castilla-rhoGroundwaterCommonPool2020}.
-% Conflicts of interest often occur in allocation and competitions of water resources, with water governance policies often leading to long-term changes in human–water relationships and the redistribution of benefits \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013,chingManagingsocioecologyvery2015}.
-
-% Two rapid shifts in institutional structure that occurred in 1987 and 1998 (see Supplementary Material S1) provide unique settings to exploit quasi-natural experiments of a large river basin, the Yellow River Basin (YRB) in China \cite{xiaDevelopmentWaterAllocation2012}.
-
-% After a period of severe drying up, an institutional shift implemented in 1987 represented the beginning of attempts to control water use in the YRB through the use of quotas, with the goals of alleviating conflicts between supply and demand and achieving sustainable development.
-
-% Our results show that this initiative actually accelerated water withdrawals, resulting in an unintended “sprint effect”, where institutional mismatches created an even stronger incentive for each resource user to withdraw resources until the next major institutional shift in 1998.
-% Our analysis contributes to a deeper understanding of the mechanisms underlying the relationships among institutions, SES structures, and outcomes.
-By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings are consistent with the urgent calls for a more dynamic design for water use allocation to achieve sustainability.
-
-\section{Institutions and SES structures}
-% 机构可以塑造社会经济体系的结构，对其进行抽象是机械地理解结构和结果之间联系的第一步。
-Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{fig:framework}A).
-% 例如，机构可以创建一种被确定为与良好的社会经济效益相关联的水平匹配结构，如果它鼓励管理相连生态成分的不同行动者之间的协作(图1B)。
-For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{fig:framework}B), leading to sustainable outcomes.
-% 例如，机构可以创建一个结构，鼓励不同行为者之间的合作，管理相连的生态成分
-Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{fig:framework}C and D).
-% 在实践中，一个大型、复杂的河流流域的制度变化将创造或摧毁数百种不同的联系。这些局部变化的更广泛影响可以从系统的整体行为中看到。
-% 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
-We thus explored the causal linkages between the SES structures and sustainability (outcomes) in quasi-natural experiments of the YRB, which provides an informative case study for two main reasons.
-% 首先，长江流域管理的急剧结构变化使我们能够定量估计高层制度设计变化对用水的净影响。决定水分配的制度包括自下而上的协议或社会规范，以及自上而下的配额或法规，它们对社会经济结构有不同的影响;自上而下的监管可能会立即引发制度转变和SES的剧烈结构性变化。通过与由自下而上的制度转变引起的更渐进的变化相比，探索自上而下变化的影响，在对社会经济地位的定量分析中，极大地减少了来自不可观测因素的潜在干扰，提高了社会经济地位结构和结果之间因果关系的清晰度。
-First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use.
-Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013}; top-down regulations can trigger immediate institutional shifts, and sharp SES structural changes \cite{speedBasinwaterallocation2013,rolandUnderstandinginstitutionalchange2004}.
-In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and improves the clarity of the causal link between SES structure and outcome.
-% 其次，通过比较长江流域两次制度变迁所分裂的三种不同制度结构的净效应，我们也可以更深入地理解“盆地固定效应”下结构格局的影响。尽管流域内的社会经济单位从世界各地的大型河流流域和许多地区的水资源中受益，但很少有流域多次经历过如此激进的社会经济结构变化。
-Second, by comparing the net effects of three different institutional structures split by two institutional shifts in the YRB, we can also better understand of the influence of structural alignments under a fixed basin.
-Although socioeconomic units within a basin benefit from water resources in large river basins all over the world and many locations have shown increased levels of regulation, few basins have experienced such radical SES structural changes several times (see \textit{Supplementary Material} S1).
-Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in SES institutional structure.
-% 因此，黄河流域的“流域固定效应”为SES结构的自我比较提供了宝贵的机会。
-% Thus, the YRB provides valuable settings for understanding the direct impacts of changes in SES institutional structure.
-
-\section{results}
-% % 然后，我们反复比较了两个SES结构(分别自1987年和1998年)，以量化是否有显著不同的影响，YRB用水或分配。
-% Then we repeatedly compared between two SES structures (since 1987 and 1998, respectively) to quantify if there were significantly different impacts on water uses or allocation (\textbf{methods}).
-
-\section{discussion}
-% 我们展示了不匹配的分配制度是如何导致激励失真导致水资源加速耗竭的(即“冲刺效应”)。“冲刺效应”是CPR系统面临的一种特殊情况，在这种情况下，制度的不匹配为每个资源使用者创造了更强的动机(扭曲)，促使他们收回资源
-We have shown how a mismatched allocation institution can lead to an accelerated depletion of water resources (i.e., the “sprint effect”) caused by incentive distortion.
-The sprint effect is a special case faced by CPR systems, where institutional mismatches create an even stronger incentive (with distortion) for each resource user to withdraw resources
-\cite{ostromRevisitingCommonsLocal1999,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017}.
-% 过往研究指出制度常常是避免公共池塘资源系统的崩溃的关键，但“短跑效应”的出现表明在自上而下进行制度设计所形成的错配SES结构中，制度也可以成为系统加速崩溃的触发者。
-Previous studies have suggested that institutions are often the key to avoid the collapse of a CPR system, but the emergence of a sprint effect shows that an institution with structural mismatches can also be the trigger that accelerates system collapse \cite{bodinConservationSuccessFunction2014,bodinCollaborativeenvironmentalgovernance2017,wangAlignmentsocialecological2019}.
-The initial formulation of the water quota in our case studies went through a stage of “bargaining” among stakeholders (from 1982 to 1987) \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}, where each province attempted to demonstrate its development potential related to water use.
-% 为了防止公共池资源被过度利用，总配额在强制禁止水资源过度利用的环境规制中发挥着重要作用，从而形成一个长期匹配的水资源分配机制。
-Adoption of an overall quota plays an important role in preventing overuse of CPRs \cite{tilmanLocalizedprosocialpreferences2019}.
-However, the negative effects of incentive distortion imply a trade-off between long-term SES benefits and current stability, and the proportion of available resources allocated under quota schemes matters when institutions change \cite{ladeRegimeshiftssocialecological2013}.
-According to our analysis of plausible scenario assumptions based on our general economic model, the sprint effect will be reinforced when stakeholders anticipate that technological advances will amplify the benefits of water quotas in the future (see \textit{Supplementary Material S3}).
-% 然而，如果有水权转换机制允许利益相关者之间通过交易来弥补 shadow value，当前这种错乱的动机就不会那么强。
-However, if an institution allowed stakeholders to compensate for the shadow value (i.e., potential returns sacrificed due to water constraints and water scarcity) \cite{howarthAccountingvalueecosystem2002} of future water use, incentive distortion would be less devastating (e.g., through water rights transfer).
-Policymakers can also weaken the sprint effect by increasing the frequency of quota updates, supporting the idea that a more dynamic institution that responds to changing conditions (see \textit{Supplementary Material S3}) will adapt more effectively to its social-ecological context.
-
-% 近年来黄河流域面临的分水制度调整问题也说明了动态设置配额的重要性。
-Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of dynamic quota setting (see \textit{Supplementary Material S1}) \cite{yuAdaptabilityassessmentpromotion2019}.
-Following the institutional reforms of 1998, the Yellow River has not dried up since 1999.
-However, given recent changes in the YRB, its rigid resource allocation scheme can no longer meet the new demands of economic development \cite{wangThingsCurrentSignificance2019}.
-The Chinese government has embarked on an ambitious plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}).
-Other SESs around the world face similar problems in establishing successful resource allocation institutions \cite{cummingQuantifyingSocialEcologicalScale2020, muneepeerakulStrategicbehaviorsgovernance2017, cummingAdvancingunderstandingnatural2020, leslieOperationalizingsocialecologicalsystems2015}.
-These initiatives can benefit from our analysis by actively considering and incorporating social-ecological complexity and incentive structures when developing new approaches that avoid unsustainable outcomes.
-Our research provides a cautionary tale of how institutions can act as a double-edged sword when trying to attain sustainability.
-
-% 我们展示了不匹配的分配制度是如何导致激励失真导致水资源加速耗竭的(即“冲刺效应”)。“冲刺效应”是CPR系统面临的一种特殊情况，在这种情况下，制度的不匹配为每个资源使用者创造了更强的动机(扭曲)，促使他们收回资源
-\cite{ostromRevisitingCommonsLocal1999,ostromGeneralFrameworkAnalyzing2009,castilla-rhoSocialtippingpoints2017}.
-% 过往研究指出制度常常是避免公共池塘资源系统的崩溃的关键，但“短跑效应”的出现表明在自上而下进行制度设计所形成的错配SES结构中，制度也可以成为系统加速崩溃的触发者。
-Previous studies have suggested that institutions are often the key to avoiding the collapse of a CPR system, but the emergence of a sprint effect shows that an institution with structural mismatches can also be the trigger that accelerates system collapse \cite{bodinConservationSuccessFunction2014,bodinCollaborativeenvironmentalgovernance2017,wangAlignmentsocialecological2019}.
-
-##
-% Linking structures to outcomes need advancement when understanding an SES.
-Two particular weaknesses in existing knowledge include understanding (1) the causal links between SES structures and outcomes; and (2) details of the underlying processes, especially the coordination of the incentives of different participants, that result from an institutional lack of fit.
-These weaknesses limit our understanding of institutional design, and they may reduce the speed and transfer of new knowledge and experience related to improving the sustainability of comprehensive water resources management.
-
-The adverse effects of incentive distortion imply a trade-off between long-term SES benefits and current stability, and the proportion of available resources allocated under quota schemes matters when institutions change \cite{lade2013}
-
-% 在我们的研究期间(从1975年到2008年)，机构在三种不同的结构之间转换:免费访问、87-WAS和98-UBR。
-In our study period, the institution shifted between three different structures (Figure~\ref{structure} A to C).
-% 长江水利委员会是长江流域的主要负责人，其任务是报告和分析1998年以前长江流域的用水量(87-WAS之后)。
-However, the YRCC, whose primary official response to the river before 1998, the mandate was to conserve the riverway environment, construct and maintain infrastructures, and report on and analyze water consumption (after the 87-WAS) in the YRB, i.e., connecting the ecological nodes (different river reaches) horizontally ~\cite{wang2019a}.
+Before 1987, the YRCC had no links to the provinces regarding water use, and the provinces could link to the Yellow River reaches directly (Figure~\ref{structure}).
+However, according to the extracted information from the 87-WAS, the YRCC started to report water use from the provinces.
+Furthermore, information from the 98-UBR documents demonstrated that the provinces had to apply their plan for an annual water use licence instead of direct access to the Yellow River water.
+Thus, there were links between the YRCC and the provinces.
+Although we abstract the two major institutional shifts from document interpretations, many studies used these two changes as baselines for the YRB's water governance history and widely recognized their importance.

### 2022-04-12 docs/papers/01_manuscript/drafs.tex
docs(structures): add abstracting structures as a new section
BREAKING CHANGE: according to discussion

@@
 These weaknesses limit our understanding of institutional design, and they may reduce the speed and transfer of new knowledge and experience related to improving the sustainability of comprehensive water resources management.
-
-% 机构可以塑造社会经济体系的结构，对其进行抽象是机械地理解结构和结果之间联系的第一步。
-Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{framework} A).
-% 例如，机构可以创建一种被确定为与良好的社会经济效益相关联的水平匹配结构，如果它鼓励管理相连生态成分的不同行动者之间的协作(图1B)。
-For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{framework} B), leading to sustainable outcomes.
-% 例如，机构可以创建一个结构，鼓励不同行为者之间的合作，管理相连的生态成分
-Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{framework} C and D).
-
-% 从国家官员到流域管理官员，从省、市到区，长江流域自上而下的制度结构开始演变至今
-Including the national authorities, the basin management authorities, provinces, cities, and even districts, top-down institutional structures of the YRB started to evolve up to now (\textit{S1 in Supplementary Material}).
-
-Our analysis period, therefore, spans from 1975 to 2008, with the human-water system shifted between three different institutional structures (Figure~\ref{structure}).
 
@@
 \section{Institutions and SES structures}
-% 机构可以塑造社会经济体系的结构，对其进行抽象是机械地理解结构和结果之间联系的第一步。
-Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{fig:framework}A).
-% 例如，机构可以创建一种被确定为与良好的社会经济效益相关联的水平匹配结构，如果它鼓励管理相连生态成分的不同行动者之间的协作(图1B)。
-For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{fig:framework}B), leading to sustainable outcomes.
-% 例如，机构可以创建一个结构，鼓励不同行为者之间的合作，管理相连的生态成分
-Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{fig:framework}C and D).
-% 在实践中，一个大型、复杂的河流流域的制度变化将创造或摧毁数百种不同的联系。这些局部变化的更广泛影响可以从系统的整体行为中看到。
 % 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
@@
 
-% 为此，长江流域作为中国水治理转型的先驱者，从上世纪70年代开始探索初步的配水方案，到1998年找到了解决水资源枯竭问题的成功方案，并从2008年开始全面推广。
-% 1987年(被称为“87年水分配计划，87- was”)和1998年(统一流域管理，98-UBR)的制度转变是水治理的两个被广泛认可的里程碑。
-% 相反，在自98-UBR以来在恢复河流枯竭方面取得显著成就之前，第一个限制87-WAS用水的诱惑被认为是对体制转变的不满足的期望。
-% 在87-WAS之前，利益攸关方可以免费使用YR水资源，但淡水需求和可用性之间存在地理和时间差异。
-% 由于需求和供应之间的不匹配不断增加，国家当局在87-WAS中建议在YR盆地沿线10个省(或区域)之间分配具体的水配额。
-% 然而，这个有争议的计划在扭转水资源枯竭方面帮助不大，直到1998年一项不同的战略扩大了流域当局在综合水资源管理方面的责任，并开始在恢复方面取得进展。
-For that, as a pioneer in water governance shifting in China, the YRB started to explore the initial water allocating scheme in the 1970s, then found a successful solution of dring-up in 1998, and promoted entirely since 2008.
-The institutional shifts in 1987 (known as the ``87 Water Allocation Scheme, 87-WAS'') and 1998 (Unified Basinal Regulation, 98-UBR) were two widely recognized milestones of water governance.
-Before the remarkable achievement in the restoration of river depletion since the 98-UBR, on the contrary, the first temptation to restrict water uses in the 87-WAS was recognized as a not fulfilling expectation of institutional shift.
-Until the 87-WAS, stakeholders have free access to the YR water resources, with geographic and temporal differences between freshwater demand and availability.
-As the mismatch between demands and supply kept increasing, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin.
-However, this controversial scheme helped little in turning water depletion around until a different strategy expanded the responsibilities of basinal authorities in integrated water management in 1998 and started progress in the restoration.
-
 Water governance tends to shift to institutional solutions within a complex basinal system, where societal drivers impact through water use and related technical interventions \cite{fischer2020}.

### 2022-04-12 docs/papers/01_manuscript/01_introduction.tex
docs(analysis-results-2): re-analyze the result-2 section
BREAKING CHANGE:
docs(finish-the-manuscript): manuscript v1.2
BREAKING CHANGE:

@@
 Furthermore, human interferences such as soil conservation and water conservancy project boosted water withdrawal and then stressed the water scarcity of the Yellow River.
-To balance ecological and developing demands in such a human-dominated basin, therefore, is a problem for China in terms of water governance throughout and for large rivers worldwide.
+In the context of future climate change, the contradiction between supplies and demands of water resources in the YRB will become more prominent, and limiting water use intensity will be still in the first bid
+%! Citation: Hao Wang presentation.
+Therefore, balancing ecological and developing demands in such a human-dominated basin is a problem for China in terms of water governance throughout and for large rivers worldwide.
 

### 2022-04-12 docs/papers/01_manuscript/04_discussion.tex
docs(finish-the-manuscript): manuscript v1.2
BREAKING CHANGE:

--- 2022-03-29 docs/papers/01_manuscript/04_discussion.tex
@@
 
-\subsection{Novel insights and policy implications}
+\subsection{Limitation, novel insights and policy implications}
 \label{insights}
 
+Agents matching the ecological scale appear widespread as motifs in SES of successful governance, whether in fisheries, forests, or groundwater management, suggesting that reducing independent stakeholders linked to fragmentation is an essential primary mechanism for a structure to produce good results.
 % 由于87-WAS和98-UBR分别带来的两种结构在很多的SES中都是反复出现的构件，我们提出的机制对理解这类耦合系统至关重要
@@
 Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in the SES institutional structure.
-% 最后，我们的研究也存在一定局限性，那就是很难排除同期其他政策的效应。
 Finally, one of the limitations of our method is that it is difficult to rule out the effects of other policies over the same time breakpoints.
-% 然而，鉴于学者对于87-WAS与98-UBR两次制度转变的重要性基本达成共识，其结果差异仍对理解水治理有重要借鉴意义。
-However, since scholars have reached a consensus on the importance of the two institutional shifts of 87-WAS and 98-UBR, the differences in their results still provide important references for understanding water governance.
+However, since scholars have reached a consensus on the importance of the two institutional shifts of 87-WAS and 98-UBR, the differences in their results still provide important insights for understanding water governance.
 
 % 我们的模型结果与机制探讨加深了SES结构的理解，强化了孤立利益相关者形成的结构不利于制度解决环境问题的基本认识
-Our results and discussion deepen the understanding of SES structure and strengthen the basic understanding that the mismatched structure formed by isolated stakeholders is not conducive to institutional solutions to environmental sustainability.
-% 而随后 98-UBR 的成功从理论和实际上都佐证了制度尺度匹配的重要性，即需要强调与生态单元的尺度（这里是流域尺度）相符的代理人建立利益相关者之间的横向联系。
-Moreover, the subsequent success of 98-UBR has proved the importance of institutional scale matching both theoretically and practically; that is, it is necessary to emphasize the establishment of potential connections between stakeholders by agents consistent with the scale of the ecological system (in this case, basinal scale and the YRCC).
-Furthermore, according to our analysis of plausible scenario assumptions based on our model, when stakeholders anticipate that technological advances will amplify the benefits of water quotas in the future, the incentive distortion will be reinforced (see \textit{Supplementary Material S4}).
-However, an institution allowed stakeholders to compensate for the shadow value (i.e., potential returns sacrificed due to water constraints and water scarcity) \cite{howarth2002} of future water use would weaken incentive distortion (e.g., through water rights transfer) (see \textit{Supplementary Material S4}).
-Policymakers can also propose a more dynamic institution by increasing the frequency of quota updates that responds to changing conditions will adapt more effectively to its social-ecological context (see \textit{Supplementary Material S4}).
+Our results and discussion deepen the understanding of SES structure and strengthen the basic understanding that the mismatched structure formed by isolated stakeholders is not conducive to institutional solutions; -and then reported how another social-ecological fit structure contributed to successful water governance and sustainability.
+Moreover, the subsequent success of 98-UBR has proved the importance of institutional scale matching both theoretically and practically.
+Therefore, it is necessary to emphasize the establishment of potentially connected building blocks between stakeholders by agents consistent with the scale of the ecological system (in this case, the basinal scale and the YRCC).
+Furthermore, we applied several scenarios based on the marginal benefit model (see \textit{Supplementary Material S4}) for some further insights into sustainable water governance.
+For example, water rights transfers can be another way to emerge horizontal links between stakeholders that also have the potential in resulting in better water governance.
+In addition, the policymakers can also propose a more dynamic and flexible institution by increasing the frequency of quota updates that responds to changing conditions and will adapt more effectively to its SES context.
 
 % 未来的政策建议
-% 近年来黄河流域面临的分水制度调整问题也说明了动态设置配额的重要性。
 Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of dynamic quota setting (see \textit{Supplementary Material S1}) \cite{yu2019}.
@@
 As a result, the Chinese government has embarked on an ambitious plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}).
-Other SESs around the world face similar problems in establishing successful institutions for governance \cite{cumming2020b, muneepeerakul2017, cumming2020a, leslie2015}.
 These initiatives can benefit from our analysis by actively considering and incorporating social-ecological complexity and incentive structures when developing new approaches that avoid unsustainable outcomes.
-Our research provides a cautionary tale of how a mismatched structure of institutions can be a double-edged sword when attaining sustainability.
+Our research provides a cautionary tale of how institutions can be a double-edged sword in attaining sustainability.
+Therefore, insights from the YRB can be a valuable guideline for SESs around the world facing similar governance problems \cite{cumming2020b, muneepeerakul2017, cumming2020a, leslie2015}.

### 2022-04-12 docs/papers/01_manuscript/05_conclusion.tex
docs(finish-the-manuscript): manuscript v1.2
BREAKING CHANGE:

%! Author = songshgeo
%! Date = 2022/3/10

Intense water use in one of the most anthropogenic interfered large river basins, the Yellow River Basin (YRB), once led to overburdened drying up but finally had a successful restoration by sequential water governance institutions.
Focusing on two water-demand institutions, the Water Allocation Scheme since 1987 (87-WAS) and the Unified Basinal Regulation since 1998 (98-UBR), we quantitatively analyzed how and how important the institutional shifts played a role in the water governance achievement of the YRB.

First, by abstracting institutions into building blocks of a social-ecological system (SES), we explored the linkages within the YRB before and after two institutional shifts.
Then, we applied Differenced Synthetic Control method to quantify their impacts on water use of the YRB.
The observed water use of the YRB provinces had an $8.57\%$ increase than our estimation in the decade after the 87-WAS but significantly decreased by $0.49 km^3$ per year after the 98-UBR (the model still suggests a $1.03 km^3$ annual increases).
Finally, by analyzing the differences in stakeholders' responses to the institutional shifts, we found that 87-WAS stimulated water use in provinces with more water uses (e.g., Neimeng, Henan, and Shandong) 98-UBR regulated nearly all provinces.

Since the above results closely align with our mathematical marginal benefits model, we can link the structures (widespread building blocks) and outcomes (goals of the institution, i.e., limiting water demands) by the quasi-natural experiments of the YRB.
We demonstrate again that social-ecological fits lead to successful governance, whether in fisheries, forests, or groundwater management; reducing independent stakeholders linked to fragmentation is an essential primary mechanism for a structure to produce good results.
Therefore, insights from the YRB can be a valuable guideline for SESs worldwide facing similar water governance problems.

### 2022-04-12 docs/papers/01_manuscript/drafs.tex
docs(finish-the-manuscript): manuscript v1.2
BREAKING CHANGE:

@@
 By highlighting potential concerns for ecosystem collapse under structural mismatches, our findings are consistent with the urgent calls for a more dynamic design for water use allocation to achieve sustainability.
-
-\section{Institutions and SES structures}
-% 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
-We thus explored the causal linkages between the SES structures and sustainability (outcomes) in quasi-natural experiments of the YRB, which provides an informative case study for two main reasons.
-% 首先，长江流域管理的急剧结构变化使我们能够定量估计高层制度设计变化对用水的净影响。决定水分配的制度包括自下而上的协议或社会规范，以及自上而下的配额或法规，它们对社会经济结构有不同的影响;自上而下的监管可能会立即引发制度转变和SES的剧烈结构性变化。通过与由自下而上的制度转变引起的更渐进的变化相比，探索自上而下变化的影响，在对社会经济地位的定量分析中，极大地减少了来自不可观测因素的潜在干扰，提高了社会经济地位结构和结果之间因果关系的清晰度。
-First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use.
-Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wangAlignmentsocialecological2019,speedBasinwaterallocation2013}; top-down regulations can trigger immediate institutional shifts, and sharp SES structural changes \cite{speedBasinwaterallocation2013,rolandUnderstandinginstitutionalchange2004}.
-In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and improves the clarity of the causal link between SES structure and outcome.
-% 其次，通过比较长江流域两次制度变迁所分裂的三种不同制度结构的净效应，我们也可以更深入地理解“盆地固定效应”下结构格局的影响。尽管流域内的社会经济单位从世界各地的大型河流流域和许多地区的水资源中受益，但很少有流域多次经历过如此激进的社会经济结构变化。
-Second, by comparing the net effects of three different institutional structures split by two institutional shifts in the YRB, we can also better understand of the influence of structural alignments under a fixed basin.
-Although socioeconomic units within a basin benefit from water resources in large river basins all over the world and many locations have shown increased levels of regulation, few basins have experienced such radical SES structural changes several times (see \textit{Supplementary Material} S1).
-Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in SES institutional structure.
-% 因此，黄河流域的“流域固定效应”为SES结构的自我比较提供了宝贵的机会。
-% Thus, the YRB provides valuable settings for understanding the direct impacts of changes in SES institutional structure.
 
@@
 However, various outcomes following institutional shifts of YRB demonstrate that stakeholders may react to quota with distortion when pursuing returns isolated under mismatched SES structures.
-% 与生态尺度相匹配的代理人在成功治理的SES中作为 motif 反复出现，无论是在渔业、森林、还是在地下水治理中，表明减少与割裂生态fragment直接相连的独立利益相关者是结构产生良好效果的重要普遍性机制。
-Agents matching the ecological scale appear widespread as motifs in SES of successful governance, whether in fisheries, forests, or groundwater management, suggesting that reducing independent stakeholders linked to fragmentation is an essential primary mechanism for a structure to produce good results.
+
+## methods
+\subsection{Placebo Test}
+% 作为一种稳健性检验，安慰剂测试的必要性体现在两个原因上。
+For robustness, we conducted a placebo test because the synthetic control method neglects the influences of overall changes in factors in the same year by simply dividing time periods according to institutional shifts.
+Three steps were required to apply the placebo test:
+% (1) 对目标组中的每个省份$i$，计算所有潜在控制组与它之间特征向量的欧氏距离
+(1) For each province in the target group, we calculated the Euclidean distance of vectors between all provinces in the potential control group.
+% (2) 将距离由小到大排序后，选取特征向量最相似的三个省份，所有特征的均值作为 $i$ 的替代
+(2) After ranking the distances, the three provinces with the most similar economic context were used to generate an average paired treatment target unit.
+% (3) 对这个配对目标同样实施控制合成法（潜在控制组排除构成它的三个省）
+(3) We performed the same synthetic control analysis for this paired target (i.e., the potential control group excluding the three provinces in step 2).
+% 经过上述步骤，我们在理论上构建了一个相似的“区域”并实施了同样的控制合成实验。
+In this way, we theoretically constructed a pseudo-treated unit and performed the same synthetic control treatments.
+Because these placebo tests were directed at units unaffected by the institutional shifts, the results can be regarded as a reasonable baseline expectation or null model from which to assess the changes caused by other factors.

### 2022-04-12 docs/papers/01_manuscript/manuscript.tex
docs(finish-the-manuscript): manuscript v1.2
BREAKING CHANGE:

@@
     \centering
-    \includegraphics[width=32pc]{diagrams/structure.png}
+    \includegraphics[width=32pc]{diagrams/diagram.pdf}
 	\caption{
@@
 		% 国家政府在1987年和1998年先后两次出台了改变流域制度的政策，而黄河水利委员会、利益攸关的各省在不同制度时期具备的功能是不同的。
-		\textbf{A.} The national government changed YRB management policies and institutions in 1987 and 1998.
+%		\textbf{A.} The national government changed YRB management policies and institutions in 1987 and 1998.
 As a result, the Yellow River Conservancy Commission (YRCC) and the provinces acted differently in different periods.
@@
 		% 没有任何政策限制，各利益相关者此时期可以从单向但联通的河流生态单元内自由取水
-		\textbf{B.} 1975–1987: Without any constraints, water resources were freely accessible to each stakeholder (the provinces in this case, denoted by red circles) from a one-way but connected ecological unit (the Yellow River, denoted by the blue rectangle).
+		\textbf{1975–1987:} Without any constraints, water resources were freely accessible to each stakeholder (the provinces in this case, denoted by red circles) from a one-way but connected ecological unit (the Yellow River, denoted by the blue rectangle).
 		% 在政策1之后，每个使用者都被分配了能够开采河流地表水资源的配额，而黄委会的工作是对配额的使用进行统计与汇报。
-		\textbf{C.} 1987–1998: After the implementation of policy 1 in 1987, each user was assigned a quota to withdraw surface water resources, and the YRCC (yellow triangle) was tasked with reporting on water quota use.
+		\textbf{1987–1998:} After the implementation of policy 1 in 1987, each user was assigned a quota to withdraw surface water resources, and the YRCC (yellow triangle) was tasked with reporting on water quota use.
 		% 第二个政策之后，利益相关者取水需要向黄委会申请，黄委会则根据用水配额来批发许可。因此此时黄委会与利益相关者之间产生了直接的双向联系，监督他们对资源配额的取用。
-		\textbf{D.} 1998–2008: After the implementation of policy 2, stakeholders had to apply for water resources from the YRCC, which then licensed water use according to the quota.
+		\textbf{1998–2008:} After the implementation of policy 2, stakeholders had to apply for water resources from the YRCC, which then licensed water use according to the quota.
 Under this institution, the YRCC had direct two-way connections between provinces and ecological components.
@@
 %\end{figure*}
+\input{02_structures.tex}
 \input{02_results.tex}
@@
 To quantify water use, we used synthetic control methods to estimate possible trends of water use in the absence of institutional shifts.
-In addition, as a robustness test, we conducted a matched placebo test (creating a “null model”) to exclude the effects of other factors that were contemporaneous with the institutional shifts.
 Finally, we created an economic model based on marginal revenue to provide a theoretical explanation for the observed “sprint effect” phenomenon.
@@
 
-We focused on two features of water use in the YRB: total water use and diversification of water allocation.
+We focused on total water use in the YRB.
 The actual water uses are given by the dataset, but when the synthetic control method is used to predict the water use of the control group, other independent influences need to be considered.
-Thus, we used economic features that are highly related to water use to extrapolate demand (e.g., agriculture, industry, service industry, and domestics, see \textit{Supplementary Material S2, Table 1} To measure resource allocation diversification between the upper, middle, and lower reaches, we used “entropy” as a simple index,
+Thus, we used economic features that are highly related to water use to extrapolate demand (e.g., agriculture, industry, service industry, and domestics, see \textit{Supplementary Material S2, Table 1}
 
-$$ Index_{entropy} = \sum_i{p_i *log(p_i)} $$
-
-% 式子中的p是每个使用的水占流域总用水的比例
-Where $p_i$ is the proportion of water uses for region $i$ to the total water uses in the basin.
-A larger index value indicates the proportion of water resources actually used is closer to the average among the upper, middle, and lower reaches.
-
-\subsection{Synthetic Control}
+\subsection{Difference Synthetic Control}
 Synthetic control is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadie2010, abadie2015, hill2021}.
@@
 The net effect of the water allocation institutional shift was then estimated by calculating the difference of water uses after the institutional shift between the treated group and the control group, compared with the water use difference before the shift.
-
-\subsection{Placebo Test}
-% 作为一种稳健性检验，安慰剂测试的必要性体现在两个原因上。
-For robustness, we conducted a placebo test because the synthetic control method neglects the influences of overall changes in factors in the same year by simply dividing time periods according to institutional shifts.
-Three steps were required to apply the placebo test:
-% (1) 对目标组中的每个省份$i$，计算所有潜在控制组与它之间特征向量的欧氏距离
-(1) For each province in the target group, we calculated the Euclidean distance of vectors between all provinces in the potential control group.
-% (2) 将距离由小到大排序后，选取特征向量最相似的三个省份，所有特征的均值作为 $i$ 的替代
-(2) After ranking the distances, the three provinces with the most similar economic context were used to generate an average paired treatment target unit.
-% (3) 对这个配对目标同样实施控制合成法（潜在控制组排除构成它的三个省）
-(3) We performed the same synthetic control analysis for this paired target (i.e., the potential control group excluding the three provinces in step 2).
-% 经过上述步骤，我们在理论上构建了一个相似的“区域”并实施了同样的控制合成实验。
-In this way, we theoretically constructed a pseudo-treated unit and performed the same synthetic control treatments.
-Because these placebo tests were directed at units unaffected by the institutional shifts, the results can be regarded as a reasonable baseline expectation or null model from which to assess the changes caused by other factors.
 

### 2022-04-12 docs/papers/02_appendix/abstract.tex
testing
docs(finish-the-manuscript): manuscript v1.2
BREAKING CHANGE:

--- 2022-03-10 docs/papers/elements/abstract.tex
@@
-%! Abstract
-Increasing competition for water is challenging management institutions of large river basins around the world.
-Institutions that successfully support sustainable water resource use are structurally well-aligned with water provisioning and social-ecological demands.
-However, what constitutes a well-aligned institution in this context is poorly understood.
-We analyzed institutional shifts in water resource allocation, exploiting two quasi-natural experiments of the Yellow River Basin, China.
-Using a synthetic control identification strategy, we analyzed an institution that was intended to prevent water overuse but instead resulted in a social-ecological structural mismatch, leading to a 164\% increase beyond the expected total water use.
-We applied a novel economic model that suggested that this “sprint effect” (i.e., rapid competing in resource use) and the resulting ecological crisis were driven by incentive distortions in water allocation bargaining, which in turn, led to each province trying to pre-emptively increase their water quotas for long-term gain.
-Our analysis highlights the need to carefully evaluate institutional fit in the management of water in large river basins, particularly to avoid the possibility of incentive distortion.
+Increasing competition for water is leading depletion of freshwater globally and calls for an urgent transformation of the governance system.
+Intense water use in one of the most anthropogenic interfered large river basins, the Yellow River Basin (YRB), once led to overburdened drying up but finally had a successful restoration by sequential water governance institutions.
+Focusing on two water-demand institutions, the Water Allocation Scheme since 1987 (87-WAS) and the Unified Basinal Regulation since 1998 (98-UBR), we quantitatively analyzed how the institutional shifts played a role in the YRB.
+Our results suggest that the observed water use of the YRB provinces had an $8.57\%$ increase than expectation in the decade after the 87-WAS but significantly decreased by $0.49 km^3$ per year after the 98-UBR.
+Furthermore, the 87-WAS stimulated water use in provinces with more water uses (e.g., Neimeng, Henan, and Shandong) but the 98-UBR regulated nearly all provinces.
+Linking our results to a mathematical marginal benefits model for a coherent interpretation, we deepen insights between the structures and outcomes in such social-ecological systems by the quasi-natural experiments of the YRB, thus providing a valuable guideline for SESs worldwide facing water depletion.

### 2022-04-16 docs/papers/01_manuscript/02_structures.tex
refactor(change-structure-of-the-paper-into-results/discussions-detached-version): refactor the manuscript

@@
-\subsection{Shifts of institution and SES structure in the YRB}
-\label{result-0}
+%! Author = songshgeo
+%! Date = 2022/3/10
+
+% \subsection{INSTITUTIONAL SHIFTS AND STRUCTURES}
+\subsection{Institutional shifts and structures}
+\label{results-1}
 
 % 制度变动综述
-Including the national authorities, the basin management authorities, provinces, cities, and even districts, top-down institutional structures of the YRB started to evolve up to now (\textit{S1 in Supplementary Material}).
+% Including the national authorities, the basin management authorities, provinces, cities, and even districts, top-down institutional structures of the YRB started to evolve up to now (\textit{S1 in Supplementary Material}).
 As a pioneer in water governance shifting in China, the YRB started to explore the initial water allocating scheme in the 1970s.
@@
 Although we abstract the two major institutional shifts from document interpretations, many studies used these two changes as baselines for the YRB's water governance history and widely recognized their importance.
+
+\begin{figure*}[!ht]
+    \centering
+    \includegraphics[width=32pc]{diagrams/diagram.pdf}
+	\caption{
+		% 黄河流域的制度变迁与经济社会结构差异。
+		Institutional shifts and related SES structures in the Yellow River Basin (YRB). See \textit{Supplementary Material S1} for detailed introduction for the institutions.
+		% 国家政府在1987年和1998年先后两次出台了改变流域制度的政策，而黄河水利委员会、利益攸关的各省在不同制度时期具备的功能是不同的。
+%		\textbf{A.} The national government changed YRB management policies and institutions in 1987 and 1998.
+As a result, the Yellow River Conservancy Commission (YRCC) and the provinces acted differently in different periods.
+Three different SES structures existed successively in the YRB.
+		% 没有任何政策限制，各利益相关者此时期可以从单向但联通的河流生态单元内自由取水
+		\textbf{1975–1987:} Without any constraints, water resources were freely accessible to each stakeholder (the provinces in this case, denoted by red circles) from a one-way but connected ecological unit (the Yellow River, denoted by the blue rectangle).
+		% 在政策1之后，每个使用者都被分配了能够开采河流地表水资源的配额，而黄委会的工作是对配额的使用进行统计与汇报。
+		\textbf{1987–1998:} After the implementation of policy 1 in 1987, each user was assigned a quota to withdraw surface water resources, and the YRCC (yellow triangle) was tasked with reporting on water quota use.
+		% 第二个政策之后，利益相关者取水需要向黄委会申请，黄委会则根据用水配额来批发许可。因此此时黄委会与利益相关者之间产生了直接的双向联系，监督他们对资源配额的取用。
+		\textbf{1998–2008:} After the implementation of policy 2, stakeholders had to apply for water resources from the YRCC, which then licensed water use according to the quota.
+Under this institution, the YRCC had direct two-way connections between provinces and ecological components.
+	}
+	\label{structure}
+\end{figure*}

### 2022-04-16 docs/papers/01_manuscript/03_results.tex
refactor(change-structure-of-the-paper-into-results/discussions-detached-version): refactor the manuscript

@@
 % \MakeUppercase{\subsection{Cascading effects of the institutional shifts}}
-\subsection{Cascading effects of the institutional shifts}
-\label{effects}
-% 从国家官员到流域管理官员，从省、市到区，长江流域自上而下的制度结构开始演变至今
-Including the national authorities, the basin management authorities, provinces, cities, and even districts, top-down institutional structures of the YRB started to evolve up to now (\textit{S1 in Supplementary Material}).
-% 从70年代黄河断流开始摸索87-WAS的初步治理方案，到98-UBR成功解决断流后于2008年强化该制度，黄河一直是中国水治理制度转变的先行者。
-As a pioneer in water governance shifting in China, the YRB started to explore the initial water allocating scheme in the 1970s, then found a successful solution of dring-up in 1998, and promoted completely since 2008.
-% 1987年(87-WAS)和1998年(98-UBR)的制度变迁是YRB中两个被广泛认可的制度演变里程碑(图~\ref{fig:structure} \textit{S1 in  Supplementary  Methods})。
-Throughout, the institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones of water governance (Figure~\ref{fig:structure} and \textit{S1 in Supplementary Material}).
-Our analysis period, therefore, spans from 1975 to 2008, with the human-water system shifted between three different institutional structures (Figure~\ref{fig:structure}).
 
-Here, we use Differenced Synthetic Control method, which considers economic growth and natural background, to estimate theoretical water uses scenarios without these policy interferences (\textbf{Methods}; \textit{S2 in Supplementary Material}).
-% 我们的结果表明，1987年(87-WAS)的制度转变实际上刺激了各省比没有干扰时使用更多的水，观测到比预期增加了10(图~\ref{fig:main_results}A和B)。
-Our results suggest that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without the interference (Figure~\ref{fig:main_results}A).
-% 在1998年制度再次改变后，用水量增加的趋势似乎被有效地抑制了，观察到的总用水量比预期减少了10(图~\ref{fig:main_results} C和D)。
-However, after the institution shifted again in 1998 (98-UBR), the trend of increasing water use appeared to be effectively suppressed, with total observed water consumption decreasing by $260\%$ relative to the estimation (Figure~\ref{fig:main_results} B).
-% 87-WAS后用水量的增加与1987 - 1998年地表径流严重干涸的事实相吻合，这是河流退化和环境危机的一个明显的试金石
-The increased water uses after 87-WAS align with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{fig:main_results}C).
-% 尽管在1998年制度转变后的十年内，干旱程度有增无减，但断流的环境危机却得到了有效解决。
-On the other hand, although the density of droughts increased in the decade after the 98-UBR, the environmental crisis of river drying-up was effectively resolved (Figure~\ref{fig:main_results}C).
-% 正如许多研究指出的，这主要是大规模制度变迁的成功
-As literature has suggested, this institution shift contributed a lot to the successful water governance.
+% \subsection{ISS IMPACT ON WATER USE OF THE YRB}
+\subsection{ISs impact on water use of the YRB}
+\label{result-2}
+% 结果一：展示制度转变带来的用水量变化
+
+\label{result-1-p2}
+Here, we use Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without basinal policy interferences (\textbf{Methods}; \textit{S2 in Supplementary Material}).
+Our results suggest that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without the interference (Figure~\ref{main_results}A).
+From 1988 to 1998, while the estimation of water use only suggests $956.38 km^3$, the observed water use of the YRB provinces reached $1038.36 km^3$ in sum, $8.57\%$ increased.
+However, after the institution shifted again in 1998 (98-UBR), the trend of increasing water use appeared to be effectively suppressed.
+From 1998 to 2008, the total observed water use decreased by $0.49 km^3$ per year, while the estimation of water use still suggests $1.03 km^3$ increases (Figure~\ref{main_results} B).
+The increased water uses after 87-WAS aligns with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{main_results}C).
+On the other hand, the environmental crisis of river drying up was effectively resolved after the 98-UBR, though the density of droughts still increased for decades (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{main_results}C).
+In line with previous literature had reported; therefore, the institution shift of 98-UBR contributed a lot to the successful water governance. %! citation
 
@@
         \textbf{B.} water uses of the YRB before and after the institutional shift in 1998 (98-UBR).
-While the blue lines are statistic water use data, grey ones are the estimation from the Differenced Synthetic Control method with economic and environmental background controlled.
-        \textbf{C.}
+While the blue lines are statistic water use data, the grey ones are the estimation from the Differenced Synthetic Control method with economic and environmental background controlled.
+        \textbf{C.} Drought intensity in the YRB and drying up events of the Yellow River. The size of the grey bubbles denotes the length of a drying upstream.
     }
-    \label{fig:main_results}
+    \label{main_results}
 \end{figure*}
 
-% 然而，87-WAS 也非大多分析报告所认为的“没有起到效果”，因为制度变化完全没有产生影响时，流域的用水量将更接近我们的模型预测。
-Furthermore, 87-WAS did not ``have no effect'' as previous analyses suggested because water uses will be closer to what our models predicted when the shift was a blank policy.
-% 除了环境背景外，我们的预测还考虑了经济因素，假设经济总量与用水量之间的生产函数保持不变。
-Besides environmental background, our forecast takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textit{S2 in Supplementary Material}).
-% 由于单位水资源的生产效率在这一时期实际上保持了相似的趋势，这意味着流域用水量的加速增长不是经济增长的必然结果。
-However, the production efficiency of unit water resources kept similar trends between provinces of the YRB and others (Figure \textit{S3 in Supplementary Material}), which means that the accelerated growth of basinal water uses was not the inevitable result of economic growth.
-% 但实际上，我们的结果表明相对于正常的经济发展进程来说，黄河流域的水资源利用反而更像是受到了刺激。
-However, our results suggest that water use (especially for irrigation) in the YRB was more likely to be partly stimulated by the shift in 1987 besides economic growth.
-% 这种用水量的加速增长与制度设计时遏制用水、保护黄河流域有限的水资源的初衷相悖。
-This accelerated growth in water use was contrary to the original intention of the 87-WAS in conserving the limited water.
+% \subsection{REGIONAL DIFFERENCES IN RESPONSES TO THE IS}
+\subsection{Regional differences in responses to the ISs}
+\label{result-3}
+% 结果2部分：展示区域相应差异
 
-% 两次制度转变带来的级联效应存在巨大差异
-The cascading effects of the two institutional shifts were very different, while their reframed SES structures have direct differences.
-% 在我们的研究期间(从1975年到2008年)，机构在三种不同的结构之间转换:免费访问、87-WAS和98-UBR。
-In our study period, the institution shifted between three different structures (XXX, XXX, and XXX) (Figure~\ref{fig:structure}).
-%! 这里还是需要名字的
-% 长江水利委员会是长江流域的主要负责人，其任务是报告和分析1998年以前长江流域的用水量(87-WAS之后)。
-However, the YRCC, whose primary official response to the river before 1998, the mandate was to conserve the riverway environment, construct and maintain infrastructures, and report on and analyze water consumption (after the 87-WAS) in the YRB, i.e., connecting the ecological nodes (different river reaches) horizontally ~\cite{wang2019a}.
-% 这意味着，而与生态节点直接联系的各利益相关者之间没有横向连接。
-Thus, until the institutional shift of 98-UBR, with no necessity to apply for a water permit from YRCC, there were no horizontal connections (cooperations or agreements) between the various stakeholders (provinces) directly connected to the ecological sections.
-% 许多不同领域的经验研究指出这种结构很可能是错配的，因为这些利益相关者难以从全局出发维护好互相联系的生态系统。
-Empirical studies in many different fields indicate that this structure is likely to be mismatched, as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
-\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
-% 87-WAS带来的效果再一次说明了这种阻碍可持续性的治理结构需要得到重视。
-The cascading effect of the 87-WAS once again demonstrates that the more stakeholders, the more difficult it is to have a win-win situation of environment and interests \cite{hegwood2021} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.
+Differences between stakeholders in responses to institutional shifts are vital to understanding the mechanism between structures and outcomes.
+Our results show that the proportion of accelerated water use in each province after the decade of 87-WAS (the proportion of actual water use exceeding the predicted water use by the model) has a significant correlation ($p<0.05$, see \textbf{Methods}) to the Yellow River water use in each province (Figure~\ref{upset}A).
+Furthermore, while no evident impacts for most provinces (no more than $10\%$ differences, the apparent acceleration effects were only prominent in the big water-using provinces (e.g., Neimeng, Henan, and Shandong.
+Figure~\ref{upset}B).
+In particular, Neimeng and Shandong, both provinces that exceeded the prescribed water uses of the 87-WAS, used $44.25\%$ and $25.69\%$ more water uses than the prediction from 1987 to 1998, respectively.
+Furthermore, the satisfaction of each province with the water allocation stipulated by the 87-WAS (expressed by the difference between the actual water allocation of each province and the expected planning value) has little significant correlation to the acceleration.
+By contrast, after the 98-UBR, except Shaanxi (which has always been abundant in water quota) had an evident ($17.53\%$) increase in water use, almost all provinces have seen significant declines in water use ($-12.5\%$ on average).
+However, neither the satisfaction nor Yellow River water use correlates with the declines after the 98-UBR.
+
+\begin{figure*}[!h]
+    \centering
+    \includegraphics[width=32pc]{outputs/upset_87.pdf}
+    \caption{
+        \textbf{A.} The partial correlation coefficient between wate uses (WU) of Yellow River (YR), unsatisfied ratio (compared with requirements in water plan and supply in the 87-WAS), and the average accelerated ratio.
+        \textbf{B.} Average accelerated ratio of water uses for each province in the YRB during the decade after 87-WAS (from 1987 to 1998).
+        \textbf{Mian users:} Major water consumption provinces (over the median).
+        \textbf{Overused:} violate the 87-WAS in average water uses.
+    }
+    \label{upset}
+\end{figure*}

### 2022-04-16 docs/papers/01_manuscript/04_discussion.tex
refactor(change-structure-of-the-paper-into-results/discussions-detached-version): refactor the manuscript

@@
 
-\subsection{Limitation, novel insights and policy implications}
-\label{insights}
+% \subsection{CAUSES OF INSTITUTIONAL IMPACTS}
+% \subsection{}
+\label{discussion-1}
+% discussion-1: 主要介绍结果的意义、合理性
+
+Besides environmental background, our forecast by DSC takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textit{S2 in Supplementary Material}).
+It means the forecast of water use includes the part caused by the increased economic volume, while the outcomes of the economy (GDP in different sectors) of the YRB maintained a parallel trend with other regions during the period (\textit{S3 in Supplementary Material} Figure~\ref{S3-1}).
+Therefore, 87-WAS did not ``have little effect'' as previous analyses suggested (cites) but led to increased water use because the difference between prediction and observation will be trivial when the shift was just a blank policy by applying the DSC method.
+%!
+Citation
+Water-use intensity is another crucial factor in interpreting the differences besides the economic factors (e.g., irrigated areas and industrial outcomes) considered and controlled by the method.
+In addition to the expansion of irrigation area after the 87-WAS, water uses per unit of irrigation area also rapidly widened the gap with the average level of the rest provinces.
+However, the industry water use intensity hardly changed (\textit{S3 in Supplementary Material} Figure~\ref{S3-2}).
+As a previous report sigh: although the key to alleviating the drought is saving water in the irrigated areas, the tragedy of scrambling for water appeared in provinces and irrigated areas %!
+\cite{mao2000}.
+In terms of the average ratio of water-saving irrigation area (refer to drip or sprinkler irrigation systems and canal lining), although there was a significant increase in the whole country after 1987, the YRB did not rapidly open a noticeable gap until about 1994 (Figure~\ref{S3-3}).
+As a result, despite the irrigation area expanding, scrambling for water resources without any incentive to optimize production per unit of water resources accelerated holistic water use.
+This accelerated water use was contrary to the original intention of the 87-WAS in conserving the limited water, and the failure was a barrier to the sustainability %! \cite{huangang2002}.
+
+% 过去的研究总结出87-WAS收效甚微的几个因素：
+Previous studies have summarised factors that contribute to the non-ideal effect of 87-WAS: (1) The YRCC had no right to punish the provinces for over-exploitation; (2) the water quotas were annual values, causing provinces to rob water in the dry season; (3) The YRCC can make statistics on water use in the mainstream but cannot on the tributaries, so provinces water use underreport %!
+\cite{huangang2002}.
+However, the effects of the two institutional shifts (the 87-WAS and the 98-UBR) were significantly different, which the above reasons cannot fully explain.
+Between the 98-UBR and the further refinement of the unified regulation in 2008, there was still a lack of a temporary water allocation scheme and effective monitoring of tributaries.
+Moreover, without any actual punishment, provinces with high water consumption (such as Inner Mongolia and Shandong) continued to exceed the quota after 98-UBR.
+As we have analyzed (Figure~\ref{structure}), the difference between the two institutional shifts is mainly reflected in the structure of linkages between social actors.
+Until the institutional shift of 98-UBR, with no necessity to apply for a water permit from YRCC, there were no horizontal connections (cooperations or agreements) between the various stakeholders (provinces) directly connected to the ecological units.
+Make it clear that the YRCC was responsible for regulating provincial water use; that is, each province has made it clear that in the long run, water resources are not ``internal'' but ``dependent'' on YRCC.
+In that way, the YRCC, whose authority scale matches the whole river basin, also took the primary responsibilities to the river, and literature recognized the structure as a social-ecological fit that usually led to good outcomes.
+Empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
+\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
+The effect of the institutional shifts once again demonstrated that it is not easy to have a win-win situation of environment and interests in complex coupled human-nature systems \cite{hegwood2022} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.
+
+% \subsection{LINKING STRUCTURES WITH ISS OUTCOMES}
+% \subsection{Linking structures with ISs outcomes}
+\label{discussion-2}
+% discussion-2: 机制解释
+% 经济模型与理论解释
+Differences in the pattern of the response by provinces can demonstrate the influence of social-ecological structures led by the institutional shifts.
+We analyzed mathematically why the mismatched structure made limited water use holistically elusive in the institution shift of the 87-WAS but finally achieved by the 98-UBR (\textit{method} and \textit{Supplementary Material S4}).
+By taking the structure before and after the two institutional shifts as different basic assumptions (before 87-WAS: free access to water; after 87-WAS but before 98-UBR: decisions on water use under quotas; after 98-UBR: unified regulation), we use the marginal benefit model to analyze the theoretical optimal water consumption of stakeholders in each scenario.
+The analysis of the model also shows that 98-UBR can reduce the overall water use of the basin while 87-WAS can increase the water use of the basin when the same parameters are guaranteed but the institutional structure changes.
+Before the 98-UBR, the model assumes that the separated ecological units (river reaches) link to stakeholders (related provinces) who use water to pursue their marginal benefits but have a potential political cost if they exceed the quota 87-WAS.
+Our model suggests that for users who are already economically efficient (who are already using more water), greater marginal returns from water induce the acceleration of extracting resources for future economic growth (Figure~\ref{economic_model}).
+Therefore, isolated stakeholders reacted to the similar marginal cost, and smaller water users have a threshold because of the political cost, so 87-WAS triggered an increased water use for the significant users.
+On the contrary, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs holistically as stakeholders only take corresponding responsibilities (follow the quota as possible as they can) to the YRCC (\textit{Supplementary Material S4}).
+As a result, unified regulating acted the core role after the 98-UBR and reduced water use of all stakeholders (provinces) by irregular ratios.
+
+The alignments of differences in institutional structures and outcomes here echo the hypothesis that successful governance of SES emerged by indirectly (or vertically) creating links between different stakeholders (in the YRB cases, through administration).
+When links The water quotas of 87-WAS (or the initial water rights) in our case studies went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
+The bargaining itself was also a process towards matches between their economic volume and water shares, as studies show that the large water users (like Shandong and Henan) need more water than their quota (in the 87-WAS) if only considering the economic equity when designing the institution.
+Furthermore, with information asymmetry between upper-level decision-makers and lower-level stakeholders in water use allocation, those with more current water use might have greater bargaining power.
+In practice, therefore, although the affected provinces may not have directly encouraged excessive resource use because of the institutional shift, they had a more considerable incentive to show their economic potential
+That aligns with the historical records that, even after the 87-WAS had already confirmed the quotas, provinces, especially water-intensive ones, challenged it by appearing to the higher central government for larger quotas.
+On the contrary, after YRCC as governing agent coordinated between stakeholders since 98-UBR, the external appeal of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment, \textit{Supplementary Material S3})
+\cite{krieger1955, ostrom1990}.
+Then, the YRCC, the authority for approving water applications from all stakeholders, could adjust water use quotas according to the river conditions of the whole basin.
+The 98-UBR led to a structure for achieving social-ecological fits in both basins (between YRCC and the YRB) and regions (between provincial economy and their water shares).
+
+% \subsection{LIMITATION, INSIGHTS AND IMPLICATIONS}
+\subsection{Limitation, insights and implications}
+\label{discussion-3}
+% discussion-3: 启示、未来的展望
 
@@
 First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use.
-Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wang2019d,speed2013}; top-down regulations can trigger immediate institutional shifts, and sharp SES structural changes \cite{speed2013,roland2004}.
+Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wang2019d,speed2013}; top-down regulations can trigger immediate institutional shifts and sharp SES structural changes \cite{speed2013,roland2004}.
 In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and clarifies the causal link between SES structure and outcome.

### 2022-04-16 docs/papers/01_manuscript/06_methods.tex
refactor(change-structure-of-the-paper-into-results/discussions-detached-version): refactor the manuscript

--- 2022-04-12 docs/papers/01_manuscript/manuscript.tex
@@
-\documentclass{../nsr}
-
-\usepackage{amsmath,graphicx,array}
-\usepackage{dcolumn,soul}%
-\let\openbox\relax
-\usepackage{amsthm}
-\usepackage[figuresright]{rotating}%
-\usepackage{algorithm, algorithmicx, algpseudocode}
-\usepackage{listings}%
-\usepackage{hyperref}
-
-\makeatletter
-%%
-\def\uns{\ifmmode\,\else$\,$\fi}%
-\newtheorem{theorem}{Theorem}
-\newtheorem{construction}{Construction}
-\newtheorem{estimate}{Estimate}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-\newtheorem{result}{Result}
-\newtheorem{algth}{Algorithm}
-\newtheorem{proposition}{Proposition}
-\newtheorem{hypothesis}{Hypothesis}
-\newtheorem{experiment}{Experiment}
-\newtheorem{definition}{Definition}
-\newtheorem{condition}{Condition}
-\newtheorem{property}{Property}
-\newtheorem{problem}{Problem}
-\newtheorem{fact}{Fact}
-\newtheorem{assumption}{Assumption}
-\newtheorem{eexample}{Example}
-\newtheorem{model}{Model}
-%%
-\makeatother
-
-\jvol{XX}
-\jnum{X}
-\jyear{Year}
-\doi{10.1093/nsr/XXXX}
-\received{XX XX Year}
-\revised{XX XX Year}
-\accepted{XX XX Year}
-
-\markboth{One, Two, and Three}{One, Two, and Three}
-\graphicspath{{../../../figs/}}
-
-\begin{document}
-
-\dhead{RESEARCH ARTICLE}
-\subhead{EARTH SCIENCES}
-\newtheorem{ass}{Assumption}   % My command. Assumptions.
-\newtheorem{case}{Case}  % My command. Cases
-
-\bibliographystyle{../nsr}
-
-\title{\input{title.tex}}  %! Notice Input
-
-\author{Shuang Song$^{1,2}$}
-\author{Huiyu Wen$^3$}
-\author{*Shuai Wang$^{1,2}$}
-\author{Xutong Wu$^{1,2}$}
-
-\author{Graeme S. Cumming$^{4}$}
-\author{Bojie Fu$^{1,2,5}$}
-
-\affil{$^1$State Key Laboratory of Earth Surface Processes and Resource Ecology,
-     Faculty of Geographical Science,
-     Beijing Normal University,
-     Beijing 100875,
-     P.R. China}
-
-\affil{$^2$Institute of Land Surface System and Sustainability,
-     Faculty of Geographical Science,
-     Beijing Normal University,
-     Beijing 100875,
-     P.R. China}
-
-\affil{$^3$School of Finance,
-     Renmin University of China,
-     Beijing 100875,
-     P.R. China}
-
-\affil{$^4$ARC Centre of Excellence for Coral Reef Studies,
-     James Cook University,
-     Townsville 4811,
-     QLD, Australia}
-
-\affil{$^5$The research for this article was financed by.......
-The authors thank.......
-for insightful comments and .......
-for expert research assistance.
-A supplementary online appendix is available with this article at the \em{National Science Review} website.}
-
-\authornote{\textbf{Corresponding authors.} Email: shuaiwang@bnu.edu.cn}
-%\authornote{Shuang Song and Huiyu Wen equally contributed to this work.}
-
-\abstract[ABSTRACT]{
-    \input{abstract}
-}  %! Notice input
-
-\keywords{\input{keywords}}  %! Notice input
-\maketitle
-
-\section{INTRODUCTION}\label{intro}
-\input{01_introduction.tex}
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=16pc]{diagrams/framework.jpg}
-%	\caption{
-%		Framework for understanding linkages between SES structures and outcomes.
-%		\textbf{a.} The general framework for analyzing social-ecological systems (SESs) (adapted from Ostrom \cite{ostromGeneralFrameworkAnalyzing2009}).
-Institutions embedded in SESs may reshape structures by changing the interactions between core subsystems, resulting in different outcomes.
-%        Three typical types of abstracted SES structures are shown as \textbf{b.}, \textbf{c.} and \textbf{d.} (adapted from Bodin, 2017)\cite{bodinCollaborativeenvironmentalgovernance2017}.
-Red circles indicate social actors, and green ones indicate ecological components.
-Connection (ties between two ecological components), collaboration (ties between two social actors), or management (ties between a social actor and an ecological component) exist when two units are linked by gray lines.
-The gray dashed lines show aligned SES structures that are more likely to result in a desirable outcome according to empirical evidence.
-%	}
-%    \label{framework}
-%\end{figure}
-
-%\section{Context of institutional shifts}\label{institution}
-%\input{02_institution.tex}
-
-\begin{figure*}[!ht]
-    \centering
-    \includegraphics[width=32pc]{diagrams/diagram.pdf}
-	\caption{
-		% 黄河流域的制度变迁与经济社会结构差异。
-		Institutional shifts and related SES structures in the Yellow River Basin (YRB). See \textit{Supplementary Material S1} for detailed introduction for the institutions.
-		% 国家政府在1987年和1998年先后两次出台了改变流域制度的政策，而黄河水利委员会、利益攸关的各省在不同制度时期具备的功能是不同的。
-%		\textbf{A.} The national government changed YRB management policies and institutions in 1987 and 1998.
-As a result, the Yellow River Conservancy Commission (YRCC) and the provinces acted differently in different periods.
-Three different SES structures existed successively in the YRB.
-		% 没有任何政策限制，各利益相关者此时期可以从单向但联通的河流生态单元内自由取水
-		\textbf{1975–1987:} Without any constraints, water resources were freely accessible to each stakeholder (the provinces in this case, denoted by red circles) from a one-way but connected ecological unit (the Yellow River, denoted by the blue rectangle).
-		% 在政策1之后，每个使用者都被分配了能够开采河流地表水资源的配额，而黄委会的工作是对配额的使用进行统计与汇报。
-		\textbf{1987–1998:} After the implementation of policy 1 in 1987, each user was assigned a quota to withdraw surface water resources, and the YRCC (yellow triangle) was tasked with reporting on water quota use.
-		% 第二个政策之后，利益相关者取水需要向黄委会申请，黄委会则根据用水配额来批发许可。因此此时黄委会与利益相关者之间产生了直接的双向联系，监督他们对资源配额的取用。
-		\textbf{1998–2008:} After the implementation of policy 2, stakeholders had to apply for water resources from the YRCC, which then licensed water use according to the quota.
-Under this institution, the YRCC had direct two-way connections between provinces and ecological components.
-		% 由于政策1与政策2都是为了解决黄河断流的生态问题而提出的，因此在结果与政策预期严重相反的第二时期（灰色阴影时段），是制度导致了错配的社会-生态系统结构。
-%		\textbf{E.} A timeline of the Yellow River and drying conditions.
-The size of the circles indicates the length of section that dried up (km), and the y-axis indicates the length of the drying period.
-Both policy 1 and policy 2 were put forward to solve this ecological crisis.
-The mismatch created by policy 1 is clearly correlated with the unintended outcomes shown in the second (gray-shaded) period.
-	}
-	\label{structure}
-\end{figure*}
-
-\section{RESULTS AND DISCUSSION}\label{results}
-%\begin{figure*}[!h]
-%    \centering
-%    \includegraphics[width=32pc]{outputs/main_results2.jpg}
-%    \caption{
-%        Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
-\textbf{A}: water uses of the YRB before and after the institutional shift in 1987 (87-WAS); \textbf{A}: water uses of the YRB before and after the institutional shift in 1998 (98-UBR).
-While the blue lines are observed data, gray ones are estimated by the Differenced Synthetic Control method with economic and environmental background controlled.
-\textbf{C}
-%    }
-%    \label{main_results}
-%\end{figure*}
-\input{02_structures.tex}
-\input{02_results.tex}
-\input{03_causes.tex}
-\input{04_discussion.tex}
-%\subsection{CAUSES}\label{causes}
-%\input{model}
-%\input{table.tex}
-
-%\section{DISCUSSION}\label{discussion}
-%\input{04_discussion.tex}
-
-\section{MATERIALS AND METHODS}
-%Detailed methods are given inthe online supplementary material.
+%! Author = songshgeo
+%! Date = 2022/3/10
 
@@
 Extensions of the model are shown in \textit{Supplementary Material S3}.
-
-\section{CONCLUSION}\label{conclusion}
-\input{05_conclusion.tex}
-
-\appendix
-\label{appendix}
-%%%%%%%% -----  02_appendix -------- %%%%%%%%%%
-
-%% Put the bibliography here, most people will use BiBTeX in
-%% which case the environment below should be replaced with
-%% the \bibliography{} command.
-\bibliography{../WAInstitution_YRB_2021}
-
-%% Here is the endmatter stuff: Supplementary Info, etc.
-%% Use \item's to separate, default label is "Acknowledgements"
-
-\end{document}

### 2022-04-16 docs/papers/01_manuscript/manuscript.tex
refactor(change-structure-of-the-paper-into-results/discussions-detached-version): refactor the manuscript

@@
 \usepackage{hyperref}
-
 \makeatletter
-%%
 \def\uns{\ifmmode\,\else$\,$\fi}%
@@
 
-\section{INTRODUCTION}\label{intro}
+\section{INTRODUCTION}\label{sec:introduction}
 \input{01_introduction.tex}
 
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=16pc]{diagrams/framework.jpg}
-%	\caption{
-%		Framework for understanding linkages between SES structures and outcomes.
-%		\textbf{a.} The general framework for analyzing social-ecological systems (SESs) (adapted from Ostrom \cite{ostromGeneralFrameworkAnalyzing2009}).
-Institutions embedded in SESs may reshape structures by changing the interactions between core subsystems, resulting in different outcomes.
-%        Three typical types of abstracted SES structures are shown as \textbf{b.}, \textbf{c.} and \textbf{d.} (adapted from Bodin, 2017)\cite{bodinCollaborativeenvironmentalgovernance2017}.
-Red circles indicate social actors, and green ones indicate ecological components.
-Connection (ties between two ecological components), collaboration (ties between two social actors), or management (ties between a social actor and an ecological component) exist when two units are linked by gray lines.
-The gray dashed lines show aligned SES structures that are more likely to result in a desirable outcome according to empirical evidence.
-%	}
-%    \label{framework}
-%\end{figure}
+\section{RESULTS}\label{sec:results}
+\input{02_structures.tex}
+\input{03_results.tex}
 
-%\section{Context of institutional shifts}\label{institution}
-%\input{02_institution.tex}
+\section{DISCUSSION}\label{sec:discussion}
+\input{04_discussion.tex}
 
-\begin{figure*}[!ht]
-    \centering
-    \includegraphics[width=32pc]{diagrams/diagram.pdf}
-	\caption{
-		% 黄河流域的制度变迁与经济社会结构差异。
-		Institutional shifts and related SES structures in the Yellow River Basin (YRB). See \textit{Supplementary Material S1} for detailed introduction for the institutions.
-		% 国家政府在1987年和1998年先后两次出台了改变流域制度的政策，而黄河水利委员会、利益攸关的各省在不同制度时期具备的功能是不同的。
-%		\textbf{A.} The national government changed YRB management policies and institutions in 1987 and 1998.
-As a result, the Yellow River Conservancy Commission (YRCC) and the provinces acted differently in different periods.
-Three different SES structures existed successively in the YRB.
-		% 没有任何政策限制，各利益相关者此时期可以从单向但联通的河流生态单元内自由取水
-		\textbf{1975–1987:} Without any constraints, water resources were freely accessible to each stakeholder (the provinces in this case, denoted by red circles) from a one-way but connected ecological unit (the Yellow River, denoted by the blue rectangle).
-		% 在政策1之后，每个使用者都被分配了能够开采河流地表水资源的配额，而黄委会的工作是对配额的使用进行统计与汇报。
-		\textbf{1987–1998:} After the implementation of policy 1 in 1987, each user was assigned a quota to withdraw surface water resources, and the YRCC (yellow triangle) was tasked with reporting on water quota use.
-		% 第二个政策之后，利益相关者取水需要向黄委会申请，黄委会则根据用水配额来批发许可。因此此时黄委会与利益相关者之间产生了直接的双向联系，监督他们对资源配额的取用。
-		\textbf{1998–2008:} After the implementation of policy 2, stakeholders had to apply for water resources from the YRCC, which then licensed water use according to the quota.
-Under this institution, the YRCC had direct two-way connections between provinces and ecological components.
-		% 由于政策1与政策2都是为了解决黄河断流的生态问题而提出的，因此在结果与政策预期严重相反的第二时期（灰色阴影时段），是制度导致了错配的社会-生态系统结构。
-%		\textbf{E.} A timeline of the Yellow River and drying conditions.
-The size of the circles indicates the length of section that dried up (km), and the y-axis indicates the length of the drying period.
-Both policy 1 and policy 2 were put forward to solve this ecological crisis.
-The mismatch created by policy 1 is clearly correlated with the unintended outcomes shown in the second (gray-shaded) period.
-	}
-	\label{structure}
-\end{figure*}
+\section{MATERIALS AND METHODS}\label{sec:methods}
+\input{06_methods.tex}
 
-\section{RESULTS AND DISCUSSION}\label{results}
-%\begin{figure*}[!h]
-%    \centering
-%    \includegraphics[width=32pc]{outputs/main_results2.jpg}
-%    \caption{
-%        Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
-\textbf{A}: water uses of the YRB before and after the institutional shift in 1987 (87-WAS); \textbf{A}: water uses of the YRB before and after the institutional shift in 1998 (98-UBR).
-While the blue lines are observed data, gray ones are estimated by the Differenced Synthetic Control method with economic and environmental background controlled.
-\textbf{C}
-%    }
-%    \label{main_results}
-%\end{figure*}
-\input{02_structures.tex}
-\input{02_results.tex}
-\input{03_causes.tex}
-\input{04_discussion.tex}
-%\subsection{CAUSES}\label{causes}
-%\input{model}
-%\input{table.tex}
-
-%\section{DISCUSSION}\label{discussion}
-%\input{04_discussion.tex}
-
-\section{MATERIALS AND METHODS}
-%Detailed methods are given inthe online supplementary material.
-
-% 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程
-We estimated and analyzed the net effects of two SES structural changes of water use.
-The actual water use of the Yellow River Basin was peroxided by the sum of the water use of the target group provinces.
-To quantify water use, we used synthetic control methods to estimate possible trends of water use in the absence of institutional shifts.
-Finally, we created an economic model based on marginal revenue to provide a theoretical explanation for the observed “sprint effect” phenomenon.
-A brief technical overview is given in \textit{Supplementary Material S2}.
-
-\subsection{Dataset and variables}
-% 我们使用中国1978年至2012年各省的年度用水量数据集，这个公开的数据集由全国水资源利用调查得到，详细可查看。
-We used China’s provincial annual water consumption dataset from 1978 to 2012.
-This publicly available dataset was obtained from the National Water Resources Utilization Survey; details are accessible from Zhou (2020)
-\cite{zhou2020}.
-A total of 10 provinces or regions have been directly affected by the water allocation institutional shifts in the YRB, accounting for $8.6\%$ of the total population of China (in 1990).
-Eight provinces have been particularly affected because of their greater dependence on the water resources from the Yellow River (see \textit{Supplementary Material S2}).
-Therefore, we divided the dataset into a “target group” and a “control group”, treating provinces that were greatly affected as the target group $(n=8)$ and provinces that were not affected by the institutional shifts as the potential control group $(n=20)$.
-
-We focused on total water use in the YRB.
-The actual water uses are given by the dataset, but when the synthetic control method is used to predict the water use of the control group, other independent influences need to be considered.
-Thus, we used economic features that are highly related to water use to extrapolate demand (e.g., agriculture, industry, service industry, and domestics, see \textit{Supplementary Material S2, Table 1}
-
-\subsection{Difference Synthetic Control}
-Synthetic control is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadie2010, abadie2015, hill2021}.
-In this study, we used a comparative event approach and compared actual post-institutional shift induced water use changes with an appropriate counterfactual of what the water use change would have been.
-The counterfactual was built as the optimally weighted average of provinces not exposed to the institutional shifts.
-The synthetic control method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity \cite{billmeier2013, smith2015}.
-In practice, each of the units (i.e., provinces) in the treated group were affected by institutional shifts in 1987 and 1998, each of which was taken as the “shifted” point $t_0$ and the two steady institutions as $t$ for analyzing in each shift.
-The synthetic control method generates the control unit by assigning a weight matrix $W$ to units of the potential control group, so that the treated unit and its control unit are similar in each variable before $t_0$, i.e.,
-
-$$\min(V_{i}^{t<t_0} - W_i * F_{control}^{t<t_0})$$
-
-where $V_i$ is a vector that indicates all features of a unit $i$ of the treated group, and $F_{control}$ is a matrix that consists of all features and units of the potential control group.
-$W_i$ is the weight matrix for target unit $i$.
-We minimized the root mean square error (RMSE) by using the Synth package in R \cite{abadieSynthPackageSynthetic2011, abadieComparativePoliticsSynthetic2015}.
-All codes are accessible in the repository.
-
-% 这样一来，基于降维的思想，我们构建出了一系列特征上与实验组最为接近的可比对照。
-In accordance with the idea of dimensionality reduction, we constructed a series of comparable control units that were most similar in characteristics to the treated units.
-Because the units of the control group were not affected by the institutional shifts, after giving the same weight to the total water use of the control group $M_i * WU_{control}$, the result $W_i*WU_{control}$ could be considered a reasonable estimation of the untreated situation.
-The net effect of the water allocation institutional shift was then estimated by calculating the difference of water uses after the institutional shift between the treated group and the control group, compared with the water use difference before the shift.
-
-\subsection{Economic model}
-In order to understand the mechanisms underlying the empirical results, we developed a dynamic economic model to analyze how institutional change could have led to the sprint effect in water use.
-Specifically, we modeled individual provincial decision-making in water resources before quota execution.
-The analysis result implied that the underlying driver of CPR overuse was incentive distortion.
-
-In developing the model, we highlighted the main features of the YRB, as well as the water use institutions of 1987 and 1998. We proposed three intuitive and general assumptions.
-
-\begin{ass}
-    % (生产)为了简化，由于不可替代性，水是每个省的同质生产函数10的唯一投入。$F(x)$是连续的，满足Inada条件，即$F'(x)>0, F''(x)<0$(边际收益递减假设)，$F'(0)=\infty$,$ F'(\infty)=0$。产品产量处于完全竞争状态，单位价格为15。
-    (Water-dependent production) For simplicity, water is assumed to be the only input of the homogenous production function $F(x)$ of each province because of its irreplaceability.
-$F(x)$ is continuous and satisfies the Inada Conditions, i.e., $F'(x)>0, F''(x)<0$ (the diminishing marginal returns assumption), $F'(0)=\infty$,$ F'(\infty)=0$.
-The production output is under perfect competition, with a constant unit price of $P$.
-\end{ass}
-\begin{ass}
-    (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in N provinces, the cost of water use is equally assigned to each province under any water use.
-The unit cost of water is a constant $C$.
-\end{ass}
-\begin{ass}
-    (Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water uses.
-\end{ass}
-
-Under the above assumptions, we can demonstrate three cases consisting of local governments in YRB to simulate their water use decision-making and water use patterns.
-
-\begin{case} Decentralized institution:
-    This case corresponds to a situation without any high-level water allocation institution (i.e., before 1987, see Figure~\ref{structure} B).
-
-    When each province independently decides on its water use, the optimal water use $\hat x_i^*$ in province $i$ satisfies:
-    $$F'(x)=\frac{C}{P \cdot N}$$
-
-    When the decisions in different periods are independent, for $t=0,1,2 \ldots$, then:
-    $$\hat x_{it}^*=\hat x_i^*$$
-
-\end{case}
-
-\begin{case} Mismatched institution
-    This case corresponds to a mismatched institution (i.e., $1987\sim1998$, see Figure~\ref{structure} C).
-
-    The water quota is determined at $t=0$ and imposed in $t=1,2,\ldots$ The total quota is a constant denoted as $Q$, and the quota for province $i$ is determined in a proportional form:
-    $$Q_i=Q \cdot \frac{x_i}{x_i + \begin{matrix} \sum x_{-i} \end{matrix}}$$
-
-    Under a scenario with decentralized decision-making with a water quota institution, given other provinces’ water use decisions remain unchanged, the optimal water use $\widetilde x_{i0}^*$ of province $i$ at $t=0$ satisfies:
-
-    $F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot f(Q \cdot \frac{x_{i,0}}{\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix})^2}$.
-
-    When future water use is constrained by a water quota, the dynamic optimization problem of province $i$ is shown as follows:
-
-    $max  \quad P \cdot F(x_{i,0})-\frac{C \cdot \begin{matrix} \sum x_{i,0} + x_{-i,0} \end{matrix}}{N}+\beta P \cdot F(x_{i,1})+\beta^2 P \cdot F(x_{i,2})+...$
-
-    $=P \cdot F(x_{i,0})-C \cdot \frac{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}{N}+\frac{\beta}{1-\beta} P \cdot F(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}})$
-
-    First-order condition: $P \cdot F'(x_{i,0})-\frac{C}{N}+\frac{\beta}{1-\beta}[P \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0}+\begin{matrix} \sum  x_{-i,0} \end{matrix})^2}]=0$
-
-    where $f(\cdot)$ is the differential function of $F(\cdot)$.
-
-    The optimal water use in province i at t=0 $\widetilde x_{i,0}^*$ satisfies $P \cdot F'(x_{i,0})=\frac{C}{N}-\frac{\beta}{1-\beta} \cdot P \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$, i.e., $F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$.
-
-\end{case}
-
-\begin{case} Matched institution
-
-    This case corresponds to the institution under which the YRCC centrally managed water allocation between provinces (i.e., $1998\sim2008$, see Figure~\ref{structure} D).
-
-    When the $N$ provinces decide on water uses as unified whole (e.g., the central government completely decides and controls on the water use in each province), the optimal water use $x_i^*$ of province $i$ satisfies:
-
-    $$F'(x)=\frac{C}{P}$$
-
-\end{case}
-
-We propose Proposition 1 and Proposition 2:
-
-\textbf{Proposition 1}: Compared with the decentralized institution, a matched institution with unified management decreases total water use.
-
-Because $F’$ is monotonically decreasing, based on a comparison of costs and benefits for stakeholders (provinces) in the three cases,
-
-$$\widetilde x_i^*>\hat x_i^*>x_i^*$$
-
-The result of $\hat x_i^*>x_i^*$ indicates that individual rationality would deviate from collective rationality when property rights are unclear \cite{hardinTragedyCommons2009}, because of the common-pool characteristics of water
-\cite{castilla-rhoGroundwaterCommonPool2020,ostromGeneralFrameworkAnalyzing2009}.
-
-The difference of $\widetilde x_i^*$ and $\hat x_i^*$ stems from two parts: the marginal returns effect and the marginal costs effect.
-First, the “shadow value” provides additional marginal returns of water use in $t=0$, wwhich increases the incentives of water overuse by encouraging bargaining for a larger quota.
-Second, the future cost of water use would be degraded from $\frac{P}{N}$ to an irrelevant cost.
-
-The optimal water use under the three cases implies that mismatched institutions cause incentive distortions and lead to resource overuse.
-
-\textbf{Proposition 2}: The quota determination of the mismatched institution increases the incentives of current water use.
-
-The intuition for this proposition is straight-forward in that all provinces would use up their allocated quota under a relatively small $Q$.
-As $Q$ increases, the quota would provide higher future benefits for a pre-emptive water use strategy.
-Since the provincial water use decisions are exactly symmetric, total water use would increase when each province has higher incentives for current water use.
-This situation corresponds to a “sprint” effect, where the total water use dramatically increases in the “sprint” period.
-
-Extensions of the model are shown in \textit{Supplementary Material S3}.
-
-\section{CONCLUSION}\label{conclusion}
+\section{CONCLUSION}\label{sec:conclusion}
 \input{05_conclusion.tex}
 
+%%%%%%%% -----  02_appendix -------- %%%%%%%%%%
 \appendix
 \label{appendix}
-%%%%%%%% -----  02_appendix -------- %%%%%%%%%%
 
@@
 %% the \bibliography{} command.
-\bibliography{../WAInstitution_YRB_2021}
-
-%% Here is the endmatter stuff: Supplementary Info, etc.
-%% Use \item's to separate, default label is "Acknowledgements"
-
+\bibliography{../WAInstitution_YRB_2021}\label{bib}
 \end{document}

### 2022-04-17 docs/papers/00_cover_letter/abstract.tex
docs(refactor-paper-and-fixed-according-to-comments-from-ShuaiWang-and-XutongWu): refactor paper and fix language according to the comments from ShuaiWang and XutongWu
BREAKING CHANGE: v-1.3.0

@@
-Increasing competition for water is challenging management institutions of large river basins worldwide.
-Institutions that successfully support sustainable water resource use are structurally well-aligned with water provisioning and social-ecological demands.
-However, what constitutes a well-aligned institution in this context is poorly understood.
-We analyzed institutional shifts in water governance, exploiting two quasi-natural experiments of the Yellow River Basin.
-First, using a Differenced Synthetic Control method to control economic and environmental contexts, we found the Water Allocation Scheme (87-WAS), which intended to limit water use, unexpectedly resulting in a structural mismatch of the social-ecological system (SES) with increased water use.
-We then applied a mathematical model to suggest that incentive distortions contributed to the rapid water use under the typical mismatched SES structure.
-Our analysis highlights the need to evaluate institutional fit in coupled human and natural systems carefully.
+Increasing competition for water is leading to depletion of freshwater globally and calls for an urgent transformation of the governance system.
+To quantitatively analyse how institutions contributed to water governance, we focus on institutional shifts of the Yellow River Basin (YRB), one of the most anthropogenic interfered large river basins overburdened in water use, then drying up, but finally successfully restored.
+Our results suggest that two institutional shifts, the Water Allocation Scheme since 1987 (87-WAS) and the Unified Basinal Regulation since 1998 (98-UBR), framed different structures of social-ecological systems (SESs) in regional and basinal water use.
+During the decade after the 87-WAS, the observed water use of the YRB had an $8.57\%$ increase than an expectation.
+However, the 98-UBR significantly decreased total water use by $4.9$ billion $m^3/yr$.
+Specifically, the 87-WAS stimulated water use in provinces with more water uses (e.g., Inner Mongolia, Henan, and Shandong), but the 98-UBR regulated nearly all provinces.
+Linking our results to a mathematical marginal benefits model, we suggest that the outcomes with regional variations come from the effects of SES structural changes.
+These quasi-natural experiments of the YRB deepened insights on SESs structures and outcomes, thus providing a valuable guideline for SESs worldwide facing water depletion.

### 2022-04-17 docs/papers/01_manuscript/01_introduction.tex
docs(refactor-paper-and-fixed-according-to-comments-from-ShuaiWang-and-XutongWu): refactor paper and fix language according to the comments from ShuaiWang and XutongWu
BREAKING CHANGE: v-1.3.0

--- 2022-04-11 docs/papers/01_manuscript/01_introduction.tex
@@
 % 水竞争的重要性
-Widespread freshwater scarcity and overuse, resulting in systematic risks to economies, societies, and ecosystems globally, are critical environmental challenges to sustainability \cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
+Widespread freshwater scarcity and overuse challenge the sustainability of large river basins, resulting in systematic risks to economies, societies, and ecosystems globally \cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
 With steadily increasing demand, competition for water causes depletion of freshwater globally and calls for an urgent transformation of the governance system by considering water use conservation \cite{gleick2010, ziolkowska2016, wang2019d}.
@@
 Furthermore, human interferences such as soil conservation and water conservancy project boosted water withdrawal and then stressed the water scarcity of the Yellow River.
-To balance ecological and developing demands in such a human-dominated basin, therefore, is a problem for China in terms of water governance throughout and for large rivers worldwide.
+In the context of future climate change, the contradiction between supplies and demands of water resources in the YRB will become more prominent.
+%! Citation: Hao Wang presentation.
+Therefore, balancing ecological and developing demands in such a human-dominated basin is a problem for China in water governance throughout and for large rivers worldwide.
 
 % 第三段 过去管理的经验，断流的严重程度，连续多少没有断流，少有的解决断流的大河。治理成功的流域？分析背后的机制，基础。往用水上靠。
-In China, there were several ambitious water management practices in the last century, such as reservoir regulation, South-to-north Water Diversion Project (WDP), Water Allocation Scheme since 1987 (87-WAS), and the Unified Basinal Regulation since 1998 (98-UBR), to solve the water stress of the YRB.
+% 为了缓解用水压力
+Chinese authorities implemented several ambitious water management practices in the YRB in the last century to relieve the water stress, such as reservoir regulation, South-to-north Water Diversion Project (WDP), and Water Allocation Scheme since 1987 (87-WAS), and the Unified Basinal Regulation since 1998 (98-UBR).
 Through those efforts, ecological restoration of wetland and estuary delta in the YRB without drying up for over $20$ is widely considered a considerable river management achievement.
@@
 Such institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human, and natural system, including interplays between social actors, ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
-Understanding the complex interlinkages is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
+Understanding those complex interlinkages, therefore, is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
 However, while literature had well evaluated and quantified the effects of engineering solutions beforehand, there are few attempts to assess institutional contributions to successful water governance.
@@
 % 第四段 目标 制度变化。是不是制度变化产生的，如果是的话怎么影响。
-In addition to widespread recognition of the rising importance of institutions as an approach to water sustainable use within large river (especially transboundary river) basins, their specific effects are still in open discussion \cite{agrawal2003, persha2011, agrawal2001}.
+In addition to widespread recognition of the rising importance of institutions as an approach to water sustainable use within large river basins (especially transboundary rivers like the YRB), their specific effects are still in open discussion \cite{agrawal2003, persha2011, agrawal2001}.
 Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, therefore, supporting (but do not guarantee) sustainability of SES \cite{epstein2015, wang2019d}.
 Some institutional shifts have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and collaborative water governance systems in Europe \cite{green2013}).
-However, shifting institutions in a large, complex river basin may create or destroy hundreds of different connections, where matched human-water relationships are not ubiquitous.
-How and how important the institutional shifts played a role in the water governance achievement of the YRB, therefore, are still uncertain.
-Here, we quantitatively analyzed the impacts of two significant institutional shifts (the 87-WAS and the 98-UBR) on water uses of the YRB.
-By linking structures and outcomes within the coupled human and natural system, we further explored mechanisms of institutional effects in the YRB for a deeper understanding of institutions' role in water governance worldwide.
+However, shifting institutions in a large, complex river basin may create or destroy hundreds of different connections between social agents and ecological units, where matched social-ecological structures are not ubiquitous.
+Therefore, the role of institutional shifts in the water governance achievement of the YRB and their impacts on water use is still uncertain without an understanding of SES structures.
+% 通过抽象文件变化
+Here, by abstracting changes in official documents following institutional shifts (the 87-WAS and the 98-UBR), we depicted the SES structures of the YRB from 1975 to 2008.
+Then, we use Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without the institutional shifts (\textbf{Methods}; \textit{S2 in Supplementary Material}).
+By further interpreting the differences of the effects in the YRB, we explored the mechanisms linking SESs structure and outcomes for a deeper understanding of institutions' role in water governance worldwide.

### 2022-04-17 docs/papers/01_manuscript/02_structures.tex
docs(refactor-paper-and-fixed-according-to-comments-from-ShuaiWang-and-XutongWu): refactor paper and fix language according to the comments from ShuaiWang and XutongWu
BREAKING CHANGE: v-1.3.0

@@
 As a pioneer in water governance shifting in China, the YRB started to explore the initial water allocating scheme in the 1970s.
-The institutional shifts in 1987 (known as the ``87 Water Allocation Scheme, 87-WAS'') and 1998 (Unified Basinal Regulation, 98-UBR) were two widely recognized milestones of water governance.
-Until the 87-WAS, stakeholders have free access to the YR water resources, with geographic and temporal differences between freshwater demand and availability.
-As the mismatch between demands and supply kept increasing, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin.
-However, this controversial scheme helped slight turn water depletion around until a different strategy expanded the responsibilities of basinal authorities in integrated water management in 1998 (the 98-UBR).
-Ten years later, the YRB authorities require to further divide the provinces' quota into cities, counties, and districts.
-Therefore, our analysis period spans from 1975 to 2008, with the human-water system shifted between three different institutions, which were different from other large river basins in China.
+The institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones of water governance.
+Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
+As a compounded result of development, the provinces such as Shandong, Henan and Inner Mongolia used more water resources in the YRB with larger economies (primarily for irrigation agriculture).
+For shrinking water deficits, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin.
+However, the controversial scheme helped little in turning the water depletion around until another strategy attempted to strengthen the responsibilities of the YRCC in integrated water management in 1998 (the 98-UBR).
+Therefore, our analysis period spans from 1975 (emergence of river depletion) to 2008 (a further polish of the 98-UBR), with the SESs shifted between three varying institutions which were different from other large river basins in China.
 
 % 制度结构关系抽象
-Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{framework} A).
-For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{framework} B), leading to sustainable outcomes.
-Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{framework} C and D).
-Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures, and a network model is a widely used way to depict them by abstracting links and nodes.
-We thus selected institutional regulatory documents on water use issued by national ministries (for validation to both watershed and regional agents) and extracted the interactions between the agents involved (\textit{Supplementary Material S2}).
+% Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{framework} A).
+% For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{framework} B), leading to sustainable outcomes.
+% Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{framework} C and D).
+% Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures, and a network model is a widely used way to depict them by abstracting links and nodes.
 
+We selected institutional regulatory documents on water use issued by national ministries (for validation to both watershed and regional agents) and extracted the interactions between the agents involved (\textit{Supplementary Material S2}).
 Before 1987, the YRCC had no links to the provinces regarding water use, and the provinces could link to the Yellow River reaches directly (Figure~\ref{structure}).
@@
 Furthermore, information from the 98-UBR documents demonstrated that the provinces had to apply their plan for an annual water use licence instead of direct access to the Yellow River water.
-Thus, there were links between the YRCC and the provinces.
-Although we abstract the two major institutional shifts from document interpretations, many studies used these two changes as baselines for the YRB's water governance history and widely recognized their importance.
+Thus, there have been links between the YRCC and the provinces since the strengthening responsibilities of the YRCC in 1998.
 
-\begin{figure*}[!ht]
-    \centering
+\begin{figure*}[!h]
     \includegraphics[width=32pc]{diagrams/diagram.pdf}
@@
 		% 没有任何政策限制，各利益相关者此时期可以从单向但联通的河流生态单元内自由取水
-		\textbf{1975–1987:} Without any constraints, water resources were freely accessible to each stakeholder (the provinces in this case, denoted by red circles) from a one-way but connected ecological unit (the Yellow River, denoted by the blue rectangle).
+%		\textbf{1975–1987:} Without any constraints, water resources were freely accessible to each stakeholder (the provinces, in this case, denoted by red circles) from a one-way but connected ecological unit (the Yellow River, denoted by the blue rectangle).
 		% 在政策1之后，每个使用者都被分配了能够开采河流地表水资源的配额，而黄委会的工作是对配额的使用进行统计与汇报。
-		\textbf{1987–1998:} After the implementation of policy 1 in 1987, each user was assigned a quota to withdraw surface water resources, and the YRCC (yellow triangle) was tasked with reporting on water quota use.
+%		\textbf{1987–1998:} After the implementation of policy 1 in 1987, each user was assigned a quota to withdraw surface water resources, and the YRCC (yellow triangle) was tasked with reporting on water quota use.
 		% 第二个政策之后，利益相关者取水需要向黄委会申请，黄委会则根据用水配额来批发许可。因此此时黄委会与利益相关者之间产生了直接的双向联系，监督他们对资源配额的取用。
-		\textbf{1998–2008:} After the implementation of policy 2, stakeholders had to apply for water resources from the YRCC, which then licensed water use according to the quota.
+%		\textbf{1998–2008:} After the implementation of policy 2, stakeholders had to apply for water resources from the YRCC, which then licensed water use according to the quota.
 Under this institution, the YRCC had direct two-way connections between provinces and ecological components.

### 2022-04-17 docs/papers/01_manuscript/03_results.tex
docs(refactor-paper-and-fixed-according-to-comments-from-ShuaiWang-and-XutongWu): refactor paper and fix language according to the comments from ShuaiWang and XutongWu
BREAKING CHANGE: v-1.3.0

@@
 
-% \subsection{ISS IMPACT ON WATER USE OF THE YRB}
-\subsection{ISs impact on water use of the YRB}
+%\subsection{INSTITUTIONAL SHIFTS IMPACT ON WATER USE OF THE YRB}
+\subsection{Institutional shifts impact on water use of the YRB}
 \label{result-2}
@@
 \label{result-1-p2}
-Here, we use Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without basinal policy interferences (\textbf{Methods}; \textit{S2 in Supplementary Material}).
-Our results suggest that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without the interference (Figure~\ref{main_results}A).
-From 1988 to 1998, while the estimation of water use only suggests $956.38 km^3$, the observed water use of the YRB provinces reached $1038.36 km^3$ in sum, $8.57\%$ increased.
+Our estimation of theoretical water use suggests that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without an institutional shift (Figure~\ref{main_results}A).
+From 1988 to 1998 on average, while the estimation of annual water use only suggests $956.38$ billion $m^3$, the observed water use of the YRB provinces reached $1038.36$ billion $m^3$ in sum, $8.57\%$ increased.
 However, after the institution shifted again in 1998 (98-UBR), the trend of increasing water use appeared to be effectively suppressed.
-From 1998 to 2008, the total observed water use decreased by $0.49 km^3$ per year, while the estimation of water use still suggests $1.03 km^3$ increases (Figure~\ref{main_results} B).
+From 1998 to 2008, the total observed water use decreased by $4.9$ billion $m^3/yr$ per year, while the estimation of water use still suggests $10.3$ billion $m^3/yr$ increases (Figure~\ref{main_results} B).
 The increased water uses after 87-WAS aligns with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{main_results}C).
-On the other hand, the environmental crisis of river drying up was effectively resolved after the 98-UBR, though the density of droughts still increased for decades (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{main_results}C).
-In line with previous literature had reported; therefore, the institution shift of 98-UBR contributed a lot to the successful water governance. %! citation
+On the other hand, the 98-UBR ended river depletion, despite the density of droughts still increasing for decades (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{main_results}C).
 
@@
 
-% \subsection{REGIONAL DIFFERENCES IN RESPONSES TO THE IS}
-\subsection{Regional differences in responses to the ISs}
+%\subsection{REGIONAL DIFFERENCES IN RESPONSES TO INSTITUTIONAL SHIFTS}
+\subsection{Regional differences in responses to institutional shifts}
 \label{result-3}
 % 结果2部分：展示区域相应差异
-
-Differences between stakeholders in responses to institutional shifts are vital to understanding the mechanism between structures and outcomes.
-Our results show that the proportion of accelerated water use in each province after the decade of 87-WAS (the proportion of actual water use exceeding the predicted water use by the model) has a significant correlation ($p<0.05$, see \textbf{Methods}) to the Yellow River water use in each province (Figure~\ref{upset}A).
-Furthermore, while no evident impacts for most provinces (no more than $10\%$ differences, the apparent acceleration effects were only prominent in the big water-using provinces (e.g., Neimeng, Henan, and Shandong.
+Our results also suggest huge differences between patterns of provinces in their responses to the two institutional shifts.
+During the decade after the 87-WAS, the proportion of accelerated water use for each province (the proportion of actual water use exceeding the predicted water use by the model) has a significant correlation ($p<0.05$) to the Yellow River water use (Figure~\ref{upset}A).
+While non-obvious impacts (less than $10\%$ in proportion) for most provinces, the apparent acceleration was prominent for the central water-using provinces (e.g., Inner Mongolia, Henan, and Shandong.
 Figure~\ref{upset}B).
-In particular, Neimeng and Shandong, both provinces that exceeded the prescribed water uses of the 87-WAS, used $44.25\%$ and $25.69\%$ more water uses than the prediction from 1987 to 1998, respectively.
-Furthermore, the satisfaction of each province with the water allocation stipulated by the 87-WAS (expressed by the difference between the actual water allocation of each province and the expected planning value) has little significant correlation to the acceleration.
-By contrast, after the 98-UBR, except Shaanxi (which has always been abundant in water quota) had an evident ($17.53\%$) increase in water use, almost all provinces have seen significant declines in water use ($-12.5\%$ on average).
-However, neither the satisfaction nor Yellow River water use correlates with the declines after the 98-UBR.
+In particular, Inner Mongolia and Shandong, both provinces that exceeded the prescribed water uses of the 87-WAS, used $44.25\%$ and $25.69\%$ more water uses than the prediction from 1987 to 1998, respectively.
+In addition, the deficits of the water quota for each province (expressed by the difference between the water quota in 87-WAS and an expectation in water demands from a beforehand plan) have no significant ($p>0.05$) correlation to the acceleration.
+By contrast, after the 98-UBR, except Shanxi (whose water quota has always been abundant since the 87-WAS) had an evident ($17.53\%$) increase in water use, almost all provinces have seen evident declines in water use ($-12.5\%$ on average).
+Furthermore, neither the Yellow River water use nor the deficits correlate with the decreased proportions.
 
@@
     \centering
-    \includegraphics[width=32pc]{outputs/upset_87.pdf}
-    \caption{
-        \textbf{A.} The partial correlation coefficient between wate uses (WU) of Yellow River (YR), unsatisfied ratio (compared with requirements in water plan and supply in the 87-WAS), and the average accelerated ratio.
+    \includegraphics[width=32pc]{outputs/combined_upset.pdf}
+    \caption{Responses of the provinces to the institutional shifts (upper: the 87-WAS, lower: the 98-UBR).
+        \textbf{A.} The partial correlation coefficient between water use (WU) of Yellow River (YR), unsatisfied ratio (compared with requirements in water plan and supply in the 87-WAS), and the average accelerated ratio.
         \textbf{B.} Average accelerated ratio of water uses for each province in the YRB during the decade after 87-WAS (from 1987 to 1998).

### 2022-04-17 docs/papers/01_manuscript/04_discussion.tex
docs(refactor-paper-and-fixed-according-to-comments-from-ShuaiWang-and-XutongWu): refactor paper and fix language according to the comments from ShuaiWang and XutongWu
BREAKING CHANGE: v-1.3.0

@@
 % discussion-1: 主要介绍结果的意义、合理性
-
-Besides environmental background, our forecast by DSC takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textit{S2 in Supplementary Material}).
-It means the forecast of water use includes the part caused by the increased economic volume, while the outcomes of the economy (GDP in different sectors) of the YRB maintained a parallel trend with other regions during the period (\textit{S3 in Supplementary Material} Figure~\ref{S3-1}).
-Therefore, 87-WAS did not ``have little effect'' as previous analyses suggested (cites) but led to increased water use because the difference between prediction and observation will be trivial when the shift was just a blank policy by applying the DSC method.
+In addition to quantitatively demonstrating the regulatory effect of 98-UBR by previous studies, our study also found that 87-WAS would increase overall water use of the YRB.
+The results challenged the previous analyses suggesting that the 87-WAS ``has little effect'' because the difference between prediction and observation will be trivial when the institutional shift was just a blank policy by applying the DSC method.
 %!
-Citation
-Water-use intensity is another crucial factor in interpreting the differences besides the economic factors (e.g., irrigated areas and industrial outcomes) considered and controlled by the method.
-In addition to the expansion of irrigation area after the 87-WAS, water uses per unit of irrigation area also rapidly widened the gap with the average level of the rest provinces.
-However, the industry water use intensity hardly changed (\textit{S3 in Supplementary Material} Figure~\ref{S3-2}).
-As a previous report sigh: although the key to alleviating the drought is saving water in the irrigated areas, the tragedy of scrambling for water appeared in provinces and irrigated areas %!
+(cites)
+Fixing the environmental background, the forecast by DSC takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textit{S2 in Supplementary Material}).
+As the accumulations of economy volume (GDP in different sectors) in the YRB maintained a parallel trend with other regions throughout (\textit{S3 in Supplementary Material} Figure~\ref{S3-1}), differences after the institutional shifts suggest water use changing per unit of production, especially in agriculture (\textit{S3 in Supplementary Material} Figure~\ref{S3-2}).
+This fact is in line with the sigh from then: although the key to alleviating the drought is saving water in the irrigated areas, the tragedy of frequently scrambling for water appeared in some provinces %!
 \cite{mao2000}.
-In terms of the average ratio of water-saving irrigation area (refer to drip or sprinkler irrigation systems and canal lining), although there was a significant increase in the whole country after 1987, the YRB did not rapidly open a noticeable gap until about 1994 (Figure~\ref{S3-3}).
-As a result, despite the irrigation area expanding, scrambling for water resources without any incentive to optimize production per unit of water resources accelerated holistic water use.
-This accelerated water use was contrary to the original intention of the 87-WAS in conserving the limited water, and the failure was a barrier to the sustainability %! \cite{huangang2002}.
+Since the 98-UBR improved tragedy of water competition greatly, many studies attributed the restoration from river depletion mainly to the successful institutional shift.
 
 % 过去的研究总结出87-WAS收效甚微的几个因素：
-Previous studies have summarised factors that contribute to the non-ideal effect of 87-WAS: (1) The YRCC had no right to punish the provinces for over-exploitation; (2) the water quotas were annual values, causing provinces to rob water in the dry season; (3) The YRCC can make statistics on water use in the mainstream but cannot on the tributaries, so provinces water use underreport %!
-\cite{huangang2002}.
-However, the effects of the two institutional shifts (the 87-WAS and the 98-UBR) were significantly different, which the above reasons cannot fully explain.
-Between the 98-UBR and the further refinement of the unified regulation in 2008, there was still a lack of a temporary water allocation scheme and effective monitoring of tributaries.
-Moreover, without any actual punishment, provinces with high water consumption (such as Inner Mongolia and Shandong) continued to exceed the quota after 98-UBR.
-As we have analyzed (Figure~\ref{structure}), the difference between the two institutional shifts is mainly reflected in the structure of linkages between social actors.
-Until the institutional shift of 98-UBR, with no necessity to apply for a water permit from YRCC, there were no horizontal connections (cooperations or agreements) between the various stakeholders (provinces) directly connected to the ecological units.
-Make it clear that the YRCC was responsible for regulating provincial water use; that is, each province has made it clear that in the long run, water resources are not ``internal'' but ``dependent'' on YRCC.
-In that way, the YRCC, whose authority scale matches the whole river basin, also took the primary responsibilities to the river, and literature recognized the structure as a social-ecological fit that usually led to good outcomes.
-Empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
+Although previous studies summarised reasons for the non-ideal effect of 87-WAS, few improvements in the 98-UBR indicate that they underestimated influences from the structural changes (\textit{S3 in Supplementary Material} Figure~\ref{fig:ref{S3-3}}).
+As we have depicted (Figure~\ref{structure}), the institutional shifts twice framed the structure of SESs in the YRB and led to different building blocks, which were also reported in various types of SESs worldwide.
+The empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
 \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
+On the contrary, the YRCC, whose authority matched the YRB in scale after the 98-UBR, led to a well-recognized structure for institutional alignments to social-ecological fit and good outcomes.
 The effect of the institutional shifts once again demonstrated that it is not easy to have a win-win situation of environment and interests in complex coupled human-nature systems \cite{hegwood2022} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.
@@
 % 经济模型与理论解释
+% Differences between stakeholders in responses to institutional shifts are vital to understanding the mechanism between structures and outcomes.
 Differences in the pattern of the response by provinces can demonstrate the influence of social-ecological structures led by the institutional shifts.
@@
 Before the 98-UBR, the model assumes that the separated ecological units (river reaches) link to stakeholders (related provinces) who use water to pursue their marginal benefits but have a potential political cost if they exceed the quota 87-WAS.
-Our model suggests that for users who are already economically efficient (who are already using more water), greater marginal returns from water induce the acceleration of extracting resources for future economic growth (Figure~\ref{economic_model}).
+Our model suggests that for users who are already economically efficient (who are already using more water), greater marginal returns from water induce the acceleration of extracting resources for future economic growth (\textit{Supplementary Material S4}).
 Therefore, isolated stakeholders reacted to the similar marginal cost, and smaller water users have a threshold because of the political cost, so 87-WAS triggered an increased water use for the significant users.
@@
 
-% \subsection{LIMITATION, INSIGHTS AND IMPLICATIONS}
-\subsection{Limitation, insights and implications}
+\subsection{LIMITATION, INSIGHTS AND IMPLICATIONS}
+% \subsection{Limitation, insights and implications}
 \label{discussion-3}
@@
 
-Agents matching the ecological scale appear widespread as motifs in SES of successful governance, whether in fisheries, forests, or groundwater management, suggesting that reducing independent stakeholders linked to fragmentation is an essential primary mechanism for a structure to produce good results.
-% 由于87-WAS和98-UBR分别带来的两种结构在很多的SES中都是反复出现的构件，我们提出的机制对理解这类耦合系统至关重要
-Since the structures introduced by 87-WAS and 98-UBR are recurring motifs in many SES, our proposed mechanism is crucial to understanding such coupled systems.
-% 因此，我们通过黄河流域的准自然实验，探讨了社会经济结构与可持续发展(结果)之间的因果关系，为两个主要原因提供了一个有益的案例研究。
-Furthermore, we explored the causal linkages between the SES structures and sustainability (outcomes) in quasi-natural experiments of the YRB, which provides an informative case study for two main reasons.
-% 首先，长江流域管理的急剧结构变化使我们能够定量估计高层制度设计变化对用水的净影响。
-First, the sharp structural shifts in YRB management enabled us to quantitatively estimate the net effects of changes in high-level institutional design on water use.
-Institutions that determine water allocation include bottom-up agreements or social norms as well as top-down quotas or regulations, with different effects on SES structure \cite{wang2019d,speed2013}; top-down regulations can trigger immediate institutional shifts and sharp SES structural changes \cite{speed2013,roland2004}.
-In comparison with investigations of more gradual changes induced by bottom-up institutional shifts, exploring the impacts of a top-down change substantially diminishes potential problems of omitted variables in the quantitative analysis of SES and clarifies the causal link between SES structure and outcome.
-% 其次，通过比较长江流域两次制度变迁所分裂的三种不同制度结构的净效应，我们也可以更深入地理解“盆地固定效应”下结构格局的影响。尽管流域内的社会经济单位从世界各地的大型河流流域和许多地区的水资源中受益，但很少有流域多次经历过如此激进的社会经济结构变化。
-Second, we can better understand the influence of structural alignments under a fixed basin by comparing the net effects of three different institutional structures split by two institutional shifts in the YRB.
-Although socioeconomic units within a basin benefit from water resources in large river basins all over the world, and many locations have shown increased levels of regulation, few basins have experienced such radical SES structural changes several times (see \textit{Supplementary Material} S1).
-Thus, the YRB provides a valuable setting for understanding the direct impacts of changes in the SES institutional structure.
-Finally, one of the limitations of our method is that it is difficult to rule out the effects of other policies over the same time breakpoints.
-However, since scholars have reached a consensus on the importance of the two institutional shifts of 87-WAS and 98-UBR, the differences in their results still provide important insights for understanding water governance.
+Matching social and ecological scales appears widespread as building blocks (or motifs) in successfully governed SES, whether in fisheries, forests, or groundwater management.
+Since the building blocks introduced by 87-WAS and 98-UBR are recurring motifs in many SES, our proposed mechanism is crucial to understanding such coupled systems.
+We explored these causal linkages between the SES structures and sustainability (outcomes) by quasi-natural experiments (the institutional shifts) of the YRB, which provides an informative case study for two main reasons.
+First, different from gradual changes following bottom-up emergence, the top-down institutional shifts induced sharp changes in SES structures in the YRB, enabling us to estimate their net effects quantitatively.
+Second, as few basins experienced such radical institutional shifts more than once, the YRB provides comparable settings for understanding the impacts of structural changes in SESs.
+However, one of the inevitable limitations of our method is that it is difficult to rule out the effects of other policies over the same time breakpoints.
+Since scholars have reached a consensus on the importance of the two institutional shifts of 87-WAS and 98-UBR, the differences in their results still provide important insights for understanding water governance.
 
 % 我们的模型结果与机制探讨加深了SES结构的理解，强化了孤立利益相关者形成的结构不利于制度解决环境问题的基本认识
-Our results and discussion deepen the understanding of SES structure and strengthen the basic understanding that the mismatched structure formed by isolated stakeholders is not conducive to institutional solutions; -and then reported how another social-ecological fit structure contributed to successful water governance and sustainability.
-Moreover, the subsequent success of 98-UBR has proved the importance of institutional scale matching both theoretically and practically.
-Therefore, it is necessary to emphasize the establishment of potentially connected building blocks between stakeholders by agents consistent with the scale of the ecological system (in this case, the basinal scale and the YRCC).
-Furthermore, we applied several scenarios based on the marginal benefit model (see \textit{Supplementary Material S4}) for some further insights into sustainable water governance.
+Our results and discussion deepen the understanding of SES structure and strengthen the basic understanding that the mismatched structure (isolated stakeholders with the fragmentation of ecology) is not conducive to institutional solutions.
+Moreover, we report how another institutional shift contributed to successful water governance  -the subsequent success of 98-UBR has proved the importance of social-ecological fit again, theoretically and practically.
+For sustainability in the future, therefore, it is necessary to emphasize the necessity of strengthening connections between stakeholders by agents consistent with the scale of the ecological system (in this case, the basinal scale and the YRCC).
+From these starting points, several other scenarios given by a marginal benefit model (see \textit{Supplementary Material S4}) can provide plausible insights into water governance.
 For example, water rights transfers can be another way to emerge horizontal links between stakeholders that also have the potential in resulting in better water governance.
-In addition, the policymakers can also propose a more dynamic and flexible institution by increasing the frequency of quota updates that responds to changing conditions and will adapt more effectively to its SES context.
+In addition, the policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to respond to changing SES context.
 
 % 未来的政策建议
-Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of dynamic quota setting (see \textit{Supplementary Material S1}) \cite{yu2019}.
-Following the institutional reforms of 1998, the Yellow River has not dried up since 1999.
-However, given recent changes in the YRB, its rigid resource allocation scheme can no longer meet the new demands of economic development \cite{wang2019a}.
-As a result, the Chinese government has embarked on an ambitious plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}).
-These initiatives can benefit from our analysis by actively considering and incorporating social-ecological complexity and incentive structures when developing new approaches that avoid unsustainable outcomes.
-Our research provides a cautionary tale of how institutions can be a double-edged sword in attaining sustainability.
-Therefore, insights from the YRB can be a valuable guideline for SESs around the world facing similar governance problems \cite{cumming2020b, muneepeerakul2017, cumming2020a, leslie2015}.
+Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions to sustainability (see \textit{Supplementary Material S1}) \cite{yu2019}.
+Given recent changes in the YRB, outdated and inflexible water quota can no longer meet the new demands of economic development \cite{wang2019a}.
+As a result, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}).
+These initiatives can benefit from our analysis by actively incorporating social-ecological matched building blocks when developing a new institutional shift toward sustainability.
+Moreover, our research provides a cautionary tale of how institutions can be double-edged, while insights from the YRB can be a valuable guideline for SESs worldwide \cite{cumming2020b, muneepeerakul2017, cumming2020a, leslie2015}.

### 2022-04-17 docs/papers/01_manuscript/05_conclusion.tex
docs(refactor-paper-and-fixed-according-to-comments-from-ShuaiWang-and-XutongWu): refactor paper and fix language according to the comments from ShuaiWang and XutongWu
BREAKING CHANGE: v-1.3.0

@@
 
-Intense water use in one of the most anthropogenic interfered large river basins, the Yellow River Basin (YRB), once led to overburdened drying up but finally had a successful restoration by sequential water governance institutions.
-Focusing on two water-demand institutions, the Water Allocation Scheme since 1987 (87-WAS) and the Unified Basinal Regulation since 1998 (98-UBR), we quantitatively analyzed how and how important the institutional shifts played a role in the water governance achievement of the YRB.
-
-First, by abstracting institutions into building blocks of a social-ecological system (SES), we explored the linkages within the YRB before and after two institutional shifts.
-Then, we applied Differenced Synthetic Control method to quantify their impacts on water use of the YRB.
-The observed water use of the YRB provinces had an $8.57\%$ increase than our estimation in the decade after the 87-WAS but significantly decreased by $0.49 km^3$ per year after the 98-UBR (the model still suggests a $1.03 km^3$ annual increases).
-Finally, by analyzing the differences in stakeholders' responses to the institutional shifts, we found that 87-WAS stimulated water use in provinces with more water uses (e.g., Neimeng, Henan, and Shandong) 98-UBR regulated nearly all provinces.
-
-Since the above results closely align with our mathematical marginal benefits model, we can link the structures (widespread building blocks) and outcomes (goals of the institution, i.e., limiting water demands) by the quasi-natural experiments of the YRB.
-We demonstrate again that social-ecological fits lead to successful governance, whether in fisheries, forests, or groundwater management; reducing independent stakeholders linked to fragmentation is an essential primary mechanism for a structure to produce good results.
-Therefore, insights from the YRB can be a valuable guideline for SESs worldwide facing similar water governance problems.
+Intense water use in one of the most anthropogenic interfered large river basins, the Yellow River Basin (YRB), once led to overburdened drying up but finally had a successful restoration by sequential water governance practices.
+Focusing on two water-demand institutions, 87-WAS and the 98-UBR, we quantitatively analyzed how institutional shifts played a role in the water governance achievement of the YRB.
+Shifting throughout different SES structures framed by them, the observed water use of the YRB provinces had an $8.57\%$ increase than expected during the decade after the 87-WAS.
+Then, water use significantly decreased by  $4.9 billion m^3$ per year since the 98-UBR, while the model still suggests a $10.3 billion m^3$ annual increase in expectation.
+Finally, as differences in stakeholders' response to the institutional shifts, water use rises after the 87-WAS in provinces with more water uses (e.g., Inner Mongolia, Henan, and Shandong) while shrunk in nearly all provinces after the 98-UBR.
+Since the above results closely align with interpretations from a mathematical marginal benefits model, we can link the structures (widespread building blocks) and outcomes (goals of the institution, i.e., limiting water demands) by these quasi-natural experiments of the YRB.
+We demonstrate that social-ecological fits lead to successful governance where reducing independent stakeholders linked to fragmentation is an essential primary mechanism for good SES outcomes.

### 2022-04-17 config.py

@@ -23,8 +23,8 @@ SCHEME_87 = {
     "Gansu": 3.04,
     "Ningxia": 4.00,
     "Neimeng": 5.86,
-    "Shanxi": 3.80,
-    "Shaanxi": 4.31,
+    "Shanxi": 4.31,
+    "Shaanxi": 3.80,
     "Henan": 5.54,
     "Shandong": 7,
     # 'Jinji': 2
@@ -36,8 +36,8 @@ PROVINCES_CHN2ENG = {
     "甘肃": "Gansu",
     "宁夏": "Ningxia",
     "内蒙古": "Neimeng",
-    "陕西": "Shanxi",
-    "山西": "Shaanxi",
+    "陕西": "Shaanxi",
+    "山西": "Shanxi",
     "河南": "Henan",
     "山东": "Shandong",
     "河北": "Hebei",

### 2022-04-17 func/handle.py

@@ -467,7 +467,12 @@ class ExpResultsHandler(Experiment):
         return {"k_obs": k_obs, "k_syn": k_syn}
 
     def plot_upset(
-        self, items, threshold=0.05, figszie=(8, 4), height_ratio=(3, 1.5)
+        self,
+        items,
+        threshold=0.05,
+        figszie=(8, 4),
+        height_ratio=(3, 1.5),
+        sort=True,
     ):
         fig = plt.figure(figsize=figszie, constrained_layout=False)
         plt.subplots_adjust(
@@ -517,9 +522,9 @@ class ExpResultsHandler(Experiment):
         ax3.set_title("Correlation", size=10)
         ax2.set_xlabel("Provinces in the YRB")
 
-        ratio = self.dfs["statistic"]["diff_ratio"].sort_values(
-            ascending=False
-        )
+        ratio = self.dfs["statistic"]["diff_ratio"]
+        if sort:
+            ratio = ratio.sort_values(ascending=False)
 
         ax1.bar(
             range(len(ratio)),
@@ -594,6 +599,7 @@ class ExpResultsHandler(Experiment):
             ticks=np.arange(0, 1.1, 0.5), labels=["1.0", "0.5", "0.0"]
         )
         pass
+        return ax1, ax2, ax3
 
 
 if __name__ == "__main__":

### 2022-04-26 docs/papers/01_manuscript/04_discussion.tex
fix(contextplot.ipynb,-discussion.py,-config.py): re-plot, grammarly fix, use bidict,

@@
 From these starting points, several other scenarios given by a marginal benefit model (see \textit{Supplementary Material S4}) can provide plausible insights into water governance.
-For example, water rights transfers can be another way to emerge horizontal links between stakeholders that also have the potential in resulting in better water governance.
+For example, water rights transfers can be another way to emerge horizontal links between stakeholders that also have the potential to result in better water governance.
 In addition, the policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to respond to changing SES context.

### 2022-04-26 config.py

@@ -10,6 +10,9 @@ import logging
 import os
 import sys
 
+# https://towardsdatascience.com/python-bi-dictionary-key-can-be-value-and-value-can-be-key-50715a2046af
+from bidict import bidict
+
 from func.experiment import Experiment
 from func.handle import ExpResultsHandler
 from func.model import do_synth_analysis, do_synth_model
@@ -78,6 +81,7 @@ NATURAL = {
     "pres": "Near surface air pressure",
     "shum": "Near surface air specific humidity",
 }
+NATURAL = bidict(NATURAL)
 
 # BASIC logging settings.
 LOG_FORMAT = "%(asctime)s %(levelname)s %(filename)s %(message)s "

### 2022-05-01 docs/papers/01_manuscript/01_introduction.tex
feat(new-plot-fig-3): re-draw fig 3
BREAKING CHANGE:

@@
 %! Citation: Hao Wang presentation.
-Therefore, balancing ecological and developing demands in such a human-dominated basin is a problem for China in water governance throughout and for large rivers worldwide.
+Therefore, balancing ecological and developing demands in such a human-dominated basin is a problem for China in terms of water governance throughout and for large rivers worldwide.
 
@@
 Through those efforts, ecological restoration of wetland and estuary delta in the YRB without drying up for over $20$ is widely considered a considerable river management achievement.
-Different from the engineering of WDP provides further water supply or reservoir matches water supply and demands, institutional strategies like the 87-WAS (assign water quotas for provinces in the YRB) and the 98-UBR (the provinces had to be allowed for using water by the Yellow River Conservancy Commission, YRCC) mainly focused on limiting demands of water use.
-Such institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human, and natural system, including interplays between social actors, ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
+Different from the engineering of WDP provides further water supply or reservoir matches water supply and demands, institutional strategies like the 87-WAS (assign water quotas for provinces in the YRB) and the 98-UBR (the provinces had to be allowed to use water by the Yellow River Conservancy Commission, YRCC) mainly focused on limiting demands of water use.
+Such institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human and natural system, including interplays between social actors, ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
 Understanding those complex interlinkages, therefore, is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.

### 2022-05-01 docs/papers/01_manuscript/04_discussion.tex
feat(new-plot-fig-3): re-draw fig 3
BREAKING CHANGE:

@@
 % 过去的研究总结出87-WAS收效甚微的几个因素：
-Although previous studies summarised reasons for the non-ideal effect of 87-WAS, few improvements in the 98-UBR indicate that they underestimated influences from the structural changes (\textit{S3 in Supplementary Material} Figure~\ref{fig:ref{S3-3}}).
+Although previous studies summarised reasons for the non-ideal effect of 87-WAS, few improvements in the 98-UBR indicate that they underestimated influences from the structural changes (\textit{S3 in Supplementary Material} Figure~\ref{fig:{S3-3}).
 As we have depicted (Figure~\ref{structure}), the institutional shifts twice framed the structure of SESs in the YRB and led to different building blocks, which were also reported in various types of SESs worldwide.

### 2022-05-01 docs/papers/01_manuscript/04_discussion.tex
fix(fix-bad-unicode-in-bodin2017b-and-compile.): compiling by vscode

@@
 % 过去的研究总结出87-WAS收效甚微的几个因素：
-Although previous studies summarised reasons for the non-ideal effect of 87-WAS, few improvements in the 98-UBR indicate that they underestimated influences from the structural changes (\textit{S3 in Supplementary Material} Figure~\ref{fig:{S3-3}).
+Although previous studies summarised reasons for the non-ideal effect of 87-WAS, few improvements in the 98-UBR indicate that they underestimated influences from the structural changes (\textit{S3 in Supplementary Material} Figure~\ref{fig:S3-3}).
 As we have depicted (Figure~\ref{structure}), the institutional shifts twice framed the structure of SESs in the YRB and led to different building blocks, which were also reported in various types of SESs worldwide.

### 2022-05-04 docs/papers/01_manuscript/03_results.tex
feat(new-plot-fig-3): re-draw fig 3
BREAKING CHANGE:
fix(fix-bad-unicode-in-bodin2017b-and-compile.): compiling by vscode
feat(results,-fig3,-compile-manuscript): add figure 3 in the main text
BREAKING CHANGE:

@@
 %\subsection{INSTITUTIONAL SHIFTS IMPACT ON WATER USE OF THE YRB}
-\subsection{Institutional shifts impact on water use of the YRB}
+\subsection{Institutional shifts impact on water use}
 \label{result-2}
@@
 Our estimation of theoretical water use suggests that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without an institutional shift (Figure~\ref{main_results}A).
-From 1988 to 1998 on average, while the estimation of annual water use only suggests $956.38$ billion $m^3$, the observed water use of the YRB provinces reached $1038.36$ billion $m^3$ in sum, $8.57\%$ increased.
+From 1988 to 1998, on average, while the estimation of annual water use only suggests $956.38$ billion $m^3$, the observed water use of the YRB provinces reached $1038.36$ billion $m^3$ in sum, $8.57\%$ increased.
 However, after the institution shifted again in 1998 (98-UBR), the trend of increasing water use appeared to be effectively suppressed.
@@
 %\subsection{REGIONAL DIFFERENCES IN RESPONSES TO INSTITUTIONAL SHIFTS}
-\subsection{Regional differences in responses to institutional shifts}
+\subsection{Institutional effects on regulating differences}
 \label{result-3}
 % 结果2部分：展示区域相应差异
-Our results also suggest huge differences between patterns of provinces in their responses to the two institutional shifts.
-During the decade after the 87-WAS, the proportion of accelerated water use for each province (the proportion of actual water use exceeding the predicted water use by the model) has a significant correlation ($p<0.05$) to the Yellow River water use (Figure~\ref{upset}A).
-While non-obvious impacts (less than $10\%$ in proportion) for most provinces, the apparent acceleration was prominent for the central water-using provinces (e.g., Inner Mongolia, Henan, and Shandong.
-Figure~\ref{upset}B).
+Our results also suggest differences between patterns of provinces in their responses to the two institutional regulating.
+During the decade after the 87-WAS, the major water-using provinces (e.g., Inner Mongolia, Henan, Shandong) had apparent accelerations (Figure~\ref{regulating}).
+The proportion of increased (or decreased) water use for each province (over the estimated water use by the model) has a significant correlation (partial correlation coefficient is $0.84$, $p<0.05$) to the actual water use from the Yellow River.
 In particular, Inner Mongolia and Shandong, both provinces that exceeded the prescribed water uses of the 87-WAS, used $44.25\%$ and $25.69\%$ more water uses than the prediction from 1987 to 1998, respectively.
-In addition, the deficits of the water quota for each province (expressed by the difference between the water quota in 87-WAS and an expectation in water demands from a beforehand plan) have no significant ($p>0.05$) correlation to the acceleration.
-By contrast, after the 98-UBR, except Shanxi (whose water quota has always been abundant since the 87-WAS) had an evident ($17.53\%$) increase in water use, almost all provinces have seen evident declines in water use ($-12.5\%$ on average).
-Furthermore, neither the Yellow River water use nor the deficits correlate with the decreased proportions.
+By contrast, after the 98-UBR, except Shanxi (whose water quota has always been far abundant over its actual water use since the 87-WAS) had an evident ($17.53\%$) increase in water use, almost all provinces have seen evident declines in water use ($-12.5\%$ on average).
+Furthermore, the regulated water use of provinces was not correlated ($-0.03$) with their water use from the Yellow River in proportions.
 
@@
     \centering
-    \includegraphics[width=32pc]{outputs/combined_upset.pdf}
-    \caption{Responses of the provinces to the institutional shifts (upper: the 87-WAS, lower: the 98-UBR).
-        \textbf{A.} The partial correlation coefficient between water use (WU) of Yellow River (YR), unsatisfied ratio (compared with requirements in water plan and supply in the 87-WAS), and the average accelerated ratio.
-        \textbf{B.} Average accelerated ratio of water uses for each province in the YRB during the decade after 87-WAS (from 1987 to 1998).
-        \textbf{Mian users:} Major water consumption provinces (over the median).
-        \textbf{Overused:} violate the 87-WAS in average water uses.
+    \includegraphics[width=32pc]{outputs/fig3.pdf}
+    \caption{
+        Regulating differences for provinces in the YRB.
+        Red and green bars denote actual water use over the estimation from the model in a decade after the institutional shift -the 87-WAS and the 98-UBR, respectively.
+        The grey bars indicate the proportions of actual water use for each province to total water use of the provinces in a decade after the institutional shift.
+        The triangles mark the water quotas assigned in the institution, scaled into ratios by the same total actual water use, too.
     }
-    \label{upset}
+    \label{regulating}
 \end{figure*}

### 2022-05-04 docs/papers/01_manuscript/01_introduction.tex
feat(results,-structures): new figure 1

@@
 The Yellow River Basin (YRB), the fifth large river worldwide, is known for its irreplaceable role in the social-economic development of China, and thus also drastically interference by anthropogenic stress.
-Supporting $35.63\%$ irrigation and $30\%$ population with only $2.66\%$ water resources of China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: 28 February 2021), the overburdened Yellow River dried up in consecutive years, resulting in substantial ecological, economic and social crisis (e.g., wetland shrink, agriculture reduction, and scramble for water).
+Supporting $35.63\%$ irrigation and $30\%$ population with only $2.66\%$ water resources of China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today), the overburdened Yellow River dried up in consecutive years, resulting in substantial ecological, economic and social crisis (e.g., wetland shrink, agriculture reduction, and scramble for water).
 Intense water use, accounting for about $80\%$ of Yellow River surface runoff in the 1980s, was remarked as the significant reason for the degradation.
@@
 Here, by abstracting changes in official documents following institutional shifts (the 87-WAS and the 98-UBR), we depicted the SES structures of the YRB from 1975 to 2008.
-Then, we use Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without the institutional shifts (\textbf{Methods}; \textit{S2 in Supplementary Material}).
+Then, we use Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without the institutional shifts (\textbf{Methods} and \textit{Appendix S2}).
 By further interpreting the differences of the effects in the YRB, we explored the mechanisms linking SESs structure and outcomes for a deeper understanding of institutions' role in water governance worldwide.

### 2022-05-04 docs/papers/01_manuscript/02_structures.tex
feat(results,-structures): new figure 1

@@
 % Including the national authorities, the basin management authorities, provinces, cities, and even districts, top-down institutional structures of the YRB started to evolve up to now (\textit{S1 in Supplementary Material}).
-As a pioneer in water governance shifting in China, the YRB started to explore the initial water allocating scheme in the 1970s.
-The institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones of water governance.
+% As a pioneer in water governance shifting in China, the YRB started to explore a water allocating scheme since 1970s.
+The institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among national water governance practices (\textit{Appendix}~S1).
 Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
@@
 However, the controversial scheme helped little in turning the water depletion around until another strategy attempted to strengthen the responsibilities of the YRCC in integrated water management in 1998 (the 98-UBR).
-Therefore, our analysis period spans from 1975 (emergence of river depletion) to 2008 (a further polish of the 98-UBR), with the SESs shifted between three varying institutions which were different from other large river basins in China.
-
-% 制度结构关系抽象
-% Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{framework} A).
-% For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{framework} B), leading to sustainable outcomes.
-% Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{framework} C and D).
-% Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures, and a network model is a widely used way to depict them by abstracting links and nodes.
+Therefore, our analysis period spans from 1975 (emergence of river depletion) to 2008 (a further polish of the 98-UBR), with the SESs shifted between three varying institutions (Figure~\ref{structure}).
 
@@
 \begin{figure*}[!h]
-    \includegraphics[width=32pc]{diagrams/diagram.pdf}
+    \includegraphics[width=\linewidth]{diagrams/diagram.pdf}
 	\caption{
 		% 黄河流域的制度变迁与经济社会结构差异。
-		Institutional shifts and related SES structures in the Yellow River Basin (YRB). See \textit{Supplementary Material S1} for detailed introduction for the institutions.
-		% 国家政府在1987年和1998年先后两次出台了改变流域制度的政策，而黄河水利委员会、利益攸关的各省在不同制度时期具备的功能是不同的。
-%		\textbf{A.} The national government changed YRB management policies and institutions in 1987 and 1998.
-As a result, the Yellow River Conservancy Commission (YRCC) and the provinces acted differently in different periods.
-Three different SES structures existed successively in the YRB.
-		% 没有任何政策限制，各利益相关者此时期可以从单向但联通的河流生态单元内自由取水
-%		\textbf{1975–1987:} Without any constraints, water resources were freely accessible to each stakeholder (the provinces, in this case, denoted by red circles) from a one-way but connected ecological unit (the Yellow River, denoted by the blue rectangle).
-		% 在政策1之后，每个使用者都被分配了能够开采河流地表水资源的配额，而黄委会的工作是对配额的使用进行统计与汇报。
-%		\textbf{1987–1998:} After the implementation of policy 1 in 1987, each user was assigned a quota to withdraw surface water resources, and the YRCC (yellow triangle) was tasked with reporting on water quota use.
-		% 第二个政策之后，利益相关者取水需要向黄委会申请，黄委会则根据用水配额来批发许可。因此此时黄委会与利益相关者之间产生了直接的双向联系，监督他们对资源配额的取用。
-%		\textbf{1998–2008:} After the implementation of policy 2, stakeholders had to apply for water resources from the YRCC, which then licensed water use according to the quota.
-Under this institution, the YRCC had direct two-way connections between provinces and ecological components.
+		Institutional shifts and related SES structures in the Yellow River Basin (YRB).
+		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{Appendix S1} Table~\ref{tab:scheme87}).
+The national administrations are the ultimate authority in issuing water governance policies, which are often implemented by basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
+		\textbf{B.} Since the YRCC does not use but monitor water, the provincial administrative agencies are the major stakeholders.
+Since the 87-WAS, with surface water withdraw from the Yellow River restricted by specific quotas, each stakeholder seperatly develop by planning and using fundamental water resources.
+However, the natural hydrological processes are connected.
+Although the institutions focus mainly on the surface water (Sur.), it can also influence groundwater inside (Gro.) or water resources outside (Sur.
+and Gro.'), through systematic socio-hydrological processes within the YRB.
+		\textbf{C.} Institutional shifts and following structures changes.
+(1) From 1975 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from connected ecological unit (the reach of Yellow River, denoted by the blue circles).
+(2) After 1987-WAS, the YRCC (the yellow circles) was monitoring (the dot-line links) river reaches with the water use quota.
+(3) Since the 98-UBR, stakeholders have to apply water use licences from the YRCC (the connections between the red and yellow circles).
 	}

### 2022-05-04 docs/papers/01_manuscript/03_results.tex
feat(results,-structures): new figure 1

@@
 The increased water uses after 87-WAS aligns with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{main_results}C).
-On the other hand, the 98-UBR ended river depletion, despite the density of droughts still increasing for decades (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{main_results}C).
+On the other hand, the 98-UBR ended river depletion, despite the intensity of droughts still increasing for decades (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{main_results}C).
 
-\begin{figure*}[!h]
+\begin{figure*}[!tb]
     \centering
@@
 By contrast, after the 98-UBR, except Shanxi (whose water quota has always been far abundant over its actual water use since the 87-WAS) had an evident ($17.53\%$) increase in water use, almost all provinces have seen evident declines in water use ($-12.5\%$ on average).
-Furthermore, the regulated water use of provinces was not correlated ($-0.03$) with their water use from the Yellow River in proportions.
+Furthermore, the regulated water use of provinces was not correlated (partial correlation coefficient is $-0.03$, $p>0.1$) with their water use from the Yellow River in proportions.
 
-\begin{figure*}[!h]
+\begin{figure*}[!tb]
     \centering

### 2022-05-04 docs/papers/01_manuscript/04_discussion.tex
feat(results,-structures): new figure 1

@@
 Fixing the environmental background, the forecast by DSC takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textit{S2 in Supplementary Material}).
-As the accumulations of economy volume (GDP in different sectors) in the YRB maintained a parallel trend with other regions throughout (\textit{S3 in Supplementary Material} Figure~\ref{S3-1}), differences after the institutional shifts suggest water use changing per unit of production, especially in agriculture (\textit{S3 in Supplementary Material} Figure~\ref{S3-2}).
+As the accumulations of economy volume (GDP in different sectors) in the YRB maintained a parallel trend with other regions throughout (\textit{Appendix S3} Figure~\ref{S3-1}), differences after the institutional shifts suggest water use changing per unit of production, especially in agriculture (\textit{S3 in Supplementary Material} Figure~\ref{S3-2}).
 This fact is in line with the sigh from then: although the key to alleviating the drought is saving water in the irrigated areas, the tragedy of frequently scrambling for water appeared in some provinces %!

### 2022-05-04 docs/papers/01_manuscript/05_conclusion.tex
feat(results,-structures): new figure 1

@@
 Shifting throughout different SES structures framed by them, the observed water use of the YRB provinces had an $8.57\%$ increase than expected during the decade after the 87-WAS.
-Then, water use significantly decreased by  $4.9 billion m^3$ per year since the 98-UBR, while the model still suggests a $10.3 billion m^3$ annual increase in expectation.
+Then, water use significantly decreased by  $4.9$ billions $m^3$ per year since the 98-UBR, while the model still suggests a $10.3$ billions $m^3$ annual increase in expectation.
 Finally, as differences in stakeholders' response to the institutional shifts, water use rises after the 87-WAS in provinces with more water uses (e.g., Inner Mongolia, Henan, and Shandong) while shrunk in nearly all provinces after the 98-UBR.

### 2022-05-04 docs/papers/01_manuscript/06_methods.tex
feat(results,-structures): new figure 1

@@
 % 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程
-We estimated and analyzed the net effects of two SES structural changes of water use.
-The actual water use of the Yellow River Basin was peroxided by the sum of the water use of the target group provinces.
-To quantify water use, we used synthetic control methods to estimate possible trends of water use in the absence of institutional shifts.
-Finally, we created an economic model based on marginal revenue to provide a theoretical explanation for the observed “sprint effect” phenomenon.
-A brief technical overview is given in \textit{Supplementary Material S2}.
+We first abstract the SES structures of water using in the YRB from 1975 to 2008, where two institutional shifts split the period into three pieces.
+We then estimated the net effects of two institutional shifts on total water uses, changing trends, and differences of the YRB's provinces, by Differenced Synthetic Control (DSC) method \cite{arkhangelsky2019}.
+Finally, for discussion, we created an economic model based on marginal revenue to provide a theoretical interpretation for the observed water use outcomes.
 
-\subsection{Dataset and variables}
-% 我们使用中国1978年至2012年各省的年度用水量数据集，这个公开的数据集由全国水资源利用调查得到，详细可查看。
-We used China’s provincial annual water consumption dataset from 1978 to 2012.
-This publicly available dataset was obtained from the National Water Resources Utilization Survey; details are accessible from Zhou (2020)
-\cite{zhou2020}.
-A total of 10 provinces or regions have been directly affected by the water allocation institutional shifts in the YRB, accounting for $8.6\%$ of the total population of China (in 1990).
-Eight provinces have been particularly affected because of their greater dependence on the water resources from the Yellow River (see \textit{Supplementary Material S2}).
-Therefore, we divided the dataset into a “target group” and a “control group”, treating provinces that were greatly affected as the target group $(n=8)$ and provinces that were not affected by the institutional shifts as the potential control group $(n=20)$.
+\subsection{Portraying structures}
+% 制度结构关系抽象
+% Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{framework} A).
+% For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{framework} B), leading to sustainable outcomes.
+% Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{framework} C and D).
+% Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures, and a network model is a widely used way to depict them by abstracting links and nodes.
 
-We focused on total water use in the YRB.
-The actual water uses are given by the dataset, but when the synthetic control method is used to predict the water use of the control group, other independent influences need to be considered.
-Thus, we used economic features that are highly related to water use to extrapolate demand (e.g., agriculture, industry, service industry, and domestics, see \textit{Supplementary Material S2, Table 1}
-
-\subsection{Difference Synthetic Control}
+\subsection{Differenced Synthetic Control}
 Synthetic control is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadie2010, abadie2015, hill2021}.
@@
 $W_i$ is the weight matrix for target unit $i$.
-We minimized the root mean square error (RMSE) by using the Synth package in R \cite{abadieSynthPackageSynthetic2011, abadieComparativePoliticsSynthetic2015}.
+We minimized the root mean square error (RMSE) by using the SyntheticControl package in python3.
 All codes are accessible in the repository.
@@
 The net effect of the water allocation institutional shift was then estimated by calculating the difference of water uses after the institutional shift between the treated group and the control group, compared with the water use difference before the shift.
+
+\subsection{Dataset and variables}
+% 我们使用中国1978年至2012年各省的年度用水量数据集，这个公开的数据集由全国水资源利用调查得到，详细可查看。
+We used China’s provincial annual water consumption dataset from 1978 to 2012.
+This publicly available dataset was obtained from the National Water Resources Utilization Survey; details are accessible from Zhou (2020) \cite{zhou2020}.
+A total of 10 provinces or regions have been directly affected by the water allocation institutional shifts in the YRB, accounting for $8.6\%$ of the total population of China (in 1990).
+Eight provinces have been particularly affected because of their greater dependence on the water resources from the Yellow River (see \textit{Supplementary Material S2}).
+Therefore, we divided the dataset into a “target group” and a “control group”, treating provinces that were greatly affected as the target group $(n=8)$ and provinces that were not affected by the institutional shifts as the potential control group $(n=20)$.
+
+We focused on total water use in the YRB.
+The actual water uses are given by the dataset, but when the synthetic control method is used to predict the water use of the control group, other independent influences need to be considered.
+Thus, we used economic features that are highly related to water use to extrapolate demand (e.g., agriculture, industry, service industry, and domestics, see \textit{Supplementary Material S2, Table 1}
 
@@
 
-Because $F’$ is monotonically decreasing, based on a comparison of costs and benefits for stakeholders (provinces) in the three cases,
+Because $F'$ is monotonically decreasing, based on a comparison of costs and benefits for stakeholders (provinces) in the three cases,
 
@@
 
-The result of $\hat x_i^*>x_i^*$ indicates that individual rationality would deviate from collective rationality when property rights are unclear \cite{hardinTragedyCommons2009}, because of the common-pool characteristics of water
-\cite{castilla-rhoGroundwaterCommonPool2020,ostromGeneralFrameworkAnalyzing2009}.
+The result of $\hat x_i^*>x_i^*$ indicates that individual rationality would deviate from collective rationality when property rights are unclear, because of the common-pool characteristics of water.
 

### 2022-05-04 docs/papers/02_appendix/01_institution_context.tex
feat(results,-structures): new figure 1

--- 2022-03-20 docs/papers/tex/appendix/institution_context.tex
@@
 % 水资源分配方案在全世界范围内都是流域管理的普遍制度。
-Water allocation schemes are widespread in large river basin management programs throughout the world (see \textit{Supplementary Material Figure~\ref{fig:world}}) \cite{speedBasinwaterallocation2013}.
+Water allocation schemes are widespread in large river basin management programs throughout the world (see \textit{Supplementary Material Figure~\ref{fig:world}}) \cite{speed2013}.
 % 其中中国的黄河流域以典型的自上而下进行制度改革，这种模式会对制度产生迅速的影响，使我们能够定量地估计高层制度设计变化对用水的净影响。
@@
 \begin{itemize}
-    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}.
+    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wang2019, wang2019a}.
     \item \textbf{1987}: Implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
@@
 % 基于上述分析，我们抽象出了如正文图2中所展示的流域水资源分配制度的运行结构，并将研究时段选择在1975到2008之间。
-On the basis of the above analysis, we abstracted the operational structure of the water resource allocation institution of the YRB as shown in Figure 2 of the main text, focusing on the period between 1975 and 2008.
+% On the basis of the above analysis, we abstracted the operational structure of the water resource allocation institution of the YRB as shown in Figure 2 of the main text, focusing on the period between 1975 and 2008.
 By comparing the net effects of three different institutional structures split by the two institutional shifts, we were able to reach a stronger understanding of the influence of structural alignments under the same basin (previous structure-based analysis usually focus on a certain type of systems but with different geographic contexts).
 
-\begin{figure}[!htb]
+\begin{figure*}[!htb]
     \centering
@@
     \label{fig:world}
-\end{figure}
+\end{figure*}
 
-\begin{figure}[!htb]
-    \centering
-	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/YRB_scheme}
-	\caption{
-		% 中国自上而下的水资源分配制度模式（以黄河流域为例）
-		A top-down water resources allocation scheme in China (a case study of the YRB).
-		% 共有十个省或地区从黄河获取地表水资源，其中8个省的依赖性较强（see Supplementary Material Fig）。
-		\textbf{A.} A total of 10 provinces or regions withdraw surface water resources from the Yellow River, of which 8 are highly dependent on the river (see \textit{Supplementary Material S2}).
-		% 中国政府是下发流域管理政策的最高权威，其政策常常能够很快自上而下全面推行。
-		\textbf{B.} The Chinese government is the ultimate authority in issuing watershed management policies, which are often quickly implemented from top down.
-		% 流域管理机构（在黄河是黄河水利委员会）主要负责顺从国家的政策方针来进行流域的日常管理工作。
-		\textbf{C.} The basin-level agency (here, the YRCC) is primarily responsible for the river-related management of the basin in accordance with national policy guidelines.
-		% 利益相关者是各省
-		\textbf{D.} The water management system directly affects the process by which local governments (major stakeholders) plan and use water resources for development.
+% \begin{figure}[!htb]
+%     \centering
+% 	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/YRB_scheme}
+% 	\caption{
+% 		% 中国自上而下的水资源分配制度模式（以黄河流域为例）
+% 		A top-down water resources allocation scheme in China (a case study of the YRB).
+% 		% 共有十个省或地区从黄河获取地表水资源，其中8个省的依赖性较强（see Supplementary Material Fig）。
+% 		\textbf{A.} A total of 10 provinces or regions withdraw surface water resources from the Yellow River, of which 8 are highly dependent on the river (see \textit{Supplementary Material S2}).
+% 		% 中国政府是下发流域管理政策的最高权威，其政策常常能够很快自上而下全面推行。
+% 		\textbf{B.} The Chinese government is the ultimate authority in issuing watershed management policies, which are often quickly implemented from top down.
+% 		% 流域管理机构（在黄河是黄河水利委员会）主要负责顺从国家的政策方针来进行流域的日常管理工作。
+% 		\textbf{C.} The basin-level agency (here, the YRCC) is primarily responsible for the river-related management of the basin in accordance with national policy guidelines.
+% 		% 利益相关者是各省
+% 		\textbf{D.} The water management system directly affects the process by which local governments (major stakeholders) plan and use water resources for development.
 Although only surface water (Sur.) is usually traced and restricted, it can also influence groundwater through related hydro-processes such as recharge.
-	}
-	\label{fig:framework}
-\end{figure}
+% 	}
+% 	\label{fig:framework}
+% \end{figure}
+
+% \begin{table*}
+%     \centering
+%     \small
+%     \caption{Policies and regulations above YRB level which affected the whole basin in water utilization}\label{tab:policies}
+%     \begin{minipage}{\linewidth}
+%     \resizebox{\linewidth}{!}{
+%     \begin{tabular}{p{0.6\linewidth}rp{0.35\linewidth}}
+%         Name & Year & Agency \\
+%         \midrule
+%         1. Water Law of PRC & 1988 & National People's Congress of the PRC \\
+%         2. Water Law of PRC -revised 1 & 2009 & National People's Congress of the PRC \\
+%         3. Water Law of PRC -revised 2 & 2016 & National People's Congress of the PRC \\
+%         4. Regulations on the Administration of Water Drawing Licences and The Collection of water resource fees & 2006 & State Council of the PRC \\
+%         5. Regulations on the Administration of Water Drawing Licences and The Collection of water resource fees -revised 1 & 2017 & State Council of the PRC \\
+%         6. Regulations on the Allocation of Water in the Yellow River & 2006 & State Council of the PRC \\
+%         7. Yellow River water supply distribution scheme & 1987 & State Council of the PRC \\
+%         8. Measures for the Administration of Water Drawing Permits & 2008 & Ministry of Water Resources of the PRC \\
+%         9. Measures for the Administration of Water Drawing Permits -revised 1 & 2015 & Ministry of Water Resources of the PRC \\
+%         10. Measures for the Administration of Water Drawing Permits -revised 2 & 2017 & Ministry of Water Resources of the PRC \\
+%         11. Regulations on the Allocation of Water in the Yellow River & 2006 & State Council of the PRC \\
+%         12. Annual distribution of available water supply of the Yellow River and mainstream water dispatching scheme & 1998 & Ministry of Water Resources of the PRC \\
+%         13. The Yellow River water dispatching management measures & 1998 & Ministry of Water Resources \\
+%         14. Measures for the Implementation of the Yellow River Water Rights Conversion Management & 2004 & Ministry of Water Resources \\
+%         15. Regulations on the Administration of Water Drawing Licences and The Collection of water resource fees & 2006 & State Council of the PRC \\
+%         16. Measures for the implementation of the water drawing Permit system & 1993 \\ State Council of the PRC \\
+%         17. Measures for the demonstration and management of water resources in construction projects & 2002 & Ministry of Water Resources of the PRC \\
+%         18. Implementation Opinions on the Reform of Water Conservancy Project Management System & 2006 & State Council of the PRC \\
+%         \bottomrule
+%     \end{tabular}}
+
+%     \footnotesize[1]{If a policy was proposed by multiple legacies, we only show the highest one.}
+%     \end{minipage}
+% \end{table*}

### 2022-05-04 docs/papers/01_manuscript/02_structures.tex
feat(institution-context): appendix sec1

@@
 		Institutional shifts and related SES structures in the Yellow River Basin (YRB).
-		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{Appendix S1} Table~\ref{tab:scheme87}).
+		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{Appendix S1} Table~\ref{tab:quota}).
 The national administrations are the ultimate authority in issuing water governance policies, which are often implemented by basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
@@
 and Gro.'), through systematic socio-hydrological processes within the YRB.
-		\textbf{C.} Institutional shifts and following structures changes.
+		\textbf{C.} Institutional shifts and following structures changes (details in \textit{Appendix S1}).
 (1) From 1975 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from connected ecological unit (the reach of Yellow River, denoted by the blue circles).

### 2022-05-04 docs/papers/01_manuscript/04_discussion.tex
feat(institution-context): appendix sec1

@@
 % 过去的研究总结出87-WAS收效甚微的几个因素：
-Although previous studies summarised reasons for the non-ideal effect of 87-WAS, few improvements in the 98-UBR indicate that they underestimated influences from the structural changes (\textit{S3 in Supplementary Material} Figure~\ref{fig:S3-3}).
+Although previous studies summarised reasons for the non-ideal effect of 87-WAS, few improvements in the 98-UBR indicate that they underestimated influences from the structural changes (\textit{Appendix S3} Figure~\ref{fig:S3-3}).
 As we have depicted (Figure~\ref{structure}), the institutional shifts twice framed the structure of SESs in the YRB and led to different building blocks, which were also reported in various types of SESs worldwide.

### 2022-05-04 docs/papers/02_appendix/01_institution_context.tex
feat(institution-context): appendix sec1

--- 2022-03-20 docs/papers/tex/appendix/institution_context.tex
@@
 % 水资源分配方案在全世界范围内都是流域管理的普遍制度。
-Water allocation schemes are widespread in large river basin management programs throughout the world (see \textit{Supplementary Material Figure~\ref{fig:world}}) \cite{speedBasinwaterallocation2013}.
-% 其中中国的黄河流域以典型的自上而下进行制度改革，这种模式会对制度产生迅速的影响，使我们能够定量地估计高层制度设计变化对用水的净影响。
-The Yellow River Basin (YRB) in China has a typical top-down approach to institutional reform, which produces rapid institutional impacts and allows researchers to quantitatively estimate the net impact of changes in high-level institutional design on water use (see \textit{Supplementary Material Figure~\ref{fig:framework}}).
-% 作为中国最早实施水资源分配制度的流域，黄河的制度变化可以在几个水利部发布的文件中得以窥见
-This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level):
+Water allocation schemes are widespread in large river basin management programs throughout the world (see \textit{Appendix} Figure~\ref{fig:world}) \cite{speed2013}.
+This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level)\cite{wang2019a}:
 \begin{itemize}
-    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}.
+    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wang2019, wang2019a}.
     \item \textbf{1987}: Implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
@@
     % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
-    \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wangReviewImplementationYellow2019, wangThingsCurrentSignificance2019}.
+    \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wang2019,wang2019a}.
     \item \textbf{2021}: A call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
@@
 % 在上述文件中，1982年的文件标志着设计分水制度尝试的开始，2008年标志着该制度走向成熟（完全建立起流域-省-市区的多级水资源分配和统一调度）。
-The 1982 document marked the beginning of the attempt to design a water allocation institution, and the 2008 document marked the maturity of the system (complete establishment of basin-level, provincial, and district water allocation and unified regulation).
-Currently, a major overhaul is in the planning stages.
-Major shifts of the institution can be analyzed by using the 1987 and 1998 documents.
-It is worth noting that, although the essential reason for these institutions was the mismatch between the spatial and temporal distribution of water resources as well as social and economic water demands, the direct reason for their introduction was the drying-up of the Yellow River \cite{wangReviewImplementationYellow2019}.
+Since 1982, administrations attemptted to design a quota institution, and the 2008 document marked the maturity of the scheme (complete establishment of basin-level, provincial, and district water quotas).
+Between the period, two significant institutional shits can be analyzed by using the 1987 (87-WAS) and 1998 (98-UBR) documents.
 
-\textbf{The official documents in 1987 clearly convey the following key points:}
-\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today.
+% It is worth noting that, although the essential reason for these institutions was the mismatch between the spatial and temporal distribution of water resources as well as social and economic water demands, the direct reason for their introduction was the depletion of the Yellow River.
+
+The official documents in 1987 (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today) clearly convey the following key points:
+
 \begin{itemize}
 	% 该政策面向的目标是各省（区域），黄委会没有被提及
-	\item The policy is aimed at related provinces (or regions), and the YRCC is not mentioned.
+	\item The policy is aimed at related provinces (or regions in the same administrative level).
 	% 政策制定的首要考虑是解决断流问题
-	\item Drying-up of the river is identified as the first consideration of this institution.
+	\item Depletion of the river is identified as the first consideration of this institution.
 	% 各省被鼓励在此配额下制定自己的用水计划
@@
 
-\textbf{The official documents in 1998 clearly convey the following key points:}
-\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today.
+The official documents in 1998
+(\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today) clearly convey the following key points:
+
 \begin{itemize}
@@
 		% 世界已有水资源分配制度的大河流域，其中黄河流域最早于1987年提出资源分配方案，后于1998年更改为统一调度方案。
-		\textbf{A.} Major river basins in the world with existing water resource allocation systems (shaded red); the YRB first proposed a resource allocation scheme in 1987 (designed in 1983) and then changed to a unified regulation scheme in 1998 (designed in 1997 but implemented in 1998).
+		\textbf{A.} Major river basins in the world with water resource allocation systems (shaded red); the YRB first proposed a resource allocation scheme in 1987 (designed since 1983) and then changed to a unified regulation scheme in 1998 (designed in 1997 but implemented in 1998) \cite{speed2013}.
 		% 不同的水资源分配制度设计模式，中国黄河流域是典型的自上而下。
-		\textbf{B.} Different water resource allocation system design patterns; the YRB is typical of a top-down system with multiple levels.
+		\textbf{B.} Different water resource allocation system design patterns; the YRB is typical of a top-down system.
 		% 流域分水制度的演化。这种多层次的制度设计有其历史变化过程。
@@
     \label{fig:world}
-\end{figure}
+\end{figure*}
 
-\begin{figure}[!htb]
+% 基于上述分析，我们抽象出了两次制度转变之后的SES结构变化如正文的图1C所示。
+Based on the above documents, we abstracted the structural changes of SES (see \textit{Appendix S2}) after the two institutional changes, as shown in Figure~\ref{structure}~C.
+
+\begin{table*}
     \centering
-	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/YRB_scheme}
-	\caption{
-		% 中国自上而下的水资源分配制度模式（以黄河流域为例）
-		A top-down water resources allocation scheme in China (a case study of the YRB).
-		% 共有十个省或地区从黄河获取地表水资源，其中8个省的依赖性较强（see Supplementary Material Fig）。
-		\textbf{A.} A total of 10 provinces or regions withdraw surface water resources from the Yellow River, of which 8 are highly dependent on the river (see \textit{Supplementary Material S2}).
-		% 中国政府是下发流域管理政策的最高权威，其政策常常能够很快自上而下全面推行。
-		\textbf{B.} The Chinese government is the ultimate authority in issuing watershed management policies, which are often quickly implemented from top down.
-		% 流域管理机构（在黄河是黄河水利委员会）主要负责顺从国家的政策方针来进行流域的日常管理工作。
-		\textbf{C.} The basin-level agency (here, the YRCC) is primarily responsible for the river-related management of the basin in accordance with national policy guidelines.
-		% 利益相关者是各省
-		\textbf{D.} The water management system directly affects the process by which local governments (major stakeholders) plan and use water resources for development.
-Although only surface water (Sur.) is usually traced and restricted, it can also influence groundwater through related hydro-processes such as recharge.
-	}
-	\label{fig:framework}
-\end{figure}
+    \small
+    \caption{Water quotas assigned in the 87-WAS}\label{tab:quota}
+	\resizebox{\linewidth}{!}{
+    \begin{tabular}{p{0.24\linewidth}llllp{0.1\linewidth}lllll}
+	\hline
+	Items (water volume, billion $m^3$)                    & Qinghai & Sichuan & Gansu   & Ningxia & Inner Mongolia & Shanxi  & Shaanxi & Henan   & Shandong & Jinji  \\
+	\hline
+	Demands in water plan                                                & 35.7    & 0       & 73.5    & 60.5    & 148.9          & 115     & 60.8    & 111.8   & 84       & 6      \\
+	Quota designed in 1983                                               & 14      & 0       & 30      & 40      & 62             & 43      & 52      & 58      & 75       & 0      \\
+	Quota assigned in 1987                                               & 14.1    & 0.4     & 30.4    & 40.0    & 58.6           & 38.0    & 43.1    & 55.4    & 70.0     & 20     \\
+	Average water consumption from the Yellow River from 1987-2008       & 12.03   & 0.25$^a$   & 25.80   & 36.58   & 61.97          & 21.16   & 11.97   & 34.30   & 77.87    & 5.85$^a$  \\
+	Proportion of water from the Yellow River in total water consumption & 48.12\% & 0.10$^b$\%  & 30.79\% & 58.45\% & 47.82\%        & 73.55\% & 44.39\% & 24.77\% & 34.41\%  & 3.11\%$^b$ \\
+    \hline
+    \end{tabular}}
+	\footnotesize[a]\leftline{{Calculated by data from 2004 to 2017.}}\\
+	\footnotesize[b]{\leftline{The share is too small, thus the provinces (or region) Sichuan and Jinji not to be considered in this study.}}
+\end{table*}

### 2022-05-04 docs/papers/01_manuscript/06_methods.tex
fix(appendix): appendix sort

@@
 In developing the model, we highlighted the main features of the YRB, as well as the water use institutions of 1987 and 1998. We proposed three intuitive and general assumptions.
-
-\begin{ass}
-    % (生产)为了简化，由于不可替代性，水是每个省的同质生产函数10的唯一投入。$F(x)$是连续的，满足Inada条件，即$F'(x)>0, F''(x)<0$(边际收益递减假设)，$F'(0)=\infty$,$ F'(\infty)=0$。产品产量处于完全竞争状态，单位价格为15。
-    (Water-dependent production) For simplicity, water is assumed to be the only input of the homogenous production function $F(x)$ of each province because of its irreplaceability.
-$F(x)$ is continuous and satisfies the Inada Conditions, i.e., $F'(x)>0, F''(x)<0$ (the diminishing marginal returns assumption), $F'(0)=\infty$,$ F'(\infty)=0$.
-The production output is under perfect competition, with a constant unit price of $P$.
-\end{ass}
-\begin{ass}
-    (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in N provinces, the cost of water use is equally assigned to each province under any water use.
-The unit cost of water is a constant $C$.
-\end{ass}
-\begin{ass}
-    (Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water uses.
-\end{ass}
-
-Under the above assumptions, we can demonstrate three cases consisting of local governments in YRB to simulate their water use decision-making and water use patterns.
-
-\begin{case} Decentralized institution:
-    This case corresponds to a situation without any high-level water allocation institution (i.e., before 1987, see Figure~\ref{structure} B).
-
-    When each province independently decides on its water use, the optimal water use $\hat x_i^*$ in province $i$ satisfies:
-    $$F'(x)=\frac{C}{P \cdot N}$$
-
-    When the decisions in different periods are independent, for $t=0,1,2 \ldots$, then:
-    $$\hat x_{it}^*=\hat x_i^*$$
-
-\end{case}
-
-\begin{case} Mismatched institution
-    This case corresponds to a mismatched institution (i.e., $1987\sim1998$, see Figure~\ref{structure} C).
-
-    The water quota is determined at $t=0$ and imposed in $t=1,2,\ldots$ The total quota is a constant denoted as $Q$, and the quota for province $i$ is determined in a proportional form:
-    $$Q_i=Q \cdot \frac{x_i}{x_i + \begin{matrix} \sum x_{-i} \end{matrix}}$$
-
-    Under a scenario with decentralized decision-making with a water quota institution, given other provinces’ water use decisions remain unchanged, the optimal water use $\widetilde x_{i0}^*$ of province $i$ at $t=0$ satisfies:
-
-    $F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot f(Q \cdot \frac{x_{i,0}}{\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix})^2}$.
-
-    When future water use is constrained by a water quota, the dynamic optimization problem of province $i$ is shown as follows:
-
-    $max  \quad P \cdot F(x_{i,0})-\frac{C \cdot \begin{matrix} \sum x_{i,0} + x_{-i,0} \end{matrix}}{N}+\beta P \cdot F(x_{i,1})+\beta^2 P \cdot F(x_{i,2})+...$
-
-    $=P \cdot F(x_{i,0})-C \cdot \frac{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}{N}+\frac{\beta}{1-\beta} P \cdot F(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}})$
-
-    First-order condition: $P \cdot F'(x_{i,0})-\frac{C}{N}+\frac{\beta}{1-\beta}[P \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0}+\begin{matrix} \sum  x_{-i,0} \end{matrix})^2}]=0$
-
-    where $f(\cdot)$ is the differential function of $F(\cdot)$.
-
-    The optimal water use in province i at t=0 $\widetilde x_{i,0}^*$ satisfies $P \cdot F'(x_{i,0})=\frac{C}{N}-\frac{\beta}{1-\beta} \cdot P \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$, i.e., $F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$.
-
-\end{case}
-
-\begin{case} Matched institution
-
-    This case corresponds to the institution under which the YRCC centrally managed water allocation between provinces (i.e., $1998\sim2008$, see Figure~\ref{structure} D).
-
-    When the $N$ provinces decide on water uses as unified whole (e.g., the central government completely decides and controls on the water use in each province), the optimal water use $x_i^*$ of province $i$ satisfies:
-
-    $$F'(x)=\frac{C}{P}$$
-
-\end{case}
-
-We propose Proposition 1 and Proposition 2:
-
-\textbf{Proposition 1}: Compared with the decentralized institution, a matched institution with unified management decreases total water use.
-
-Because $F'$ is monotonically decreasing, based on a comparison of costs and benefits for stakeholders (provinces) in the three cases,
-
-$$\widetilde x_i^*>\hat x_i^*>x_i^*$$
-
-The result of $\hat x_i^*>x_i^*$ indicates that individual rationality would deviate from collective rationality when property rights are unclear, because of the common-pool characteristics of water.
-
-The difference of $\widetilde x_i^*$ and $\hat x_i^*$ stems from two parts: the marginal returns effect and the marginal costs effect.
-First, the “shadow value” provides additional marginal returns of water use in $t=0$, wwhich increases the incentives of water overuse by encouraging bargaining for a larger quota.
-Second, the future cost of water use would be degraded from $\frac{P}{N}$ to an irrelevant cost.
-
-The optimal water use under the three cases implies that mismatched institutions cause incentive distortions and lead to resource overuse.
-
-\textbf{Proposition 2}: The quota determination of the mismatched institution increases the incentives of current water use.
-
-The intuition for this proposition is straight-forward in that all provinces would use up their allocated quota under a relatively small $Q$.
-As $Q$ increases, the quota would provide higher future benefits for a pre-emptive water use strategy.
-Since the provincial water use decisions are exactly symmetric, total water use would increase when each province has higher incentives for current water use.
-This situation corresponds to a “sprint” effect, where the total water use dramatically increases in the “sprint” period.
-
-Extensions of the model are shown in \textit{Supplementary Material S3}.

### 2022-05-04 docs/papers/02_appendix/04_theoretical_model.tex
fix(appendix): appendix sort

%! Author = songshgeo
%! Date = 2022/3/19

\paragraph{Setup}

In order to understand the mechanisms underlying the empirical results, we developed a dynamic economic model to analyze how institutional mismatch could have led to the sprint effect in water use, especially among provinces with high incentives for excess water use. Specifically, we modeled individual provincial decision-making in water resources before quota execution.

We proposed three intuitive and general assumptions.

%There are infinite discrete periods (t=1, 2,...) and N provinces. The water use of province i is denoted as $x_{i}$. At t=0, there is no constraints on water use. In the following periods (t=1,2,...), each province is imposed of quota restrictions determined at t=0. The water use decision of each province is forward-looking, based on not only current benefits and costs but also its future impacts on quota restriction. There are several key assumptions on the water use about production input, output, and water use constraints.

\begin{ass}
(Water-dependent production) Because of irreplaceability, water is assumed to be the only input of the production function with two types of production efficiency. The production function of a high-incentive province is $A_HF(x)$, and the production function of a low-incentive province is $A_LF(x)$ ($A_H>A_L$). F(x) is continuous, $F'(0)=\infty$, $ F'(\infty)=0$, $F'(x)>0$, and $F''(x)<0$. The production output is under perfect competition, with a constant unit price of $P$.
\end{ass}

\begin{ass}
 (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in $N$ provinces, the cost of water use is equally assigned to each province under any water use. The unit cost of water is a constant $C$.
\end{ass}
\begin{ass}
(Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water use.
\end{ass}
Under the above assumptions, we can demonstrate three cases to simulate the water use decision-making and water use patterns in a whole basin.

Under the above assumptions, we can demonstrate three cases consisting of local governments in a whole basin to simulate their water use decision-making and water use patterns.

 %case1
\begin{case}Dentralized decision: This case corresponds to a situation without any high-level water allocation institution.

When each province independently decides on its water use, the optimal water use $x_i^*$ in province $i$ satisfies:

 $AF'(x)=\frac{C}{P}$,

 where A denotes $A_H$ for a high-incentive province and $A_L$ for a low-incentive province.

 When the decisions in different periods are independent, for $t$ = 0, 1, 2, ..., then:

 $x_{it}^* = x_i^*$

 \end{case}

 %case2
 \begin{case} Mismatched decision: This case corresponds to a mismatched institution.

 The water quota is determined at $t$=0 and imposed in $t$=1,2,... Under the subjective expectation of each province that current water use may influence the future water allocation determined by high-level authorities, the total quota is a constant denoted as Q, and the quota for province $i$ is determined in a proportional form:

 $Q_i=Q \cdot \frac{x_i}{x_i + \begin{matrix}\sum{x_{-i}} \end{matrix}}  $.

Under a scenario with decentralized decision-making with a water quota, given other provinces' decisions on water use remain unchanged, the optimal water use of province $i$ at $t$=0 satisfies:

$AF'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix})^2}$,

where A denotes $A_H$ for a high-incentive province and $A_L$ for a low-incentive province.

\end{case}

%case3
\begin{case} Matched institution: This case corresponds to the institution under which water use in a basin is centrally managed.

When the $N$ provinces decide on water use as a unified whole (e.g., the central government completely decides and controls the water use in each province), the optimal water use $x_i^*$ of province $i$ satisfies:

$F'(x)=\frac{C}{P}$.

\end{case}

We propose Proposition 1 and Proposition 2:

Proposition 1: Compared with the decentralized institution, a matched institution with unified management decreases total water use.

The optimal water use under the three cases implies that mismatched institutions cause incentive distortions and lead to resource overuse.

Proposition 2: The water overuse is higher among provinces with high water use incentives than that with low water use incentives under a mismatched institution.

The intuition for this proposition is straightforward in that all provinces would use up their allocated quota under a relatively small $Q$. As production efficiency increases, the marginal benefits of a unit quota increase, and the quota would provide higher future benefits for a pre-emptive water use strategy. Provinces with high production efficiency have higher optimal values of water use under the decentralized decision, and the divergence in water use would be exaggerated during the period that the water quota is expected to be implemented and water use is in greater competition.

Extensions of the model are shown in \textit{Appendix S5}.%%%

\begin{case_appendix}Centralized decision

When the N provinces decide on water uses as a unity, the marginal cost is C, equal to its fixed unit cost.
The water use of province $i$ aims to maximize $P\cdot A\cdot F(x)-C$.
Hence, $x_i^*$ satisfies $P \cdot A\cdot F'(x)=C$, i.e., $AF'(x)=\frac{C}{P}$, where A denotes $A_H$ for a high-incentive province and $A_L$ for a low-incentive province.

\end{case_appendix}

%case2
	\begin{case_appendix}Decentralized decision

When each of the N provinces independently decides on its water use, the marginal cost of water use would be $\frac{C}{N}$ as a result of cost-sharing with others.
Hence, the optimal water use in province i at period t, denoted as $\hat x_i^*$, satisfies $P \cdot A \cdot F'(x_{it})=\frac{C}{N}$, i.e., $A \cdot F'(x)=\frac{C}{P \cdot N}$.
Since $F'$ is monotonically decreasing, $\hat x_{it}^*>x_i^*$.
\end{case_appendix}

%case3
	\begin{case_appendix}Forward-looking decentralized decision under quota restrictions

	When the future water use would be constrained by the water quota, the dynamic optimization problem of province i is shown as follows. In t=1,2,..., there would be no relevant cost when the quota is bound that each province takes constant costs of $\frac{P \cdot Q}{N}$ regardless of the allocation. It is sufficient to consider only the total water quota is smaller than total water use in Case 2 since a ``too large'' quota doesn't make sense for ecological policies.

$max  \quad P \cdot A \cdot F(x_{i,0})-\frac{C \cdot \begin{matrix} \sum x_{i,0} + x_{-i,0} \end{matrix}}{N}+\beta P \cdot A \cdot F(x_{i,1})+\beta^2 P \cdot A \cdot F(x_{i,2})+...$

$=P \cdot A \cdot F(x_{i,0})-C \cdot \frac{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}{N}+\frac{\beta}{1-\beta} P \cdot A \cdot F(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}})$

First-order condition: $P \cdot A \cdot F'(x_{i,0})-\frac{C}{N}+\frac{\beta}{1-\beta}[P \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0}+\begin{matrix} \sum  x_{-i,0} \end{matrix})^2}]=0$

where $f(\cdot)$ is the differential function of $F(\cdot)$.

The optimal water use in province i at t=0 $\widetilde x_{i,0}^*$ satisfies $P \cdot A \cdot F'(x_{i,0})=\frac{C}{N}-\frac{\beta}{1-\beta} \cdot P \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$,
i.e.,
$A \cdot F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$.

Since $F'>0$ and $F''<0$, $\widetilde x_i^*>\hat x_i^*>x_i^*$, taken others' water use $x_{-i,0}$ as given. Since the provincial water use decisions are exactly symmetric, total water use would increase when each province has higher incentives for current water use.

%Proposition 1
Proof of Proposition 1:

Because $F'>0$ and $F''(x)<0$ is monotonically decreasing, based on a comparison of costs and benefits for stakeholders (provinces) in the three cases,

$\widetilde x_i^*>\hat x_i^*>x_i^*$.

The result of $\hat x_i^*>x_i^*$ indicates that individual rationality would deviate from collective rationality under unclear property rights where a water user is fully responsible for the relevant costs. The result of $\hat x_i^*>x_i^*$

The difference between $ x_i^*$ and $\hat x_i^*$ stems from two parts: the effect of the marginal returns and the effect of the marginal costs. First, the ``shadow value'' provides additional marginal returns of water use in $t$ = 0, which increases the incentives of water overuse by encouraging bargaining for a larger quota. Second, the future cost of water use would be degraded from $\frac{P}{N}$ to an irrelevant cost.

%Proposition 2
Proof of Proposition 2:

Since $A_H>A_L$, $F'(x_H)<F'(x_L)$,
Eq.(xxx) %此处引用：$AF'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix})^2}$
implies a positive relation between $x_{i0}$ and A, when $\beta, P, C, Q$, and other provinces' water use are taken as given.

The difference between $\widetilde x_i^*$ and $\hat x_i^*$ (i.e., $\frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$) represents the incentive of water overuse derived from an expectation of water quota allocation. The incentive of water overuse increases by A.
\end{case_appendix}

%图注释

\begin{fig}
Optimal water use under different institutions

\tiny Notes: The figure depicts the relationship of marginal return deducted from marginal cost and water use of province $i$ at t=0 under centralized decisions, decentralized decisions, and decentralized decisions under quota restrictions, for a province with high water use incentive in Panel (A), and for a province with low water use incentive in Panel (B). Assume $F_H(x)=A_Hln(1+x), F_L(x)=A_Lln(1+x), A_H=1, A_L=0.8, N=8, P=1, C=0.5, \beta=0.7$, and $Q=8$. In Case 3, others' water use is taken as given, equal to the optimal water use under Case 2. The horizontal coordinate of each intersection of marginal return minus the marginal cost and break-even line represents the optimal water use under each case.
\end{fig}

### 2022-05-04 docs/papers/02_appendix/05_model_extensions.tex
fix(appendix): appendix sort

%Model extension部分
Further analysis of the general economic model

Using the general economic model (see the Methods section in the main text), we also explored the response of stakeholders to water quota policies. We considered two additional scenarios for stakeholders, one that considered technology growth and one that considered different valuations through time (via the discount rate) of economic benefits and ecological costs. In the following scenarios, the cost is assumed to be untransferable, which could be fully allocated to the one incurring the water use. Explaining plausible scenarios for these stakeholders will help us better understand the causes of the water overuse and potential solutions. We argue that the water overuse remains robust even if a complete and equitable system.

% technology growth
    \begin{case_appendix}Forward-looking decentralized decision, taken ecology cost into considerations

    Even if the negative externality of water overuse is eliminated by``fair" ecology cost of $\frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \cdot Q \cdot C$, it is possible that the future growth opportunities and ``remote" ecological costs provide enough incentive for the sprint.  The water overuse has the value of future economical benefits by slacking the water use constraint in the future. The heterogeneous production efficiency is omitted in this section, and we set A=1.

(a) technology growth

Assume that there is an exogenous technology growth rate of g in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$, and discount factor $\beta$. For simplicity, consider a finite-period water use optimization:

$ max \quad P \cdot (1+g)^t ln(1+x_{i,0})-\frac{C}{N}+\beta^t \begin{matrix} \sum_{t=1}^T [P \cdot (1+g)^t ln(x_{i,t}+1)-C \cdot x_{i,t}] \end{matrix}$

$s.t. \quad x_{i,t} \leq Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \quad for \quad \forall t$

We depict the relationship of multi-period profit and water use $x_{i,0}$ in different horizons in Figure 4%%此处引用图片
,and thus find out the optimal water use pattern under technology growth. The higher marginal output of water might create enough incentive to set off the untransferable cost since a higher allocated quota provides growth option value. As the provincial decision is under a longer horizon, there is a greater sprint effect due to higher accumulated yield and relatively tighter water use constraints over time.

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=0.7\linewidth]{Fig3.jpg}
% \end{figure}

% \begin{fig}
% Multi-period optimization of optimal water use under technology growth

% \tiny Notes: The figure depicts the relationship of multi-period benefits of province $i$ and water use under Case 3 with technology growth. Assume F(x)=ln(1+x), N=8, P=1, C=0.5, $\beta$=0.7, g=0.2, and Q=8.
% \end{fig}

(b) Economic benefits and ``remote'' ecological costs with different discount factors

Assume that there is a high discount rate for economical benefits and a low discount rate for ecological costs, in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$, discount factor $\beta^{economy}$ and $\beta^{ecology}$ ($\beta^{economy} > \beta^{ecology}$). For simplicity, consider the following finite-period water use optimization, noting the water use of province $i$ at period $t$:

$ max \quad P \cdot ln(1+x_{i,0})-\frac{C}{N}+\beta_1^t \begin{matrix} \sum_{t=1}^T [P \cdot ln(x_{i,t}+1)]  \end{matrix} - \beta_2^t \begin{matrix} \sum_{t=1}^T [C \cdot x_{i,t}] \end{matrix}$

$s.t. \quad x_{i,t} \leq Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \quad for \quad \forall t$

We depict the relationship of multi-period net income and water use $x_{i,0}$ in different horizons in Figure 4%此处引用图片
, and thus find out the optimal water use pattern under ``remote'' ecological costs. The higher discounted ecological costs might create enough incentive to set off the untransferable cost. As the provincial decision is under a longer horizon, there is a greater sprint effect due to a higher accumulated yield.

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=0.7\linewidth]{Fig4.jpg}
% \end{figure}

% \begin{fig}
% Multi-period optimization of water use under ``remote'' ecological cost

% \tiny Notes: The figure depicts the relationship of multi-period benefits of province $i$ and water use under Case 3 with ``remote'' ecological cost. Assume F(x)=ln(1+x), N=8, P=1, C=0.5, $\beta_{economy}$=0.7, $\beta_{ecology}$=0.3, and Q=8.
% \end{fig}

\end{case_appendix}

### 2022-05-05 docs/papers/01_manuscript/01_introduction.tex
docs(appendix-S3-results-extensions): interpret changes by variables' diff ratio, finished results extension in appendix S3
BREAKING CHANGE:

@@
 Here, by abstracting changes in official documents following institutional shifts (the 87-WAS and the 98-UBR), we depicted the SES structures of the YRB from 1975 to 2008.
-Then, we use Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without the institutional shifts (\textbf{Methods} and \textit{Appendix S2}).
+Then, we use Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without the institutional shifts (\textit{\hyperref[{sec:methods}]{Methods}} and \textit{Appendix~\nameref{secS2}}).
 By further interpreting the differences of the effects in the YRB, we explored the mechanisms linking SESs structure and outcomes for a deeper understanding of institutions' role in water governance worldwide.

### 2022-05-05 docs/papers/01_manuscript/02_structures.tex
docs(appendix-S3-results-extensions): interpret changes by variables' diff ratio, finished results extension in appendix S3
BREAKING CHANGE:

@@
 % As a pioneer in water governance shifting in China, the YRB started to explore a water allocating scheme since 1970s.
-The institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among national water governance practices (\textit{Appendix}~S1).
+The institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among national water governance practices (\textit{Appendix}~\refname{secS1}).
 Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
@@
 
-We selected institutional regulatory documents on water use issued by national ministries (for validation to both watershed and regional agents) and extracted the interactions between the agents involved (\textit{Supplementary Material S2}).
+We selected institutional regulatory documents on water use issued by national ministries (for validation to both watershed and regional agents) and extracted the interactions between the agents involved (\textit{Appendix \nameref{secS1}}).
 Before 1987, the YRCC had no links to the provinces regarding water use, and the provinces could link to the Yellow River reaches directly (Figure~\ref{structure}).
@@
 		Institutional shifts and related SES structures in the Yellow River Basin (YRB).
-		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{Appendix S1} Table~\ref{tab:quota}).
+		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{Appendix \nameref{secS1}} Table~\ref{tab:quota}).
 The national administrations are the ultimate authority in issuing water governance policies, which are often implemented by basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.

### 2022-05-05 docs/papers/01_manuscript/03_results.tex
docs(appendix-S3-results-extensions): interpret changes by variables' diff ratio, finished results extension in appendix S3
BREAKING CHANGE:

@@
 By contrast, after the 98-UBR, except Shanxi (whose water quota has always been far abundant over its actual water use since the 87-WAS) had an evident ($17.53\%$) increase in water use, almost all provinces have seen evident declines in water use ($-12.5\%$ on average).
-Furthermore, the regulated water use of provinces was not correlated (partial correlation coefficient is $-0.03$, $p>0.1$) with their water use from the Yellow River in proportions.
+Furthermore, the regulated water use of provinces was irrelevant (partial correlation coefficient is $-0.03$, $p>0.1$) with their water use from the Yellow River in proportions.
 

### 2022-05-05 docs/papers/01_manuscript/04_discussion.tex
docs(appendix-S3-results-extensions): interpret changes by variables' diff ratio, finished results extension in appendix S3
BREAKING CHANGE:

@@
 In addition to quantitatively demonstrating the regulatory effect of 98-UBR by previous studies, our study also found that 87-WAS would increase overall water use of the YRB.
-The results challenged the previous analyses suggesting that the 87-WAS ``has little effect'' because the difference between prediction and observation will be trivial when the institutional shift was just a blank policy by applying the DSC method.
-%!
-(cites)
-Fixing the environmental background, the forecast by DSC takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textit{S2 in Supplementary Material}).
-As the accumulations of economy volume (GDP in different sectors) in the YRB maintained a parallel trend with other regions throughout (\textit{Appendix S3} Figure~\ref{S3-1}), differences after the institutional shifts suggest water use changing per unit of production, especially in agriculture (\textit{S3 in Supplementary Material} Figure~\ref{S3-2}).
-This fact is in line with the sigh from then: although the key to alleviating the drought is saving water in the irrigated areas, the tragedy of frequently scrambling for water appeared in some provinces %!
-\cite{mao2000}.
-Since the 98-UBR improved tragedy of water competition greatly, many studies attributed the restoration from river depletion mainly to the successful institutional shift.
+The results challenged the previous analyses (who suggested that the 87-WAS ``has little effect'') because the difference between prediction and observation will be trivial when the institutional shift was just a blank policy by applying the DSC method \cite{abadie2015,hill2021}.
+Fixing the environmental background, the forecast by DSC takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textbf{methods} and \textit{Appendix~\nameref{secS2}}).
+After 87-WAS, the growth of economic volume (both in agriculture, industry and services) in the YRB broke the parallel trend with other regions since 1975 (\textit{Appendix S3} Figure~\ref{fig:variables}), though domestics water and environmental context remained their trends.
+Furthermore, construction of water-saving facilities (especially in agriculture) after the 87-WAS may contribute to the water use changing per unit of production (\textit{Appendix~\nameref{secS3}}~Figure~\ref{fig:variables}).
+These facts of saving water and speeding up water use simultaneously, are in line with the sigh from then: the tragedy of frequently scrambling for water appeared in some provinces \cite{mao2000}.
+Since the 98-UBR improved tragedy of water competition greatly by water licences, therefore, many studies attributed the restoration from river depletion mainly to the successful institutional shift \cite{chen2021,huangang2002,an2007}.
 
 % 过去的研究总结出87-WAS收效甚微的几个因素：
-Although previous studies summarised reasons for the non-ideal effect of 87-WAS, few improvements in the 98-UBR indicate that they underestimated influences from the structural changes (\textit{Appendix S3} Figure~\ref{fig:S3-3}).
-As we have depicted (Figure~\ref{structure}), the institutional shifts twice framed the structure of SESs in the YRB and led to different building blocks, which were also reported in various types of SESs worldwide.
-The empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
-\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
+Although previous studies summarised reasons for the non-ideal effect of 87-WAS \cite{huangang2002}, few chanegs of those aspects in the 98-UBR indicate that influences from the structural changes were underestimated.
+As we have depicted in Figure~\ref{structure}, the institutional shifts twice framed the structure of SESs in the YRB and led to different building blocks, which were also reported in various types of SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}.
+The empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
 On the contrary, the YRCC, whose authority matched the YRB in scale after the 98-UBR, led to a well-recognized structure for institutional alignments to social-ecological fit and good outcomes.
@@
 
-% \subsection{LINKING STRUCTURES WITH ISS OUTCOMES}
 % \subsection{Linking structures with ISs outcomes}
@@
 % 经济模型与理论解释
-% Differences between stakeholders in responses to institutional shifts are vital to understanding the mechanism between structures and outcomes.
 Differences in the pattern of the response by provinces can demonstrate the influence of social-ecological structures led by the institutional shifts.
-We analyzed mathematically why the mismatched structure made limited water use holistically elusive in the institution shift of the 87-WAS but finally achieved by the 98-UBR (\textit{method} and \textit{Supplementary Material S4}).
+We analyzed mathematically why the mismatched structure made limited water use holistically elusive in the institution shift of the 87-WAS but finally achieved by the 98-UBR (Figure~\ref{fig:model} and \textit{Appendix S4}).
 By taking the structure before and after the two institutional shifts as different basic assumptions (before 87-WAS: free access to water; after 87-WAS but before 98-UBR: decisions on water use under quotas; after 98-UBR: unified regulation), we use the marginal benefit model to analyze the theoretical optimal water consumption of stakeholders in each scenario.
@@
 Before the 98-UBR, the model assumes that the separated ecological units (river reaches) link to stakeholders (related provinces) who use water to pursue their marginal benefits but have a potential political cost if they exceed the quota 87-WAS.
-Our model suggests that for users who are already economically efficient (who are already using more water), greater marginal returns from water induce the acceleration of extracting resources for future economic growth (\textit{Supplementary Material S4}).
+Our model suggests that for users who are already economically efficient (who are already using more water), greater marginal returns from water induce the acceleration of extracting resources for future economic growth (\textit{Appendix~\nameref{secS4}}).
 Therefore, isolated stakeholders reacted to the similar marginal cost, and smaller water users have a threshold because of the political cost, so 87-WAS triggered an increased water use for the significant users.
-On the contrary, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs holistically as stakeholders only take corresponding responsibilities (follow the quota as possible as they can) to the YRCC (\textit{Supplementary Material S4}).
+On the contrary, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs holistically as stakeholders only take corresponding responsibilities (follow the quota as possible as they can) to the YRCC (\textit{Appendix~\nameref{secS4}}).
 As a result, unified regulating acted the core role after the 98-UBR and reduced water use of all stakeholders (provinces) by irregular ratios.
@@
 % 未来的政策建议
-Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions to sustainability (see \textit{Supplementary Material S1}) \cite{yu2019}.
+Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions to sustainability (see \textit{Appendix \nameref{secS1}}) \cite{yu2019}.
 Given recent changes in the YRB, outdated and inflexible water quota can no longer meet the new demands of economic development \cite{wang2019a}.
-As a result, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{Supplementary Material S1}).
+As a result, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{Appendix~\nameref{secS1}}).
 These initiatives can benefit from our analysis by actively incorporating social-ecological matched building blocks when developing a new institutional shift toward sustainability.

### 2022-05-05 docs/papers/02_appendix/02_method_details.tex
docs(appendix-S3-results-extensions): interpret changes by variables' diff ratio, finished results extension in appendix S3
BREAKING CHANGE:

@@
 
-To quantify and interpret the institutional effects, we followed the technical route illustrated in \textit{Supplementary Material Figure~\ref{fig:roadmap}}. It was a two-step process in which we
-% 基于数据使用合成控制法和安慰剂匹配法，创建可比的控制对照和期望（零模型）来分析制度变化对用水产生的影响。
-(i) created a comparable control group and an expectation (a “null model”) to analyze the impact of the institutional shifts on water use by using synthetic control and placebo matching methods, and
-% 创建一个基于边际收益的一般经济模型，解释我们发现的“冲刺效应”，并设计情景来进一步分析。
-(ii) created a general economic model based on marginal revenue to explain the “sprint effect” we observed and designed scenarios for further analysis.
-
-\begin{figure}[!hbt]
-    \centering
-    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/roadmap}
-    \caption{
-        Technical roadmap for quantitatively analyzing the “sprint effect”. WU is the the core variable we concerned -total water uses of the Yellow River Basin.
-    }
-    \label{fig:roadmap}
-\end{figure}
-
 % 为了使用合成控制法预测没有制度变化下的用水变化趋势，需要使用影响用水的社会经济数据作为自变量输入。
-In order to use the synthetic control method to predict the trend of water use without institutional change, socioeconomic data affecting water use were used as the input independent variables (see the \textit{Methods in the main text}).
+In order to use the synthetic control method to predict the trend of water use without institutional change, socioeconomic data affecting water use were used as the input independent variables.
 All variables used are listed in Table~\ref{tab:variables}.
@@
 Results show that the goodness of fit $R^2$ exceeded $0.8$; thus, the dependent variable is well-explained by the linear combination of independent variables, and the dataset can be used in the synthetic control method (Figure~\ref{fig:linear}B).
-% 为了估计用水量变化的期望值，我们对黄河流域各省用各自变量最接近的三个其它省（最近邻法）匹配了一个用作安慰剂实验的数据集
-To estimate the expected water use changes, we used the placebo test method as a null model (see the \textit{Methods}), which gives a comparable baseline for matched datasets.
-% 从图可以看出，匹配的数据集无论是数值还是变化趋势都与实际数据相似。
-Figure~\ref{fig:placebo} indicates that the matched dataset is similar to the actual data both in values and change trends.
-This means that the differences between the predictions made from actual data and from the matched data by the synthetic control method are more likely to be result of the impacts of institutional shifts.
 
@@
 \end{figure}
-
-\begin{figure}[!thb]
-	\centering
-	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/compared_placebo}
-	\caption{
-		\textbf{A.} A comparison of the matched placebo dataset and the actual YRB dataset for each province.
-		\textbf{B.} Trend of total water use $(10^8 m^3)$ for the matched placebo and actual datasets.
-	}
-\label{fig:placebo}
-\end{figure}

### 2022-05-05 docs/papers/02_appendix/03_results_appendix.tex
docs(appendix-S3-results-extensions): interpret changes by variables' diff ratio, finished results extension in appendix S3
BREAKING CHANGE:

@@
 
+The Differenced Synthetic Control (DSC) method estimates water use $y'$ by assuming that the control group (provinces out of the YRB) and experiment group (provinces in the YRB) keep their changing trends after an institutional shift in $t_0$, i.e., $f_{t<t_0}(X) = f_{t>t_0}(X)$.
+Therefore, when comparing the actual water use $y$ and the estimated water use $y'$ after institutional shifts, if $y'_{t<t_0} \approx y_{t<t_0}$ but $y'_{t>t_0} \neq y_{t>t_0}$), there are two cases: (1) changing trends of independent variables $X$ are different between control groups and experiment groups; (2) functions of variables are different between pre- and post- institutional shift periods i.e., $f_{t<t_0}(X) \neq f_{t>t_0}(X)$.
+Corresponding to the problem of this study, they mean: (1) Institutional shift changes the trend of independent variables (environment, economy, technology); (2) Institutional shift makes difference of water use caused by the change of unit independent variable combination different.
+
+In practice, both two factors may contribute simultaneously.
+Here, we analyze the differences between the YRB (affecting the actual water consumption) and other provinces (used by DSC generating synthetic control group) for the representative independent variables in each category of Table~\ref{tab:variables} by calculating their differences in ratio $Diff_{ratio}$:
+
+\begin{equation}
+    Diff_{ratio} = \frac{\vec{var}^{YRB}_{t} - \vec{var}^{others}_{t}}{\frac{1}{T} * \sum_{t}^T (var^{YRB}_{t} - var^{others}_{t})}
+\end{equation}
+
+where $\vec{var}$ is a vector of specific independent variable in $X_{t, var}$, $t\in [1975, 2008]$.
+
+For the first case, in terms of environmental factors, the differences between provinces in the YRB and other Chinese provinces has not changed significantly throughout (i.e., kept parallel, Figure~\ref{fig:variables} A and B).
+However, the economic factors (both in agriculture, industry, and services) had significant changes after the first institutional shift (the 87-WAS) (Figure~\ref{fig:variables}~C, D and E), but not in population (Figure~\ref{fig:variables}~F).
+
+% 对第二种情况
+For the second case, since the production functions of water use are mainly dependent on its efficiency, which influenced by water-saving facilities a lot, we analyze the differences between water conservation infrastructures (WCI) ratio and industrial water recycling (IWR) ratio.
+While an abruptly changing trend occurred after the 87-WAS for WCI, ratio of IWR rised its differences between the YRB provinces and other provinces (without abrupt change) until the 98-UBR (Figure~\ref{fig:variables}~G and H).
+
+As results, the differences between the DSC estimated YRB's water use and its actual water use are contributed by both abrupt changes of independent variables and functions.
+Furthermore, the economic variables (agriculture, industry, and services) contributed much more rather than environmental variables or population.
+
 \begin{figure*}
-    \includegraphics[width=0.7\linewidth]{outputs/economy.pdf}
+    \includegraphics[width=0.9\linewidth]{outputs/variables.pdf}
     \centering
-    \caption{test}
-    \label{S3-1}
+    \caption{Differences ratio of different variables: \textbf{A.} precipitation, \textbf{B.} temperature, \textbf{C.} total irrigated areas, \textbf{D.} industrial gross value added (industrial GVA), \textbf{E.} services GVA, \textbf{F.} population, \textbf{G.} water conservation irrigation (WCI) ratio, and \textbf{H.} industrial water recycling (IWR) ratio.}
+    \label{fig:variables}
 \end{figure*}
 
-\begin{figure*}
-    \includegraphics[width=0.7\linewidth]{outputs/S3_WUI.pdf}
-    \centering
-    \caption{test}
-    \label{S3-2}
-\end{figure*}
+% \begin{figure*}
+%     \includegraphics[width=0.9\linewidth]{outputs/economy.pdf}
+%     \centering
+%     \caption{Double mass curve of Gross Domestic Product (GDP) in the YRB provinces and other provinces in \textbf{A.} Agriculture, \textbf{B.} industry, \textbf{C.} services and \textbf{D.} average GDP per capita.}
+%     \label{fig:variables}
+% \end{figure*}
 
-\begin{figure*}
-    \includegraphics[width=0.7\linewidth]{outputs/S3_wci.pdf}
-    \centering
-    \caption{test}
-    \label{S3-3}
-\end{figure*}
+% \begin{figure}
+%     \includegraphics[width=0.7\linewidth]{outputs/S3_WUI.pdf}
+%     \centering
+%     \caption{Water use intensity differences in \textbf{A.} agriculture and \textbf{B.} industry between the YRB provinces and other provinces in China.}
+%     \label{S3-2}
+% \end{figure}
+
+% \begin{figure*}
+%     \includegraphics[width=0.7\linewidth]{outputs/S3_wci.pdf}
+%     \centering
+%     \caption{Ratio of irrigated area with water-saving equipments (drip irrigation, pipe irrigation, channel hardening) to the total irrigated area in the YRB provinces and other provinces in China.}
+%     \label{S3-3}
+% \end{figure*}

### 2022-05-07 docs/papers/01_manuscript/01_introduction.tex
docs(appendix): finish appendix (introduction of institutional shifts, detailed methods, economic model, model extension)
BREAKING CHANGE:

--- 2022-05-04 docs/papers/01_manuscript/01_introduction.tex
@@
 Here, by abstracting changes in official documents following institutional shifts (the 87-WAS and the 98-UBR), we depicted the SES structures of the YRB from 1975 to 2008.
-Then, we use Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without the institutional shifts (\textbf{Methods} and \textit{Appendix S2}).
+Then, we use Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without the institutional shifts (\textit{\hyperref[{sec:methods}]{Methods}} and \textit{Appendix~\nameref{secS3}}).
 By further interpreting the differences of the effects in the YRB, we explored the mechanisms linking SESs structure and outcomes for a deeper understanding of institutions' role in water governance worldwide.

### 2022-05-07 docs/papers/01_manuscript/02_structures.tex
docs(appendix): finish appendix (introduction of institutional shifts, detailed methods, economic model, model extension)
BREAKING CHANGE:

@@
 % As a pioneer in water governance shifting in China, the YRB started to explore a water allocating scheme since 1970s.
-The institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among national water governance practices (\textit{Appendix}~\refname{secS1}).
+The institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among national water governance practices (\textit{Appendix}~\nameref{secS1}).
 Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
@@
 
-\begin{figure*}[!h]
+\begin{figure*}[!htb]
     \includegraphics[width=\linewidth]{diagrams/diagram.pdf}
@@
 and Gro.'), through systematic socio-hydrological processes within the YRB.
-		\textbf{C.} Institutional shifts and following structures changes (details in \textit{Appendix S1}).
+		\textbf{C.} Institutional shifts and following structures changes (details in \textit{Appendix \nameref{secS1}}).
 (1) From 1975 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from connected ecological unit (the reach of Yellow River, denoted by the blue circles).

### 2022-05-07 docs/papers/01_manuscript/04_discussion.tex
docs(appendix): finish appendix (introduction of institutional shifts, detailed methods, economic model, model extension)
BREAKING CHANGE:

@@
 The results challenged the previous analyses (who suggested that the 87-WAS ``has little effect'') because the difference between prediction and observation will be trivial when the institutional shift was just a blank policy by applying the DSC method \cite{abadie2015,hill2021}.
-Fixing the environmental background, the forecast by DSC takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textbf{methods} and \textit{Appendix~\nameref{secS2}}).
+Fixing the environmental background, the forecast by DSC takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textbf{methods} and \textit{Appendix~\nameref{secS3}}).
 After 87-WAS, the growth of economic volume (both in agriculture, industry and services) in the YRB broke the parallel trend with other regions since 1975 (\textit{Appendix S3} Figure~\ref{fig:variables}), though domestics water and environmental context remained their trends.
@@
 Differences in the pattern of the response by provinces can demonstrate the influence of social-ecological structures led by the institutional shifts.
-We analyzed mathematically why the mismatched structure made limited water use holistically elusive in the institution shift of the 87-WAS but finally achieved by the 98-UBR (Figure~\ref{fig:model} and \textit{Appendix S4}).
-By taking the structure before and after the two institutional shifts as different basic assumptions (before 87-WAS: free access to water; after 87-WAS but before 98-UBR: decisions on water use under quotas; after 98-UBR: unified regulation), we use the marginal benefit model to analyze the theoretical optimal water consumption of stakeholders in each scenario.
-The analysis of the model also shows that 98-UBR can reduce the overall water use of the basin while 87-WAS can increase the water use of the basin when the same parameters are guaranteed but the institutional structure changes.
+We analyzed mathematically why the mismatched structure made limited water use holistically elusive in the institution shift of the 87-WAS but finally achieved by the 98-UBR (see \refname{sec:model}~Figure~\ref{fig:model}).
+By taking the structure before and after the two institutional shifts as different basic assumptions (before 87-WAS: free access to water; after 87-WAS but before 98-UBR: decisions on water use under quotas; after 98-UBR: unified regulation), we use the marginal benefit model to analyze the theoretical optimal water consumption of stakeholders in each case (detailed derivation in \textit{Appendix~\nameref{secS4}}).
+The analysis of the model also shows that 98-UBR can reduce the overall water use of the basin while 87-WAS can increase the water use of the basin when the same parameters are guaranteed but the institutional structure changes (Figure~\ref{fig:model}~A).
 Before the 98-UBR, the model assumes that the separated ecological units (river reaches) link to stakeholders (related provinces) who use water to pursue their marginal benefits but have a potential political cost if they exceed the quota 87-WAS.
@@
 As a result, unified regulating acted the core role after the 98-UBR and reduced water use of all stakeholders (provinces) by irregular ratios.
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=0.9\linewidth]{outputs/economic_model.pdf}
+	\caption{
+		\textbf{A.} The relationship of marginal benefits and water use of province $i$ at $t = 0$ for three different cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{structure}, assuming $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, and $\beta=0.4$ as an example (see \textit{\nameref{sec:model}} The horizontal coordinate of each intersection of marginal benefits and the break-even line represents the optimal water use under each case.}
+		% \textbf{Panel B.} The relation between optimal water use of province $i$ and total quota for Case 3, under time horizon of $T=5$, $T=10$, and an infinite $T$, respectively.
+The settings are the same as the panel \textbf{A}.
+	\label{fig:model}
+\end{figure}
 

### 2022-05-07 docs/papers/01_manuscript/06_methods.tex
docs(appendix): finish appendix (introduction of institutional shifts, detailed methods, economic model, model extension)
BREAKING CHANGE:

@@
 We first abstract the SES structures of water using in the YRB from 1975 to 2008, where two institutional shifts split the period into three pieces.
-We then estimated the net effects of two institutional shifts on total water uses, changing trends, and differences of the YRB's provinces, by Differenced Synthetic Control (DSC) method \cite{arkhangelsky2019}.
+We then estimated the net effects of two institutional shifts on total water uses, changing trends, and differences of the YRB's provinces, by Differenced Synthetic Control (DSC) method \cite{arkhangelsky2021}.
 Finally, for discussion, we created an economic model based on marginal revenue to provide a theoretical interpretation for the observed water use outcomes.
@@
 % 制度结构关系抽象
-% Because institutions may shape the structure of SESs, describing institutional structure is a first step toward understanding the mechanisms linking structures and outcomes in SESs (Figure~\ref{framework} A).
-% For example, institutions may create a structure that encourages collaboration between the different actors managing connected ecological components (Figure~\ref{framework} B), leading to sustainable outcomes.
-% Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating horizontal relationships (Figure~\ref{framework} C and D).
-% Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures, and a network model is a widely used way to depict them by abstracting links and nodes.
+We apply network approach to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), govern unit (the YRCC) into general building blocks (or motifs) (see Figure~\ref{framework}), from the official documents.
+For example, institutions may create a horizontal connected structure that encourages collaboration between the different stakeholders managing ecological components (Figure~\ref{framework} c).
+Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating through the higher-level governing node (Figure~\ref{framework} d).
+Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures, and a network-based description is a widely used way to depict them by abstracting links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.
+In this study, we examined the official documents of the two institutional shifts of concern (87-WAS and 98-UBR, see \textit{Appendix \nameref{secS1}} for details), in which the agents are abstracted as nodes and the required interactions between agents are abstracted as links.
+The resulting structure is mainly used to inference the mechanism of institutional impact in the discussion, and to give an overview understanding of the institutional shifts.
+We try to approve that focusing on SES structures rather than institutional details, can well interpret the differences caused by institutional shifts in the YRB, and keeps consistent with previous studies theoretically.
 
 \subsection{Differenced Synthetic Control}
-Synthetic control is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadie2010, abadie2015, hill2021}.
-In this study, we used a comparative event approach and compared actual post-institutional shift induced water use changes with an appropriate counterfactual of what the water use change would have been.
-The counterfactual was built as the optimally weighted average of provinces not exposed to the institutional shifts.
-The synthetic control method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity \cite{billmeier2013, smith2015}.
-In practice, each of the units (i.e., provinces) in the treated group were affected by institutional shifts in 1987 and 1998, each of which was taken as the “shifted” point $t_0$ and the two steady institutions as $t$ for analyzing in each shift.
-The synthetic control method generates the control unit by assigning a weight matrix $W$ to units of the potential control group, so that the treated unit and its control unit are similar in each variable before $t_0$, i.e.,
+We estimate water use without institutional shifts effect by using the Differenced Synthetic Control (DSC) method.
+The DSC method is a improved version of the Synthetic Control, an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadie2010, abadie2015, hill2021}.
+This method assumes that the outcome of the treated unit can be explained in terms of a set of control units that were themselves not affected by the intervention (i.e., institutional shifts here).
+By using data-driven weights to balance pre-treatment outcomes for treated and control units, the DSC method imputes post-treatment control outcomes for the treated unit(s) by constructing a synthetic version of the treated unit(s) equal to a convex combination of control units with a new estimator with improved bias properties.
 
-$$\min(V_{i}^{t<t_0} - W_i * F_{control}^{t<t_0})$$
+In practice, each of the units (i.e., provinces) in the treated group were affected by institutional shifts in 1987 and 1998, each of which was taken as the ``shifted'' time $t_0$ within two individually analyzed periods $T$: 1975-1998; 1987-2008.
+Including each province in the YRB ($n=8$, see \textit{\nameref{sec:dataset}}) as the only treated unit, we consider the $J+1$ units observed in time periods $T = {1,2 \cdots , T}$ with the remaining $J=20$ units are untreated provinces from outside.
+We define $T_0$ to represent the number of pre-treatment periods ($1,\cdots,t_0$) and $T_1$ the number post-treatment periods ($t_0,\cdots,T$), such that $T = T_0+ T_1$.
+That is, treated unit is exposed to the institutional shift in every post-treatment period $T_0$, and unaffected by the institutional shift in all preceding periods $T_1$.
+Then, any weighted average of the control units is a synthetic control and can be represented by a ($J * 1$) vector of weights $\mathbf{W} = (w_{1},...,w_{J})$, with $w_j \in (0, 1)$.
+Among them, by introduce a ($k * k$) diagonal, semidefinite matrix $\mathbf{V}$ that signifies the relative importance of each covariate, the DSC method procedure for finding the optimal synthetic control ($W$) is expressed as follows:
 
-where $V_i$ is a vector that indicates all features of a unit $i$ of the treated group, and $F_{control}$ is a matrix that consists of all features and units of the potential control group.
-$W_i$ is the weight matrix for target unit $i$.
-We minimized the root mean square error (RMSE) by using the SyntheticControl package in python3.
-All codes are accessible in the repository.
+\begin{equation}
+    \mathbf{W^{*}(V)}=\underset{\mathbf{W} \in \mathcal{W}}{\operatorname{minimize}}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)^{\prime} \mathbf{V}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)
+\end{equation}
 
-% 这样一来，基于降维的思想，我们构建出了一系列特征上与实验组最为接近的可比对照。
-In accordance with the idea of dimensionality reduction, we constructed a series of comparable control units that were most similar in characteristics to the treated units.
-Because the units of the control group were not affected by the institutional shifts, after giving the same weight to the total water use of the control group $M_i * WU_{control}$, the result $W_i*WU_{control}$ could be considered a reasonable estimation of the untreated situation.
-The net effect of the water allocation institutional shift was then estimated by calculating the difference of water uses after the institutional shift between the treated group and the control group, compared with the water use difference before the shift.
+where $\mathbf{W}^{*}(V)$ is the vector of weights $\mathbf{W}$ that minimizes the difference between the pre-treatment characteristics of the treated unit and the synthetic control, given $\mathbf{V}$.
+That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W*(V)}$.
+We choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{W*(V)}$ that minimizes the following expression:
 
-\subsection{Dataset and variables}
-% 我们使用中国1978年至2012年各省的年度用水量数据集，这个公开的数据集由全国水资源利用调查得到，详细可查看。
-We used China’s provincial annual water consumption dataset from 1978 to 2012.
-This publicly available dataset was obtained from the National Water Resources Utilization Survey; details are accessible from Zhou (2020) \cite{zhou2020}.
-A total of 10 provinces or regions have been directly affected by the water allocation institutional shifts in the YRB, accounting for $8.6\%$ of the total population of China (in 1990).
-Eight provinces have been particularly affected because of their greater dependence on the water resources from the Yellow River (see \textit{Supplementary Material S2}).
-Therefore, we divided the dataset into a “target group” and a “control group”, treating provinces that were greatly affected as the target group $(n=8)$ and provinces that were not affected by the institutional shifts as the potential control group $(n=20)$.
+\begin{equation}
+    \mathbf{V}^{*}=\underset{\mathbf{V} \in \mathcal{V}}{\operatorname{argmin}}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)^{\prime}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)
+\end{equation}
 
-We focused on total water use in the YRB.
-The actual water uses are given by the dataset, but when the synthetic control method is used to predict the water use of the control group, other independent influences need to be considered.
-Thus, we used economic features that are highly related to water use to extrapolate demand (e.g., agriculture, industry, service industry, and domestics, see \textit{Supplementary Material S2, Table 1}
+That is the minimum difference between the outcome of the treated unit and the synthetic control in the pre-treatment period, where $\mathbf{Z}_{1}$ is a ($1*T_0$) matrix containing every observation of the outcome for the treated unit in the pre-treatment period.
+Similarly, let $\mathbf{Z}_{0}$ is a ($k * T_0$) matrix containing the outcome for each control unit in the pre-treatment period, $k$ is number of variables in the datasets.
+The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with double robustness properties \cite{billmeier2013, smith2015}.
 
-\subsection{Economic model}
-In order to understand the mechanisms underlying the empirical results, we developed a dynamic economic model to analyze how institutional change could have led to the sprint effect in water use.
-Specifically, we modeled individual provincial decision-making in water resources before quota execution.
-The analysis result implied that the underlying driver of CPR overuse was incentive distortion.
+\subsection{Dataset and variables}\label{sec:dataset}
+In this study, we aim to compare on actural and estimated water use of the YRB.
+The actual water uses are accessible in China’s provincial annual water consumption dataset from the National Water Resources Utilization Survey, whose details are accessible from Zhou (2020) \cite{zhou2020}.
+To estimate the water use of the YRB by assuming there were not effects from institutional shifts, we focused on variables from five categories (environmental, economic, domestic, and technological) water use factors.
+Their specific items and origins are listed in Table~\ref{tab:variables}.
 
-In developing the model, we highlighted the main features of the YRB, as well as the water use institutions of 1987 and 1998. We proposed three intuitive and general assumptions.
+Among the total $31$ data-accessible provinces (or regions) directly affected by the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin and Beijing because they influenced by the institutions, but trivial in their water use (see \textit{Appendix}~Table~\ref{tab:quota}).
+We then divided the dataset into a ``target group'' and a ``control group'', treating provinces involved in water quota as the target group $(n=8)$ and other provinces as the control group $(n=20)$, for applying the DSC.
+
+\subsection{Economic model}\label{sec:model}
+In order to inference the mechanisms underlying the results, we developed a economic model based on marginal revenue to analyze how institutional shift could have led to differences in water use.
+
+\begin{ass}
+    (Water-dependent production) Because of irreplaceability, water is assumed to be the only input of the production function with two types of production efficiency.
+The production function of a high-incentive province is $A_HF(x)$, and the production function of a low-incentive province is $A_LF(x)$ ($A_H>A_L$).
+F(x) is continuous, $F'(0)=\infty$, $ F'(\infty)=0$, $F'(x)>0$, and $F''(x)<0$.
+The production output is under perfect competition, with a constant unit price of $P$.
+\end{ass}
+
+\begin{ass}
+    (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in $N$ provinces, the cost of water use is equally assigned to each province under any water use.
+The unit cost of water is a constant $C$.
+\end{ass}
+
+\begin{ass}
+    (Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water use.
+\end{ass}
+
+Under the above simplified assumptions, we can demonstrate three cases -corresponding the abstracted SES structures (Figure~\ref{structure}), inference stakeholders in a whole basin to simulate their water use patterns by optimization of marginal revenue.
+As one of the possible interpretation for the causity between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.

### 2022-05-07 docs/papers/02_appendix/02_method_details.tex
docs(appendix): finish appendix (introduction of institutional shifts, detailed methods, economic model, model extension)
BREAKING CHANGE:

@@
 
-\begin{figure}[!thb]
-	\centering
-	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/linear}
-	\caption{
-		\textbf{A.} Correlation between independent variables and the dependent variable (water use).
-		\textbf{B.} Linear relationship between the independent variables and the dependent variable trained by a linear model.
-	}
-\label{fig:linear}
-\end{figure}
+% \begin{figure}[!thb]
+% 	\centering
+% 	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/linear}
+% 	\caption{
+% 		\textbf{A.} Correlation between independent variables and the dependent variable (water use).
+% 		\textbf{B.} Linear relationship between the independent variables and the dependent variable trained by a linear model.
+% 	}
+% \label{fig:linear}
+% \end{figure}

### 2022-05-07 docs/papers/02_appendix/03_results_appendix.tex
docs(appendix): finish appendix (introduction of institutional shifts, detailed methods, economic model, model extension)
BREAKING CHANGE:

@@
 % 对第二种情况
-For the second case, since the production functions of water use are mainly dependent on its efficiency, which influenced by water-saving facilities a lot, we analyze the differences between water conservation infrastructures (WCI) ratio and industrial water recycling (IWR) ratio.
+For the second case, since water the production functions of water use are mainly dependent on its efficiency, which is influenced by water-saving facilities a lot, we analyze the differences between water conservation infrastructures (WCI) ratio and industrial water recycling (IWR) ratio.
 While an abruptly changing trend occurred after the 87-WAS for WCI, ratio of IWR rised its differences between the YRB provinces and other provinces (without abrupt change) until the 98-UBR (Figure~\ref{fig:variables}~G and H).
@@
 % \end{figure*}
+
+\begin{table*}[!ht]
+	\caption{Variables and their categories for water use predictions}
+	\scriptsize
+	\label{tab:variables}
+	\begin{tabular}{lllll}
+	\hline
+	Economic sector &
+	  Category &
+	  Unit &
+	  Description &
+	  Variables \\ \hline
+	Agriculture &
+	  Irrigation Area &
+	  thousand ha &
+	  \begin{tabular}[c]{@{}l@{}}Area equipped for irrgiation by different \\ crop:\end{tabular} &
+	  \begin{tabular}[c]{@{}l@{}}Rice, \\ Wheat, \\ Maize, \\ Fruits, \\ Others.\end{tabular} \\ \hline
+	Industry &
+	  \begin{tabular}[c]{@{}l@{}}Industrial gross \\ value added\end{tabular} &
+	  Billion Yuan &
+	  Industrial GVA by industries &
+	  \begin{tabular}[c]{@{}l@{}}Textile, \\ Papermaking, \\ Petrochemicals, \\ Metallurgy, \\ Mining, \\ Food, \\ Cements, \\ Machinery, \\ Electronics, \\ Thermal electrivity, \\ Others.\end{tabular} \\
+	 &
+	  \begin{tabular}[c]{@{}l@{}}Industrial water \\ use efficiency\end{tabular} &
+	  \% &
+	  \begin{tabular}[c]{@{}l@{}}The ratio of recycled water and evaporated \\ water to total industrial water use\end{tabular} &
+	  \begin{tabular}[c]{@{}l@{}}Ratio of industrial water recycling, \\ Ratio of industrial water evaporated.\end{tabular} \\ \hline
+	Services &
+	  \begin{tabular}[c]{@{}l@{}}Services gross \\ value added\end{tabular} &
+	  Billion Yuan &
+	  GVA of service activities &
+	  Services GVA \\ \hline
+	Domestic &
+	  Urban population &
+	  Million Capita &
+	  Population living in urban regions. &
+	  Urban pop \\
+	 &
+	  Rural population &
+	  Million Capita &
+	  Population living in rural regions. &
+	  Rural pop \\
+	 &
+	  Livestock population &
+	  Billion KJ &
+	  \begin{tabular}[c]{@{}l@{}}Livestock commodity calories summed from \\ 7 types of animal.\end{tabular} &
+	  Livestock \\ \hline
+	\end{tabular}
+\end{table*}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.9\linewidth]{diagrams/framework.jpg}
+	\caption{
+		Framework for understanding linkages between SES structures and outcomes.
+		\textbf{a.} The general framework for analyzing social-ecological systems (SESs) (adapted from Ostrom \cite{ostrom2009}).
+Institutions embedded in SESs may reshape structures by changing the interactions between core subsystems, resulting in different outcomes.
+        Three typical types of abstracted SES structures are shown as \textbf{b.}, \textbf{c.} and \textbf{d.} (adapted from Bodin, 2017)\cite{bodin2017b}.
+Red circles indicate social actors, and green ones indicate ecological components.
+Connection (ties between two ecological components), collaboration (ties between two social actors), or management (ties between a social actor and an ecological component) exist when two units are linked by gray lines.
+The gray dashed lines show aligned SES structures that are more likely to result in a desirable outcome according to empirical evidence.
+        }
+    \label{framework}
+\end{figure}

### 2022-05-07 docs/papers/02_appendix/05_model_extensions.tex
docs(appendix): finish appendix (introduction of institutional shifts, detailed methods, economic model, model extension)
BREAKING CHANGE:

@@
 
-We depict the relationship of multi-period profit and water use $x_{i,0}$ in different horizons in Figure 4%%此处引用图片
+We depict the relationship of multi-period profit and water use $x_{i,0}$ in different horizons in Figure~\ref{fig:technology}%%此处引用图片
 ,and thus find out the optimal water use pattern under technology growth.
@@
 
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=0.7\linewidth]{Fig3.jpg}
-% \end{figure}
-
-% \begin{fig}
-% Multi-period optimization of optimal water use under technology growth
-
-% \tiny Notes: The figure depicts the relationship of multi-period benefits of province $i$ and water use under Case 3 with technology growth.
-Assume F(x)=ln(1+x), N=8, P=1, C=0.5, $\beta$=0.7, g=0.2, and Q=8.
-% \end{fig}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\linewidth]{outputs/Fig3.jpg}
+    \caption{Multi-period optimization of optimal water use under technology growth.
+The figure depicts the relationship of multi-period benefits of province $i$ and water use under Case 3 with technology growth.
+Assume $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta=0.7$, $g=0.2$, and $Q=8$.}
+    \label{fig:technology}
+\end{figure}
 
@@
 
-We depict the relationship of multi-period net income and water use $x_{i,0}$ in different horizons in Figure 4%此处引用图片
+We depict the relationship of multi-period net income and water use $x_{i,0}$ in different horizons in Figure~\ref{fig:remote}%此处引用图片
 , and thus find out the optimal water use pattern under ``remote'' ecological costs.
@@
 
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[width=0.7\linewidth]{Fig4.jpg}
-% \end{figure}
-
-% \begin{fig}
-% Multi-period optimization of water use under ``remote'' ecological cost
-
-% \tiny Notes: The figure depicts the relationship of multi-period benefits of province $i$ and water use under Case 3 with ``remote'' ecological cost.
-Assume F(x)=ln(1+x), N=8, P=1, C=0.5, $\beta_{economy}$=0.7, $\beta_{ecology}$=0.3, and Q=8.
-% \end{fig}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\linewidth]{outputs/Fig4.jpg}
+    \caption{Multi-period optimization of water use under ``remote'' ecological cost.
+The figure depicts the relationship of multi-period benefits of province $i$ and water use under Case 3 with ``remote'' ecological cost.
+Assume $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta_{economy}=0.7$, $\beta_{ecology}=0.3$, and $Q=8$.}
+    \label{fig:remote}
+\end{figure}
 

### 2022-05-20 docs/papers/01_manuscript/01_introduction.tex
feat: pca analysis
BREAKING CHANGE:

@@
 % 通过抽象文件变化
-Here, by abstracting changes in official documents following institutional shifts (the 87-WAS and the 98-UBR), we depicted the SES structures of the YRB from 1975 to 2008.
+Here, by abstracting changes in official documents following institutional shifts (the 87-WAS and the 98-UBR), we depicted the SES structures of the YRB from 1979 to 2008.
 Then, we use Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without the institutional shifts (\textit{\hyperref[{sec:methods}]{Methods}} and \textit{Appendix~\nameref{secS3}}).

### 2022-05-20 docs/papers/01_manuscript/02_structures.tex
feat: pca analysis
BREAKING CHANGE:

@@
 However, the controversial scheme helped little in turning the water depletion around until another strategy attempted to strengthen the responsibilities of the YRCC in integrated water management in 1998 (the 98-UBR).
-Therefore, our analysis period spans from 1975 (emergence of river depletion) to 2008 (a further polish of the 98-UBR), with the SESs shifted between three varying institutions (Figure~\ref{structure}).
+Therefore, our analysis period spans from 1979 (emergence of river depletion) to 2008 (a further polish of the 98-UBR), with the SESs shifted between three varying institutions (Figure~\ref{structure}).
 
@@
 		\textbf{C.} Institutional shifts and following structures changes (details in \textit{Appendix \nameref{secS1}}).
-(1) From 1975 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from connected ecological unit (the reach of Yellow River, denoted by the blue circles).
+(1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from connected ecological unit (the reach of Yellow River, denoted by the blue circles).
 (2) After 1987-WAS, the YRCC (the yellow circles) was monitoring (the dot-line links) river reaches with the water use quota.

### 2022-05-20 docs/papers/01_manuscript/03_results.tex
feat: pca analysis
BREAKING CHANGE:

@@
 Our estimation of theoretical water use suggests that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without an institutional shift (Figure~\ref{main_results}A).
-From 1988 to 1998, on average, while the estimation of annual water use only suggests $956.38$ billion $m^3$, the observed water use of the YRB provinces reached $1038.36$ billion $m^3$ in sum, $8.57\%$ increased.
+From 1988 to 1998, on average, while the estimation of annual water use only suggests $974.34$ billion $m^3$, the observed water use of the YRB provinces reached $1038.36$ billion $m^3$ in sum, $6.57\%$ increased.
 However, after the institution shifted again in 1998 (98-UBR), the trend of increasing water use appeared to be effectively suppressed.
-From 1998 to 2008, the total observed water use decreased by $4.9$ billion $m^3/yr$ per year, while the estimation of water use still suggests $10.3$ billion $m^3/yr$ increases (Figure~\ref{main_results} B).
+From 1998 to 2008, the total observed water use decreased by $0.49$ billion $m^3/yr$ per year, while the estimation of water use still suggests $0.82$ billion $m^3/yr$ increases (Figure~\ref{main_results} B).
 The increased water uses after 87-WAS aligns with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{main_results}C).
@@
 During the decade after the 87-WAS, the major water-using provinces (e.g., Inner Mongolia, Henan, Shandong) had apparent accelerations (Figure~\ref{regulating}).
-The proportion of increased (or decreased) water use for each province (over the estimated water use by the model) has a significant correlation (partial correlation coefficient is $0.84$, $p<0.05$) to the actual water use from the Yellow River.
-In particular, Inner Mongolia and Shandong, both provinces that exceeded the prescribed water uses of the 87-WAS, used $44.25\%$ and $25.69\%$ more water uses than the prediction from 1987 to 1998, respectively.
-By contrast, after the 98-UBR, except Shanxi (whose water quota has always been far abundant over its actual water use since the 87-WAS) had an evident ($17.53\%$) increase in water use, almost all provinces have seen evident declines in water use ($-12.5\%$ on average).
-Furthermore, the regulated water use of provinces was irrelevant (partial correlation coefficient is $-0.03$, $p>0.1$) with their water use from the Yellow River in proportions.
+The proportion of increased (or decreased) water use for each province (over the estimated water use by the model) has a significant correlation (partial correlation coefficient is $0.77$, $p<0.05$) to the actual water use from the Yellow River.
+On everage, the major water users (Shandong, Inner Mongolia, Henan and Ningxia) used $32.14\%$ more water uses than the prediction from 1987 to 1998.
+By contrast, after the 98-UBR (from 1998 to 2008), almost all provinces have seen evident ($-16.54\%$ on average) declines in water use.
+The only exception is Inner Mongolia, whose water use throughout still exceeded the quota, but also considerably slowdown ($74.39\%$ decreased than the decade after 87-WAS) its rising.
+Furthermore, the regulated water use of provinces was irrelevant (partial correlation coefficient is $0.33$, $p>0.1$) with their water use from the Yellow River in proportions.
 

### 2022-05-20 docs/papers/01_manuscript/04_discussion.tex
feat: pca analysis
BREAKING CHANGE:

@@
 Fixing the environmental background, the forecast by DSC takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textbf{methods} and \textit{Appendix~\nameref{secS3}}).
-After 87-WAS, the growth of economic volume (both in agriculture, industry and services) in the YRB broke the parallel trend with other regions since 1975 (\textit{Appendix S3} Figure~\ref{fig:variables}), though domestics water and environmental context remained their trends.
+After 87-WAS, the growth of economic volume (both in agriculture, industry and services) in the YRB broke the parallel trend with other regions since 1979 (\textit{Appendix S3} Figure~\ref{fig:variables}), though domestics water and environmental context remained their trends.
 Furthermore, construction of water-saving facilities (especially in agriculture) after the 87-WAS may contribute to the water use changing per unit of production (\textit{Appendix~\nameref{secS3}}~Figure~\ref{fig:variables}).
@@
 As we have depicted in Figure~\ref{structure}, the institutional shifts twice framed the structure of SESs in the YRB and led to different building blocks, which were also reported in various types of SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}.
-The empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
+The empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated actors struggle with holistically maintaining interconnected ecosystems \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
 On the contrary, the YRCC, whose authority matched the YRB in scale after the 98-UBR, led to a well-recognized structure for institutional alignments to social-ecological fit and good outcomes.
@@
 The analysis of the model also shows that 98-UBR can reduce the overall water use of the basin while 87-WAS can increase the water use of the basin when the same parameters are guaranteed but the institutional structure changes (Figure~\ref{fig:model}~A).
-Before the 98-UBR, the model assumes that the separated ecological units (river reaches) link to stakeholders (related provinces) who use water to pursue their marginal benefits but have a potential political cost if they exceed the quota 87-WAS.
+Before the 98-UBR, the separated ecological units (river reaches) link to stakeholders (related provinces) who use water to pursue their benefits.
 Our model suggests that for users who are already economically efficient (who are already using more water), greater marginal returns from water induce the acceleration of extracting resources for future economic growth (\textit{Appendix~\nameref{secS4}}).
-Therefore, isolated stakeholders reacted to the similar marginal cost, and smaller water users have a threshold because of the political cost, so 87-WAS triggered an increased water use for the significant users.
+Therefore, isolated stakeholders reacted to the similar marginal cost, and smaller water users have a threshold, so 87-WAS triggered an increased water use for the significant users.
 On the contrary, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs holistically as stakeholders only take corresponding responsibilities (follow the quota as possible as they can) to the YRCC (\textit{Appendix~\nameref{secS4}}).
@@
 Since scholars have reached a consensus on the importance of the two institutional shifts of 87-WAS and 98-UBR, the differences in their results still provide important insights for understanding water governance.
+Another limitation is the contributions of different economic growth and institutional shifts are still uncomparable because of intertwined causality.
+Economic growth and changing relative variables are also contributing factors influenced by other numerous policies, but our quasi-experiments approach proved that the YRB's unique institutional shifts are followed by change of water use trajectory.
 

### 2022-05-20 docs/papers/01_manuscript/06_methods.tex
feat: pca analysis
BREAKING CHANGE:

@@
 % 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程
-We first abstract the SES structures of water using in the YRB from 1975 to 2008, where two institutional shifts split the period into three pieces.
+We first abstract the SES structures of water using in the YRB from 1979 to 2008, where two institutional shifts split the period into three pieces.
 We then estimated the net effects of two institutional shifts on total water uses, changing trends, and differences of the YRB's provinces, by Differenced Synthetic Control (DSC) method \cite{arkhangelsky2021}.
-Finally, for discussion, we created an economic model based on marginal revenue to provide a theoretical interpretation for the observed water use outcomes.
+For the stability of DSC model, we use Principal Components Analysis (PCA) method to reduce the dimensionality of many variables affecting the total water use.
+Finally, for discussion, we created an economic model based on marginal revenue to provide the observed water use changes a theoretical interpretation.
+
+% 为了DSC的模型稳定性，我们使用PCA为影响用水量的众多变量进行了降维
 
@@
 We estimate water use without institutional shifts effect by using the Differenced Synthetic Control (DSC) method.
-The DSC method is a improved version of the Synthetic Control, an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadie2010, abadie2015, hill2021}.
-This method assumes that the outcome of the treated unit can be explained in terms of a set of control units that were themselves not affected by the intervention (i.e., institutional shifts here).
-By using data-driven weights to balance pre-treatment outcomes for treated and control units, the DSC method imputes post-treatment control outcomes for the treated unit(s) by constructing a synthetic version of the treated unit(s) equal to a convex combination of control units with a new estimator with improved bias properties.
+The DSC method is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadie2010, abadie2015, hill2021}.
+This method aims to evaluate the effects of policy change that are not random across units but focus on some of the units (i.e., institutional shifts in the YRB here).
+By re-weighting units to match the pre-trend for the treated and control units, the DSC method imputes post-treatment control outcomes for the treated unit(s) by constructing a synthetic version of the treated unit(s) equal to a convex combination of control units with a new estimator with improved bias properties.
 
-In practice, each of the units (i.e., provinces) in the treated group were affected by institutional shifts in 1987 and 1998, each of which was taken as the ``shifted'' time $t_0$ within two individually analyzed periods $T$: 1975-1998; 1987-2008.
-Including each province in the YRB ($n=8$, see \textit{\nameref{sec:dataset}}) as the only treated unit, we consider the $J+1$ units observed in time periods $T = {1,2 \cdots , T}$ with the remaining $J=20$ units are untreated provinces from outside.
+In practice, each of the units (i.e., provinces) in the treated group were affected by institutional shifts in 1987 and 1998, each of which was taken as the ``shifted'' time $t_0$ within two individually analyzed periods $T$: 1979-1998; 1987-2008.
+We include each province in the YRB ($n=8$, see \textit{\nameref{sec:dataset}}) as the treated unit separately, as multiple treated units approach had been widely applied \cite{abadie2021}.
+Then, we consider the $J+1$ units observed in time periods $T = {1,2 \cdots , T}$ with the remaining $J=20$ units are untreated provinces from outside.
 We define $T_0$ to represent the number of pre-treatment periods ($1,\cdots,t_0$) and $T_1$ the number post-treatment periods ($t_0,\cdots,T$), such that $T = T_0+ T_1$.
@@
 
-\subsection{Dataset and variables}\label{sec:dataset}
-In this study, we aim to compare on actural and estimated water use of the YRB.
+\subsection{Dataset and preprocessing}\label{sec:dataset}
+We choose dataset and variables to compare on actural and estimated water use of the YRB.
 The actual water uses are accessible in China’s provincial annual water consumption dataset from the National Water Resources Utilization Survey, whose details are accessible from Zhou (2020) \cite{zhou2020}.
@@
 
-Among the total $31$ data-accessible provinces (or regions) directly affected by the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin and Beijing because they influenced by the institutions, but trivial in their water use (see \textit{Appendix}~Table~\ref{tab:quota}).
+Among the total $31$ data-accessible provinces (or regions) assigned quotas in the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin and Beijing because their trivial water use from the YRB (see \textit{Appendix}~Table~\ref{tab:quota}).
 We then divided the dataset into a ``target group'' and a ``control group'', treating provinces involved in water quota as the target group $(n=8)$ and other provinces as the control group $(n=20)$, for applying the DSC.
+
+Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ pricipal components Appendix~\nameref{secS3}.
+Bayan had proved that combining PCA and DSC can rise robustness of causal inference \cite{bayani2021}.
+Here, we first applied the Zero-Mean normalization (unit variance), as the variables' unit are far different.
+We use Elbow method to choose number of the pricipal components, as Appendix~\nameref{secS3}~Figure~\ref{fig:elbow} shows, $5$ components well reduced the dimensions of the dataset with $89.63\%$ variance explaination.
 
@@
     (Water-dependent production) Because of irreplaceability, water is assumed to be the only input of the production function with two types of production efficiency.
-The production function of a high-incentive province is $A_HF(x)$, and the production function of a low-incentive province is $A_LF(x)$ ($A_H>A_L$).
-F(x) is continuous, $F'(0)=\infty$, $ F'(\infty)=0$, $F'(x)>0$, and $F''(x)<0$.
-The production output is under perfect competition, with a constant unit price of $P$.
 \end{ass}
@@
 \begin{ass}
-    (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in $N$ provinces, the cost of water use is equally assigned to each province under any water use.
-The unit cost of water is a constant $C$.
+    (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved, the cost of water use is equally assigned to each province.
 \end{ass}
@@
 \begin{ass}
-    (Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water use.
+    (Multi-period settings) There are multiple settings periods with a constant discount factor for expectation of future water use.
 \end{ass}
 
-Under the above simplified assumptions, we can demonstrate three cases -corresponding the abstracted SES structures (Figure~\ref{structure}), inference stakeholders in a whole basin to simulate their water use patterns by optimization of marginal revenue.
-As one of the possible interpretation for the causity between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.
+Under the above simplified assumptions, we demonstrate three cases -corresponding the abstracted SES structures (Figure~\ref{structure}), inference how SES structure alters the expected marginal benefits and costs of provinces making decisions.
+As one of the possible interpretation for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.

### 2022-05-20 docs/papers/01_manuscript/manuscript.tex
docs(refactor-paper-and-fixed-according-to-comments-from-ShuaiWang-and-XutongWu): refactor paper and fix language according to the comments from ShuaiWang and XutongWu
BREAKING CHANGE: v-1.3.0
feat(results,-structures): new figure 1
feat(institution-context): appendix sec1
fix(appendix): appendix sort
docs(appendix-S3-results-extensions): interpret changes by variables' diff ratio, finished results extension in appendix S3
BREAKING CHANGE:
docs(appendix): finish appendix (introduction of institutional shifts, detailed methods, economic model, model extension)
BREAKING CHANGE:
feat: pca analysi

@@
 \usepackage{hyperref}
+% \usepackage[nofiglist,notablist]{endfloat}
 \makeatletter
 \def\uns{\ifmmode\,\else$\,$\fi}%
-\newtheorem{theorem}{Theorem}
-\newtheorem{construction}{Construction}
-\newtheorem{estimate}{Estimate}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-\newtheorem{result}{Result}
-\newtheorem{algth}{Algorithm}
-\newtheorem{proposition}{Proposition}
-\newtheorem{hypothesis}{Hypothesis}
-\newtheorem{experiment}{Experiment}
-\newtheorem{definition}{Definition}
-\newtheorem{condition}{Condition}
+\newtheorem{defn}{Definition}
+\newtheorem{thm}{Theorem}
+\newtheorem{ass}{Assumption}
+\newtheorem{prop}{Proposition}
+\newtheorem{fig}{Fig.}
+\newtheorem{case}{Case}
+\newtheorem{case_appendix}{Case}
+\newtheorem{example}{Example}[section]
+\renewcommand{\proofname}{\textbf{Proof}}
 \newtheorem{property}{Property}
-\newtheorem{problem}{Problem}
-\newtheorem{fact}{Fact}
-\newtheorem{assumption}{Assumption}
-\newtheorem{eexample}{Example}
-\newtheorem{model}{Model}
+\newtheorem{remark}{Remark}
+%\usepackage{enumerate}
+\usepackage{enumitem}
+\usepackage{float}
+\usepackage{multirow}
+\setenumerate{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=0pt}
+\setitemize{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=5pt}
+\setdescription{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=5pt}
+
+\usepackage{booktabs}
+\usepackage{diagbox}
 %%
@@
 \subhead{EARTH SCIENCES}
-\newtheorem{ass}{Assumption}   % My command. Assumptions.
-\newtheorem{case}{Case}  % My command. Cases
 
@@
 
-\author{Shuang Song$^{1,2}$}
-\author{Huiyu Wen$^3$}
-\author{*Shuai Wang$^{1,2}$}
-\author{Xutong Wu$^{1,2}$}
+\author{Shuang Song$^{1}$}
+\author{Huiyu Wen$^2$}
+\author{*Shuai Wang$^{1}$}
+\author{Xutong Wu$^{1}$}
 
-\author{Graeme S. Cumming$^{4}$}
-\author{Bojie Fu$^{1,2,5}$}
+\author{Graeme S. Cumming$^{3}$}
+\author{Bojie Fu$^{1,4}$}
 
@@
 
-\affil{$^2$Institute of Land Surface System and Sustainability,
-     Faculty of Geographical Science,
-     Beijing Normal University,
-     Beijing 100875,
-     P.R. China}
+% \affil{$^2$Institute of Land Surface System and Sustainability,
+%      Faculty of Geographical Science,
+%      Beijing Normal University,
+%      Beijing 100875,
+%      P.R. China}
 
-\affil{$^3$School of Finance,
+\affil{$^2$School of Finance,
      Renmin University of China,
@@
 
-\affil{$^4$ARC Centre of Excellence for Coral Reef Studies,
+\affil{$^3$ARC Centre of Excellence for Coral Reef Studies,
      James Cook University,
@@
 
-\affil{$^5$The research for this article was financed by.......
+\affil{$^4$The research for this article was financed by.......
 The authors thank.......
@@
 
+\section{CONCLUSION}\label{sec:conclusion}
+\input{05_conclusion.tex}
+
 \section{MATERIALS AND METHODS}\label{sec:methods}
 \input{06_methods.tex}
-
-\section{CONCLUSION}\label{sec:conclusion}
-\input{05_conclusion.tex}
 
@@
 
+\section{S1: Contexts of institutional shifts}\label{secS1}
+\input{../02_appendix/01_institution_context.tex}
+
+\section{S2: Sensitivity analysis}\label{secS2}
+\input{../02_appendix/02_method_details.tex}
+
+\section{S2: Methods in details}\label{secS3}
+\input{../02_appendix/03_results_appendix.tex}
+
+\section{S3: Optimization model for water use}\label{secS4}
+\input{../02_appendix/04_theoretical_model.tex}
+
+\section{S4: Model extensions}\label{secS5}
+\input{../02_appendix/05_model_extensions.tex}
+
 %% Put the bibliography here, most people will use BiBTeX in
@@
 %% the \bibliography{} command.
-\bibliography{../WAInstitution_YRB_2021}\label{bib}
+\bibliography{../mybib}
+\label{bib}
 \end{document}

### 2022-05-20 docs/papers/02_appendix/02_method_details.tex
feat: pca analysis
BREAKING CHANGE:

--- 2022-05-05 docs/papers/02_appendix/02_method_details.tex
@@
 
-% 为了使用合成控制法预测没有制度变化下的用水变化趋势，需要使用影响用水的社会经济数据作为自变量输入。
-In order to use the synthetic control method to predict the trend of water use without institutional change, socioeconomic data affecting water use were used as the input independent variables.
-All variables used are listed in Table~\ref{tab:variables}.
-% 这些变量涉及了省级单元在利用水资源时需要考虑的主要经济因素（农业、工业、服务业与居民生活），它们与因变量（水资源使用）的相关性如图所示。
-These variables refer to major economic factors (agriculture, industry, service industry, and domestic) that provincial units need to take into account when using water resources; their correlation coefficients with the dependent variable (water resource use) are shown in Figure~\ref{fig:linear} A.
+There are two approaches in validity testing of the DSC: (1) comparing the post- and pre- period reconstructions, (2) testing robustness through placebo analysis.
 
-% 此外，合成控制法有一个假设是自变量的线性组合可以有效预测因变量，因此我们还对数据线性拟合的效果进行了测试。
-In addition, the synthetic control method assumes that a linear combination of independent variables can effectively predict the dependent variables.
-% 将数据集区分为80%的训练样本和20%的测试样本，我们使用训练样本构建了多元线性模型对用水量进行了预测，并使用测试数据集去检验模型拟合效果。
-We therefore divided the dataset into two groups, training samples $(80\%)$ and test samples $(20\%)$, and used the training samples to build a multivariate linear model to predict the water consumption.
-We then used the test dataset to test the model-fitting effect.
-% 结果表明拟合优度R2超过了0.8，因变量可以很好的被自变量的线性组合所解释，该数据集可以用于控制合成法。
-Results show that the goodness of fit $R^2$ exceeded $0.8$; thus, the dependent variable is well-explained by the linear combination of independent variables, and the dataset can be used in the synthetic control method (Figure~\ref{fig:linear}B).
+A good synthetic control will reconstruct (a) the outcome of the treated unit and (b) the covariates of the treated unit over the pre-treatment period.
+The plots and the Root Mean Square Percentage Error (RMSPE) help us evaluate (a), this table is meant to evaluate (b).
+If the synthetic control has good fit, the following things should be true:
 
-\begin{table}[!h]
-	\caption{Variables and their categories for water use predictions}
-	\scriptsize
-	\label{tab:variables}
-	\begin{tabular}{lllll}
-	\hline
-	Economic sector &
-	  Category &
-	  Unit &
-	  Description &
-	  Variables \\ \hline
-	Agriculture &
-	  Irrigation Area &
-	  thousand ha &
-	  \begin{tabular}[c]{@{}l@{}}Area equipped for irrgiation by different \\ crop:\end{tabular} &
-	  \begin{tabular}[c]{@{}l@{}}Rice, \\ Wheat, \\ Maize, \\ Fruits, \\ Others.\end{tabular} \\ \hline
-	Industry &
-	  \begin{tabular}[c]{@{}l@{}}Industrial gross \\ value added\end{tabular} &
-	  Billion Yuan &
-	  Industrial GVA by industries &
-	  \begin{tabular}[c]{@{}l@{}}Textile, \\ Papermaking, \\ Petrochemicals, \\ Metallurgy, \\ Mining, \\ Food, \\ Cements, \\ Machinery, \\ Electronics, \\ Thermal electrivity, \\ Others.\end{tabular} \\
-	 &
-	  \begin{tabular}[c]{@{}l@{}}Industrial water \\ use efficiency\end{tabular} &
-	  \% &
-	  \begin{tabular}[c]{@{}l@{}}The ratio of recycled water and evaporated \\ water to total industrial water use\end{tabular} &
-	  \begin{tabular}[c]{@{}l@{}}Ratio of industrial water recycling, \\ Ratio of industrial water evaporated.\end{tabular} \\ \hline
-	Services &
-	  \begin{tabular}[c]{@{}l@{}}Services gross \\ value added\end{tabular} &
-	  Billion Yuan &
-	  GVA of service activities &
-	  Services GVA \\ \hline
-	Domestic &
-	  Urban population &
-	  Million Capita &
-	  Population living in urban regions. &
-	  Urban pop \\
-	 &
-	  Rural population &
-	  Million Capita &
-	  Population living in rural regions. &
-	  Rural pop \\
-	 &
-	  Livestock population &
-	  Billion KJ &
-	  \begin{tabular}[c]{@{}l@{}}Livestock commodity calories summed from \\ 7 types of animal.\end{tabular} &
-	  Livestock \\ \hline
-	\end{tabular}
-\end{table}
+Each row of the first two columns should be approximately equal. This means the synthetic control has reconstructed the treated unit values.
 
-\begin{figure}[!thb]
-	\centering
-	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/linear}
-	\caption{
-		\textbf{A.} Correlation between independent variables and the dependent variable (water use).
-		\textbf{B.} Linear relationship between the independent variables and the dependent variable trained by a linear model.
-	}
-\label{fig:linear}
-\end{figure}
+Placebo analysis is another standard approach to.

### 2022-05-20 docs/papers/02_appendix/03_results_appendix.tex
feat: pca analysis
BREAKING CHANGE:

@@
 
+\subsection*{Sensitive analysis}
+
+\subsection*{}
+
 The Differenced Synthetic Control (DSC) method estimates water use $y'$ by assuming that the control group (provinces out of the YRB) and experiment group (provinces in the YRB) keep their changing trends after an institutional shift in $t_0$, i.e., $f_{t<t_0}(X) = f_{t>t_0}(X)$.
-Therefore, when comparing the actual water use $y$ and the estimated water use $y'$ after institutional shifts, if $y'_{t<t_0} \approx y_{t<t_0}$ but $y'_{t>t_0} \neq y_{t>t_0}$), there are two cases: (1) changing trends of independent variables $X$ are different between control groups and experiment groups; (2) functions of variables are different between pre- and post- institutional shift periods i.e., $f_{t<t_0}(X) \neq f_{t>t_0}(X)$.
+Therefore, when comparing the actual water use $y$ and the estimated water use $y'$ after institutional shifts, if $y'_{t<t_0} \approx y_{t<t_0}$ but $y'_{t>t_0} \neq y_{t>t_0}$, there are two cases: (1) changing trends of independent variables $X$ are different between control groups and experiment groups; (2) functions of variables are different between pre- and post- institutional shift periods i.e., $f_{t<t_0}(X) \neq f_{t>t_0}(X)$.
 Corresponding to the problem of this study, they mean: (1) Institutional shift changes the trend of independent variables (environment, economy, technology); (2) Institutional shift makes difference of water use caused by the change of unit independent variable combination different.
@@
 
-where $\vec{var}$ is a vector of specific independent variable in $X_{t, var}$, $t\in [1975, 2008]$.
+where $\vec{var}$ is a vector of specific independent variable in $X_{t, var}$, $t\in [1979, 2008]$.
 
@@
     \label{fig:variables}
+\end{figure*}
+
+\begin{figure*}
+    \includegraphics[width=0.9\linewidth]{outputs/elbow.pdf}
+    \centering
+    \caption{Choose number of pricipal components by Elbow method, $5$ pricipal components already capture $89.63\%$ explained variance.}
+    \label{fig:elbow}
 \end{figure*}

### 2022-05-20 docs/papers/02_appendix/04_theoretical_model.tex
docs(appendix): finish appendix (introduction of institutional shifts, detailed methods, economic model, model extension)
BREAKING CHANGE:
feat: pca analysis
BREAKING CHANGE:

@@
 
-In order to understand the mechanisms underlying the empirical results, we developed a dynamic economic model to analyze how institutional mismatch could have led to the sprint effect in water use, especially among provinces with high incentives for excess water use.
+In order to understand the mechanisms through which the SES structure impacts provincial water use, we developed a dynamic economic model to analyze how institutional mismatch could have led to the changes of water use, especially among provinces with high incentives for excess water use.
 Specifically, we modeled individual provincial decision-making in water resources before quota execution.
@@
 
-Extensions of the model are shown in \textit{Appendix S5}.%%%
+Extensions of the model are shown in Supplementary Material S3.%%%
 
+%Appendix的模型和proposition推导细节部分
+%放在Appendix
+Appendix: Water Use Optimization
+
+%case1
 \begin{case_appendix}Centralized decision

### 2022-05-20 core/analysis.py

@@ -48,6 +48,7 @@ class AnalystItem(ItemBase):
         return self.is_checked
 
     def do_analysis(self, save_mode=False, *argv, **kwargs):
+        # TODO: Safe mode -- check it before do analysis.
         results = self.method.function(
             self.data.obj, self.method.parameters, *argv, **kwargs
         )
@@ -73,7 +74,7 @@ class Analyst(UnitBase):
         item.update_metadata("data", data_item.name)
         item.update_metadata("method", method_item.name)
         self.add_item(item)
-        pass
+        return item
 
     def report(self, show=True, show_notes=False, max_width=30):
         table = super().report(show=False, show_notes=show_notes)

### 2022-05-20 core/datasets.py

@@ -63,7 +63,13 @@ class Datasets(UnitBase):
             return True
 
     def add_item_from_dataframe(
-        self, data, name, category="assets", rel_path_folder="", save=False, description=""
+        self,
+        data,
+        name,
+        category="assets",
+        rel_path_folder="",
+        save=False,
+        description="",
     ):
         if not self.in_category(category):
             raise ValueError(
@@ -72,7 +78,7 @@ class Datasets(UnitBase):
         path = self.return_or_add_dir(rel_path_folder)
         abs_path = os.path.join(path, f"{name}.csv")
         if save:
-            data.to_csv(abs_path, index=False)
+            data.to_csv(abs_path)
 
         item = DataItem(
             name=name,
@@ -87,13 +93,14 @@ class Datasets(UnitBase):
         return item
 
     def add_item_from_file(
-            self,
-            rel_path,
-            name=None,
-            category="assets",
-            format='csv',
-            description="",
-            **kwargs):
+        self,
+        rel_path,
+        name=None,
+        category="assets",
+        format="csv",
+        description="",
+        **kwargs,
+    ):
         func = getattr(pd, f"read_{format}")
         path = os.path.join(self.path, rel_path)
         if os.path.isfile(path):
@@ -111,7 +118,7 @@ class Datasets(UnitBase):
             name,
             rel_path_folder=rel_path_folder,
             category=category,
-            description=description
+            description=description,
         )
         return item
 

### 2022-05-20 core/experiment.py

@@ -15,6 +15,11 @@ import yaml
 from attrs import define, field
 
 from .src.tools import send_finish_message
+from .unit_base import ItemBase, UnitBase
+
+
+class Pipeline(ItemBase):
+    pass
 
 
 @define
@@ -288,6 +293,9 @@ class Experiment(object):
             sent = send_finish_message(self.name)
             self.update(msg=f"Notification sending msg: {sent['errmsg']}.")
         return self.state
+
+    def save(self, model, notification=False):
+        pass
 
 
 if __name__ == "__main__":

### 2022-05-20 core/model.py

@@ -55,7 +55,7 @@ class Method(UnitBase):
         )
         item.update_metadata("parameters", parameters)
         self.add_item(item)
-        pass
+        return item
 
     def add_item_from_yaml(self, yaml_file):
         pass

### 2022-05-20 core/src/filter_features.py

@@ -12,6 +12,25 @@ from sklearn import preprocessing
 from statsmodels.stats.outliers_influence import variance_inflation_factor
 
 
+def check_data_align(data):
+    province_counting = data.groupby("Province").count().iloc[:, 0]
+    if not province_counting.max() == province_counting.min():
+        raise ValueError(
+            f"NOT aligned dataset: max year: {province_counting.max()} max year:{province_counting.min()}"
+        )
+    if data["Year"].unique().__len__() != province_counting.min():
+        raise ValueError()
+    return data
+
+
+def generate_pca_data(data, params):
+    features = params["features"]
+    variables = ["Province"]
+    variables.extend(features)
+    data = data[variables].dropna(how="any")
+    return data
+
+
 def fit_pca(pca_data, params):
     features = params["features"]
     n_components = params["n_components"]
@@ -25,8 +44,8 @@ def fit_pca(pca_data, params):
 
 
 def transform_features(transform_data, params, fitted_model):
-    transform_data = transform_data.dropna(how="any")
     features = params["features"]
+    transform_data = transform_data.dropna(how="any", subset=features)
     if params["normalize"]:
         scaled_features = preprocessing.scale(transform_data[features])
     else:

### 2022-05-29 docs/papers/01_manuscript/01_introduction.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

--- 2022-05-05 docs/papers/01_manuscript/01_introduction.tex
@@
 The Yellow River Basin (YRB), the fifth large river worldwide, is known for its irreplaceable role in the social-economic development of China, and thus also drastically interference by anthropogenic stress.
-Supporting $35.63\%$ irrigation and $30\%$ population with only $2.66\%$ water resources of China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today), the overburdened Yellow River dried up in consecutive years, resulting in substantial ecological, economic and social crisis (e.g., wetland shrink, agriculture reduction, and scramble for water).
+Supporting $35.63\%$ irrigation and $30\%$ population with only $2.66\%$ water resources of China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today), the overburdened Yellow River depleted in consecutive years, resulting in substantial ecological, economic and social crisis (e.g., wetland shrink, agriculture reduction, and scramble for water).
 Intense water use, accounting for about $80\%$ of Yellow River surface runoff in the 1980s, was remarked as the significant reason for the degradation.
@@
 Chinese authorities implemented several ambitious water management practices in the YRB in the last century to relieve the water stress, such as reservoir regulation, South-to-north Water Diversion Project (WDP), and Water Allocation Scheme since 1987 (87-WAS), and the Unified Basinal Regulation since 1998 (98-UBR).
-Through those efforts, ecological restoration of wetland and estuary delta in the YRB without drying up for over $20$ is widely considered a considerable river management achievement.
-Different from the engineering of WDP provides further water supply or reservoir matches water supply and demands, institutional strategies like the 87-WAS (assign water quotas for provinces in the YRB) and the 98-UBR (the provinces had to be allowed to use water by the Yellow River Conservancy Commission, YRCC) mainly focused on limiting demands of water use.
+Through those efforts, ecological restoration of wetlands and estuary delta in the YRB without drying up for over $20$ is widely considered a considerable river management achievement.
+Different from the engineering that provides further water supply, institutional strategies like the 87-WAS (assign water quotas for provinces in the YRB) and the 98-UBR (the provinces had to be allowed to use water by the Yellow River Conservancy Commission, YRCC) mainly focused on limiting demands of water use.
 Such institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human and natural system, including interplays between social actors, ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
@@
 In addition to widespread recognition of the rising importance of institutions as an approach to water sustainable use within large river basins (especially transboundary rivers like the YRB), their specific effects are still in open discussion \cite{agrawal2003, persha2011, agrawal2001}.
-Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, therefore, supporting (but do not guarantee) sustainability of SES \cite{epstein2015, wang2019d}.
+Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, therefore, supporting (but not guaranteeing) the sustainability of SES \cite{epstein2015, wang2019d}.
 Some institutional shifts have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and collaborative water governance systems in Europe \cite{green2013}).
@@
 % 通过抽象文件变化
-Here, by abstracting changes in official documents following institutional shifts (the 87-WAS and the 98-UBR), we depicted the SES structures of the YRB from 1975 to 2008.
+Here, by abstracting changes in official documents following institutional shifts (the 87-WAS and the 98-UBR), we depicted the SES structures of the YRB from 1979 to 2008.
 Then, we use Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without the institutional shifts (\textit{\hyperref[{sec:methods}]{Methods}} and \textit{Appendix~\nameref{secS2}}).

### 2022-05-29 docs/papers/01_manuscript/02_structures.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

@@
 % 制度变动综述
-% Including the national authorities, the basin management authorities, provinces, cities, and even districts, top-down institutional structures of the YRB started to evolve up to now (\textit{S1 in Supplementary Material}).
-% As a pioneer in water governance shifting in China, the YRB started to explore a water allocating scheme since 1970s.
 The institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among national water governance practices (\textit{Appendix}~\nameref{secS1}).
 Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
-As a compounded result of development, the provinces such as Shandong, Henan and Inner Mongolia used more water resources in the YRB with larger economies (primarily for irrigation agriculture).
-For shrinking water deficits, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin.
+As a compounded result of development, the provinces such as Shandong, Henan, and Inner Mongolia used more water resources in the YRB with larger economies (primarily for irrigation agriculture).
+For shrinking water deficits, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin (Table~\ref{tab:quota}).
 However, the controversial scheme helped little in turning the water depletion around until another strategy attempted to strengthen the responsibilities of the YRCC in integrated water management in 1998 (the 98-UBR).
@@
 
-We selected institutional regulatory documents on water use issued by national ministries (for validation to both watershed and regional agents) and extracted the interactions between the agents involved (\textit{Appendix \nameref{secS1}}).
+We selected institutional regulatory documents on water use issued by national ministries (for validation to both watershed and regional agents) and then extracted the interactions between the agents involved (\textit{Appendix \nameref{secS1}}).
 Before 1987, the YRCC had no links to the provinces regarding water use, and the provinces could link to the Yellow River reaches directly (Figure~\ref{structure}).
 However, according to the extracted information from the 87-WAS, the YRCC started to report water use from the provinces.
-Furthermore, information from the 98-UBR documents demonstrated that the provinces had to apply their plan for an annual water use licence instead of direct access to the Yellow River water.
+Furthermore, information from the 98-UBR documents demonstrated that the provinces had to apply their plan for an annual water use license instead of direct access to the Yellow River water.
 Thus, there have been links between the YRCC and the provinces since the strengthening responsibilities of the YRCC in 1998.
@@
 The national administrations are the ultimate authority in issuing water governance policies, which are often implemented by basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
-		\textbf{B.} Since the YRCC does not use but monitor water, the provincial administrative agencies are the major stakeholders.
-Since the 87-WAS, with surface water withdraw from the Yellow River restricted by specific quotas, each stakeholder seperatly develop by planning and using fundamental water resources.
+		\textbf{B.} Provincial administrative agencies are the major stakeholders.
+Since the 87-WAS, with surface water withdrawal from the Yellow River restricted by specific quotas, each stakeholder plan and use water resources for development.
 However, the natural hydrological processes are connected.
-Although the institutions focus mainly on the surface water (Sur.), it can also influence groundwater inside (Gro.) or water resources outside (Sur.
-and Gro.'), through systematic socio-hydrological processes within the YRB.
+Although the institutions focus mainly on surface water (Sur.), it can also influence groundwater inside (Gro.) or water resources outside (Sur.
+and Gro.') through systematic socio-hydrological processes within the YRB.
+The YRCC only monitors water withdrawals at that time.
 		\textbf{C.} Institutional shifts and following structures changes (details in \textit{Appendix \nameref{secS1}}).
-(1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from connected ecological unit (the reach of Yellow River, denoted by the blue circles).
+(1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from the connected ecological unit (the reach of Yellow River, denoted by the blue circles).
 (2) After 1987-WAS, the YRCC (the yellow circles) was monitoring (the dot-line links) river reaches with the water use quota.
-(3) Since the 98-UBR, stakeholders have to apply water use licences from the YRCC (the connections between the red and yellow circles).
+(3) Since the 98-UBR, stakeholders have to apply for water use licenses from the YRCC (the connections between the red and yellow circles).
 	}

### 2022-05-29 docs/papers/01_manuscript/03_results.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

@@
 %\subsection{REGIONAL DIFFERENCES IN RESPONSES TO INSTITUTIONAL SHIFTS}
-\subsection{Institutional effects on regulating differences}
+\subsection{Heterogeneous institutional effects}
 \label{result-3}
@@
 The proportion of increased (or decreased) water use for each province (over the estimated water use by the model) has a significant correlation (partial correlation coefficient is $0.77$, $p<0.05$) to the actual water use from the Yellow River.
-On everage, the major water users (Shandong, Inner Mongolia, Henan and Ningxia) used $32.14\%$ more water uses than the prediction from 1987 to 1998.
+On average, the major water users (Shandong, Inner Mongolia, Henan, and Ningxia) used $32.14\%$ more water use than the prediction from 1987 to 1998.
 By contrast, after the 98-UBR (from 1998 to 2008), almost all provinces have seen evident ($-16.54\%$ on average) declines in water use.
-The only exception is Inner Mongolia, whose water use throughout still exceeded the quota, but also considerably slowdown ($74.39\%$ decreased than the decade after 87-WAS) its rising.
 Furthermore, the regulated water use of provinces was irrelevant (partial correlation coefficient is $0.33$, $p>0.1$) with their water use from the Yellow River in proportions.
@@
         Regulating differences for provinces in the YRB.
-        Red and green bars denote actual water use over the estimation from the model in a decade after the institutional shift -the 87-WAS and the 98-UBR, respectively.
-        The grey bars indicate the proportions of actual water use for each province to total water use of the provinces in a decade after the institutional shift.
-        The triangles mark the water quotas assigned in the institution, scaled into ratios by the same total actual water use, too.
+        Red (the 87-WAS) and green bars (the 98-UBR) denote an increased or decreased ratio for the actual water use over the estimation from the model in a decade after the institutional shift.
+        The grey bars indicate the proportions of actual water use for each province to their total water use in a decade after the institutional shift.
+        The triangles mark the water quotas assigned in the institution, scaled into ratios by dividing by their sum, too.
     }

### 2022-05-29 docs/papers/01_manuscript/04_discussion.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

--- 2022-05-05 docs/papers/01_manuscript/04_discussion.tex
@@
 \label{discussion-1}
-% discussion-1: 主要介绍结果的意义、合理性
-In addition to quantitatively demonstrating the regulatory effect of 98-UBR by previous studies, our study also found that 87-WAS would increase overall water use of the YRB.
-The results challenged the previous analyses (who suggested that the 87-WAS ``has little effect'') because the difference between prediction and observation will be trivial when the institutional shift was just a blank policy by applying the DSC method \cite{abadie2015,hill2021}.
-Fixing the environmental background, the forecast by DSC takes economic factors into account under the assumptions that the production function between economic volume and water uses remained unchanged (\textbf{methods} and \textit{Appendix~\nameref{secS2}}).
-After 87-WAS, the growth of economic volume (both in agriculture, industry and services) in the YRB broke the parallel trend with other regions since 1975 (\textit{Appendix S3} Figure~\ref{fig:variables}), though domestics water and environmental context remained their trends.
-Furthermore, construction of water-saving facilities (especially in agriculture) after the 87-WAS may contribute to the water use changing per unit of production (\textit{Appendix~\nameref{secS3}}~Figure~\ref{fig:variables}).
-These facts of saving water and speeding up water use simultaneously, are in line with the sigh from then: the tragedy of frequently scrambling for water appeared in some provinces \cite{mao2000}.
-Since the 98-UBR improved tragedy of water competition greatly by water licences, therefore, many studies attributed the restoration from river depletion mainly to the successful institutional shift \cite{chen2021,huangang2002,an2007}.
+% discussion-1:
+% 用水量的上升、下降-结果解读
+We quantitatively demonstrated that the 98-UBR decreased, but the 87-WAS increased YRB's water use.
+The results challenged the previous analyses (they used to suggest that the 87-WAS ``has little practical effect'') because theoretically, the DSC method would show few differences between estimation and observation for a blank policy \cite{abadie2015,hill2021}.
+However, the significant net effect suggests the institutional shift (87-WAS) followed by backfired more water use even after controlling the environmental and economic variables (see \textit{Appendix~\nameref{secS2}}~Table~\ref{tab:variables}).
+The speeding up water use aligns with the sigh from then: the tragedy of frequently scrambling for water appeared in some provinces \cite{mao2000}.
+On the contrary, 98-UBR reduced the tragedy of water competition considerably by water licenses, so many studies attributed the restoration from river depletion mainly to the successful institutional shift \cite{chen2021,huangang2002,an2007}.
 
-% 过去的研究总结出87-WAS收效甚微的几个因素：
-Although previous studies summarised reasons for the non-ideal effect of 87-WAS \cite{huangang2002}, few chanegs of those aspects in the 98-UBR indicate that influences from the structural changes were underestimated.
-As we have depicted in Figure~\ref{structure}, the institutional shifts twice framed the structure of SESs in the YRB and led to different building blocks, which were also reported in various types of SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}.
-The empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
-On the contrary, the YRCC, whose authority matched the YRB in scale after the 98-UBR, led to a well-recognized structure for institutional alignments to social-ecological fit and good outcomes.
-The effect of the institutional shifts once again demonstrated that it is not easy to have a win-win situation of environment and interests in complex coupled human-nature systems \cite{hegwood2022} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.
+% 我们认为制度结构的变化是被长期忽略的重要因素
+We proposed that for these institutional shifts' divergent outcomes regarding water use, the key factors long ignored can be institutional structure changes.
+The structural building blocks we depicted in Figure~\ref{structure}, which were also reported in various types of SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}, and here twice reframed by the institutional shifts.
+Before the 98-UBR, the SES structure (i.e., fragment ecological units are linked to separate social actors) is more likely to be mismatched because isolated actors generally struggle with holistically maintaining interconnected ecosystems \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
+On the contrary, institutional alignments since the 98-UBR improved YRCC's authority in water use regulation to match the YRB in scale, thus leading to social-ecological fit and good outcomes -a ``scale-matched'' example \cite{cumming2020a,wang2019d}.
+Despite other reasons for the non-ideal effect of the 87-WAS being widely discussed \cite{huangang2002} (such as enforcement, feasibility, and equity), few radical improvements in the 98-UBR suggest an over-attention paid to non-structural impacts.
 
@@
 % discussion-2: 机制解释
-% 经济模型与理论解释
-Differences in the pattern of the response by provinces can demonstrate the influence of social-ecological structures led by the institutional shifts.
-We analyzed mathematically why the mismatched structure made limited water use holistically elusive in the institution shift of the 87-WAS but finally achieved by the 98-UBR (Figure~\ref{fig:model} and \textit{Appendix S4}).
-By taking the structure before and after the two institutional shifts as different basic assumptions (before 87-WAS: free access to water; after 87-WAS but before 98-UBR: decisions on water use under quotas; after 98-UBR: unified regulation), we use the marginal benefit model to analyze the theoretical optimal water consumption of stakeholders in each scenario.
-The analysis of the model also shows that 98-UBR can reduce the overall water use of the basin while 87-WAS can increase the water use of the basin when the same parameters are guaranteed but the institutional structure changes.
-Before the 98-UBR, the model assumes that the separated ecological units (river reaches) link to stakeholders (related provinces) who use water to pursue their marginal benefits but have a potential political cost if they exceed the quota 87-WAS.
-Our model suggests that for users who are already economically efficient (who are already using more water), greater marginal returns from water induce the acceleration of extracting resources for future economic growth (\textit{Appendix~\nameref{secS4}}).
-Therefore, isolated stakeholders reacted to the similar marginal cost, and smaller water users have a threshold because of the political cost, so 87-WAS triggered an increased water use for the significant users.
-On the contrary, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs holistically as stakeholders only take corresponding responsibilities (follow the quota as possible as they can) to the YRCC (\textit{Appendix~\nameref{secS4}}).
-As a result, unified regulating acted the core role after the 98-UBR and reduced water use of all stakeholders (provinces) by irregular ratios.
+Different individual provinces' water-use responses to the institutional shifts also support influences from SES structures.
+Our results show that the correlation between current water use and changed (increased or decreased) water use was significant after the 87-WAS.
+This ``major users use more'' pattern supports the hypothesis that separated stakeholder (individual province here) decides on linked ecological units for output maximization (water use).
+Therefore, we theoretically abstracted the structures associated with the structural changes induced and analyzed how different water allocation structures shape different outcomes.
+Assuming that water is the factor input with decreasing marginal output of each province, we discuss the marginal return and optimal water use under three different cases (analogy to Figure~\ref{structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{Appendix~\nameref{secS4}}).
+The incentive for water overuse (compared to the water quotas) in each province derives from the mismatch between the benefits and costs of water use.
+Until water-use decisions are consolidated into unified management, each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive of water use, leading to higher water use.
+Therefore, the water users with higher capability are more stimulated by institutional shifts and away from the theoretically optimal water use under the unified allocation.
+Our model interprets the results from structural perspectives: excessive water use incentive induces the acceleration of extracting resources for future economic growth, and a unified institution is indispensable for sustainable water use.
 
-The alignments of differences in institutional structures and outcomes here echo the hypothesis that successful governance of SES emerged by indirectly (or vertically) creating links between different stakeholders (in the YRB cases, through administration).
-When links The water quotas of 87-WAS (or the initial water rights) in our case studies went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
-The bargaining itself was also a process towards matches between their economic volume and water shares, as studies show that the large water users (like Shandong and Henan) need more water than their quota (in the 87-WAS) if only considering the economic equity when designing the institution.
-Furthermore, with information asymmetry between upper-level decision-makers and lower-level stakeholders in water use allocation, those with more current water use might have greater bargaining power.
-In practice, therefore, although the affected provinces may not have directly encouraged excessive resource use because of the institutional shift, they had a more considerable incentive to show their economic potential
-That aligns with the historical records that, even after the 87-WAS had already confirmed the quotas, provinces, especially water-intensive ones, challenged it by appearing to the higher central government for larger quotas.
-On the contrary, after YRCC as governing agent coordinated between stakeholders since 98-UBR, the external appeal of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment, \textit{Supplementary Material S3})
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=0.9\linewidth]{outputs/economic_model.pdf}
+	\caption{
+		\textbf{A.} The relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
+	\label{fig:model}
+\end{figure}
+
+% The effect of the institutional shifts once again demonstrated that it is not easy to have a win-win situation of environment and interests in complex coupled human-nature systems \cite{hegwood2022}, which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.
+Our above theoretical discussion also aligns with the evolution of the institutions in the YRB.
+When links The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
+The bargaining was also a process for matching their water shares to economic volume because the major water users (like Shandong and Henan) need more water than their quota (if only considering economic potentials when designing the institution) \cite{zuo2020}.
+Furthermore, those with more current water use might have greater bargaining power in water use allocation because of information asymmetry between decision-makers and stakeholders.
+Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligns with the fact that they appeared to the higher central government for larger shares \cite{wang2019a, wang2019d}.
+On the contrary, after YRCC as governing agent coordinated between stakeholders since 98-UBR, the external appeal of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)
 \cite{krieger1955, ostrom1990}.
 Then, the YRCC, the authority for approving water applications from all stakeholders, could adjust water use quotas according to the river conditions of the whole basin.
-The 98-UBR led to a structure for achieving social-ecological fits in both basins (between YRCC and the YRB) and regions (between provincial economy and their water shares).
+The 98-UBR thus led to expected institutional outcomes at a basin scale, indicating that successful governance of SES emerged by indirectly (or vertically) creating links between different stakeholders.
 
@@
 
-Matching social and ecological scales appears widespread as building blocks (or motifs) in successfully governed SES, whether in fisheries, forests, or groundwater management.
-Since the building blocks introduced by 87-WAS and 98-UBR are recurring motifs in many SES, our proposed mechanism is crucial to understanding such coupled systems.
-We explored these causal linkages between the SES structures and sustainability (outcomes) by quasi-natural experiments (the institutional shifts) of the YRB, which provides an informative case study for two main reasons.
-First, different from gradual changes following bottom-up emergence, the top-down institutional shifts induced sharp changes in SES structures in the YRB, enabling us to estimate their net effects quantitatively.
-Second, as few basins experienced such radical institutional shifts more than once, the YRB provides comparable settings for understanding the impacts of structural changes in SESs.
-However, one of the inevitable limitations of our method is that it is difficult to rule out the effects of other policies over the same time breakpoints.
-Since scholars have reached a consensus on the importance of the two institutional shifts of 87-WAS and 98-UBR, the differences in their results still provide important insights for understanding water governance.
+We explored these causal linkages between the SES structures and sustainability (outcomes) by quasi-natural experiments (the institutional shifts) of the YRB, which provides a unique case for two main reasons:
+(1) The top-down institutional shifts induced sharp changes in SES structures in the YRB, enabling us to estimate their net effects quantitatively.
+(2) Since few basins experienced such radical institutional shifts more than once, the YRB provides comparable settings for understanding the structural changes of SESs.
+
+In complex coupled human-nature systems, however, our approach also has inevitable limitations:
+(1) The contributions of economic growth and institutional shifts are still incomparable because of intertwined causality (institutional changes can also influence the relative economic variables).
+Still, our quasi-experiment approach focused on and proved that a change in water use trajectory follows the YRB's unique institutional shifts.
+(2) When applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
+However, since the analysis had agreed on the importance of the two institutional shifts of 87-WAS and 98-UBR in water governance \cite{wang2012b}, our results on their effects still provide insights for understanding water governance.
 
 % 我们的模型结果与机制探讨加深了SES结构的理解，强化了孤立利益相关者形成的结构不利于制度解决环境问题的基本认识
-Our results and discussion deepen the understanding of SES structure and strengthen the basic understanding that the mismatched structure (isolated stakeholders with the fragmentation of ecology) is not conducive to institutional solutions.
-Moreover, we report how another institutional shift contributed to successful water governance  -the subsequent success of 98-UBR has proved the importance of social-ecological fit again, theoretically and practically.
-For sustainability in the future, therefore, it is necessary to emphasize the necessity of strengthening connections between stakeholders by agents consistent with the scale of the ecological system (in this case, the basinal scale and the YRCC).
-From these starting points, several other scenarios given by a marginal benefit model (see \textit{Supplementary Material S4}) can provide plausible insights into water governance.
+Our results and discussion deepen the understanding of SES structure and strengthen the basic knowledge that the mismatched structure (isolated stakeholders with the fragmentation of ecology) is not conducive to institutional solutions \cite{bodin2017b, ostrom2009, reyers2018}.
+Moreover, we report how another structure contributed to successful governance -the subsequent success of the 98-UBR institutional shift theoretically and practically proved the importance of social-ecological fit again.
+For sustainability in the future, therefore, it is necessary to emphasize the necessity of strengthening connections between stakeholders by agents consistent with the scale of the ecological system.
+From these perspectives, we give two scenarios based on the marginal benefit model (see \textit{Appendix \nameref{secS5}}), which can inspire institutional design on how to reduce mismatches.
 For example, water rights transfers can be another way to emerge horizontal links between stakeholders that also have the potential to result in better water governance.
-In addition, the policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to respond to changing SES context.
+In addition, the policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to respond to changing SES context \cite{reyers2018}.
 
-% 未来的政策建议
+The structural building blocks that led to different outcomes are recurring motifs in global SESs, so our proposed mechanism is crucial to governing such coupled systems.
 Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions to sustainability (see \textit{Appendix \nameref{secS1}}) \cite{yu2019}.
-Given recent changes in the YRB, outdated and inflexible water quota can no longer meet the new demands of economic development \cite{wang2019a}.
-As a result, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{Appendix~\nameref{secS1}}).
-These initiatives can benefit from our analysis by actively incorporating social-ecological matched building blocks when developing a new institutional shift toward sustainability.
-Moreover, our research provides a cautionary tale of how institutions can be double-edged, while insights from the YRB can be a valuable guideline for SESs worldwide \cite{cumming2020b, muneepeerakul2017, cumming2020a, leslie2015}.
+Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development \cite{wang2019a}.
+Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{Appendix~\nameref{secS1}}).
+These initiatives can benefit from our analysis by actively incorporating social-ecological matched building blocks when developing a new institutional shift for sustainability \cite{bodin2017b}.
+Moreover, our research provides a cautionary tale of how institutions can be double-edged \cite{hegwood2022}, while insights from the YRB can be a valuable guideline for SESs worldwide \cite{muneepeerakul2017, leslie2015}.

### 2022-05-29 docs/papers/01_manuscript/05_conclusion.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

--- 2022-04-17 docs/papers/01_manuscript/05_conclusion.tex
@@
 Intense water use in one of the most anthropogenic interfered large river basins, the Yellow River Basin (YRB), once led to overburdened drying up but finally had a successful restoration by sequential water governance practices.
-Focusing on two water-demand institutions, 87-WAS and the 98-UBR, we quantitatively analyzed how institutional shifts played a role in the water governance achievement of the YRB.
-Shifting throughout different SES structures framed by them, the observed water use of the YRB provinces had an $8.57\%$ increase than expected during the decade after the 87-WAS.
-Then, water use significantly decreased by  $4.9 billion m^3$ per year since the 98-UBR, while the model still suggests a $10.3 billion m^3$ annual increase in expectation.
+Focusing on two water-demand institutions (87-WAS and the 98-UBR), we quantitatively analyzed how institutional shifts played a role in the water governance achievement of the YRB.
+Shifting throughout different SES structures framed by them, the observed water use of the YRB provinces had a $6.57\%$ increase than expected during the decade after the 87-WAS.
+Then, water use significantly decreased by $0.49$ billion $m^3$ per year since the 98-UBR, while the model still suggests a $0.82$ billion $m^3$ annual increase in expectation.
 Finally, as differences in stakeholders' response to the institutional shifts, water use rises after the 87-WAS in provinces with more water uses (e.g., Inner Mongolia, Henan, and Shandong) while shrunk in nearly all provinces after the 98-UBR.

### 2022-05-29 docs/papers/01_manuscript/06_methods.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

@@
 % 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程
-We first abstract the SES structures of water using in the YRB from 1979 to 2008, where two institutional shifts split the period into three pieces.
-We then estimated the net effects of two institutional shifts on total water uses, changing trends, and differences of the YRB's provinces, by Differenced Synthetic Control (DSC) method \cite{arkhangelsky2021}.
-For the stability of DSC model, we use Principal Components Analysis (PCA) method to reduce the dimensionality of many variables affecting the total water use.
-Finally, for discussion, we created an economic model based on marginal revenue to provide the observed water use changes a theoretical interpretation.
+We first abstract the SES structures of water used in the YRB from 1979 to 2008, where two institutional shifts split the period into three pieces.
+For preprocessing the data, we use Principal Components Analysis (PCA) method to reduce the dimensionality of variables affecting the total water use.
+We then estimated the net effects of two institutional shifts on total water use, changing trends, and differences of the YRB's provinces, by Differenced Synthetic Control (DSC) method \cite{arkhangelsky2021}.
+Finally, for discussion, we created an economic model based on marginal revenue to provide the observed pattern of water use changes with a theoretical interpretation.
 
@@
 
-\subsection{Portraying structures}
+\subsection{Portraying structures}\label{sec:structures}
 % 制度结构关系抽象
-We apply network approach to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), govern unit (the YRCC) into general building blocks (or motifs) (see Figure~\ref{framework}), from the official documents.
-For example, institutions may create a horizontal connected structure that encourages collaboration between the different stakeholders managing ecological components (Figure~\ref{framework} c).
-Similarly, institutions for vertical management may enhance multi-layered SES matching by coordinating through the higher-level governing node (Figure~\ref{framework} d).
-Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures, and a network-based description is a widely used way to depict them by abstracting links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.
-In this study, we examined the official documents of the two institutional shifts of concern (87-WAS and 98-UBR, see \textit{Appendix \nameref{secS1}} for details), in which the agents are abstracted as nodes and the required interactions between agents are abstracted as links.
-The resulting structure is mainly used to inference the mechanism of institutional impact in the discussion, and to give an overview understanding of the institutional shifts.
-We try to approve that focusing on SES structures rather than institutional details, can well interpret the differences caused by institutional shifts in the YRB, and keeps consistent with previous studies theoretically.
+We apply the network \cite{bodin2017b} approach to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit (the YRCC) into general building blocks (or motifs) (see Figure~\ref{framework}), from the official documents.
+Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures, and the network-based approach is to abstract connections between entities into links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.
+In this study, we examined the official documents of the two institutional shifts of concern (87-WAS and 98-UBR, see \textit{Appendix \nameref{secS1}} for details).
+Besides the ecologically connected river reaches, the agents (provinces and the YRCC) are abstracted as nodes, and their required interactions regarding water use are summarized as links.
+The 1987-WAS requires the YRCC to monitor each river's reach, while the 1998-UBR requires direct interactions (through water use licenses) between the YRCC and the provinces.
+Therefore, we linked the YRCC unit to each ecological unit after 87-WAS and each province unit after the 98-UBR.
+We try to approve that focusing on SES structures rather than institutional details can reasonably interpret the differences caused by institutional shifts in the YRB.
 
-\subsection{Differenced Synthetic Control}
-We estimate water use without institutional shifts effect by using the Differenced Synthetic Control (DSC) method.
+\subsection{Dataset and preprocessing}\label{sec:dataset}
+We choose datasets and variables to compare on actual and estimated water use of the YRB.
+The actual water uses are accessible in China’s provincial annual water consumption dataset from the National Water Resources Utilization Survey, whose details are accessible from Zhou (2020) \cite{zhou2020}.
+To estimate the water use of the YRB by assuming there were no effects from institutional shifts, we focused on variables from five categories (environmental, economic, domestic, and technological) water use factors.
+Their specific items and origins are listed in Table~\ref{tab:variables}.
+
+Among the total $31$ data-accessible provinces (or regions) assigned quotas in the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin, and Beijing because of their trivial water use from the YRB (see \textit{Appendix}~Table~\ref{tab:quota}).
+We then divided the dataset into a ``target group'' and a ``control group'', treating provinces involved in water quota as the target group $(n=8)$ and other provinces as the control group $(n=20)$ for applying the DSC.
+
+Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ principal components \textit{Appendix~\nameref{secS2}}.
+Bayan had proved that combining PCA and DSC can raise the robustness of causal inference \cite{bayani2021}.
+We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different.
+Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\nameref{secS2}~Figure~\ref{fig:elbow}}).
+Finally, we transform the dataset and input the dimensions-reduced output into the DSC model.
+
+\subsection{Differenced Synthetic Control}\label{sec:DSC}
+We estimate water use without institutional shifts effect using the Differenced Synthetic Control (DSC) method.
 The DSC method is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadie2010, abadie2015, hill2021}.
-This method aims to evaluate the effects of policy change that are not random across units but focus on some of the units (i.e., institutional shifts in the YRB here).
-By re-weighting units to match the pre-trend for the treated and control units, the DSC method imputes post-treatment control outcomes for the treated unit(s) by constructing a synthetic version of the treated unit(s) equal to a convex combination of control units with a new estimator with improved bias properties.
 
-In practice, each of the units (i.e., provinces) in the treated group were affected by institutional shifts in 1987 and 1998, each of which was taken as the ``shifted'' time $t_0$ within two individually analyzed periods $T$: 1979-1998; 1987-2008.
+This method aims to evaluate the effects of policy change that are not random across units but focuses on some of them (i.e., institutional shifts in the YRB here).
+By re-weighting units to match the pre-trend for the treated and control units, the DSC method imputes post-treatment control outcomes for the treated unit(s) by constructing a synthetic version of the treated unit(s) equal to a convex combination of control units.
+Therefore, the synthetic and actual version difference can be estimated as a net effect for a treated unit.
+
+In practice, all treated units (i.e., provinces) were affected by institutional shifts in 1987 and 1998, each taken as the ``shifted'' time $t_0$ within two individually analyzed periods $T$: 1979-1998; 1987-2008.
 We include each province in the YRB ($n=8$, see \textit{\nameref{sec:dataset}}) as the treated unit separately, as multiple treated units approach had been widely applied \cite{abadie2021}.
@@
 We define $T_0$ to represent the number of pre-treatment periods ($1,\cdots,t_0$) and $T_1$ the number post-treatment periods ($t_0,\cdots,T$), such that $T = T_0+ T_1$.
-That is, treated unit is exposed to the institutional shift in every post-treatment period $T_0$, and unaffected by the institutional shift in all preceding periods $T_1$.
+The treated unit is exposed to the institutional shift in every post-treatment period $T_0$, unaffected by the institutional shift in all preceding periods $T_1$.
 Then, any weighted average of the control units is a synthetic control and can be represented by a ($J * 1$) vector of weights $\mathbf{W} = (w_{1},...,w_{J})$, with $w_j \in (0, 1)$.
@@
 That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W*(V)}$.
-We choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{W*(V)}$ that minimizes the following expression:
+Therefore, we choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{W*(V)}$ that minimizes the following expression:
 
@@
 That is the minimum difference between the outcome of the treated unit and the synthetic control in the pre-treatment period, where $\mathbf{Z}_{1}$ is a ($1*T_0$) matrix containing every observation of the outcome for the treated unit in the pre-treatment period.
-Similarly, let $\mathbf{Z}_{0}$ is a ($k * T_0$) matrix containing the outcome for each control unit in the pre-treatment period, $k$ is number of variables in the datasets.
+Similarly, let $\mathbf{Z}_{0}$ be a ($k * T_0$) matrix containing the outcome for each control unit in the pre-treatment period, and $k$ is the number of variables in the datasets.
 The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with double robustness properties \cite{billmeier2013, smith2015}.
 
-\subsection{Dataset and preprocessing}\label{sec:dataset}
-We choose dataset and variables to compare on actural and estimated water use of the YRB.
-The actual water uses are accessible in China’s provincial annual water consumption dataset from the National Water Resources Utilization Survey, whose details are accessible from Zhou (2020) \cite{zhou2020}.
-To estimate the water use of the YRB by assuming there were not effects from institutional shifts, we focused on variables from five categories (environmental, economic, domestic, and technological) water use factors.
-Their specific items and origins are listed in Table~\ref{tab:variables}.
-
-Among the total $31$ data-accessible provinces (or regions) assigned quotas in the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin and Beijing because their trivial water use from the YRB (see \textit{Appendix}~Table~\ref{tab:quota}).
-We then divided the dataset into a ``target group'' and a ``control group'', treating provinces involved in water quota as the target group $(n=8)$ and other provinces as the control group $(n=20)$, for applying the DSC.
-
-Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ pricipal components Appendix~\nameref{secS3}.
-Bayan had proved that combining PCA and DSC can rise robustness of causal inference \cite{bayani2021}.
-Here, we first applied the Zero-Mean normalization (unit variance), as the variables' unit are far different.
-We use Elbow method to choose number of the pricipal components, as Appendix~\nameref{secS3}~Figure~\ref{fig:elbow} shows, $5$ components well reduced the dimensions of the dataset with $89.63\%$ variance explaination.
-
 \subsection{Economic model}\label{sec:model}
-In order to inference the mechanisms underlying the results, we developed a economic model based on marginal revenue to analyze how institutional shift could have led to differences in water use.
+To infer the mechanisms underlying the results, we developed an economic model based on marginal revenue to analyze how the institutional shift could have led to differences in water use.
 
@@
 \begin{ass}
-    (Multi-period settings) There are multiple settings periods with a constant discount factor for expectation of future water use.
+    (Multi-period settings) There are multiple settings periods with a constant discount factor for the expectation of future water use.
 \end{ass}
 
-Under the above simplified assumptions, we demonstrate three cases -corresponding the abstracted SES structures (Figure~\ref{structure}), inference how SES structure alters the expected marginal benefits and costs of provinces making decisions.
-As one of the possible interpretation for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.
+Under the above-simplified assumptions, we demonstrate three cases -corresponding to the abstracted SES structures (Figure~\ref{structure}), inference of how SES structure alters the expected marginal benefits and costs of provinces making decisions.
+As one of the possible interpretations for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.

### 2022-05-29 docs/papers/02_appendix/01_institution_context.tex
feat: pca analysis
BREAKING CHANGE:
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

@@
 
+We aim to abstract the water allocating institutions from the description in official documents with necessary context into SES building blocks (Figure~\ref{framework})
+Widespread building blocks in SES are the key to the functioning of structures, and a network-based description is a widely used way to depict them by abstracting links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.9\linewidth]{diagrams/framework.jpg}
+	\caption{
+		Framework for understanding linkages between SES structures and outcomes.
+		\textbf{a.} The general framework for analyzing social-ecological systems (SESs) (adapted from Ostrom \cite{ostrom2009}).
+Institutions embedded in SESs may reshape structures by changing the interactions between core subsystems, resulting in different outcomes.
+        Three typical types of abstracted SES structures are shown as \textbf{b.}, \textbf{c.} and \textbf{d.} (adapted from Bodin, 2017)\cite{bodin2017b}.
+Red circles indicate social actors, and green ones indicate ecological components.
+Connection (ties between two ecological components), collaboration (ties between two social actors), or management (ties between a social actor and an ecological component) exist when gray lines link two units.
+According to empirical evidence, the gray dashed lines show aligned SES structures that are more likely to achieve a desirable outcome.
+        }
+    \label{framework}
+\end{figure}
+
 % 水资源分配方案在全世界范围内都是流域管理的普遍制度。
-Water allocation schemes are widespread in large river basin management programs throughout the world (see \textit{Appendix} Figure~\ref{fig:world}) \cite{speed2013}.
+Water allocation institutions are widespread in large river basin management programs throughout the world (see \textit{Appendix} Figure~\ref{fig:world}) \cite{speed2013}.
 This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level)\cite{wang2019a}:
@@
 
-The official documents in 1987 (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today) clearly convey the following key points:
+The official documents in 1987 (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today) convey the following key points:
 
@@
 	% 该政策面向的目标是各省（区域），黄委会没有被提及
-	\item The policy is aimed at related provinces (or regions in the same administrative level).
+	\item The policy is aimed at related provinces (or regions at the same administrative level).
 	% 政策制定的首要考虑是解决断流问题
@@
 	% 各省被鼓励在此配额下制定自己的用水计划
-	\item Provinces are encouraged to develop their own water use plans based on a quota system.
+	\item Provinces are encouraged to develop their water use plans based on a quota system.
 	% 水资源供给无法满足需求对相关省（地区）是普遍现象。
@@
 The official documents in 1998
-(\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today) clearly convey the following key points:
+(\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today) convey the following key points:
 
@@
 	% 除了说明政策针对的各省区之外，明确指出其用水需要黄河水利委员会进行申报，并由其组织和监管
-	\item The document clearly points out that not only provinces and autonomous regions involved in water resources management (see \textit{Article 3}), the provinces’ and regions’ water use shall be declared, organized, and supervised by the YRCC (\textit{Article 11 and Chapter III to Chapter V, and Chapter VII}).
+	\item The document points out that not only provinces and autonomous regions involved in water resources management (see \textit{Article 3}), the provinces’ and regions’ water use shall be declared, organized, and supervised by the YRCC (\textit{Article 11 and Chapter III to Chapter V, and Chapter VII}).
 	% 本研究(\textit{ Article 1})首先考虑的是上、中、下游用水的总体规划。
@@
 \end{itemize}
-
-% 基于上述分析，我们抽象出了如正文图2中所展示的流域水资源分配制度的运行结构，并将研究时段选择在1975到2008之间。
-% On the basis of the above analysis, we abstracted the operational structure of the water resource allocation institution of the YRB as shown in Figure 2 of the main text, focusing on the period between 1975 and 2008.
-By comparing the net effects of three different institutional structures split by the two institutional shifts, we were able to reach a stronger understanding of the influence of structural alignments under the same basin (previous structure-based analysis usually focus on a certain type of systems but with different geographic contexts).
 

### 2022-05-29 docs/papers/02_appendix/02_method_details.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

--- 2022-05-05 docs/papers/02_appendix/02_method_details.tex
@@
 
-% 为了使用合成控制法预测没有制度变化下的用水变化趋势，需要使用影响用水的社会经济数据作为自变量输入。
-In order to use the synthetic control method to predict the trend of water use without institutional change, socioeconomic data affecting water use were used as the input independent variables.
-All variables used are listed in Table~\ref{tab:variables}.
-% 这些变量涉及了省级单元在利用水资源时需要考虑的主要经济因素（农业、工业、服务业与居民生活），它们与因变量（水资源使用）的相关性如图所示。
-These variables refer to major economic factors (agriculture, industry, service industry, and domestic) that provincial units need to take into account when using water resources; their correlation coefficients with the dependent variable (water resource use) are shown in Figure~\ref{fig:linear} A.
+% 找到具解释力的变量是构造合成控制法稳健的关键。
+Explanatory variables are the key to constructing a robust synthetic control method.
+% 我们共使用了用水量密切相关的26个变量，这些变量的数据集已在先前的研究中被用来解释中国的用水量变化
+We used a total of $24$ variables related to water consumption Table~\ref{tab:variables}, which datasets have been used in previous studies to explain changes in water use in China \cite{zhou2020}.
+% 由于这些变量间存在自相关，我们通过肘部法供选择了5个主成分作为DSC的输入，前人研究表明PCA方法的结合能够增强合成控制法的稳健性
+In addition, we selected $5$ principal components as input by the elbow method because selection in autocorrelated variables reduces dimensions and then enhances the robustness of the DSC (Figure~\ref{fig:elbow}).
 
-% 此外，合成控制法有一个假设是自变量的线性组合可以有效预测因变量，因此我们还对数据线性拟合的效果进行了测试。
-In addition, the synthetic control method assumes that a linear combination of independent variables can effectively predict the dependent variables.
-% 将数据集区分为80%的训练样本和20%的测试样本，我们使用训练样本构建了多元线性模型对用水量进行了预测，并使用测试数据集去检验模型拟合效果。
-We therefore divided the dataset into two groups, training samples $(80\%)$ and test samples $(20\%)$, and used the training samples to build a multivariate linear model to predict the water consumption.
-We then used the test dataset to test the model-fitting effect.
-% 结果表明拟合优度R2超过了0.8，因变量可以很好的被自变量的线性组合所解释，该数据集可以用于控制合成法。
-Results show that the goodness of fit $R^2$ exceeded $0.8$; thus, the dependent variable is well-explained by the linear combination of independent variables, and the dataset can be used in the synthetic control method (Figure~\ref{fig:linear}B).
+There are two approaches to validity testing of the DSC: (1) comparing the post-treated and pre-treated reconstructions and (2) testing robustness through placebo analysis.
+For (1), differences between each province and their synthetic are significant in post-treated periods and small in pre-treated periods (Figure~\ref{fig:87panel} and figure~\ref{fig:98panel}), which show good reconstructions of their water use changes' estimation.
+For (2), we applied the in-place placebo analysis described by \cite{abadie2010}.
+In most provinces, ratios of post-MSPE to pre-MSPE are higher than the median of other placebo units, which suggests the institutional shifts in treated time (1987 and 1998 here) influenced them more than most of the other provinces (figure~\ref{fig:87placebo}, figure~\ref{fig:98placebo}, Table~\ref{tab:DSC_summary}).
 
-\begin{table}[!h]
+\begin{figure*}
+    \includegraphics[width=0.9\linewidth]{outputs/87panel.pdf}
+    \centering
+    \caption{Comparations between YRB' provinces and their synthetic controls around the 87-WAS.}
+    \label{fig:87panel}
+\end{figure*}
+
+\begin{figure*}
+    \includegraphics[width=0.9\linewidth]{outputs/98panel.pdf}
+    \centering
+    \caption{Comparations between YRB' provinces and their synthetic controls around the 98-UBR.}
+    \label{fig:98panel}
+\end{figure*}
+
+\begin{figure*}
+    \includegraphics[width=0.9\linewidth]{outputs/87placebo.pdf}
+    \centering
+    \caption{Gaps in change in water use between provinces outside the YRB and their synthetic control, around the 87-WAS, excluding the provinces with high pre-treatment RMSPE (more than $3$ times of treated units' RMSPE).}
+    \label{fig:87placebo}
+\end{figure*}
+
+\begin{figure*}
+    \includegraphics[width=0.9\linewidth]{outputs/98placebo.pdf}
+    \centering
+    \caption{Gaps in change in water use between provinces outside the YRB and their synthetic control, around the 98-UBR, excluding the provinces with high pre-treatment RMSPE (more than $3$ times of treated units' RMSPE)}
+    \label{fig:98placebo}
+\end{figure*}
+
+\begin{table*}[!ht]
 	\caption{Variables and their categories for water use predictions}
@@
 	\end{tabular}
-\end{table}
+\end{table*}
 
-\begin{figure}[!thb]
+\begin{figure*}
+    \includegraphics[width=0.9\linewidth]{outputs/elbow.pdf}
     \centering
-	\includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/outputs/linear}
-	\caption{
-		\textbf{A.} Correlation between independent variables and the dependent variable (water use).
-		\textbf{B.} Linear relationship between the independent variables and the dependent variable trained by a linear model.
-	}
-\label{fig:linear}
-\end{figure}
+    \caption{Choose number of pricipal components by Elbow method, $5$ pricipal components already capture $89.63\%$ explained variance.}
+    \label{fig:elbow}
+\end{figure*}
+
+\begin{table*}
+	\caption{Pre and post treatment root mean squared prediction error (RMSPE) for YRB's provinces}
+	\label{tab:DSC_summary}
+	\scriptsize
+	\centering
+	\begin{tabular}{lrrrrrrrr}
+	\hline
+	 & \multicolumn{4}{c}{1987-WAS} & \multicolumn{4}{c}{1998-UBR} \\
+	 Provinces & Pre-RMSPE & Post-RMSPE & Ratio & Significant$^a$ & Pre-RMSPE & Post-RMSPE & Ratio & Significant$^a$ \\
+	 \hline
+	 Qinghai & 0.016 & 0.231 & 14.606 & True & 0.230 & 1.170 & 5.096 & True \\
+	Gansu & 0.056 & 1.307 & 23.265 & True & 0.244 & 0.841 & 3.448 & True \\
+	Ningxia & 0.097 & 0.944 & 9.697 & True & 0.332 & 1.091 & 3.284 & True \\
+	Neimeng & 0.335 & 3.846 & 11.479 & True & 1.320 & 1.183 & 0.896 & False \\
+	Shanxi & 0.208 & 0.675 & 3.241 & False & 0.264 & 0.401 & 1.520 & False \\
+	Shaanxi & 0.181 & 0.572 & 3.164 & False & 0.096 & 0.724 & 7.579 & True \\
+	Henan & 0.210 & 3.207 & 15.292 & True & 1.222 & 2.479 & 2.029 & False \\
+	Shandong & 0.209 & 1.840 & 8.785 & True & 0.431 & 1.517 & 3.516 & True \\
+	\hline
+	\end{tabular}
+	\footnotesize[a]\leftline{{Larger post/pre RMSPE than the median of the placebos.}}\\
+\end{table*}

### 2022-05-29 docs/papers/02_appendix/04_theoretical_model.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

@@
 
-In order to understand the mechanisms through which the SES structure impacts provincial water use, we developed a dynamic economic model to analyze how institutional mismatch could have led to the changes of water use, especially among provinces with high incentives for excess water use.
+To understand the mechanisms through which the SES structure impacts provincial water use, we developed a dynamic economic model to analyze how institutional mismatch could have led to the changes in water use, especially among provinces with high incentives for excess water use.
 Specifically, we modeled individual provincial decision-making in water resources before quota execution.
 
-We proposed three intuitive and general assumptions.
-
-%There are infinite discrete periods (t=1, 2,...) and N provinces.
-The water use of province i is denoted as $x_{i}$.
-At t=0, there is no constraints on water use.
-In the following periods (t=1,2,...), each province is imposed of quota restrictions determined at t=0.
-The water use decision of each province is forward-looking, based on not only current benefits and costs but also its future impacts on quota restriction.
-There are several key assumptions on the water use about production input, output, and water use constraints.
+We proposed three intuitive and general assumptions:
 
@@
 
- where A denotes $A_H$ for a high-incentive province and $A_L$ for a low-incentive province.
+ where $A_H$ and $A_L$ denote high-incentive and low-incentive provinces, respectively.
 
- When the decisions in different periods are independent, for $t$ = 0, 1, 2, ..., then:
+ When the decisions in different periods are independent, for $t$ = $0, 1, 2 \cdots$, then:
 
@@
 
- $Q_i=Q \cdot \frac{x_i}{x_i + \begin{matrix}\sum{x_{-i}} \end{matrix}}  $.
+ $Q_i=Q \cdot \frac{x_i}{x_i + \begin{matrix}\sum{x_{-i}} \end{matrix}}$.
 
@@
 
-where A denotes $A_H$ for a high-incentive province and $A_L$ for a low-incentive province.
+where $A_H$ denotes a high-incentive province and $A_L$ denotes a low-incentive province.
 
@@
 
-Proposition 2: The water overuse is higher among provinces with high water use incentives than that with low water use incentives under a mismatched institution.
+Proposition 2: Water overuse is higher among provinces with high water use incentives than low- water use incentives under a mismatched institution.
 
@@
 As production efficiency increases, the marginal benefits of a unit quota increase, and the quota would provide higher future benefits for a pre-emptive water use strategy.
-Provinces with high production efficiency have higher optimal values of water use under the decentralized decision, and the divergence in water use would be exaggerated during the period that the water quota is expected to be implemented and water use is in greater competition.
+Provinces with high production efficiency have higher optimal water use values under the decentralized decision.
+The divergence in water use would be exaggerated when the water quota is expected to be implemented with greater competition.
 
@@
 
- When the future water use would be constrained by the water quota, the dynamic optimization problem of province i is shown as follows.
-In t=1,2,..., there would be no relevant cost when the quota is bound that each province takes constant costs of $\frac{P \cdot Q}{N}$ regardless of the allocation.
-It is sufficient to consider only the total water quota is smaller than total water use in Case 2 since a ``too large'' quota doesn't make sense for ecological policies.
+ When the water quota would constrain future water use, the dynamic optimization problem of province i is shown as follows.
+In $t=1,2,\cdots$, there would be no relevant cost when the quota is bound that each province takes ongoing costs of $\frac{P \cdot Q}{N}$ regardless of the allocation.
+Therefore, it is sufficient to consider only the total water quota is less than total water use in Case 2 since a ``too large'' quota doesn't make sense for ecological policies.
 
@@
 \end{case_appendix}
-
-%图注释
-
-\begin{fig}
-Optimal water use under different institutions
-
-\tiny Notes: The figure depicts the relationship of marginal return deducted from marginal cost and water use of province $i$ at t=0 under centralized decisions, decentralized decisions, and decentralized decisions under quota restrictions, for a province with high water use incentive in Panel (A), and for a province with low water use incentive in Panel (B).
-Assume $F_H(x)=A_Hln(1+x), F_L(x)=A_Lln(1+x), A_H=1, A_L=0.8, N=8, P=1, C=0.5, \beta=0.7$, and $Q=8$.
-In Case 3, others' water use is taken as given, equal to the optimal water use under Case 2.
-The horizontal coordinate of each intersection of marginal return minus the marginal cost and break-even line represents the optimal water use under each case.
-\end{fig}

### 2022-05-29 docs/papers/02_appendix/05_model_extensions.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

@@
 %Model extension部分
-Further analysis of the general economic model
-
 Using the general economic model (see the Methods section in the main text), we also explored the response of stakeholders to water quota policies.
-We considered two additional scenarios for stakeholders, one that considered technology growth and one that considered different valuations through time (via the discount rate) of economic benefits and ecological costs.
+We considered two additional scenarios for stakeholders: technology growth and one that felt different valuations through time (via the discount rate) of economic benefits and ecological costs.
 In the following scenarios, the cost is assumed to be untransferable, which could be fully allocated to the one incurring the water use.
-Explaining plausible scenarios for these stakeholders will help us better understand the causes of the water overuse and potential solutions.
-We argue that the water overuse remains robust even if a complete and equitable system.
+Explaining plausible scenarios for these stakeholders will help us better understand the causes of water overuse and potential solutions.
+We argue that water overuse remains robust even if a complete and equitable system.
 
@@
 
-    Even if the negative externality of water overuse is eliminated by``fair" ecology cost of $\frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \cdot Q \cdot C$, it is possible that the future growth opportunities and ``remote" ecological costs provide enough incentive for the sprint.
-The water overuse has the value of future economical benefits by slacking the water use constraint in the future.
+    Even if the negative externality of water overuse is eliminated by ``fair'' ecology cost of $\frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \cdot Q \cdot C$, it is possible that the future growth opportunities and ``remote" ecological costs provide enough incentive for the sprint.
+Water overuse has the value of future economic benefits by slacking the water use constraint in the future.
 The heterogeneous production efficiency is omitted in this section, and we set A=1.
@@
 
-We depict the relationship of multi-period profit and water use $x_{i,0}$ in different horizons in Figure~\ref{fig:technology}%%此处引用图片
-,and thus find out the optimal water use pattern under technology growth.
-The higher marginal output of water might create enough incentive to set off the untransferable cost since a higher allocated quota provides growth option value.
-As the provincial decision is under a longer horizon, there is a greater sprint effect due to higher accumulated yield and relatively tighter water use constraints over time.
+We depict the relationship between multi-period profit and water use $x_{i,0}$ in different horizons in Figure~\ref{fig:technology}
+, and thus find out the optimal water use pattern under technology growth.
+The higher marginal water output might create enough incentive to offset the untransferable cost since a higher allocated quota provides growth option value.
+On the other hand, as the provincial decision is under a longer horizon, there is a more significant sprint effect due to higher accumulated yield and relatively tighter water use constraints over time.
 
@@
 
-Assume that there is a high discount rate for economical benefits and a low discount rate for ecological costs, in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$, discount factor $\beta^{economy}$ and $\beta^{ecology}$ ($\beta^{economy} > \beta^{ecology}$).
+Assuming that there is a high discount rate for economic benefits and a low discount rate for ecological costs, in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$, discount factor $\beta^{economy}$ and $\beta^{ecology}$ ($\beta^{economy} > \beta^{ecology}$).
 For simplicity, consider the following finite-period water use optimization, noting the water use of province $i$ at period $t$:
@@
 
-We depict the relationship of multi-period net income and water use $x_{i,0}$ in different horizons in Figure~\ref{fig:remote}%此处引用图片
+We depict the relationship of multi-period net income and water use $x_{i,0}$ in different horizons in Figure~\ref{fig:remote}
 , and thus find out the optimal water use pattern under ``remote'' ecological costs.
 The higher discounted ecological costs might create enough incentive to set off the untransferable cost.
-As the provincial decision is under a longer horizon, there is a greater sprint effect due to a higher accumulated yield.
+On the other hand, as the provincial decision is under a longer horizon, a more significant sprint effect is due to a higher accumulated yield.
 

### 2022-05-29 core/handle.py

@@ -168,7 +168,7 @@ class ExpResultsHandler(Experiment):
         sc = self.result.get(province)
         sc.plot(panels)
 
-    def panel_plots(self, how="original", save_path=None):
+    def panel_plots(self, how="original", save_path=None, **kwargs):
         fig, (axs1, axs2) = plt.subplots(
             2, 4, figsize=(16, 8), constrained_layout=True
         )
@@ -177,7 +177,7 @@ class ExpResultsHandler(Experiment):
         axs.extend(axs2)
         for province, ax in zip(self.provinces, axs):
             sc = self.result.get(province)
-            basic_plot(how=how, ax=ax, sc=sc)
+            basic_plot(how=how, ax=ax, sc=sc, **kwargs)
             ax.set_xlabel(f"{province}")
         if save_path:
             self.log.info(f"Panel plots saved in {save_path}.")

### 2022-05-29 docs/papers/02_appendix/02_method_details.tex
fix(method_details.tex): fix an error: environmental background variables ignored

@@
 	\hline
-	Economic sector &
+	Sector &
 	  Category &
@@
 	  Livestock \\ \hline
+	Environment &
+		  Temperature & $K$ & Near surface air temperature & Temperature \\
+			& Precipitation & $mm$ & Annual accumulated precipitation & Precipitation \\ \hline
 	\end{tabular}

### 2022-05-29 docs/papers/01_manuscript/04_discussion.tex
fix(discussion-model): fix a sentence according to Wen's comment (email)

@@
 This ``major users use more'' pattern supports the hypothesis that separated stakeholder (individual province here) decides on linked ecological units for output maximization (water use).
-Therefore, we theoretically abstracted the structures associated with the structural changes induced and analyzed how different water allocation structures shape different outcomes.
+Therefore, we theoretically abstracted the SES structures and analyzed how different structures shape different outcomes with provincial heterogeneity.
 Assuming that water is the factor input with decreasing marginal output of each province, we discuss the marginal return and optimal water use under three different cases (analogy to Figure~\ref{structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{Appendix~\nameref{secS4}}).

### 2022-05-30 docs/papers/01_manuscript/04_discussion.tex
fix(output.docx,-version,-fix-figure-label.): fix figure caption, and output as a word version

@@
 	\caption{
-		\textbf{A.} The relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
+		The relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
 	\label{fig:model}

### 2022-06-11 docs/papers/01_manuscript/01_introduction.tex
fix(paper-docs): fixed grammar in introduction and refactor results

@@
 Widespread freshwater scarcity and overuse challenge the sustainability of large river basins, resulting in systematic risks to economies, societies, and ecosystems globally \cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
-With steadily increasing demand, competition for water causes depletion of freshwater globally and calls for an urgent transformation of the governance system by considering water use conservation \cite{gleick2010, ziolkowska2016, wang2019d}.
-Despite worldwide trying to govern water, however, degradation of large river basins is not easily reversible because of few alignments between practice and theory in successful water governance cases.
+With steadily increasing demand, competition for water causes depletion of freshwater globally.
+Therefore, it creates a strong need for an urgent transformation of the water governance system to improve water use conservation \cite{gleick2010, ziolkowska2016, wang2019d}.
+Despite worldwide efforts to govern water sustainably, overuse and the resulting degradation of large river basins are not easily reversible.
+Thus, there have been relatively few successful governance practices and theory re-alignments
 \cite{giuliani2013, falkenmark2019, jaeger2019}.
+In the context of future climate change, the gap between supply and demand for water resources in large river basins is expected to become increasingly more prominent.
+% TODO citation
+Balancing the water demands of ecosystems and development in heavily human-dominated river basins is a challenge not just for China but also across many large river basins worldwide.
 
 % 黄河的介绍
-The Yellow River Basin (YRB), the fifth large river worldwide, is known for its irreplaceable role in the social-economic development of China, and thus also drastically interference by anthropogenic stress.
-Supporting $35.63\%$ irrigation and $30\%$ population with only $2.66\%$ water resources of China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today), the overburdened Yellow River depleted in consecutive years, resulting in substantial ecological, economic and social crisis (e.g., wetland shrink, agriculture reduction, and scramble for water).
-Intense water use, accounting for about $80\%$ of Yellow River surface runoff in the 1980s, was remarked as the significant reason for the degradation.
-Furthermore, human interferences such as soil conservation and water conservancy project boosted water withdrawal and then stressed the water scarcity of the Yellow River.
-In the context of future climate change, the contradiction between supplies and demands of water resources in the YRB will become more prominent.
-%! Citation: Hao Wang presentation.
-Therefore, balancing ecological and developing demands in such a human-dominated basin is a problem for China in terms of water governance throughout and for large rivers worldwide.
+The Yellow River Basin (YRB), the fifth-largest river basin worldwide, is known for its vital role in the socio-economic development of China.
+It supports $35.63\%$ of China's irrigation and $30\%$ of its population while containing only $2.66\%$ of its water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today).
+In the 1980s, intense water use, accounting for about $80\%$ of Yellow River surface runoff, combined with other forms of human interference (e.g., soil conservation and water conservancy projects), caused consecutive drying events and substantial ecological, economic, and social crises (e.g., wetland shrinkage, agriculture reduction, and a scramble for water).
 
 % 第三段 过去管理的经验，断流的严重程度，连续多少没有断流，少有的解决断流的大河。治理成功的流域？分析背后的机制，基础。往用水上靠。
-% 为了缓解用水压力
-Chinese authorities implemented several ambitious water management practices in the YRB in the last century to relieve the water stress, such as reservoir regulation, South-to-north Water Diversion Project (WDP), and Water Allocation Scheme since 1987 (87-WAS), and the Unified Basinal Regulation since 1998 (98-UBR).
-Through those efforts, ecological restoration of wetlands and estuary delta in the YRB without drying up for over $20$ is widely considered a considerable river management achievement.
-Different from the engineering that provides further water supply, institutional strategies like the 87-WAS (assign water quotas for provinces in the YRB) and the 98-UBR (the provinces had to be allowed to use water by the Yellow River Conservancy Commission, YRCC) mainly focused on limiting demands of water use.
-Such institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human and natural system, including interplays between social actors, ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
-Understanding those complex interlinkages, therefore, is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
-However, while literature had well evaluated and quantified the effects of engineering solutions beforehand, there are few attempts to assess institutional contributions to successful water governance.
+In response, Chinese authorities implemented several ambitious water management practices in the YRB to relieve water stress, such as reservoir regulation, the South-to-north Water Diversion Project (WDP), the 1987 Water Allocation Scheme (87-WAS), and the 1998 Unified Basinal Regulation (98-UBR).
+Those efforts led to ecological restoration of wetlands and estuarine delta, and drying up has been avoided for over 20 years, widely considered considerable management achievements.
+Unlike engineering providing further water supply, institutional strategies like the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, authority at a basin-level) focused mainly on limiting demands of water use.
+Such institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human and natural system, including interplays between social actors, ecological units, or between social and ecological system elements
+\cite{young2008,cumming2020b,lien2020, bodin2017b}.
+Therefore, understanding those complex interplays is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
 
+While researchers have carefully evaluated and quantified the effects of engineering solutions, there have been few attempts to assess institutional contributions to successful water governance in the YRB.
 % 第四段 目标 制度变化。是不是制度变化产生的，如果是的话怎么影响。
-In addition to widespread recognition of the rising importance of institutions as an approach to water sustainable use within large river basins (especially transboundary rivers like the YRB), their specific effects are still in open discussion \cite{agrawal2003, persha2011, agrawal2001}.
-Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, therefore, supporting (but not guaranteeing) the sustainability of SES \cite{epstein2015, wang2019d}.
-Some institutional shifts have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and collaborative water governance systems in Europe \cite{green2013}).
-However, shifting institutions in a large, complex river basin may create or destroy hundreds of different connections between social agents and ecological units, where matched social-ecological structures are not ubiquitous.
-Therefore, the role of institutional shifts in the water governance achievement of the YRB and their impacts on water use is still uncertain without an understanding of SES structures.
-% 通过抽象文件变化
-Here, by abstracting changes in official documents following institutional shifts (the 87-WAS and the 98-UBR), we depicted the SES structures of the YRB from 1979 to 2008.
-Then, we use Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without the institutional shifts (\textit{\hyperref[{sec:methods}]{Methods}} and \textit{Appendix~\nameref{secS2}}).
-By further interpreting the differences of the effects in the YRB, we explored the mechanisms linking SESs structure and outcomes for a deeper understanding of institutions' role in water governance worldwide.
+In addition to widespread recognition of the rising importance of governmental institutions for sustainable water use within large river basins (especially in the case of transboundary basins like the YRB), the best approach to designing effective institutions remains an open question \cite{agrawal2003, persha2011, agrawal2001}.
+Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, supporting (but not guaranteeing) the sustainability of SES \cite{epstein2015, wang2019d}.
+Some institutional advances have had desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d}, and collaborative water governance systems in Europe \cite{green2013}).
+However, imposing institutional changes on a large, complex river basin may create or destroy hundreds of different connections between social agents and ecological units, where matched social-ecological structures are not ubiquitous.
+
+To better understand how water management institutions can be designed to fit their social-ecological context, we used data on changes in official documents following institutional shifts (the 87-WAS and the 98-UBR) to describe changes in the SES structures associated with the YRB from 1979 to 2008.
+We then used Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without institutional shifts (\textit{\hyperref[{sec:methods}]{Methods}} and \textit{Appendix~\nameref{secS2}}).
+It allowed us to create a counterfactual against which to explore the mechanisms linking SESs structure and outcomes for a deeper understanding of the potential role of institutions in water governance worldwide.

### 2022-06-11 docs/papers/01_manuscript/02_structures.tex
fix(paper-docs): fixed grammar in introduction and refactor results

@@
 % 制度变动综述
-The institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among national water governance practices (\textit{Appendix}~\nameref{secS1}).
+The institutional shifts in the YRB in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among YRB's water governance practices (\textit{Appendix}~\nameref{secS1}).
 Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
-As a compounded result of development, the provinces such as Shandong, Henan, and Inner Mongolia used more water resources in the YRB with larger economies (primarily for irrigation agriculture).
-For shrinking water deficits, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin (Table~\ref{tab:quota}).
-However, the controversial scheme helped little in turning the water depletion around until another strategy attempted to strengthen the responsibilities of the YRCC in integrated water management in 1998 (the 98-UBR).
-Therefore, our analysis period spans from 1979 (emergence of river depletion) to 2008 (a further polish of the 98-UBR), with the SESs shifted between three varying institutions (Figure~\ref{structure}).
-
-We selected institutional regulatory documents on water use issued by national ministries (for validation to both watershed and regional agents) and then extracted the interactions between the agents involved (\textit{Appendix \nameref{secS1}}).
-Before 1987, the YRCC had no links to the provinces regarding water use, and the provinces could link to the Yellow River reaches directly (Figure~\ref{structure}).
-However, according to the extracted information from the 87-WAS, the YRCC started to report water use from the provinces.
-Furthermore, information from the 98-UBR documents demonstrated that the provinces had to apply their plan for an annual water use license instead of direct access to the Yellow River water.
-Thus, there have been links between the YRCC and the provinces since the strengthening responsibilities of the YRCC in 1998.
+Therefore, the YRCC had no links to the provinces regarding water use before 1987, and the provinces could link directly to the Yellow River reaches (Figure~\ref{structure}~C).
+To shrink water deficits, in 87-WAS, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin (Table~\ref{tab:quota}).
+Simultaneously, according to the extracted information from documents of the 87-WAS issued by national ministries, the YRCC started to report water use in each reach.
+As it was the first time YRCC's responsibility involved water use, we introduced new links between the YRCC and the ecological nodes (Figure~\ref{structure}~C).
+However, the controversial 87-WAS did not resolve water depletion.
+In 1998, another strategy (98-UBR) was developed to strengthen the responsibilities of the YRCC for integrated managing water use.
+Information from the 98-UBR documents demonstrated that the provinces had to apply their plan for an annual water use license to YRCC instead of direct access to the Yellow River water.
+Thus, the YRCC has been linked to the provinces since 1998 (Figure~\ref{structure}~C).
 

### 2022-06-11 docs/papers/01_manuscript/03_results.tex
fix(paper-docs): fixed grammar in introduction and refactor results

@@
 Our estimation of theoretical water use suggests that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without an institutional shift (Figure~\ref{main_results}A).
-From 1988 to 1998, on average, while the estimation of annual water use only suggests $974.34$ billion $m^3$, the observed water use of the YRB provinces reached $1038.36$ billion $m^3$ in sum, $6.57\%$ increased.
-However, after the institution shifted again in 1998 (98-UBR), the trend of increasing water use appeared to be effectively suppressed.
+From 1988 to 1998, on average, while the estimation of annual water use only suggests $974.34$ billion $m^3$, the observed water use of the YRB provinces reached $1038.36$ billion $m^3$ (an increase of $6.57\%$).
+However, after the institutional change in 1998 (98-UBR), trends of increasing water use appeared to be effectively suppressed.
 From 1998 to 2008, the total observed water use decreased by $0.49$ billion $m^3/yr$ per year, while the estimation of water use still suggests $0.82$ billion $m^3/yr$ increases (Figure~\ref{main_results} B).
-The increased water uses after 87-WAS aligns with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{main_results}C).
-On the other hand, the 98-UBR ended river depletion, despite the intensity of droughts still increasing for decades (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{main_results}C).
+The increased water uses after 87-WAS aligns with the severe drying-down of the surface streamflow from 1987 to 1998, an obvious indicator of river degradation and environmental crisis (Figure~\ref{main_results}C).
+On the other hand, the 98-UBR ended river depletion, despite subsequent increases in drought intensity (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{main_results}C).
 
@@
         \textbf{B.} water uses of the YRB before and after the institutional shift in 1998 (98-UBR).
-While the blue lines are statistic water use data, the grey ones are the estimation from the Differenced Synthetic Control method with economic and environmental background controlled.
-        \textbf{C.} Drought intensity in the YRB and drying up events of the Yellow River. The size of the grey bubbles denotes the length of a drying upstream.
+Blue lines are statistics derived from water use data; grey lines are estimates from the Differenced Synthetic Control method with economic and environmental background controlled;
+        \textbf{C.} Drought intensity in the YRB and drying up events of the Yellow River. The size of the grey bubbles denotes the length of drying upstream.
     }
@@
 During the decade after the 87-WAS, the major water-using provinces (e.g., Inner Mongolia, Henan, Shandong) had apparent accelerations (Figure~\ref{regulating}).
-The proportion of increased (or decreased) water use for each province (over the estimated water use by the model) has a significant correlation (partial correlation coefficient is $0.77$, $p<0.05$) to the actual water use from the Yellow River.
-On average, the major water users (Shandong, Inner Mongolia, Henan, and Ningxia) used $32.14\%$ more water use than the prediction from 1987 to 1998.
-By contrast, after the 98-UBR (from 1998 to 2008), almost all provinces have seen evident ($-16.54\%$ on average) declines in water use.
-Furthermore, the regulated water use of provinces was irrelevant (partial correlation coefficient is $0.33$, $p>0.1$) with their water use from the Yellow River in proportions.
+The proportion of increased (or decreased) water use for each province (over the estimated water use by the model) correlated significantly (partial correlation coefficient is $0.77$, $p<0.05$) with actual water use from the Yellow River.
+On average, the major water users (Shandong, Inner Mongolia, Henan, and Ningxia) used $32.14\%$ more water than predicted from 1987 to 1998.
+By contrast, after the 98-UBR (from 1998 to 2008), almost all provinces have seen declines ($-16.54\%$ on average) in water use.
+Furthermore, the regulated water use of provinces was unrelated (partial correlation coefficient is $0.33$, $p>0.1$) to their proportional water use from the Yellow River.
 
@@
         Regulating differences for provinces in the YRB.
-        Red (the 87-WAS) and green bars (the 98-UBR) denote an increased or decreased ratio for the actual water use over the estimation from the model in a decade after the institutional shift.
-        The grey bars indicate the proportions of actual water use for each province to their total water use in a decade after the institutional shift.
-        The triangles mark the water quotas assigned in the institution, scaled into ratios by dividing by their sum, too.
+        Red (the 87-WAS) and green (the 98-UBR) bars denote an increased or decreased ratio for actual water use relative to the estimate from the model, in the decade after the institutional shift.
+        The grey bars indicate the proportions of actual water use for each province relative to their total water use in the decade after the institutional shift.
+        The triangles mark the water quotas assigned under the institution, converted to ratios by dividing by their sum.
     }
@@
 \end{figure*}
+
+\subsection{Structure-based marginal benefits model}
+\label{result-4}
+We then compared the marginal returns and optimal water use under three different structural cases theoretically (analogy to Figure~\ref{structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{Appendix~\nameref{secS4}}).
+Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentive for water use in each province derives from the mismatch between the benefits and costs of water use.
+Until water-use decisions are consolidated into unified management, each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive to use water, leading to higher water use.
+Furthermore, water users with higher capability are more stimulated by institutional shifts and away from the theoretically optimal water use under a unified allocation.
+
+\begin{figure}[!ht]
+    \centering
+    \includegraphics[width=0.9\linewidth]{outputs/economic_model.pdf}
+	\caption{
+		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
+	\label{fig:model}
+\end{figure}

### 2022-06-11 docs/papers/01_manuscript/04_discussion.tex
fix(paper-docs): fixed grammar in introduction and refactor results

@@
 % 用水量的上升、下降-结果解读
-We quantitatively demonstrated that the 98-UBR decreased, but the 87-WAS increased YRB's water use.
-The results challenged the previous analyses (they used to suggest that the 87-WAS ``has little practical effect'') because theoretically, the DSC method would show few differences between estimation and observation for a blank policy \cite{abadie2015,hill2021}.
-However, the significant net effect suggests the institutional shift (87-WAS) followed by backfired more water use even after controlling the environmental and economic variables (see \textit{Appendix~\nameref{secS2}}~Table~\ref{tab:variables}).
-The speeding up water use aligns with the sigh from then: the tragedy of frequently scrambling for water appeared in some provinces \cite{mao2000}.
-On the contrary, 98-UBR reduced the tragedy of water competition considerably by water licenses, so many studies attributed the restoration from river depletion mainly to the successful institutional shift \cite{chen2021,huangang2002,an2007}.
+Our results show that while 98-UBR decreased water use in the YRB, 87-WAS increased it.
+The results challenged previous analyses (i.e., suggesting that 87-WAS ''had little practical effect'') because theoretically, there should be few gaps between actual and synthetic YRB's water use if no effect is present \cite{abadie2015,hill2021}.
+However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{Appendix~\nameref{secS2}}~Table~\ref{tab:variables}).
+Increased water use aligns with concerns about frequently scrambling for water that were voiced in some provinces during this period \cite{mao2000}.
+On the contrary, the 98-UBR reduced water competition, so many studies attributed the restoration mainly to the successful introduction of this institution \cite{chen2021,huangang2002,an2007}.
 
@@
 Therefore, we theoretically abstracted the SES structures and analyzed how different structures shape different outcomes with provincial heterogeneity.
-Assuming that water is the factor input with decreasing marginal output of each province, we discuss the marginal return and optimal water use under three different cases (analogy to Figure~\ref{structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{Appendix~\nameref{secS4}}).
-The incentive for water overuse (compared to the water quotas) in each province derives from the mismatch between the benefits and costs of water use.
-Until water-use decisions are consolidated into unified management, each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive of water use, leading to higher water use.
-Therefore, the water users with higher capability are more stimulated by institutional shifts and away from the theoretically optimal water use under the unified allocation.
-Our model interprets the results from structural perspectives: excessive water use incentive induces the acceleration of extracting resources for future economic growth, and a unified institution is indispensable for sustainable water use.
 
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=0.9\linewidth]{outputs/economic_model.pdf}
-	\caption{
-		The relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
-	\label{fig:model}
-\end{figure}
+Thus, our model suggests that a unified scale-matched institution is indispensable for sustainable water use.
 

### 2022-06-11 docs/papers/01_manuscript/03_results.tex
fix(discussion.tex): fix grammar and structure according to Cumming's comments
BREAKING CHANGE:

@@
         Regulating differences for provinces in the YRB.
-        Red (the 87-WAS) and green (the 98-UBR) bars denote an increased or decreased ratio for actual water use relative to the estimate from the model, in the decade after the institutional shift.
+        Red (the 87-WAS) and green (the 98-UBR) bars denote an increased or decreased ratio for actual water use relative to the estimate from the model in the decade after the institutional shift.
         The grey bars indicate the proportions of actual water use for each province relative to their total water use in the decade after the institutional shift.

### 2022-06-11 docs/papers/01_manuscript/04_discussion.tex
fix(discussion.tex): fix grammar and structure according to Cumming's comments
BREAKING CHANGE:

@@
 However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{Appendix~\nameref{secS2}}~Table~\ref{tab:variables}).
-Increased water use aligns with concerns about frequently scrambling for water that were voiced in some provinces during this period \cite{mao2000}.
 On the contrary, the 98-UBR reduced water competition, so many studies attributed the restoration mainly to the successful introduction of this institution \cite{chen2021,huangang2002,an2007}.
 
-% 我们认为制度结构的变化是被长期忽略的重要因素
-We proposed that for these institutional shifts' divergent outcomes regarding water use, the key factors long ignored can be institutional structure changes.
-The structural building blocks we depicted in Figure~\ref{structure}, which were also reported in various types of SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}, and here twice reframed by the institutional shifts.
-Before the 98-UBR, the SES structure (i.e., fragment ecological units are linked to separate social actors) is more likely to be mismatched because isolated actors generally struggle with holistically maintaining interconnected ecosystems \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
-On the contrary, institutional alignments since the 98-UBR improved YRCC's authority in water use regulation to match the YRB in scale, thus leading to social-ecological fit and good outcomes -a ``scale-matched'' example \cite{cumming2020a,wang2019d}.
-Despite other reasons for the non-ideal effect of the 87-WAS being widely discussed \cite{huangang2002} (such as enforcement, feasibility, and equity), few radical improvements in the 98-UBR suggest an over-attention paid to non-structural impacts.
+\label{discussion-2}
+% discussion-2: 87的增加
+Increased water use after 87-WAS aligns with concerns about frequently scrambling for water in some provinces during this period \cite{mao2000}.
+Although reasons for the non-ideal effect of 87-WAS had been widely discussed \cite{huangang2002} (such as enforcement, feasibility, and equity), structural change has received limited attention.
+Our results show that the correlation between current water use and changed (increased or decreased) water use was significant after 87-WAS (Figure~\ref{regulating}).
+This ``major users use more'' pattern supports the hypothesis that separated stakeholders (individual provinces) will maximize resource demands (interpreted in our structure-based model, see Figure~\ref{fig:model}).
+Our theoretical analysis keeps in line with two facts.
+(1) When links The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
+The bargaining was also a process for matching their water shares to economic volume because the major water users (like Shandong and Henan) need more water than their quota (if only considering economic potentials when designing the institution) \cite{zuo2020}.
+(2) Those with more current water use might have greater bargaining power in water use allocation because of information asymmetry between decision-makers and stakeholders.
+Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligns with the fact that they appeared to the higher central government for larger shares \cite{wang2019a, wang2019d}.
 
-% \subsection{Linking structures with ISs outcomes}
-\label{discussion-2}
-% discussion-2: 机制解释
-Different individual provinces' water-use responses to the institutional shifts also support influences from SES structures.
-Our results show that the correlation between current water use and changed (increased or decreased) water use was significant after the 87-WAS.
-This ``major users use more'' pattern supports the hypothesis that separated stakeholder (individual province here) decides on linked ecological units for output maximization (water use).
-Therefore, we theoretically abstracted the SES structures and analyzed how different structures shape different outcomes with provincial heterogeneity.
-
-Thus, our model suggests that a unified scale-matched institution is indispensable for sustainable water use.
-
-% The effect of the institutional shifts once again demonstrated that it is not easy to have a win-win situation of environment and interests in complex coupled human-nature systems \cite{hegwood2022}, which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.
-Our above theoretical discussion also aligns with the evolution of the institutions in the YRB.
-When links The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
-The bargaining was also a process for matching their water shares to economic volume because the major water users (like Shandong and Henan) need more water than their quota (if only considering economic potentials when designing the institution) \cite{zuo2020}.
-Furthermore, those with more current water use might have greater bargaining power in water use allocation because of information asymmetry between decision-makers and stakeholders.
-Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligns with the fact that they appeared to the higher central government for larger shares \cite{wang2019a, wang2019d}.
+\label{discussion-3}
 On the contrary, after YRCC as governing agent coordinated between stakeholders since 98-UBR, the external appeal of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)
@@
 Then, the YRCC, the authority for approving water applications from all stakeholders, could adjust water use quotas according to the river conditions of the whole basin.
+During this period, proportional decreased water use of provinces decoupled with their ability (reflected by current water use volume), indicating a result of regulation.
 The 98-UBR thus led to expected institutional outcomes at a basin scale, indicating that successful governance of SES emerged by indirectly (or vertically) creating links between different stakeholders.
+Based on the structure, our model demonstrates that a unified scale-matched institution is also indispensable for sustainable water use.
+
+We explored causal linkages between SES structures and sustainability-related outcomes by quasi-natural experiments (institutional shifts imposed by central government) in the YRB.
+The YRB provides an informative case for two main reasons:
+(1) The top-down institutional shifts induced sharp changes in SES structures, enabling us to estimate their net effects quantitatively.
+(2) Since few large river basins have experienced such radical institutional shifts more than once, it provides a valuable natural experiment for understanding the impacts of structural changes in SESs on natural resources.
+
+The structural building blocks we depicted here (Figure~\ref{structure}) have also been reported in other SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}.
+Before 98-UBR, SES structure (i.e., fragment ecological units linked to separate social actors) was more likely to be mismatched because isolated actors generally struggle to maintain interconnected ecosystems holistically \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
+Institutional re-alignments since 98-UBR improved YRCC's authority and helped it match the scale of resource provisioning in the YRB, leading to enhanced social-ecological fit and better outcomes \cite{cumming2020a,wang2019d}.
+The comparison demonstrates again it's not easy to have a win-win situation in coupled human-nature systems \cite{hegwood2022}, which calls for an exceptional understanding of the SES structures \cite{bergsten2019, sayles2019}.
 
@@
 % \subsection{Limitation, insights and implications}
-\label{discussion-3}
+\label{discussion-4}
 % discussion-3: 启示、未来的展望
 
-We explored these causal linkages between the SES structures and sustainability (outcomes) by quasi-natural experiments (the institutional shifts) of the YRB, which provides a unique case for two main reasons:
-(1) The top-down institutional shifts induced sharp changes in SES structures in the YRB, enabling us to estimate their net effects quantitatively.
-(2) Since few basins experienced such radical institutional shifts more than once, the YRB provides comparable settings for understanding the structural changes of SESs.
-
-In complex coupled human-nature systems, however, our approach also has inevitable limitations:
-(1) The contributions of economic growth and institutional shifts are still incomparable because of intertwined causality (institutional changes can also influence the relative economic variables).
+In complex coupled human-nature systems, our approach has inevitable limitations:
+First, the contributions of economic growth and institutional shifts are still incomparable because of intertwined causality (institutional changes can also influence the relative economic variables).
 Still, our quasi-experiment approach focused on and proved that a change in water use trajectory follows the YRB's unique institutional shifts.

### 2022-06-11 docs/papers/01_manuscript/04_discussion.tex
fix(metadata.yaml,-manuscript.tex,-conclusion.tex): fix paper grammar and structure according to Cumming's comment
BREAKING CHANGE:

@@
 
-In complex coupled human-nature systems, our approach has inevitable limitations:
-First, the contributions of economic growth and institutional shifts are still incomparable because of intertwined causality (institutional changes can also influence the relative economic variables).
-Still, our quasi-experiment approach focused on and proved that a change in water use trajectory follows the YRB's unique institutional shifts.
-(2) When applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
-However, since the analysis had agreed on the importance of the two institutional shifts of 87-WAS and 98-UBR in water governance \cite{wang2012b}, our results on their effects still provide insights for understanding water governance.
-
-% 我们的模型结果与机制探讨加深了SES结构的理解，强化了孤立利益相关者形成的结构不利于制度解决环境问题的基本认识
-Our results and discussion deepen the understanding of SES structure and strengthen the basic knowledge that the mismatched structure (isolated stakeholders with the fragmentation of ecology) is not conducive to institutional solutions \cite{bodin2017b, ostrom2009, reyers2018}.
-Moreover, we report how another structure contributed to successful governance -the subsequent success of the 98-UBR institutional shift theoretically and practically proved the importance of social-ecological fit again.
+In complex coupled human-nature systems, our approach has inevitable limitations.
+First, the contributions of economic growth and institutional shifts are difficult to compare because of intertwined causality (institutional changes can also influence the relative economic variables);
+and second, when applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
+Our quasi-experiment approach nonetheless provides evidence supporting the view that a change in water use trajectory followed the YRB's unique institutional shifts and offers insights into water governance (and particularly the importance of having a scale-matched, basin-wide authority for water allocation solutions \cite{bodin2017b, ostrom2009, reyers2018})
+Moreover, the ultimate success of the 98-UBR institutional shift theoretically and practically proved the importance of social-ecological fit.
 For sustainability in the future, therefore, it is necessary to emphasize the necessity of strengthening connections between stakeholders by agents consistent with the scale of the ecological system.
-From these perspectives, we give two scenarios based on the marginal benefit model (see \textit{Appendix \nameref{secS5}}), which can inspire institutional design on how to reduce mismatches.
-For example, water rights transfers can be another way to emerge horizontal links between stakeholders that also have the potential to result in better water governance.
-In addition, the policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to respond to changing SES context \cite{reyers2018}.
+From these perspectives, two scenarios based on the marginal benefit model (see \textit{Appendix \nameref{secS5}}) can inspire institutional design on how to reduce mismatches.
+For example, water rights transfers may be another way to build horizontal links between stakeholders that also have the potential to result in better water governance.
+In addition, policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to a changing SES context \cite{reyers2018}.
 
 The structural building blocks that led to different outcomes are recurring motifs in global SESs, so our proposed mechanism is crucial to governing such coupled systems.
-Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions to sustainability (see \textit{Appendix \nameref{secS1}}) \cite{yu2019}.
+Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{Appendix \nameref{secS1}}) \cite{yu2019}.
 Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development \cite{wang2019a}.
 Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{Appendix~\nameref{secS1}}).
-These initiatives can benefit from our analysis by actively incorporating social-ecological matched building blocks when developing a new institutional shift for sustainability \cite{bodin2017b}.
-Moreover, our research provides a cautionary tale of how institutions can be double-edged \cite{hegwood2022}, while insights from the YRB can be a valuable guideline for SESs worldwide \cite{muneepeerakul2017, leslie2015}.
+Our analysis suggests that these initiatives can benefit by actively incorporating social-ecological matched building blocks when developing new institutions \cite{bodin2017b}.
+Moreover, our research provides a cautionary tale of how institutions can create perverse incentives \cite{hegwood2022}, while insights from the YRB contribute to improving guidelines for SESs management worldwide \cite{muneepeerakul2017, leslie2015}.

### 2022-06-11 docs/papers/01_manuscript/05_conclusion.tex
fix(metadata.yaml,-manuscript.tex,-conclusion.tex): fix paper grammar and structure according to Cumming's comment
BREAKING CHANGE:

--- 2022-04-17 docs/papers/01_manuscript/05_conclusion.tex
@@
 
-Intense water use in one of the most anthropogenic interfered large river basins, the Yellow River Basin (YRB), once led to overburdened drying up but finally had a successful restoration by sequential water governance practices.
-Focusing on two water-demand institutions, 87-WAS and the 98-UBR, we quantitatively analyzed how institutional shifts played a role in the water governance achievement of the YRB.
-Shifting throughout different SES structures framed by them, the observed water use of the YRB provinces had an $8.57\%$ increase than expected during the decade after the 87-WAS.
-Then, water use significantly decreased by  $4.9 billion m^3$ per year since the 98-UBR, while the model still suggests a $10.3 billion m^3$ annual increase in expectation.
-Finally, as differences in stakeholders' response to the institutional shifts, water use rises after the 87-WAS in provinces with more water uses (e.g., Inner Mongolia, Henan, and Shandong) while shrunk in nearly all provinces after the 98-UBR.
-Since the above results closely align with interpretations from a mathematical marginal benefits model, we can link the structures (widespread building blocks) and outcomes (goals of the institution, i.e., limiting water demands) by these quasi-natural experiments of the YRB.
-We demonstrate that social-ecological fits lead to successful governance where reducing independent stakeholders linked to fragmentation is an essential primary mechanism for good SES outcomes.
+Intense water use in one of the most anthropogenically altered large river basins, the Yellow River Basin (YRB), once led to drying up.
+Alterations of institutions eventually successfully restored water governance practices on a decadal time scale.
+We propose that the institutional shifts in the YRB (87-WAS and 98-UBR) framed two different SES structures and depicted them as widespread building blocks.
+We quantitatively estimate the net effects of these changes in the YRB and analyze the reasons from SES structural perspectives.
+Our results show that the historical records, the responses from stakeholders to structural changes, and the theoretical analysis from the marginal benefits model all support that fragmented ecological units linked to separate social actors frames a mismatched SES structure.
+Through the quasi-natural experiments of the YRB, we demonstrate that social-ecological fits can lead to successful SESs management worldwide with better sustainability outcomes.

### 2022-06-11 docs/papers/01_manuscript/abstract.tex
fix(metadata.yaml,-manuscript.tex,-conclusion.tex): fix paper grammar and structure according to Cumming's comment
BREAKING CHANGE:

Increasing competition for water is leading to depletion of freshwater globally and calls for an urgent transformation of water governance. To better understand how institutions contribute to water governance, we quantified institutional shifts for the Yellow River Basin (YRB).  The YRB is a valuable case study because it is one of the most anthropogenically altered large river basins. It was first overdrawn, then dried up, and finally has been successfully restored. Our results suggest that two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), framed different social-ecological system (SES) structures. During the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected while 98-UBR successfully decreased total water use, ultimately. Specifically, 87-WAS stimulated increased water use in some provinces (e.g., Inner Mongolia, Henan, and Shandong), but 98-UBR regulated nearly all provinces. A mathematical marginal benefits model supports the hypothesis that regional variations were driven by SES structural changes. The quasi-natural experimental setting of the YRB and its significant structural changes over time offer deep insights into the links between SESs structures and outcomes, providing valuable guidelines for SESs worldwide that are facing water depletion.

### 2022-06-12 docs/papers/00_cover_letter/abstract.tex
docs(manuscript.tex-and-all-relative-files.): make LaTeX format better, delete unnecessary files
BREAKING CHANGE:

--- 2022-03-29 docs/papers/00_cover_letter/abstract.tex
@@
-Increasing competition for water is challenging management institutions of large river basins worldwide.
-Institutions that successfully support sustainable water resource use are structurally well-aligned with water provisioning and social-ecological demands.
-However, what constitutes a well-aligned institution in this context is poorly understood.
-We analyzed institutional shifts in water governance, exploiting two quasi-natural experiments of the Yellow River Basin.
-First, using a Differenced Synthetic Control method to control economic and environmental contexts, we found the Water Allocation Scheme (87-WAS), which intended to limit water use, unexpectedly resulting in a structural mismatch of the social-ecological system (SES) with increased water use.
-We then applied a mathematical model to suggest that incentive distortions contributed to the rapid water use under the typical mismatched SES structure.
-Our analysis highlights the need to evaluate institutional fit in coupled human and natural systems carefully.
+Increasing competition for water is leading to depletion of freshwater globally and calls for an urgent transformation of water governance.
+To better understand how institutions contribute to water governance, we quantified institutional shifts for the Yellow River Basin (YRB).
+The YRB is a valuable case study because it is one of the most anthropogenically altered large river basins.
+It was first overdrawn, then dried up, and finally has been successfully restored.
+Our results suggest that two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), framed different social-ecological system (SES) structures.
+During the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected while 98-UBR successfully decreased total water use, ultimately.
+Specifically, 87-WAS stimulated increased water use in some provinces (e.g., Inner Mongolia, Henan, and Shandong), but 98-UBR regulated nearly all provinces.
+A mathematical economic model supports the hypothesis that regional variations were driven by SES structural changes.
+The quasi-natural experimental setting of the YRB and its significant structural changes over time offer deep insights into the links between SESs structures and outcomes, providing valuable guidelines for SESs worldwide that are facing water depletion.

### 2022-06-12 docs/papers/01_manuscript/01_introduction.tex
docs(manuscript.tex-and-all-relative-files.): make LaTeX format better, delete unnecessary files
BREAKING CHANGE:

@@
 \cite{giuliani2013, falkenmark2019, jaeger2019}.
-In the context of future climate change, the gap between supply and demand for water resources in large river basins is expected to become increasingly more prominent.
-% TODO citation
+In the context of future climate change, the gap between supply and demand for water resources in large river basins is expected to become increasingly more prominent \cite{florke2018, yoon2021}.
 Balancing the water demands of ecosystems and development in heavily human-dominated river basins is a challenge not just for China but also across many large river basins worldwide.
@@
 % 第三段 过去管理的经验，断流的严重程度，连续多少没有断流，少有的解决断流的大河。治理成功的流域？分析背后的机制，基础。往用水上靠。
-In response, Chinese authorities implemented several ambitious water management practices in the YRB to relieve water stress, such as reservoir regulation, the South-to-north Water Diversion Project (WDP), the 1987 Water Allocation Scheme (87-WAS), and the 1998 Unified Basinal Regulation (98-UBR).
+In response, Chinese authorities implemented several ambitious water management practices in the YRB to relieve water stress, such as reservoir regulation, the South-to-north Water Diversion Project (WDP), the 1987 Water Allocation Scheme (87-WAS), and the 1998 Unified Basinal Regulation (98-UBR) \cite{long2020, wang2019d}.
 Those efforts led to ecological restoration of wetlands and estuarine delta, and drying up has been avoided for over 20 years, widely considered considerable management achievements.
@@
 
-While researchers have carefully evaluated and quantified the effects of engineering solutions, there have been few attempts to assess institutional contributions to successful water governance in the YRB.
+While researchers have carefully evaluated and quantified the effects of engineering solutions\cite{long2020}, there have been few attempts to assess institutional contributions to successful water governance in the YRB.
 % 第四段 目标 制度变化。是不是制度变化产生的，如果是的话怎么影响。
@@
 Some institutional advances have had desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d}, and collaborative water governance systems in Europe \cite{green2013}).
-However, imposing institutional changes on a large, complex river basin may create or destroy hundreds of different connections between social agents and ecological units, where matched social-ecological structures are not ubiquitous.
+However, imposing institutional changes on a large, complex river basin may create or destroy hundreds of connections between social agents and ecological units, where matched social-ecological structures are not ubiquitous.
 
 To better understand how water management institutions can be designed to fit their social-ecological context, we used data on changes in official documents following institutional shifts (the 87-WAS and the 98-UBR) to describe changes in the SES structures associated with the YRB from 1979 to 2008.
-We then used Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without institutional shifts (\textit{\hyperref[{sec:methods}]{Methods}} and \textit{Appendix~\nameref{secS2}}).
+We then used Differenced Synthetic Control (DSC) method \cite{arkhangelsky2021}, which considers economic growth and natural background, to estimate theoretical water use scenarios without institutional shifts (\textit{\hyperref[{sec:methods}]{Methods}} and \textit{\nameref{secS2}}).
 It allowed us to create a counterfactual against which to explore the mechanisms linking SESs structure and outcomes for a deeper understanding of the potential role of institutions in water governance worldwide.

### 2022-06-12 docs/papers/01_manuscript/02_structures.tex
docs(manuscript.tex-and-all-relative-files.): make LaTeX format better, delete unnecessary files
BREAKING CHANGE:

@@
 % 制度变动综述
-The institutional shifts in the YRB in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among YRB's water governance practices (\textit{Appendix}~\nameref{secS1}).
+The institutional shifts in the YRB in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among YRB's water governance practices (\textit{\nameref{secS1}}).
 Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
-Therefore, the YRCC had no links to the provinces regarding water use before 1987, and the provinces could link directly to the Yellow River reaches (Figure~\ref{structure}~C).
+Therefore, the YRCC had no links to the provinces regarding water use before 1987, and the provinces could link directly to the Yellow River reaches (Figure~\ref{fig:structure}~C).
 To shrink water deficits, in 87-WAS, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin (Table~\ref{tab:quota}).
 Simultaneously, according to the extracted information from documents of the 87-WAS issued by national ministries, the YRCC started to report water use in each reach.
-As it was the first time YRCC's responsibility involved water use, we introduced new links between the YRCC and the ecological nodes (Figure~\ref{structure}~C).
+As it was the first time YRCC's responsibility involved water use, we introduced new links between the YRCC and the ecological nodes (Figure~\ref{fig:structure}~C).
 However, the controversial 87-WAS did not resolve water depletion.
@@
 Information from the 98-UBR documents demonstrated that the provinces had to apply their plan for an annual water use license to YRCC instead of direct access to the Yellow River water.
-Thus, the YRCC has been linked to the provinces since 1998 (Figure~\ref{structure}~C).
+Thus, the YRCC has been linked to the provinces since 1998 (Figure~\ref{fig:structure}~C).
 
@@
 		Institutional shifts and related SES structures in the Yellow River Basin (YRB).
-		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{Appendix \nameref{secS1}} Table~\ref{tab:quota}).
+		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{\nameref{secS1}} Table~\ref{tab:quota}).
 The national administrations are the ultimate authority in issuing water governance policies, which are often implemented by basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
@@
 The YRCC only monitors water withdrawals at that time.
-		\textbf{C.} Institutional shifts and following structures changes (details in \textit{Appendix \nameref{secS1}}).
+		\textbf{C.} Institutional shifts and following structures changes (details in \textit{\nameref{secS1}}).
 (1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from the connected ecological unit (the reach of Yellow River, denoted by the blue circles).
@@
 	}
-	\label{structure}
+	\label{fig:structure}
 \end{figure*}

### 2022-06-12 docs/papers/01_manuscript/03_results.tex
docs(manuscript.tex-and-all-relative-files.): make LaTeX format better, delete unnecessary files
BREAKING CHANGE:

@@
 \label{result-1-p2}
-Our estimation of theoretical water use suggests that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without an institutional shift (Figure~\ref{main_results}A).
+Our estimation of theoretical water use suggests that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without an institutional shift (Figure~\ref{fig:main_results}A).
 From 1988 to 1998, on average, while the estimation of annual water use only suggests $974.34$ billion $m^3$, the observed water use of the YRB provinces reached $1038.36$ billion $m^3$ (an increase of $6.57\%$).
 However, after the institutional change in 1998 (98-UBR), trends of increasing water use appeared to be effectively suppressed.
-From 1998 to 2008, the total observed water use decreased by $0.49$ billion $m^3/yr$ per year, while the estimation of water use still suggests $0.82$ billion $m^3/yr$ increases (Figure~\ref{main_results} B).
-The increased water uses after 87-WAS aligns with the severe drying-down of the surface streamflow from 1987 to 1998, an obvious indicator of river degradation and environmental crisis (Figure~\ref{main_results}C).
-On the other hand, the 98-UBR ended river depletion, despite subsequent increases in drought intensity (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{main_results}C).
+From 1998 to 2008, the total observed water use decreased by $0.49$ billion $m^3/yr$ per year, while the estimation of water use still suggests $0.82$ billion $m^3/yr$ increases (Figure~\ref{fig:main_results} B).
+The increased water uses after 87-WAS aligns with the severe drying-down of the surface streamflow from 1987 to 1998, an obvious indicator of river degradation and environmental crisis (Figure~\ref{fig:main_results}C).
+On the other hand, the 98-UBR ended river depletion, despite subsequent increases in drought intensity (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{fig:main_results}C).
 
@@
     }
-    \label{main_results}
+    \label{fig:main_results}
 \end{figure*}
@@
 Our results also suggest differences between patterns of provinces in their responses to the two institutional regulating.
-During the decade after the 87-WAS, the major water-using provinces (e.g., Inner Mongolia, Henan, Shandong) had apparent accelerations (Figure~\ref{regulating}).
+During the decade after the 87-WAS, the major water-using provinces (e.g., Inner Mongolia, Henan, Shandong) had apparent accelerations (Figure~\ref{fig:regulating}).
 The proportion of increased (or decreased) water use for each province (over the estimated water use by the model) correlated significantly (partial correlation coefficient is $0.77$, $p<0.05$) with actual water use from the Yellow River.
@@
     }
-    \label{regulating}
+    \label{fig:regulating}
 \end{figure*}
 
-\subsection{Structure-based marginal benefits model}
+\subsection{Structure-based marginal benefit analysis}
 \label{result-4}
-We then compared the marginal returns and optimal water use under three different structural cases theoretically (analogy to Figure~\ref{structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{Appendix~\nameref{secS4}}).
+We then compared the marginal returns and optimal water use under three different structural cases theoretically (analogy to Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
 Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentive for water use in each province derives from the mismatch between the benefits and costs of water use.
@@
 	\caption{
-		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
+		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
 	\label{fig:model}

### 2022-06-12 docs/papers/01_manuscript/04_discussion.tex
docs(manuscript.tex-and-all-relative-files.): make LaTeX format better, delete unnecessary files
BREAKING CHANGE:

@@
 The results challenged previous analyses (i.e., suggesting that 87-WAS ''had little practical effect'') because theoretically, there should be few gaps between actual and synthetic YRB's water use if no effect is present \cite{abadie2015,hill2021}.
-However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{Appendix~\nameref{secS2}}~Table~\ref{tab:variables}).
+However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{\nameref{secS2}}~Table~\ref{tab:variables}).
 On the contrary, the 98-UBR reduced water competition, so many studies attributed the restoration mainly to the successful introduction of this institution \cite{chen2021,huangang2002,an2007}.
@@
 Although reasons for the non-ideal effect of 87-WAS had been widely discussed \cite{huangang2002} (such as enforcement, feasibility, and equity), structural change has received limited attention.
-Our results show that the correlation between current water use and changed (increased or decreased) water use was significant after 87-WAS (Figure~\ref{regulating}).
-This ``major users use more'' pattern supports the hypothesis that separated stakeholders (individual provinces) will maximize resource demands (interpreted in our structure-based model, see Figure~\ref{fig:model}).
+Our results show that the correlation between current water use and changed (increased or decreased) water use was significant after 87-WAS (Figure~\ref{fig:regulating}).
+This ``major users use more'' pattern supports the hypothesis that separated stakeholders (individual provinces) will response to structure for utility maximization (interpreted in our structure-based model, see Figure~\ref{fig:model}).
 Our theoretical analysis keeps in line with two facts.
@@
 Then, the YRCC, the authority for approving water applications from all stakeholders, could adjust water use quotas according to the river conditions of the whole basin.
-During this period, proportional decreased water use of provinces decoupled with their ability (reflected by current water use volume), indicating a result of regulation.
+During this period, proportional decreased water use of provinces decoupled with their ability (reflected by current water use volume), indicating a result of the regulation (see \nameref{result-3}).
 The 98-UBR thus led to expected institutional outcomes at a basin scale, indicating that successful governance of SES emerged by indirectly (or vertically) creating links between different stakeholders.
@@
 
-The structural building blocks we depicted here (Figure~\ref{structure}) have also been reported in other SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}.
+The structural building blocks we depicted here (Figure~\ref{fig:structure}) have also been reported in other SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}.
 Before 98-UBR, SES structure (i.e., fragment ecological units linked to separate social actors) was more likely to be mismatched because isolated actors generally struggle to maintain interconnected ecosystems holistically \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
@@
 For sustainability in the future, therefore, it is necessary to emphasize the necessity of strengthening connections between stakeholders by agents consistent with the scale of the ecological system.
-From these perspectives, two scenarios based on the marginal benefit model (see \textit{Appendix \nameref{secS5}}) can inspire institutional design on how to reduce mismatches.
+From these perspectives, two scenarios based on the marginal benefit analysis (see \textit{\nameref{secS5}}) can inspire institutional design on how to reduce mismatches.
 For example, water rights transfers may be another way to build horizontal links between stakeholders that also have the potential to result in better water governance.
@@
 The structural building blocks that led to different outcomes are recurring motifs in global SESs, so our proposed mechanism is crucial to governing such coupled systems.
-Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{Appendix \nameref{secS1}}) \cite{yu2019}.
+Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{\nameref{secS1}}) \cite{yu2019}.
 Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development \cite{wang2019a}.
-Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{Appendix~\nameref{secS1}}).
+Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{\nameref{secS1}}).
 Our analysis suggests that these initiatives can benefit by actively incorporating social-ecological matched building blocks when developing new institutions \cite{bodin2017b}.

### 2022-06-12 docs/papers/01_manuscript/05_conclusion.tex
docs(manuscript.tex-and-all-relative-files.): make LaTeX format better, delete unnecessary files
BREAKING CHANGE:

@@
 We quantitatively estimate the net effects of these changes in the YRB and analyze the reasons from SES structural perspectives.
-Our results show that the historical records, the responses from stakeholders to structural changes, and the theoretical analysis from the marginal benefits model all support that fragmented ecological units linked to separate social actors frames a mismatched SES structure.
+Our results show that the historical records, the responses from stakeholders to structural changes, and the theoretical analysis from the marginal benefits analysis all support that fragmented ecological units linked to separate social actors frames a mismatched SES structure.
 Through the quasi-natural experiments of the YRB, we demonstrate that social-ecological fits can lead to successful SESs management worldwide with better sustainability outcomes.

### 2022-06-12 docs/papers/01_manuscript/06_methods.tex
docs(manuscript.tex-and-all-relative-files.): make LaTeX format better, delete unnecessary files
BREAKING CHANGE:

@@
 We first abstract the SES structures of water used in the YRB from 1979 to 2008, where two institutional shifts split the period into three pieces.
-For preprocessing the data, we use Principal Components Analysis (PCA) method to reduce the dimensionality of variables affecting the total water use.
+To process the data, we use the Principal Components Analysis (PCA) method to reduce the dimensionality of variables affecting the total water use.
 We then estimated the net effects of two institutional shifts on total water use, changing trends, and differences of the YRB's provinces, by Differenced Synthetic Control (DSC) method \cite{arkhangelsky2021}.
-Finally, for discussion, we created an economic model based on marginal revenue to provide the observed pattern of water use changes with a theoretical interpretation.
+Finally, for theoretical discussion, we developed a marginal benefit analysis based on identified SES structures to provide the observed pattern of water use changes with a theoretical interpretation.
 
@@
 We apply the network \cite{bodin2017b} approach to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit (the YRCC) into general building blocks (or motifs) (see Figure~\ref{framework}), from the official documents.
-Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures, and the network-based approach is to abstract connections between entities into links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.
+Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures.
+The network-based approach is to abstract connections between entities into links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.
 In this study, we examined the official documents of the two institutional shifts of concern (87-WAS and 98-UBR, see \textit{Appendix \nameref{secS1}} for details).
@@
 \subsection{Differenced Synthetic Control}\label{sec:DSC}
-We estimate water use without institutional shifts effect using the Differenced Synthetic Control (DSC) method.
+Using the Differenced Synthetic Control (DSC) method, we estimate water use without the effect of the institutional shift.
 The DSC method is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadie2010, abadie2015, hill2021}.
@@
 
-\subsection{Economic model}\label{sec:model}
-To infer the mechanisms underlying the results, we developed an economic model based on marginal revenue to analyze how the institutional shift could have led to differences in water use.
+\subsection{Marginal benefits analysis}\label{sec:model}
+To infer the mechanisms underlying the results, we developed an marginal benefits analysis based on marginal revenue to analyze how the institutional shift could have led to differences in water use.
 
 \begin{ass}
-    (Water-dependent production) Because of irreplaceability, water is assumed to be the only input of the production function with two types of production efficiency.
+    (Water-dependent production) Because of irreplaceably, water is assumed to be the only production function input with two production efficiency types.
 \end{ass}
@@
 \begin{ass}
-    (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved, the cost of water use is equally assigned to each province.
+    (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin, the water use cost is equally assigned to each province.
 \end{ass}
@@
 
-Under the above-simplified assumptions, we demonstrate three cases -corresponding to the abstracted SES structures (Figure~\ref{structure}), inference of how SES structure alters the expected marginal benefits and costs of provinces making decisions.
+Under the above-simplified assumptions, we demonstrate three cases -corresponding to the abstracted SES structures (Figure~\ref{fig:structure}), inference of how SES structure alters the expected marginal benefits and costs of provinces making decisions.
 As one of the possible interpretations for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.

### 2022-06-12 docs/papers/01_manuscript/manuscript.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:
docs(manuscript.tex-and-all-relative-files.): make LaTeX format better, delete unnecessary files
BREAKING CHANGE:

@@
 \usepackage{multirow}
+\usepackage[switch]{lineno}
 \setenumerate{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=0pt}
@@
 
-\affil{$^4$The research for this article was financed by.......
-The authors thank.......
-for insightful comments and .......
-for expert research assistance.
+\affil{$^4$The research for this article was financed by the National Natural Science Foundation of China (CN) (Grant Nos.
+NSFC 42041007).
+The authors thank Fuqiang Tian for his insightful comments.
 A supplementary online appendix is available with this article at the \em{National Science Review} website.}
@@
 %\authornote{Shuang Song and Huiyu Wen equally contributed to this work.}
-
+\pagewiselinenumbers
 \abstract[ABSTRACT]{
-    \input{abstract}
+     Increasing competition for water is leading to depletion of freshwater globally and calls for an urgent transformation of water governance.
+To better understand how institutions contribute to water governance, we quantified institutional shifts for the Yellow River Basin (YRB).
+The YRB is a valuable case study because it is one of the most anthropogenically altered large river basins.
+It was first overdrawn, then dried up, and finally has been successfully restored.
+Our results suggest that two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), framed different social-ecological system (SES) structures.
+During the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
+Furthermore, these heterogeneous effects and a further theoretical marginal benefits analysis support the hypothesis that SES structural changes play a vital role in YRB's restoration.
+This quasi-natural experiment of the YRB offers profound insights into the links between SESs structures and outcomes, providing valuable guidelines for water depletion basins worldwide.
      }  %! Notice input
@@
 \label{appendix}
+\renewcommand{\figurename}{Supplementary Figure}
+\renewcommand{\appendixname}{Appendix~\Alph{section}}
+\setcounter{section}{0}
 
-\section{S1: Contexts of institutional shifts}\label{secS1}
+\section{Appendix~A: Contexts of institutional shifts}\label{secS1}
+\renewcommand{\thefigure}{A\arabic{figure}}
+\renewcommand{\thetable}{A\arabic{table}}
+\setcounter{figure}{0}
+\setcounter{table}{0}
 \input{../02_appendix/01_institution_context.tex}
 
-\section{S2: Sensitivity analysis}\label{secS2}
+\section{Appendix~B: Robustness of DSC method}\label{secS2}
+\renewcommand{\thefigure}{B\arabic{figure}}
+\renewcommand{\thetable}{B\arabic{table}}
+\setcounter{figure}{0}
+\setcounter{table}{0}
 \input{../02_appendix/02_method_details.tex}
 
-\section{S2: Methods in details}\label{secS3}
-\input{../02_appendix/03_results_appendix.tex}
+% \section{S2: Methods in details}\label{secS3}
+% \input{../02_appendix/03_results_appendix.tex}
 
-\section{S3: Optimization model for water use}\label{secS4}
+\section{Appendix~C: Optimization model for water use}\label{secS4}
+\renewcommand{\thefigure}{C\arabic{figure}}
+\renewcommand{\thetable}{C\arabic{table}}
+\setcounter{figure}{0}
+\setcounter{table}{0}
 \input{../02_appendix/04_theoretical_model.tex}
 
-\section{S4: Model extensions}\label{secS5}
+\section{Appendix~D: Model extensions}\label{secS5}
+\renewcommand{\thefigure}{D\arabic{figure}}
+\renewcommand{\thetable}{D\arabic{table}}
+\setcounter{figure}{0}
+\setcounter{table}{0}
 \input{../02_appendix/05_model_extensions.tex}

### 2022-06-12 docs/papers/02_appendix/01_institution_context.tex
docs(manuscript.tex-and-all-relative-files.): make LaTeX format better, delete unnecessary files
BREAKING CHANGE:

@@
 % 基于上述分析，我们抽象出了两次制度转变之后的SES结构变化如正文的图1C所示。
-Based on the above documents, we abstracted the structural changes of SES (see \textit{Appendix S2}) after the two institutional changes, as shown in Figure~\ref{structure}~C.
+Based on the above documents, we abstracted the structural changes of SES (see \textit{Appendix S2}) after the two institutional changes, as shown in Figure~\ref{fig:structure}~C.
 

### 2022-06-12 docs/papers/02_appendix/04_theoretical_model.tex
docs(manuscript.tex-and-all-relative-files.): make LaTeX format better, delete unnecessary files
BREAKING CHANGE:

@@
 
-To understand the mechanisms through which the SES structure impacts provincial water use, we developed a dynamic economic model to analyze how institutional mismatch could have led to the changes in water use, especially among provinces with high incentives for excess water use.
+To understand the mechanisms through which the SES structure impacts provincial water use, we developed a dynamic marginal benefits analysis to analyze how institutional mismatch could have led to the changes in water use, especially among provinces with high incentives for excess water use.
 Specifically, we modeled individual provincial decision-making in water resources before quota execution.

### 2022-06-21 docs/papers/01_manuscript/01_introduction.tex
docs(all-paper): submit 1.7.1
BREAKING CHANGE:

@@
 Widespread freshwater scarcity and overuse challenge the sustainability of large river basins, resulting in systematic risks to economies, societies, and ecosystems globally \cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
-With steadily increasing demand, competition for water causes depletion of freshwater globally.
-Therefore, it creates a strong need for an urgent transformation of the water governance system to improve water use conservation \cite{gleick2010, ziolkowska2016, wang2019d}.
+With steadily increasing demand, competition for water causes depletion of freshwater globally and creates a strong need for an urgent transformation of the water governance system to improve water use conservation \cite{gleick2010, ziolkowska2016, wang2019d}.
 Despite worldwide efforts to govern water sustainably, overuse and the resulting degradation of large river basins are not easily reversible.
@@
 In the context of future climate change, the gap between supply and demand for water resources in large river basins is expected to become increasingly more prominent \cite{florke2018, yoon2021}.
-Balancing the water demands of ecosystems and development in heavily human-dominated river basins is a challenge not just for China but also across many large river basins worldwide.
+Balancing the water demands of ecosystems and development in heavily human-dominated river basins is a challenge not just for China, but also across many large river basins worldwide.
 
@@
 In response, Chinese authorities implemented several ambitious water management practices in the YRB to relieve water stress, such as reservoir regulation, the South-to-north Water Diversion Project (WDP), the 1987 Water Allocation Scheme (87-WAS), and the 1998 Unified Basinal Regulation (98-UBR) \cite{long2020, wang2019d}.
-Those efforts led to ecological restoration of wetlands and estuarine delta, and drying up has been avoided for over 20 years, widely considered considerable management achievements.
-Unlike engineering providing further water supply, institutional strategies like the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, authority at a basin-level) focused mainly on limiting demands of water use.
-Such institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human and natural system, including interplays between social actors, ecological units, or between social and ecological system elements
+Those efforts led to ecological restoration of wetlands and the estuarine delta. Drying up has been avoided for over 20 years, which is widely considered a substantial management achievement.
+Instead of relying on engineering to increase water supply, institutional strategies like the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, authority at a basin-level) focused mainly on limiting demand for water.
+Institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human and natural system, including interplays between social actors, ecological units, or between social and ecological system elements
 \cite{young2008,cumming2020b,lien2020, bodin2017b}.
-Therefore, understanding those complex interplays is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
+Understanding these complex interplays is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
 
-While researchers have carefully evaluated and quantified the effects of engineering solutions\cite{long2020}, there have been few attempts to assess institutional contributions to successful water governance in the YRB.
+While researchers have carefully evaluated and quantified the effects of engineering solutions on water supply\cite{long2020}, there have been few attempts to assess institutional contributions to successful water governance in the YRB.
 % 第四段 目标 制度变化。是不是制度变化产生的，如果是的话怎么影响。
@@
 To better understand how water management institutions can be designed to fit their social-ecological context, we used data on changes in official documents following institutional shifts (the 87-WAS and the 98-UBR) to describe changes in the SES structures associated with the YRB from 1979 to 2008.
-We then used Differenced Synthetic Control (DSC) method \cite{arkhangelsky2021}, which considers economic growth and natural background, to estimate theoretical water use scenarios without institutional shifts (\textit{\hyperref[{sec:methods}]{Methods}} and \textit{\nameref{secS2}}).
-It allowed us to create a counterfactual against which to explore the mechanisms linking SESs structure and outcomes for a deeper understanding of the potential role of institutions in water governance worldwide.
+We then used a method called `Differenced Synthetic Control (DSC)' \cite{arkhangelsky2021}, which considers economic growth and natural background, to estimate theoretical water use scenarios without institutional shifts (\textit{\hyperref[{sec:methods}]{Methods}} and \textit{\nameref{secS2}}).
+This approach allowed us to create a counterfactual against which to explore the mechanisms linking SESs structure and outcomes for a deeper understanding of the potential role of institutions in water governance worldwide.

### 2022-06-21 docs/papers/01_manuscript/02_structures.tex
docs(all-paper): submit 1.7.1
BREAKING CHANGE:

@@
 Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
-Therefore, the YRCC had no links to the provinces regarding water use before 1987, and the provinces could link directly to the Yellow River reaches (Figure~\ref{fig:structure}~C).
+The YRCC had no links to the provinces regarding water use before 1987, and the provinces could link directly to the Yellow River reaches (Figure~\ref{fig:structure}~C).
 To shrink water deficits, in 87-WAS, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin (Table~\ref{tab:quota}).
 Simultaneously, according to the extracted information from documents of the 87-WAS issued by national ministries, the YRCC started to report water use in each reach.
-As it was the first time YRCC's responsibility involved water use, we introduced new links between the YRCC and the ecological nodes (Figure~\ref{fig:structure}~C).
+As it was the first time the responsibility of the YRCC involved water use, this introduced new links between the YRCC and the ecological nodes (Figure~\ref{fig:structure}~C).
 However, the controversial 87-WAS did not resolve water depletion.

### 2022-06-21 docs/papers/01_manuscript/03_results.tex
docs(all-paper): submit 1.7.1
BREAKING CHANGE:

@@
 \label{result-4}
-We then compared the marginal returns and optimal water use under three different structural cases theoretically (analogy to Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
-Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentive for water use in each province derives from the mismatch between the benefits and costs of water use.
+We compared the theoretical marginal returns and optimal water use under three different structural cases (analogy to Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
+Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.
 Until water-use decisions are consolidated into unified management, each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive to use water, leading to higher water use.

### 2022-06-21 docs/papers/01_manuscript/04_discussion.tex
docs(all-paper): submit 1.7.1
BREAKING CHANGE:

@@
 Our results show that while 98-UBR decreased water use in the YRB, 87-WAS increased it.
-The results challenged previous analyses (i.e., suggesting that 87-WAS ''had little practical effect'') because theoretically, there should be few gaps between actual and synthetic YRB's water use if no effect is present \cite{abadie2015,hill2021}.
+The results challenged previous analyses (i.e., suggesting that 87-WAS ''had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present \cite{abadie2015,hill2021}.
 However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{\nameref{secS2}}~Table~\ref{tab:variables}).
@@
 Our results show that the correlation between current water use and changed (increased or decreased) water use was significant after 87-WAS (Figure~\ref{fig:regulating}).
-This ``major users use more'' pattern supports the hypothesis that separated stakeholders (individual provinces) will response to structure for utility maximization (interpreted in our structure-based model, see Figure~\ref{fig:model}).
-Our theoretical analysis keeps in line with two facts.
-(1) When links The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
-The bargaining was also a process for matching their water shares to economic volume because the major water users (like Shandong and Henan) need more water than their quota (if only considering economic potentials when designing the institution) \cite{zuo2020}.
-(2) Those with more current water use might have greater bargaining power in water use allocation because of information asymmetry between decision-makers and stakeholders.
-Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligns with the fact that they appeared to the higher central government for larger shares \cite{wang2019a, wang2019d}.
+This ``major users use more'' pattern supports the hypothesis that separated stakeholders (individual provinces) will response to structure by maximizing utility (interpreted in our structure-based model, see Figure~\ref{fig:model}).
+
+The validity of our theoretical analysis is supported two facts:
+(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
+The bargaining was also a process for matching water shares to economic volume, because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution) \cite{zuo2020}.
+(2) Provinces with higher current water use might have greater bargaining power in water use allocation because of information asymmetry between decision-makers and stakeholders.
+Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligned with their appeals to the higher central government for larger shares \cite{wang2019a, wang2019d}.
 
 \label{discussion-3}
-On the contrary, after YRCC as governing agent coordinated between stakeholders since 98-UBR, the external appeal of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)
+After 98-UBR, the YRCC could adjust water use quotas to match river conditions for the whole YRB.
+When the YRCC began to coordinate among stakeholders, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)
 \cite{krieger1955, ostrom1990}.
-Then, the YRCC, the authority for approving water applications from all stakeholders, could adjust water use quotas according to the river conditions of the whole basin.
-During this period, proportional decreased water use of provinces decoupled with their ability (reflected by current water use volume), indicating a result of the regulation (see \nameref{result-3}).
+During this period, proportional decreased water use of provinces indicated a positive result of regulation (see \nameref{result-3}).
 The 98-UBR thus led to expected institutional outcomes at a basin scale, indicating that successful governance of SES emerged by indirectly (or vertically) creating links between different stakeholders.
-Based on the structure, our model demonstrates that a unified scale-matched institution is also indispensable for sustainable water use.
+Our model demonstrates that in this case, a unified scale-matched institution was indispensable for sustainable water use.
 
@@
 (1) The top-down institutional shifts induced sharp changes in SES structures, enabling us to estimate their net effects quantitatively.
-(2) Since few large river basins have experienced such radical institutional shifts more than once, it provides a valuable natural experiment for understanding the impacts of structural changes in SESs on natural resources.
+(2) Since few large river basins have experienced such radical institutional shifts more than once, this case study provides a valuable natural experiment for understanding the impacts of structural changes in SESs on natural resources.
 
@@
 Before 98-UBR, SES structure (i.e., fragment ecological units linked to separate social actors) was more likely to be mismatched because isolated actors generally struggle to maintain interconnected ecosystems holistically \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
-Institutional re-alignments since 98-UBR improved YRCC's authority and helped it match the scale of resource provisioning in the YRB, leading to enhanced social-ecological fit and better outcomes \cite{cumming2020a,wang2019d}.
-The comparison demonstrates again it's not easy to have a win-win situation in coupled human-nature systems \cite{hegwood2022}, which calls for an exceptional understanding of the SES structures \cite{bergsten2019, sayles2019}.
+Institutional re-alignments since 98-UBR improved the authority of the YRCC and helped it match the scale of resource provisioning in the YRB, leading to enhanced social-ecological fit and better outcomes \cite{cumming2020a,wang2019d}.
+The comparison demonstrates again the challenge of finding win-win situations in coupled human-nature systems \cite{hegwood2022}, and the need more deeply understand the role of social-ecological structures \cite{bergsten2019, sayles2019}.
 
@@
 
-In complex coupled human-nature systems, our approach has inevitable limitations.
-First, the contributions of economic growth and institutional shifts are difficult to compare because of intertwined causality (institutional changes can also influence the relative economic variables);
+Our approach has some inevitable limitations.
+First, the contributions of economic growth and institutional shifts are difficult to distinguish because of intertwined causality (institutional changes can also influence the relative economic variables);
 and second, when applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
-Our quasi-experiment approach nonetheless provides evidence supporting the view that a change in water use trajectory followed the YRB's unique institutional shifts and offers insights into water governance (and particularly the importance of having a scale-matched, basin-wide authority for water allocation solutions \cite{bodin2017b, ostrom2009, reyers2018})
+Our quasi-experiment approach nonetheless provides evidence supporting the view that there was a change in water use trajectory following the YRB's unique institutional shifts, and offers insights into water governance (and particularly the importance of having a scale-matched, basin-wide authority for water allocation solutions \cite{bodin2017b, ostrom2009, reyers2018})
 Moreover, the ultimate success of the 98-UBR institutional shift theoretically and practically proved the importance of social-ecological fit.

### 2022-06-21 docs/papers/01_manuscript/06_methods.tex
docs(all-paper): submit 1.7.1
BREAKING CHANGE:

@@
 Therefore, we linked the YRCC unit to each ecological unit after 87-WAS and each province unit after the 98-UBR.
-We try to approve that focusing on SES structures rather than institutional details can reasonably interpret the differences caused by institutional shifts in the YRB.
+We tested whether focusing on SES structures rather than institutional details could reasonably explain the differences caused by institutional shifts in the YRB.
 

### 2022-06-21 docs/papers/01_manuscript/manuscript.tex
docs(all-paper): submit 1.7.1
BREAKING CHANGE:

@@
 
-\title{\input{title.tex}}  %! Notice Input
+\title{Institutional shifts and sustainable water use of the Yellow River Basin}  %! Notice Input
 
@@
 The YRB is a valuable case study because it is one of the most anthropogenically altered large river basins.
-It was first overdrawn, then dried up, and finally has been successfully restored.
+Its flow was first overdrawn, then dried up, and finally has been successfully restored.
 Our results suggest that two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), framed different social-ecological system (SES) structures.
 During the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
-Furthermore, these heterogeneous effects and a further theoretical marginal benefits analysis support the hypothesis that SES structural changes play a vital role in YRB's restoration.
-This quasi-natural experiment of the YRB offers profound insights into the links between SESs structures and outcomes, providing valuable guidelines for water depletion basins worldwide.
+Furthermore, these heterogeneous effects and a further theoretical marginal benefits analysis support the hypothesis that SES structural changes played a vital role in YRB restoration.
+This quasi-natural experiment on the YRB offers profound insights into the links between SESs structures and outcomes, providing valuable guidelines for water depletion in basins worldwide.
      }  %! Notice input
 
-\keywords{\input{keywords}}  %! Notice input
+\keywords{Yellow River, water use, water governance, social-ecological system, institutional fit}  %! Notice input
 \maketitle

### 2022-06-21 docs/papers/01_manuscript/01_introduction.tex
docs: plain text version

@@
 Those efforts led to ecological restoration of wetlands and the estuarine delta. Drying up has been avoided for over 20 years, which is widely considered a substantial management achievement.
-Instead of relying on engineering to increase water supply, institutional strategies like the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, authority at a basin-level) focused mainly on limiting demand for water.
+Instead of relying on engineering to increase water supply, institutional strategies like the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, authority at a basin-level) focused mainly on limiting demand for water \cite{bouckaert2022, speed2013}.
 Institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human and natural system, including interplays between social actors, ecological units, or between social and ecological system elements

### 2022-06-21 docs/papers/01_manuscript/03_results.tex
docs: plain text version

@@
 
-\label{result-1-p2}
-Our estimation of theoretical water use suggests that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without an institutional shift (Figure~\ref{fig:main_results}A).
-From 1988 to 1998, on average, while the estimation of annual water use only suggests $974.34$ billion $m^3$, the observed water use of the YRB provinces reached $1038.36$ billion $m^3$ (an increase of $6.57\%$).
-However, after the institutional change in 1998 (98-UBR), trends of increasing water use appeared to be effectively suppressed.
-From 1998 to 2008, the total observed water use decreased by $0.49$ billion $m^3/yr$ per year, while the estimation of water use still suggests $0.82$ billion $m^3/yr$ increases (Figure~\ref{fig:main_results} B).
-The increased water uses after 87-WAS aligns with the severe drying-down of the surface streamflow from 1987 to 1998, an obvious indicator of river degradation and environmental crisis (Figure~\ref{fig:main_results}C).
-On the other hand, the 98-UBR ended river depletion, despite subsequent increases in drought intensity (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{fig:main_results}C).
-
-\begin{figure*}[!tb]
+\begin{figure*}[!htb]
 	\centering
-    \includegraphics[width=32pc]{outputs/main_results2.pdf}
+	\includegraphics[width=0.9\linewidth]{outputs/main_results2.pdf}
 	\caption{
@@
 
+\label{result-1-p2}
+Our estimation of theoretical water use suggests that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without an institutional shift (Figure~\ref{fig:main_results}A).
+From 1988 to 1998, on average, while the estimation of annual water use only suggests $974.34$ billion $m^3$, the observed water use of the YRB provinces reached $1038.36$ billion $m^3$ (an increase of $6.57\%$).
+However, after the institutional change in 1998 (98-UBR), trends of increasing water use appeared to be effectively suppressed.
+From 1998 to 2008, the total observed water use decreased by $0.49$ billion $m^3/yr$ per year, while the estimation of water use still suggests $0.82$ billion $m^3/yr$ increases (Figure~\ref{fig:main_results} B).
+The increased water uses after 87-WAS aligns with the severe drying-down of the surface streamflow from 1987 to 1998, an obvious indicator of river degradation and environmental crisis (Figure~\ref{fig:main_results}C).
+On the other hand, the 98-UBR ended river depletion, despite subsequent increases in drought intensity (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{fig:main_results}C).
+
 %\subsection{REGIONAL DIFFERENCES IN RESPONSES TO INSTITUTIONAL SHIFTS}
@@
 \label{result-3}
-% 结果2部分：展示区域相应差异
-Our results also suggest differences between patterns of provinces in their responses to the two institutional regulating.
-During the decade after the 87-WAS, the major water-using provinces (e.g., Inner Mongolia, Henan, Shandong) had apparent accelerations (Figure~\ref{fig:regulating}).
-The proportion of increased (or decreased) water use for each province (over the estimated water use by the model) correlated significantly (partial correlation coefficient is $0.77$, $p<0.05$) with actual water use from the Yellow River.
-On average, the major water users (Shandong, Inner Mongolia, Henan, and Ningxia) used $32.14\%$ more water than predicted from 1987 to 1998.
-By contrast, after the 98-UBR (from 1998 to 2008), almost all provinces have seen declines ($-16.54\%$ on average) in water use.
-Furthermore, the regulated water use of provinces was unrelated (partial correlation coefficient is $0.33$, $p>0.1$) to their proportional water use from the Yellow River.
 
-\begin{figure*}[!tb]
+\begin{figure*}[!htb]
 	\centering
-    \includegraphics[width=32pc]{outputs/fig3.pdf}
+	\includegraphics[width=0.9\linewidth]{outputs/fig3.pdf}
 	\caption{
@@
 
+% 结果2部分：展示区域相应差异
+Our results also suggest differences between patterns of provinces in their responses to the two institutional regulating.
+During the decade after the 87-WAS, the major water-using provinces (e.g., Inner Mongolia, Henan, Shandong) had apparent accelerations (Figure~\ref{fig:regulating}).
+The proportion of increased (or decreased) water use for each province (over the estimated water use by the model) correlated significantly (partial correlation coefficient is $0.77$, $p<0.05$) with actual water use from the Yellow River.
+On average, the major water users (Shandong, Inner Mongolia, Henan, and Ningxia) used $32.14\%$ more water than predicted from 1987 to 1998.
+By contrast, after the 98-UBR (from 1998 to 2008), almost all provinces have seen declines ($-16.54\%$ on average) in water use.
+Furthermore, the regulated water use of provinces was unrelated (partial correlation coefficient is $0.33$, $p>0.1$) to their proportional water use from the Yellow River.
+
 \subsection{Structure-based marginal benefit analysis}
 \label{result-4}
+
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.6\linewidth]{outputs/economic_model.pdf}
+	\caption{
+		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
+	\label{fig:model}
+\end{figure}
+
 We compared the theoretical marginal returns and optimal water use under three different structural cases (analogy to Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
@@
 Furthermore, water users with higher capability are more stimulated by institutional shifts and away from the theoretically optimal water use under a unified allocation.
-
-\begin{figure}[!ht]
-    \centering
-    \includegraphics[width=0.9\linewidth]{outputs/economic_model.pdf}
-	\caption{
-		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
-	\label{fig:model}
-\end{figure}

### 2022-06-21 docs/papers/01_manuscript/04_discussion.tex
docs: plain text version

@@
 % discussion-2: 87的增加
-Increased water use after 87-WAS aligns with concerns about frequently scrambling for water in some provinces during this period \cite{mao2000}.
+Increased water use after 87-WAS aligns with concerns about frequently scrambling for water in some provinces during this period \cite{mao2000, bouckaert2022}.
 Although reasons for the non-ideal effect of 87-WAS had been widely discussed \cite{huangang2002} (such as enforcement, feasibility, and equity), structural change has received limited attention.

### 2022-06-21 docs/papers/01_manuscript/manuscript.tex
docs: plain text version

@@
-\documentclass{../nsr}
-
+\documentclass[default, sn-standardnature]{sn-jnl}
 \usepackage{amsmath,graphicx,array}
@@
 \usepackage{hyperref}
+\newgeometry{left=2cm, right=2cm}
+\linespread{1.5}
 % \usepackage[nofiglist,notablist]{endfloat}
@@
 \usepackage{multirow}
-\usepackage[switch]{lineno}
+\usepackage{lineno}
 \setenumerate{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=0pt}
@@
 
-\jvol{XX}
-\jnum{X}
-\jyear{Year}
-\doi{10.1093/nsr/XXXX}
-\received{XX XX Year}
-\revised{XX XX Year}
-\accepted{XX XX Year}
+% \jvol{XX}
+% \jnum{X}
+% \jyear{Year}
+% \doi{10.1093/nsr/XXXX}
+% \received{XX XX Year}
+% \revised{XX XX Year}
+% \accepted{XX XX Year}
 
@@
 \begin{document}
-
-\dhead{RESEARCH ARTICLE}
-\subhead{EARTH SCIENCES}
+\normalsize
+% \dhead{RESEARCH ARTICLE}
+% \subhead{EARTH SCIENCES}
 
@@
 \author{Graeme S. Cumming$^{3}$}
-\author{Bojie Fu$^{1,4}$}
+\author{Bojie Fu$^{1}$}
 
@@
 
-\affil{$^4$The research for this article was financed by the National Natural Science Foundation of China (CN) (Grant Nos.
+% \affil{$^4$The research for this article was financed by the National Natural Science Foundation of China (CN) (Grant Nos.
 NSFC 42041007).
-The authors thank Fuqiang Tian for his insightful comments.
 A supplementary online appendix is available with this article at the \em{National Science Review} website.}
 
-\authornote{\textbf{Corresponding authors.} Email: shuaiwang@bnu.edu.cn}
+% \authornote{\textbf{Corresponding authors.} Email: shuaiwang@bnu.edu.cn}
 %\authornote{Shuang Song and Huiyu Wen equally contributed to this work.}
-\pagewiselinenumbers
-\abstract[ABSTRACT]{
+\renewcommand\linenumberfont{\normalfont\bfseries\small}
+\linenumbers
+\abstract{
      Increasing competition for water is leading to depletion of freshwater globally and calls for an urgent transformation of water governance.
@@
 
+\bibliography{../mybib}
+\bibliographystyle{sn-standardnature}
+\label{bib}
+
 %%%%%%%% -----  02_appendix -------- %%%%%%%%%%
+\newpage
 \appendix
@@
 %% the \bibliography{} command.
-\bibliography{../mybib}
-\label{bib}
+% \newpage
+% \newpage
+% \bibliography{../mybib}
+% \bibliographystyle{sn-standardnature}
+% \label{bib}
 \end{document}

### 2022-07-01 docs/papers/01_manuscript/01_introduction.tex
feat(title,-introduction,-method,-abstract,-in-that-order): now mark the YRB as a case study, only introduce it in method and SI
NSR editors require us to focus more on methodology innovations.

BREAKING CHANGE:

--- 2022-06-21 docs/papers/01_manuscript/01_introduction.tex
@@
 Widespread freshwater scarcity and overuse challenge the sustainability of large river basins, resulting in systematic risks to economies, societies, and ecosystems globally \cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
-With steadily increasing demand, competition for water causes depletion of freshwater globally and creates a strong need for an urgent transformation of the water governance system to improve water use conservation \cite{gleick2010, ziolkowska2016, wang2019d}.
-Despite worldwide efforts to govern water sustainably, overuse and the resulting degradation of large river basins are not easily reversible.
-Thus, there have been relatively few successful governance practices and theory re-alignments
-\cite{giuliani2013, falkenmark2019, jaeger2019}.
 In the context of future climate change, the gap between supply and demand for water resources in large river basins is expected to become increasingly more prominent \cite{florke2018, yoon2021}.
-Balancing the water demands of ecosystems and development in heavily human-dominated river basins is a challenge not just for China, but also across many large river basins worldwide.
+Those river basin systems successfully supporting sustainable water resource use are structurally well-aligned with water provisioning and social-ecological demands, without inefficient competition or overuses \cite{wang2019d}.
+However, balancing the water demands of ecosystems and development in heavily human-dominated river basins is a challenge because human activities and water are intertwined in their structures as complex social-ecological systems (SES) \cite{huggins2022,konar2019}.
 
-% 黄河的介绍
-The Yellow River Basin (YRB), the fifth-largest river basin worldwide, is known for its vital role in the socio-economic development of China.
-It supports $35.63\%$ of China's irrigation and $30\%$ of its population while containing only $2.66\%$ of its water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today).
-In the 1980s, intense water use, accounting for about $80\%$ of Yellow River surface runoff, combined with other forms of human interference (e.g., soil conservation and water conservancy projects), caused consecutive drying events and substantial ecological, economic, and social crises (e.g., wetland shrinkage, agriculture reduction, and a scramble for water).
+For governing river basin systems, their SES structures can be reshaped by institutions, such as policies, laws, and norms \cite{young2008,cumming2020b}.
+Representing all relative governance practices, institutions include interplays between social actors, ecological units, or between social and ecological system elements
+\cite{lien2020, bodin2017b}.
+Understanding how these complex interplays is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems \cite{kluger2020}.
+However, the best approach to designing effective institutions remains an open question \cite{agrawal2003, persha2011, agrawal2001}.
 
-% 第三段 过去管理的经验，断流的严重程度，连续多少没有断流，少有的解决断流的大河。治理成功的流域？分析背后的机制，基础。往用水上靠。
-In response, Chinese authorities implemented several ambitious water management practices in the YRB to relieve water stress, such as reservoir regulation, the South-to-north Water Diversion Project (WDP), the 1987 Water Allocation Scheme (87-WAS), and the 1998 Unified Basinal Regulation (98-UBR) \cite{long2020, wang2019d}.
-Those efforts led to ecological restoration of wetlands and the estuarine delta. Drying up has been avoided for over 20 years, which is widely considered a substantial management achievement.
-Instead of relying on engineering to increase water supply, institutional strategies like the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, authority at a basin-level) focused mainly on limiting demand for water.
-Institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human and natural system, including interplays between social actors, ecological units, or between social and ecological system elements
-\cite{young2008,cumming2020b,lien2020, bodin2017b}.
-Understanding these complex interplays is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
-
-While researchers have carefully evaluated and quantified the effects of engineering solutions on water supply\cite{long2020}, there have been few attempts to assess institutional contributions to successful water governance in the YRB.
-% 第四段 目标 制度变化。是不是制度变化产生的，如果是的话怎么影响。
-In addition to widespread recognition of the rising importance of governmental institutions for sustainable water use within large river basins (especially in the case of transboundary basins like the YRB), the best approach to designing effective institutions remains an open question \cite{agrawal2003, persha2011, agrawal2001}.
 Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, supporting (but not guaranteeing) the sustainability of SES \cite{epstein2015, wang2019d}.
@@
 However, imposing institutional changes on a large, complex river basin may create or destroy hundreds of connections between social agents and ecological units, where matched social-ecological structures are not ubiquitous.
+Two particular weaknesses in existing knowledge of institutional matches include understanding: (i) the causal links between SES structures and outcomes; (ii) details of the underlying processes, and especially the coordination of the incentives of different participants, that result from an institutional lack of match.
+These weaknesses limit understanding of institutional design, and hinder approaches toward institutional matches for improving the sustainability of river basin systems.
 
-To better understand how water management institutions can be designed to fit their social-ecological context, we used data on changes in official documents following institutional shifts (the 87-WAS and the 98-UBR) to describe changes in the SES structures associated with the YRB from 1979 to 2008.
-We then used a method called `Differenced Synthetic Control (DSC)' \cite{arkhangelsky2021}, which considers economic growth and natural background, to estimate theoretical water use scenarios without institutional shifts (\textit{\hyperref[{sec:methods}]{Methods}} and \textit{\nameref{secS2}}).
+To better understand how water governance institutions can be designed to match their social-ecological context, we take the Yellow River Basin (YRB), China, as an example \textit{\nameref{sec:yrb}} to dive into causal links between SES structures and outcomes.
+We used data on changes in official documents following two institutional shifts (the 87-WAS and the 98-UBR) to describe comparable changes in the SES structures associated with the YRB from 1979 to 2008 \textit{\nameref{sec:structures}}.
+We then used a method called `Differenced Synthetic Control (DSC)' \cite{arkhangelsky2021}, which considers economic growth and natural background, to estimate theoretical water use scenarios without institutional shifts (\textit{\nameref{sec:DSC}} and \textit{\nameref{secS2}}).
 This approach allowed us to create a counterfactual against which to explore the mechanisms linking SESs structure and outcomes for a deeper understanding of the potential role of institutions in water governance worldwide.
+Finally, we further developed an approach for marginal benefits analysis, to interpret the underlying processes of match and mismatched institutions based on SESs structures (\textit{\nameref{sec:model}}).

### 2022-07-01 docs/papers/01_manuscript/02_structures.tex
docs: plain text version
feat(title,-introduction,-method,-abstract,-in-that-order): now mark the YRB as a case study, only introduce it in method and SI
NSR editors require us to focus more on methodology innovations.

BREAKING CHANGE:

@@
 
-% 制度变动综述
-The institutional shifts in the YRB in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among YRB's water governance practices (\textit{\nameref{secS1}}).
-Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
-The YRCC had no links to the provinces regarding water use before 1987, and the provinces could link directly to the Yellow River reaches (Figure~\ref{fig:structure}~C).
-To shrink water deficits, in 87-WAS, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin (Table~\ref{tab:quota}).
-Simultaneously, according to the extracted information from documents of the 87-WAS issued by national ministries, the YRCC started to report water use in each reach.
-As it was the first time the responsibility of the YRCC involved water use, this introduced new links between the YRCC and the ecological nodes (Figure~\ref{fig:structure}~C).
-However, the controversial 87-WAS did not resolve water depletion.
-In 1998, another strategy (98-UBR) was developed to strengthen the responsibilities of the YRCC for integrated managing water use.
-Information from the 98-UBR documents demonstrated that the provinces had to apply their plan for an annual water use license to YRCC instead of direct access to the Yellow River water.
-Thus, the YRCC has been linked to the provinces since 1998 (Figure~\ref{fig:structure}~C).
-
-\begin{figure*}[!htb]
+\begin{figure*}[!t]
 	\includegraphics[width=\linewidth]{diagrams/diagram.pdf}
@@
 \end{figure*}
+
+% 制度变动综述
+The institutional shifts in the YRB in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among YRB's water governance practices (\textit{\nameref{sec:yrb}} and \textit{\nameref{secS1}}).
+Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
+The YRCC had no links to the provinces regarding water use before 1987, and the provinces could link directly to the Yellow River reaches (Figure~\ref{fig:structure}~C).
+To shrink water deficits, in 87-WAS, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin (Table~\ref{tab:quota}).
+Simultaneously, according to the extracted information from documents of the 87-WAS issued by national ministries, the YRCC started to report water use in each reach.
+As it was the first time the responsibility of the YRCC involved water use, this introduced new links between the YRCC and the ecological nodes (Figure~\ref{fig:structure}~C).
+However, the controversial 87-WAS did not resolve water depletion.
+In 1998, another strategy (98-UBR) was developed to strengthen the responsibilities of the YRCC for integrated managing water use.
+Information from the 98-UBR documents demonstrated that the provinces had to apply their plan for an annual water use license to YRCC instead of direct access to the Yellow River water.
+Thus, the YRCC has been linked to the provinces since 1998 (Figure~\ref{fig:structure}~C).

### 2022-07-01 docs/papers/01_manuscript/06_methods.tex
feat(title,-introduction,-method,-abstract,-in-that-order): now mark the YRB as a case study, only introduce it in method and SI
NSR editors require us to focus more on methodology innovations.

BREAKING CHANGE:

@@
 
-% 为了DSC的模型稳定性，我们使用PCA为影响用水量的众多变量进行了降维
+\subsection{Study area}\label{sec:yrb}
+
+% 黄河的介绍
+The Yellow River Basin (YRB), the fifth-largest river basin worldwide, is known for its vital role in the socio-economic development of China.
+It supports $35.63\%$ of China's irrigation and $30\%$ of its population while containing only $2.66\%$ of its water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today).
+In the 1980s, intense water use, accounting for about $80\%$ of Yellow River surface runoff, combined with other forms of human interference (e.g., soil conservation and water conservancy projects), caused consecutive drying events and substantial ecological, economic, and social crises (e.g., wetland shrinkage, agriculture reduction, and a scramble for water).
+In response, Chinese authorities implemented several ambitious water management practices in the YRB to relieve water stress, such as reservoir regulation, the South-to-north Water Diversion Project (WDP), the 1987 Water Allocation Scheme (87-WAS), and the 1998 Unified Basinal Regulation (98-UBR) \cite{long2020, wang2019d}.
+Those efforts led to ecological restoration of wetlands and the estuarine delta. Drying up has been avoided for over 20 years, which is widely considered a substantial management achievement.
+Instead of relying on engineering to increase water supply, institutional strategies like the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, authority at a basin-level) focused mainly on limiting demand for water \cite{bouckaert2022, speed2013}.
+While researchers have carefully evaluated and quantified the effects of engineering solutions on water supply\cite{long2020}, there have been few attempts to assess institutional contributions to successful water governance in the YRB.
 

### 2022-07-01 docs/papers/01_manuscript/manuscript.tex
feat(title,-introduction,-method,-abstract,-in-that-order): now mark the YRB as a case study, only introduce it in method and SI
NSR editors require us to focus more on methodology innovations.

BREAKING CHANGE:

@@
 
-\title{Institutional shifts and sustainable water use of the Yellow River Basin}  %! Notice Input
+\title{Approaching institutional matches of river basin systems}  %! Notice Input
 
@@
 \abstract{
-     Increasing competition for water is leading to depletion of freshwater globally and calls for an urgent transformation of water governance.
-To better understand how institutions contribute to water governance, we quantified institutional shifts for the Yellow River Basin (YRB).
-The YRB is a valuable case study because it is one of the most anthropogenically altered large river basins.
-Its flow was first overdrawn, then dried up, and finally has been successfully restored.
-Our results suggest that two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), framed different social-ecological system (SES) structures.
-During the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
-Furthermore, these heterogeneous effects and a further theoretical marginal benefits analysis support the hypothesis that SES structural changes played a vital role in YRB restoration.
+     Increasing competition for water is leading to depletion of freshwater globally and calls for efficient institutions in water governance.
+     Alignment of social-ecological system (SES) structures is an crucial approach to institutional matches, but understanding of its causal links and underlying processes are still weaknesses.
+     To fill these knowledge gaps, the Yellow River Basin in China is a valuable case study, because it is one of the most anthropogenically altered large river basins.
+     Under different institutions, its streamflow was first overdrawn, then dried up, and finally has been successfully restored.
+     We focused on two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), which re-framed different social-ecological system (SES) structures.
+     By creating counterfactual against, our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
+     Furthermore, these heterogeneous effects aligned with our further theoretical marginal benefits analysis, supporting the hypothesis that SES structural changes played a vital role in YRB restoration.
      This quasi-natural experiment on the YRB offers profound insights into the links between SESs structures and outcomes, providing valuable guidelines for water depletion in basins worldwide.

### 2022-07-01 docs/papers/01_manuscript/manuscript.tex
fix: fix abbreviations in abstract

@@
      Alignment of social-ecological system (SES) structures is an crucial approach to institutional matches, but understanding of its causal links and underlying processes are still weaknesses.
-     To fill these knowledge gaps, the Yellow River Basin in China is a valuable case study, because it is one of the most anthropogenically altered large river basins.
+     To fill these knowledge gaps, the Yellow River Basin (YRB) in China is a valuable case study, because it is one of the most anthropogenically altered large river basins.
      Under different institutions, its streamflow was first overdrawn, then dried up, and finally has been successfully restored.
-     We focused on two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), which re-framed different social-ecological system (SES) structures.
+     We focused on two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), which re-framed different SES structures.
      By creating counterfactual against, our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.

### 2022-07-03 docs/papers/01_manuscript/01_introduction.tex
fix(introduction,-structures,-results,-discussions): fix problems by Wen and Wu

@@
 \cite{lien2020, bodin2017b}.
-Understanding how these complex interplays is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems \cite{kluger2020}.
-However, the best approach to designing effective institutions remains an open question \cite{agrawal2003, persha2011, agrawal2001}.
-
+Understanding how these complex interplays are crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems \cite{kluger2020}.
 Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, supporting (but not guaranteeing) the sustainability of SES \cite{epstein2015, wang2019d}.
@@
 However, imposing institutional changes on a large, complex river basin may create or destroy hundreds of connections between social agents and ecological units, where matched social-ecological structures are not ubiquitous.
-Two particular weaknesses in existing knowledge of institutional matches include understanding: (i) the causal links between SES structures and outcomes; (ii) details of the underlying processes, and especially the coordination of the incentives of different participants, that result from an institutional lack of match.
-These weaknesses limit understanding of institutional design, and hinder approaches toward institutional matches for improving the sustainability of river basin systems.
+Two particular weaknesses in existing knowledge of institutional matches include understanding: (i) the causal links between SES structures and outcomes; (ii) details of the underlying processes, and especially the coordination of the incentives of different participants, that result from an institutional lack of matches.
+These weaknesses limit understanding of institutional design and hinder approaches toward institutional matches for improving the sustainability of river basin systems.
 
-To better understand how water governance institutions can be designed to match their social-ecological context, we take the Yellow River Basin (YRB), China, as an example \textit{\nameref{sec:yrb}} to dive into causal links between SES structures and outcomes.
-We used data on changes in official documents following two institutional shifts (the 87-WAS and the 98-UBR) to describe comparable changes in the SES structures associated with the YRB from 1979 to 2008 \textit{\nameref{sec:structures}}.
+To better understand how water governance institutions match their social-ecological context, we take the Yellow River Basin (YRB), China, as an example \textit{\nameref{sec:yrb}} to dive into causal links between SES structures and outcomes.
+Specifically, we focused on two institutional shifts in water allocation of the YRB: the 1987 Water Allocation Scheme (87-WAS), and the 1998 Unified Basinal Regulation (98-UBR), which reframed SES structures significantly.
+The YRB provides an informative case for two main reasons:
+(1) The top-down institutional shifts induced sharp changes in SES structures, enabling us to estimate their net effects quantitatively.
+(2) Since few large river basins have experienced such radical institutional shifts more than once, this case study provides comparable natural experiments for understanding the impacts of structural changes in SESs on natural resources.
+
+In methodology, we explored causal linkages between SES structures and sustainability-related outcomes by quasi-natural experiments (institutional shifts imposed by central government) in the YRB.
+Firstly, we used data on changes in official documents following two institutional shifts (the 87-WAS and the 98-UBR) to describe comparable changes in the SES structures associated with the YRB from 1979 to 2008, by abstracting them into SES structures motifs (or building blocks, see \textit{\nameref{sec:structures}}).
 We then used a method called `Differenced Synthetic Control (DSC)' \cite{arkhangelsky2021}, which considers economic growth and natural background, to estimate theoretical water use scenarios without institutional shifts (\textit{\nameref{sec:DSC}} and \textit{\nameref{secS2}}).
 This approach allowed us to create a counterfactual against which to explore the mechanisms linking SESs structure and outcomes for a deeper understanding of the potential role of institutions in water governance worldwide.
-Finally, we further developed an approach for marginal benefits analysis, to interpret the underlying processes of match and mismatched institutions based on SESs structures (\textit{\nameref{sec:model}}).
+Finally, we further developed an approach for marginal benefits analysis, to interpret the underlying processes of the match and mismatched institutions based on SESs structures (\textit{\nameref{sec:model}}).

### 2022-07-03 docs/papers/01_manuscript/03_results.tex
fix(introduction,-structures,-results,-discussions): fix problems by Wen and Wu

@@
 %\subsection{REGIONAL DIFFERENCES IN RESPONSES TO INSTITUTIONAL SHIFTS}
-\subsection{Heterogeneous institutional effects}
+\subsection{Heterogeneous effects and interpretation}
 \label{result-3}
@@
 
-\subsection{Structure-based marginal benefit analysis}
-\label{result-4}
+% \subsection{Structure-based marginal benefit analysis}
+% \label{result-4}
 
@@
 
-We compared the theoretical marginal returns and optimal water use under three different structural cases (analogy to Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
+For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (analogy to Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
 Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.

### 2022-07-03 docs/papers/01_manuscript/04_discussion.tex
fix(introduction,-structures,-results,-discussions): fix problems by Wen and Wu

--- 2022-06-21 docs/papers/01_manuscript/04_discussion.tex
@@
 % 用水量的上升、下降-结果解读
-Our results show that while 98-UBR decreased water use in the YRB, 87-WAS increased it.
+% 制度对社会生态系统的结果产生影响在世界范围内都很普遍，
+The influences of institutions on the outcomes of social-ecological systems (SESs) were widely reported worldwide, but few attempts to quantify their net effects \cite{cumming2020a}.
+Our results show that while 98-UBR decreased water use in the YRB, 87-WAS increased it by $8.57\%$.
 The results challenged previous analyses (i.e., suggesting that 87-WAS ''had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present \cite{abadie2015,hill2021}.
@@
 % discussion-2: 87的增加
-Increased water use after 87-WAS aligns with concerns about frequently scrambling for water in some provinces during this period \cite{mao2000}.
-Although reasons for the non-ideal effect of 87-WAS had been widely discussed \cite{huangang2002} (such as enforcement, feasibility, and equity), structural change has received limited attention.
+% 结果与制度的目的完全相反的87-WAS与许多其它的SES失败治理案例类似，表明不匹配的社会生态结构可能促进了对公共资源的掠夺式开采。
+The above comparison suggests that the 87-WAS, whose results were contrary to the purpose of the institution, is similar to many other SES governance failures, supporting that mismatched socio-ecological structures can deterioration of common resources \cite{kellenberg2009,cai2016,barnes2019}.
+The increased water use after 87-WAS aligns with concerns about frequently scrambling for water in some provinces during this period \cite{mao2000, bouckaert2022}.
+Although reasons for the non-ideal effect of 87-WAS had been widely discussed \cite{huangang2002} (such as enforcement, feasibility, and equity), however, structural change has received limited attention.
 Our results show that the correlation between current water use and changed (increased or decreased) water use was significant after 87-WAS (Figure~\ref{fig:regulating}).
-This ``major users use more'' pattern supports the hypothesis that separated stakeholders (individual provinces) will response to structure by maximizing utility (interpreted in our structure-based model, see Figure~\ref{fig:model}).
+This ``major users use more'' pattern supports the hypothesis that separated stakeholders (individual provinces) will respond to structure by maximizing utility (interpreted in our structure-based model, see Figure~\ref{fig:model}).
 
-The validity of our theoretical analysis is supported two facts:
+The validity of our theoretical analysis is supported by two facts:
 (1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
-The bargaining was also a process for matching water shares to economic volume, because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution) \cite{zuo2020}.
+The bargaining was also a process for matching water shares to economic volume because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution) \cite{zuo2020}.
 (2) Provinces with higher current water use might have greater bargaining power in water use allocation because of information asymmetry between decision-makers and stakeholders.
@@
 \label{discussion-3}
+On the other hand, social-ecological matches can also be supported by structure effects.
 After 98-UBR, the YRCC could adjust water use quotas to match river conditions for the whole YRB.
@@
 \cite{krieger1955, ostrom1990}.
-During this period, proportional decreased water use of provinces indicated a positive result of regulation (see \nameref{result-3}).
+During this period, proportional decreased water use of provinces indicated a positive result of the regulation (see \nameref{result-3}).
 The 98-UBR thus led to expected institutional outcomes at a basin scale, indicating that successful governance of SES emerged by indirectly (or vertically) creating links between different stakeholders.
 Our model demonstrates that in this case, a unified scale-matched institution was indispensable for sustainable water use.
-
-We explored causal linkages between SES structures and sustainability-related outcomes by quasi-natural experiments (institutional shifts imposed by central government) in the YRB.
-The YRB provides an informative case for two main reasons:
-(1) The top-down institutional shifts induced sharp changes in SES structures, enabling us to estimate their net effects quantitatively.
-(2) Since few large river basins have experienced such radical institutional shifts more than once, this case study provides a valuable natural experiment for understanding the impacts of structural changes in SESs on natural resources.
 
@@
 Institutional re-alignments since 98-UBR improved the authority of the YRCC and helped it match the scale of resource provisioning in the YRB, leading to enhanced social-ecological fit and better outcomes \cite{cumming2020a,wang2019d}.
-The comparison demonstrates again the challenge of finding win-win situations in coupled human-nature systems \cite{hegwood2022}, and the need more deeply understand the role of social-ecological structures \cite{bergsten2019, sayles2019}.
+The comparison demonstrates again the challenge of finding win-win situations in coupled human-nature systems \cite{hegwood2022}, and the need to more deeply understand the role of social-ecological structures \cite{bergsten2019, sayles2019}.
+% Therefore, the YRB cases can provide further explanation of the matching and mismatching of the previous SES building blocks, linking SES structure and outcomes by plausible reasons of causality and underlying processes.
 
-\subsection{LIMITATION, INSIGHTS AND IMPLICATIONS}
+% \subsection{LIMITATION, INSIGHTS AND IMPLICATIONS}
 % \subsection{Limitation, insights and implications}
-\label{discussion-4}
+% \label{discussion-4}
 % discussion-3: 启示、未来的展望
@@
 and second, when applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
-Our quasi-experiment approach nonetheless provides evidence supporting the view that there was a change in water use trajectory following the YRB's unique institutional shifts, and offers insights into water governance (and particularly the importance of having a scale-matched, basin-wide authority for water allocation solutions \cite{bodin2017b, ostrom2009, reyers2018})
+Our quasi-experiment approach nonetheless provides evidence supporting the view that there was a change in water use trajectory following the YRB's unique institutional shifts and offers insights into water governance (and particularly the importance of having a scale-matched, basin-wide authority for water allocation solutions \cite{bodin2017b, ostrom2009, reyers2018})
 Moreover, the ultimate success of the 98-UBR institutional shift theoretically and practically proved the importance of social-ecological fit.
@@
 Our analysis suggests that these initiatives can benefit by actively incorporating social-ecological matched building blocks when developing new institutions \cite{bodin2017b}.
-Moreover, our research provides a cautionary tale of how institutions can create perverse incentives \cite{hegwood2022}, while insights from the YRB contribute to improving guidelines for SESs management worldwide \cite{muneepeerakul2017, leslie2015}.
+Moreover, our research provides a cautionary tale of how institutions can create perverse incentives \cite{hegwood2022}, while insights from the YRB can provide guidelines for SESs management worldwide \cite{muneepeerakul2017, leslie2015}.

### 2022-07-03 docs/papers/01_manuscript/manuscript.tex
fix(introduction,-structures,-results,-discussions): fix problems by Wen and Wu

@@
 
-\title{Approaching institutional matches of river basin systems}  %! Notice Input
+\title{Approaching social-ecological matches of river basin systems for sustainability}  %! Notice Input
 
@@
      Increasing competition for water is leading to depletion of freshwater globally and calls for efficient institutions in water governance.
-     Alignment of social-ecological system (SES) structures is an crucial approach to institutional matches, but understanding of its causal links and underlying processes are still weaknesses.
-     To fill these knowledge gaps, the Yellow River Basin (YRB) in China is a valuable case study, because it is one of the most anthropogenically altered large river basins.
-     Under different institutions, its streamflow was first overdrawn, then dried up, and finally has been successfully restored.
+     Alignments of social-ecological system (SES) structures are a crucial approach to institutional matches, but an understanding of its causal links and underlying processes are still weaknesses.
+     To fill these knowledge gaps, we select the Yellow River Basin (YRB) in China as a typical case study to quantitatively measure the effects of SES structures changing because it is one of the most anthropogenically altered large river basins.
+     Under different water allocation institutions, its streamflow was first overdrawn, then dried up, and finally has been successfully restored.
      We focused on two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), which re-framed different SES structures.
-     By creating counterfactual against, our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
-     Furthermore, these heterogeneous effects aligned with our further theoretical marginal benefits analysis, supporting the hypothesis that SES structural changes played a vital role in YRB restoration.
-     This quasi-natural experiment on the YRB offers profound insights into the links between SESs structures and outcomes, providing valuable guidelines for water depletion in basins worldwide.
+     We conduct counterfactual identification on the effect of these institutional shifts, our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
+     Furthermore, these heterogeneous effects of water use responses to SES structures aligned with our further theoretical marginal benefits analysis, supporting the hypothesis that SES structural changes played a vital role in sustainable water use.
+     This quasi-natural experiment on the YRB offers profound insights into the links between SESs structures and outcomes, suggesting that fragmented ecological units linked to separated social actors should be avoided for sustainability.
      }  %! Notice input

### 2022-07-03 docs/papers/01_manuscript/out/compiled_v-2.0.2.tex
fix(introduction,-structures,-results,-discussions): fix problems by Wen and Wu

\documentclass[default, sn-standardnature]{sn-jnl}
\usepackage{amsmath,graphicx,array}
\usepackage{dcolumn,soul}%
\let\openbox\relax
\usepackage{amsthm}
\usepackage[figuresright]{rotating}%
\usepackage{algorithm, algorithmicx, algpseudocode}
\usepackage{listings}%
\usepackage{hyperref}
\newgeometry{left=2cm, right=2cm}
\linespread{1.5}
% \usepackage[nofiglist,notablist]{endfloat}
\makeatletter
\def\uns{\ifmmode\,\else$\,$\fi}%
\newtheorem{defn}{Definition}
\newtheorem{thm}{Theorem}
\newtheorem{ass}{Assumption}
\newtheorem{prop}{Proposition}
\newtheorem{fig}{Fig.}
\newtheorem{case}{Case}
\newtheorem{case_appendix}{Case}
\newtheorem{example}{Example}[section]
\renewcommand{\proofname}{\textbf{Proof}}
\newtheorem{property}{Property}
\newtheorem{remark}{Remark}
%\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{float}
\usepackage{multirow}
\usepackage{lineno}
\setenumerate{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=0pt}
\setitemize{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=5pt}
\setdescription{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=5pt}

\usepackage{booktabs}
\usepackage{diagbox}
%%
\makeatother

% \jvol{XX}
% \jnum{X}
% \jyear{Year}
% \doi{10.1093/nsr/XXXX}
% \received{XX XX Year}
% \revised{XX XX Year}
% \accepted{XX XX Year}

\markboth{One, Two, and Three}{One, Two, and Three}
\graphicspath{{../../../figs/}}

\begin{document}
\normalsize
% \dhead{RESEARCH ARTICLE}
% \subhead{EARTH SCIENCES}

\bibliographystyle{../nsr}

\title{Approaching social-ecological matches of river basin systems for sustainability}  %! Notice Input

\author{Shuang Song$^{1}$}
\author{Huiyu Wen$^2$}
\author{*Shuai Wang$^{1}$}
\author{Xutong Wu$^{1}$}

\author{Graeme S. Cumming$^{3}$}
\author{Bojie Fu$^{1}$}

\affil{$^1$State Key Laboratory of Earth Surface Processes and Resource Ecology,
     Faculty of Geographical Science,
     Beijing Normal University,
     Beijing 100875,
     P.R. China}

% \affil{$^2$Institute of Land Surface System and Sustainability,
%      Faculty of Geographical Science,
%      Beijing Normal University,
%      Beijing 100875,
%      P.R. China}

\affil{$^2$School of Finance,
     Renmin University of China,
     Beijing 100875,
     P.R. China}

\affil{$^3$ARC Centre of Excellence for Coral Reef Studies,
     James Cook University,
     Townsville 4811,
     QLD, Australia}

% \affil{$^4$The research for this article was financed by the National Natural Science Foundation of China (CN) (Grant Nos. NSFC 42041007). A supplementary online appendix is available with this article at the \em{National Science Review} website.}

% \authornote{\textbf{Corresponding authors.} Email: shuaiwang@bnu.edu.cn}
%\authornote{Shuang Song and Huiyu Wen equally contributed to this work.}
\renewcommand\linenumberfont{\normalfont\bfseries\small}
\linenumbers
\abstract{
     Increasing competition for water is leading to depletion of freshwater globally and calls for efficient institutions in water governance.
     Alignments of social-ecological system (SES) structures are a crucial approach to institutional matches, but an understanding of its causal links and underlying processes are still weaknesses.
     To fill these knowledge gaps, we select the Yellow River Basin (YRB) in China as a typical case study to quantitatively measure the effects of SES structures changing because it is one of the most anthropogenically altered large river basins.
     Under different water allocation institutions, its streamflow was first overdrawn, then dried up, and finally has been successfully restored.
     We focused on two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), which re-framed different SES structures.
     We conduct counterfactual identification on the effect of these institutional shifts, our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
     Furthermore, these heterogeneous effects of water use responses to SES structures aligned with our further theoretical marginal benefits analysis, supporting the hypothesis that SES structural changes played a vital role in sustainable water use.
     This quasi-natural experiment on the YRB offers profound insights into the links between SESs structures and outcomes, suggesting that fragmented ecological units linked to separated social actors should be avoided for sustainability.
     }  %! Notice input

\keywords{Yellow River, water use, water governance, social-ecological system, institutional fit}  %! Notice input
\maketitle

\section{INTRODUCTION}\label{sec:introduction}
% 水竞争的重要性
Widespread freshwater scarcity and overuse challenge the sustainability of large river basins, resulting in systematic risks to economies, societies, and ecosystems globally \cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
In the context of future climate change, the gap between supply and demand for water resources in large river basins is expected to become increasingly more prominent \cite{florke2018, yoon2021}.
Those river basin systems successfully supporting sustainable water resource use are structurally well-aligned with water provisioning and social-ecological demands, without inefficient competition or overuses \cite{wang2019d}.
However, balancing the water demands of ecosystems and development in heavily human-dominated river basins is a challenge because human activities and water are intertwined in their structures as complex social-ecological systems (SES) \cite{huggins2022,konar2019}.

For governing river basin systems, their SES structures can be reshaped by institutions, such as policies, laws, and norms \cite{young2008,cumming2020b}.
Representing all relative governance practices, institutions include interplays between social actors, ecological units, or between social and ecological system elements
\cite{lien2020, bodin2017b}.
Understanding how these complex interplays are crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems \cite{kluger2020}.
Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, supporting (but not guaranteeing) the sustainability of SES \cite{epstein2015, wang2019d}.
Some institutional advances have had desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d}, and collaborative water governance systems in Europe \cite{green2013}).
However, imposing institutional changes on a large, complex river basin may create or destroy hundreds of connections between social agents and ecological units, where matched social-ecological structures are not ubiquitous.
Two particular weaknesses in existing knowledge of institutional matches include understanding: (i) the causal links between SES structures and outcomes; (ii) details of the underlying processes, and especially the coordination of the incentives of different participants, that result from an institutional lack of matches.
These weaknesses limit understanding of institutional design and hinder approaches toward institutional matches for improving the sustainability of river basin systems.

To better understand how water governance institutions match their social-ecological context, we take the Yellow River Basin (YRB), China, as an example \textit{\nameref{sec:yrb}} to dive into causal links between SES structures and outcomes.
Specifically, we focused on two institutional shifts in water allocation of the YRB: the 1987 Water Allocation Scheme (87-WAS), and the 1998 Unified Basinal Regulation (98-UBR), which reframed SES structures significantly.
The YRB provides an informative case for two main reasons:
(1) The top-down institutional shifts induced sharp changes in SES structures, enabling us to estimate their net effects quantitatively.
(2) Since few large river basins have experienced such radical institutional shifts more than once, this case study provides comparable natural experiments for understanding the impacts of structural changes in SESs on natural resources.

In methodology, we explored causal linkages between SES structures and sustainability-related outcomes by quasi-natural experiments (institutional shifts imposed by central government) in the YRB.
Firstly, we used data on changes in official documents following two institutional shifts (the 87-WAS and the 98-UBR) to describe comparable changes in the SES structures associated with the YRB from 1979 to 2008, by abstracting them into SES structures motifs (or building blocks, see \textit{\nameref{sec:structures}}).
We then used a method called `Differenced Synthetic Control (DSC)' \cite{arkhangelsky2021}, which considers economic growth and natural background, to estimate theoretical water use scenarios without institutional shifts (\textit{\nameref{sec:DSC}} and \textit{\nameref{secS2}}).
This approach allowed us to create a counterfactual against which to explore the mechanisms linking SESs structure and outcomes for a deeper understanding of the potential role of institutions in water governance worldwide.
Finally, we further developed an approach for marginal benefits analysis, to interpret the underlying processes of the match and mismatched institutions based on SESs structures (\textit{\nameref{sec:model}}).

\section{RESULTS}\label{sec:results}
%! Author = songshgeo
%! Date = 2022/3/10

% \subsection{INSTITUTIONAL SHIFTS AND STRUCTURES}
\subsection{Institutional shifts and structures}
\label{results-1}

\begin{figure*}[!t]
	\includegraphics[width=\linewidth]{diagrams/diagram.pdf}
	\caption{
		% 黄河流域的制度变迁与经济社会结构差异。
		Institutional shifts and related SES structures in the Yellow River Basin (YRB).
		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{\nameref{secS1}} Table~\ref{tab:quota}). The national administrations are the ultimate authority in issuing water governance policies, which are often implemented by basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
		\textbf{B.} Provincial administrative agencies are the major stakeholders. Since the 87-WAS, with surface water withdrawal from the Yellow River restricted by specific quotas, each stakeholder plan and use water resources for development. However, the natural hydrological processes are connected. Although the institutions focus mainly on surface water (Sur.), it can also influence groundwater inside (Gro.) or water resources outside (Sur. and Gro.') through systematic socio-hydrological processes within the YRB. The YRCC only monitors water withdrawals at that time.
		\textbf{C.} Institutional shifts and following structures changes (details in \textit{\nameref{secS1}}). (1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from the connected ecological unit (the reach of Yellow River, denoted by the blue circles). (2) After 1987-WAS, the YRCC (the yellow circles) was monitoring (the dot-line links) river reaches with the water use quota. (3) Since the 98-UBR, stakeholders have to apply for water use licenses from the YRCC (the connections between the red and yellow circles).
	}
	\label{fig:structure}
\end{figure*}

% 制度变动综述
The institutional shifts in the YRB in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among YRB's water governance practices (\textit{\nameref{sec:yrb}} and \textit{\nameref{secS1}}).
Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
The YRCC had no links to the provinces regarding water use before 1987, and the provinces could link directly to the Yellow River reaches (Figure~\ref{fig:structure}~C).
To shrink water deficits, in 87-WAS, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin (Table~\ref{tab:quota}).
Simultaneously, according to the extracted information from documents of the 87-WAS issued by national ministries, the YRCC started to report water use in each reach.
As it was the first time the responsibility of the YRCC involved water use, this introduced new links between the YRCC and the ecological nodes (Figure~\ref{fig:structure}~C).
However, the controversial 87-WAS did not resolve water depletion.
In 1998, another strategy (98-UBR) was developed to strengthen the responsibilities of the YRCC for integrated managing water use.
Information from the 98-UBR documents demonstrated that the provinces had to apply their plan for an annual water use license to YRCC instead of direct access to the Yellow River water.
Thus, the YRCC has been linked to the provinces since 1998 (Figure~\ref{fig:structure}~C).
% 因此，两次制度转换重塑了，形成了三个由社会行动者和生态节点连接而成的一般性结构
As result, the two institutional shifts reshaped SES structures, leading to three general structures linked by social actors and ecological nodes (Figure~\ref{fig:structure}~C).

%! Author = songshgeo
%! Date = 2022/3/10
% \MakeUppercase{\subsection{Cascading effects of the institutional shifts}}

%\subsection{INSTITUTIONAL SHIFTS IMPACT ON WATER USE OF THE YRB}
\subsection{Institutional shifts impact on water use}
\label{result-2}
% 结果一：展示制度转变带来的用水量变化

\begin{figure*}[!htb]
	\centering
	\includegraphics[width=0.9\linewidth]{outputs/main_results2.pdf}
	\caption{
		Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
		\textbf{A.} water uses of the YRB before and after the institutional shift in 1987 (87-WAS);
		\textbf{B.} water uses of the YRB before and after the institutional shift in 1998 (98-UBR). Blue lines are statistics derived from water use data; grey lines are estimates from the Differenced Synthetic Control method with economic and environmental background controlled;
		\textbf{C.} Drought intensity in the YRB and drying up events of the Yellow River. The size of the grey bubbles denotes the length of drying upstream.
	}
	\label{fig:main_results}
\end{figure*}

\label{result-1-p2}
Our estimation of theoretical water use suggests that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without an institutional shift (Figure~\ref{fig:main_results}A).
From 1988 to 1998, on average, while the estimation of annual water use only suggests $974.34$ billion $m^3$, the observed water use of the YRB provinces reached $1038.36$ billion $m^3$ (an increase of $6.57\%$).
However, after the institutional change in 1998 (98-UBR), trends of increasing water use appeared to be effectively suppressed. From 1998 to 2008, the total observed water use decreased by $0.49$ billion $m^3/yr$ per year, while the estimation of water use still suggests $0.82$ billion $m^3/yr$ increases (Figure~\ref{fig:main_results} B).
The increased water uses after 87-WAS aligns with the severe drying-down of the surface streamflow from 1987 to 1998, an obvious indicator of river degradation and environmental crisis (Figure~\ref{fig:main_results}C).
On the other hand, the 98-UBR ended river depletion, despite subsequent increases in drought intensity (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{fig:main_results}C).

%\subsection{REGIONAL DIFFERENCES IN RESPONSES TO INSTITUTIONAL SHIFTS}
\subsection{Heterogeneous effects and interpretation}
\label{result-3}

\begin{figure*}[!htb]
	\centering
	\includegraphics[width=0.9\linewidth]{outputs/fig3.pdf}
	\caption{
		Regulating differences for provinces in the YRB.
		Red (the 87-WAS) and green (the 98-UBR) bars denote an increased or decreased ratio for actual water use relative to the estimate from the model in the decade after the institutional shift.
		The grey bars indicate the proportions of actual water use for each province relative to their total water use in the decade after the institutional shift.
		The triangles mark the water quotas assigned under the institution, converted to ratios by dividing by their sum.
	}
	\label{fig:regulating}
\end{figure*}

% 结果2部分：展示区域相应差异
Our results also suggest differences between patterns of provinces in their responses to the two institutional regulating.
During the decade after the 87-WAS, the major water-using provinces (e.g., Inner Mongolia, Henan, Shandong) had apparent accelerations (Figure~\ref{fig:regulating}).
The proportion of increased (or decreased) water use for each province (over the estimated water use by the model) correlated significantly (partial correlation coefficient is $0.77$, $p<0.05$) with actual water use from the Yellow River.
On average, the major water users (Shandong, Inner Mongolia, Henan, and Ningxia) used $32.14\%$ more water than predicted from 1987 to 1998.
By contrast, after the 98-UBR (from 1998 to 2008), almost all provinces have seen declines ($-16.54\%$ on average) in water use.
Furthermore, the regulated water use of provinces was unrelated (partial correlation coefficient is $0.33$, $p>0.1$) to their proportional water use from the Yellow River.

% \subsection{Structure-based marginal benefit analysis}
% \label{result-4}

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.6\linewidth]{outputs/economic_model.pdf}
	\caption{
		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
	\label{fig:model}
\end{figure}

For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (analogy to Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.
Until water-use decisions are consolidated into unified management, each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive to use water, leading to higher water use.
Furthermore, water users with higher capability are more stimulated by institutional shifts and away from the theoretically optimal water use under a unified allocation.

\section{DISCUSSION}\label{sec:discussion}
%! Author = songshgeo
%! Date = 2022/3/10

% \subsection{CAUSES OF INSTITUTIONAL IMPACTS}
% \subsection{}
\label{discussion-1}
% discussion-1:
% 用水量的上升、下降-结果解读
% 制度对社会生态系统的结果产生影响在世界范围内都很普遍，
The influences of institutions on the outcomes of social-ecological systems (SESs) were widely reported worldwide, but few attempts to quantify their net effects \cite{cumming2020a}.
Our results show that while 98-UBR decreased water use in the YRB, 87-WAS increased it by $8.57\%$.
The results challenged previous analyses (i.e., suggesting that 87-WAS ''had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present \cite{abadie2015,hill2021}.
However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{\nameref{secS2}}~Table~\ref{tab:variables}).
On the contrary, the 98-UBR reduced water competition, so many studies attributed the restoration mainly to the successful introduction of this institution \cite{chen2021,huangang2002,an2007}.

\label{discussion-2}
% discussion-2: 87的增加
% 结果与制度的目的完全相反的87-WAS与许多其它的SES失败治理案例类似，表明不匹配的社会生态结构可能促进了对公共资源的掠夺式开采。
The above comparison suggests that the 87-WAS, whose results were contrary to the purpose of the institution, is similar to many other SES governance failures, supporting that mismatched socio-ecological structures can deterioration of common resources \cite{kellenberg2009,cai2016,barnes2019}.
The increased water use after 87-WAS aligns with concerns about frequently scrambling for water in some provinces during this period \cite{mao2000, bouckaert2022}.
Although reasons for the non-ideal effect of 87-WAS had been widely discussed \cite{huangang2002} (such as enforcement, feasibility, and equity), however, structural change has received limited attention.
Our results show that the correlation between current water use and changed (increased or decreased) water use was significant after 87-WAS (Figure~\ref{fig:regulating}).
This ``major users use more'' pattern supports the hypothesis that separated stakeholders (individual provinces) will respond to structure by maximizing utility (interpreted in our structure-based model, see Figure~\ref{fig:model}).

The validity of our theoretical analysis is supported by two facts:
(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
The bargaining was also a process for matching water shares to economic volume because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution) \cite{zuo2020}.
(2) Provinces with higher current water use might have greater bargaining power in water use allocation because of information asymmetry between decision-makers and stakeholders.
Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligned with their appeals to the higher central government for larger shares \cite{wang2019a, wang2019d}.

\label{discussion-3}
On the other hand, social-ecological matches can also be supported by structure effects.
After 98-UBR, the YRCC could adjust water use quotas to match river conditions for the whole YRB.
When the YRCC began to coordinate among stakeholders, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)
\cite{krieger1955, ostrom1990}.
During this period, proportional decreased water use of provinces indicated a positive result of the regulation (see \nameref{result-3}).
The 98-UBR thus led to expected institutional outcomes at a basin scale, indicating that successful governance of SES emerged by indirectly (or vertically) creating links between different stakeholders.
Our model demonstrates that in this case, a unified scale-matched institution was indispensable for sustainable water use.

The structural building blocks we depicted here (Figure~\ref{fig:structure}) have also been reported in other SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}.
Before 98-UBR, SES structure (i.e., fragment ecological units linked to separate social actors) was more likely to be mismatched because isolated actors generally struggle to maintain interconnected ecosystems holistically \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
Institutional re-alignments since 98-UBR improved the authority of the YRCC and helped it match the scale of resource provisioning in the YRB, leading to enhanced social-ecological fit and better outcomes \cite{cumming2020a,wang2019d}.
The comparison demonstrates again the challenge of finding win-win situations in coupled human-nature systems \cite{hegwood2022}, and the need to more deeply understand the role of social-ecological structures \cite{bergsten2019, sayles2019}.
% Therefore, the YRB cases can provide further explanation of the matching and mismatching of the previous SES building blocks, linking SES structure and outcomes by plausible reasons of causality and underlying processes.

% \subsection{LIMITATION, INSIGHTS AND IMPLICATIONS}
% \subsection{Limitation, insights and implications}
% \label{discussion-4}
% discussion-3: 启示、未来的展望

Our approach has some inevitable limitations.
First, the contributions of economic growth and institutional shifts are difficult to distinguish because of intertwined causality (institutional changes can also influence the relative economic variables);
and second, when applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
Our quasi-experiment approach nonetheless provides evidence supporting the view that there was a change in water use trajectory following the YRB's unique institutional shifts and offers insights into water governance (and particularly the importance of having a scale-matched, basin-wide authority for water allocation solutions \cite{bodin2017b, ostrom2009, reyers2018})
Moreover, the ultimate success of the 98-UBR institutional shift theoretically and practically proved the importance of social-ecological fit.
For sustainability in the future, therefore, it is necessary to emphasize the necessity of strengthening connections between stakeholders by agents consistent with the scale of the ecological system.
From these perspectives, two scenarios based on the marginal benefit analysis (see \textit{\nameref{secS5}}) can inspire institutional design on how to reduce mismatches.
For example, water rights transfers may be another way to build horizontal links between stakeholders that also have the potential to result in better water governance.
In addition, policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to a changing SES context \cite{reyers2018}.

The structural building blocks that led to different outcomes are recurring motifs in global SESs, so our proposed mechanism is crucial to governing such coupled systems.
Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{\nameref{secS1}}) \cite{yu2019}.
Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development \cite{wang2019a}.
Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{\nameref{secS1}}).
Our analysis suggests that these initiatives can benefit by actively incorporating social-ecological matched building blocks when developing new institutions \cite{bodin2017b}.
Moreover, our research provides a cautionary tale of how institutions can create perverse incentives \cite{hegwood2022}, while insights from the YRB can provide guidelines for SESs management worldwide \cite{muneepeerakul2017, leslie2015}.

\section{CONCLUSION}\label{sec:conclusion}
%! Author = songshgeo
%! Date = 2022/3/10

Intense water use in one of the most anthropogenically altered large river basins, the Yellow River Basin (YRB), once led to drying up.
Alterations of institutions eventually successfully restored water governance practices on a decadal time scale.
We propose that the institutional shifts in the YRB (87-WAS and 98-UBR) framed two different SES structures and depicted them as widespread building blocks.
We quantitatively estimate the net effects of these changes in the YRB and analyze the reasons from SES structural perspectives.
Our results show that the historical records, the responses from stakeholders to structural changes, and the theoretical analysis from the marginal benefits analysis all support that fragmented ecological units linked to separate social actors frames a mismatched SES structure.
Through the quasi-natural experiments of the YRB, we demonstrate that social-ecological fits can lead to successful SESs management worldwide with better sustainability outcomes.

\section{MATERIALS AND METHODS}\label{sec:methods}
%! Author = songshgeo
%! Date = 2022/3/10

% 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程
We first abstract the SES structures of water used in the YRB from 1979 to 2008, where two institutional shifts split the period into three pieces.
To process the data, we use the Principal Components Analysis (PCA) method to reduce the dimensionality of variables affecting the total water use.
We then estimated the net effects of two institutional shifts on total water use, changing trends, and differences of the YRB's provinces, by Differenced Synthetic Control (DSC) method \cite{arkhangelsky2021}.
Finally, for theoretical discussion, we developed a marginal benefit analysis based on identified SES structures to provide the observed pattern of water use changes with a theoretical interpretation.

\subsection{Study area}\label{sec:yrb}

% 黄河的介绍
The Yellow River Basin (YRB), the fifth-largest river basin worldwide, is known for its vital role in the socio-economic development of China.
It supports $35.63\%$ of China's irrigation and $30\%$ of its population while containing only $2.66\%$ of its water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today).
In the 1980s, intense water use, accounting for about $80\%$ of Yellow River surface runoff, combined with other forms of human interference (e.g., soil conservation and water conservancy projects), caused consecutive drying events and substantial ecological, economic, and social crises (e.g., wetland shrinkage, agriculture reduction, and a scramble for water).
In response, Chinese authorities implemented several ambitious water management practices in the YRB to relieve water stress, such as reservoir regulation, the South-to-north Water Diversion Project (WDP), the 1987 Water Allocation Scheme (87-WAS), and the 1998 Unified Basinal Regulation (98-UBR) \cite{long2020, wang2019d}.
Those efforts led to ecological restoration of wetlands and the estuarine delta. Drying up has been avoided for over 20 years, which is widely considered a substantial management achievement.
Instead of relying on engineering to increase water supply, institutional strategies like the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, authority at a basin-level) focused mainly on limiting demand for water \cite{bouckaert2022, speed2013}.
While researchers have carefully evaluated and quantified the effects of engineering solutions on water supply\cite{long2020}, there have been few attempts to assess institutional contributions to successful water governance in the YRB.

\subsection{Portraying structures}\label{sec:structures}
% 制度结构关系抽象
We apply the network \cite{bodin2017b} approach to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit (the YRCC) into general building blocks (or motifs) (see Figure~\ref{framework}), from the official documents.
Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures. The network-based approach is to abstract connections between entities into links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.
In this study, we examined the official documents of the two institutional shifts of concern (87-WAS and 98-UBR, see \textit{Appendix \nameref{secS1}} for details).
Besides the ecologically connected river reaches, the agents (provinces and the YRCC) are abstracted as nodes, and their required interactions regarding water use are summarized as links.
The 1987-WAS requires the YRCC to monitor each river's reach, while the 1998-UBR requires direct interactions (through water use licenses) between the YRCC and the provinces.
Therefore, we linked the YRCC unit to each ecological unit after 87-WAS and each province unit after the 98-UBR.
We tested whether focusing on SES structures rather than institutional details could reasonably explain the differences caused by institutional shifts in the YRB.

\subsection{Dataset and preprocessing}\label{sec:dataset}
We choose datasets and variables to compare on actual and estimated water use of the YRB.
The actual water uses are accessible in China’s provincial annual water consumption dataset from the National Water Resources Utilization Survey, whose details are accessible from Zhou (2020) \cite{zhou2020}.
To estimate the water use of the YRB by assuming there were no effects from institutional shifts, we focused on variables from five categories (environmental, economic, domestic, and technological) water use factors. Their specific items and origins are listed in Table~\ref{tab:variables}.

Among the total $31$ data-accessible provinces (or regions) assigned quotas in the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin, and Beijing because of their trivial water use from the YRB (see \textit{Appendix}~Table~\ref{tab:quota}). We then divided the dataset into a ``target group'' and a ``control group'', treating provinces involved in water quota as the target group $(n=8)$ and other provinces as the control group $(n=20)$ for applying the DSC.

Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ principal components \textit{Appendix~\nameref{secS2}}. Bayan had proved that combining PCA and DSC can raise the robustness of causal inference \cite{bayani2021}. We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different. Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\nameref{secS2}~Figure~\ref{fig:elbow}}). Finally, we transform the dataset and input the dimensions-reduced output into the DSC model.

\subsection{Differenced Synthetic Control}\label{sec:DSC}
Using the Differenced Synthetic Control (DSC) method, we estimate water use without the effect of the institutional shift.
The DSC method is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadie2010, abadie2015, hill2021}.

This method aims to evaluate the effects of policy change that are not random across units but focuses on some of them (i.e., institutional shifts in the YRB here).
By re-weighting units to match the pre-trend for the treated and control units, the DSC method imputes post-treatment control outcomes for the treated unit(s) by constructing a synthetic version of the treated unit(s) equal to a convex combination of control units.
Therefore, the synthetic and actual version difference can be estimated as a net effect for a treated unit.

In practice, all treated units (i.e., provinces) were affected by institutional shifts in 1987 and 1998, each taken as the ``shifted'' time $t_0$ within two individually analyzed periods $T$: 1979-1998; 1987-2008.
We include each province in the YRB ($n=8$, see \textit{\nameref{sec:dataset}}) as the treated unit separately, as multiple treated units approach had been widely applied \cite{abadie2021}.
Then, we consider the $J+1$ units observed in time periods $T = {1,2 \cdots , T}$ with the remaining $J=20$ units are untreated provinces from outside.
We define $T_0$ to represent the number of pre-treatment periods ($1,\cdots,t_0$) and $T_1$ the number post-treatment periods ($t_0,\cdots,T$), such that $T = T_0+ T_1$.
The treated unit is exposed to the institutional shift in every post-treatment period $T_0$, unaffected by the institutional shift in all preceding periods $T_1$.
Then, any weighted average of the control units is a synthetic control and can be represented by a ($J * 1$) vector of weights $\mathbf{W} = (w_{1},...,w_{J})$, with $w_j \in (0, 1)$.
Among them, by introduce a ($k * k$) diagonal, semidefinite matrix $\mathbf{V}$ that signifies the relative importance of each covariate, the DSC method procedure for finding the optimal synthetic control ($W$) is expressed as follows:

\begin{equation}
    \mathbf{W^{*}(V)}=\underset{\mathbf{W} \in \mathcal{W}}{\operatorname{minimize}}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)^{\prime} \mathbf{V}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)
\end{equation}

where $\mathbf{W}^{*}(V)$ is the vector of weights $\mathbf{W}$ that minimizes the difference between the pre-treatment characteristics of the treated unit and the synthetic control, given $\mathbf{V}$. That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W*(V)}$. Therefore, we choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{W*(V)}$ that minimizes the following expression:

\begin{equation}
    \mathbf{V}^{*}=\underset{\mathbf{V} \in \mathcal{V}}{\operatorname{argmin}}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)^{\prime}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)
\end{equation}

That is the minimum difference between the outcome of the treated unit and the synthetic control in the pre-treatment period, where $\mathbf{Z}_{1}$ is a ($1*T_0$) matrix containing every observation of the outcome for the treated unit in the pre-treatment period. Similarly, let $\mathbf{Z}_{0}$ be a ($k * T_0$) matrix containing the outcome for each control unit in the pre-treatment period, and $k$ is the number of variables in the datasets.
The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with double robustness properties \cite{billmeier2013, smith2015}.

\subsection{Marginal benefits analysis}\label{sec:model}
To infer the mechanisms underlying the results, we developed an marginal benefits analysis based on marginal revenue to analyze how the institutional shift could have led to differences in water use.

\begin{ass}
    (Water-dependent production) Because of irreplaceably, water is assumed to be the only production function input with two production efficiency types.
\end{ass}

\begin{ass}
    (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin, the water use cost is equally assigned to each province.
\end{ass}

\begin{ass}
    (Multi-period settings) There are multiple settings periods with a constant discount factor for the expectation of future water use.
\end{ass}

Under the above-simplified assumptions, we demonstrate three cases -corresponding to the abstracted SES structures (Figure~\ref{fig:structure}), inference of how SES structure alters the expected marginal benefits and costs of provinces making decisions.
As one of the possible interpretations for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.

\bibliography{../mybib}
\bibliographystyle{sn-standardnature}
\label{bib}

%%%%%%%% -----  02_appendix -------- %%%%%%%%%%
\newpage
\appendix
\label{appendix}
\renewcommand{\figurename}{Supplementary Figure}
\renewcommand{\appendixname}{Appendix~\Alph{section}}
\setcounter{section}{0}

\section{Appendix~A: Contexts of institutional shifts}\label{secS1}
\renewcommand{\thefigure}{A\arabic{figure}}
\renewcommand{\thetable}{A\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}
%! Author = songshgeo
%! Date = 2022/3/10

We aim to abstract the water allocating institutions from the description in official documents with necessary context into SES building blocks (Figure~\ref{framework})
Widespread building blocks in SES are the key to the functioning of structures, and a network-based description is a widely used way to depict them by abstracting links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.

\begin{figure}[!bh]
	\centering
	\includegraphics[width=0.9\linewidth]{diagrams/framework.jpg}
	\caption{
		Framework for understanding linkages between SES structures and outcomes.
		\textbf{a.} The general framework for analyzing social-ecological systems (SESs) (adapted from Ostrom \cite{ostrom2009}). Institutions embedded in SESs may reshape structures by changing the interactions between core subsystems, resulting in different outcomes.
        Three typical types of abstracted SES structures are shown as \textbf{b.}, \textbf{c.} and \textbf{d.} (adapted from Bodin, 2017)\cite{bodin2017b}. Red circles indicate social actors, and green ones indicate ecological components. Connection (ties between two ecological components), collaboration (ties between two social actors), or management (ties between a social actor and an ecological component) exist when gray lines link two units. According to empirical evidence, the gray dashed lines show aligned SES structures that are more likely to achieve a desirable outcome.
        }
    \label{framework}
\end{figure}

% 水资源分配方案在全世界范围内都是流域管理的普遍制度。
Water allocation institutions are widespread in large river basin management programs throughout the world (see \textit{Appendix} Figure~\ref{fig:world}) \cite{speed2013}.
This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level)\cite{wang2019a}:
\begin{itemize}
    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wang2019, wang2019a}.
    \item \textbf{1987}: Implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
    \item \textbf{1998}: Implementation of unified regulation. (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
    % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
    \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wang2019,wang2019a}.
    \item \textbf{2021}: A call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
\end{itemize}

% 在上述文件中，1982年的文件标志着设计分水制度尝试的开始，2008年标志着该制度走向成熟（完全建立起流域-省-市区的多级水资源分配和统一调度）。
Since 1982, administrations attemptted to design a quota institution, and the 2008 document marked the maturity of the scheme (complete establishment of basin-level, provincial, and district water quotas).
Between the period, two significant institutional shits can be analyzed by using the 1987 (87-WAS) and 1998 (98-UBR) documents.

% It is worth noting that, although the essential reason for these institutions was the mismatch between the spatial and temporal distribution of water resources as well as social and economic water demands, the direct reason for their introduction was the depletion of the Yellow River.

The official documents in 1987 (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today) convey the following key points:

\begin{itemize}
	% 该政策面向的目标是各省（区域），黄委会没有被提及
	\item The policy is aimed at related provinces (or regions at the same administrative level).
	% 政策制定的首要考虑是解决断流问题
	\item Depletion of the river is identified as the first consideration of this institution.
	% 各省被鼓励在此配额下制定自己的用水计划
	\item Provinces are encouraged to develop their water use plans based on a quota system.
	% 水资源供给无法满足需求对相关省（地区）是普遍现象。
	\item Water in short supply is a common phenomenon in relevant provinces (regions).
\end{itemize}

The official documents in 1998
(\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today) convey the following key points:

\begin{itemize}
	% 除了说明政策针对的各省区之外，明确指出其用水需要黄河水利委员会进行申报，并由其组织和监管
	\item The document points out that not only provinces and autonomous regions involved in water resources management (see \textit{Article 3}), the provinces’ and regions’ water use shall be declared, organized, and supervised by the YRCC (\textit{Article 11 and Chapter III to Chapter V, and Chapter VII}).
	% 本研究(\textit{ Article 1})首先考虑的是上、中、下游用水的总体规划。
	\item Creating the overall plan of water use in the upper, middle, and lower reaches is identified as the first consideration of this institution (\textit{Article 1}).
	% 各省需要
	\item With the same quota as used in the 1987 policy, provinces were encouraged to further distribute their quota into lower-level administrations (see \textit{Article 6 and Article 41}).
	% 强调以总量确定供给，以供给决定需求。
	\item They emphasize that supply is determined by total quantity, and water use should not exceed the quota proposed in 1987 (see \textit{Article 2}).
\end{itemize}

\begin{figure*}[!htb]
    \centering
    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/world_institutions}
	\caption{
		Overview of water allocation institutions.
		% 世界已有水资源分配制度的大河流域，其中黄河流域最早于1987年提出资源分配方案，后于1998年更改为统一调度方案。
		\textbf{A.} Major river basins in the world with water resource allocation systems (shaded red); the YRB first proposed a resource allocation scheme in 1987 (designed since 1983) and then changed to a unified regulation scheme in 1998 (designed in 1997 but implemented in 1998) \cite{speed2013}.
		% 不同的水资源分配制度设计模式，中国黄河流域是典型的自上而下。
		\textbf{B.} Different water resource allocation system design patterns; the YRB is typical of a top-down system.
		% 流域分水制度的演化。这种多层次的制度设计有其历史变化过程。
		\textbf{C.} The four periods of institutional evolution of water allocation of the YRB.
	}
    \label{fig:world}
\end{figure*}

% 基于上述分析，我们抽象出了两次制度转变之后的SES结构变化如正文的图1C所示。
Based on the above documents, we abstracted the structural changes of SES (see \textit{Appendix S2}) after the two institutional changes, as shown in Figure~\ref{fig:structure}~C.

\begin{table*}
    \centering
    \small
    \caption{Water quotas assigned in the 87-WAS}\label{tab:quota}
	\resizebox{\linewidth}{!}{
    \begin{tabular}{p{0.24\linewidth}llllp{0.1\linewidth}lllll}
	\hline
	Items (water volume, billion $m^3$)                    & Qinghai & Sichuan & Gansu   & Ningxia & Inner Mongolia & Shanxi  & Shaanxi & Henan   & Shandong & Jinji  \\
	\hline
	Demands in water plan                                                & 35.7    & 0       & 73.5    & 60.5    & 148.9          & 115     & 60.8    & 111.8   & 84       & 6      \\
	Quota designed in 1983                                               & 14      & 0       & 30      & 40      & 62             & 43      & 52      & 58      & 75       & 0      \\
	Quota assigned in 1987                                               & 14.1    & 0.4     & 30.4    & 40.0    & 58.6           & 38.0    & 43.1    & 55.4    & 70.0     & 20     \\
	Average water consumption from the Yellow River from 1987-2008       & 12.03   & 0.25$^a$   & 25.80   & 36.58   & 61.97          & 21.16   & 11.97   & 34.30   & 77.87    & 5.85$^a$  \\
	Proportion of water from the Yellow River in total water consumption & 48.12\% & 0.10$^b$\%  & 30.79\% & 58.45\% & 47.82\%        & 73.55\% & 44.39\% & 24.77\% & 34.41\%  & 3.11\%$^b$ \\
    \hline
    \end{tabular}}
	\footnotesize[a]\leftline{{Calculated by data from 2004 to 2017.}}\\
	\footnotesize[b]{\leftline{The share is too small, thus the provinces (or region) Sichuan and Jinji not to be considered in this study.}}
\end{table*}

\section{Appendix~B: Robustness of DSC method}\label{secS2}
\renewcommand{\thefigure}{B\arabic{figure}}
\renewcommand{\thetable}{B\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}
%! Author = songshgeo
%! Date = 2022/3/19

% 找到具解释力的变量是构造合成控制法稳健的关键。
Explanatory variables are the key to constructing a robust synthetic control method.
% 我们共使用了用水量密切相关的26个变量，这些变量的数据集已在先前的研究中被用来解释中国的用水量变化
We used a total of $24$ variables related to water consumption Table~\ref{tab:variables}, which datasets have been used in previous studies to explain changes in water use in China \cite{zhou2020}.
% 由于这些变量间存在自相关，我们通过肘部法供选择了5个主成分作为DSC的输入，前人研究表明PCA方法的结合能够增强合成控制法的稳健性
In addition, we selected $5$ principal components as input by the elbow method because selection in autocorrelated variables reduces dimensions and then enhances the robustness of the DSC (Figure~\ref{fig:elbow}).

There are two approaches to validity testing of the DSC: (1) comparing the post-treated and pre-treated reconstructions and (2) testing robustness through placebo analysis.
For (1), differences between each province and their synthetic are significant in post-treated periods and small in pre-treated periods (Figure~\ref{fig:87panel} and figure~\ref{fig:98panel}), which show good reconstructions of their water use changes' estimation.
For (2), we applied the in-place placebo analysis described by \cite{abadie2010}. In most provinces, ratios of post-MSPE to pre-MSPE are higher than the median of other placebo units, which suggests the institutional shifts in treated time (1987 and 1998 here) influenced them more than most of the other provinces (figure~\ref{fig:87placebo}, figure~\ref{fig:98placebo}, Table~\ref{tab:DSC_summary}).

\begin{figure*}
    \includegraphics[width=0.9\linewidth]{outputs/87panel.pdf}
    \centering
    \caption{Comparations between YRB' provinces and their synthetic controls around the 87-WAS.}
    \label{fig:87panel}
\end{figure*}

\begin{figure*}
    \includegraphics[width=0.9\linewidth]{outputs/98panel.pdf}
    \centering
    \caption{Comparations between YRB' provinces and their synthetic controls around the 98-UBR.}
    \label{fig:98panel}
\end{figure*}

\begin{figure*}
    \includegraphics[width=0.9\linewidth]{outputs/87placebo.pdf}
    \centering
    \caption{Gaps in change in water use between provinces outside the YRB and their synthetic control, around the 87-WAS, excluding the provinces with high pre-treatment RMSPE (more than $3$ times of treated units' RMSPE).}
    \label{fig:87placebo}
\end{figure*}

\begin{figure*}
    \includegraphics[width=0.9\linewidth]{outputs/98placebo.pdf}
    \centering
    \caption{Gaps in change in water use between provinces outside the YRB and their synthetic control, around the 98-UBR, excluding the provinces with high pre-treatment RMSPE (more than $3$ times of treated units' RMSPE)}
    \label{fig:98placebo}
\end{figure*}

\begin{table*}[!ht]
	\caption{Variables and their categories for water use predictions}
	\scriptsize
	\label{tab:variables}
	\resizebox{\linewidth}{!}{
	\begin{tabular}{lllll}
	\hline
	Sector &
	  Category &
	  Unit &
	  Description &
	  Variables \\ \hline
	Agriculture &
	  Irrigation Area &
	  thousand ha &
	  \begin{tabular}[c]{@{}l@{}}Area equipped for irrgiation by different \\ crop:\end{tabular} &
	  \begin{tabular}[c]{@{}l@{}}Rice, \\ Wheat, \\ Maize, \\ Fruits, \\ Others.\end{tabular} \\ \hline
	Industry &
	  \begin{tabular}[c]{@{}l@{}}Industrial gross \\ value added\end{tabular} &
	  Billion Yuan &
	  Industrial GVA by industries &
	  \begin{tabular}[c]{@{}l@{}}Textile, \\ Papermaking, \\ Petrochemicals, \\ Metallurgy, \\ Mining, \\ Food, \\ Cements, \\ Machinery, \\ Electronics, \\ Thermal electrivity, \\ Others.\end{tabular} \\
	 &
	  \begin{tabular}[c]{@{}l@{}}Industrial water \\ use efficiency\end{tabular} &
	  \% &
	  \begin{tabular}[c]{@{}l@{}}The ratio of recycled water and evaporated \\ water to total industrial water use\end{tabular} &
	  \begin{tabular}[c]{@{}l@{}}Ratio of industrial water recycling, \\ Ratio of industrial water evaporated.\end{tabular} \\ \hline
	Services &
	  \begin{tabular}[c]{@{}l@{}}Services gross \\ value added\end{tabular} &
	  Billion Yuan &
	  GVA of service activities &
	  Services GVA \\ \hline
	Domestic &
	  Urban population &
	  Million Capita &
	  Population living in urban regions. &
	  Urban pop \\
	 &
	  Rural population &
	  Million Capita &
	  Population living in rural regions. &
	  Rural pop \\
	 &
	  Livestock population &
	  Billion KJ &
	  \begin{tabular}[c]{@{}l@{}}Livestock commodity calories summed from \\ 7 types of animal.\end{tabular} &
	  Livestock \\ \hline
	Environment &
		  Temperature & $K$ & Near surface air temperature & Temperature \\
			& Precipitation & $mm$ & Annual accumulated precipitation & Precipitation \\ \hline
	\end{tabular}}
\end{table*}

\begin{figure*}
    \includegraphics[width=0.9\linewidth]{outputs/elbow.pdf}
    \centering
    \caption{Choose number of pricipal components by Elbow method, $5$ pricipal components already capture $89.63\%$ explained variance.}
    \label{fig:elbow}
\end{figure*}

\begin{table*}
	\caption{Pre and post treatment root mean squared prediction error (RMSPE) for YRB's provinces}
	\label{tab:DSC_summary}
	\scriptsize
	\centering
	\resizebox{\linewidth}{!}{
	\begin{tabular}{lrrrrrrrr}
	\hline
	 & \multicolumn{4}{c}{1987-WAS} & \multicolumn{4}{c}{1998-UBR} \\
	 Provinces & Pre-RMSPE & Post-RMSPE & Ratio & Significant$^a$ & Pre-RMSPE & Post-RMSPE & Ratio & Significant$^a$ \\
	 \hline
	 Qinghai & 0.016 & 0.231 & 14.606 & True & 0.230 & 1.170 & 5.096 & True \\
	Gansu & 0.056 & 1.307 & 23.265 & True & 0.244 & 0.841 & 3.448 & True \\
	Ningxia & 0.097 & 0.944 & 9.697 & True & 0.332 & 1.091 & 3.284 & True \\
	Neimeng & 0.335 & 3.846 & 11.479 & True & 1.320 & 1.183 & 0.896 & False \\
	Shanxi & 0.208 & 0.675 & 3.241 & False & 0.264 & 0.401 & 1.520 & False \\
	Shaanxi & 0.181 & 0.572 & 3.164 & False & 0.096 & 0.724 & 7.579 & True \\
	Henan & 0.210 & 3.207 & 15.292 & True & 1.222 & 2.479 & 2.029 & False \\
	Shandong & 0.209 & 1.840 & 8.785 & True & 0.431 & 1.517 & 3.516 & True \\
	\hline
	\end{tabular}}
	\footnotesize[a]\leftline{{Larger post/pre RMSPE than the median of the placebos.}}\\
\end{table*}

% \section{S2: Methods in details}\label{secS3}
% \input{../02_appendix/03_results_appendix.tex}

\section{Appendix~C: Optimization model for water use}\label{secS4}
\renewcommand{\thefigure}{C\arabic{figure}}
\renewcommand{\thetable}{C\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}
%! Author = songshgeo
%! Date = 2022/3/19

\paragraph{Setup}

To understand the mechanisms through which the SES structure impacts provincial water use, we developed a dynamic marginal benefits analysis to analyze how institutional mismatch could have led to the changes in water use, especially among provinces with high incentives for excess water use. Specifically, we modeled individual provincial decision-making in water resources before quota execution.

We proposed three intuitive and general assumptions:

\begin{ass}
(Water-dependent production) Because of irreplaceability, water is assumed to be the only input of the production function with two types of production efficiency. The production function of a high-incentive province is $A_HF(x)$, and the production function of a low-incentive province is $A_LF(x)$ ($A_H>A_L$). F(x) is continuous, $F'(0)=\infty$, $ F'(\infty)=0$, $F'(x)>0$, and $F''(x)<0$. The production output is under perfect competition, with a constant unit price of $P$.
\end{ass}

\begin{ass}
 (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in $N$ provinces, the cost of water use is equally assigned to each province under any water use. The unit cost of water is a constant $C$.
\end{ass}
\begin{ass}
(Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water use.
\end{ass}
Under the above assumptions, we can demonstrate three cases to simulate the water use decision-making and water use patterns in a whole basin.

Under the above assumptions, we can demonstrate three cases consisting of local governments in a whole basin to simulate their water use decision-making and water use patterns.

 %case1
\begin{case}Dentralized decision: This case corresponds to a situation without any high-level water allocation institution.

When each province independently decides on its water use, the optimal water use $x_i^*$ in province $i$ satisfies:

 $AF'(x)=\frac{C}{P}$,

 where $A_H$ and $A_L$ denote high-incentive and low-incentive provinces, respectively.

 When the decisions in different periods are independent, for $t$ = $0, 1, 2 \cdots$, then:

 $x_{it}^* = x_i^*$

 \end{case}

 %case2
 \begin{case} Mismatched decision: This case corresponds to a mismatched institution.

 The water quota is determined at $t$=0 and imposed in $t$=1,2,... Under the subjective expectation of each province that current water use may influence the future water allocation determined by high-level authorities, the total quota is a constant denoted as Q, and the quota for province $i$ is determined in a proportional form:

 $Q_i=Q \cdot \frac{x_i}{x_i + \begin{matrix}\sum{x_{-i}} \end{matrix}}$.

Under a scenario with decentralized decision-making with a water quota, given other provinces' decisions on water use remain unchanged, the optimal water use of province $i$ at $t$=0 satisfies:

$AF'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix})^2}$,

where $A_H$ denotes a high-incentive province and $A_L$ denotes a low-incentive province.

 \end{case}

 %case3
 \begin{case} Matched institution: This case corresponds to the institution under which water use in a basin is centrally managed.

 When the $N$ provinces decide on water use as a unified whole (e.g., the central government completely decides and controls the water use in each province), the optimal water use $x_i^*$ of province $i$ satisfies:

$F'(x)=\frac{C}{P}$.

 \end{case}

We propose Proposition 1 and Proposition 2:

Proposition 1: Compared with the decentralized institution, a matched institution with unified management decreases total water use.

The optimal water use under the three cases implies that mismatched institutions cause incentive distortions and lead to resource overuse.

Proposition 2: Water overuse is higher among provinces with high water use incentives than low- water use incentives under a mismatched institution.

The intuition for this proposition is straightforward in that all provinces would use up their allocated quota under a relatively small $Q$. As production efficiency increases, the marginal benefits of a unit quota increase, and the quota would provide higher future benefits for a pre-emptive water use strategy. Provinces with high production efficiency have higher optimal water use values under the decentralized decision. The divergence in water use would be exaggerated when the water quota is expected to be implemented with greater competition.

Extensions of the model are shown in Supplementary Material S3.%%%

%Appendix的模型和proposition推导细节部分
%放在Appendix
Appendix: Water Use Optimization

%case1
\begin{case_appendix}Centralized decision

When the N provinces decide on water uses as a unity, the marginal cost is C, equal to its fixed unit cost.
The water use of province $i$ aims to maximize $P\cdot A\cdot F(x)-C$.
Hence, $x_i^*$ satisfies $P \cdot A\cdot F'(x)=C$, i.e., $AF'(x)=\frac{C}{P}$, where A denotes $A_H$ for a high-incentive province and $A_L$ for a low-incentive province.

\end{case_appendix}

%case2
 \begin{case_appendix}Decentralized decision

When each of the N provinces independently decides on its water use, the marginal cost of water use would be $\frac{C}{N}$ as a result of cost-sharing with others.
Hence, the optimal water use in province i at period t, denoted as $\hat x_i^*$, satisfies $P \cdot A \cdot F'(x_{it})=\frac{C}{N}$, i.e., $A \cdot F'(x)=\frac{C}{P \cdot N}$.
Since $F'$ is monotonically decreasing, $\hat x_{it}^*>x_i^*$.
\end{case_appendix}

%case3
 \begin{case_appendix}Forward-looking decentralized decision under quota restrictions

 When the water quota would constrain future water use, the dynamic optimization problem of province i is shown as follows. In $t=1,2,\cdots$, there would be no relevant cost when the quota is bound that each province takes ongoing costs of $\frac{P \cdot Q}{N}$ regardless of the allocation. Therefore, it is sufficient to consider only the total water quota is less than total water use in Case 2 since a ``too large'' quota doesn't make sense for ecological policies.

$max  \quad P \cdot A \cdot F(x_{i,0})-\frac{C \cdot \begin{matrix} \sum x_{i,0} + x_{-i,0} \end{matrix}}{N}+\beta P \cdot A \cdot F(x_{i,1})+\beta^2 P \cdot A \cdot F(x_{i,2})+...$

$=P \cdot A \cdot F(x_{i,0})-C \cdot \frac{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}{N}+\frac{\beta}{1-\beta} P \cdot A \cdot F(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}})$

First-order condition: $P \cdot A \cdot F'(x_{i,0})-\frac{C}{N}+\frac{\beta}{1-\beta}[P \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0}+\begin{matrix} \sum  x_{-i,0} \end{matrix})^2}]=0$

where $f(\cdot)$ is the differential function of $F(\cdot)$.

The optimal water use in province i at t=0 $\widetilde x_{i,0}^*$ satisfies $P \cdot A \cdot F'(x_{i,0})=\frac{C}{N}-\frac{\beta}{1-\beta} \cdot P \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$,
i.e.,
$A \cdot F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$.

Since $F'>0$ and $F''<0$, $\widetilde x_i^*>\hat x_i^*>x_i^*$, taken others' water use $x_{-i,0}$ as given. Since the provincial water use decisions are exactly symmetric, total water use would increase when each province has higher incentives for current water use.

%Proposition 1
Proof of Proposition 1:

Because $F'>0$ and $F''(x)<0$ is monotonically decreasing, based on a comparison of costs and benefits for stakeholders (provinces) in the three cases,

$\widetilde x_i^*>\hat x_i^*>x_i^*$.

The result of $\hat x_i^*>x_i^*$ indicates that individual rationality would deviate from collective rationality under unclear property rights where a water user is fully responsible for the relevant costs. The result of $\hat x_i^*>x_i^*$

The difference between $ x_i^*$ and $\hat x_i^*$ stems from two parts: the effect of the marginal returns and the effect of the marginal costs. First, the ``shadow value'' provides additional marginal returns of water use in $t$ = 0, which increases the incentives of water overuse by encouraging bargaining for a larger quota. Second, the future cost of water use would be degraded from $\frac{P}{N}$ to an irrelevant cost.

%Proposition 2
Proof of Proposition 2:

Since $A_H>A_L$, $F'(x_H)<F'(x_L)$,
Eq.(xxx) %此处引用：$AF'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix})^2}$
implies a positive relation between $x_{i0}$ and A, when $\beta, P, C, Q$, and other provinces' water use are taken as given.

The difference between $\widetilde x_i^*$ and $\hat x_i^*$ (i.e., $\frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$) represents the incentive of water overuse derived from an expectation of water quota allocation. The incentive of water overuse increases by A.
\end{case_appendix}

\section{Appendix~D: Model extensions}\label{secS5}
\renewcommand{\thefigure}{D\arabic{figure}}
\renewcommand{\thetable}{D\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}
%Model extension部分
Using the marginal benefits analysis (see the Methods section in the main text), we also explored the response of stakeholders to water quota policies. We considered two additional scenarios for stakeholders: technology growth and one that felt different valuations through time (via the discount rate) of economic benefits and ecological costs. In the following scenarios, the cost is assumed to be untransferable, which could be fully allocated to the one incurring the water use. Explaining plausible scenarios for these stakeholders will help us better understand the causes of water overuse and potential solutions. We argue that water overuse remains robust even if a complete and equitable system.

% technology growth
    \begin{case_appendix}Forward-looking decentralized decision, taken ecology cost into considerations

    Even if the negative externality of water overuse is eliminated by ``fair'' ecology cost of $\frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \cdot Q \cdot C$, it is possible that the future growth opportunities and ``remote" ecological costs provide enough incentive for the sprint.  Water overuse has the value of future economic benefits by slacking the water use constraint in the future. The heterogeneous production efficiency is omitted in this section, and we set A=1.

(a) technology growth

Assume that there is an exogenous technology growth rate of g in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$, and discount factor $\beta$. For simplicity, consider a finite-period water use optimization:

$ max \quad P \cdot (1+g)^t ln(1+x_{i,0})-\frac{C}{N}+\beta^t \begin{matrix} \sum_{t=1}^T [P \cdot (1+g)^t ln(x_{i,t}+1)-C \cdot x_{i,t}] \end{matrix}$

$s.t. \quad x_{i,t} \leq Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \quad for \quad \forall t$

We depict the relationship between multi-period profit and water use $x_{i,0}$ in different horizons in Figure~\ref{fig:technology}
, and thus find out the optimal water use pattern under technology growth. The higher marginal water output might create enough incentive to offset the untransferable cost since a higher allocated quota provides growth option value. On the other hand, as the provincial decision is under a longer horizon, there is a more significant sprint effect due to higher accumulated yield and relatively tighter water use constraints over time.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\linewidth]{outputs/Fig3.jpg}
    \caption{Multi-period optimization of optimal water use under technology growth. The figure depicts the relationship of multi-period benefits of province $i$ and water use under Case 3 with technology growth. Assume $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta=0.7$, $g=0.2$, and $Q=8$.}
    \label{fig:technology}
\end{figure}

(b) Economic benefits and ``remote'' ecological costs with different discount factors

Assuming that there is a high discount rate for economic benefits and a low discount rate for ecological costs, in the scenario of $N$ provinces bargaining for water use under total quota $Q$, with unit price of output $P$, unit cost $C$, discount factor $\beta^{economy}$ and $\beta^{ecology}$ ($\beta^{economy} > \beta^{ecology}$). For simplicity, consider the following finite-period water use optimization, noting the water use of province $i$ at period $t$:

$ max \quad P \cdot ln(1+x_{i,0})-\frac{C}{N}+\beta_1^t \begin{matrix} \sum_{t=1}^T [P \cdot ln(x_{i,t}+1)]  \end{matrix} - \beta_2^t \begin{matrix} \sum_{t=1}^T [C \cdot x_{i,t}] \end{matrix}$

$s.t. \quad x_{i,t} \leq Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}} \quad for \quad \forall t$

We depict the relationship of multi-period net income and water use $x_{i,0}$ in different horizons in Figure~\ref{fig:remote}
, and thus find out the optimal water use pattern under ``remote'' ecological costs. The higher discounted ecological costs might create enough incentive to set off the untransferable cost. On the other hand, as the provincial decision is under a longer horizon, a more significant sprint effect is due to a higher accumulated yield.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\linewidth]{outputs/Fig4.jpg}
    \caption{Multi-period optimization of water use under ``remote'' ecological cost. The figure depicts the relationship of multi-period benefits of province $i$ and water use under Case 3 with ``remote'' ecological cost. Assume $F(x)=ln(1+x)$, $N=8$, $P=1$, $C=0.5$, $\beta_{economy}=0.7$, $\beta_{ecology}=0.3$, and $Q=8$.}
    \label{fig:remote}
\end{figure}

\end{case_appendix}

%% Put the bibliography here, most people will use BiBTeX in
%% which case the environment below should be replaced with
%% the \bibliography{} command.
% \newpage
% \newpage
% \bibliography{../mybib}
% \bibliographystyle{sn-standardnature}
% \label{bib}
\end{document}

### 2022-07-04 docs/papers/01_manuscript/01_introduction.tex
fix(shuaiwang-comments): rectify by shuaiwang comments

@@
 
-In methodology, we explored causal linkages between SES structures and sustainability-related outcomes by quasi-natural experiments (institutional shifts imposed by central government) in the YRB.
-Firstly, we used data on changes in official documents following two institutional shifts (the 87-WAS and the 98-UBR) to describe comparable changes in the SES structures associated with the YRB from 1979 to 2008, by abstracting them into SES structures motifs (or building blocks, see \textit{\nameref{sec:structures}}).
+We explored causal linkages between SES structures and sustainability-related outcomes by quasi-natural experiments (institutional shifts imposed by central government) in the YRB.
+Firstly, we used data on changes in official documents following two institutional shifts to describe comparable changes in the SES structures associated with the YRB from 1979 to 2008, by abstracting them into SES structures motifs (or building blocks, see \textit{\nameref{sec:structures}}).
 We then used a method called `Differenced Synthetic Control (DSC)' \cite{arkhangelsky2021}, which considers economic growth and natural background, to estimate theoretical water use scenarios without institutional shifts (\textit{\nameref{sec:DSC}} and \textit{\nameref{secS2}}).

### 2022-07-04 docs/papers/01_manuscript/03_results.tex
fix(shuaiwang-comments): rectify by shuaiwang comments

@@
 	\caption{
-		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
+		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}~C) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
 	\label{fig:model}
@@
 Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.
-Until water-use decisions are consolidated into unified management, each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive to use water, leading to higher water use.
-Furthermore, water users with higher capability are more stimulated by institutional shifts and away from the theoretically optimal water use under a unified allocation.
+Until water-use decisions are consolidated into unified management (case 3), each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive to use water (case 2), leading to higher water use than that of the past decentralized situation (case 1).
+Furthermore, in case 2, the water users with higher capability are more stimulated by the institutional shift and away from the theoretically optimal water use under a unified allocation.

### 2022-07-04 docs/papers/01_manuscript/03_results.tex
fix(rectify-by-shuaiwang-comment): fix case1-case3 in order
BREAKING CHANGE:

@@
 
-For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (analogy to Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
+For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (case 1 to case 3, corresponding to different SES structures in Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
 Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.
-Until water-use decisions are consolidated into unified management (case 3), each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive to use water (case 2), leading to higher water use than that of the past decentralized situation (case 1).
-Furthermore, in case 2, the water users with higher capability are more stimulated by the institutional shift and away from the theoretically optimal water use under a unified allocation.
+As a benchmark, case 1 analogy to a decentralized stakeholders situation and lead to medium-level water use.
+In case 2, each stakeholder expects that current water use helps bargain for a favorable water quota in the face of institutional shift (see \textit{\nameref{secS4}}), which can intensify the incentive to use water, leading to higher water use.
+Furthermore, the water users with higher capability are more stimulated by the institutional shift and away from the theoretically optimal water use under a unified allocation.
+After water-use decisions are consolidated into unified management (case 3), marginal benefits analysis suggests the lowest water use among the cases.

### 2022-07-04 docs/papers/01_manuscript/06_methods.tex
fix(rectify-by-shuaiwang-comment): fix case1-case3 in order
BREAKING CHANGE:

@@
 
-Under the above-simplified assumptions, we demonstrate three cases -corresponding to the abstracted SES structures (Figure~\ref{fig:structure}), inference of how SES structure alters the expected marginal benefits and costs of provinces making decisions.
+Under the above-simplified assumptions, we demonstrate three cases -corresponding to the abstracted SES structures (Figure~\ref{fig:structure}~C), inference of how SES structure alters the expected marginal benefits and costs of provinces making decisions.
 As one of the possible interpretations for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.

### 2022-07-04 docs/papers/02_appendix/04_theoretical_model.tex
fix(rectify-by-shuaiwang-comment): fix case1-case3 in order
BREAKING CHANGE:

@@
  %case1
-\begin{case}Dentralized decision: This case corresponds to a situation without any high-level water allocation institution.
+\begin{case} Dentralized decision: This case corresponds to a situation without any high-level water allocation institution.
 
@@
  %case2
- \begin{case} Mismatched decision: This case corresponds to a mismatched institution.
+ \begin{case} Mismatched institution: This case corresponds to an SES structure where fragmented stakeholders are linked to unified river reaches.
 

### 2022-07-15 docs/papers/01_manuscript/01_introduction.tex
docs(cover-letter): re-submission to NSR

@@
 Those river basin systems successfully supporting sustainable water resource use are structurally well-aligned with water provisioning and social-ecological demands, without inefficient competition or overuses \cite{wang2019d}.
-However, balancing the water demands of ecosystems and development in heavily human-dominated river basins is a challenge because human activities and water are intertwined in their structures as complex social-ecological systems (SES) \cite{huggins2022,konar2019}.
+However, balancing the water demands of ecosystems and development in heavily human-dominated river basins is a challenge because human activities and water are intertwined in their structures as complex social-ecological systems (SES) \cite{huggins2022,konar2019} (Figure~\ref{fig:framework}).
 
@@
 Understanding how these complex interplays are crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems \cite{kluger2020}.
-Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, supporting (but not guaranteeing) the sustainability of SES \cite{epstein2015, wang2019d}.
+Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, supporting (but not guaranteeing) the sustainability of SES \cite{epstein2015, wang2019d} (Figure~\ref{fig:framework}~\textbf{a}).
 Some institutional advances have had desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d}, and collaborative water governance systems in Europe \cite{green2013}).
 However, imposing institutional changes on a large, complex river basin may create or destroy hundreds of connections between social agents and ecological units, where matched social-ecological structures are not ubiquitous.
-Two particular weaknesses in existing knowledge of institutional matches include understanding: (i) the causal links between SES structures and outcomes; (ii) details of the underlying processes, and especially the coordination of the incentives of different participants, that result from an institutional lack of matches.
+Two particular weaknesses in existing knowledge of institutional matches include understanding (Figure~\ref{fig:framework}~\textbf{b}): (i) the causal links between SES structures and outcomes; (ii) details of the underlying processes, and especially the coordination of the incentives of different participants, that result from an institutional lack of matches.
 These weaknesses limit understanding of institutional design and hinder approaches toward institutional matches for improving the sustainability of river basin systems.
 
-To better understand how water governance institutions match their social-ecological context, we take the Yellow River Basin (YRB), China, as an example \textit{\nameref{sec:yrb}} to dive into causal links between SES structures and outcomes.
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.5\linewidth]{diagrams/framework.png}
+	\caption{
+		Framework for understanding linkages between SES structures and outcomes.
+\textbf{a.} In the general framework for analyzing social-ecological systems (SESs), (Adapted from Ostrom, 2008 \cite{ostrom2009}).
+Institutional shifts can change interactions within the SES and reframe the structures.
+\textbf{b.} We aim to investigate causal links between matched/mismatched SES structures and their corresponding outcomes.
+	}
+	\label{fig:framework}
+\end{figure}
+
+To better understand how water governance institutions match their social-ecological context, we take the Yellow River Basin (YRB), China, as an example (see \textit{\nameref{sec:yrb}}) to dive into causal links between SES structures and outcomes.
 Specifically, we focused on two institutional shifts in water allocation of the YRB: the 1987 Water Allocation Scheme (87-WAS), and the 1998 Unified Basinal Regulation (98-UBR), which reframed SES structures significantly.

### 2022-07-15 docs/papers/01_manuscript/06_methods.tex
docs(cover-letter): re-submission to NSR

@@
 % 制度结构关系抽象
-We apply the network \cite{bodin2017b} approach to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit (the YRCC) into general building blocks (or motifs) (see Figure~\ref{framework}), from the official documents.
+Widespread building blocks in SES are the key to the functioning of structures, and a network-based description is a widely used way to depict them by abstracting links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.
+We apply the network approach \cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit (the YRCC) into general building blocks (or motifs) (see Figure~\ref{framework}), from the official documents.
 Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures.

### 2022-07-15 docs/papers/02_appendix/01_institution_context.tex
docs: plain text version
fix(figures-update): fig updates
docs(cover-letter): re-submission to NSR

@@
 
-We aim to abstract the water allocating institutions from the description in official documents with necessary context into SES building blocks (Figure~\ref{framework})
-Widespread building blocks in SES are the key to the functioning of structures, and a network-based description is a widely used way to depict them by abstracting links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.9\linewidth]{diagrams/framework.jpg}
-	\caption{
-		Framework for understanding linkages between SES structures and outcomes.
-		\textbf{a.} The general framework for analyzing social-ecological systems (SESs) (adapted from Ostrom \cite{ostrom2009}).
+% \begin{figure}[!bh]
+% 	\centering
+% 	\includegraphics[width=0.9\linewidth]{diagrams/framework.jpg}
+% 	\caption{
+% 		Framework for understanding linkages between SES structures and outcomes.
+% 		\textbf{a.} The general framework for analyzing social-ecological systems (SESs) (adapted from Ostrom \cite{ostrom2009}).
 Institutions embedded in SESs may reshape structures by changing the interactions between core subsystems, resulting in different outcomes.
-        Three typical types of abstracted SES structures are shown as \textbf{b.}, \textbf{c.} and \textbf{d.} (adapted from Bodin, 2017)\cite{bodin2017b}.
+%         Three typical types of abstracted SES structures are shown as \textbf{b.}, \textbf{c.} and \textbf{d.} (adapted from Bodin, 2017)\cite{bodin2017b}.
 Red circles indicate social actors, and green ones indicate ecological components.
@@
 According to empirical evidence, the gray dashed lines show aligned SES structures that are more likely to achieve a desirable outcome.
-        }
-    \label{framework}
-\end{figure}
+%         }
+%     \label{framework}
+% \end{figure}
 
@@
     \centering
-    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/world_institutions}
+    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/world_institutions.pdf}
 	\caption{

### 2022-11-03 docs/papers/01_manuscript/01_introduction.tex
tem

@@
 Some institutional advances have had desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d}, and collaborative water governance systems in Europe \cite{green2013}).
-However, imposing institutional changes on a large, complex river basin may create or destroy hundreds of connections between social agents and ecological units, where matched social-ecological structures are not ubiquitous.
-Two particular weaknesses in existing knowledge of institutional matches include understanding (Figure~\ref{fig:framework}~\textbf{b}): (i) the causal links between SES structures and outcomes; (ii) details of the underlying processes, and especially the coordination of the incentives of different participants, that result from an institutional lack of matches.
-These weaknesses limit understanding of institutional design and hinder approaches toward institutional matches for improving the sustainability of river basin systems.
+However, imposing institutional changes on a large, complex river basin may create or destroy connections between social agents and ecological units, where matched social-ecological structures are not ubiquitous.
+Two particular weaknesses in existing knowledge of institutional matches include understanding (Figure~\ref{fig:framework}~\textbf{b}): (i) the causal links between SES structures and outcomes; (ii) details of the underlying processes, and especially the incentives of different participants, that result from an institutional lack of matches.
+These weaknesses limit understanding of institutional design and hinder approaches toward institutional matches.
 
@@
 
-To better understand how water governance institutions match their social-ecological context, we take the Yellow River Basin (YRB), China, as an example (see \textit{\nameref{sec:yrb}}) to dive into causal links between SES structures and outcomes.
+To better understand how water governance institutions match/mismatch their social-ecological context, we take the Yellow River Basin (YRB), China, as an example (see \textit{\nameref{sec:yrb}}) to dive into causal links between SES structures and outcomes.
 Specifically, we focused on two institutional shifts in water allocation of the YRB: the 1987 Water Allocation Scheme (87-WAS), and the 1998 Unified Basinal Regulation (98-UBR), which reframed SES structures significantly.
@@
 
-We explored causal linkages between SES structures and sustainability-related outcomes by quasi-natural experiments (institutional shifts imposed by central government) in the YRB.
+We explored causal linkages between SES structures and outcomes by quasi-natural experiments (institutional shifts imposed by central government) in the YRB.
 Firstly, we used data on changes in official documents following two institutional shifts to describe comparable changes in the SES structures associated with the YRB from 1979 to 2008, by abstracting them into SES structures motifs (or building blocks, see \textit{\nameref{sec:structures}}).
@@
 This approach allowed us to create a counterfactual against which to explore the mechanisms linking SESs structure and outcomes for a deeper understanding of the potential role of institutions in water governance worldwide.
-Finally, we further developed an approach for marginal benefits analysis, to interpret the underlying processes of the match and mismatched institutions based on SESs structures (\textit{\nameref{sec:model}}).
+Finally, we further developed an approach for marginal benefits analysis, to interpret the underlying processes of mismatched institutions based on SESs structures (\textit{\nameref{sec:model}}).

### 2022-11-03 docs/papers/01_manuscript/02_structures.tex
fix(introduction,-structures,-results,-discussions): fix problems by Wen and Wu
tem

@@
 As it was the first time the responsibility of the YRCC involved water use, this introduced new links between the YRCC and the ecological nodes (Figure~\ref{fig:structure}~C).
-However, the controversial 87-WAS did not resolve water depletion.
+However, the controversial 87-WAS did not resolve streamflow depletion.
 In 1998, another strategy (98-UBR) was developed to strengthen the responsibilities of the YRCC for integrated managing water use.
@@
 Thus, the YRCC has been linked to the provinces since 1998 (Figure~\ref{fig:structure}~C).
+% 因此，两次制度转换重塑了，形成了三个由社会行动者和生态节点连接而成的一般性结构
+As result, the two institutional shifts reshaped SES structures, leading to three general structures linked by social actors and ecological nodes (Figure~\ref{fig:structure}~C).

### 2022-11-03 docs/papers/01_manuscript/04_discussion.tex
tem

@@
 However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{\nameref{secS2}}~Table~\ref{tab:variables}).
-On the contrary, the 98-UBR reduced water competition, so many studies attributed the restoration mainly to the successful introduction of this institution \cite{chen2021,huangang2002,an2007}.
+On the contrary, the 98-UBR reduced surface water competition, so many studies attributed the streamflow restoration mainly to the successful introduction of this institution \cite{chen2021,huangang2002,an2007}.
 
@@
 \label{discussion-3}
-On the other hand, social-ecological matches can also be supported by structure effects.
-After 98-UBR, the YRCC could adjust water use quotas to match river conditions for the whole YRB.
+On the other hand, social-ecological matches can also be supported by structural effects.
+After 98-UBR, the YRCC could adjust surface water use quotas according to climate conditions for the whole YRB.
 When the YRCC began to coordinate among stakeholders, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)
 \cite{krieger1955, ostrom1990}.
-During this period, proportional decreased water use of provinces indicated a positive result of the regulation (see \nameref{result-3}).
-The 98-UBR thus led to expected institutional outcomes at a basin scale, indicating that successful governance of SES emerged by indirectly (or vertically) creating links between different stakeholders.
-Our model demonstrates that in this case, a unified scale-matched institution was indispensable for sustainable water use.
+During this period, proportional decreased water use of provinces indicated expected river regulating results (see \nameref{result-3}).
+Meanwhile, our model also demonstrates that in this case, the unified scale-matched institution was indispensable for decreased water use.
+However, since the 98-UBR only regulated surface water use, many clues suggested the institution shift may cause broader influences (cascading effects) because of unsatisfied water demands. 
+For example, literature estimated increased groundwater withdrawals after 98-UBR in many intensive irrigation regions, despite little eligible data on groundwater use and stakeholders being accessible \cite{sun2022b}.
+Since the 21st century, similar water quota policies started to be implemented nationally and altering the relationship between social actors and resource units. 
+As both of the institutional shifts examined here induced unexpected changes or cascading effects within SESs, better governance is calling for more institutional analysis of coupled human and natural systems in the future.
 
-The structural building blocks we depicted here (Figure~\ref{fig:structure}) have also been reported in other SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}.
+The structural building blocks (or motifs) we depicted here (Figure~\ref{fig:structure}) have also been reported in other SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}.
 Before 98-UBR, SES structure (i.e., fragment ecological units linked to separate social actors) was more likely to be mismatched because isolated actors generally struggle to maintain interconnected ecosystems holistically \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
-Institutional re-alignments since 98-UBR improved the authority of the YRCC and helped it match the scale of resource provisioning in the YRB, leading to enhanced social-ecological fit and better outcomes \cite{cumming2020a,wang2019d}.
+Institutional re-alignments since 98-UBR improved the authority of the YRCC and helped it match the scale of resource provisioning in the YRB, leading to enhanced social-ecological fit and better outcomes regarding runoff restoration \cite{cumming2020a,wang2019d}.
 The comparison demonstrates again the challenge of finding win-win situations in coupled human-nature systems \cite{hegwood2022}, and the need to more deeply understand the role of social-ecological structures \cite{bergsten2019, sayles2019}.
@@
 The structural building blocks that led to different outcomes are recurring motifs in global SESs, so our proposed mechanism is crucial to governing such coupled systems.
-Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{\nameref{secS1}}) \cite{yu2019}.
+Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{\nameref{secS1}}) \cite{yu2019, niu2022}.
 Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development \cite{wang2019a}.
 Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{\nameref{secS1}}).
-Our analysis suggests that these initiatives can benefit by actively incorporating social-ecological matched building blocks when developing new institutions \cite{bodin2017b}.
-Moreover, our research provides a cautionary tale of how institutions can create perverse incentives \cite{hegwood2022}, while insights from the YRB can provide guidelines for SESs management worldwide \cite{muneepeerakul2017, leslie2015}.
+Our analysis suggests that these initiatives can lead to distortions because of mismatched building blocks when developing new institutions \cite{bodin2017b}.
+Therefore, our research provides a cautionary tale of how institutions can change perverse incentives \cite{hegwood2022}, while insights from the YRB can provide guidelines for SESs management worldwide \cite{muneepeerakul2017, leslie2015}.

### 2022-11-03 core/analysis.py

@@ -9,10 +9,11 @@ from core.unit_base import ItemBase, UnitBase
 
 
 class AnalystItem(ItemBase):
-    def __init__(self, data_item, method_item, **kwargs):
+    def __init__(self, data_item, method_item, parameters=None, **kwargs):
         super().__init__(**kwargs)
         self._data = data_item
         self._method = method_item
+        self._parameters = parameters
         self._is_checked = False
         self._results = None
 
@@ -27,6 +28,10 @@ class AnalystItem(ItemBase):
     @property
     def method(self):
         return self._method
+
+    @property
+    def parameters(self):
+        return self._parameters
 
     @property
     def is_checked(self):
@@ -47,10 +52,12 @@ class AnalystItem(ItemBase):
         self.is_checked = self.obj(*argv, **kwargs)
         return self.is_checked
 
-    def do_analysis(self, save_mode=False, *argv, **kwargs):
+    def do_analysis(self, safe_mode=False, *argv, **kwargs):
         # TODO: Safe mode -- check it before do analysis.
+        if self.parameters:
+            kwargs.update(self.parameters)
         results = self.method.function(
-            self.data.obj, self.method.parameters, *argv, **kwargs
+            self.data, *argv, **kwargs
         )
         self._results = results
         return results
@@ -62,12 +69,13 @@ class Analyst(UnitBase):
         super().__init__(unit_name=name, **kwargs)
 
     def add_analyst_item(
-        self, name, description, data_item, method_item, check=None
+        self, name, description, data_item, method_item, parameters=None, check=None
     ):
         item = AnalystItem(
             obj=check,
             data_item=data_item,
             method_item=method_item,
+            parameters=parameters,
             name=name,
             description=description,
         )
@@ -75,6 +83,15 @@ class Analyst(UnitBase):
         item.update_metadata("method", method_item.name)
         self.add_item(item)
         return item
+
+    def do_all(self):
+        do_this_time = []
+        for item in self.items:
+            analysis = self.get_item(item)
+            if analysis.results is None:
+                analysis.do_analysis()
+                do_this_time.append(analysis.name)
+        return do_this_time
 
     def report(self, show=True, show_notes=False, max_width=30):
         table = super().report(show=False, show_notes=show_notes)

### 2022-11-04 docs/papers/01_manuscript/04_discussion.tex
docs(manuscript.tex,-introduction,-discussion): change title, emphasize methology

@@
 Since the 21st century, similar water quota policies started to be implemented nationally and altering the relationship between social actors and resource units.
-As both of the institutional shifts examined here induced unexpected changes or cascading effects within SESs, better governance is calling for more institutional analysis of coupled human and natural systems in the future.
+As both institutional shifts examined here induced unexpected changes or cascading effects within SESs, better governance calls for more institutional analysis of coupled human and natural systems in the future.
 

### 2022-11-04 docs/papers/01_manuscript/manuscript.tex
tem
docs(manuscript.tex,-introduction,-discussion): change title, emphasize methology

@@
 \documentclass[default, sn-standardnature]{sn-jnl}
-\usepackage{amsmath,graphicx,array}
-\usepackage{dcolumn,soul}%
+\usepackage{amsmath, graphicx, array}
+\usepackage{dcolumn, soul}%
 \let\openbox\relax
@@
 
-\bibliographystyle{../nsr}
+% \bibliographystyle{../nsr}
 
-\title{Approaching social-ecological matches of river basin systems for sustainability}  %! Notice Input
+\title{Approaching causal linkages between SES structures and outcomes of the Yellow River Basin, China}  %! Notice Input
 
@@
      To fill these knowledge gaps, we select the Yellow River Basin (YRB) in China as a typical case study to quantitatively measure the effects of SES structures changing because it is one of the most anthropogenically altered large river basins.
-     Under different water allocation institutions, its streamflow was first overdrawn, then dried up, and finally has been successfully restored.
+     Under different surface water allocation institutions, its streamflow was first overdrawn, then dried up, and finally has been successfully restored.
      We focused on two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), which re-framed different SES structures.
      We conduct counterfactual identification on the effect of these institutional shifts, our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
-     Furthermore, these heterogeneous effects of water use responses to SES structures aligned with our further theoretical marginal benefits analysis, supporting the hypothesis that SES structural changes played a vital role in sustainable water use.
+     Furthermore, these heterogeneous effects of water use responses to SES structures aligned with our further theoretical marginal benefits analysis, supporting the hypothesis that SES structural changes played a vital role.
      This quasi-natural experiment on the YRB offers profound insights into the links between SESs structures and outcomes, suggesting that fragmented ecological units linked to separated social actors should be avoided for sustainability.
@@
 
-\keywords{Yellow River, water use, water governance, social-ecological system, institutional fit}  %! Notice input
+\keywords{water use, water governance, social-ecological system, institutional fit, Yellow River}  %! Notice input
 \maketitle

### 2022-11-06 docs/papers/01_manuscript/manuscript.tex
docs: E&S submission
BREAKING CHANGE:

@@
 \abstract{
-     Increasing competition for water is leading to depletion of freshwater globally and calls for efficient institutions in water governance.
-     Alignments of social-ecological system (SES) structures are a crucial approach to institutional matches, but an understanding of its causal links and underlying processes are still weaknesses.
+     Increasing competition for water is leading to the depletion of freshwater globally and calls for efficient institutions in water governance.
+Alignments of social-ecological system (SES) structures are a crucial approach to institutional matches, but an understanding of its causal links and underlying processes still needs to be improved.
 To fill these knowledge gaps, we select the Yellow River Basin (YRB) in China as a typical case study to quantitatively measure the effects of SES structures changing because it is one of the most anthropogenically altered large river basins.
-     Under different surface water allocation institutions, its streamflow was first overdrawn, then dried up, and finally has been successfully restored.
+Under different surface water allocation institutions, its streamflow was first overdrawn, dried up, and successfully restored.
 We focused on two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), which re-framed different SES structures.
-     We conduct counterfactual identification on the effect of these institutional shifts, our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
+We conduct counterfactual identification on the effect of these institutional shifts; our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
 Furthermore, these heterogeneous effects of water use responses to SES structures aligned with our further theoretical marginal benefits analysis, supporting the hypothesis that SES structural changes played a vital role.
@@
 \input{06_methods.tex}
+
+% Authors Contribution
+% SW and BF designed this research. SS performed the study and analysed data. SS and HW wrote the paper. XW, GC, and HW revised and polished the manuscript and gave significant advice.
+
+% Acknowledgments
+% This research has been supported by the National Natural Science Foundation of China (grant no. 42041007) and the Fundamental Research Funds for the Central Universities
 

### 2022-11-11 docs/papers/02_appendix/01_institution_context.tex
docs(appendix.tex): splitting into four sections

@@
 % 基于上述分析，我们抽象出了两次制度转变之后的SES结构变化如正文的图1C所示。
-Based on the above documents, we abstracted the structural changes of SES (see \textit{Appendix S2}) after the two institutional changes, as shown in Figure~\ref{fig:structure}~C.
+Based on the above documents, we abstracted the structural changes of SES after the two institutional changes, as shown in the main text \textbf{Figure 2C}.
 

### 2023-04-16 docs/papers/01_manuscript/manuscript.tex
refactor(project): :lipstick: 更改为JH的LaTeX排版

@@
-\documentclass[default, sn-standardnature]{sn-jnl}
+% chktex-file 46
+\documentclass[preprint, 12pt]{elsarticle}
+
+%% Use the option review to obtain double line spacing
+%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
+
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+%% \documentclass[final,1p,times]{elsarticle}
+%% \documentclass[final,1p,times,twocolumn]{elsarticle}
+%% \documentclass[final,3p,times]{elsarticle}
+%% \documentclass[final,3p,times,twocolumn]{elsarticle}
+%% \documentclass[final,5p,times]{elsarticle}
+%% \documentclass[final,5p,times,twocolumn]{elsarticle}
+
+%% For including figures, graphicx.sty has been loaded in
+%% elsarticle.cls. If you prefer to use the old commands
+%% please give \usepackage{epsfig}
+
+%% The amssymb package provides various useful mathematical symbols
+\usepackage{amssymb}
 \usepackage{amsmath, graphicx, array}
@@
 \usepackage{hyperref}
-\newgeometry{left=2cm, right=2cm}
+
+% 行距
 \linespread{1.5}
 % \usepackage[nofiglist,notablist]{endfloat}
-\makeatletter
-\def\uns{\ifmmode\,\else$\,$\fi}%
+% \def\uns{\ifmmode\,\else$\,$\fi}%
 \newtheorem{defn}{Definition}
@@
 \usepackage{multirow}
-\usepackage{lineno}
-\setenumerate{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=0pt}
-\setitemize{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=5pt}
-\setdescription{itemsep=0pt,partopsep=0pt,parsep=\parskip,topsep=5pt}
-
+% \usepackage{lineno}
 \usepackage{booktabs}
@@
 %%
-\makeatother
 
@@
 
-\markboth{One, Two, and Three}{One, Two, and Three}
+% \markboth{One, Two, and Three}{One, Two, and Three}
 \graphicspath{{../../../figs/}}
+\journal{Jounral of Hydrology}
 
 \begin{document}
-\normalsize
+\begin{frontmatter}
+% \normalsize
 % \dhead{RESEARCH ARTICLE}
@@
 % \bibliographystyle{../nsr}
+% 社会水文学专刊地址
+% https://www.sciencedirect.com/journal/journal-of-hydrology/about/call-for-papers#grounded-sociohydrology
+\title{Achieving Effective River Basin Governance: Examining Institutional Shifts and Incentives in the Yellow River Basin's Social-Ecological Systems}
 
-\title{Approaching causal linkages between SES structures and outcomes of the Yellow River Basin, China}  %! Notice Input
+\author[inst1]{Shuang Song}
+\author[inst2]{Huiyu Wen}
+\author[inst1]{*Shuai Wang}
+\author[inst1]{Xutong Wu}
 
-\author{Shuang Song$^{1}$}
-\author{Huiyu Wen$^2$}
-\author{*Shuai Wang$^{1}$}
-\author{Xutong Wu$^{1}$}
+\author[inst3]{Graeme S. Cumming}
+\author[inst1]{Bojie Fu}
 
-\author{Graeme S. Cumming$^{3}$}
-\author{Bojie Fu$^{1}$}
-
-\affil{$^1$State Key Laboratory of Earth Surface Processes and Resource Ecology,
+\affiliation[inst1]{
+     State Key Laboratory of Earth Surface Processes and Resource Ecology,
      Faculty of Geographical Science,
@@
 
-% \affil{$^2$Institute of Land Surface System and Sustainability,
+% \affil{stitute of Land Surface System and Sustainability,
 %      Faculty of Geographical Science,
@@
 
-\affil{$^2$School of Finance,
+\affiliation[inst2]{School of Finance,
      Renmin University of China,
@@
 
-\affil{$^3$ARC Centre of Excellence for Coral Reef Studies,
+\affiliation[inst3]{
+     ARC Centre of Excellence for Coral Reef Studies,
      James Cook University,
@@
 
-% \affil{$^4$The research for this article was financed by the National Natural Science Foundation of China (CN) (Grant Nos.
+% \affil{e research for this article was financed by the National Natural Science Foundation of China (CN) (Grant Nos.
 NSFC 42041007).
@@
 %\authornote{Shuang Song and Huiyu Wen equally contributed to this work.}
-\renewcommand\linenumberfont{\normalfont\bfseries\small}
-\linenumbers
-\abstract{
+% \renewcommand\linenumberfont{\normalfont\bfseries\small}
+% \linenumbers
+\begin{abstract}
 Increasing competition for water is leading to the depletion of freshwater globally and calls for efficient institutions in water governance.
@@
 This quasi-natural experiment on the YRB offers profound insights into the links between SESs structures and outcomes, suggesting that fragmented ecological units linked to separated social actors should be avoided for sustainability.
-     }  %! Notice input
+\end{abstract}
 
-\keywords{water use, water governance, social-ecological system, institutional fit, Yellow River}  %! Notice input
+%%Graphical abstract
+\begin{graphicalabstract}
+     \includegraphics{outputs/main_results2.pdf}
+\end{graphicalabstract}
+
+%%Research highlights
+\begin{highlights}
+     \item Research highlight 1
+     \item Research highlight 2
+\end{highlights}
+
+\begin{keyword}
+     water use \sep water governance \sep social-ecological system \sep institutional fit \sep Yellow River
+\end{keyword}
+
+\end{frontmatter}
+
 \maketitle
@@
 \bibliography{../mybib}
-\bibliographystyle{sn-standardnature}
+\bibliographystyle{elsarticle-num}
+
 \label{bib}
@@
 \newpage
-\appendix
-\label{appendix}
-\renewcommand{\figurename}{Supplementary Figure}
-\renewcommand{\appendixname}{Appendix~\Alph{section}}
-\setcounter{section}{0}
+\appendix\label{appendix}
 
-\section{Appendix~A: Contexts of institutional shifts}\label{secS1}
+\section{Contexts of institutional shifts}\label{secS1}
 \renewcommand{\thefigure}{A\arabic{figure}}
@@
 
-\section{Appendix~B: Robustness of DSC method}\label{secS2}
+\section{Robustness of DSC method}\label{secS2}
 \renewcommand{\thefigure}{B\arabic{figure}}
@@
 
-\section{Appendix~C: Optimization model for water use}\label{secS4}
+\section{Optimization model for water use}\label{secS4}
 \renewcommand{\thefigure}{C\arabic{figure}}
@@
 
-\section{Appendix~D: Model extensions}\label{secS5}
+\section{Model extensions}\label{secS5}
 \renewcommand{\thefigure}{D\arabic{figure}}
@@
 
-%% Put the bibliography here, most people will use BiBTeX in
-%% which case the environment below should be replaced with
-%% the \bibliography{} command.
-% \newpage
-% \newpage
-% \bibliography{../mybib}
-% \bibliographystyle{sn-standardnature}
-% \label{bib}
 \end{document}

### 2023-04-22 docs/papers/01_manuscript/01_introduction.tex
refactor(introduction): :recycle: 重构到JH写法

--- 2022-07-04 docs/papers/01_manuscript/01_introduction.tex
@@
 % 水竞争的重要性
-Widespread freshwater scarcity and overuse challenge the sustainability of large river basins, resulting in systematic risks to economies, societies, and ecosystems globally \cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
-In the context of future climate change, the gap between supply and demand for water resources in large river basins is expected to become increasingly more prominent \cite{florke2018, yoon2021}.
-Those river basin systems successfully supporting sustainable water resource use are structurally well-aligned with water provisioning and social-ecological demands, without inefficient competition or overuses \cite{wang2019d}.
-However, balancing the water demands of ecosystems and development in heavily human-dominated river basins is a challenge because human activities and water are intertwined in their structures as complex social-ecological systems (SES) \cite{huggins2022,konar2019}.
+Widespread freshwater scarcity and overuse challenge the sustainability of large river basins, resulting in systematic risks to economies, societies, and ecosystems globally~\cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
+In the context of climate change, the mismatches between supply and demand for water resources are expected to become increasingly more prominent~\cite{florke2018, yoon2021}.
+Hence, large river basins are increasingly seeking for effective water governance solutions by coordinating stakeholders, providing water resources, and ensuring the sustainable allocation of shared water resources~\cite{wang2019d}.
+As results, hydrological processes are tightly intertwined with societies, shown as an social-ecological system (SES) at a basin scale where complex socio-hydrological feedback merges SES structures.
 
-For governing river basin systems, their SES structures can be reshaped by institutions, such as policies, laws, and norms \cite{young2008,cumming2020b}.
-Representing all relative governance practices, institutions include interplays between social actors, ecological units, or between social and ecological system elements
-\cite{lien2020, bodin2017b}.
-Understanding how these complex interplays are crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems \cite{kluger2020}.
-Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, supporting (but not guaranteeing) the sustainability of SES \cite{epstein2015, wang2019d}.
-Some institutional advances have had desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d}, and collaborative water governance systems in Europe \cite{green2013}).
-However, imposing institutional changes on a large, complex river basin may create or destroy hundreds of connections between social agents and ecological units, where matched social-ecological structures are not ubiquitous.
-Two particular weaknesses in existing knowledge of institutional matches include understanding: (i) the causal links between SES structures and outcomes; (ii) details of the underlying processes, and especially the coordination of the incentives of different participants, that result from an institutional lack of matches.
-These weaknesses limit understanding of institutional design and hinder approaches toward institutional matches for improving the sustainability of river basin systems.
+Governing river basin systems involves reshaping their SES structures through institutions such as policies, laws, and norms~\cite{young2008,cumming2020b}.
+Institutions encompass the interplay between social actors, ecological units, and their interactions~\cite{lien2020, bodin2017b}.
+Effective institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, contributing to the sustainability of SES~\cite{epstein2015, wang2019d} (Figure~\ref{fig:framework}~\textbf{a}).
+While some institutional advances have led to desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China~\cite{wang2019d}, and collaborative water governance systems in Europe~\cite{green2013}),
+imposing institutional shifts may create or destroy connections and effectiveness are not ubiquitous~\cite{loos2022}. 
+For example, Colorado River once had sever water shortage and costly water competition until confirming water rights with following water institutional system~\cite{hadjimichael2020}.
+% TODO check this expression.
+科罗拉多河的这个例子还要举得更好一些
+Therefore, examining when and how an institution leads to effective water governance can bring crucial insights for sustainability in global river basins.
 
-To better understand how water governance institutions match their social-ecological context, we take the Yellow River Basin (YRB), China, as an example \textit{\nameref{sec:yrb}} to dive into causal links between SES structures and outcomes.
-Specifically, we focused on two institutional shifts in water allocation of the YRB: the 1987 Water Allocation Scheme (87-WAS), and the 1998 Unified Basinal Regulation (98-UBR), which reframed SES structures significantly.
-The YRB provides an informative case for two main reasons:
-(1) The top-down institutional shifts induced sharp changes in SES structures, enabling us to estimate their net effects quantitatively.
-(2) Since few large river basins have experienced such radical institutional shifts more than once, this case study provides comparable natural experiments for understanding the impacts of structural changes in SESs on natural resources.
+% match & mismatch
+Recent studies explored various effects of institutions on river basins governance, while quantitative assessments with controlled comparisons are remaining scarce~\cite{bouckaert2022, vallury2022, loch2020, kirchhoff2016}.
+Additionally, understanding how different SESs structures influence institutional effectiveness is challenging due to the complexity and dynamics of these systems~\cite{bodin2017b}.
+Thus, the knowledge gap lies in the limited understanding of aligning institutions with SES structures to promote sustainable river basins governance.
+It hinders designing effective institutions that address the diverse challenges and opportunities in various social-ecological contexts, ultimately impacting long-term sustainability.
 
-We explored causal linkages between SES structures and sustainability-related outcomes by quasi-natural experiments (institutional shifts imposed by central government) in the YRB.
-Firstly, we used data on changes in official documents following two institutional shifts to describe comparable changes in the SES structures associated with the YRB from 1979 to 2008, by abstracting them into SES structures motifs (or building blocks, see \textit{\nameref{sec:structures}}).
-We then used a method called `Differenced Synthetic Control (DSC)' \cite{arkhangelsky2021}, which considers economic growth and natural background, to estimate theoretical water use scenarios without institutional shifts (\textit{\nameref{sec:DSC}} and \textit{\nameref{secS2}}).
-This approach allowed us to create a counterfactual against which to explore the mechanisms linking SESs structure and outcomes for a deeper understanding of the potential role of institutions in water governance worldwide.
-Finally, we further developed an approach for marginal benefits analysis, to interpret the underlying processes of the match and mismatched institutions based on SESs structures (\textit{\nameref{sec:model}}).
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=0.5\linewidth]{diagrams/framework.png}
+	\caption{
+		Framework for understanding institutional shifts and SES structures.
+\textbf{a.} In the general framework for analyzing social-ecological systems (SESs), (Adapted from Ostrom, 2008~\cite{ostrom2009}).
+Institutional shifts can change interactions within the SES and reframe the structures.
+\textbf{b.} We aim to investigate how institutional shifts impacts effective governance by structuring SES.}\label{fig:framework}
+\end{figure}
+
+To gain a deeper understanding of how institutions align or misalign with their social-ecological context, we use the Yellow River Basin (YRB), China, as a case study to examine the consequences and incentives of two significant institutional shifts in water allocation: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulation (98-UBR).
+These shifts considerably transformed the SES structures within the basin, and offered valuable insights for two main reasons:
+(1) the top-down institutional shifts led to substantial changes in SES structures, allowing us to quantitatively estimate their net effects; and (2) the basin's unique experience of multiple radical institutional shifts provides a rare opportunity to compare natural experiments and understand the impacts of SES structural changes on water governance.
+
+Our investigation of the consequences of YRB's institutional shifts involves analyzing quasi-natural experiments with causal inference approach.
+First, we use data from official documents following the two institutional shifts to describe the YRB's SES structures' comparable changes between 1979 and 2008.
+Next, we employ the ``Differenced Synthetic Control (DSC)'' method~\cite{arkhangelsky2021}, which accounts for economic growth and natural background, to estimate theoretical water use scenarios in the absence of institutional shifts.
+This approach enables us to establish a counterfactual basis for exploring the consequences and incentives related to SES structures, thereby enhancing our understanding of institutions' potential role in global water governance.
+% Finally, we develop a marginal benefits analysis approach to interpret the underlying processes of misaligned institutions based on SES structures.

### 2023-04-22 docs/papers/01_manuscript/manuscript.tex
refactor(introduction): :recycle: 重构到JH写法

@@
 % https://www.sciencedirect.com/journal/journal-of-hydrology/about/call-for-papers#grounded-sociohydrology
-\title{Achieving Effective River Basin Governance: Examining Institutional Shifts and Incentives in the Yellow River Basin's Social-Ecological Systems}
+\title{Achieving Effective River Basin Governance through Institutional Shifts: Examining the Yellow River Basin's Social-Ecological Systems in China}
 
@@
 %%Graphical abstract
-\begin{graphicalabstract}
-     \includegraphics{outputs/main_results2.pdf}
-\end{graphicalabstract}
+% \begin{graphicalabstract}
+%      \includegraphics{outputs/main_results2.pdf}
+% \end{graphicalabstract}
 
@@
 \bibliography{../mybib}
-\bibliographystyle{elsarticle-num}
-
-\label{bib}
+\bibliographystyle{elsarticle-num}\label{bib}
 

### 2023-04-22 docs/papers/01_manuscript/03_results.tex
refactor(project): :recycle: JH表述修改

--- 2022-07-03 docs/papers/01_manuscript/03_results.tex
@@
 
+% \subsection{}
+
 %\subsection{INSTITUTIONAL SHIFTS IMPACT ON WATER USE OF THE YRB}
-\subsection{Institutional shifts impact on water use}
-\label{result-2}
+\subsection{Institutional shifts impact on water use}\label{result-2}
 % 结果一：展示制度转变带来的用水量变化
@@
 		\textbf{C.} Drought intensity in the YRB and drying up events of the Yellow River. The size of the grey bubbles denotes the length of drying upstream.
-	}
-	\label{fig:main_results}
+	}\label{fig:main_results}
 \end{figure*}
 
-\label{result-1-p2}
 Our estimation of theoretical water use suggests that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without an institutional shift (Figure~\ref{fig:main_results}A).
@@
 %\subsection{REGIONAL DIFFERENCES IN RESPONSES TO INSTITUTIONAL SHIFTS}
-\subsection{Heterogeneous effects and interpretation}
-\label{result-3}
+\subsection{Heterogeneous effects and interpretation}\label{result-3}
 
@@
 		The triangles mark the water quotas assigned under the institution, converted to ratios by dividing by their sum.
-	}
-	\label{fig:regulating}
+	}\label{fig:regulating}
 \end{figure*}
@@
 Furthermore, the regulated water use of provinces was unrelated (partial correlation coefficient is $0.33$, $p>0.1$) to their proportional water use from the Yellow River.
-
-% \subsection{Structure-based marginal benefit analysis}
-% \label{result-4}
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.6\linewidth]{outputs/economic_model.pdf}
-	\caption{
-		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
-	\label{fig:model}
-\end{figure}
-
-For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (analogy to Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
-Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.
-Until water-use decisions are consolidated into unified management, each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive to use water, leading to higher water use.
-Furthermore, water users with higher capability are more stimulated by institutional shifts and away from the theoretically optimal water use under a unified allocation.
+To interpret this pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases theoretically where the water using structure between 1987 and 1998 is the largest-consuming case (\ref{secS4}).

### 2023-04-22 docs/papers/01_manuscript/04_discussion.tex
refactor(project): :recycle: JH表述修改

@@
 % \subsection{}
-\label{discussion-1}
 % discussion-1:
@@
 % 制度对社会生态系统的结果产生影响在世界范围内都很普遍，
-The influences of institutions on the outcomes of social-ecological systems (SESs) were widely reported worldwide, but few attempts to quantify their net effects \cite{cumming2020a}.
-Our results show that while 98-UBR decreased water use in the YRB, 87-WAS increased it by $8.57\%$.
-The results challenged previous analyses (i.e., suggesting that 87-WAS ''had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present \cite{abadie2015,hill2021}.
+The influences of institutional shifts on governing effects of social-ecological systems (SESs) were widely reported worldwide, but few attempts to quantify their net effects~\cite{cumming2020a}.
+Our results show that while 98-UBR decreased water use in the YRB, 87-WAS increased it by $5.75\%$.
+The results challenged previous analyses (i.e., suggesting that 87-WAS ``had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present~\cite{abadie2015,hill2021}.
 However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{\nameref{secS2}}~Table~\ref{tab:variables}).
-On the contrary, the 98-UBR reduced surface water competition, so many studies attributed the streamflow restoration mainly to the successful introduction of this institution \cite{chen2021,huangang2002,an2007}.
+On the contrary, the 98-UBR reduced surface water competition, so many studies attributed the streamflow restoration mainly to the successful introduction of this institution~\cite{chen2021,huangang2002,an2007}.
 
-\label{discussion-2}
 % discussion-2: 87的增加
 % 结果与制度的目的完全相反的87-WAS与许多其它的SES失败治理案例类似，表明不匹配的社会生态结构可能促进了对公共资源的掠夺式开采。
-The above comparison suggests that the 87-WAS, whose results were contrary to the purpose of the institution, is similar to many other SES governance failures, supporting that mismatched socio-ecological structures can deterioration of common resources \cite{kellenberg2009,cai2016,barnes2019}.
-The increased water use after 87-WAS aligns with concerns about frequently scrambling for water in some provinces during this period \cite{mao2000, bouckaert2022}.
-Although reasons for the non-ideal effect of 87-WAS had been widely discussed \cite{huangang2002} (such as enforcement, feasibility, and equity), however, structural change has received limited attention.
+The above comparison suggests that the 87-WAS, whose results were contrary to the purpose of the institution, is similar to many other SES governance failures, supporting that mismatched socio-ecological structures can deterioration of common resources~\cite{kellenberg2009,cai2016,barnes2019}.
+The increased water use after 87-WAS aligns with concerns about frequently scrambling for water in some provinces during this period~\cite{mao2000, bouckaert2022}.
+Although reasons for the non-ideal effect of 87-WAS had been widely discussed~\cite{huangang2002} (such as enforcement, feasibility, and equity), however, structural change has received limited attention.
 Our results show that the correlation between current water use and changed (increased or decreased) water use was significant after 87-WAS (Figure~\ref{fig:regulating}).
@@
 The validity of our theoretical analysis is supported by two facts:
-(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
-The bargaining was also a process for matching water shares to economic volume because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution) \cite{zuo2020}.
+(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987)~\cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
+The bargaining was also a process for matching water shares to economic volume because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution)~\cite{zuo2020}.
 (2) Provinces with higher current water use might have greater bargaining power in water use allocation because of information asymmetry between decision-makers and stakeholders.
-Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligned with their appeals to the higher central government for larger shares \cite{wang2019a, wang2019d}.
+Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligned with their appeals to the higher central government for larger shares~\cite{wang2019a, wang2019d}.
 
-\label{discussion-3}
 On the other hand, social-ecological matches can also be supported by structural effects.
@@
 However, since the 98-UBR only regulated surface water use, many clues suggested the institution shift may cause broader influences (cascading effects) because of unsatisfied water demands.
-For example, literature estimated increased groundwater withdrawals after 98-UBR in many intensive irrigation regions, despite little eligible data on groundwater use and stakeholders being accessible \cite{sun2022b}.
+For example, literature estimated increased groundwater withdrawals after 98-UBR in many intensive irrigation regions, despite little eligible data on groundwater use and stakeholders being accessible~\cite{sun2022b}.
 Since the 21st century, similar water quota policies started to be implemented nationally and altering the relationship between social actors and resource units.
@@
 
-The structural building blocks (or motifs) we depicted here (Figure~\ref{fig:structure}) have also been reported in other SESs worldwide \cite{kluger2020,guerrero2015,bodin2012}.
-Before 98-UBR, SES structure (i.e., fragment ecological units linked to separate social actors) was more likely to be mismatched because isolated actors generally struggle to maintain interconnected ecosystems holistically \cite{sayles2017,sayles2019,cai2016,bergsten2019}.
-Institutional re-alignments since 98-UBR improved the authority of the YRCC and helped it match the scale of resource provisioning in the YRB, leading to enhanced social-ecological fit and better outcomes regarding runoff restoration \cite{cumming2020a,wang2019d}.
-The comparison demonstrates again the challenge of finding win-win situations in coupled human-nature systems \cite{hegwood2022}, and the need to more deeply understand the role of social-ecological structures \cite{bergsten2019, sayles2019}.
+The structural pattern we depicted here (Figure~\ref{fig:structure}) have also been reported in other SESs worldwide~\cite{kluger2020,guerrero2015,bodin2012}.
+Before 98-UBR, SES structure (i.e., fragment ecological units linked to separate social actors) was more likely to be mismatched because isolated actors generally struggle to maintain interconnected ecosystems holistically~\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
+Institutional re-alignments since 98-UBR improved the authority of the YRCC and helped it match the scale of resource provisioning in the YRB, leading to enhanced effectiveness regarding runoff restoration~\cite{cumming2020a,wang2019d}.
+The comparison demonstrates again the challenge of finding win-win situations in coupled human-nature systems~\cite{hegwood2022}, and the need to more deeply understand the role of social-ecological structures~\cite{bergsten2019, sayles2019}.
 % Therefore, the YRB cases can provide further explanation of the matching and mismatching of the previous SES building blocks, linking SES structure and outcomes by plausible reasons of causality and underlying processes.
@@
 and second, when applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
-Our quasi-experiment approach nonetheless provides evidence supporting the view that there was a change in water use trajectory following the YRB's unique institutional shifts and offers insights into water governance (and particularly the importance of having a scale-matched, basin-wide authority for water allocation solutions \cite{bodin2017b, ostrom2009, reyers2018})
+Our quasi-experiment approach nonetheless provides evidence supporting the view that there was a change in water use trajectory following the YRB's unique institutional shifts and offers insights into water governance (and particularly the importance of having a scale-matched, basin-wide authority for water allocation solutions~\cite{bodin2017b, ostrom2009, reyers2018})
 Moreover, the ultimate success of the 98-UBR institutional shift theoretically and practically proved the importance of social-ecological fit.
@@
 For example, water rights transfers may be another way to build horizontal links between stakeholders that also have the potential to result in better water governance.
-In addition, policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to a changing SES context \cite{reyers2018}.
+In addition, policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to a changing SES context~\cite{reyers2018}.
 
-The structural building blocks that led to different outcomes are recurring motifs in global SESs, so our proposed mechanism is crucial to governing such coupled systems.
-Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{\nameref{secS1}}) \cite{yu2019, niu2022}.
-Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development \cite{wang2019a}.
-Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{\nameref{secS1}}).
-Our analysis suggests that these initiatives can lead to distortions because of mismatched building blocks when developing new institutions \cite{bodin2017b}.
-Therefore, our research provides a cautionary tale of how institutions can change perverse incentives \cite{hegwood2022}, while insights from the YRB can provide guidelines for SESs management worldwide \cite{muneepeerakul2017, leslie2015}.
+The structural pattern that led to different effectiveness widespread in global SESs, so our proposed mechanism is crucial to governing such coupled systems.
+Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{\nameref{secS1}})~\cite{yu2019, niu2022}.
+Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development~\cite{wang2019a}.
+Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation scheme (see \textit{\nameref{secS1}}).
+Our analysis suggests that these initiatives can lead to distortions because of mismatched structure when shifting to another institution~\cite{bodin2017b}.
+Therefore, our research provides a cautionary tale of how institutions can change perverse incentives~\cite{hegwood2022}, while insights from the YRB can provide guidelines for SESs management worldwide~\cite{muneepeerakul2017, leslie2015}.

### 2023-04-22 docs/papers/01_manuscript/05_conclusion.tex
refactor(project): :recycle: JH表述修改

--- 2022-06-11 docs/papers/01_manuscript/05_conclusion.tex
@@
 %! Date = 2022/3/10
-
-Intense water use in one of the most anthropogenically altered large river basins, the Yellow River Basin (YRB), once led to drying up.
-Alterations of institutions eventually successfully restored water governance practices on a decadal time scale.
-We propose that the institutional shifts in the YRB (87-WAS and 98-UBR) framed two different SES structures and depicted them as widespread building blocks.
-We quantitatively estimate the net effects of these changes in the YRB and analyze the reasons from SES structural perspectives.
-Our results show that the historical records, the responses from stakeholders to structural changes, and the theoretical analysis from the marginal benefits model all support that fragmented ecological units linked to separate social actors frames a mismatched SES structure.
-Through the quasi-natural experiments of the YRB, we demonstrate that social-ecological fits can lead to successful SESs management worldwide with better sustainability outcomes.
+Our study emphasizes the importance of social-ecological system (SES) structures in effective water resource management.
+By examining the Yellow River Basin (YRB) in China as a case study, we found that the 1987 Water Allocation Scheme (87-WAS) led to an 5.75\% increase in observed water use, while the 1998 Unified Basinal Regulation (98-UBR) effectively reduced total water use.
+Our findings highlight the critical role of well-designed SES structures in driving water resource management outcomes.
+To achieve sustainability, we recommend avoiding fragmented ecological units linked to separated social actors and underscore the need for a deeper understanding of the underlying processes and relationships in SES structures for effective water governance.

### 2023-04-22 docs/papers/01_manuscript/06_methods.tex
docs: E&S submission
BREAKING CHANGE:
refactor(project): :recycle: JH表述修改

--- 2022-07-01 docs/papers/01_manuscript/06_methods.tex
@@
 % 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程
-We first abstract the SES structures of water used in the YRB from 1979 to 2008, where two institutional shifts split the period into three pieces.
+the YRB from 1979 to 2008, where two institutional shifts split the period into three pieces.
 To process the data, we use the Principal Components Analysis (PCA) method to reduce the dimensionality of variables affecting the total water use.
-We then estimated the net effects of two institutional shifts on total water use, changing trends, and differences of the YRB's provinces, by Differenced Synthetic Control (DSC) method \cite{arkhangelsky2021}.
+We then estimated the net effects of two institutional shifts on total water use, changing trends, and differences of the YRB's provinces, by Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021}.
 Finally, for theoretical discussion, we developed a marginal benefit analysis based on identified SES structures to provide the observed pattern of water use changes with a theoretical interpretation.
@@
 In the 1980s, intense water use, accounting for about $80\%$ of Yellow River surface runoff, combined with other forms of human interference (e.g., soil conservation and water conservancy projects), caused consecutive drying events and substantial ecological, economic, and social crises (e.g., wetland shrinkage, agriculture reduction, and a scramble for water).
-In response, Chinese authorities implemented several ambitious water management practices in the YRB to relieve water stress, such as reservoir regulation, the South-to-north Water Diversion Project (WDP), the 1987 Water Allocation Scheme (87-WAS), and the 1998 Unified Basinal Regulation (98-UBR) \cite{long2020, wang2019d}.
+In response, Chinese authorities implemented several ambitious water management practices in the YRB to relieve water stress, such as reservoir regulation, the South-to-north Water Diversion Project (WDP), the 1987 Water Allocation Scheme (87-WAS), and the 1998 Unified Basinal Regulation (98-UBR)~\cite{long2020, wang2019d}.
 Those efforts led to ecological restoration of wetlands and the estuarine delta. Drying up has been avoided for over 20 years, which is widely considered a substantial management achievement.
-Instead of relying on engineering to increase water supply, institutional strategies like the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, authority at a basin-level) focused mainly on limiting demand for water \cite{bouckaert2022, speed2013}.
+Instead of relying on engineering to increase water supply, institutional strategies like the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, authority at a basin-level) focused mainly on limiting demand for water~\cite{bouckaert2022, speed2013}.
 While researchers have carefully evaluated and quantified the effects of engineering solutions on water supply\cite{long2020}, there have been few attempts to assess institutional contributions to successful water governance in the YRB.
@@
 % 制度结构关系抽象
-We apply the network \cite{bodin2017b} approach to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit (the YRCC) into general building blocks (or motifs) (see Figure~\ref{framework}), from the official documents.
-Empirical studies have suggested that such widespread building blocks in SES are the key to the functioning of structures.
-The network-based approach is to abstract connections between entities into links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.
+A network-based description is a widely used way to depict them by abstracting links and nodes~\cite{bodin2017a,kluger2020,guerrero2015}.
+We apply the network approach~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit (the YRCC) into structural pattern from the official documents.
+Empirical studies have suggested that such widespread pattern in SES are the key to the functioning of structures.
+The network-based approach is to abstract connections between entities into links and nodes~\cite{bodin2017a,kluger2020,guerrero2015}.
 In this study, we examined the official documents of the two institutional shifts of concern (87-WAS and 98-UBR, see \textit{Appendix \nameref{secS1}} for details).
@@
 We choose datasets and variables to compare on actual and estimated water use of the YRB.
-The actual water uses are accessible in China’s provincial annual water consumption dataset from the National Water Resources Utilization Survey, whose details are accessible from Zhou (2020) \cite{zhou2020}.
+The actual water uses are accessible in China’s provincial annual water consumption dataset from the National Water Resources Utilization Survey, whose details are accessible from Zhou (2020)~\cite{zhou2020}.
 To estimate the water use of the YRB by assuming there were no effects from institutional shifts, we focused on variables from five categories (environmental, economic, domestic, and technological) water use factors.
@@
 Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ principal components \textit{Appendix~\nameref{secS2}}.
-Bayan had proved that combining PCA and DSC can raise the robustness of causal inference \cite{bayani2021}.
+Bayan had proved that combining PCA and DSC can raise the robustness of causal inference~\cite{bayani2021}.
 We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different.
@@
 Using the Differenced Synthetic Control (DSC) method, we estimate water use without the effect of the institutional shift.
-The DSC method is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit \cite{abadie2010, abadie2015, hill2021}.
+The DSC method is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit~\cite{abadie2010, abadie2015, hill2021}.
 
@@
 In practice, all treated units (i.e., provinces) were affected by institutional shifts in 1987 and 1998, each taken as the ``shifted'' time $t_0$ within two individually analyzed periods $T$: 1979-1998; 1987-2008.
-We include each province in the YRB ($n=8$, see \textit{\nameref{sec:dataset}}) as the treated unit separately, as multiple treated units approach had been widely applied \cite{abadie2021}.
+We include each province in the YRB ($n=8$, see \textit{\nameref{sec:dataset}}) as the treated unit separately, as multiple treated units approach had been widely applied~\cite{abadie2021}.
 Then, we consider the $J+1$ units observed in time periods $T = {1,2 \cdots , T}$ with the remaining $J=20$ units are untreated provinces from outside.
@@
 Similarly, let $\mathbf{Z}_{0}$ be a ($k * T_0$) matrix containing the outcome for each control unit in the pre-treatment period, and $k$ is the number of variables in the datasets.
-The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with double robustness properties \cite{billmeier2013, smith2015}.
+The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with double robustness properties~\cite{billmeier2013, smith2015}.
 
-\subsection{Marginal benefits analysis}\label{sec:model}
-To infer the mechanisms underlying the results, we developed an marginal benefits analysis based on marginal revenue to analyze how the institutional shift could have led to differences in water use.
+% \subsection{Marginal benefits analysis}\label{sec:model}
+% To infer the mechanisms underlying the results, we developed an marginal benefits analysis based on marginal revenue to analyze how the institutional shift could have led to differences in water use.
 
-\begin{ass}
-    (Water-dependent production) Because of irreplaceably, water is assumed to be the only production function input with two production efficiency types.
-\end{ass}
+% \begin{ass}
+%     (Water-dependent production) Because of irreplaceably, water is assumed to be the only production function input with two production efficiency types.
+% \end{ass}
 
-\begin{ass}
-    (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin, the water use cost is equally assigned to each province.
-\end{ass}
+% \begin{ass}
+%     (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin, the water use cost is equally assigned to each province.
+% \end{ass}
 
-\begin{ass}
-    (Multi-period settings) There are multiple settings periods with a constant discount factor for the expectation of future water use.
-\end{ass}
+% \begin{ass}
+%     (Multi-period settings) There are multiple settings periods with a constant discount factor for the expectation of future water use.
+% \end{ass}
 
-Under the above-simplified assumptions, we demonstrate three cases -corresponding to the abstracted SES structures (Figure~\ref{fig:structure}), inference of how SES structure alters the expected marginal benefits and costs of provinces making decisions.
-As one of the possible interpretations for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.
+% Under the above-simplified assumptions, we demonstrate three cases -corresponding to the abstracted SES structures (Figure~\ref{fig:structure}~C), inference of how SES structure alters the expected marginal benefits and costs of provinces making decisions.
+% As one of the possible interpretations for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.

### 2023-04-22 docs/papers/01_manuscript/manuscript.tex
refactor(project): :recycle: JH表述修改

@@
 \usepackage{hyperref}
+\usepackage{geometry}
 
+\geometry{a4paper,left=2.0cm,right=2.0cm,top=2.5cm,bottom=2.5cm}
 % 行距
@@
 \begin{abstract}
-Increasing competition for water is leading to the depletion of freshwater globally and calls for efficient institutions in water governance.
-Alignments of social-ecological system (SES) structures are a crucial approach to institutional matches, but an understanding of its causal links and underlying processes still needs to be improved.
-To fill these knowledge gaps, we select the Yellow River Basin (YRB) in China as a typical case study to quantitatively measure the effects of SES structures changing because it is one of the most anthropogenically altered large river basins.
-Under different surface water allocation institutions, its streamflow was first overdrawn, dried up, and successfully restored.
-We focused on two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), which re-framed different SES structures.
-We conduct counterfactual identification on the effect of these institutional shifts; our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
-Furthermore, these heterogeneous effects of water use responses to SES structures aligned with our further theoretical marginal benefits analysis, supporting the hypothesis that SES structural changes played a vital role.
-This quasi-natural experiment on the YRB offers profound insights into the links between SESs structures and outcomes, suggesting that fragmented ecological units linked to separated social actors should be avoided for sustainability.
+     Global freshwater depletion necessitates efficient water governance that accounts for social-ecological system (SES) structures.
+To improve our understanding of the relationships between SES structures and water governance, we investigated the Yellow River Basin (YRB) in China, which has experienced significant anthropogenic alterations.
+We analyzed two institutional shifts, the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulation (98-UBR), that re-framed SES structures.
+Our counterfactual identification showed that water use in the YRB increased by 5.75\% more than expected following the 87-WAS, while the 98-UBR reduced total water use.
+These heterogeneous effects align with our marginal benefits analysis, confirming the importance of well-designed SES structures in water governance.
+Our quasi-natural experiment on the YRB highlights the need to avoid fragmented ecological units and separated social actors for sustainable water governance, while also emphasizing the significance of understanding the underlying processes and relationships in SES structures.
 \end{abstract}
@@
 %%Research highlights
-\begin{highlights}
-     \item Research highlight 1
-     \item Research highlight 2
-\end{highlights}
+% \begin{highlights}
+%      \item Research highlight 1
+%      \item Research highlight 2
+% \end{highlights}
 
 \begin{keyword}
-     water use \sep water governance \sep social-ecological system \sep institutional fit \sep Yellow River
+     water use~\sep~water governance~\sep~social-ecological system~\sep~institutions~\sep~Yellow River
 \end{keyword}
@@
 
-\maketitle
-
 \section{INTRODUCTION}\label{sec:introduction}
 \input{01_introduction.tex}
+
+\section{MATERIALS AND METHODS}\label{sec:methods}
+\input{06_methods.tex}
 
@@
 \input{05_conclusion.tex}
-
-\section{MATERIALS AND METHODS}\label{sec:methods}
-\input{06_methods.tex}
 

### 2023-04-22 docs/papers/01_manuscript/out/compiled_v-2.0.2.tex
fix(figures-update): fig updates
refactor(project): :recycle: JH表述修改

@@
      We focused on two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), which re-framed different SES structures.
-     We conduct counterfactual identification on the effect of these institutional shifts, our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected, while 98-UBR ultimately decreased total water use.
+     We conduct counterfactual identification on the effect of these institutional shifts, our results suggested that during the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $5.75\%$ more than expected, while 98-UBR ultimately decreased total water use.
      Furthermore, these heterogeneous effects of water use responses to SES structures aligned with our further theoretical marginal benefits analysis, supporting the hypothesis that SES structural changes played a vital role in sustainable water use.
@@
 The influences of institutions on the outcomes of social-ecological systems (SESs) were widely reported worldwide, but few attempts to quantify their net effects \cite{cumming2020a}.
-Our results show that while 98-UBR decreased water use in the YRB, 87-WAS increased it by $8.57\%$.
+Our results show that while 98-UBR decreased water use in the YRB, 87-WAS increased it by $5.75\%$.
 The results challenged previous analyses (i.e., suggesting that 87-WAS ''had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present \cite{abadie2015,hill2021}.

### 2023-04-22 docs/papers/02_appendix/04_theoretical_model.tex
refactor(project): :recycle: JH表述修改

@@
 %! Date = 2022/3/19
+
+% \subsection{Structure-based marginal benefit analysis}
+% \label{result-4}
+
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.6\linewidth]{outputs/economic_model.pdf}
+	\caption{
+		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}~C) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}\label{fig:model}
+\end{figure}
+
+For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (case 1 to case 3, corresponding to different SES structures in Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
+
+Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.
+As a benchmark, case 1 analogy to a decentralized stakeholders situation and lead to medium-level water use.
+In case 2, each stakeholder expects that current water use helps bargain for a favorable water quota in the face of institutional shift (see \textit{\nameref{secS4}}), which can intensify the incentive to use water, leading to higher water use.
+Furthermore, the water users with higher capability are more stimulated by the institutional shift and away from the theoretically optimal water use under a unified allocation.
+After water-use decisions are consolidated into unified management (case 3), marginal benefits analysis suggests the lowest water use among the cases.
 

### 2023-04-22 docs/papers/03_diff_versions/mature_version.tex
refactor(project): :recycle: JH表述修改

--- 2023-04-22 docs/papers/01_manuscript/out/compiled_v-2.0.2.tex
@@
 
-For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (analogy to Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
+For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (case 1 to case 3, corresponding to different SES structures in Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
 Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.
-Until water-use decisions are consolidated into unified management, each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive to use water, leading to higher water use.
-Furthermore, water users with higher capability are more stimulated by institutional shifts and away from the theoretically optimal water use under a unified allocation.
+As a benchmark, case 1 analogy to a decentralized stakeholders situation and lead to medium-level water use.
+In case 2, each stakeholder expects that current water use helps bargain for a favorable water quota in the face of institutional shift (see \textit{\nameref{secS4}}), which can intensify the incentive to use water, leading to higher water use.
+Furthermore, the water users with higher capability are more stimulated by the institutional shift and away from the theoretically optimal water use under a unified allocation.
+After water-use decisions are consolidated into unified management (case 3), marginal benefits analysis suggests the lowest water use among the cases.
 

### 2023-05-04 docs/papers/01_manuscript/01_introduction.tex
refactor(introduction): :recycle: 重构引言
不再出现因果，使用JH风格写作

@@
 Hence, large river basins are increasingly seeking for effective water governance solutions by coordinating stakeholders, providing water resources, and ensuring the sustainable allocation of shared water resources~\cite{wang2019d}.
-As results, hydrological processes are tightly intertwined with societies, shown as an social-ecological system (SES) at a basin scale where complex socio-hydrological feedback merges SES structures.
+As results, hydrological processes are tightly intertwined with societies, shown as an social-ecological system (SES) at a basin scale with complex socio-hydrological feedback.
 
+Institutions encompass the interplay between social actors, ecological units, and their interactions~\cite{lien2020, bodin2017b, wang2022g}.
+These interactions consist a type of structure of SES, where effective institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different interactions, contributing to the sustainability~\cite{epstein2015, wang2019d} (Figure~\ref{fig:framework}~\textbf{a}).
 Governing river basin systems involves reshaping their SES structures through institutions such as policies, laws, and norms~\cite{young2008,cumming2020b}.
-Institutions encompass the interplay between social actors, ecological units, and their interactions~\cite{lien2020, bodin2017b}.
-Effective institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, contributing to the sustainability of SES~\cite{epstein2015, wang2019d} (Figure~\ref{fig:framework}~\textbf{a}).
-While some institutional advances have led to desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China~\cite{wang2019d}, and collaborative water governance systems in Europe~\cite{green2013}),
+While some institutional advances have led to effective water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China~\cite{wang2019d}, and collaborative water governance systems in Europe~\cite{green2013}),
 imposing institutional shifts may create or destroy connections and effectiveness are not ubiquitous~\cite{loos2022}.
-For example, Colorado River once had sever water shortage and costly water competition until confirming water rights with following water institutional system~\cite{hadjimichael2020}.
-% TODO check this expression.
-科罗拉多河的这个例子还要举得更好一些
-Therefore, examining when and how an institution leads to effective water governance can bring crucial insights for sustainability in global river basins.
+For example, Colorado River once had sever water shortage and institutions led to various shortage magnitude for different stakeholders even under the same water demands level~\cite{hadjimichael2020}.
+Therefore, examining when and how an institution leads to effective water governance can bring crucial insights for sustainability of river basins.
 
 % match & mismatch
-Recent studies explored various effects of institutions on river basins governance, while quantitative assessments with controlled comparisons are remaining scarce~\cite{bouckaert2022, vallury2022, loch2020, kirchhoff2016}.
-Additionally, understanding how different SESs structures influence institutional effectiveness is challenging due to the complexity and dynamics of these systems~\cite{bodin2017b}.
-Thus, the knowledge gap lies in the limited understanding of aligning institutions with SES structures to promote sustainable river basins governance.
-It hinders designing effective institutions that address the diverse challenges and opportunities in various social-ecological contexts, ultimately impacting long-term sustainability.
+Recent studies explored diverse effects of institutions on river basins governance~\cite{bouckaert2022, vallury2022, loch2020, kirchhoff2016}, while the current analysis is more about interpreting outcomes after the institutional changes, but it cannot compares how the scenarios would be without these institutional changes.
+Additionally, understanding how the different SESs structures influence institutional effectiveness is challenging due to the complexity and dynamics of socio-hydrological systems~\cite{bodin2017b}.
+Thus, knowledge gaps lies in the limited understanding of effective alignments between institutional shifts and SES structures, hinders designing effective policies to promote sustainable river basins governance.
+To fill these knowledge gaps, we study the Yellow river basin, one of the most anthropogenically altered river basins, to quantitatively measure the effects of changing SES structure.
+The Yellow River Basin (YRB) is the fifth-largest river basin worldwide, supporting $35.63\%$ of China's irrigation and $30\%$ of its population while containing only $2.66\%$ of its water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today).
 
@@
 
-To gain a deeper understanding of how institutions align or misalign with their social-ecological context, we use the Yellow River Basin (YRB), China, as a case study to examine the consequences and incentives of two significant institutional shifts in water allocation: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulation (98-UBR).
-These shifts considerably transformed the SES structures within the basin, and offered valuable insights for two main reasons:
-(1) the top-down institutional shifts led to substantial changes in SES structures, allowing us to quantitatively estimate their net effects; and (2) the basin's unique experience of multiple radical institutional shifts provides a rare opportunity to compare natural experiments and understand the impacts of SES structural changes on water governance.
+% 黄河的介绍
+In the $1980s$, intense water use, accounting for about $80\%$ of Yellow River surface water, caused consecutive drying-up crises of runoff, leading to wetland shrinkage, agriculture reduction, and scrambles for water.
+In response, Chinese authorities implemented several ambitious water management policies in the YRB to relieve water stress, such as the South-to-north Water Diversion Project and the Water Allocation Institutions~\cite{long2020, wang2019d}.
+In this study, we specifically examined two significant institutional shifts in water allocation of the YRB\: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulating (98-UBR).
+Instead of engineering and increasing water supply, 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, authority at a basin-level) focused mainly on limiting demands for water~\cite{bouckaert2022, speed2013}.
+These institutional shifts can offer valuable insights because of two main reasons:
+(1) the top-down institutional shifts suddenly led to transforms of SES structures, allowing us to quantitatively estimate their net effects; and (2) the two institutional shifts within the same river basin provide rarely comparable quasi-natural experiments.
 
-Our investigation of the consequences of YRB's institutional shifts involves analyzing quasi-natural experiments with causal inference approach.
-First, we use data from official documents following the two institutional shifts to describe the YRB's SES structures' comparable changes between 1979 and 2008.
-Next, we employ the ``Differenced Synthetic Control (DSC)'' method~\cite{arkhangelsky2021}, which accounts for economic growth and natural background, to estimate theoretical water use scenarios in the absence of institutional shifts.
-This approach enables us to establish a counterfactual basis for exploring the consequences and incentives related to SES structures, thereby enhancing our understanding of institutions' potential role in global water governance.
-% Finally, we develop a marginal benefits analysis approach to interpret the underlying processes of misaligned institutions based on SES structures.
+Here, we portrayed changes of SES structures throughout the YRB's institutional shifts (the 87-WAS and the 98-UBR) and quantitatively investigated their consequences, then including an discussion of the effectiveness of institutional shifts.
+Specifically, we first use the descriptions of official documents following the two institutional shifts to abstract the interactions between main stakeholders and their river segment units for interpreting SES structures changes between 1979 and 2008.
+Next, and perhaps most importantly, we use the ``Differenced Synthetic Control (DSC)'' method~\cite{arkhangelsky2021}, which accounts for economic growth and natural background, to estimate theoretical water use volumes under the absence of institutional shifts scenarios.
+Finally in discussion, we linked the effectiveness of institutional shifts to the portrayed structures, by comparing YRB's case to previous SES structure studies and developing a marginal benefits analysis.

### 2023-05-05 docs/papers/01_manuscript/01_introduction.tex
refactor(introduction): :recycle: 介绍黄河情况

@@
 Thus, knowledge gaps lies in the limited understanding of effective alignments between institutional shifts and SES structures, hinders designing effective policies to promote sustainable river basins governance.
-To fill these knowledge gaps, we study the Yellow river basin, one of the most anthropogenically altered river basins, to quantitatively measure the effects of changing SES structure.
-The Yellow River Basin (YRB) is the fifth-largest river basin worldwide, supporting $35.63\%$ of China's irrigation and $30\%$ of its population while containing only $2.66\%$ of its water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today).
+To fill these knowledge gaps, we study the Yellow river basin, the fifth-largest river worldwide and one of the most anthropogenically altered river basins, to quantitatively measure the effects of changing SES structure.
 
@@
 % 黄河的介绍
-In the $1980s$, intense water use, accounting for about $80\%$ of Yellow River surface water, caused consecutive drying-up crises of runoff, leading to wetland shrinkage, agriculture reduction, and scrambles for water.
-In response, Chinese authorities implemented several ambitious water management policies in the YRB to relieve water stress, such as the South-to-north Water Diversion Project and the Water Allocation Institutions~\cite{long2020, wang2019d}.
+In the $1980s$, intense water use, accounting for about $80\%$ of Yellow River surface water, caused consecutive drying-up crises of runoff, leading to wetland shrinkage, agriculture reduction, and scrambles for water~\cite{wohlfart2016}.
+Then, Chinese authorities implemented several ambitious water management policies in the YRB to relieve water stress, such as the South-to-north Water Diversion Project and the Water Allocation Institutions~\cite{long2020, wang2019d}.
 In this study, we specifically examined two significant institutional shifts in water allocation of the YRB\: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulating (98-UBR).

### 2023-05-05 docs/papers/01_manuscript/06_methods.tex
refactor(introduction): :recycle: 介绍黄河情况

@@
 % 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程
-the YRB from 1979 to 2008, where two institutional shifts split the period into three pieces.
 To process the data, we use the Principal Components Analysis (PCA) method to reduce the dimensionality of variables affecting the total water use.
@@
 
-\subsection{Study area}\label{sec:yrb}
-
-% 黄河的介绍
-The Yellow River Basin (YRB), the fifth-largest river basin worldwide, is known for its vital role in the socio-economic development of China.
-It supports $35.63\%$ of China's irrigation and $30\%$ of its population while containing only $2.66\%$ of its water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today).
-In the 1980s, intense water use, accounting for about $80\%$ of Yellow River surface runoff, combined with other forms of human interference (e.g., soil conservation and water conservancy projects), caused consecutive drying events and substantial ecological, economic, and social crises (e.g., wetland shrinkage, agriculture reduction, and a scramble for water).
-In response, Chinese authorities implemented several ambitious water management practices in the YRB to relieve water stress, such as reservoir regulation, the South-to-north Water Diversion Project (WDP), the 1987 Water Allocation Scheme (87-WAS), and the 1998 Unified Basinal Regulation (98-UBR)~\cite{long2020, wang2019d}.
-Those efforts led to ecological restoration of wetlands and the estuarine delta. Drying up has been avoided for over 20 years, which is widely considered a substantial management achievement.
-Instead of relying on engineering to increase water supply, institutional strategies like the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, authority at a basin-level) focused mainly on limiting demand for water~\cite{bouckaert2022, speed2013}.
-While researchers have carefully evaluated and quantified the effects of engineering solutions on water supply\cite{long2020}, there have been few attempts to assess institutional contributions to successful water governance in the YRB.
-
 \subsection{Portraying structures}\label{sec:structures}
 % 制度结构关系抽象
-A network-based description is a widely used way to depict them by abstracting links and nodes~\cite{bodin2017a,kluger2020,guerrero2015}.
+A point-axis network type structure of SES is a widely used way to depict them by abstracting links and nodes~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
 We apply the network approach~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit (the YRCC) into structural pattern from the official documents.
@@
 The 1987-WAS requires the YRCC to monitor each river's reach, while the 1998-UBR requires direct interactions (through water use licenses) between the YRCC and the provinces.
-Therefore, we linked the YRCC unit to each ecological unit after 87-WAS and each province unit after the 98-UBR.
-We tested whether focusing on SES structures rather than institutional details could reasonably explain the differences caused by institutional shifts in the YRB.
+Therefore, we linked the YRCC unit to each ecological unit after 87-WAS and each province unit after the 98-UBR.\\
+We tested whether focusing on SES structures rather than institutional details could reasonably explain the differences caused by institutional shifts in the YRB.\\
 
@@
 The DSC method is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit~\cite{abadie2010, abadie2015, hill2021}.
+This approach enables us to establish a counterfactual basis for exploring the consequences and incentives related to policy changes.
 
 This method aims to evaluate the effects of policy change that are not random across units but focuses on some of them (i.e., institutional shifts in the YRB here).
-By re-weighting units to match the pre-trend for the treated and control units, the DSC method imputes post-treatment control outcomes for the treated unit(s) by constructing a synthetic version of the treated unit(s) equal to a convex combination of control units.
+By re-weighting units to match the pre-trend for the treated and control units, the DSC method imputes post-treatment control outcomes for the treated units by constructing a synthetic version of the treated units equal to a convex combination of control units.
 Therefore, the synthetic and actual version difference can be estimated as a net effect for a treated unit.
 
-In practice, all treated units (i.e., provinces) were affected by institutional shifts in 1987 and 1998, each taken as the ``shifted'' time $t_0$ within two individually analyzed periods $T$: 1979-1998; 1987-2008.
+In practice, all treated units (i.e., provinces) were affected by institutional shifts in 1987 and 1998, each taken as the ``shifted'' time $t_0$ within two individually analyzed periods $T$: from 1979 to 1998; from 1987 to 2008.
 We include each province in the YRB ($n=8$, see \textit{\nameref{sec:dataset}}) as the treated unit separately, as multiple treated units approach had been widely applied~\cite{abadie2021}.
 Then, we consider the $J+1$ units observed in time periods $T = {1,2 \cdots , T}$ with the remaining $J=20$ units are untreated provinces from outside.
-We define $T_0$ to represent the number of pre-treatment periods ($1,\cdots,t_0$) and $T_1$ the number post-treatment periods ($t_0,\cdots,T$), such that $T = T_0+ T_1$.
+We define $T_0$ to represent the number of pre-treatment periods ($1,\ldots,t_0$) and $T_1$ the number post-treatment periods ($t_0, \ldots, T$), such that $T = T_0+ T_1$.
 The treated unit is exposed to the institutional shift in every post-treatment period $T_0$, unaffected by the institutional shift in all preceding periods $T_1$.
-Then, any weighted average of the control units is a synthetic control and can be represented by a ($J * 1$) vector of weights $\mathbf{W} = (w_{1},...,w_{J})$, with $w_j \in (0, 1)$.
-Among them, by introduce a ($k * k$) diagonal, semidefinite matrix $\mathbf{V}$ that signifies the relative importance of each covariate, the DSC method procedure for finding the optimal synthetic control ($W$) is expressed as follows:
+Then, any weighted average of the control units is a synthetic control and can be represented by a ($J * 1$) vector of weights $\mathbf{W} = (w_{1}, \ldots ,w_{J})$, with $w_j \in (0, 1)$.
+Among them, by introduce a ($k * k$) diagonal, matrix $\mathbf{V}$ that signifies the relative importance of each covariant, the DSC method procedure for finding the optimal synthetic control ($W$) is expressed as follows:
 
@@
 The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with double robustness properties~\cite{billmeier2013, smith2015}.
+
+\subsection{Robustness analysis}\label{sec:robustness}
+
+There are two main methods to test the robustness of DSC.
+First of all, the reconstruction effect on inferred variables (water consumption in this chapter) before and after treatment (the intervention of watershed water division policy in this chapter) can be compared.
+If there is a small gap between the model predicted value reconstructed before treatment and the actual observed value, and a large gap between the predicted value and observed value reconstructed after treatment, it indicates that the effect of policy intervention is very obvious.
+In the study of this chapter, in order to judge whether the intervention effect is significant, the paired sample $T$ test is used to calculate statistics, and the model prediction and actual observation data in the early and late period of institutional intervention are respectively tested for the two institutional interventions of "August 7" water separation scheme in $1987$ and unified watershed scheduling in $1998$.
+If $p$ value after policy intervention is less than the threshold value (the confidence level of 95\% is adopted in this chapter, that is, the threshold value is $0.05$), the original hypothesis $H_0$ that "there is no significant difference between the two" can be rejected, and it is believed that the institutional intervention has significantly changed the water consumption in this region.
+If the significance level of $T$ test before institutional intervention is greater than the threshold value, it means that the DSC model successfully predicted the change of water consumption in this region over time before institutional intervention, and the fitting effect is good.
+
+Second, placebo trials are another common way to evaluate the effectiveness of synthetic control methods.
+In a placebo trial, a placebo unit selected from the control unit library is substituted for the treated unit, and a synthetic control method is applied to the placebo unit using the same data and parameters as the treated unit.
+If the synthetic control method is effective, there should be a clear difference between the placebo unit and the control unit, since the placebo unit should not be affected by the intervention.
+Placebo tests can be used to assess the effectiveness of the synthetic control method and detect any bias or confounding factors in the analysis.
+In this study, the placebo test step \cite{abadie2010} suggested by Abadie when proposing the synthetic control method was adopted, and the Python library of the differential synthetic control method developed by Dmitry et al.
+was used for the placebo test.
+If the ratio of the root mean square error (see Equation \ref{ch5:eq:RMSE}) to the pre-synthesis period was significantly higher in most provinces (again using the $T$ test to determine the significance of the difference) than the results of other placebo units, it would suggest that the Yellow River basin was more affected than most other provinces during the regime treatment period ($1987$ and $1998$ years).
+
+\begin{equation}
+    \label{ch5:eq:RMSE}
+    \text{RMSE} = \sqrt{\frac{1}{n}\sum_{i=1}^{n}{(y_i-\hat{y}_i)}^2}
+\end{equation}
+
+Where $n$ is the observed number, $y_i$ is the actual value, and $\hat{y}_i$ is the predicted value.
 

### 2023-05-05 docs/papers/01_manuscript/study_area.tex
refactor(introduction): :recycle: 介绍黄河情况

The YRB, cradle of Chinese civilization, locates in north-central China and crosses ten province-level regions whose socio-economic development highly depend on water from the Yellow River~\ref{fig:yrb}.
As semi-arid and arid region, YRB's annual precipitation varies from about $100$ to $1000~mm$ and increases from the northwest to the southeast, while annual pan evaporation varies from about $700$ to $1800~mm$~\cite{wang2022e}.
Taken together, YRB supports $35.63\%$ of China's irrigation and $30\%$ of its population while containing only $2.66\%$ of its water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today).
Hence, over withdrawing water from the Yellow River became an urgent concern since the river began to dry up since early $1970s$.
Among the policies proposed for solving the problem, a series of water resource allocation institutions aimed to limit water use of each region into specific quotas, remarked as of the most important solutions.
However, few attempts quantitatively assessed how the YRB's water allocation scheme contributed to water governance, while other engineering solutions were carefully evaluated~\cite{long2020}.
% 出现报错是因为最后的大写结尾LaTeX无法判断是缩写还是一个句子结束，这里是句子结束所以加 \\
% https://tex.stackexchange.com/questions/55105/when-should-i-use-intersentence-spacing

% Despite the essential reason for these institutions was the mismatch between the spatial and temporal distribution of water resources as well as social and economic water demands, the direct reason for their introduction was the depletion of the Yellow River.

YRB was the first basin in China for which a water resource allocation institutions were created, and institutional shifts can be traced through several regulating documents released by the Chinese government (at the national level)\cite{wang2019a}:
(1) In $1980s$, the provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River~\cite{wang2019, wang2019a}.
(2) In $1987$, implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
(3) In $1998$, implementation of unified regulation. (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
% 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
(4) In $2008$, provinces are asked to draw up new water resources plans for the YRB to further refine water allocations~\cite{wang2019,wang2019a}.
(5) In $2021$, a call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).

Our study period ranges from $1980$ (proposing the water quotas) to $2008$, when it started to completely establish a regulating system with quotas throughout basin, provincial, and district levels.
During the period, two significant institutional shifts can be analyzed by using documents of $1987$ (87-WAS) and $1998$ (98-UBR), which split the study period into three pieces: from 1980 to 1987 (before 87-WAS), from 1988 to 1997 (after 87-WAS and before 98-UBR), and from 1998 to 2007 (after 98-UBR).
% Those efforts led to ecological restoration of wetlands and the estuarine delta. Drying up has been avoided for over $20$ years, which is widely considered a substantial management achievement.

### 2023-05-05 docs/papers/02_appendix/01_institution_context.tex
refactor(project): :lipstick: 更改为JH的LaTeX排版
refactor(introduction): :recycle: 介绍黄河情况

@@
 % 水资源分配方案在全世界范围内都是流域管理的普遍制度。
-Water allocation institutions are widespread in large river basin management programs throughout the world (see \textit{Appendix} Figure~\ref{fig:world}) \cite{speed2013}.
-This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level)\cite{wang2019a}:
-\begin{itemize}
-    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wang2019, wang2019a}.
-    \item \textbf{1987}: Implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
-    \item \textbf{1998}: Implementation of unified regulation.
+% Water allocation institutions are widespread in large river basin management programs throughout the world (see \textit{Appendix} Figure~\ref{fig:world})~\cite{speed2013}.
+% This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level)\cite{wang2019a}:
+% \begin{itemize}
+%     \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wang2019, wang2019a}.
+%     \item \textbf{1987}: Implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
+%     \item \textbf{1998}: Implementation of unified regulation.
 (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
-    % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
-    \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wang2019,wang2019a}.
-    \item \textbf{2021}: A call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
-\end{itemize}
+%     % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
+%     \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wang2019,wang2019a}.
+%     \item \textbf{2021}: A call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
+% \end{itemize}
 
 % 在上述文件中，1982年的文件标志着设计分水制度尝试的开始，2008年标志着该制度走向成熟（完全建立起流域-省-市区的多级水资源分配和统一调度）。
-Since 1982, administrations attemptted to design a quota institution, and the 2008 document marked the maturity of the scheme (complete establishment of basin-level, provincial, and district water quotas).
-Between the period, two significant institutional shits can be analyzed by using the 1987 (87-WAS) and 1998 (98-UBR) documents.
-
-% It is worth noting that, although the essential reason for these institutions was the mismatch between the spatial and temporal distribution of water resources as well as social and economic water demands, the direct reason for their introduction was the depletion of the Yellow River.
 
@@
     \centering
-    \includegraphics[width=12cm]{/Users/songshgeo/Documents/Pycharm/WAInstitution_YRB_2021/figs/diagrams/world_institutions.pdf}
+    \includegraphics[width=12cm]{diagrams/world_institutions.pdf}
 	\caption{

### 2023-05-05 docs/papers/01_manuscript/01_introduction.tex
docs(introduction): :art: GPT润色语言

--- 2023-04-22 docs/papers/01_manuscript/01_introduction.tex
@@
 Widespread freshwater scarcity and overuse challenge the sustainability of large river basins, resulting in systematic risks to economies, societies, and ecosystems globally~\cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
-In the context of climate change, the mismatches between supply and demand for water resources are expected to become increasingly more prominent~\cite{florke2018, yoon2021}.
-Hence, large river basins are increasingly seeking for effective water governance solutions by coordinating stakeholders, providing water resources, and ensuring the sustainable allocation of shared water resources~\cite{wang2019d}.
-As results, hydrological processes are tightly intertwined with societies, shown as an social-ecological system (SES) at a basin scale where complex socio-hydrological feedback merges SES structures.
+Amidst climate change, mismatches between supply and demand for water resources are expected to become increasingly more prominent~\cite{florke2018, yoon2021}.
+Consequently, large river basins are progressively seeking effective water governance solutions by coordinating stakeholders, providing water resources, and ensuring the sustainable allocation of shared water resources~\cite{wang2019d}.
+In this way, hydrological processes are tightly intertwined with societies, forming a social-ecological system (SES) at a basin scale with complex socio-hydrological feedback.
 
-Governing river basin systems involves reshaping their SES structures through institutions such as policies, laws, and norms~\cite{young2008,cumming2020b}.
-Institutions encompass the interplay between social actors, ecological units, and their interactions~\cite{lien2020, bodin2017b}.
-Effective institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, contributing to the sustainability of SES~\cite{epstein2015, wang2019d} (Figure~\ref{fig:framework}~\textbf{a}).
-While some institutional advances have led to desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China~\cite{wang2019d}, and collaborative water governance systems in Europe~\cite{green2013}),
-imposing institutional shifts may create or destroy connections and effectiveness are not ubiquitous~\cite{loos2022}. 
-For example, Colorado River once had sever water shortage and costly water competition until confirming water rights with following water institutional system~\cite{hadjimichael2020}.
-% TODO check this expression.
-科罗拉多河的这个例子还要举得更好一些
-Therefore, examining when and how an institution leads to effective water governance can bring crucial insights for sustainability in global river basins.
+Institutions encompass the interplay between social actors, ecological units, and their interactions~\cite{young2008, lien2020, bodin2017b, wang2022g}.
+These interactions constitute a type of SES structure, where effective institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different interactions, contributing to sustainability~\cite{epstein2015, wang2019d}.
+% (Figure~\ref{fig:framework}~\textbf{a}).
+% Governing river basin systems involves reshaping their SES structures through institutions such as policies, laws, and norms~\cite{,cumming2020b}.
+While some institutional advances have led to effective water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China~\cite{wang2019d}, and collaborative water governance systems in Europe~\cite{green2013}), imposing institutional shifts may create or destroy connections and effectiveness is not ubiquitous~\cite{loos2022}.
+For example, the Colorado River once experienced severe water shortage, and institutions led to various shortage magnitudes for different stakeholders even under the same water demand levels~\cite{hadjimichael2020}.
+Therefore, examining when and how an institution leads to effective water governance can bring crucial insights for the sustainability of river basins.
 
 % match & mismatch
-Recent studies explored various effects of institutions on river basins governance, while quantitative assessments with controlled comparisons are remaining scarce~\cite{bouckaert2022, vallury2022, loch2020, kirchhoff2016}.
-Additionally, understanding how different SESs structures influence institutional effectiveness is challenging due to the complexity and dynamics of these systems~\cite{bodin2017b}.
-Thus, the knowledge gap lies in the limited understanding of aligning institutions with SES structures to promote sustainable river basins governance.
-It hinders designing effective institutions that address the diverse challenges and opportunities in various social-ecological contexts, ultimately impacting long-term sustainability.
+Recent studies have explored diverse effects of institutions on river basin governance~\cite{bouckaert2022, vallury2022, loch2020, kirchhoff2016}, while the current analysis is more about interpreting outcomes after the institutional changes but cannot compare how scenarios would be without these institutional changes.
+Moreover, understanding how different SES structures influence institutional effectiveness is challenging due to the complexity and dynamics of socio-hydrological systems~\cite{bodin2017b}.
+Thus, knowledge gaps lie in the limited understanding of effective alignments between institutional shifts and SES structures, hindering the design of effective policies to promote sustainable river basin governance.
+To fill these knowledge gaps, we study the Yellow River basin, the fifth-largest river worldwide and one of the most anthropogenically altered river basins, to quantitatively measure the effects of changing SES structures.
 
@@
 
-To gain a deeper understanding of how institutions align or misalign with their social-ecological context, we use the Yellow River Basin (YRB), China, as a case study to examine the consequences and incentives of two significant institutional shifts in water allocation: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulation (98-UBR).
-These shifts considerably transformed the SES structures within the basin, and offered valuable insights for two main reasons:
-(1) the top-down institutional shifts led to substantial changes in SES structures, allowing us to quantitatively estimate their net effects; and (2) the basin's unique experience of multiple radical institutional shifts provides a rare opportunity to compare natural experiments and understand the impacts of SES structural changes on water governance.
+% 黄河的介绍
+In the 1980s, intense water use, accounting for about $80\%$ of the Yellow River surface water, caused consecutive drying-up crises of runoff, leading to wetland shrinkage, agriculture reduction, and scrambles for water~\cite{wohlfart2016}.
+To alleviate water stress, Chinese authorities implemented several ambitious water management policies in the Yellow River Basin (YRB), such as the South-to-North Water Diversion Project and the Water Resources Allocation Institutions~\cite{long2020, wang2019d}.
+In this study, we specifically examined two significant institutional shifts in water allocation of the YRB\: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulating (98-UBR).
+the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulating (98-UBR).
+Instead of focusing on engineering and increasing water supply, the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, an authority at a basin level) mainly aimed to limit water demands~\cite{bouckaert2022, speed2013}.
+These institutional shifts can offer valuable insights for two main reasons:
+(1) the top-down institutional shifts suddenly led to transformations of SES structures, allowing us to quantitatively estimate their net effects; and (2) the two institutional shifts within the same river basin provide rare comparable quasi-natural experiments.
 
-Our investigation of the consequences of YRB's institutional shifts involves analyzing quasi-natural experiments with causal inference approach.
-First, we use data from official documents following the two institutional shifts to describe the YRB's SES structures' comparable changes between 1979 and 2008.
-Next, we employ the ``Differenced Synthetic Control (DSC)'' method~\cite{arkhangelsky2021}, which accounts for economic growth and natural background, to estimate theoretical water use scenarios in the absence of institutional shifts.
-This approach enables us to establish a counterfactual basis for exploring the consequences and incentives related to SES structures, thereby enhancing our understanding of institutions' potential role in global water governance.
-% Finally, we develop a marginal benefits analysis approach to interpret the underlying processes of misaligned institutions based on SES structures.
+In this study, we portrayed changes of SES structures throughout the YRB's institutional shifts (the 87-WAS and the 98-UBR) and quantitatively investigated their consequences, followed by a discussion on the effectiveness of institutional shifts.
+Specifically, we first used the descriptions of official documents following the two institutional shifts to abstract the interactions between main stakeholders and their river segment units for interpreting SES structure changes between 1979 and 2008.
+Next, and perhaps most importantly, we employed the ``Differenced Synthetic Control (DSC)'' method~\cite{arkhangelsky2021}, which accounts for economic growth and natural background, to estimate theoretical water use volumes under scenarios absent of institutional shifts.
+Finally, in the discussion, we linked the effectiveness of institutional shifts to the portrayed structures, by comparing the YRB's case to previous SES structure studies and developing a marginal benefits analysis.

### 2023-05-05 docs/papers/01_manuscript/study_area.tex
docs(introduction): :art: GPT润色语言

@@
-The YRB, cradle of Chinese civilization, locates in north-central China and crosses ten province-level regions whose socio-economic development highly depend on water from the Yellow River~\ref{fig:yrb}.
-As semi-arid and arid region, YRB's annual precipitation varies from about $100$ to $1000~mm$ and increases from the northwest to the southeast, while annual pan evaporation varies from about $700$ to $1800~mm$~\cite{wang2022e}.
-Taken together, YRB supports $35.63\%$ of China's irrigation and $30\%$ of its population while containing only $2.66\%$ of its water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today).
-Hence, over withdrawing water from the Yellow River became an urgent concern since the river began to dry up since early $1970s$.
-Among the policies proposed for solving the problem, a series of water resource allocation institutions aimed to limit water use of each region into specific quotas, remarked as of the most important solutions.
-However, few attempts quantitatively assessed how the YRB's water allocation scheme contributed to water governance, while other engineering solutions were carefully evaluated~\cite{long2020}.
+The YRB, cradle of Chinese civilization, is located in north-central China and spans ten province-level regions whose socio-economic development heavily depends on water from the Yellow River.
+As a semi-arid and arid region, the YRB's annual precipitation varies from about 100 to 1,000 mm and increases from the northwest to the southeast, while the annual pan evaporation varies from about 700 to 1,800 mm~\cite{wang2022e}.
+Together, the YRB supports $35.63\%$ of China's irrigation and $30\%$ of its population while containing only $2.66\%$ of its water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today).
+Hence, over-withdrawing water from the Yellow River became an urgent concern when the river began to dry up in the early 1970s.
+Among the policies proposed to address the problem, a series of water resource allocation institutions aimed to limit water use for each region with specific quotas, which were regarded as some of the most important solutions.
+However, few attempts have been made to quantitatively assess how the YRB's water allocation scheme contributed to water governance, while other engineering solutions have been carefully evaluated~\cite{long2020}.
 % 出现报错是因为最后的大写结尾LaTeX无法判断是缩写还是一个句子结束，这里是句子结束所以加 \\
@@
 
-YRB was the first basin in China for which a water resource allocation institutions were created, and institutional shifts can be traced through several regulating documents released by the Chinese government (at the national level)\cite{wang2019a}:
-(1) In $1980s$, the provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River~\cite{wang2019, wang2019a}.
-(2) In $1987$, implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
-(3) In $1998$, implementation of unified regulation. (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
+The YRB was the first basin in China for which water resource allocation institutions were created, and institutional shifts can be traced through several regulating documents released by the Chinese government (at the national level):
+(1) In $1980s$, proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019, wang2019a}.
+(2) In $1987$, the Water Allocation Scheme was implemented (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
+(3) In $1998$, the Unified Basinal Regulation was implemented (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
 % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
-(4) In $2008$, provinces are asked to draw up new water resources plans for the YRB to further refine water allocations~\cite{wang2019,wang2019a}.
-(5) In $2021$, a call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
+(4) In $2008$, provinces were asked to draw up new water resources plans for the YRB to further refine water allocations~\cite{wang2019,wang2019a}.
+(5) In $2021$, there was a call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
 
-Our study period ranges from $1980$ (proposing the water quotas) to $2008$, when it started to completely establish a regulating system with quotas throughout basin, provincial, and district levels.
-During the period, two significant institutional shifts can be analyzed by using documents of $1987$ (87-WAS) and $1998$ (98-UBR), which split the study period into three pieces: from 1980 to 1987 (before 87-WAS), from 1988 to 1997 (after 87-WAS and before 98-UBR), and from 1998 to 2007 (after 98-UBR).
+Our study period therefore ranges from $1980$ (when water quotas were proposed) to $2008$, when a regulating system with quotas was fully established at basin, provincial, and district levels.
+During this period, two significant institutional shifts can be analyzed using documents from $1987$ (87-WAS) and $1998$ (98-UBR), which split the study period into three sections: from $1980$ to $1987$ (before 87-WAS), from $1988$ to $1997$ (after 87-WAS and before 98-UBR), and from $1998$ to $2007$ (after 98-UBR).
 % Those efforts led to ecological restoration of wetlands and the estuarine delta. Drying up has been avoided for over $20$ years, which is widely considered a substantial management achievement.

### 2023-05-05 docs/papers/01_manuscript/06_methods.tex
refactor(method): :recycle: 重构并润色方法部分

@@
 
-% 为了量化制度变迁为黄河流域用水带来的影响，我们按附图1所示的技术路线执行了分析过程
-To process the data, we use the Principal Components Analysis (PCA) method to reduce the dimensionality of variables affecting the total water use.
-We then estimated the net effects of two institutional shifts on total water use, changing trends, and differences of the YRB's provinces, by Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021}.
-Finally, for theoretical discussion, we developed a marginal benefit analysis based on identified SES structures to provide the observed pattern of water use changes with a theoretical interpretation.
+In the methodology section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as point-axis networks during different periods of time.
+Next, we introduce the dataset we used here and employ the Principal Components Analysis (PCA) method to reduce the dimensionality of variables affecting the total water use.
+We then estimate the net effects of the two institutional shifts on total water use, changing trends, and differences in the YRB's provinces using the Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021}.
+Finally, we present the robustness tests approach for the DSC model.
+% Finally, for discussion, we developed a marginal benefit analysis based on identified SES structures to provide the observed pattern of water use changes with a theoretical interpretation.
 
 \subsection{Portraying structures}\label{sec:structures}
-% 制度结构关系抽象
-A point-axis network type structure of SES is a widely used way to depict them by abstracting links and nodes~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
-We apply the network approach~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit (the YRCC) into structural pattern from the official documents.
-Empirical studies have suggested that such widespread pattern in SES are the key to the functioning of structures.
-The network-based approach is to abstract connections between entities into links and nodes~\cite{bodin2017a,kluger2020,guerrero2015}.
-In this study, we examined the official documents of the two institutional shifts of concern (87-WAS and 98-UBR, see \textit{Appendix \nameref{secS1}} for details).
-Besides the ecologically connected river reaches, the agents (provinces and the YRCC) are abstracted as nodes, and their required interactions regarding water use are summarized as links.
-The 1987-WAS requires the YRCC to monitor each river's reach, while the 1998-UBR requires direct interactions (through water use licenses) between the YRCC and the provinces.
-Therefore, we linked the YRCC unit to each ecological unit after 87-WAS and each province unit after the 98-UBR.\\
-We tested whether focusing on SES structures rather than institutional details could reasonably explain the differences caused by institutional shifts in the YRB.\\
+A point-axis network type structure of SES is widely used to depict them by abstracting links and nodes~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
+We apply the network approach~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit at the basin scale (the Yellow River Conservancy Commission) into structural patterns from official documents.
+The network-based approach abstracts connections between entities into links according to their interactions~\cite{bodin2017a,kluger2020,guerrero2015}, so we examined the official documents of the two institutional shifts (87-WAS and 98-UBR) to portray these interactions in this study.
+It is important to note that it can result in very different structures when basin-scale regulatory entity (YRCC) is responsible for river reach regulation, or have direct authority to interact with provincial units.
 
 \subsection{Dataset and preprocessing}\label{sec:dataset}
-We choose datasets and variables to compare on actual and estimated water use of the YRB.
-The actual water uses are accessible in China’s provincial annual water consumption dataset from the National Water Resources Utilization Survey, whose details are accessible from Zhou (2020)~\cite{zhou2020}.
-To estimate the water use of the YRB by assuming there were no effects from institutional shifts, we focused on variables from five categories (environmental, economic, domestic, and technological) water use factors.
+The data of water consumption surveys conducted by the Ministry of Water Resources were taken as the observed values throughout the years.
+Then, to estimate the water use of the YRB by assuming there were no effects from institutional shifts, we focused on variables from five categories (environmental, economic, domestic, and technological) water use factors.
 Their specific items and origins are listed in Table~\ref{tab:variables}.
+Among the total $31$ data-accessible provinces (or regions) assigned quotas in the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin, and Beijing because of their trivial water use from the YRB (see Table~\ref{tab:quota}).
+% We then divided the dataset into a ``target group'' and a ``control group'', treating provinces involved in water quota as the target group $(n=8)$ and other provinces as the control group $(n=20)$ for applying the DSC.\\
 
-Among the total $31$ data-accessible provinces (or regions) assigned quotas in the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin, and Beijing because of their trivial water use from the YRB (see \textit{Appendix}~Table~\ref{tab:quota}).
-We then divided the dataset into a ``target group'' and a ``control group'', treating provinces involved in water quota as the target group $(n=8)$ and other provinces as the control group $(n=20)$ for applying the DSC.
-
-Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ principal components \textit{Appendix~\nameref{secS2}}.
-Bayan had proved that combining PCA and DSC can raise the robustness of causal inference~\cite{bayani2021}.
+Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ principal components.
+Previous study has proved that combining PCA and DSC can raise the robustness of causal inference~\cite{bayani2021}.
 We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different.
-Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\nameref{secS2}~Figure~\ref{fig:elbow}}).
+Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\nameref{secS2}~Figure\ref{fig:elbow}}).
 Finally, we transform the dataset and input the dimensions-reduced output into the DSC model.
@@
 \subsection{Differenced Synthetic Control}\label{sec:DSC}
-Using the Differenced Synthetic Control (DSC) method, we estimate water use without the effect of the institutional shift.
+Using the Differenced Synthetic Control (DSC) method, we can estimate water use under the scenarios of no institutional shift.
 The DSC method is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit~\cite{abadie2010, abadie2015, hill2021}.
@@
 
-There are two main methods to test the robustness of DSC.
-First of all, the reconstruction effect on inferred variables (water consumption in this chapter) before and after treatment (the intervention of watershed water division policy in this chapter) can be compared.
-If there is a small gap between the model predicted value reconstructed before treatment and the actual observed value, and a large gap between the predicted value and observed value reconstructed after treatment, it indicates that the effect of policy intervention is very obvious.
-In the study of this chapter, in order to judge whether the intervention effect is significant, the paired sample $T$ test is used to calculate statistics, and the model prediction and actual observation data in the early and late period of institutional intervention are respectively tested for the two institutional interventions of "August 7" water separation scheme in $1987$ and unified watershed scheduling in $1998$.
-If $p$ value after policy intervention is less than the threshold value (the confidence level of 95\% is adopted in this chapter, that is, the threshold value is $0.05$), the original hypothesis $H_0$ that "there is no significant difference between the two" can be rejected, and it is believed that the institutional intervention has significantly changed the water consumption in this region.
-If the significance level of $T$ test before institutional intervention is greater than the threshold value, it means that the DSC model successfully predicted the change of water consumption in this region over time before institutional intervention, and the fitting effect is good.
+Two primary methods can be employed to test the robustness of the DSC approach.
 
-Second, placebo trials are another common way to evaluate the effectiveness of synthetic control methods.
-In a placebo trial, a placebo unit selected from the control unit library is substituted for the treated unit, and a synthetic control method is applied to the placebo unit using the same data and parameters as the treated unit.
-If the synthetic control method is effective, there should be a clear difference between the placebo unit and the control unit, since the placebo unit should not be affected by the intervention.
-Placebo tests can be used to assess the effectiveness of the synthetic control method and detect any bias or confounding factors in the analysis.
-In this study, the placebo test step \cite{abadie2010} suggested by Abadie when proposing the synthetic control method was adopted, and the Python library of the differential synthetic control method developed by Dmitry et al.
-was used for the placebo test.
-If the ratio of the root mean square error (see Equation \ref{ch5:eq:RMSE}) to the pre-synthesis period was significantly higher in most provinces (again using the $T$ test to determine the significance of the difference) than the results of other placebo units, it would suggest that the Yellow River basin was more affected than most other provinces during the regime treatment period ($1987$ and $1998$ years).
+Firstly, the reconstruction effect on inferred variables (water consumption here) before and after treatment (the interventions of 87-WAS and 98-UBR) can be compared.
+If there are small gaps between the predicted and observed values before treatment, and a large gap after treatment, it indicates that the policy intervention's effect is apparent.
+In this study, to determine whether the intervention effect is significant, the paired sample $T$ test is used to calculate statistics, comparing the model predictions and actual observation data in the periods before and after institutional interventions for both the 87-WAS in $1987$ and 98-UBR in $1998$.
+% If the $p$ value after the policy intervention is less than the threshold value ($0.05$), the null hypothesis $H_0$ of no significant difference can be rejected, and it is believed that the institutional intervention has significantly changed the water consumption in this region.
+% If the significance level of the $T$ test before institutional intervention is greater than the threshold value, it means that the DSC model successfully predicted the change in water consumption in this region over time before institutional intervention, indicating a good fit.
+A robust synthetic control model will show a significant difference after treatment but not before treatment.
+
+Secondly, placebo experiments are another common way to evaluate the effectiveness of synthetic control methods.
+Placebo units are selected from the control unit pool and substituted for the treated unit, applying the synthetic control method to the placebo unit using the same data and parameters as the treated unit.
+If the synthetic control method is effective, there should be a clear difference between the placebo unit and the control unit since the placebo unit should not be affected by the intervention.
+% Placebo tests can be used to assess the effectiveness of the synthetic control method and detect any bias or confounding factors in the analysis.
+In this study, we adopt the placebo test step suggested by Abadie when proposing the synthetic control method~\cite{abadie2010} and utilize the Python library of the differential synthetic control method for the placebo test.
+If the ratio of the root mean square error (see Equation~\ref{ch5:eq:RMSE}) in the pre-synthesis period is significantly higher for most provinces (again using the $T$ test to determine the significance of the difference) than the results of other placebo units, it would suggest that the Yellow River Basin was more significantly affected than most other provinces during the treatment periods ($1987$ and $1998$), i.e., the results are more robust.
 

### 2023-05-05 docs/papers/01_manuscript/02_structures.tex
refactor(introduction): :recycle: 重构到JH写法
refactor(project): :recycle: JH表述修改
refactor(result): :recycle: 重构并润色结果部分

--- 2022-07-01 docs/papers/01_manuscript/02_structures.tex
@@
 % \subsection{INSTITUTIONAL SHIFTS AND STRUCTURES}
-\subsection{Institutional shifts and structures}
-\label{results-1}
+\subsection{Institutional shifts and structures}\label{results-1}
 
@@
 		Institutional shifts and related SES structures in the Yellow River Basin (YRB).
-		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{\nameref{secS1}} Table~\ref{tab:quota}).
-The national administrations are the ultimate authority in issuing water governance policies, which are often implemented by basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
+		\textbf{A.} The YRB crosses $10$ provinces or the same-level administrative regions, $8$ of which heavily rely on the water resources from the YRB (Table~\ref{tab:quota}).
+The national administrations hold ultimate authority in issuing water governance policies, which are often implemented by the basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
 		\textbf{B.} Provincial administrative agencies are the major stakeholders.
-Since the 87-WAS, with surface water withdrawal from the Yellow River restricted by specific quotas, each stakeholder plan and use water resources for development.
-However, the natural hydrological processes are connected.
-Although the institutions focus mainly on surface water (Sur.), it can also influence groundwater inside (Gro.) or water resources outside (Sur.
-and Gro.') through systematic socio-hydrological processes within the YRB.
-The YRCC only monitors water withdrawals at that time.
-		\textbf{C.} Institutional shifts and following structures changes (details in \textit{\nameref{secS1}}).
-(1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from the connected ecological unit (the reach of Yellow River, denoted by the blue circles).
-(2) After 1987-WAS, the YRCC (the yellow circles) was monitoring (the dot-line links) river reaches with the water use quota.
-(3) Since the 98-UBR, stakeholders have to apply for water use licenses from the YRCC (the connections between the red and yellow circles).
-	}
-	\label{fig:structure}
+Since the 87-WAS, with surface water withdrawal from the Yellow River restricted by specific quotas, each stakeholder plans and uses water resources for development.
+However, natural hydrological processes are interconnected.
+Although the institutions focus mainly on surface water (Sur.), they can also influence groundwater inside (Gro.) or water resources outside (Sur.\ and Gro.') through systematic socio-hydrological processes within the YRB.\\ The YRCC only monitors water withdrawals at that time.
+		\textbf{C.} Institutional shifts and subsequent structural changes (details in \textit{\nameref{secS1}}).
+(1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from the connected ecological unit (the reach of the Yellow River, denoted by the blue circles).
+(2) After 1987-WAS, the YRCC (the yellow circles) monitored (the dot-line links) river reaches with water use quotas.
+(3) Since the 98-UBR, stakeholders have had to apply for water use licenses from the YRCC (the connections between the red and yellow circles).
+	}\label{fig:structure}
 \end{figure*}
@@
 % 制度变动综述
-The institutional shifts in the YRB in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among YRB's water governance practices (\textit{\nameref{sec:yrb}} and \textit{\nameref{secS1}}).
-Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
-The YRCC had no links to the provinces regarding water use before 1987, and the provinces could link directly to the Yellow River reaches (Figure~\ref{fig:structure}~C).
-To shrink water deficits, in 87-WAS, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin (Table~\ref{tab:quota}).
-Simultaneously, according to the extracted information from documents of the 87-WAS issued by national ministries, the YRCC started to report water use in each reach.
-As it was the first time the responsibility of the YRCC involved water use, this introduced new links between the YRCC and the ecological nodes (Figure~\ref{fig:structure}~C).
-However, the controversial 87-WAS did not resolve water depletion.
-In 1998, another strategy (98-UBR) was developed to strengthen the responsibilities of the YRCC for integrated managing water use.
-Information from the 98-UBR documents demonstrated that the provinces had to apply their plan for an annual water use license to YRCC instead of direct access to the Yellow River water.
-Thus, the YRCC has been linked to the provinces since 1998 (Figure~\ref{fig:structure}~C).
+% The institutional shifts in the YRB in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among YRB's water governance practices (\textit{\nameref{sec:yrb}} and \textit{\nameref{secS1}}).
+Until the 87-WAS, provincial regions in the YRB had unrestricted access to the Yellow River water resources for development, despite geographic and temporal differences between freshwater demand and availability.
+The YRCC had no links to the provinces regarding water use before 1987, and the provinces could connect directly to the Yellow River reaches (Figure~\ref{fig:structure}~C).
+Following the 87-WAS, national authorities proposed allocating specific water quotas among the provinces, and the YRCC's duty became to report actual water use volumes in each reach.
+As it was the first time the YRCC's responsibilities included water use, this introduced new links between the YRCC and the river (i.e., ecological nodes Figure~\ref{fig:structure}~C).
+The 98-UBR further reinforced the YRCC's responsibilities for integrated water use management.
+Since $1998$, provinces have been required to submit their annual water use plans for water use licenses to the YRCC instead of freely accessing the Yellow River water.
+Consequently, the YRCC has been directly linked to the provinces since then (Figure~\ref{fig:structure}C).
+% As result, the two institutional shifts reshaped SES structures, leading to three general structures linked by social actors and ecological nodes (Figure~\ref{fig:structure}~C).

### 2023-05-05 docs/papers/01_manuscript/03_results.tex
refactor(result): :recycle: 重构并润色结果部分

@@
 	Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
-		\textbf{A.} water uses of the YRB before and after the institutional shift in 1987 (87-WAS);
-		\textbf{B.} water uses of the YRB before and after the institutional shift in 1998 (98-UBR).
+	\textbf{A.} Water uses of the YRB before and after the institutional shift in 1987 (87-WAS);
+	\textbf{B.} Water uses of the YRB before and after the institutional shift in 1998 (98-UBR).
 Blue lines are statistics derived from water use data; grey lines are estimates from the Differenced Synthetic Control method with economic and environmental background controlled;
@@
 
-Our estimation of theoretical water use suggests that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without an institutional shift (Figure~\ref{fig:main_results}A).
-From 1988 to 1998, on average, while the estimation of annual water use only suggests $974.34$ billion $m^3$, the observed water use of the YRB provinces reached $1038.36$ billion $m^3$ (an increase of $6.57\%$).
-However, after the institutional change in 1998 (98-UBR), trends of increasing water use appeared to be effectively suppressed.
-From 1998 to 2008, the total observed water use decreased by $0.49$ billion $m^3/yr$ per year, while the estimation of water use still suggests $0.82$ billion $m^3/yr$ increases (Figure~\ref{fig:main_results} B).
-The increased water uses after 87-WAS aligns with the severe drying-down of the surface streamflow from 1987 to 1998, an obvious indicator of river degradation and environmental crisis (Figure~\ref{fig:main_results}C).
+% 黄河流域的总用水量在反事实推断模型和实际观测值在两次制度变化后呈现出差异显著，在之前此差异则较小且不显著（见图\ref{ch5:fig:main_results}A和B），这表明其用水变化的估计重建良好。
+The total water use of the YRB exhibited a significant difference between the counterfactual prediction and the actual observed value after the two institutional shifts, while the difference was small and insignificant before (see Figures~\ref{fig:main_results}A and B).
+This indicates that the estimated reconstruction of water use change was robust.
+Figure~\ref{fig:main_results}A suggests that the 87-WAS prompted the provinces to withdraw even more water than would have been used without an institutional shift (Figure~\ref{fig:main_results}A).
+From 1988 to 1998, on average, while the estimation of annual water use only suggests $887.05~km^3$ billion $m^3$, the observed water use of the YRB provinces reached $938.06$ billion $m^3$ (an increase of $5.75\%$).
+However, after the 98-UBR, trends of increasing water use appeared to be effectively suppressed.
+From 1998 to 2008, the total observed water use decreased by $6.6$ billion $m^3/yr$ per year, while the estimation of water use still suggests $5.5$ billion $m^3/yr$ increases (Figure~\ref{fig:main_results} B).
+The increased water uses after 87-WAS align with the severe dry-up of the surface streamflow from $1987$ to $1998$, a clear indicator of river degradation and environmental crisis (Figure~\ref{fig:main_results}C).
 On the other hand, the 98-UBR ended river depletion, despite subsequent increases in drought intensity (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{fig:main_results}C).
@@
 	\caption{
-		Regulating differences for provinces in the YRB.
+		Regulating differences for provinces in the YRB.\\
 		Red (the 87-WAS) and green (the 98-UBR) bars denote an increased or decreased ratio for actual water use relative to the estimate from the model in the decade after the institutional shift.
@@
 
-% 结果2部分：展示区域相应差异
-Our results also suggest differences between patterns of provinces in their responses to the two institutional regulating.
-During the decade after the 87-WAS, the major water-using provinces (e.g., Inner Mongolia, Henan, Shandong) had apparent accelerations (Figure~\ref{fig:regulating}).
-The proportion of increased (or decreased) water use for each province (over the estimated water use by the model) correlated significantly (partial correlation coefficient is $0.77$, $p<0.05$) with actual water use from the Yellow River.
-On average, the major water users (Shandong, Inner Mongolia, Henan, and Ningxia) used $32.14\%$ more water than predicted from 1987 to 1998.
-By contrast, after the 98-UBR (from 1998 to 2008), almost all provinces have seen declines ($-16.54\%$ on average) in water use.
-Furthermore, the regulated water use of provinces was unrelated (partial correlation coefficient is $0.33$, $p>0.1$) to their proportional water use from the Yellow River.
-To interpret this pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases theoretically where the water using structure between 1987 and 1998 is the largest-consuming case (\ref{secS4}).
+Our results demonstrate that there are differences in the response patterns of the two changes in the water resources allocation system.
+In Figure~\ref{fig:regulating}, the red bar chart (87-WAS) and the green bar chart (98-UBR) respectively represent the increase or decrease ratio of actual water consumption compared to the estimated water use of the DSC model within ten years after the institutional shifts.
+The gray bar chart shows the ratio of actual water use by provinces to their total water use in the decade after the two changes; The triangle marks indicate the ratio of the theoretical water resource quota of the province to the total available water in the YRB.\
+In the ten years after the 87-WAS, the proportion of water consumption increase (or decrease) compared to that estimated by the DSC model was positively correlated with the proportion of water consumption taken from the YRB at present (partial correlation coefficient was $0.64$, Figure~\ref{fig:regulating}).
+From 1987 to 1998, some provinces with high water consumption (e.g., Inner Mongolia, Henan, and Shandong) also showed significant increases in water consumption (Figure~\ref{fig:regulating}), with the average water consumption in Shandong, Inner Mongolia, Henan, and Ningxia exceeding the predicted value by $32.14\%$.
+However, from 1998 to 2008, almost all provinces experienced a decrease in water consumption (by an average of $16.54\%$).
+In addition, the water consumption of each province has a negative correlation with the proportion of water taken from the Yellow River Basin (partial correlation coefficient is $-0.51$).

### 2023-05-05 docs/papers/01_manuscript/04_discussion.tex
refactor(discussion): :recycle: 重构讨论部分

@@
 The influences of institutional shifts on governing effects of social-ecological systems (SESs) were widely reported worldwide, but few attempts to quantify their net effects~\cite{cumming2020a}.
-Our results show that while 98-UBR decreased water use in the YRB, 87-WAS increased it by $5.75\%$.
-The results challenged previous analyses (i.e., suggesting that 87-WAS ``had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present~\cite{abadie2015,hill2021}.
+Our case study of the YRB's water governance suggests that while 98-UBR decreased total water use as expected, 87-WAS unexpected increased it by $5.75\%$, comparison of which can produce insights on effectiveness of governance.
+Firstly, the results challenged previous analyses (i.e., suggesting that 87-WAS ``had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present~\cite{abadie2015,hill2021}.
 However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{\nameref{secS2}}~Table~\ref{tab:variables}).
@@
 
-% discussion-2: 87的增加
-% 结果与制度的目的完全相反的87-WAS与许多其它的SES失败治理案例类似，表明不匹配的社会生态结构可能促进了对公共资源的掠夺式开采。
-The above comparison suggests that the 87-WAS, whose results were contrary to the purpose of the institution, is similar to many other SES governance failures, supporting that mismatched socio-ecological structures can deterioration of common resources~\cite{kellenberg2009,cai2016,barnes2019}.
-The increased water use after 87-WAS aligns with concerns about frequently scrambling for water in some provinces during this period~\cite{mao2000, bouckaert2022}.
-Although reasons for the non-ideal effect of 87-WAS had been widely discussed~\cite{huangang2002} (such as enforcement, feasibility, and equity), however, structural change has received limited attention.
-Our results show that the correlation between current water use and changed (increased or decreased) water use was significant after 87-WAS (Figure~\ref{fig:regulating}).
-This ``major users use more'' pattern supports the hypothesis that separated stakeholders (individual provinces) will respond to structure by maximizing utility (interpreted in our structure-based model, see Figure~\ref{fig:model}).
+Examining the unexpected 87-WAS policy, we found it framed a similar structure to many other SES governance failures, supporting the hypothesis that specific mismatched structures can rapidly exhaust common resources~\cite{kellenberg2009,cai2016,barnes2019}.
+Generally, these structure-based failures when social actors freely access linked resource units (like the institution before 1987), while the monitoring duty of YRCC after 87-WAS was a sign that water quota was valuable to pursue (between 1987 and 1998).
+This conjecture aligns with the increased water use after 87-WAS and the concerns about frequently scrambling for water in some provinces during this period~\cite{mao2000, bouckaert2022}.
+Previous study analyzed reasons for the non-ideal effect of 87-WAS~\cite{huangang2002} where core concerns were lack of enforcement and controlling approaches, while major stakeholders kept arguing they need more quotas from 1983 to 1990s.
+It indicates that it was reasonable for stakeholders to pursue more water quota by withdrawing more water, beyond their economic growth.
+Our results stand in line with this hypothesis since the correlation between current water use and changed (increased or decreased) water use was significant after the 87-WAS but not after the 98-UBR (Figure~\ref{fig:regulating}).
+In addition, through a theoretically marginal benefit analysis, this ``major users use more'' pattern can be inferred from a simple assumption that stakeholder can expect water quota's value in the short future, also supporting the above hypothesis (see Figure~\ref{fig:model}).
 
-The validity of our theoretical analysis is supported by two facts:
-(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987)~\cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
-The bargaining was also a process for matching water shares to economic volume because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution)~\cite{zuo2020}.
-(2) Provinces with higher current water use might have greater bargaining power in water use allocation because of information asymmetry between decision-makers and stakeholders.
-Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligned with their appeals to the higher central government for larger shares~\cite{wang2019a, wang2019d}.
+Besides our results, the above hypothesis also keeps in line with two reported facts:
+(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) and the bargaining arguments even last years after 1987~\cite{wang2019a, wang2019d}.
+It was the process where each province attempted to demonstrate its development potential related to water use, for matching water shares to economy because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution)~\cite{zuo2020}.
+(2) During the ``bargaining'', more significant stakeholders had considerable incentives to pursue more water quotas, which aligned with those major water users submitted appeals to the higher central government for larger shares~\cite{wang2019a, wang2019d}.
+It means provinces with higher current water use have greater bargaining power in water use allocation.
 
-On the other hand, social-ecological matches can also be supported by structural effects.
-After 98-UBR, the YRCC could adjust surface water use quotas according to climate conditions for the whole YRB.
-When the YRCC began to coordinate among stakeholders, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)
-\cite{krieger1955, ostrom1990}.
-During this period, proportional decreased water use of provinces indicated expected river regulating results (see \nameref{result-3}).
-Meanwhile, our model also demonstrates that in this case, the unified scale-matched institution was indispensable for decreased water use.
-However, since the 98-UBR only regulated surface water use, many clues suggested the institution shift may cause broader influences (cascading effects) because of unsatisfied water demands.
-For example, literature estimated increased groundwater withdrawals after 98-UBR in many intensive irrigation regions, despite little eligible data on groundwater use and stakeholders being accessible~\cite{sun2022b}.
-Since the 21st century, similar water quota policies started to be implemented nationally and altering the relationship between social actors and resource units.
-As both institutional shifts examined here induced unexpected changes or cascading effects within SESs, better governance calls for more institutional analysis of coupled human and natural systems in the future.
+On the other hand, since the YRCC could coordinate stakeholders by water quotas licenses according to water conditions for the whole YRB after 98-UBR, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)~\cite{krieger1955, ostrom1990}.
+Again, proportional decreased water use of provinces and the theoretical minimal water use of marginal benefit model indicated this policy lead to successful governance as expected (see \nameref{result-3}).
+However, since the 98-UBR only regulated surface water use, many clues suggested the institution shift may cause broader influences, including estimated increased groundwater withdrawals after 98-UBR in many intensive water use regions~\cite{sun2022b}.
+With little eligible data on groundwater use, related assessment is out of this study but quite important, as similar water quota policies started to be implemented nationally since the 21st century.
 
 The structural pattern we depicted here (Figure~\ref{fig:structure}) have also been reported in other SESs worldwide~\cite{kluger2020,guerrero2015,bodin2012}.
-Before 98-UBR, SES structure (i.e., fragment ecological units linked to separate social actors) was more likely to be mismatched because isolated actors generally struggle to maintain interconnected ecosystems holistically~\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
-Institutional re-alignments since 98-UBR improved the authority of the YRCC and helped it match the scale of resource provisioning in the YRB, leading to enhanced effectiveness regarding runoff restoration~\cite{cumming2020a,wang2019d}.
-The comparison demonstrates again the challenge of finding win-win situations in coupled human-nature systems~\cite{hegwood2022}, and the need to more deeply understand the role of social-ecological structures~\cite{bergsten2019, sayles2019}.
+Before 98-UBR, fragment ecological units linked to separate social actors, which can more likely lead to lower effectiveness because isolated actors generally struggle to maintain interconnected ecosystems holistically~\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
+Institutional re-alignments since 98-UBR enhanced the responsibilities of the basin-scale authority (YRCC) and led to effectiveness in runoff restoration, which are usually named scale match or institutional match of SESs~\cite{cumming2020a,wang2019d}.
+Taken together, the comparison demonstrates again the challenge of finding win-win situations in coupled social-ecological systems~\cite{hegwood2022}, and the need to more deeply understand the role of institutions in water governance~\cite{bergsten2019, sayles2019}.
 % Therefore, the YRB cases can provide further explanation of the matching and mismatching of the previous SES building blocks, linking SES structure and outcomes by plausible reasons of causality and underlying processes.
@@
 The structural pattern that led to different effectiveness widespread in global SESs, so our proposed mechanism is crucial to governing such coupled systems.
+As both institutional shifts examined here induced unexpected changes or cascading effects within SESs, better governance calls for more institutional analysis of coupled human and natural systems in the future.
 Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{\nameref{secS1}})~\cite{yu2019, niu2022}.
@@
 Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation scheme (see \textit{\nameref{secS1}}).
-Our analysis suggests that these initiatives can lead to distortions because of mismatched structure when shifting to another institution~\cite{bodin2017b}.
-Therefore, our research provides a cautionary tale of how institutions can change perverse incentives~\cite{hegwood2022}, while insights from the YRB can provide guidelines for SESs management worldwide~\cite{muneepeerakul2017, leslie2015}.
+Our analysis suggests that these initiatives can lead to unexpected result because of mismatched structure when shifting to another institution~\cite{bodin2017b}.
+Therefore, our research provides insights of how institutions can effect achieving successful river basin governance when socio-hydrological interplays framing  SES structures~\cite{muneepeerakul2017, leslie2015, hegwood2022}.

### 2023-05-06 docs/papers/01_manuscript/04_discussion.tex
docs(discussion): :zap: GPT润色

@@
 % 制度对社会生态系统的结果产生影响在世界范围内都很普遍，
-The influences of institutional shifts on governing effects of social-ecological systems (SESs) were widely reported worldwide, but few attempts to quantify their net effects~\cite{cumming2020a}.
-Our case study of the YRB's water governance suggests that while 98-UBR decreased total water use as expected, 87-WAS unexpected increased it by $5.75\%$, comparison of which can produce insights on effectiveness of governance.
-Firstly, the results challenged previous analyses (i.e., suggesting that 87-WAS ``had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present~\cite{abadie2015,hill2021}.
-However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{\nameref{secS2}}~Table~\ref{tab:variables}).
-On the contrary, the 98-UBR reduced surface water competition, so many studies attributed the streamflow restoration mainly to the successful introduction of this institution~\cite{chen2021,huangang2002,an2007}.
+The impacts of institutional shifts on the governing effects of social-ecological systems (SESs) have been widely reported worldwide, but few attempts have been made to quantify their net effects~\cite{cumming2020a}.
+Our case study of the YRB's water governance suggests that while the 98-UBR decreased total water use as expected, the 87-WAS unexpectedly increased it by $5.75\%$, a comparison of which can yield insights into the effectiveness of governance.
+Firstly, the results challenge previous analyses (i.e., suggesting that 87-WAS ``had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present~\cite{abadie2015,hill2021}.
+However, the significant net effect indicated by our analysis suggests that the 87-WAS was followed by increased water use even after controlling for environmental and economic variables (see \textit{\nameref{secS2}} Table~\ref{tab:variables}).
+In contrast, the 98-UBR reduced surface water competition, so many studies attributed the streamflow restoration mainly to the successful introduction of this institution~\cite{chen2021,huangang2002,an2007}.
 
-Examining the unexpected 87-WAS policy, we found it framed a similar structure to many other SES governance failures, supporting the hypothesis that specific mismatched structures can rapidly exhaust common resources~\cite{kellenberg2009,cai2016,barnes2019}.
-Generally, these structure-based failures when social actors freely access linked resource units (like the institution before 1987), while the monitoring duty of YRCC after 87-WAS was a sign that water quota was valuable to pursue (between 1987 and 1998).
+Examining the unexpected 87-WAS policy, we found it shared a similar structure with many other SES governance failures, supporting the hypothesis that specific mismatched structures can rapidly exhaust common resources~\cite{kellenberg2009,cai2016,barnes2019}.
+Generally, these structure-based failures occur when social actors freely access linked resource units (like the institution before 1987), while the monitoring duty of the YRCC after 87-WAS was a sign that water quota was valuable to pursue (between 1987 and 1998).
 This conjecture aligns with the increased water use after 87-WAS and the concerns about frequently scrambling for water in some provinces during this period~\cite{mao2000, bouckaert2022}.
-Previous study analyzed reasons for the non-ideal effect of 87-WAS~\cite{huangang2002} where core concerns were lack of enforcement and controlling approaches, while major stakeholders kept arguing they need more quotas from 1983 to 1990s.
+A previous study analyzed reasons for the non-ideal effect of 87-WAS~\cite{huangang2002}, where core concerns were the lack of enforcement and controlling approaches, while major stakeholders kept arguing they needed more quotas from 1983 to the 1990s.
 It indicates that it was reasonable for stakeholders to pursue more water quota by withdrawing more water, beyond their economic growth.
-Our results stand in line with this hypothesis since the correlation between current water use and changed (increased or decreased) water use was significant after the 87-WAS but not after the 98-UBR (Figure~\ref{fig:regulating}).
-In addition, through a theoretically marginal benefit analysis, this ``major users use more'' pattern can be inferred from a simple assumption that stakeholder can expect water quota's value in the short future, also supporting the above hypothesis (see Figure~\ref{fig:model}).
+Our results align with this hypothesis since the correlation between current water use and changed (increased or decreased) water use was significant after the 87-WAS but not after the 98-UBR (Figure~\ref{fig:regulating}).
+In addition, through a theoretically marginal benefit analysis, this ``major users use more'' pattern can be inferred from a simple assumption that stakeholders can expect water quota's value in the short future, also supporting the above hypothesis (see Figure~\ref{fig:model}).
 
-Besides our results, the above hypothesis also keeps in line with two reported facts:
-(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) and the bargaining arguments even last years after 1987~\cite{wang2019a, wang2019d}.
-It was the process where each province attempted to demonstrate its development potential related to water use, for matching water shares to economy because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution)~\cite{zuo2020}.
-(2) During the ``bargaining'', more significant stakeholders had considerable incentives to pursue more water quotas, which aligned with those major water users submitted appeals to the higher central government for larger shares~\cite{wang2019a, wang2019d}.
-It means provinces with higher current water use have greater bargaining power in water use allocation.
+Besides our results, the above hypothesis also aligns with two reported facts:
+(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) and the bargaining arguments even persisted years after 1987~\cite{wang2019a, wang2019d}.
+During this process, each province attempted to demonstrate its development potential related to water use, to match water shares to their economy because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution)~\cite{zuo2020}.
+(2) During the ``bargaining'', more significant stakeholders had considerable
+incentives to pursue more water quotas, which aligned with the fact that major water users submitted appeals to the higher central government for larger shares~\cite{wang2019a, wang2019d}.
+This means provinces with higher current water use have greater bargaining power in water use allocation.
 
-On the other hand, since the YRCC could coordinate stakeholders by water quotas licenses according to water conditions for the whole YRB after 98-UBR, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)~\cite{krieger1955, ostrom1990}.
-Again, proportional decreased water use of provinces and the theoretical minimal water use of marginal benefit model indicated this policy lead to successful governance as expected (see \nameref{result-3}).
+On the other hand, since the YRCC could coordinate stakeholders by water quota licenses according to water conditions for the entire YRB after 98-UBR, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)~\cite{krieger1955, ostrom1990}.
+Similar, proportional decreased water use of provinces and the theoretical minimal water use of marginal benefit model indicated this policy lead to successful governance as expected (see \nameref{result-3}).
 However, since the 98-UBR only regulated surface water use, many clues suggested the institution shift may cause broader influences, including estimated increased groundwater withdrawals after 98-UBR in many intensive water use regions~\cite{sun2022b}.
-With little eligible data on groundwater use, related assessment is out of this study but quite important, as similar water quota policies started to be implemented nationally since the 21st century.
+With limited eligible data on groundwater use, related assessment is beyond the scope of this study but remains quite important, as similar water quota policies started to be implemented nationally since the 21st century.
 
-The structural pattern we depicted here (Figure~\ref{fig:structure}) have also been reported in other SESs worldwide~\cite{kluger2020,guerrero2015,bodin2012}.
-Before 98-UBR, fragment ecological units linked to separate social actors, which can more likely lead to lower effectiveness because isolated actors generally struggle to maintain interconnected ecosystems holistically~\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
+The structural pattern we depicted here (Figure~\ref{fig:structure}) has also been reported in other SESs worldwide~\cite{kluger2020,guerrero2015,bodin2012}.
+Before 98-UBR, fragmented ecological units were linked to separate social actors, which more likely led to lower effectiveness because isolated actors generally struggle to maintain interconnected ecosystems holistically~\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
 Institutional re-alignments since 98-UBR enhanced the responsibilities of the basin-scale authority (YRCC) and led to effectiveness in runoff restoration, which are usually named scale match or institutional match of SESs~\cite{cumming2020a,wang2019d}.
-Taken together, the comparison demonstrates again the challenge of finding win-win situations in coupled social-ecological systems~\cite{hegwood2022}, and the need to more deeply understand the role of institutions in water governance~\cite{bergsten2019, sayles2019}.
+Taken together, the comparison demonstrates the challenge of finding win-win situations in coupled social-ecological systems~\cite{hegwood2022} and the need to more deeply understand the role of institutions in water governance~\cite{bergsten2019, sayles2019}.
 % Therefore, the YRB cases can provide further explanation of the matching and mismatching of the previous SES building blocks, linking SES structure and outcomes by plausible reasons of causality and underlying processes.
@@
 and second, when applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
-Our quasi-experiment approach nonetheless provides evidence supporting the view that there was a change in water use trajectory following the YRB's unique institutional shifts and offers insights into water governance (and particularly the importance of having a scale-matched, basin-wide authority for water allocation solutions~\cite{bodin2017b, ostrom2009, reyers2018})
+Our quasi-experiment approach nonetheless provides evidence supporting the view that there was a change in water use trajectory following the YRB's unique institutional shifts and offers insights into water governance (and particularly the importance of having a scale-matched, basin-wide authority for water allocation solutions~\cite{bodin2017b, ostrom2009, reyers2018}).
 Moreover, the ultimate success of the 98-UBR institutional shift theoretically and practically proved the importance of social-ecological fit.
-For sustainability in the future, therefore, it is necessary to emphasize the necessity of strengthening connections between stakeholders by agents consistent with the scale of the ecological system.
+For sustainability in the future, it is necessary to emphasize the need to strengthen connections between stakeholders through agents consistent with the scale of the ecological system.
 From these perspectives, two scenarios based on the marginal benefit analysis (see \textit{\nameref{secS5}}) can inspire institutional design on how to reduce mismatches.
@@
 
-The structural pattern that led to different effectiveness widespread in global SESs, so our proposed mechanism is crucial to governing such coupled systems.
-As both institutional shifts examined here induced unexpected changes or cascading effects within SESs, better governance calls for more institutional analysis of coupled human and natural systems in the future.
-Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{\nameref{secS1}})~\cite{yu2019, niu2022}.
-Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development~\cite{wang2019a}.
-Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation scheme (see \textit{\nameref{secS1}}).
-Our analysis suggests that these initiatives can lead to unexpected result because of mismatched structure when shifting to another institution~\cite{bodin2017b}.
-Therefore, our research provides insights of how institutions can effect achieving successful river basin governance when socio-hydrological interplays framing  SES structures~\cite{muneepeerakul2017, leslie2015, hegwood2022}.
+The structural pattern that led to different effectiveness is widespread in global SESs, making our proposed mechanism crucial to governing such coupled systems.
+Our analysis suggests that these initiatives can lead to unexpected results because of mismatched structure when shifting to another institution~\cite{bodin2017b}.
+Better governance calls for more institutional analysis while China has embarked to redesign its decades-old water allocation scheme.
+Our research provides insights into how institutions can affect achieving successful river basin governance when socio-hydrological interplays frame SES structures~\cite{muneepeerakul2017, leslie2015, hegwood2022}.

### 2023-05-06 docs/papers/01_manuscript/01_introduction.tex
refactor(project): :recycle: 重构到JH的风格

@@
 
-Institutions encompass the interplay between social actors, ecological units, and their interactions~\cite{young2008, lien2020, bodin2017b, wang2022g}.
-These interactions constitute a type of SES structure, where effective institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different interactions, contributing to sustainability~\cite{epstein2015, wang2019d}.
+Institutions encompass the interplay between social actors, ecological units, and their interactions~\cite{young2008, lien2020, bodin2017b, wang2022g} (Figure~\ref{fig:framework}~a).
+These interactions constitute a type of SES structure, where effective institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different interactions, contributing to sustainability~\cite{epstein2015, wang2019d} (Figure~\ref{fig:framework}~b).
 % (Figure~\ref{fig:framework}~\textbf{a}).
@@
 	\caption{
-		Framework for understanding institutional shifts and SES structures.
+		Illustration for understanding institutional shifts and SES structural changes.
 \textbf{a.} In the general framework for analyzing social-ecological systems (SESs), (Adapted from Ostrom, 2008~\cite{ostrom2009}).
 Institutional shifts can change interactions within the SES and reframe the structures.
-\textbf{b.} We aim to investigate how institutional shifts impacts effective governance by structuring SES.}\label{fig:framework}
+\textbf{b.} We aim to examine how institutional shifts effect river basin governance by structuring SES.}\label{fig:framework}
 \end{figure}

### 2023-05-06 docs/papers/01_manuscript/02_structures.tex
refactor(project): :recycle: 重构到JH的风格

@@
 Although the institutions focus mainly on surface water (Sur.), they can also influence groundwater inside (Gro.) or water resources outside (Sur.\ and Gro.') through systematic socio-hydrological processes within the YRB.\\ The YRCC only monitors water withdrawals at that time.
-		\textbf{C.} Institutional shifts and subsequent structural changes (details in \textit{\nameref{secS1}}).
+		\textbf{C.} Institutional shifts and subsequent structural changes (details in \textit{\nameref{sec:yrb}}).
 (1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from the connected ecological unit (the reach of the Yellow River, denoted by the blue circles).
@@
 % 制度变动综述
-% The institutional shifts in the YRB in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among YRB's water governance practices (\textit{\nameref{sec:yrb}} and \textit{\nameref{secS1}}).
 Until the 87-WAS, provincial regions in the YRB had unrestricted access to the Yellow River water resources for development, despite geographic and temporal differences between freshwater demand and availability.
@@
 % As result, the two institutional shifts reshaped SES structures, leading to three general structures linked by social actors and ecological nodes (Figure~\ref{fig:structure}~C).
+Key points of the official documents supporting the structural changes above can be found in supplementary material~\textit{\nameref{secS1}}.
+
+\input{tab_quotas.tex}

### 2023-05-06 docs/papers/01_manuscript/03_results.tex
refactor(project): :recycle: 重构到JH的风格

@@
 In the ten years after the 87-WAS, the proportion of water consumption increase (or decrease) compared to that estimated by the DSC model was positively correlated with the proportion of water consumption taken from the YRB at present (partial correlation coefficient was $0.64$, Figure~\ref{fig:regulating}).
-From 1987 to 1998, some provinces with high water consumption (e.g., Inner Mongolia, Henan, and Shandong) also showed significant increases in water consumption (Figure~\ref{fig:regulating}), with the average water consumption in Shandong, Inner Mongolia, Henan, and Ningxia exceeding the predicted value by $32.14\%$.
+From 1987 to 1998, some provinces with high water consumption (e.g., Inner Mongolia and Henan) also showed significant increases in water consumption (Figure~\ref{fig:regulating} and Table~\ref{tab:DSC_summary}), with the average water consumption in four major users (Shandong, Inner Mongolia, Henan, and Ningxia) exceeding the predicted value by $32.14\%$.
 However, from 1998 to 2008, almost all provinces experienced a decrease in water consumption (by an average of $16.54\%$).
 In addition, the water consumption of each province has a negative correlation with the proportion of water taken from the Yellow River Basin (partial correlation coefficient is $-0.51$).
+
+\input{tab_rmse.tex}

### 2023-05-06 docs/papers/01_manuscript/04_discussion.tex
refactor(project): :recycle: 重构到JH的风格

@@
 Our results align with this hypothesis since the correlation between current water use and changed (increased or decreased) water use was significant after the 87-WAS but not after the 98-UBR (Figure~\ref{fig:regulating}).
-In addition, through a theoretically marginal benefit analysis, this ``major users use more'' pattern can be inferred from a simple assumption that stakeholders can expect water quota's value in the short future, also supporting the above hypothesis (see Figure~\ref{fig:model}).
+In addition, through a theoretically marginal benefit analysis, this ``major users use more'' pattern can be inferred from a simple assumption that stakeholders can expect water quota's value in the short future, also supporting the above hypothesis (see \textit{\nameref{secS4}}).
 
 Besides our results, the above hypothesis also aligns with two reported facts:
-(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) and the bargaining arguments even persisted years after 1987~\cite{wang2019a, wang2019d}.
+(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) and the bargaining arguments even persisted years after 1987~\cite{wang2019e, wang2019d}.
 During this process, each province attempted to demonstrate its development potential related to water use, to match water shares to their economy because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution)~\cite{zuo2020}.
 (2) During the ``bargaining'', more significant stakeholders had considerable
-incentives to pursue more water quotas, which aligned with the fact that major water users submitted appeals to the higher central government for larger shares~\cite{wang2019a, wang2019d}.
+incentives to pursue more water quotas, which aligned with the fact that major water users submitted appeals to the higher central government for larger shares~\cite{wang2019e, wang2019d}.
 This means provinces with higher current water use have greater bargaining power in water use allocation.
@@
 For sustainability in the future, it is necessary to emphasize the need to strengthen connections between stakeholders through agents consistent with the scale of the ecological system.
-From these perspectives, two scenarios based on the marginal benefit analysis (see \textit{\nameref{secS5}}) can inspire institutional design on how to reduce mismatches.
 For example, water rights transfers may be another way to build horizontal links between stakeholders that also have the potential to result in better water governance.

### 2023-05-06 docs/papers/01_manuscript/05_conclusion.tex
refactor(project): :recycle: 重构到JH的风格

@@
 %! Date = 2022/3/10
-Our study emphasizes the importance of social-ecological system (SES) structures in effective water resource management.
-By examining the Yellow River Basin (YRB) in China as a case study, we found that the 1987 Water Allocation Scheme (87-WAS) led to an 5.75\% increase in observed water use, while the 1998 Unified Basinal Regulation (98-UBR) effectively reduced total water use.
-Our findings highlight the critical role of well-designed SES structures in driving water resource management outcomes.
-To achieve sustainability, we recommend avoiding fragmented ecological units linked to separated social actors and underscore the need for a deeper understanding of the underlying processes and relationships in SES structures for effective water governance.
+
+In this study, we examined the effects of two major institutional shifts in water governance within the Yellow River Basin (YRB): the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basin Regulation (98-UBR).
+By employing a Difference-in-Differences approach with Synthetic Control, we quantified the net effects of these institutional shifts on water use within the YRB.\
+Our results showed that the 87-WAS unexpectedly increased water use by $5.75\%$, contrary to its intended goals, while the 98-UBR successfully reduced water use as anticipated.
+The analysis revealed that the structural patterns of the institutions played a critical role in their effectiveness.
+The mismatched structure of the 87-WAS led to increased competition and exploitation of water resources, while the 98-UBR, with its scale-matched, basin-wide authority and stronger connections between stakeholders, resulted in improved water governance.
+
+In conclusion, our research contributes to a better understanding of the role of institutions in SES governance, particularly in the context of water management.
+By identifying the key factors that influence the success or failure of institutional shifts, we provide valuable insights for the design of effective and sustainable water governance policies.
+Future research should continue to explore the intricacies of institutions in SES governance and investigate the potential impacts of additional policies and institutional shifts on water use and sustainability.

### 2023-05-06 docs/papers/01_manuscript/06_methods.tex
refactor(project): :recycle: 重构到JH的风格

@@
 Then, to estimate the water use of the YRB by assuming there were no effects from institutional shifts, we focused on variables from five categories (environmental, economic, domestic, and technological) water use factors.
-Their specific items and origins are listed in Table~\ref{tab:variables}.
-Among the total $31$ data-accessible provinces (or regions) assigned quotas in the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin, and Beijing because of their trivial water use from the YRB (see Table~\ref{tab:quota}).
+Their specific items and origins are listed in~\ref{secS2}~Table~\ref{tab:variables}.
+Among the total $31$ data-accessible provinces (or regions) assigned quotas in the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin and Beijing (together, Jinji) because of their trivial water use from the YRB (see Table~\ref{tab:quota}).
 % We then divided the dataset into a ``target group'' and a ``control group'', treating provinces involved in water quota as the target group $(n=8)$ and other provinces as the control group $(n=20)$ for applying the DSC.\\

### 2023-05-06 docs/papers/01_manuscript/manuscript.tex
refactor(introduction): :recycle: 重构引言
不再出现因果，使用JH风格写作
refactor(introduction): :recycle: 介绍黄河情况
refactor(project): :recycle: 重构到JH的风格

@@
 \usepackage{geometry}
+\usepackage{tabularx}
 
@@
 % https://www.sciencedirect.com/journal/journal-of-hydrology/about/call-for-papers#grounded-sociohydrology
-\title{Achieving Effective River Basin Governance through Institutional Shifts: Examining the Yellow River Basin's Social-Ecological Systems in China}
+\title{Quantifying the Effects of Institutional Shifts on Water Governance in the Yellow River Basin: A Socio-Hydrological Analysis}
 
@@
 \begin{abstract}
-     Global freshwater depletion necessitates efficient water governance that accounts for social-ecological system (SES) structures.
-To improve our understanding of the relationships between SES structures and water governance, we investigated the Yellow River Basin (YRB) in China, which has experienced significant anthropogenic alterations.
-We analyzed two institutional shifts, the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulation (98-UBR), that re-framed SES structures.
-Our counterfactual identification showed that water use in the YRB increased by 5.75\% more than expected following the 87-WAS, while the 98-UBR reduced total water use.
-These heterogeneous effects align with our marginal benefits analysis, confirming the importance of well-designed SES structures in water governance.
-Our quasi-natural experiment on the YRB highlights the need to avoid fragmented ecological units and separated social actors for sustainable water governance, while also emphasizing the significance of understanding the underlying processes and relationships in SES structures.
+     Water governance in river basins worldwide faces challenges due to complex socio-economic and environmental factors.
+In the Yellow River Basin (YRB), two major institutional shifts, the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basin Regulation (98-UBR), aimed to address water allocation and usage issues.
+This study quantifies the net effects of these institutional shifts on water use within the YRB and analyzes the underlying reasons for their success or failure.
+     We employ a Differenced Synthetic Control method to assess the impacts of the institutional shifts.
+Our analysis reveals that the 87-WAS unexpectedly increased water use by $5.75\%$, while the 98-UBR successfully reduced water use as anticipated.
+Our research highlights the role of institutional structures in governance policies, demonstrating that the mismatched structure of the 87-WAS led to increased competition and exploitation of water resources, while the 98-UBR, with its scale-matched, basin-wide authority and stronger connections between stakeholders, resulted in improved water governance.
+     Our study underscores the importance of designing institutions that are consistent with the scale of the ecological system, promote cooperation among stakeholders, and adapt to changing social-ecological system (SES) contexts.
+As outdated and inflexible water quotas may no longer meet the demands of sustainable development in the YRB, governments and policymakers must consider the potential consequences of institutional shifts and their impact on water use and sustainability.
 \end{abstract}
@@
 
-\section{INTRODUCTION}\label{sec:introduction}
+\section{Introduction}\label{sec:introduction}
 \input{01_introduction.tex}
 
-\section{MATERIALS AND METHODS}\label{sec:methods}
+\section{Study area and institutional contexts}\label{sec:yrb}
+\input{study_area.tex}
+
+\section{Methods}\label{sec:methods}
 \input{06_methods.tex}
 
-\section{RESULTS}\label{sec:results}
+\section{Results}\label{sec:results}
 \input{02_structures.tex}
@@
 
-\section{DISCUSSION}\label{sec:discussion}
+\section{Discussion}\label{sec:discussion}
 \input{04_discussion.tex}
 
-\section{CONCLUSION}\label{sec:conclusion}
+\section{Conclusion}\label{sec:conclusion}
 \input{05_conclusion.tex}
@@
 
-\section{Contexts of institutional shifts}\label{secS1}
+\section{Key points in the documents of 87-WAS and 98-UBR}\label{secS1}
 \renewcommand{\thefigure}{A\arabic{figure}}
@@
 
-\section{Robustness of DSC method}\label{secS2}
+\newpage
+\section{Data source and method details}\label{secS2}
 \renewcommand{\thefigure}{B\arabic{figure}}
@@
 
-\section{Optimization model for water use}\label{secS4}
+\newpage
+\section{Marginal benefit model for water use}\label{secS4}
 \renewcommand{\thefigure}{C\arabic{figure}}
@@
 
-\section{Model extensions}\label{secS5}
-\renewcommand{\thefigure}{D\arabic{figure}}
-\renewcommand{\thetable}{D\arabic{table}}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-\input{../02_appendix/05_model_extensions.tex}
+% \section{Model extensions}\label{secS5}
+% \renewcommand{\thefigure}{D\arabic{figure}}
+% \renewcommand{\thetable}{D\arabic{table}}
+% \setcounter{figure}{0}
+% \setcounter{table}{0}
+% \input{../02_appendix/05_model_extensions.tex}
 

### 2023-05-06 docs/papers/01_manuscript/out/compiled_v-2.0.2.tex
refactor(project): :recycle: 重构到JH的风格

@@
 The validity of our theoretical analysis is supported by two facts:
-(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019a, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
+(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) \cite{wang2019e, wang2019d}, where each province attempted to demonstrate its development potential related to water use.
 The bargaining was also a process for matching water shares to economic volume because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution) \cite{zuo2020}.
 (2) Provinces with higher current water use might have greater bargaining power in water use allocation because of information asymmetry between decision-makers and stakeholders.
-Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligned with their appeals to the higher central government for larger shares \cite{wang2019a, wang2019d}.
+Therefore, stakeholders had considerable incentives to prevent water quotas from hindering their economic potential, which aligned with their appeals to the higher central government for larger shares \cite{wang2019e, wang2019d}.
 
@@
 Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{\nameref{secS1}}) \cite{yu2019}.
-Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development \cite{wang2019a}.
+Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development \cite{wang2019e}.
 Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{\nameref{secS1}}).
@@
 Water allocation institutions are widespread in large river basin management programs throughout the world (see \textit{Appendix} Figure~\ref{fig:world}) \cite{speed2013}.
-This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level)\cite{wang2019a}:
+This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level)\cite{wang2019e}:
 \begin{itemize}
-    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wang2019, wang2019a}.
+    \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wang2019d, wang2019e}.
     \item \textbf{1987}: Implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
@@
     % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
-    \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wang2019,wang2019a}.
+    \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wang2019d,wang2019e}.
     \item \textbf{2021}: A call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).

### 2023-05-06 docs/papers/01_manuscript/study_area.tex
refactor(project): :recycle: 重构到JH的风格

@@
 The YRB was the first basin in China for which water resource allocation institutions were created, and institutional shifts can be traced through several regulating documents released by the Chinese government (at the national level):
-(1) In $1980s$, proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019, wang2019a}.
+(1) In $1980s$, proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019d, wang2019e}.
 (2) In $1987$, the Water Allocation Scheme was implemented (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
@@
 % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
-(4) In $2008$, provinces were asked to draw up new water resources plans for the YRB to further refine water allocations~\cite{wang2019,wang2019a}.
+(4) In $2008$, provinces were asked to draw up new water resources plans for the YRB to further refine water allocations~\cite{wang2019d,wang2019e}.
 (5) In $2021$, there was a call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).

### 2023-05-06 docs/papers/01_manuscript/tab_rmse.tex
refactor(project): :recycle: 重构到JH的风格

% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[!htbp]\footnotesize
	\centering
	\caption{Pre and post treatment root mean squared prediction error (RMSE) for YRB's provinces}\label{tab:DSC_summary}
	\begin{tabularx}{0.8\textwidth}{XXXXXXX}
	  \toprule
			& \multicolumn{3}{c}{87-WAS} & \multicolumn{3}{c}{98-UBR} \\
  \cmidrule{2-7}    province  & \multicolumn{1}{c}{post/pre} & To avg. & \multicolumn{1}{c}{sig.} & \multicolumn{1}{c}{post/pre} & To avg.   & \multicolumn{1}{c}{sig.} \\
	  \midrule
	  Qinghai & 5.26  & =     & FALSE & 5.89  & >     & TRUE \\
	  Gansu & 10.37  & >     & TRUE  & 9.55  & >     & TRUE \\
	  Ningxia & 5.81  & =     & FALSE & 6.83  & >     & TRUE \\
	  Inner Mongolia & 7.11  & >     & TRUE  & 1.60  & <     & TRUE \\
	  Shanxi & 1.72  & <     & TRUE  & 5.60  & >     & TRUE \\
	  Shaanxi & 3.05  & <     & TRUE  & 3.01  & >     & TRUE \\
	  Henan & 20.66  & >     & TRUE  & 1.18  & <     & TRUE \\
	  Shandong & 4.54  & =     & FALSE & 4.14  & >     & TRUE \\
	  \bottomrule
	  \end{tabularx}%
	\label{tab:addlabel}%
\end{table}%

### 2023-05-06 docs/papers/02_appendix/04_theoretical_model.tex
refactor(project): :recycle: 重构到JH的风格

@@
 
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.6\linewidth]{outputs/economic_model.pdf}
-	\caption{
-		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}~C) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}\label{fig:model}
-\end{figure}
-
-For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (case 1 to case 3, corresponding to different SES structures in Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
+For interpretation of the pattern of provincial water uses, we compared the theoretical marginal returns and optimal water use under three different structural cases (case 1 to case 3, corresponding to different SES structures in Figure~\ref{fig:structure}~C).
 
@@
 
-\paragraph{Setup}
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=0.6\linewidth]{outputs/economic_model.pdf}
+	\caption{
+		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}~C) Major water users' theoretically optimal water use is also larger (see the proofs below.)}
+\end{figure}
 
-To understand the mechanisms through which the SES structure impacts provincial water use, we developed a dynamic marginal benefits analysis to analyze how institutional mismatch could have led to the changes in water use, especially among provinces with high incentives for excess water use.
-Specifically, we modeled individual provincial decision-making in water resources before quota execution.
-
-We proposed three intuitive and general assumptions:
+Below are the detailed theoretical model derivation process, where we started from proposing three intuitive and general assumptions:
 
@@
 \end{ass}
-Under the above assumptions, we can demonstrate three cases to simulate the water use decision-making and water use patterns in a whole basin.
 
@@
  %case1
-\begin{case} Dentralized decision: This case corresponds to a situation without any high-level water allocation institution.
+\begin{case} before 1987: This case corresponds to a situation without any high-level water allocation institution.
 
@@
  %case2
- \begin{case} Mismatched institution: This case corresponds to an SES structure where fragmented stakeholders are linked to unified river reaches.
+ \begin{case} from 1987 to 1998: This case corresponds to an SES structure where fragmented stakeholders are linked to unified river reaches.
 
- The water quota is determined at $t$=0 and imposed in $t$=1,2,...
-Under the subjective expectation of each province that current water use may influence the future water allocation determined by high-level authorities, the total quota is a constant denoted as Q, and the quota for province $i$ is determined in a proportional form:
+ The water quota is determined at $t$=0 and imposed in $t$=1,2, \ldots Under the subjective expectation of each province that current water use may influence the future water allocation determined by high-level authorities, the total quota is a constant denoted as Q, and the quota for province $i$ is determined in a proportional form:
 
@@
  %case3
- \begin{case} Matched institution: This case corresponds to the institution under which water use in a basin is centrally managed.
+\begin{case} after 1998: This case corresponds to the institution under which water use in a basin is centrally managed.
 
@@
 
-Proposition 1: Compared with the decentralized institution, a matched institution with unified management decreases total water use.
+Proposition 1: Compared with the decentralized institution, a institution with unified management decreases total water use.
 
@@
 
-Extensions of the model are shown in Supplementary Material S3.%%%
-
 %Appendix的模型和proposition推导细节部分
 %放在Appendix
-Appendix: Water Use Optimization
 
 %case1
-\begin{case_appendix}Centralized decision
 
@@
 
-\end{case_appendix}
-
-%case2
- \begin{case_appendix}Decentralized decision
-
 When each of the N provinces independently decides on its water use, the marginal cost of water use would be $\frac{C}{N}$ as a result of cost-sharing with others.
@@
 Since $F'$ is monotonically decreasing, $\hat x_{it}^*>x_i^*$.
-\end{case_appendix}
-
-%case3
- \begin{case_appendix}Forward-looking decentralized decision under quota restrictions
 
@@
 The incentive of water overuse increases by A.
-\end{case_appendix}

### 2023-05-07 docs/papers/01_manuscript/manuscript.tex
fix(project): :bug: 修改提交论文格式

@@
 \usepackage{multirow}
-% \usepackage{lineno}
+\usepackage{lineno}
 \usepackage{booktabs}
@@
 % https://www.sciencedirect.com/journal/journal-of-hydrology/about/call-for-papers#grounded-sociohydrology
-\title{Quantifying the Effects of Institutional Shifts on Water Governance in the Yellow River Basin: A Socio-Hydrological Analysis}
+\title{Quantifying the Effects of Institutional Shifts on Water Governance in the Yellow River Basin: A Social-ecological System Perspective}
 
@@
 % \renewcommand\linenumberfont{\normalfont\bfseries\small}
-% \linenumbers
 \begin{abstract}
@@
 \end{frontmatter}
-
+\newpage
+\linenumbers
 \section{Introduction}\label{sec:introduction}
@@
 
-% Authors Contribution
-% SW and BF designed this research. SS performed the study and analysed data. SS and HW wrote the paper. XW, GC, and HW revised and polished the manuscript and gave significant advice.
+\textbf{Authors Contribution}\\
+Shuai Wang and BF designed this research.
+Shuang Song performed the study and analysed data.
+Shuang Song and Huiyu Wen wrote the paper.
+Xutong Wu, Cumming S.
+Graeme, and HW revised and polished the manuscript and gave significant advice.
 
-% Acknowledgments
-% This research has been supported by the National Natural Science Foundation of China (grant no. 42041007) and the Fundamental Research Funds for the Central Universities
+\textbf{Acknowledgments}\\
+This research has been supported by the National Natural Science Foundation of China (grant no. 42041007) and the Fundamental Research Funds for the Central Universities
 

### 2023-07-28 docs/papers/04_response_letter/source/editor.tex
docs(project): :building_construction: 准备开始返修

% chktex-file 46
\section*{Associate Editor}\label{editor}

\subsection*{General comments}
\RC*{} Dear Author,

\RC*{} Two reviewers have assessed your paper and identified a good potential but some flaws, with which I concur. I would particularly insist on Reviewer 1's comment on DSC method description and wording.

% 除了审稿人的意见外，我还建议根据特刊主题加强讨论。你对制度变迁后果的分析，对于社会水文学来说，确实是重要而及时的。主要基于统计定量分析的方法选择是创新的，可以更好地描述社会水文系统的变化，这是好的。要深入社会水文学，需要更多背后的故事，对推动这些变化的社会和水文过程的解释。讨论在这个方向上开辟了一些途径，但在这方面过于薄弱。我漏了一些例子。1998年以后从地表水转移到地下水取水的事实)，引语(如:(关于讨价还价的论据)，谁是主要利益相关者的准确性以及他们如何影响社会水文过程。
\RC*{} In addition to reviewers' comments, I would also recomment strengthening the discussion in light of the special issue topic. Your analysis of consequences of institutional shifts is indeed important and timely for grounded sociohydrology. The methodological choice mainly based on statistical quantitative analysis is innovative to better qualify changes in SocioHydrological systems, which is good. Going to grounded sociohydrology needs more of the story behind, explanation of the social and hydrological processes that drive these changes. The discussion opens some ways in this direction but is too weak on that regard. I missed examples (eg.\ facts describing the transfer from surface to groundwater withdrawal after 98), quotations (eg.\ on bargaining arguments), precisions of who are the dominant stakeholders and how they influence the sociohydrological process.

\RC*{} I hope you will be able and keen on revising the manuscript with these directions.

\RC*{} O. Barreteau in the name of invited editorial team

\AR*{} We hope that these revisions address the concerns raised by both reviewers. We are confident that these changes have significantly improved the quality of our manuscript and made it more relevant and valuable to the scientific community. We look forward to your further feedback and the possibility of our manuscript being accepted for publication.

### 2023-07-28 docs/papers/04_response_letter/source/reviewer_1.tex
docs(project): :building_construction: 准备开始返修

% chktex-file 1
% chktex-file 46
\section{Reviewer \#1}\label{reviewer_1}

\subsection*{Overall comments}

\RC{} This study aimed at quantifying the effect of institution shifts (policy changes) and water usage in the Yellow River Basin (YRB), using the Differenced Synthetic Control (DSC) method. The study seemed methodologically sound. The topic is interesting: it integrated the policy dimension into an assessment of a river basin in a quantitative way and could be of interest to the journal's readership. That said, I believe the manuscript needs quite a few improvements and careful revisions. Please see below.

% 感谢您认可。
% 很抱歉缺少细节，可能会使您难以完全理解我们的研究。
% 为了回应您的担忧，我们已经修改了我们的稿件，并提供了更详细的结果解释。请在下面找到我们对您的具体评论的逐条回复。
\AR{} Thank you for your valuable feedback and for acknowledging our efforts \dots

\subsection{CLEARER METHOD DESCRIPTION}\label{sec:1-1}

% 气候变化在指数中没有明确的体现，这可能是本世纪黄河流量恢复的关键因素。气候变化将是未来该流域面临的巨大挑战。重大的气候变化可能影响流域的适应能力，因此需要不同的治理策略。
\RC{} Section 3.3. Differenced Synthetic Control needs to be much clearer. For example, on lines 141-145, please double-check the description and symbols used in this passage. In particular, the multiple uses of capital letter T—as the duration of a period and as a time index—were quite confusing. Then, ``post-treatment period $T_0$.\ldots all preceding periods $T_1$'' - is this correct? Anyhow, please double-check and revise to make this passage clearer.

\AR{} Thanks for the comment that \ldots

\RC{} In Eq 1, $X_0$ and $X_1$ were never defined.

\RC{} Using ``$*$'' to denote the dimension of a matrix (e.g., $k*k$) is a bit odd; please consider using a multiplication symbol, e.g., $k \times k$.

\subsection{BETTER WORD CHOICES}\label{sec:1-2}
% 结果是总结性的。我建议提供更多关于三个指数和IWGI结果的信息。例如，三个指标的结果，以及分区域的结果。请解释IS、IP、IA和IWGI这三个指标的范围，以及不同数值的含义。这些细节可以帮助读者理解结果的合理性。
\RC{} I found some of the word choices a bit strange. For example, unless the term has been used this way in the literature, "point-axis networks" sounds strange. Otherwise, please consider alternatives like "organizational charts" or "organizational diagrams," which I believe is more appropriate.

\RC{} In a similar vein, I do not think that "network approach" or "network-based approach" is an appropriate description of what is being done here. Normally, network approaches involve concepts from complex network theories, which are not present here. Indeed, calling this a network approach may provoke unnecessary objections from network researchers. I would suggest the use of simpler terms like "analysis of the organizational charts" or something along that line.

\RC{} I disagree with how the term and concept of "robustness" is used here. Normally, a robust result is a result that holds even when the input variables and/or parameters are uncertain. What is being reported here seems to be the effectiveness or efficiency of the institutional shifts, not the robustness. If I misunderstood anything here, please clarify. As it is, I don't think that the use of the term "robustness" is appropriate here.

\RC{} Is ``placebo experiments'' the term normally used in this way? If so, can you provide some references?

\subsection{Other comments}\label{sec:1-3}
% 本研究中使用的数据似乎有不同的时间段，大多数数据来自2013年之前。近十年来，黄河的水文状况和水治理应该发生了重大变化。因此，结合近十年的结果将使这项研究更加可靠。
\RC{} I would change the first two key points into full sentences; as they are, they are only fragments, while the third and fourth points are full sentences.

\RC{} Lines 39-40: "the 1987...(98-UBR)." is repeated - please remove.

\RC{} Line 75: A subject is missing in front of "proposed to..." Perhaps, "the government"?

\RC{} Lines 169-171: "A robust synthetic control model will show a significant difference after treatment, but not before treatment." Why? This statement assumes that the treatment must have an effect; what if the treatment has no effect?

\RC{} Line 209: Are parentheses missing for ``$km^3 billion m^3$''?

\RC{} Lines 261-262: It's unclear to me how Fig. 4 supports the statement "the correlation between...98-UBR (Figure 4)."

\RC{} Somehow, I did not see Appendix C explicitly referred to in the main text. There is reference to "Marginal benefit model for water use" but this was not explicitly labeled as Appendix C.

\RC{} Line 280: "Similar" -> "Similarly"

\RC{} Line 323-324: This is the first time you used the term "difference-in-differences" - so far, you have called your method "Differenced Synthetic Control" (DSC). Why different names? Likely a typo; please double-check.

\RC{} Line 327: "revealed" is too strong; perhaps "suggested"?

\RC{} Line 437, Ref [30]: Pca should be all caps, PCA.\

### 2023-07-28 docs/papers/04_response_letter/source/reviewer_2.tex
docs(project): :building_construction: 准备开始返修

\section{Reviewer \#2}\label{reviewer_2}

\subsection*{Overall comments}
% 本研究考察了黄河流域87-WAS和98-UBR两种制度变迁对水治理的影响。结果表明，87-WAS导致用水量增加，98 UBR由于其在流域范围内的权威和利益相关者之间更强的联系而成功地减少了用水量。建议根据生态规模进行制度设计，促进不同参与方的合作，并进行相应的调整。政府和决策者必须分析政策变化对水的使用和可持续性的影响。作者采用了新开发的在AER上发表的合成差中差。这篇论文写得很好，结构也很好。然而，这种方法对于水研究人员来说是全新的。我有几点建议，希望作者在改稿中进一步考虑。
\RC{} This study examines the effects of two institutional shifts in Water Governance for the Yellow River Basin - 87-WAS and 98-UBR. Results show that while 87-WAS led to an increased water use, 98 UBR successfully reduced it due to its basin wide authority and stronger connections between stakeholders. It is suggested that institutions should be designed according to ecological scale, promote cooperation with different parties involved, as well as adapting themselves accordingly. Governments and policymakers must analyze the effects of changes in policy on water usage and sustainability. The author adopted the newly developed Synthetic Difference-in-Differences published on AER. This paper is well written and strutured. However, this method is completely new to the researcher on water study. I have several suggestions wish the authors further consider them in the revised manuscript.

\AR{} We appreciate your acknowledgement of the reasonable and adaptable methodology used in this study, as well as the useful insights provided by the case analysis. We agree that the discussion could be more supportive and solid in its content of the results and we will work to revise the manuscript accordingly. Please find our point-by-point response to your specific comments below.

\subsection{\#1 Method}
% 图1:很难理解B中每个数字的含义。也许是这个数字的大小有问题。
\RC{}  It is suggested that the principle behind Differenced Synthetic Control, as well as the process for selecting treatment and control groups and conducting synthetic control, be explained using more accessible language. Currently, the explanation is too abstract and may be difficult for most readers of the journal to understand. To further expand on the suggestion, using more accessible language would involve breaking down complex ideas and jargon into simpler terms that are easier for readers to understand. This could involve providing more concrete examples and explanations, and avoiding technical terminology that may not be familiar to a general audience. Additionally, it may be helpful to provide step-by-step instructions or diagrams to illustrate the process of selecting treatment and control groups and conducting synthetic control. By doing so, readers who may not be familiar with the topic can more easily understand and appreciate the content of the journal.

\AR{} Thanks for the comment. We now improved the figure size in the revised manuscript.

\subsection{\#2 Robustness}\label{sec:2-2}
% 导言:与流域和水资源相关的指标有很多，其中一些指标具有与治理和政策相关的参数。为了突出你所制定的IWGI的新颖性，也许你可以加上对其他相关指标的审查。
\RC{} I'm glad to see that you have included a couple of robustness checks. However, there are several more details related to Differenced Synthetic Control that need to be tested. These may include testing for the sensitivity of the results to changes in the choice of control group, the inclusion or exclusion of certain covariates, and the specification of the synthetic control model. Other possible robustness checks may involve testing for heterogeneity of treatment effects across different subgroups or time periods, and assessing the impact of outliers or influential observations on the results.

\AR{} Thanks for valuable suggestion. We now added a whole paragraph to the introduction:

\subsection{\#3 Results and discussion}\label{sec:2-3}
% 方程:方程(7)中的CEM是什么?还有，水的比例指的是什么?支持信息中公式(2)中的一些术语没有解释。例如:R或WU。
\RC{} The results, discussion, and comparisons are comprehensive, and I have no further comments at this time.

\AR{} Thanks for the comment. ``CEM'' should be ``AEM'' -the indicator we applied for IA.\ This has been revised in the new manuscript:

### 2023-07-28 docs/papers/01_manuscript/06_methods.tex
fix(method): :memo: a better description of DSC method.

@@
 In practice, all treated units (i.e., provinces) were affected by institutional shifts in 1987 and 1998, each taken as the ``shifted'' time $t_0$ within two individually analyzed periods $T$: from 1979 to 1998; from 1987 to 2008.
-We include each province in the YRB ($n=8$, see \textit{\nameref{sec:dataset}}) as the treated unit separately, as multiple treated units approach had been widely applied~\cite{abadie2021}.
-Then, we consider the $J+1$ units observed in time periods $T = {1,2 \cdots , T}$ with the remaining $J=20$ units are untreated provinces from outside.
+We separately include each of the eight provinces in the YRB (see \textit{\nameref{sec:dataset}}) as individual treated units~\cite{abadie2021}.
+Then, we consider the $J+1$ units observed in time periods $T = {1, 2, \ldots, t}$ where the remaining $J=20$ units represent untreated provinces from outside the YRB.
 We define $T_0$ to represent the number of pre-treatment periods ($1,\ldots,t_0$) and $T_1$ the number post-treatment periods ($t_0, \ldots, T$), such that $T = T_0+ T_1$.
-The treated unit is exposed to the institutional shift in every post-treatment period $T_0$, unaffected by the institutional shift in all preceding periods $T_1$.
-Then, any weighted average of the control units is a synthetic control and can be represented by a ($J * 1$) vector of weights $\mathbf{W} = (w_{1}, \ldots ,w_{J})$, with $w_j \in (0, 1)$.
-Among them, by introduce a ($k * k$) diagonal, matrix $\mathbf{V}$ that signifies the relative importance of each covariant, the DSC method procedure for finding the optimal synthetic control ($W$) is expressed as follows:
+The treated unit is exposed to the institutional shift in every post-treatment period $T_1$, unaffected by the institutional shift in all preceding periods $T_0$.
+Then, any weighted average of the control units is a synthetic control and can be represented by a ($J \times 1$) vector of weights $\mathbf{W} = (w_{1}, \ldots ,w_{J})$, with $w_j \in (0, 1)$.
+Among them, by introduce a ($k \times k$) diagonal, matrix $\mathbf{V}$ that signifies the relative importance of each variable, the DSC method procedure for finding the optimal synthetic control ($\mathbf{W}$) is expressed as follows:
 
@@
 
-where $\mathbf{W}^{*}(V)$ is the vector of weights $\mathbf{W}$ that minimizes the difference between the pre-treatment characteristics of the treated unit and the synthetic control, given $\mathbf{V}$.
+where $X_1$ is the pre-treatment average of each variable in the dataset for the treated unit, while $X_0$ is a ($k \times J$) containing the pre-treatment characteristics for each of the $J$ control units; $\mathbf{W}^{*}(V)$ is the vector of weights $\mathbf{W}$ that minimizes the difference between the pre-treatment characteristics of the treated unit and the synthetic control, given $\mathbf{V}$.
 That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W*(V)}$.
@@
 
-That is the minimum difference between the outcome of the treated unit and the synthetic control in the pre-treatment period, where $\mathbf{Z}_{1}$ is a ($1*T_0$) matrix containing every observation of the outcome for the treated unit in the pre-treatment period.
-Similarly, let $\mathbf{Z}_{0}$ be a ($k * T_0$) matrix containing the outcome for each control unit in the pre-treatment period, and $k$ is the number of variables in the datasets.
+That is the minimum difference between the water uses of treated units and the synthetic controls in the pre-treatment period, where $\mathbf{Z}_{1}$ is a matrix containing every observation of the water use for the treated unit in the pre-treatment period $T_0$.
+Similarly, $\mathbf{Z}_{0}$ is a ($k \times T_0$) matrix contains the water use for each control unit in the pre-treatment period, and $k$ is the number of variables in the datasets.
+In this study, we adopted the minimization by the ``Synthetic Control Methods'' Python library (version 1.1.17)~\cite{engelbrektson2023}.
+
 The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with double robustness properties~\cite{billmeier2013, smith2015}.

### 2023-07-28 docs/papers/04_response_letter/source/reviewer_1.tex
fix(method): :memo: a better description of DSC method.

@@
 
+% \RC{}本研究旨在利用差分综合控制(DSC)方法量化黄河流域(YRB)制度变迁(政策变化)和水资源利用的影响。这项研究在方法上似乎是合理的。这个话题很有趣:它以定量的方式将政策维度整合到对流域的评估中，可能会引起期刊读者的兴趣。也就是说，我认为手稿需要相当多的改进和仔细的修改。请参阅下文。
 \RC{} This study aimed at quantifying the effect of institution shifts (policy changes) and water usage in the Yellow River Basin (YRB), using the Differenced Synthetic Control (DSC) method.
@@
 
-% 感谢您认可。
-% 很抱歉缺少细节，可能会使您难以完全理解我们的研究。
-% 为了回应您的担忧，我们已经修改了我们的稿件，并提供了更详细的结果解释。请在下面找到我们对您的具体评论的逐条回复。
 \AR{} Thank you for your valuable feedback and for acknowledging our efforts \dots
@@
 
-% 气候变化在指数中没有明确的体现，这可能是本世纪黄河流量恢复的关键因素。气候变化将是未来该流域面临的巨大挑战。重大的气候变化可能影响流域的适应能力，因此需要不同的治理策略。
 \RC{} Section 3.3.
@@
 
-\AR{} Thanks for the comment that \ldots
-
 \RC{} In Eq 1, $X_0$ and $X_1$ were never defined.
@@
 \RC{} Using ``$*$'' to denote the dimension of a matrix (e.g., $k*k$) is a bit odd; please consider using a multiplication symbol, e.g., $k \times k$.
+
+\AR{} We have revised the description of the DSC method to make it clearer and more comprehensive.
+We expanded on the purpose and process of the DSC method, provided more context on how it fits into our research, and clarified the mathematical notation.
+We also explained the specific variables used when we introduced $X_1, X_0, Z_1$, and $Z_0$, as well as mentioned the specific method used for minimization and the corresponding reference.
+We believe that these revisions have significantly improved the clarity of our method description:
+
+\begin{quote}[page=XXX, sline=XXX, eline=XXX]
+    Modification \dots
+\end{quote}
+
+\AR*{} We are grateful for your insightful feedback, which has helped us improve the quality of our manuscript. We hope that our revisions have addressed all your concerns satisfactorily.
 

### 2023-07-28 docs/papers/01_manuscript/06_methods.tex
fix(method): :memo: change expression: point-axis networks -> organization diagram

@@
 \subsection{Portraying structures}\label{sec:structures}
-A point-axis network type structure of SES is widely used to depict them by abstracting links and nodes~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
-We apply the network approach~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit at the basin scale (the Yellow River Conservancy Commission) into structural patterns from official documents.
+
+An organizational diagram is widely used to depict SES structures by abstracting links and nodes from the real-world interactions~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
+We apply the analysis of the organizational diagrams~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit at the basin scale (the Yellow River Conservancy Commission) into structural patterns from official documents.
 The network-based approach abstracts connections between entities into links according to their interactions~\cite{bodin2017a,kluger2020,guerrero2015}, so we examined the official documents of the two institutional shifts (87-WAS and 98-UBR) to portray these interactions in this study.

### 2023-07-28 docs/papers/04_response_letter/source/reviewer_1.tex
fix(method): :memo: change expression: point-axis networks -> organization diagram

@@
 \subsection{BETTER WORD CHOICES}\label{sec:1-2}
-% 结果是总结性的。我建议提供更多关于三个指数和IWGI结果的信息。例如，三个指标的结果，以及分区域的结果。请解释IS、IP、IA和IWGI这三个指标的范围，以及不同数值的含义。这些细节可以帮助读者理解结果的合理性。
+
 \RC{} I found some of the word choices a bit strange.
@@
 
-\RC{} In a similar vein, I do not think that "network approach" or "network-based approach" is an appropriate description of what is being done here.
+\AR{} Thank you once again for your valuable insights and suggestions.
+
+\AR*{} Regarding your comment on our use of the term ``point-axis networks'', we appreciate your feedback.
+The term was indeed referenced from a review article (\cite{kluger2020}), and we initially used it believing it was a common term in the literature.
+However, upon your suggestion and further consideration, we agree that the term may not be widely recognized across our readership.
+
+\AR*{} We have therefore revised the relevant sentence to use the term ``organizational diagram'', which is indeed more familiar and equally accurate. The sentence now reads:
+
+\begin{quote}[page=XXX, sline=XXX, eline=XXX]
+    An organizational diagram is widely used to depict SES structures by abstracting links and nodes from the real-world interactions~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
+\end{quote}
+
+\RC{} In a similar vein, I do not think that ``network approach'' or ``network-based approach'' is an appropriate description of what is being done here.
 Normally, network approaches involve concepts from complex network theories, which are not present here.
 Indeed, calling this a network approach may provoke unnecessary objections from network researchers.
-I would suggest the use of simpler terms like "analysis of the organizational charts" or something along that line.
+I would suggest the use of simpler terms like ``analysis of the organizational charts'' or something along that line.
 
-\RC{} I disagree with how the term and concept of "robustness" is used here.
+\RC{} I disagree with how the term and concept of ``robustness'' is used here.
 Normally, a robust result is a result that holds even when the input variables and/or parameters are uncertain.
@@
 If I misunderstood anything here, please clarify.
-As it is, I don't think that the use of the term "robustness" is appropriate here.
+As it is, I don't think that the use of the term ``robustness'' is appropriate here.
 

### 2023-07-28 docs/papers/01_manuscript/06_methods.tex
fix(method): :memo: expression of "network approach"

@@
 
-In the methodology section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as point-axis networks during different periods of time.
+In the methodology section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as organizational diagrams during different periods of time.
 Next, we introduce the dataset we used here and employ the Principal Components Analysis (PCA) method to reduce the dimensionality of variables affecting the total water use.
@@
 We apply the analysis of the organizational diagrams~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit at the basin scale (the Yellow River Conservancy Commission) into structural patterns from official documents.
-The network-based approach abstracts connections between entities into links according to their interactions~\cite{bodin2017a,kluger2020,guerrero2015}, so we examined the official documents of the two institutional shifts (87-WAS and 98-UBR) to portray these interactions in this study.
+We examined the official documents of the two institutional shifts (87-WAS and 98-UBR) to portray the organizational diagrams in this study~\cite{bodin2017a,kluger2020,guerrero2015}.
 It is important to note that it can result in very different structures when basin-scale regulatory entity (YRCC) is responsible for river reach regulation, or have direct authority to interact with provincial units.

### 2023-07-28 docs/papers/04_response_letter/source/reviewer_1.tex
fix(method): :memo: expression of "network approach"

@@
 
-\AR{} Thank you for your valuable feedback and for acknowledging our efforts \dots
+\AR{} Thank you for your valuable feedback and for acknowledging our efforts \dots.
+Your feedback greatly helps us improve the clarity and accessibility of our work.
+We sincerely appreciate your effort in reviewing our manuscript and providing these insightful comments.
 
@@
 \begin{quote}[page=XXX, sline=XXX, eline=XXX]
+    In the methodology section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as organizational diagrams during different periods of time.
+\end{quote}
+
+\begin{quote}[page=XXX, sline=XXX, eline=XXX]
     An organizational diagram is widely used to depict SES structures by abstracting links and nodes from the real-world interactions~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
@@
 I would suggest the use of simpler terms like ``analysis of the organizational charts'' or something along that line.
+
+\AR{} Thank you for your thoughtful suggestion to use the term ``analysis of the organizational charts''.
+We agree that this term is clearer and more widely understood.
+We have incorporated your suggestion into our manuscript.
+We believe this modification has improved the clarity and readability of our manuscript, making it more accessible to our readers:
+
+\begin{quote}[page=XXX, sline=XXX, eline=XXX]
+    We apply the analysis of the organizational diagrams~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit at the basin scale (the Yellow River Conservancy Commission) into structural patterns from official documents.
+    We examined the official documents of the two institutional shifts (87-WAS and 98-UBR) to portray the organizational diagrams in this study~\cite{bodin2017a,kluger2020,guerrero2015}.
+\end{quote}
 

### 2023-07-28 docs/papers/01_manuscript/06_methods.tex
fix(method): :memo: expression "robustness" and "placebo"

@@
 We then estimate the net effects of the two institutional shifts on total water use, changing trends, and differences in the YRB's provinces using the Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021}.
-Finally, we present the robustness tests approach for the DSC model.
+Finally, we present the efficiency tests approach for the DSC model.
 % Finally, for discussion, we developed a marginal benefit analysis based on identified SES structures to provide the observed pattern of water use changes with a theoretical interpretation.
@@
 Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ principal components.
-Previous study has proved that combining PCA and DSC can raise the robustness of causal inference~\cite{bayani2021}.
+Previous study has proved that combining PCA and DSC can lead to a more robust causal inference~\cite{bayani2021}.
 We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different.
@@
 Similarly, $\mathbf{Z}_{0}$ is a ($k \times T_0$) matrix contains the water use for each control unit in the pre-treatment period, and $k$ is the number of variables in the datasets.
+The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with better robustness~\cite{billmeier2013, smith2015}.
 In this study, we adopted the minimization by the ``Synthetic Control Methods'' Python library (version 1.1.17)~\cite{engelbrektson2023}.
 
-The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with double robustness properties~\cite{billmeier2013, smith2015}.
+\subsection{Efficiency tests of the DSC}\label{sec:robustness}
 
-\subsection{Robustness analysis}\label{sec:robustness}
-
-Two primary methods can be employed to test the robustness of the DSC approach.
+Two primary methods can be employed to test the efficiency of the DSC approach.
 
@@
 % If the significance level of the $T$ test before institutional intervention is greater than the threshold value, it means that the DSC model successfully predicted the change in water consumption in this region over time before institutional intervention, indicating a good fit.
-A robust synthetic control model will show a significant difference after treatment but not before treatment.
+An effective synthetic control model will show a significant difference after treatment but not before treatment.
 
-Secondly, placebo experiments are another common way to evaluate the effectiveness of synthetic control methods.
+Secondly, placebo tests are another common way to evaluate the effectiveness of synthetic control methods~\cite{abadie2010}.
 Placebo units are selected from the control unit pool and substituted for the treated unit, applying the synthetic control method to the placebo unit using the same data and parameters as the treated unit.
@@
 In this study, we adopt the placebo test step suggested by Abadie when proposing the synthetic control method~\cite{abadie2010} and utilize the Python library of the differential synthetic control method for the placebo test.
-If the ratio of the root mean square error (see Equation~\ref{ch5:eq:RMSE}) in the pre-synthesis period is significantly higher for most provinces (again using the $T$ test to determine the significance of the difference) than the results of other placebo units, it would suggest that the Yellow River Basin was more significantly affected than most other provinces during the treatment periods ($1987$ and $1998$), i.e., the results are more robust.
+If the ratio of the root mean square error (see Equation~\ref{ch5:eq:RMSE}) in the pre-synthesis period is significantly higher for most provinces (again using the $T$ test to determine the significance of the difference) than the results of other placebo units, it would suggest that the Yellow River Basin was more significantly affected than most other provinces during the treatment periods ($1987$ and $1998$), i.e., more effective.
 

### 2023-07-28 docs/papers/04_response_letter/source/reviewer_1.tex
fix(method): :memo: expression "robustness" and "placebo"

@@
 
+\AR{} Regarding your suggestion on the usage of the term ``robustness'', we have reconsidered our choice of words and agree with your point.
+We understand that the term ``efficiency'' more accurately represents our intended meaning in this context.
+Therefore, we have revised our manuscript and replaced ``robustness'' with ``efficiency''.
+We believe this change improves the clarity and precision of our work:
+
+\begin{quote}[page=XXX, sline=XXX, eline=XXX]
+    Two primary methods can be employed to test the efficiency of the DSC approach.
+\end{quote}
+
+\begin{quote}[page=XXX, sline=XXX, eline=XXX]
+    An effective synthetic control model will show a significant difference after treatment but not before treatment.
+\end{quote}
+
+\begin{quote}[page=XXX, sline=XXX, eline=XXX]
+    \dots it would suggest that the Yellow River Basin was more significantly affected than most other provinces during the treatment periods ($1987$ and $1998$), i.e., more effective.
+\end{quote}
+
+\AR*{} Thank you once again for your valuable feedback, which has greatly contributed to the quality of our manuscript.
+
 \RC{} Is ``placebo experiments'' the term normally used in this way? If so, can you provide some references?
+
+\AR{} Basically, yes, ``Placebo'' is a term.
 

### 2023-07-28 docs/papers/04_response_letter/source/reviewer_1.tex
fix(method): :memo: "placebo test"

@@
 
-\AR{} Basically, yes, ``Placebo'' is a term.
+\AR{} Basically, the term ``placebo'' is indeed used in this context in the literature, particularly in policy evaluation studies where the synthetic control method is used.
+It refers to the procedure of applying the synthetic control method to units that did not receive treatment to verify the significance of the estimated treatment effects.
+This procedure is called a ``placebo test'' or ``placebo experiment'' and is crucial for validating the results of synthetic control analyses.
+
+\AR*{} In light of your comment, we have revised our manuscript to consistently use the term ``placebo tests'' throughout, and we have added references that use this term in a similar context~\cite{abadie2010}.
+We hope this change addresses your concern and provides a clear explanation of the term's usage:
+
+\begin{quote}[page=XXX, sline=XXX, eline=XXX]
+    Secondly, placebo tests are another common way to evaluate the effectiveness of synthetic control methods~\cite{abadie2010}.
+\end{quote}
 
 \subsection{Other comments}\label{sec:1-3}
-% 本研究中使用的数据似乎有不同的时间段，大多数数据来自2013年之前。近十年来，黄河的水文状况和水治理应该发生了重大变化。因此，结合近十年的结果将使这项研究更加可靠。
+
 \RC{} I would change the first two key points into full sentences; as they are, they are only fragments, while the third and fourth points are full sentences.

### 2023-07-28 docs/papers/01_manuscript/04_discussion.tex
fix(project): :pencil2: fix minor comments with typos.

@@
 On the other hand, since the YRCC could coordinate stakeholders by water quota licenses according to water conditions for the entire YRB after 98-UBR, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)~\cite{krieger1955, ostrom1990}.
-Similar, proportional decreased water use of provinces and the theoretical minimal water use of marginal benefit model indicated this policy lead to successful governance as expected (see \nameref{result-3}).
+Similarly, proportional decreased water use of provinces and the theoretical minimal water use of marginal benefit model indicated this policy lead to successful governance as expected (see \nameref{result-3} and \textit{Appendix~\nameref{secS4}}).
 However, since the 98-UBR only regulated surface water use, many clues suggested the institution shift may cause broader influences, including estimated increased groundwater withdrawals after 98-UBR in many intensive water use regions~\cite{sun2022b}.

### 2023-07-28 docs/papers/01_manuscript/05_conclusion.tex
fix(project): :pencil2: fix minor comments with typos.

@@
 In this study, we examined the effects of two major institutional shifts in water governance within the Yellow River Basin (YRB): the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basin Regulation (98-UBR).
-By employing a Difference-in-Differences approach with Synthetic Control, we quantified the net effects of these institutional shifts on water use within the YRB.\
+By employing a Differenced Synthetic Control (DSC) approach, we quantified the net effects of these institutional shifts on water use within the YRB.\
 Our results showed that the 87-WAS unexpectedly increased water use by $5.75\%$, contrary to its intended goals, while the 98-UBR successfully reduced water use as anticipated.
-The analysis revealed that the structural patterns of the institutions played a critical role in their effectiveness.
+The analysis suggested that the structural patterns of the institutions played a critical role in their effectiveness.
 The mismatched structure of the 87-WAS led to increased competition and exploitation of water resources, while the 98-UBR, with its scale-matched, basin-wide authority and stronger connections between stakeholders, resulted in improved water governance.

### 2023-07-28 docs/papers/01_manuscript/06_methods.tex
fix(method): :memo: "placebo test"
fix(project): :pencil2: fix minor comments with typos.

@@
 
-\subsection{Efficiency tests of the DSC}\label{sec:robustness}
+\subsection{Validating results}\label{sec:robustness}
 
-Two primary methods can be employed to test the efficiency of the DSC approach.
+Two primary methods can be employed to validate the efficiency of the DSC approach.
 
@@
 In this study, to determine whether the intervention effect is significant, the paired sample $T$ test is used to calculate statistics, comparing the model predictions and actual observation data in the periods before and after institutional interventions for both the 87-WAS in $1987$ and 98-UBR in $1998$.
-% If the $p$ value after the policy intervention is less than the threshold value ($0.05$), the null hypothesis $H_0$ of no significant difference can be rejected, and it is believed that the institutional intervention has significantly changed the water consumption in this region.
-% If the significance level of the $T$ test before institutional intervention is greater than the threshold value, it means that the DSC model successfully predicted the change in water consumption in this region over time before institutional intervention, indicating a good fit.
-An effective synthetic control model will show a significant difference after treatment but not before treatment.
+A valid result would be one where a significant difference is observed after treatment but not before treatment.
+If this is not the case, it implies that the institutional changes were ineffective for the treated units.
 

### 2023-07-28 docs/papers/01_manuscript/manuscript.tex
fix(project): :pencil2: fix minor comments with typos.

@@
 
+\textbf{Declaration of generative AI and AI-assisted technologies in the writing process}
+
+During the preparation of this work the authors used ChatGPT 4.0 in order to polish sentences.
+After using this tool/service, the authors reviewed and edited the content as needed and take full responsibility for the content of the publication.
+
 \bibliography{../mybib}

### 2023-07-28 docs/papers/04_response_letter/source/reviewer_1.tex
fix(project): :pencil2: fix minor comments with typos.

@@
 
-\RC{} Lines 39-40: "the 1987...(98-UBR)." is repeated - please remove.
+\AR{} Thank you for your valuable suggestion to rewrite the key points as full sentences.
+We appreciate your attention to detail and agree that full sentences are more informative and complete.
+We have revised the key points in our manuscript as follows:
 
-\RC{} Line 75: A subject is missing in front of "proposed to..." Perhaps, "the government"?
+\begin{quote}[page=Key Points]
+    1.	We assess the impact of institutional shifts in water governance at basin scale.\\
+    2.	We conduct a quantitative analysis of Yellow River Basin's water management policies.\\
+    3.	Water Allocation Scheme in 1987 unexpectedly increased water use by 5.75\%.\\
+    4.	Unified Basin Regulation in 1998 successfully reduced water use as anticipated.\\
+\end{quote}
 
-\RC{} Lines 169-171: "A robust synthetic control model will show a significant difference after treatment, but not before treatment." Why?
+\RC{} Lines 39-40: ``the 1987\ldots (98-UBR).'' is repeated -please remove.
+
+\AR{} Thank you for pointing out the repetition in lines 39-40 regarding ``the 1987\ldots (98-UBR).'' We appreciate your careful attention to detail.
+This repetition was indeed an oversight on our part.
+We have now corrected this error by removing the duplicate phrase in our manuscript.
+
+\RC{} Line 75: A subject is missing in front of ``proposed to\ldots '' Perhaps, ``the government''?
+
+\AR{} Thank you for your attentive reading of our manuscript and for pointing out the missing subject in line 75.
+Upon your suggestion, we have revised the sentence to specify the subject, now reading:
+
+\begin{quote}[page=XXX, sline=XXX, eline=XXX]
+    In $1980s$, the central government proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019d, wang2019e}.
+\end{quote}
+
+\RC{} Lines 169-171: ``A robust synthetic control model will show a significant difference after treatment, but not before treatment.'' Why?
 This statement assumes that the treatment must have an effect; what if the treatment has no effect?
+
+\AR{} Thank you for your valuable comment regarding the clarification needed for the statement in lines 169-171.
+Upon your suggestion, we have revised the sentence for better clarity, and it now reads:
+
+\begin{quote}
+    A valid result would be one where a significant difference is observed after treatment but not before treatment.
+If this is not the case, it implies that the institutional changes were ineffective for the treated units.
+\end{quote}
 
@@
 
+\AR{} Thank you for pointing out the typo in line 209 regarding units.
+Your careful attention to detail is greatly appreciated.
+We have now corrected this typographical error in our manuscript by deleting the redundant unit:
+
+\begin{quote}
+    From 1988 to 1998, on average, while the estimation of annual water use only suggests $887.05$ billion $m^3$, the observed water use of the YRB provinces reached $938.06$ billion $m^3$ (an increase of $5.75\%$).
+\end{quote}
+
 \RC{} Lines 261-262: It's unclear to me how Fig. 4 supports the statement "the correlation between...98-UBR (Figure 4)."
+
+\AR{} Thank you for pointing out the confusion in the reference to Figure 4 in lines 261-262.
+We have now deleted this not consistently reference.
+We value your insightful feedback and thank you for helping us improve the clarity and accuracy of our manuscript.
 
@@
 
+\AR{} Thank you for pointing out the missing reference to Appendix C in our manuscript.
+We appreciate your attention to detail.
+Upon revisiting the manuscript, we realized that Appendix C was indeed not explicitly referred to in the main text.
+We have now rectified this oversight by adding an explicit reference to Appendix C where the ``Marginal benefit model for water use'' is discussed:
+
+\begin{quote}
+    Similarly, proportional decreased water use of provinces and the theoretical minimal water use of marginal benefit model indicated this policy lead to successful governance as expected (see \nameref{result-3} and \textit{Appendix~\nameref{secS4}}).
+\end{quote}
+
 \RC{} Line 280: "Similar" -> "Similarly"
+\AR{} Thank you for pointing out the typographical error in line 280. We have corrected the error by changing "Similar" to "Similarly" as you suggested.
 
@@
 
+\AR{} Upon your suggestion, we have rectified the error and now consistently use the term ``Differenced Synthetic Control'' (DSC) throughout the manuscript, ensuring the consistency and clarity of our terminology.
+
 \RC{} Line 327: "revealed" is too strong; perhaps "suggested"?
+\AR{} Thank you for pointing out the excessive use of the term "revealed" in line 327.
+We appreciate your thoughtful suggestion to soften the language.
+We have now replaced "revealed" with the more appropriate term "suggested" in our manuscript.
 
 \RC{} Line 437, Ref [30]: Pca should be all caps, PCA.\
+\AR{} Thank you for bringing to our attention the typographical error in line 437, reference [30].
+We appreciate your meticulous review of our manuscript.
+We have corrected the error by capitalizing the acronym "PCA".
+This has improved the accuracy and professionalism of our reference list.

### 2023-07-29 docs/papers/01_manuscript/06_methods.tex
docs(method): :memo: improve description of DSC

@@
 \subsection{Differenced Synthetic Control}\label{sec:DSC}
-Using the Differenced Synthetic Control (DSC) method, we can estimate water use under the scenarios of no institutional shift.
-The DSC method is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit~\cite{abadie2010, abadie2015, hill2021}.
-This approach enables us to establish a counterfactual basis for exploring the consequences and incentives related to policy changes.
 
-This method aims to evaluate the effects of policy change that are not random across units but focuses on some of them (i.e., institutional shifts in the YRB here).
-By re-weighting units to match the pre-trend for the treated and control units, the DSC method imputes post-treatment control outcomes for the treated units by constructing a synthetic version of the treated units equal to a convex combination of control units.
-Therefore, the synthetic and actual version difference can be estimated as a net effect for a treated unit.
+The Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021} is a tool we use to estimate how water use might have evolved if there had been no institutional shift.
+Think of it as creating an alternate reality or a ``what-if'' scenario to compare with what actually happened~\cite{abadie2010, abadie2015, hill2021}.
+The key idea behind this method is to evaluate the effects of policy changes that mainly affect certain units (in this case, the institutional shifts in the Yellow River Basin or YRB).
+The method creates a ``synthetic'' version of the affected units by combining information from other similar but unaffected units.
+This ``synthetic'' version serves as a control group, which we can compare with the actual affected units.
+The DSC method, therefore, is a powerful tool as it allows us to control for unobserved factors that can change over time, providing more robust results.
 

### 2023-07-29 docs/papers/04_response_letter/source/reviewer_2.tex
docs(method): :memo: improve description of DSC

@@
 \subsection{\#1 Method}
-% 图1:很难理解B中每个数字的含义。也许是这个数字的大小有问题。
+
 \RC{}  It is suggested that the principle behind Differenced Synthetic Control, as well as the process for selecting treatment and control groups and conducting synthetic control, be explained using more accessible language.
@@
 
-\AR{} Thanks for the comment. We now improved the figure size in the revised manuscript.
+\AR{} Thank you for your insightful suggestion on making the Differenced Synthetic Control (DSC) method explanation more accessible to a wider audience.
+We understand the importance of making our methodology clear to all readers, not just those with a strong background in statistical analysis.
+We have revised the section accordingly, breaking down complex ideas into simpler terms, providing concrete examples, and avoiding jargon.
+We believe these changes make the methodology more accessible to a broader audience.
+Your suggestion greatly helped us improve the clarity and accessibility of our methodology description:
+
+\begin{quote}
+    The Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021} is a tool we use to estimate how water use might have evolved if there had been no institutional shift.
+    Think of it as creating an alternate reality or a ``what-if'' scenario to compare with what actually happened~\cite{abadie2010, abadie2015, hill2021}.
+    The key idea behind this method is to evaluate the effects of policy changes that mainly affect certain units (in this case, the institutional shifts in the Yellow River Basin or YRB).
+    The method creates a ``synthetic'' version of the affected units by combining information from other similar but unaffected units.
+This ``synthetic'' version serves as a control group, which we can compare with the actual affected units.
+    The DSC method, therefore, is a powerful tool as it allows us to control for unobserved factors that can change over time, providing more robust results.
+\end{quote}
 
@@
 
-\AR{} Thanks for the comment. ``CEM'' should be ``AEM'' -the indicator we applied for IA.\ This has been revised in the new manuscript:
+\AR{} We are glad that you found our results, discussion, and comparisons comprehensive. We appreciate your time and effort in reviewing our manuscript.

### 2023-07-29 docs/papers/04_response_letter/source/reviewer_2.tex
fix(project): :adhesive_bandage: response to reviewer #2

@@
 \subsection{\#2 Robustness}\label{sec:2-2}
-% 导言:与流域和水资源相关的指标有很多，其中一些指标具有与治理和政策相关的参数。为了突出你所制定的IWGI的新颖性，也许你可以加上对其他相关指标的审查。
+
 \RC{} I'm glad to see that you have included a couple of robustness checks.
@@
 
-\AR{} Thanks for valuable suggestion. We now added a whole paragraph to the introduction:
+\AR{} We appreciate your thoughtful suggestion about additional robustness checks for our Differenced Synthetic Control (DSC) method.
+However, we have chosen not to include further robustness checks in our revised manuscript for several reasons:
+
+\AR*{} Firstly, our primary objective in this paper is not to conduct a precisely quantitative assessment.
+Rather, we aim to uncover the interesting differential responses underlying the two different institutional shifts.
+As you pointed out, readers of our paper might not expect an overload of technical details.
+To maintain conciseness and avoid overwhelming our readers, we have chosen to limit the number of methodologies we include.
+
+\AR*{} Secondly, the two approaches we have employed were recommended by the developers of the DSC method~\cite{engelbrektson2023}.
+The corresponding algorithms have been provided and are consistent with the DSC method.
+If we were to introduce further tests, we might have to develop our own algorithms.
+This could potentially lead to inconsistencies and might confuse readers who wish to apply our methods in their own work.
+
+\AR*{} Lastly, in response to a suggestion from another reviewer, we have revised the terminology from ``robustness'' to ``efficiency''.
+We believe this terminology better communicates our intentions and the nature of our methodology to readers, reducing the need for additional emphasis on robustness.
+
+\AR*{} We believe these reasons justify our decision.
+However, we appreciate your suggestion and will certainly keep it in mind for future research where more extensive robustness checks may be more appropriate.
 
 \subsection{\#3 Results and discussion}\label{sec:2-3}
-% 方程:方程(7)中的CEM是什么?还有，水的比例指的是什么?支持信息中公式(2)中的一些术语没有解释。例如:R或WU。
+
 \RC{} The results, discussion, and comparisons are comprehensive, and I have no further comments at this time.
 
-\AR{} We are glad that you found our results, discussion, and comparisons comprehensive. We appreciate your time and effort in reviewing our manuscript.
+\AR{} Thank you for your positive feedback on the comprehensiveness of the results, discussion, and comparisons in our paper.
+We're delighted to hear that you found this section satisfactory.
+Your kind words are greatly encouraging and motivate us to continue to improve our work.
+We hope that the revisions we have made in response to your helpful suggestions have improved the manuscript.

### 2023-07-29 docs/papers/01_manuscript/06_methods.tex
fix(method): :ambulance: fixed problems with GUA's help

@@
 
-Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ principal components.
+Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $D = 5$ principal components.
 Previous study has proved that combining PCA and DSC can lead to a more robust causal inference~\cite{bayani2021}.
@@
 
-In practice, all treated units (i.e., provinces) were affected by institutional shifts in 1987 and 1998, each taken as the ``shifted'' time $t_0$ within two individually analyzed periods $T$: from 1979 to 1998; from 1987 to 2008.
+In practice, all treated units (i.e., provinces) were affected by institutional shifts in 1987 and 1998, each taken as the ``shifted'' time $T_0$ within two individually analyzed periods $1, 2, \dots, T_0, T_0 + 1, \dots, T$: from 1979 to 1998; from 1987 to 2008.
 We separately include each of the eight provinces in the YRB (see \textit{\nameref{sec:dataset}}) as individual treated units~\cite{abadie2021}.
-Then, we consider the $J+1$ units observed in time periods $T = {1, 2, \ldots, t}$ where the remaining $J=20$ units represent untreated provinces from outside the YRB.
-We define $T_0$ to represent the number of pre-treatment periods ($1,\ldots,t_0$) and $T_1$ the number post-treatment periods ($t_0, \ldots, T$), such that $T = T_0+ T_1$.
-The treated unit is exposed to the institutional shift in every post-treatment period $T_1$, unaffected by the institutional shift in all preceding periods $T_0$.
-Then, any weighted average of the control units is a synthetic control and can be represented by a ($J \times 1$) vector of weights $\mathbf{W} = (w_{1}, \ldots ,w_{J})$, with $w_j \in (0, 1)$.
-Among them, by introduce a ($k \times k$) diagonal, matrix $\mathbf{V}$ that signifies the relative importance of each variable, the DSC method procedure for finding the optimal synthetic control ($\mathbf{W}$) is expressed as follows:
+Then, we consider the $J+1$ units observed in time periods $1, \dots, T$ where the remaining $J=20$ units represent untreated provinces from outside the YRB.\
+% We define $T_0$ to represent the number of pre-treatment periods ($1,\ldots,t_0$) and $T_1$ the number post-treatment periods ($t_0, \ldots, T$), such that $T = T_0+ T_1$.
+The treated unit is exposed to the institutional shift in every post-treatment period $T_0 +1, \dots, T$, unaffected by the institutional shift in all preceding periods $1, 2, \dots, T_0$.
+Then, any weighted average of the control units is a synthetic control and can be represented by a ($J \times 1$) vector of weights $\mathbf{W} = (w_{1}, \ldots ,w_{J})$, with $w_j \in (0, 1)$ and $w_2 + \cdots  + w_{J+1} = 1$.
+We denote $k$ is $T \times D$ number of covariates, in which $D$ is number of dimensions of the dataset (i.e., $D = 5$ in this case).
+Introducing a $k \times 1$ non-negative vector $\mathbf{V}$ ($\mathbf{V} = v_{1}, \ldots ,v_{k}$ and $v_1 + \cdots  + v_{k} = 1$) that signifies the relative importance of each covariate.
+% 接下来的目标就是求一个权重矩阵W，让它来表示控制组各单位的权重，使这些权重构成我们需要的“合成”版本的控制组
+The next goal is finding the optimal synthetic control ($\mathbf{W}$) which represents the ``synthetic'' versions of the affected provinces in the YRB.\
 
 \begin{equation}
-    \mathbf{W^{*}(V)}=\underset{\mathbf{W} \in \mathcal{W}}{\operatorname{minimize}}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)^{\prime} \mathbf{V}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)
+    \mathbf{W^{*}(V)}=\underset{\mathbf{W} \in \mathcal{W}}{\operatorname{argmin}}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)^{\prime} \mathbf{V}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)
 \end{equation}
 
-where $X_1$ is the pre-treatment average of each variable in the dataset for the treated unit, while $X_0$ is a ($k \times J$) containing the pre-treatment characteristics for each of the $J$ control units; $\mathbf{W}^{*}(V)$ is the vector of weights $\mathbf{W}$ that minimizes the difference between the pre-treatment characteristics of the treated unit and the synthetic control, given $\mathbf{V}$.
-That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W*(V)}$.
+Here, $\mathbf{X_1}$ is the pre-treatment average of each variable in the dataset for the treated unit, while $\mathbf{X_0}$ is a ($k \times J$) containing the pre-treatment characteristics for each of the $J$ control units; $\mathbf{W}^{*}(V)$ is the vector of weights $\mathbf{W}$ that minimizes the difference between the pre-treatment characteristics of the treated unit and the synthetic control, given $\mathbf{V}$.
+That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W^{*}(V)}$.
 Therefore, we choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{W*(V)}$ that minimizes the following expression:
@@
 That is the minimum difference between the water uses of treated units and the synthetic controls in the pre-treatment period, where $\mathbf{Z}_{1}$ is a matrix containing every observation of the water use for the treated unit in the pre-treatment period $T_0$.
-Similarly, $\mathbf{Z}_{0}$ is a ($k \times T_0$) matrix contains the water use for each control unit in the pre-treatment period, and $k$ is the number of variables in the datasets.
+Similarly, $\mathbf{Z}_{0}$ is a ($J \times T_0$) matrix contains the water use for each control unit in the pre-treatment period.
+% https://github.com/OscarEngelbrektson/SyntheticControlMethods/issues/18 这里和README不一样，因为它有问题
 The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with better robustness~\cite{billmeier2013, smith2015}.

### 2023-07-29 docs/papers/01_manuscript/04_discussion.tex
docs(discussion): :memo: update discussions based on editor's comments

--- 2023-05-06 docs/papers/01_manuscript/04_discussion.tex
@@
 % 制度对社会生态系统的结果产生影响在世界范围内都很普遍，
-The impacts of institutional shifts on the governing effects of social-ecological systems (SESs) have been widely reported worldwide, but few attempts have been made to quantify their net effects~\cite{cumming2020a}.
-Our case study of the YRB's water governance suggests that while the 98-UBR decreased total water use as expected, the 87-WAS unexpectedly increased it by $5.75\%$, a comparison of which can yield insights into the effectiveness of governance.
-Firstly, the results challenge previous analyses (i.e., suggesting that 87-WAS ``had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present~\cite{abadie2015,hill2021}.
-However, the significant net effect indicated by our analysis suggests that the 87-WAS was followed by increased water use even after controlling for environmental and economic variables (see \textit{\nameref{secS2}} Table~\ref{tab:variables}).
-In contrast, the 98-UBR reduced surface water competition, so many studies attributed the streamflow restoration mainly to the successful introduction of this institution~\cite{chen2021,huangang2002,an2007}.
+The impacts of institutional shifts on the governing effects of social-ecological systems (SESs) have attracted global attention, yet efforts to quantify their net effects remain sparse~\cite{cumming2020a}.
+Our investigation of the YRB's water governance reveals vary effects of nuanced-differences institutional shifts: while the 98-UBR led to an expected decrease in total water use, the 87-WAS surprisingly increased it by $5.75\%$.
+This comparison offers insightful perspectives on the effectiveness of governance because it suggests a significant net effect on increased water use following the implementation of this policy, in addition to the previous reports and comments suggesting that the 87-WAS was ``out-of-control''~\cite{wang2019d, departmentofearthsciences1999}.
+In contrast, the 98-UBR reduced surface water competition, so many studies attributed the streamflow restoration mainly to the successful introduction of it~\cite{chen2021,huangang2002,an2007}.
 
-Examining the unexpected 87-WAS policy, we found it shared a similar structure with many other SES governance failures, supporting the hypothesis that specific mismatched structures can rapidly exhaust common resources~\cite{kellenberg2009,cai2016,barnes2019}.
-Generally, these structure-based failures occur when social actors freely access linked resource units (like the institution before 1987), while the monitoring duty of the YRCC after 87-WAS was a sign that water quota was valuable to pursue (between 1987 and 1998).
-This conjecture aligns with the increased water use after 87-WAS and the concerns about frequently scrambling for water in some provinces during this period~\cite{mao2000, bouckaert2022}.
-A previous study analyzed reasons for the non-ideal effect of 87-WAS~\cite{huangang2002}, where core concerns were the lack of enforcement and controlling approaches, while major stakeholders kept arguing they needed more quotas from 1983 to the 1990s.
-It indicates that it was reasonable for stakeholders to pursue more water quota by withdrawing more water, beyond their economic growth.
-Our results align with this hypothesis since the correlation between current water use and changed (increased or decreased) water use was significant after the 87-WAS but not after the 98-UBR (Figure~\ref{fig:regulating}).
-In addition, through a theoretically marginal benefit analysis, this ``major users use more'' pattern can be inferred from a simple assumption that stakeholders can expect water quota's value in the short future, also supporting the above hypothesis (see \textit{\nameref{secS4}}).
+The unanticipated consequence of the 87-WAS policy echoes the structural challenges reported in many other SES governance failures.
+This suggests a general pattern where specific misaligned structures can precipitate the rapid depletion of common resources~\cite{kellenberg2009,cai2016,barnes2019}.
+These structure-based failures often occur when social actors have unregulated access to linked resource units, a feature prevalent in the institution prior to 1987~\cite{wang2019c}.
+When the central government attempted to curtail this free access by introducing water quotas, they were met with water demands from stakeholders' proposals that far exceeded expectations (Table~\ref{tab:quota}).
+A previous study attributed the suboptimal effect of 87-WAS to the lack of enforcement and control mechanisms~\cite{huangang2002}.
+Taken together, it underpins a hypothesis that in the absence of enforcement, stakeholders might have exploited the system by increasing water withdrawals to secure more water quotas for their economic prospects.
 
-Besides our results, the above hypothesis also aligns with two reported facts:
-(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) and the bargaining arguments even persisted years after 1987~\cite{wang2019e, wang2019d}.
-During this process, each province attempted to demonstrate its development potential related to water use, to match water shares to their economy because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution)~\cite{zuo2020}.
-(2) During the ``bargaining'', more significant stakeholders had considerable
-incentives to pursue more water quotas, which aligned with the fact that major water users submitted appeals to the higher central government for larger shares~\cite{wang2019e, wang2019d}.
-This means provinces with higher current water use have greater bargaining power in water use allocation.
+This hypothesis can be further substantiated by two reported facts:
+(1) There were not only surges of total water uses following the 87-WAS, but also scrambles for water reported in several provinces during this period~\cite{mao2000, bouckaert2022}.
+(2) From 1983 to the 1990s, the stakeholders persistently argued for increased the water quotas, when is a stage of ``bargaining''~\cite{wang2019e, wang2019d};
+(3) During this ``bargaining'' stage, the stakeholders who had more economic profits submitted appeals to the higher central government for larger shares~\cite{wang2019e, wang2019d}.
 
-On the other hand, since the YRCC could coordinate stakeholders by water quota licenses according to water conditions for the entire YRB after 98-UBR, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)~\cite{krieger1955, ostrom1990}.
-Similar, proportional decreased water use of provinces and the theoretical minimal water use of marginal benefit model indicated this policy lead to successful governance as expected (see \nameref{result-3}).
-However, since the 98-UBR only regulated surface water use, many clues suggested the institution shift may cause broader influences, including estimated increased groundwater withdrawals after 98-UBR in many intensive water use regions~\cite{sun2022b}.
-With limited eligible data on groundwater use, related assessment is beyond the scope of this study but remains quite important, as similar water quota policies started to be implemented nationally since the 21st century.
+Our results also corroborate some intuitive deductions of the hypothesis.
+Firstly, we found significant correlations between current and changed water use after the 87-WAS, which suggests that the key stakeholders (such as Neimeng, Henan, and Shandong), were more likely to be affected by the institutional change.\
+Secondly, a theoretical marginal benefit analysis (see \textit{\nameref{secS4}}) suggests that this ``major users are effected more'' pattern can be inferred from a simple assumption that stakeholders anticipate future value in water quotas, thereby lending further support to the above hypothesis.
+Finally, since the YRCC could forcibly coordinate stakeholders by water quota licenses for the entire YRB after 98-UBR, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)~\cite{krieger1955, ostrom1990}.
 
+On the flip side, the apparent success of the 98-UBR institutional transformation has received consistent acclaim, particularly for its role in restoring the previously dry river~\cite{wang2019e, wang2019d}.
+Our findings suggest that the 98-UBR led to a proportional decrease in water use across provinces, indeed indicative of an immediate and tangible effect.
+However, it's essential to recognize that the 98-UBR focused solely on regulating surface water use, which hints at potential broader implications.
+Notably, some evidence suggests that this institutional shift might have resulted in increased groundwater withdrawals in regions with intensive water usage following the 98-UBR~\cite{sun2022b}.
+Unfortunately, the limited availability of eligible data on groundwater use constrains a comprehensive assessment, leaving this aspect beyond the scope of the current study.
+Nonetheless, this consideration remains highly relevant, especially as similar water quota policies have begun to be implemented nationally since the turn of the 21st century.
+
+To provide an intuitive understanding of the profound impact of the Institutional shifts, we can turn to the insights shared by a representative of the Hetao Irrigation District in Neimeng.
+As a primary stakeholder, the district's representative voiced the struggle to adapt under the 98-UBR policy which strictly enforced water quotas in our surveys.
+``The water allocated to us is far from enough'', he revealed with a desire on more water quota: ``And it's not like in the past when we could actually over use, it is very strictly controlled now.''
+``Under a limited quota, of course there are conflicts between users time to time, which depends on leaderships of the water-user associates'', he reflected: ``-farmers may have their own solutions, such as switching to sunflower, which is more water-efficient, or using shallow groundwater when is available.''
+Simultaneously, the district looked forward to future projects, such as the ``South-to-North Water Diversion'' Western Route Project, which they hoped would increase their water quotas and allow for expansion of their irrigation area.
+The desire of water in Neimeng wasn't without controversy. Stakeholders in other lower reaches argued that the Hetao Irrigation District was consuming too much water from the Yellow River.
+
+The above analysis with a real-world example underscores the crucial role of institutions in water governance by shaping SES structures.
 The structural pattern we depicted here (Figure~\ref{fig:structure}) has also been reported in other SESs worldwide~\cite{kluger2020,guerrero2015,bodin2012}.
@@
 Taken together, the comparison demonstrates the challenge of finding win-win situations in coupled social-ecological systems~\cite{hegwood2022} and the need to more deeply understand the role of institutions in water governance~\cite{bergsten2019, sayles2019}.
-% Therefore, the YRB cases can provide further explanation of the matching and mismatching of the previous SES building blocks, linking SES structure and outcomes by plausible reasons of causality and underlying processes.
-
-% \subsection{LIMITATION, INSIGHTS AND IMPLICATIONS}
-% \subsection{Limitation, insights and implications}
-% \label{discussion-4}
-% discussion-3: 启示、未来的展望
 

### 2023-07-29 docs/papers/04_response_letter/source/editor.tex
docs(discussion): :memo: update discussions based on editor's comments

@@
 \subsection*{General comments}
-\RC*{} Dear Author,
+\RC{} Dear Author,
 
@@
 
-% 除了审稿人的意见外，我还建议根据特刊主题加强讨论。你对制度变迁后果的分析，对于社会水文学来说，确实是重要而及时的。主要基于统计定量分析的方法选择是创新的，可以更好地描述社会水文系统的变化，这是好的。要深入社会水文学，需要更多背后的故事，对推动这些变化的社会和水文过程的解释。讨论在这个方向上开辟了一些途径，但在这方面过于薄弱。我漏了一些例子。1998年以后从地表水转移到地下水取水的事实)，引语(如:(关于讨价还价的论据)，谁是主要利益相关者的准确性以及他们如何影响社会水文过程。
 \RC*{} In addition to reviewers' comments, I would also recomment strengthening the discussion in light of the special issue topic.
@@
 
-\AR*{} We hope that these revisions address the concerns raised by both reviewers.
-We are confident that these changes have significantly improved the quality of our manuscript and made it more relevant and valuable to the scientific community.
-We look forward to your further feedback and the possibility of our manuscript being accepted for publication.
+\AR{} Dear Dr. Barreteau and the Invited Editorial Team,
+
+\AR*{} I would like to express my sincere gratitude for the thoughtful feedback and constructive comments provided by the reviewers and yourself.
+Your insights have greatly enhanced the quality of our manuscript, and I appreciate the opportunity to respond to each concern.
+
+\AR{} DSC Method Description and Wording (Reviewer \#1's Comment)
+
+\AR*{} Thank you for highlighting this point.
+We have thoroughly revised the sections related to the DSC method, providing a more detailed explanation and improving the wording.
+This revision ensures that the method is clearly presented and its relevance to the study is well-articulated.
+
+\AR{} Strengthening the Discussion in Light of the Special Issue Topic:
+
+\AR*{} Social and Hydrological Processes: We recognize the importance of delving deeper into the underlying social and hydrological processes that drive changes in the SocioHydrological systems.
+To address this, we have enriched our discussion by:
+
+\AR*{} (1) Inclusion of Examples and Facts: As suggested, we have included specific examples such as the case of the Hetao Irrigation District and facts describing the transfer from surface to groundwater withdrawal after 98.
+These additions offer a concrete illustration of the theoretical arguments and provide contextual insights.
+
+\AR*{} (2) Quotations on Bargaining Arguments: We have integrated relevant quotations to illuminate the bargaining arguments among stakeholders during the institutional shifts.
+This inclusion offers a more vivid and grounded understanding of the negotiations and stakeholder dynamics.
+
+\AR{} I am grateful for the encouragement and the direction provided to enhance our manuscript.
+It has been a privilege to contribute to this special issue, and I believe that the revisions made align with the expectations and vision set forth by the editorial team.

### 2023-07-29 docs/papers/01_manuscript/06_methods.tex
fix(project): :bug: Checking math by Yinan Xiao

@@
 The treated unit is exposed to the institutional shift in every post-treatment period $T_0 +1, \dots, T$, unaffected by the institutional shift in all preceding periods $1, 2, \dots, T_0$.
-Then, any weighted average of the control units is a synthetic control and can be represented by a ($J \times 1$) vector of weights $\mathbf{W} = (w_{1}, \ldots ,w_{J})$, with $w_j \in (0, 1)$ and $w_2 + \cdots  + w_{J+1} = 1$.
-We denote $k$ is $T \times D$ number of covariates, in which $D$ is number of dimensions of the dataset (i.e., $D = 5$ in this case).
-Introducing a $k \times 1$ non-negative vector $\mathbf{V}$ ($\mathbf{V} = v_{1}, \ldots ,v_{k}$ and $v_1 + \cdots  + v_{k} = 1$) that signifies the relative importance of each covariate.
+Then, any weighted average of the control units is a synthetic control and can be represented by a ($J \times 1$) vector of weights $\mathbf{W} = (w_{1}, \ldots ,w_{J})$, with $w_j \in (0, 1)$ and $w_1 + \cdots  + w_{J} = 1$.
+We denote $k$ is $T * D$ number of covariates, in which $D$ is number of dimensions of the dataset (i.e., $D = 5$ in this case).
+Introducing a ($k \times 1$) non-negative vector $\mathbf{V}$ ($\mathbf{V} = v_{1}, \ldots ,v_{k}$) and $v_1 + \cdots  + v_{k} = 1$ that signifies the relative importance of each covariate.
 % 接下来的目标就是求一个权重矩阵W，让它来表示控制组各单位的权重，使这些权重构成我们需要的“合成”版本的控制组
@@
 
-Here, $\mathbf{X_1}$ is the pre-treatment average of each variable in the dataset for the treated unit, while $\mathbf{X_0}$ is a ($k \times J$) containing the pre-treatment characteristics for each of the $J$ control units; $\mathbf{W}^{*}(V)$ is the vector of weights $\mathbf{W}$ that minimizes the difference between the pre-treatment characteristics of the treated unit and the synthetic control, given $\mathbf{V}$.
+Here, $\mathbf{X_1}$ is the pre-treatment average of each variable in the dataset for the treated unit, while $\mathbf{X_0}$ is a ($k \times J$) matrix containing the pre-treatment characteristics for each of the $J$ control units; $\mathbf{W}^{*}(V)$ is the vector of weights $\mathbf{W}$ that minimizes the difference between the pre-treatment characteristics of the treated unit and the synthetic control, given $\mathbf{V}$.
 That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W^{*}(V)}$.
-Therefore, we choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{W*(V)}$ that minimizes the following expression:
+Therefore, we choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{{W}^{*}(V)}$ that minimizes the following expression:
 

### 2023-07-29 docs/papers/04_response_letter/source/reviewer_1.tex
fix(project): :bug: fix response letter compiling bug

@@
 
-\AR{} Thank you for your valuable feedback and for acknowledging our efforts \dots.
+\AR{} Thank you for your valuable feedback and for acknowledging our novelty and reasonability.
 Your feedback greatly helps us improve the clarity and accessibility of our work.
 We sincerely appreciate your effort in reviewing our manuscript and providing these insightful comments.
+Below are point-to-point modification descriptions.
 
@@
 We also explained the specific variables used when we introduced $X_1, X_0, Z_1$, and $Z_0$, as well as mentioned the specific method used for minimization and the corresponding reference.
-We believe that these revisions have significantly improved the clarity of our method description:
-
-\begin{quote}[page=XXX, sline=XXX, eline=XXX]
-    Modification \dots
-\end{quote}
-
-\AR*{} We are grateful for your insightful feedback, which has helped us improve the quality of our manuscript. We hope that our revisions have addressed all your concerns satisfactorily.
+We believe that these revisions have significantly improved the clarity of our method description.
 
@@
 \RC{} I found some of the word choices a bit strange.
-For example, unless the term has been used this way in the literature, "point-axis networks" sounds strange.
-Otherwise, please consider alternatives like "organizational charts" or "organizational diagrams," which I believe is more appropriate.
+For example, unless the term has been used this way in the literature, ``point-axis networks'' sounds strange.
+Otherwise, please consider alternatives like ``organizational charts'' or ``organizational diagrams'', which I believe is more appropriate.
 
@@
 
-\begin{quote}[page=XXX, sline=XXX, eline=XXX]
+\begin{quote}[page=5, sline=89, eline=91]
     In the methodology section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as organizational diagrams during different periods of time.
@@
 
-\begin{quote}[page=XXX, sline=XXX, eline=XXX]
+\begin{quote}[page=5, sline=98, eline=99]
     An organizational diagram is widely used to depict SES structures by abstracting links and nodes from the real-world interactions~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
@@
 
-\begin{quote}[page=XXX, sline=XXX, eline=XXX]
+\begin{quote}[page=5, sline=99, eline=103]
     We apply the analysis of the organizational diagrams~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit at the basin scale (the Yellow River Conservancy Commission) into structural patterns from official documents.
@@
 
-\begin{quote}[page=XXX, sline=XXX, eline=XXX]
-    Two primary methods can be employed to test the efficiency of the DSC approach.
+\begin{quote}[page=7, sline=162, eline=163]
+    Two primary methods can be employed to validate the efficiency of the DSC approach.
 \end{quote}
 
-\begin{quote}[page=XXX, sline=XXX, eline=XXX]
-    An effective synthetic control model will show a significant difference after treatment but not before treatment.
+\begin{quote}[page=8, sline=169, eline=172]
+    An effective result would be one where a significant difference is observed after treatment but not before treatment.
+If this is not the case, it implies that the institutional changes were ineffective for the treated units.
 \end{quote}
 
-\begin{quote}[page=XXX, sline=XXX, eline=XXX]
-    \dots it would suggest that the Yellow River Basin was more significantly affected than most other provinces during the treatment periods ($1987$ and $1998$), i.e., more effective.
+\begin{quote}[page=8, sline=180, eline=184]
+    If the ratio of the root mean square error (see Equation~3) in the pre-synthesis period is significantly higher for most provinces (again using the $T$ test to determine the significance of the difference) than the results of other placebo units, the provinces in the YRB was more significantly affected than most other provinces during the treatment periods ($1987$ and $1998$), i.e., more effective.
 \end{quote}
@@
 
-\begin{quote}[page=XXX, sline=XXX, eline=XXX]
+\begin{quote}[page=8, sline=173, eline=174]
     Secondly, placebo tests are another common way to evaluate the effectiveness of synthetic control methods~\cite{abadie2010}.
@@
 
-\begin{quote}[page=XXX, sline=XXX, eline=XXX]
+\begin{quote}[page=4, sline=74, eline=75]
     In $1980s$, the central government proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019d, wang2019e}.
@@
 
-\begin{quote}
-    A valid result would be one where a significant difference is observed after treatment but not before treatment.
+\begin{quote}[page=8, sline=169, eline=172]
+    An effective result would be one where a significant difference is observed after treatment but not before treatment.
 If this is not the case, it implies that the institutional changes were ineffective for the treated units.
@@
 
-\begin{quote}
+\begin{quote}[page=10, sline=208, eline=210]
     From 1988 to 1998, on average, while the estimation of annual water use only suggests $887.05$ billion $m^3$, the observed water use of the YRB provinces reached $938.06$ billion $m^3$ (an increase of $5.75\%$).
@@
 
-\RC{} Lines 261-262: It's unclear to me how Fig. 4 supports the statement "the correlation between...98-UBR (Figure 4)."
+\RC{} Lines 261-262: It's unclear to me how Fig. 4 supports the statement "the correlation between \dots 98-UBR (Figure 4)."
 
@@
 
-\begin{quote}
-    Similarly, proportional decreased water use of provinces and the theoretical minimal water use of marginal benefit model indicated this policy lead to successful governance as expected (see \nameref{result-3} and \textit{Appendix~\nameref{secS4}}).
+\begin{quote}[page=14, sline=267, eline=270]
+    Secondly, a theoretical marginal benefit analysis (see \textit{Appendix C}) suggests that this ``major users are effected more'' pattern can be inferred from a simple assumption that stakeholders anticipate future value in water quotas, thereby lending further support to the above hypothesis.
+.
 \end{quote}
 
-\RC{} Line 280: "Similar" -> "Similarly"
-\AR{} Thank you for pointing out the typographical error in line 280. We have corrected the error by changing "Similar" to "Similarly" as you suggested.
+\RC{} Line 280: from ``Similar'' to ``Similarly''
 
-\RC{} Line 323-324: This is the first time you used the term "difference-in-differences" - so far, you have called your method "Differenced Synthetic Control" (DSC).
+\AR{} Thank you for pointing out the typographical error in line 280. We have eliminated the error in the revision.
+
+\RC{} Line 323-324: This is the first time you used the term ``difference-in-differences'' -so far, you have called your method ``Differenced Synthetic Control'' (DSC).
 Why different names?
@@
 
-\RC{} Line 327: "revealed" is too strong; perhaps "suggested"?
-\AR{} Thank you for pointing out the excessive use of the term "revealed" in line 327.
+\RC{} Line 327: ``revealed'' is too strong; perhaps ``suggested''?
+
+\AR{} Thank you for pointing out the excessive use of the term ``revealed'' in line 327.
 We appreciate your thoughtful suggestion to soften the language.
-We have now replaced "revealed" with the more appropriate term "suggested" in our manuscript.
+We have now replaced ``revealed'' with the more appropriate term ``suggested'' in our manuscript.
 
 \RC{} Line 437, Ref [30]: Pca should be all caps, PCA.\
+
 \AR{} Thank you for bringing to our attention the typographical error in line 437, reference [30].

### 2023-07-29 docs/papers/04_response_letter/source/reviewer_2.tex
fix(project): :bug: fix response letter compiling bug

@@
 \subsection*{Overall comments}
-% 本研究考察了黄河流域87-WAS和98-UBR两种制度变迁对水治理的影响。结果表明，87-WAS导致用水量增加，98 UBR由于其在流域范围内的权威和利益相关者之间更强的联系而成功地减少了用水量。建议根据生态规模进行制度设计，促进不同参与方的合作，并进行相应的调整。政府和决策者必须分析政策变化对水的使用和可持续性的影响。作者采用了新开发的在AER上发表的合成差中差。这篇论文写得很好，结构也很好。然而，这种方法对于水研究人员来说是全新的。我有几点建议，希望作者在改稿中进一步考虑。
+
 \RC{} This study examines the effects of two institutional shifts in Water Governance for the Yellow River Basin - 87-WAS and 98-UBR.
@@
 
-\begin{quote}
+\begin{quote}[page=6, sline=124, eline=133]
     The Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021} is a tool we use to estimate how water use might have evolved if there had been no institutional shift.

### 2023-07-29 docs/papers/01_manuscript/06_methods.tex
docs(method): :pencil2: fixing valid -> efficiency

@@
 In this study, to determine whether the intervention effect is significant, the paired sample $T$ test is used to calculate statistics, comparing the model predictions and actual observation data in the periods before and after institutional interventions for both the 87-WAS in $1987$ and 98-UBR in $1998$.
-A valid result would be one where a significant difference is observed after treatment but not before treatment.
+An effective result would be one where a significant difference is observed after treatment but not before treatment.
 If this is not the case, it implies that the institutional changes were ineffective for the treated units.
@@
 In this study, we adopt the placebo test step suggested by Abadie when proposing the synthetic control method~\cite{abadie2010} and utilize the Python library of the differential synthetic control method for the placebo test.
-If the ratio of the root mean square error (see Equation~\ref{ch5:eq:RMSE}) in the pre-synthesis period is significantly higher for most provinces (again using the $T$ test to determine the significance of the difference) than the results of other placebo units, it would suggest that the Yellow River Basin was more significantly affected than most other provinces during the treatment periods ($1987$ and $1998$), i.e., more effective.
+If the ratio of the root mean square error (see Equation~\ref{ch5:eq:RMSE}) in the pre-synthesis period is significantly higher for most provinces (again using the $T$ test to determine the significance of the difference) than the results of other placebo units, the provinces in the YRB was more significantly affected than most other provinces during the treatment periods ($1987$ and $1998$), i.e., more effective.
 
@@
 Where $n$ is the observed number, $y_i$ is the actual value, and $\hat{y}_i$ is the predicted value.
-
-% \subsection{Marginal benefits analysis}\label{sec:model}
-% To infer the mechanisms underlying the results, we developed an marginal benefits analysis based on marginal revenue to analyze how the institutional shift could have led to differences in water use.
-
-% \begin{ass}
-%     (Water-dependent production) Because of irreplaceably, water is assumed to be the only production function input with two production efficiency types.
-% \end{ass}
-
-% \begin{ass}
-%     (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin, the water use cost is equally assigned to each province.
-% \end{ass}
-
-% \begin{ass}
-%     (Multi-period settings) There are multiple settings periods with a constant discount factor for the expectation of future water use.
-% \end{ass}
-
-% Under the above-simplified assumptions, we demonstrate three cases -corresponding to the abstracted SES structures (Figure~\ref{fig:structure}~C), inference of how SES structure alters the expected marginal benefits and costs of provinces making decisions.
-% As one of the possible interpretations for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.

### 2023-07-29 docs/papers/01_manuscript/manuscript_v-7.1.2.tex
build(project): :building_construction: tracking changes version

\documentclass[preprint, 12pt]{elsarticle}

\usepackage{amssymb}
\usepackage{amsmath, graphicx, array}
\usepackage{dcolumn, soul}\let\openbox\relax
\usepackage{amsthm}
\usepackage[figuresright]{rotating}\usepackage{algorithm, algorithmicx, algpseudocode}
\usepackage{listings}\usepackage{hyperref}
\usepackage{geometry}
\usepackage{tabularx}

\geometry{a4paper,left=2.0cm,right=2.0cm,top=2.5cm,bottom=2.5cm}
\linespread{1.5}
\newtheorem{defn}{Definition}
\newtheorem{thm}{Theorem}
\newtheorem{ass}{Assumption}
\newtheorem{prop}{Proposition}
\newtheorem{fig}{Fig.}
\newtheorem{case}{Case}
\newtheorem{case_appendix}{Case}
\newtheorem{example}{Example}[section]
\renewcommand{\proofname}{\textbf{Proof}}
\newtheorem{property}{Property}
\newtheorem{remark}{Remark}
\usepackage{enumitem}
\usepackage{float}
\usepackage{multirow}
\usepackage{lineno}
\usepackage{booktabs}
\usepackage{diagbox}

\graphicspath{{../../../figs/}}
\journal{Jounral of Hydrology}

\begin{document}
\begin{frontmatter}

\title{Quantifying the Effects of Institutional Shifts on Water Governance in the Yellow River Basin: A Social-ecological System Perspective}

\author[inst1]{Shuang Song}
\author[inst2]{Huiyu Wen}
\author[inst1]{*Shuai Wang}
\author[inst1]{Xutong Wu}

\author[inst3]{Graeme S. Cumming}
\author[inst1]{Bojie Fu}

\affiliation[inst1]{
     State Key Laboratory of Earth Surface Processes and Resource Ecology,
     Faculty of Geographical Science,
     Beijing Normal University,
     Beijing 100875,
     P.R. China}

\affiliation[inst2]{School of Finance,
     Renmin University of China,
     Beijing 100875,
     P.R. China}

\affiliation[inst3]{
     ARC Centre of Excellence for Coral Reef Studies,
     James Cook University,
     Townsville 4811,
     QLD, Australia}

\begin{abstract}
     Water governance in river basins worldwide faces challenges due to complex socio-economic and environmental factors. In the Yellow River Basin (YRB), two major institutional shifts, the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basin Regulation (98-UBR), aimed to address water allocation and usage issues. This study quantifies the net effects of these institutional shifts on water use within the YRB and analyzes the underlying reasons for their success or failure.
     We employ a Differenced Synthetic Control method to assess the impacts of the institutional shifts. Our analysis reveals that the 87-WAS unexpectedly increased water use by $5.75\%$, while the 98-UBR successfully reduced water use as anticipated. Our research highlights the role of institutional structures in governance policies, demonstrating that the mismatched structure of the 87-WAS led to increased competition and exploitation of water resources, while the 98-UBR, with its scale-matched, basin-wide authority and stronger connections between stakeholders, resulted in improved water governance.
     Our study underscores the importance of designing institutions that are consistent with the scale of the ecological system, promote cooperation among stakeholders, and adapt to changing social-ecological system (SES) contexts. As outdated and inflexible water quotas may no longer meet the demands of sustainable development in the YRB, governments and policymakers must consider the potential consequences of institutional shifts and their impact on water use and sustainability.
\end{abstract}

\begin{keyword}
     water use~\sep~water governance~\sep~social-ecological system~\sep~institutions~\sep~Yellow River
\end{keyword}

\end{frontmatter}
\newpage
\linenumbers
\section{Introduction}\label{sec:introduction}
Widespread freshwater scarcity and overuse challenge the sustainability of large river basins, resulting in systematic risks to economies, societies, and ecosystems globally~\cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
Amidst climate change, mismatches between supply and demand for water resources are expected to become increasingly more prominent~\cite{florke2018, yoon2021}.
Consequently, large river basins are progressively seeking effective water governance solutions by coordinating stakeholders, providing water resources, and ensuring the sustainable allocation of shared water resources~\cite{wang2019d}.
In this way, hydrological processes are tightly intertwined with societies, forming a social-ecological system (SES) at a basin scale with complex socio-hydrological feedback.

Institutions encompass the interplay between social actors, ecological units, and their interactions~\cite{young2008, lien2020, bodin2017b, wang2022g} (Figure~\ref{fig:framework}~a).
These interactions constitute a type of SES structure, where effective institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different interactions, contributing to sustainability~\cite{epstein2015, wang2019d} (Figure~\ref{fig:framework}~b).
While some institutional advances have led to effective water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China~\cite{wang2019d}, and collaborative water governance systems in Europe~\cite{green2013}), imposing institutional shifts may create or destroy connections and effectiveness is not ubiquitous~\cite{loos2022}.
For example, the Colorado River once experienced severe water shortage, and institutions led to various shortage magnitudes for different stakeholders even under the same water demand levels~\cite{hadjimichael2020}.
Therefore, examining when and how an institution leads to effective water governance can bring crucial insights for the sustainability of river basins.

Recent studies have explored diverse effects of institutions on river basin governance~\cite{bouckaert2022, vallury2022, loch2020, kirchhoff2016}, while the current analysis is more about interpreting outcomes after the institutional changes but cannot compare how scenarios would be without these institutional changes.
Moreover, understanding how different SES structures influence institutional effectiveness is challenging due to the complexity and dynamics of socio-hydrological systems~\cite{bodin2017b}.
Thus, knowledge gaps lie in the limited understanding of effective alignments between institutional shifts and SES structures, hindering the design of effective policies to promote sustainable river basin governance.
To fill these knowledge gaps, we study the Yellow River basin, the fifth-largest river worldwide and one of the most anthropogenically altered river basins, to quantitatively measure the effects of changing SES structures.

\begin{figure}[!ht]
	\centering
	\includegraphics[width=0.5\linewidth]{diagrams/framework.png}
	\caption{
		Illustration for understanding institutional shifts and SES structural changes. \textbf{a.} In the general framework for analyzing social-ecological systems (SESs), (Adapted from Ostrom, 2008~\cite{ostrom2009}). Institutional shifts can change interactions within the SES and reframe the structures.  \textbf{b.} We aim to examine how institutional shifts effect river basin governance by structuring SES.}\label{fig:framework}
\end{figure}

In the 1980s, intense water use, accounting for about $80\%$ of the Yellow River surface water, caused consecutive drying-up crises of runoff, leading to wetland shrinkage, agriculture reduction, and scrambles for water~\cite{wohlfart2016}.
To alleviate water stress, Chinese authorities implemented several ambitious water management policies in the Yellow River Basin (YRB), such as the South-to-North Water Diversion Project and the Water Resources Allocation Institutions~\cite{long2020, wang2019d}.
In this study, we specifically examined two significant institutional shifts in water allocation of the YRB\: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulating (98-UBR).
the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulating (98-UBR).
Instead of focusing on engineering and increasing water supply, the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, an authority at a basin level) mainly aimed to limit water demands~\cite{bouckaert2022, speed2013}.
These institutional shifts can offer valuable insights for two main reasons:
(1) the top-down institutional shifts suddenly led to transformations of SES structures, allowing us to quantitatively estimate their net effects; and (2) the two institutional shifts within the same river basin provide rare comparable quasi-natural experiments.

In this study, we portrayed changes of SES structures throughout the YRB's institutional shifts (the 87-WAS and the 98-UBR) and quantitatively investigated their consequences, followed by a discussion on the effectiveness of institutional shifts.
Specifically, we first used the descriptions of official documents following the two institutional shifts to abstract the interactions between main stakeholders and their river segment units for interpreting SES structure changes between 1979 and 2008.
Next, and perhaps most importantly, we employed the ``Differenced Synthetic Control (DSC)'' method~\cite{arkhangelsky2021}, which accounts for economic growth and natural background, to estimate theoretical water use volumes under scenarios absent of institutional shifts.
Finally, in the discussion, we linked the effectiveness of institutional shifts to the portrayed structures, by comparing the YRB's case to previous SES structure studies and developing a marginal benefits analysis.

\section{Study area and institutional contexts}\label{sec:yrb}

The YRB, cradle of Chinese civilization, is located in north-central China and spans ten province-level regions whose socio-economic development heavily depends on water from the Yellow River.
As a semi-arid and arid region, the YRB's annual precipitation varies from about 100 to 1,000 mm and increases from the northwest to the southeast, while the annual pan evaporation varies from about 700 to 1,800 mm~\cite{wang2022e}.
Together, the YRB supports $35.63\%$ of China's irrigation and $30\%$ of its population while containing only $2.66\%$ of its water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today).
Hence, over-withdrawing water from the Yellow River became an urgent concern when the river began to dry up in the early 1970s.
Among the policies proposed to address the problem, a series of water resource allocation institutions aimed to limit water use for each region with specific quotas, which were regarded as some of the most important solutions.
However, few attempts have been made to quantitatively assess how the YRB's water allocation scheme contributed to water governance, while other engineering solutions have been carefully evaluated~\cite{long2020}.

The YRB was the first basin in China for which water resource allocation institutions were created, and institutional shifts can be traced through several regulating documents released by the Chinese government (at the national level):
(1) In $1980s$, proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019d, wang2019e}.
(2) In $1987$, the Water Allocation Scheme was implemented (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
(3) In $1998$, the Unified Basinal Regulation was implemented (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
(4) In $2008$, provinces were asked to draw up new water resources plans for the YRB to further refine water allocations~\cite{wang2019d,wang2019e}.
(5) In $2021$, there was a call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).

Our study period therefore ranges from $1980$ (when water quotas were proposed) to $2008$, when a regulating system with quotas was fully established at basin, provincial, and district levels.
During this period, two significant institutional shifts can be analyzed using documents from $1987$ (87-WAS) and $1998$ (98-UBR), which split the study period into three sections: from $1980$ to $1987$ (before 87-WAS), from $1988$ to $1997$ (after 87-WAS and before 98-UBR), and from $1998$ to $2007$ (after 98-UBR).

\section{Methods}\label{sec:methods}

In the methodology section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as point-axis networks during different periods of time.
Next, we introduce the dataset we used here and employ the Principal Components Analysis (PCA) method to reduce the dimensionality of variables affecting the total water use.
We then estimate the net effects of the two institutional shifts on total water use, changing trends, and differences in the YRB's provinces using the Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021}.
Finally, we present the robustness tests approach for the DSC model.

\subsection{Portraying structures}\label{sec:structures}
A point-axis network type structure of SES is widely used to depict them by abstracting links and nodes~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
We apply the network approach~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit at the basin scale (the Yellow River Conservancy Commission) into structural patterns from official documents.
The network-based approach abstracts connections between entities into links according to their interactions~\cite{bodin2017a,kluger2020,guerrero2015}, so we examined the official documents of the two institutional shifts (87-WAS and 98-UBR) to portray these interactions in this study.
It is important to note that it can result in very different structures when basin-scale regulatory entity (YRCC) is responsible for river reach regulation, or have direct authority to interact with provincial units.

\subsection{Dataset and preprocessing}\label{sec:dataset}
The data of water consumption surveys conducted by the Ministry of Water Resources were taken as the observed values throughout the years.
Then, to estimate the water use of the YRB by assuming there were no effects from institutional shifts, we focused on variables from five categories (environmental, economic, domestic, and technological) water use factors. Their specific items and origins are listed in~\ref{secS2}~Table~\ref{tab:variables}.
Among the total $31$ data-accessible provinces (or regions) assigned quotas in the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin and Beijing (together, Jinji) because of their trivial water use from the YRB (see Table~\ref{tab:quota}).

Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ principal components.
Previous study has proved that combining PCA and DSC can raise the robustness of causal inference~\cite{bayani2021}.
We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different. Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\nameref{secS2}~Figure\ref{fig:elbow}}).
Finally, we transform the dataset and input the dimensions-reduced output into the DSC model.

\subsection{Differenced Synthetic Control}\label{sec:DSC}
Using the Differenced Synthetic Control (DSC) method, we can estimate water use under the scenarios of no institutional shift.
The DSC method is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit~\cite{abadie2010, abadie2015, hill2021}.
This approach enables us to establish a counterfactual basis for exploring the consequences and incentives related to policy changes.

This method aims to evaluate the effects of policy change that are not random across units but focuses on some of them (i.e., institutional shifts in the YRB here).
By re-weighting units to match the pre-trend for the treated and control units, the DSC method imputes post-treatment control outcomes for the treated units by constructing a synthetic version of the treated units equal to a convex combination of control units.
Therefore, the synthetic and actual version difference can be estimated as a net effect for a treated unit.

In practice, all treated units (i.e., provinces) were affected by institutional shifts in 1987 and 1998, each taken as the ``shifted'' time $t_0$ within two individually analyzed periods $T$: from 1979 to 1998; from 1987 to 2008.
We include each province in the YRB ($n=8$, see \textit{\nameref{sec:dataset}}) as the treated unit separately, as multiple treated units approach had been widely applied~\cite{abadie2021}.
Then, we consider the $J+1$ units observed in time periods $T = {1,2 \cdots , T}$ with the remaining $J=20$ units are untreated provinces from outside.
We define $T_0$ to represent the number of pre-treatment periods ($1,\ldots,t_0$) and $T_1$ the number post-treatment periods ($t_0, \ldots, T$), such that $T = T_0+ T_1$.
The treated unit is exposed to the institutional shift in every post-treatment period $T_0$, unaffected by the institutional shift in all preceding periods $T_1$.
Then, any weighted average of the control units is a synthetic control and can be represented by a ($J * 1$) vector of weights $\mathbf{W} = (w_{1}, \ldots ,w_{J})$, with $w_j \in (0, 1)$.
Among them, by introduce a ($k * k$) diagonal, matrix $\mathbf{V}$ that signifies the relative importance of each covariant, the DSC method procedure for finding the optimal synthetic control ($W$) is expressed as follows:

\begin{equation}
    \mathbf{W^{*}(V)}=\underset{\mathbf{W} \in \mathcal{W}}{\operatorname{minimize}}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)^{\prime} \mathbf{V}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)
\end{equation}

where $\mathbf{W}^{*}(V)$ is the vector of weights $\mathbf{W}$ that minimizes the difference between the pre-treatment characteristics of the treated unit and the synthetic control, given $\mathbf{V}$. That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W*(V)}$. Therefore, we choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{W*(V)}$ that minimizes the following expression:

\begin{equation}
    \mathbf{V}^{*}=\underset{\mathbf{V} \in \mathcal{V}}{\operatorname{argmin}}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)^{\prime}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)
\end{equation}

That is the minimum difference between the outcome of the treated unit and the synthetic control in the pre-treatment period, where $\mathbf{Z}_{1}$ is a ($1*T_0$) matrix containing every observation of the outcome for the treated unit in the pre-treatment period. Similarly, let $\mathbf{Z}_{0}$ be a ($k * T_0$) matrix containing the outcome for each control unit in the pre-treatment period, and $k$ is the number of variables in the datasets.
The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with double robustness properties~\cite{billmeier2013, smith2015}.

\subsection{Robustness analysis}\label{sec:robustness}

Two primary methods can be employed to test the robustness of the DSC approach.

Firstly, the reconstruction effect on inferred variables (water consumption here) before and after treatment (the interventions of 87-WAS and 98-UBR) can be compared.
If there are small gaps between the predicted and observed values before treatment, and a large gap after treatment, it indicates that the policy intervention's effect is apparent.
In this study, to determine whether the intervention effect is significant, the paired sample $T$ test is used to calculate statistics, comparing the model predictions and actual observation data in the periods before and after institutional interventions for both the 87-WAS in $1987$ and 98-UBR in $1998$.
A robust synthetic control model will show a significant difference after treatment but not before treatment.

Secondly, placebo experiments are another common way to evaluate the effectiveness of synthetic control methods.
Placebo units are selected from the control unit pool and substituted for the treated unit, applying the synthetic control method to the placebo unit using the same data and parameters as the treated unit.
If the synthetic control method is effective, there should be a clear difference between the placebo unit and the control unit since the placebo unit should not be affected by the intervention.
In this study, we adopt the placebo test step suggested by Abadie when proposing the synthetic control method~\cite{abadie2010} and utilize the Python library of the differential synthetic control method for the placebo test.
If the ratio of the root mean square error (see Equation~\ref{ch5:eq:RMSE}) in the pre-synthesis period is significantly higher for most provinces (again using the $T$ test to determine the significance of the difference) than the results of other placebo units, it would suggest that the Yellow River Basin was more significantly affected than most other provinces during the treatment periods ($1987$ and $1998$), i.e., the results are more robust.

\begin{equation}
    \label{ch5:eq:RMSE}
    \text{RMSE} = \sqrt{\frac{1}{n}\sum_{i=1}^{n}{(y_i-\hat{y}_i)}^2}
\end{equation}

Where $n$ is the observed number, $y_i$ is the actual value, and $\hat{y}_i$ is the predicted value.

\section{Results}\label{sec:results}

\subsection{Institutional shifts and structures}\label{results-1}

\begin{figure*}[!t]
	\includegraphics[width=\linewidth]{diagrams/diagram.pdf}
	\caption{
Institutional shifts and related SES structures in the Yellow River Basin (YRB).
		\textbf{A.} The YRB crosses $10$ provinces or the same-level administrative regions, $8$ of which heavily rely on the water resources from the YRB (Table~\ref{tab:quota}). The national administrations hold ultimate authority in issuing water governance policies, which are often implemented by the basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
		\textbf{B.} Provincial administrative agencies are the major stakeholders. Since the 87-WAS, with surface water withdrawal from the Yellow River restricted by specific quotas, each stakeholder plans and uses water resources for development. However, natural hydrological processes are interconnected. Although the institutions focus mainly on surface water (Sur.), they can also influence groundwater inside (Gro.) or water resources outside (Sur.\ and Gro.') through systematic socio-hydrological processes within the YRB.\\ The YRCC only monitors water withdrawals at that time.
		\textbf{C.} Institutional shifts and subsequent structural changes (details in \textit{\nameref{sec:yrb}}). (1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from the connected ecological unit (the reach of the Yellow River, denoted by the blue circles). (2) After 1987-WAS, the YRCC (the yellow circles) monitored (the dot-line links) river reaches with water use quotas. (3) Since the 98-UBR, stakeholders have had to apply for water use licenses from the YRCC (the connections between the red and yellow circles).
	}\label{fig:structure}
\end{figure*}

Until the 87-WAS, provincial regions in the YRB had unrestricted access to the Yellow River water resources for development, despite geographic and temporal differences between freshwater demand and availability.
The YRCC had no links to the provinces regarding water use before 1987, and the provinces could connect directly to the Yellow River reaches (Figure~\ref{fig:structure}~C).
Following the 87-WAS, national authorities proposed allocating specific water quotas among the provinces, and the YRCC's duty became to report actual water use volumes in each reach.
As it was the first time the YRCC's responsibilities included water use, this introduced new links between the YRCC and the river (i.e., ecological nodes Figure~\ref{fig:structure}~C).
The 98-UBR further reinforced the YRCC's responsibilities for integrated water use management.
Since $1998$, provinces have been required to submit their annual water use plans for water use licenses to the YRCC instead of freely accessing the Yellow River water.
Consequently, the YRCC has been directly linked to the provinces since then (Figure~\ref{fig:structure}C).
Key points of the official documents supporting the structural changes above can be found in supplementary material~\textit{\nameref{secS1}}.

\begin{table}[htbp]\footnotesize
	\centering
	\caption{Water quotas assigned for provincial regions in the YRB}\label{tab:quota}
	  \begin{tabularx}{\textwidth}{p{3cm}XXXXX}
	  \toprule
	  Provincial regions & \multicolumn{1}{l}{Water planning$^a$} & \multicolumn{1}{l}{Proposal in 1983$^b$} & \multicolumn{1}{l}{Scheme in 1987$^c$} & \multicolumn{1}{l}{Avg. WU$^d$} & \multicolumn{1}{l}{Ratio ($\%$)$^e$} \\
	  \midrule
	  Qinghai & 35.70  & 14.00  & 14.10  & 12.03  & 48.12  \\
	  Sichuan & 0.00  & 0.00  & 0.40  & 0.25  & 0.10  \\
	  Gansu & 73.50  & 30.00  & 30.40  & 25.80  & 30.79  \\
	  Ningxia & 60.50  & 40.00  & 40.00  & 36.58  & 58.45  \\
	  Inner Mongolia & 148.90  & 62.00  & 58.60  & 61.97  & 47.82  \\
	  Shanxi & 115.00  & 43.00  & 38.00  & 21.16  & 73.55  \\
	  Shaanxi & 60.80  & 52.00  & 43.10  & 11.97  & 44.39  \\
	  Henan & 111.80  & 58.00  & 55.40  & 34.30  & 24.77  \\
	  Shandong & 84.00  & 75.00  & 70.00  & 77.87  & 34.41  \\
	  Jinji & 6.00  & 0.00  & 20.00  & 5.85  & 3.11  \\
	  \bottomrule
	  \multicolumn{6}{p{\textwidth}}{$^a$ In 1982, each provincial region proposed their water use plans.}\\
	  \multicolumn{6}{p{\textwidth}}{$^b$ In 1983, the Yellow River Conservancy Commission (YRCC) proposed these initial water quotas.}\\
	  \multicolumn{6}{p{\textwidth}}{$^c$ In 1987, the quotas agreed by state department (Ministry of Water Resources).}\\
	  \multicolumn{6}{p{\textwidth}}{$^d$ Average water use (WU) from the Yellow River for each region. Because of missing data, Sichuan and Jinji were calculated by data from 2004 to 2017.}\\
	  \multicolumn{6}{p{\textwidth}}{$^e$ Ratio of the average water use (WU) from the Yellow River to provincial total water uses.}\\
	  \end{tabularx}\\
\end{table}

\subsection{Institutional shifts impact on water use}\label{result-2}

\begin{figure*}[!htb]
	\centering
	\includegraphics[width=0.9\linewidth]{outputs/main_results2.pdf}
	\caption{
	Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
	\textbf{A.} Water uses of the YRB before and after the institutional shift in 1987 (87-WAS);
	\textbf{B.} Water uses of the YRB before and after the institutional shift in 1998 (98-UBR). Blue lines are statistics derived from water use data; grey lines are estimates from the Differenced Synthetic Control method with economic and environmental background controlled;
	\textbf{C.} Drought intensity in the YRB and drying up events of the Yellow River. The size of the grey bubbles denotes the length of drying upstream.
	}\label{fig:main_results}
\end{figure*}

The total water use of the YRB exhibited a significant difference between the counterfactual prediction and the actual observed value after the two institutional shifts, while the difference was small and insignificant before (see Figures~\ref{fig:main_results}A and B). This indicates that the estimated reconstruction of water use change was robust.
Figure~\ref{fig:main_results}A suggests that the 87-WAS prompted the provinces to withdraw even more water than would have been used without an institutional shift (Figure~\ref{fig:main_results}A).
From 1988 to 1998, on average, while the estimation of annual water use only suggests $887.05~km^3$ billion $m^3$, the observed water use of the YRB provinces reached $938.06$ billion $m^3$ (an increase of $5.75\%$).
However, after the 98-UBR, trends of increasing water use appeared to be effectively suppressed.
From 1998 to 2008, the total observed water use decreased by $6.6$ billion $m^3/yr$ per year, while the estimation of water use still suggests $5.5$ billion $m^3/yr$ increases (Figure~\ref{fig:main_results} B).
The increased water uses after 87-WAS align with the severe dry-up of the surface streamflow from $1987$ to $1998$, a clear indicator of river degradation and environmental crisis (Figure~\ref{fig:main_results}C).
On the other hand, the 98-UBR ended river depletion, despite subsequent increases in drought intensity (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{fig:main_results}C).

\subsection{Heterogeneous effects and interpretation}\label{result-3}

\begin{figure*}[!htb]
	\centering
	\includegraphics[width=0.9\linewidth]{outputs/fig3.pdf}
	\caption{
		Regulating differences for provinces in the YRB.\\
		Red (the 87-WAS) and green (the 98-UBR) bars denote an increased or decreased ratio for actual water use relative to the estimate from the model in the decade after the institutional shift.
		The grey bars indicate the proportions of actual water use for each province relative to their total water use in the decade after the institutional shift.
		The triangles mark the water quotas assigned under the institution, converted to ratios by dividing by their sum.
	}\label{fig:regulating}
\end{figure*}

Our results demonstrate that there are differences in the response patterns of the two changes in the water resources allocation system.
In Figure~\ref{fig:regulating}, the red bar chart (87-WAS) and the green bar chart (98-UBR) respectively represent the increase or decrease ratio of actual water consumption compared to the estimated water use of the DSC model within ten years after the institutional shifts.
The gray bar chart shows the ratio of actual water use by provinces to their total water use in the decade after the two changes; The triangle marks indicate the ratio of the theoretical water resource quota of the province to the total available water in the YRB.\
In the ten years after the 87-WAS, the proportion of water consumption increase (or decrease) compared to that estimated by the DSC model was positively correlated with the proportion of water consumption taken from the YRB at present (partial correlation coefficient was $0.64$, Figure~\ref{fig:regulating}).
From 1987 to 1998, some provinces with high water consumption (e.g., Inner Mongolia and Henan) also showed significant increases in water consumption (Figure~\ref{fig:regulating} and Table~\ref{tab:DSC_summary}), with the average water consumption in four major users (Shandong, Inner Mongolia, Henan, and Ningxia) exceeding the predicted value by $32.14\%$.
However, from 1998 to 2008, almost all provinces experienced a decrease in water consumption (by an average of $16.54\%$).
In addition, the water consumption of each province has a negative correlation with the proportion of water taken from the Yellow River Basin (partial correlation coefficient is $-0.51$).

\begin{table}[!htbp]\footnotesize
	\centering
	\caption{Pre and post treatment root mean squared prediction error (RMSE) for YRB's provinces}\label{tab:DSC_summary}
	\begin{tabularx}{0.8\textwidth}{XXXXXXX}
	  \toprule
			& \multicolumn{3}{c}{87-WAS} & \multicolumn{3}{c}{98-UBR} \\
  \cmidrule{2-7}    province  & \multicolumn{1}{c}{post/pre} & To avg. & \multicolumn{1}{c}{sig.} & \multicolumn{1}{c}{post/pre} & To avg.   & \multicolumn{1}{c}{sig.} \\
	  \midrule
	  Qinghai & 5.26  & =     & FALSE & 5.89  & >     & TRUE \\
	  Gansu & 10.37  & >     & TRUE  & 9.55  & >     & TRUE \\
	  Ningxia & 5.81  & =     & FALSE & 6.83  & >     & TRUE \\
	  Inner Mongolia & 7.11  & >     & TRUE  & 1.60  & <     & TRUE \\
	  Shanxi & 1.72  & <     & TRUE  & 5.60  & >     & TRUE \\
	  Shaanxi & 3.05  & <     & TRUE  & 3.01  & >     & TRUE \\
	  Henan & 20.66  & >     & TRUE  & 1.18  & <     & TRUE \\
	  Shandong & 4.54  & =     & FALSE & 4.14  & >     & TRUE \\
	  \bottomrule
	  \end{tabularx}\label{tab:addlabel}\end{table}
\section{Discussion}\label{sec:discussion}

The impacts of institutional shifts on the governing effects of social-ecological systems (SESs) have been widely reported worldwide, but few attempts have been made to quantify their net effects~\cite{cumming2020a}.
Our case study of the YRB's water governance suggests that while the 98-UBR decreased total water use as expected, the 87-WAS unexpectedly increased it by $5.75\%$, a comparison of which can yield insights into the effectiveness of governance.
Firstly, the results challenge previous analyses (i.e., suggesting that 87-WAS ``had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present~\cite{abadie2015,hill2021}.
However, the significant net effect indicated by our analysis suggests that the 87-WAS was followed by increased water use even after controlling for environmental and economic variables (see \textit{\nameref{secS2}} Table~\ref{tab:variables}).
In contrast, the 98-UBR reduced surface water competition, so many studies attributed the streamflow restoration mainly to the successful introduction of this institution~\cite{chen2021,huangang2002,an2007}.

Examining the unexpected 87-WAS policy, we found it shared a similar structure with many other SES governance failures, supporting the hypothesis that specific mismatched structures can rapidly exhaust common resources~\cite{kellenberg2009,cai2016,barnes2019}.
Generally, these structure-based failures occur when social actors freely access linked resource units (like the institution before 1987), while the monitoring duty of the YRCC after 87-WAS was a sign that water quota was valuable to pursue (between 1987 and 1998).
This conjecture aligns with the increased water use after 87-WAS and the concerns about frequently scrambling for water in some provinces during this period~\cite{mao2000, bouckaert2022}.
A previous study analyzed reasons for the non-ideal effect of 87-WAS~\cite{huangang2002}, where core concerns were the lack of enforcement and controlling approaches, while major stakeholders kept arguing they needed more quotas from 1983 to the 1990s.
It indicates that it was reasonable for stakeholders to pursue more water quota by withdrawing more water, beyond their economic growth.
Our results align with this hypothesis since the correlation between current water use and changed (increased or decreased) water use was significant after the 87-WAS but not after the 98-UBR (Figure~\ref{fig:regulating}).
In addition, through a theoretically marginal benefit analysis, this ``major users use more'' pattern can be inferred from a simple assumption that stakeholders can expect water quota's value in the short future, also supporting the above hypothesis (see \textit{\nameref{secS4}}).

Besides our results, the above hypothesis also aligns with two reported facts:
(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) and the bargaining arguments even persisted years after 1987~\cite{wang2019e, wang2019d}.
During this process, each province attempted to demonstrate its development potential related to water use, to match water shares to their economy because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution)~\cite{zuo2020}.
(2) During the ``bargaining'', more significant stakeholders had considerable
incentives to pursue more water quotas, which aligned with the fact that major water users submitted appeals to the higher central government for larger shares~\cite{wang2019e, wang2019d}.
This means provinces with higher current water use have greater bargaining power in water use allocation.

On the other hand, since the YRCC could coordinate stakeholders by water quota licenses according to water conditions for the entire YRB after 98-UBR, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)~\cite{krieger1955, ostrom1990}.
Similar, proportional decreased water use of provinces and the theoretical minimal water use of marginal benefit model indicated this policy lead to successful governance as expected (see \nameref{result-3}).
However, since the 98-UBR only regulated surface water use, many clues suggested the institution shift may cause broader influences, including estimated increased groundwater withdrawals after 98-UBR in many intensive water use regions~\cite{sun2022b}.
With limited eligible data on groundwater use, related assessment is beyond the scope of this study but remains quite important, as similar water quota policies started to be implemented nationally since the 21st century.

The structural pattern we depicted here (Figure~\ref{fig:structure}) has also been reported in other SESs worldwide~\cite{kluger2020,guerrero2015,bodin2012}.
Before 98-UBR, fragmented ecological units were linked to separate social actors, which more likely led to lower effectiveness because isolated actors generally struggle to maintain interconnected ecosystems holistically~\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
Institutional re-alignments since 98-UBR enhanced the responsibilities of the basin-scale authority (YRCC) and led to effectiveness in runoff restoration, which are usually named scale match or institutional match of SESs~\cite{cumming2020a,wang2019d}.
Taken together, the comparison demonstrates the challenge of finding win-win situations in coupled social-ecological systems~\cite{hegwood2022} and the need to more deeply understand the role of institutions in water governance~\cite{bergsten2019, sayles2019}.

Our approach has some inevitable limitations.
First, the contributions of economic growth and institutional shifts are difficult to distinguish because of intertwined causality (institutional changes can also influence the relative economic variables);
and second, when applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
Our quasi-experiment approach nonetheless provides evidence supporting the view that there was a change in water use trajectory following the YRB's unique institutional shifts and offers insights into water governance (and particularly the importance of having a scale-matched, basin-wide authority for water allocation solutions~\cite{bodin2017b, ostrom2009, reyers2018}).
Moreover, the ultimate success of the 98-UBR institutional shift theoretically and practically proved the importance of social-ecological fit.
For sustainability in the future, it is necessary to emphasize the need to strengthen connections between stakeholders through agents consistent with the scale of the ecological system.
For example, water rights transfers may be another way to build horizontal links between stakeholders that also have the potential to result in better water governance.
In addition, policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to a changing SES context~\cite{reyers2018}.

The structural pattern that led to different effectiveness is widespread in global SESs, making our proposed mechanism crucial to governing such coupled systems.
Our analysis suggests that these initiatives can lead to unexpected results because of mismatched structure when shifting to another institution~\cite{bodin2017b}.
Better governance calls for more institutional analysis while China has embarked to redesign its decades-old water allocation scheme.
Our research provides insights into how institutions can affect achieving successful river basin governance when socio-hydrological interplays frame SES structures~\cite{muneepeerakul2017, leslie2015, hegwood2022}.

\section{Conclusion}\label{sec:conclusion}

In this study, we examined the effects of two major institutional shifts in water governance within the Yellow River Basin (YRB): the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basin Regulation (98-UBR). By employing a Difference-in-Differences approach with Synthetic Control, we quantified the net effects of these institutional shifts on water use within the YRB.\
Our results showed that the 87-WAS unexpectedly increased water use by $5.75\%$, contrary to its intended goals, while the 98-UBR successfully reduced water use as anticipated. The analysis revealed that the structural patterns of the institutions played a critical role in their effectiveness. The mismatched structure of the 87-WAS led to increased competition and exploitation of water resources, while the 98-UBR, with its scale-matched, basin-wide authority and stronger connections between stakeholders, resulted in improved water governance.

In conclusion, our research contributes to a better understanding of the role of institutions in SES governance, particularly in the context of water management. By identifying the key factors that influence the success or failure of institutional shifts, we provide valuable insights for the design of effective and sustainable water governance policies. Future research should continue to explore the intricacies of institutions in SES governance and investigate the potential impacts of additional policies and institutional shifts on water use and sustainability.

\textbf{Authors Contribution}\\
Shuai Wang and BF designed this research. Shuang Song performed the study and analysed data. Shuang Song and Huiyu Wen wrote the paper. Xutong Wu, Cumming S. Graeme, and HW revised and polished the manuscript and gave significant advice.

\textbf{Acknowledgments}\\
This research has been supported by the National Natural Science Foundation of China (grant no. 42041007) and the Fundamental Research Funds for the Central Universities

\bibliography{../mybib}
\bibliographystyle{elsarticle-num}\label{bib}

\newpage
\appendix\label{appendix}

\section{Key points in the documents of 87-WAS and 98-UBR}\label{secS1}
\renewcommand{\thefigure}{A\arabic{figure}}
\renewcommand{\thetable}{A\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}

The official documents in 1987 (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today) convey the following key points:

\begin{itemize}
\item The policy is aimed at related provinces (or regions at the same administrative level).
\item Depletion of the river is identified as the first consideration of this institution.
\item Provinces are encouraged to develop their water use plans based on a quota system.
\item Water in short supply is a common phenomenon in relevant provinces (regions).
\end{itemize}

The official documents in 1998
(\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today) convey the following key points:

\begin{itemize}
\item The document points out that not only provinces and autonomous regions involved in water resources management (see \textit{Article 3}), the provinces’ and regions’ water use shall be declared, organized, and supervised by the YRCC (\textit{Article 11 and Chapter III to Chapter V, and Chapter VII}).
\item Creating the overall plan of water use in the upper, middle, and lower reaches is identified as the first consideration of this institution (\textit{Article 1}).
\item With the same quota as used in the 1987 policy, provinces were encouraged to further distribute their quota into lower-level administrations (see \textit{Article 6 and Article 41}).
\item They emphasize that supply is determined by total quantity, and water use should not exceed the quota proposed in 1987 (see \textit{Article 2}).
\end{itemize}

\newpage
\section{Data source and method details}\label{secS2}
\renewcommand{\thefigure}{B\arabic{figure}}
\renewcommand{\thetable}{B\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}

\begin{table*}[!ht]
	\caption{Variables and their categories for water use predictions}
	\scriptsize
	\label{tab:variables}
	\resizebox{\linewidth}{!}{
	\begin{tabular}{lllll}
	\hline
	Sector &
	  Category &
	  Unit &
	  Description &
	  Variables \\ \hline
	Agriculture &
	  Irrigation Area &
	  thousand ha &
	  \begin{tabular}[c]{@{}l@{}}Area equipped for irrgiation by different \\ crop:\end{tabular} &
	  \begin{tabular}[c]{@{}l@{}}Rice, \\ Wheat, \\ Maize, \\ Fruits, \\ Others.\end{tabular} \\ \hline
	Industry &
	  \begin{tabular}[c]{@{}l@{}}Industrial gross \\ value added\end{tabular} &
	  Billion Yuan &
	  Industrial GVA by industries &
	  \begin{tabular}[c]{@{}l@{}}Textile, \\ Papermaking, \\ Petrochemicals, \\ Metallurgy, \\ Mining, \\ Food, \\ Cements, \\ Machinery, \\ Electronics, \\ Thermal electrivity, \\ Others.\end{tabular} \\
	 &
	  \begin{tabular}[c]{@{}l@{}}Industrial water \\ use efficiency\end{tabular} &
	  \% &
	  \begin{tabular}[c]{@{}l@{}}The ratio of recycled water and evaporated \\ water to total industrial water use\end{tabular} &
	  \begin{tabular}[c]{@{}l@{}}Ratio of industrial water recycling, \\ Ratio of industrial water evaporated.\end{tabular} \\ \hline
	Services &
	  \begin{tabular}[c]{@{}l@{}}Services gross \\ value added\end{tabular} &
	  Billion Yuan &
	  GVA of service activities &
	  Services GVA \\ \hline
	Domestic &
	  Urban population &
	  Million Capita &
	  Population living in urban regions. &
	  Urban pop \\
	 &
	  Rural population &
	  Million Capita &
	  Population living in rural regions. &
	  Rural pop \\
	 &
	  Livestock population &
	  Billion KJ &
	  \begin{tabular}[c]{@{}l@{}}Livestock commodity calories summed from \\ 7 types of animal.\end{tabular} &
	  Livestock \\ \hline
	Environment &
		  Temperature & $K$ & Near surface air temperature & Temperature \\
			& Precipitation & $mm$ & Annual accumulated precipitation & Precipitation \\ \hline
	\end{tabular}}
\end{table*}

\begin{figure*}[!h]
    \includegraphics[width=0.9\linewidth]{outputs/elbow.pdf}
    \centering
    \caption{Choose number of pricipal components by Elbow method, $5$ pricipal components already capture $89.63\%$ explained variance.}\label{fig:elbow}
\end{figure*}

\newpage
\section{Marginal benefit model for water use}\label{secS4}
\renewcommand{\thefigure}{C\arabic{figure}}
\renewcommand{\thetable}{C\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}

For interpretation of the pattern of provincial water uses, we compared the theoretical marginal returns and optimal water use under three different structural cases (case 1 to case 3, corresponding to different SES structures in Figure~\ref{fig:structure}~C).

Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.
As a benchmark, case 1 analogy to a decentralized stakeholders situation and lead to medium-level water use.
In case 2, each stakeholder expects that current water use helps bargain for a favorable water quota in the face of institutional shift (see \textit{\nameref{secS4}}), which can intensify the incentive to use water, leading to higher water use.
Furthermore, the water users with higher capability are more stimulated by the institutional shift and away from the theoretically optimal water use under a unified allocation.
After water-use decisions are consolidated into unified management (case 3), marginal benefits analysis suggests the lowest water use among the cases.

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.6\linewidth]{outputs/economic_model.pdf}
	\caption{
		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}~C) Major water users' theoretically optimal water use is also larger (see the proofs below.)}
\end{figure}

Below are the detailed theoretical model derivation process, where we started from proposing three intuitive and general assumptions:

\begin{ass}
(Water-dependent production) Because of irreplaceability, water is assumed to be the only input of the production function with two types of production efficiency. The production function of a high-incentive province is $A_HF(x)$, and the production function of a low-incentive province is $A_LF(x)$ ($A_H>A_L$). F(x) is continuous, $F'(0)=\infty$, $ F'(\infty)=0$, $F'(x)>0$, and $F''(x)<0$. The production output is under perfect competition, with a constant unit price of $P$.
\end{ass}

\begin{ass}
 (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in $N$ provinces, the cost of water use is equally assigned to each province under any water use. The unit cost of water is a constant $C$.
\end{ass}
\begin{ass}
(Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water use.
\end{ass}

Under the above assumptions, we can demonstrate three cases consisting of local governments in a whole basin to simulate their water use decision-making and water use patterns.

\begin{case} before 1987: This case corresponds to a situation without any high-level water allocation institution.

When each province independently decides on its water use, the optimal water use $x_i^*$ in province $i$ satisfies:

 $AF'(x)=\frac{C}{P}$,

 where $A_H$ and $A_L$ denote high-incentive and low-incentive provinces, respectively.

 When the decisions in different periods are independent, for $t$ = $0, 1, 2 \cdots$, then:

 $x_{it}^* = x_i^*$

 \end{case}

\begin{case} from 1987 to 1998: This case corresponds to an SES structure where fragmented stakeholders are linked to unified river reaches.

 The water quota is determined at $t$=0 and imposed in $t$=1,2, \ldots Under the subjective expectation of each province that current water use may influence the future water allocation determined by high-level authorities, the total quota is a constant denoted as Q, and the quota for province $i$ is determined in a proportional form:

 $Q_i=Q \cdot \frac{x_i}{x_i + \begin{matrix}\sum{x_{-i}} \end{matrix}}$.

Under a scenario with decentralized decision-making with a water quota, given other provinces' decisions on water use remain unchanged, the optimal water use of province $i$ at $t$=0 satisfies:

$AF'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix})^2}$,

where $A_H$ denotes a high-incentive province and $A_L$ denotes a low-incentive province.

\end{case}

\begin{case} after 1998: This case corresponds to the institution under which water use in a basin is centrally managed.

 When the $N$ provinces decide on water use as a unified whole (e.g., the central government completely decides and controls the water use in each province), the optimal water use $x_i^*$ of province $i$ satisfies:

$F'(x)=\frac{C}{P}$.

\end{case}

We propose Proposition 1 and Proposition 2:

Proposition 1: Compared with the decentralized institution, a institution with unified management decreases total water use.

The optimal water use under the three cases implies that mismatched institutions cause incentive distortions and lead to resource overuse.

Proposition 2: Water overuse is higher among provinces with high water use incentives than low- water use incentives under a mismatched institution.

The intuition for this proposition is straightforward in that all provinces would use up their allocated quota under a relatively small $Q$. As production efficiency increases, the marginal benefits of a unit quota increase, and the quota would provide higher future benefits for a pre-emptive water use strategy. Provinces with high production efficiency have higher optimal water use values under the decentralized decision. The divergence in water use would be exaggerated when the water quota is expected to be implemented with greater competition.

When the N provinces decide on water uses as a unity, the marginal cost is C, equal to its fixed unit cost.
The water use of province $i$ aims to maximize $P\cdot A\cdot F(x)-C$.
Hence, $x_i^*$ satisfies $P \cdot A\cdot F'(x)=C$, i.e., $AF'(x)=\frac{C}{P}$, where A denotes $A_H$ for a high-incentive province and $A_L$ for a low-incentive province.

When each of the N provinces independently decides on its water use, the marginal cost of water use would be $\frac{C}{N}$ as a result of cost-sharing with others.
Hence, the optimal water use in province i at period t, denoted as $\hat x_i^*$, satisfies $P \cdot A \cdot F'(x_{it})=\frac{C}{N}$, i.e., $A \cdot F'(x)=\frac{C}{P \cdot N}$.
Since $F'$ is monotonically decreasing, $\hat x_{it}^*>x_i^*$.

When the water quota would constrain future water use, the dynamic optimization problem of province i is shown as follows. In $t=1,2,\cdots$, there would be no relevant cost when the quota is bound that each province takes ongoing costs of $\frac{P \cdot Q}{N}$ regardless of the allocation. Therefore, it is sufficient to consider only the total water quota is less than total water use in Case 2 since a ``too large'' quota doesn't make sense for ecological policies.

$max  \quad P \cdot A \cdot F(x_{i,0})-\frac{C \cdot \begin{matrix} \sum x_{i,0} + x_{-i,0} \end{matrix}}{N}+\beta P \cdot A \cdot F(x_{i,1})+\beta^2 P \cdot A \cdot F(x_{i,2})+...$

$=P \cdot A \cdot F(x_{i,0})-C \cdot \frac{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}{N}+\frac{\beta}{1-\beta} P \cdot A \cdot F(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}})$

First-order condition: $P \cdot A \cdot F'(x_{i,0})-\frac{C}{N}+\frac{\beta}{1-\beta}[P \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0}+\begin{matrix} \sum  x_{-i,0} \end{matrix})^2}]=0$

where $f(\cdot)$ is the differential function of $F(\cdot)$.

The optimal water use in province i at t=0 $\widetilde x_{i,0}^*$ satisfies $P \cdot A \cdot F'(x_{i,0})=\frac{C}{N}-\frac{\beta}{1-\beta} \cdot P \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$,
i.e.,
$A \cdot F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$.

Since $F'>0$ and $F''<0$, $\widetilde x_i^*>\hat x_i^*>x_i^*$, taken others' water use $x_{-i,0}$ as given. Since the provincial water use decisions are exactly symmetric, total water use would increase when each province has higher incentives for current water use.

Proof of Proposition 1:

Because $F'>0$ and $F''(x)<0$ is monotonically decreasing, based on a comparison of costs and benefits for stakeholders (provinces) in the three cases,

$\widetilde x_i^*>\hat x_i^*>x_i^*$.

The result of $\hat x_i^*>x_i^*$ indicates that individual rationality would deviate from collective rationality under unclear property rights where a water user is fully responsible for the relevant costs. The result of $\hat x_i^*>x_i^*$

The difference between $ x_i^*$ and $\hat x_i^*$ stems from two parts: the effect of the marginal returns and the effect of the marginal costs. First, the ``shadow value'' provides additional marginal returns of water use in $t$ = 0, which increases the incentives of water overuse by encouraging bargaining for a larger quota. Second, the future cost of water use would be degraded from $\frac{P}{N}$ to an irrelevant cost.

Proof of Proposition 2:

Since $A_H>A_L$, $F'(x_H)<F'(x_L)$,
Eq.(xxx) implies a positive relation between $x_{i0}$ and A, when $\beta, P, C, Q$, and other provinces' water use are taken as given.

The difference between $\widetilde x_i^*$ and $\hat x_i^*$ (i.e., $\frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$) represents the incentive of water overuse derived from an expectation of water quota allocation. The incentive of water overuse increases by A.

\end{document}

### 2023-07-31 docs/papers/01_manuscript/04_discussion.tex
fix(project): :memo: change nameref into ref

@@
 Firstly, we found significant correlations between current and changed water use after the 87-WAS, which suggests that the key stakeholders (such as Neimeng, Henan, and Shandong), were more likely to be affected by the institutional change.\
-Secondly, a theoretical marginal benefit analysis (see \textit{\nameref{secS4}}) suggests that this ``major users are effected more'' pattern can be inferred from a simple assumption that stakeholders anticipate future value in water quotas, thereby lending further support to the above hypothesis.
+Secondly, a theoretical marginal benefit analysis (see \textit{\ref{secS4}}) suggests that this ``major users are effected more'' pattern can be inferred from a simple assumption that stakeholders anticipate future value in water quotas, thereby lending further support to the above hypothesis.
 Finally, since the YRCC could forcibly coordinate stakeholders by water quota licenses for the entire YRB after 98-UBR, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)~\cite{krieger1955, ostrom1990}.

### 2023-07-31 docs/papers/01_manuscript/06_methods.tex
fix(project): :memo: change nameref into ref

@@
 We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different.
-Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\nameref{secS2}~Figure\ref{fig:elbow}}).
+Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\ref{secS2}~Figure\ref{fig:elbow}}).
 Finally, we transform the dataset and input the dimensions-reduced output into the DSC model.

### 2023-07-31 docs/papers/01_manuscript/out/compiled_v-2.0.2.tex
fix(project): :memo: change nameref into ref

@@
 Firstly, we used data on changes in official documents following two institutional shifts (the 87-WAS and the 98-UBR) to describe comparable changes in the SES structures associated with the YRB from 1979 to 2008, by abstracting them into SES structures motifs (or building blocks, see \textit{\nameref{sec:structures}}).
-We then used a method called `Differenced Synthetic Control (DSC)' \cite{arkhangelsky2021}, which considers economic growth and natural background, to estimate theoretical water use scenarios without institutional shifts (\textit{\nameref{sec:DSC}} and \textit{\nameref{secS2}}).
+We then used a method called `Differenced Synthetic Control (DSC)' \cite{arkhangelsky2021}, which considers economic growth and natural background, to estimate theoretical water use scenarios without institutional shifts (\textit{\nameref{sec:DSC}} and \textit{\ref{secS2}}).
 This approach allowed us to create a counterfactual against which to explore the mechanisms linking SESs structure and outcomes for a deeper understanding of the potential role of institutions in water governance worldwide.
@@
 		Institutional shifts and related SES structures in the Yellow River Basin (YRB).
-		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{\nameref{secS1}} Table~\ref{tab:quota}).
+		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{\ref{secS1}} Table~\ref{tab:quota}).
 The national administrations are the ultimate authority in issuing water governance policies, which are often implemented by basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
@@
 The YRCC only monitors water withdrawals at that time.
-		\textbf{C.} Institutional shifts and following structures changes (details in \textit{\nameref{secS1}}).
+		\textbf{C.} Institutional shifts and following structures changes (details in \textit{\ref{secS1}}).
 (1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from the connected ecological unit (the reach of Yellow River, denoted by the blue circles).
@@
 % 制度变动综述
-The institutional shifts in the YRB in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among YRB's water governance practices (\textit{\nameref{sec:yrb}} and \textit{\nameref{secS1}}).
+The institutional shifts in the YRB in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among YRB's water governance practices (\textit{\nameref{sec:yrb}} and \textit{\ref{secS1}}).
 Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
@@
 	\caption{
-		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\nameref{secS4}}).}
+		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}) Major water users' theoretically optimal water use is also larger (see \nameref{sec:model} and \textit{\ref{secS4}}).}
 	\label{fig:model}
@@
 
-For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (analogy to Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\nameref{secS4}}).
+For interpretation of the pattern, we compared the theoretical marginal returns and optimal water use under three different structural cases (analogy to Figure~\ref{fig:structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{\ref{secS4}}).
 Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.
@@
 The results challenged previous analyses (i.e., suggesting that 87-WAS ''had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present \cite{abadie2015,hill2021}.
-However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{\nameref{secS2}}~Table~\ref{tab:variables}).
+However, the significant net effect indicated by our analysis suggests 87-WAS was followed by more water use even after controlling for environmental and economic variables (see \textit{\ref{secS2}}~Table~\ref{tab:variables}).
 On the contrary, the 98-UBR reduced water competition, so many studies attributed the restoration mainly to the successful introduction of this institution \cite{chen2021,huangang2002,an2007}.
@@
 For sustainability in the future, therefore, it is necessary to emphasize the necessity of strengthening connections between stakeholders by agents consistent with the scale of the ecological system.
-From these perspectives, two scenarios based on the marginal benefit analysis (see \textit{\nameref{secS5}}) can inspire institutional design on how to reduce mismatches.
+From these perspectives, two scenarios based on the marginal benefit analysis (see \textit{\ref{secS5}}) can inspire institutional design on how to reduce mismatches.
 For example, water rights transfers may be another way to build horizontal links between stakeholders that also have the potential to result in better water governance.
@@
 The structural building blocks that led to different outcomes are recurring motifs in global SESs, so our proposed mechanism is crucial to governing such coupled systems.
-Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{\nameref{secS1}}) \cite{yu2019}.
+Calls for a redesign of water allocation institutions in the YRB in recent years also illustrate the importance of institutional solutions for sustainability (see \textit{\ref{secS1}}) \cite{yu2019}.
 Given the changing environmental context, outdated and inflexible water quotas can no longer meet the demands of sustainable development \cite{wang2019e}.
-Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{\nameref{secS1}}).
+Thus, the Chinese government has embarked on a plan to redesign its decades-old water allocation institution (see \textit{\ref{secS1}}).
 Our analysis suggests that these initiatives can benefit by actively incorporating social-ecological matched building blocks when developing new institutions \cite{bodin2017b}.
@@
 The network-based approach is to abstract connections between entities into links and nodes \cite{bodin2017a,kluger2020,guerrero2015}.
-In this study, we examined the official documents of the two institutional shifts of concern (87-WAS and 98-UBR, see \textit{Appendix \nameref{secS1}} for details).
+In this study, we examined the official documents of the two institutional shifts of concern (87-WAS and 98-UBR, see \textit{Appendix \ref{secS1}} for details).
 Besides the ecologically connected river reaches, the agents (provinces and the YRCC) are abstracted as nodes, and their required interactions regarding water use are summarized as links.
@@
 
-Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ principal components \textit{Appendix~\nameref{secS2}}.
+Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ principal components \textit{Appendix~\ref{secS2}}.
 Bayan had proved that combining PCA and DSC can raise the robustness of causal inference \cite{bayani2021}.
 We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different.
-Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\nameref{secS2}~Figure~\ref{fig:elbow}}).
+Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\ref{secS2}~Figure~\ref{fig:elbow}}).
 Finally, we transform the dataset and input the dimensions-reduced output into the DSC model.
@@
 Under the above-simplified assumptions, we demonstrate three cases -corresponding to the abstracted SES structures (Figure~\ref{fig:structure}), inference of how SES structure alters the expected marginal benefits and costs of provinces making decisions.
-As one of the possible interpretations for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\nameref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\nameref{secS5}}.
+As one of the possible interpretations for the causality between SES structure and institutional effects, the derivation of the model based on the above three assumptions can be found in \textit{Appendix~\ref{secS4}}, and some simple model-based extensions are involved in \textit{Appendix~\ref{secS5}}.
 

### 2023-07-31 docs/papers/04_response_letter/source/reviewer_2.tex
fix(project): :memo: change nameref into ref

@@
 
-\AR{} We appreciate your thoughtful suggestion about additional robustness checks for our Differenced Synthetic Control (DSC) method.
-However, we have chosen not to include further robustness checks in our revised manuscript for several reasons:
+\AR{} We appreciate your thoughtful suggestion about additional checks for our Differenced Synthetic Control (DSC) method.
+We now revised the term from ``robustness'' to ``efficiency'' based on the comments from the reviewer \#1, so we basically kept the tests section without additional approach for the following reasons:
 
@@
 Your kind words are greatly encouraging and motivate us to continue to improve our work.
-We hope that the revisions we have made in response to your helpful suggestions have improved the manuscript.
+We've still improved the discussion section, and we hope you'll find this even better.

### 2023-07-31 docs/papers/01_manuscript/01_introduction.tex
fix(project): :pencil2: fix minor comments with typos.
docs(introduction): :memo: polishing texts

@@
 These interactions constitute a type of SES structure, where effective institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different interactions, contributing to sustainability~\cite{epstein2015, wang2019d} (Figure~\ref{fig:framework}~b).
-% (Figure~\ref{fig:framework}~\textbf{a}).
-% Governing river basin systems involves reshaping their SES structures through institutions such as policies, laws, and norms~\cite{,cumming2020b}.
 While some institutional advances have led to effective water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China~\cite{wang2019d}, and collaborative water governance systems in Europe~\cite{green2013}), imposing institutional shifts may create or destroy connections and effectiveness is not ubiquitous~\cite{loos2022}.
@@
 % match & mismatch
-Recent studies have explored diverse effects of institutions on river basin governance~\cite{bouckaert2022, vallury2022, loch2020, kirchhoff2016}, while the current analysis is more about interpreting outcomes after the institutional changes but cannot compare how scenarios would be without these institutional changes.
-Moreover, understanding how different SES structures influence institutional effectiveness is challenging due to the complexity and dynamics of socio-hydrological systems~\cite{bodin2017b}.
+Recent research has delved into the multifaceted effects of institutions on river basin governance, shedding light on diverse consequences and interactions~\cite{bouckaert2022, vallury2022, loch2020, kirchhoff2016}.
+Primarily due to the intricate dynamics within socio-hydrological systems, understanding the manner in which different SES structures influence institutional effectiveness remains a complex challenge~\cite{bodin2017b}.
+The current study contributes to this understanding by interpreting outcomes following institutional changes, though it does not explore hypothetical scenarios without such changes.
 Thus, knowledge gaps lie in the limited understanding of effective alignments between institutional shifts and SES structures, hindering the design of effective policies to promote sustainable river basin governance.
-To fill these knowledge gaps, we study the Yellow River basin, the fifth-largest river worldwide and one of the most anthropogenically altered river basins, to quantitatively measure the effects of changing SES structures.
+To fill these knowledge gaps, we study the fifth-largest river worldwide and one of the most anthropogenically altered river basins, the Yellow River Basin (YRB) in China, to quantitatively measure the effects of changing SES structures.
 
@@
 In this study, we specifically examined two significant institutional shifts in water allocation of the YRB\: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulating (98-UBR).
-the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulating (98-UBR).
 Instead of focusing on engineering and increasing water supply, the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, an authority at a basin level) mainly aimed to limit water demands~\cite{bouckaert2022, speed2013}.

### 2023-07-31 docs/papers/01_manuscript/manuscript.tex
fix(project): :bug: Checking math by Yinan Xiao
docs(introduction): :memo: polishing texts

@@
      We employ a Differenced Synthetic Control method to assess the impacts of the institutional shifts.
-Our analysis reveals that the 87-WAS unexpectedly increased water use by $5.75\%$, while the 98-UBR successfully reduced water use as anticipated.
-Our research highlights the role of institutional structures in governance policies, demonstrating that the mismatched structure of the 87-WAS led to increased competition and exploitation of water resources, while the 98-UBR, with its scale-matched, basin-wide authority and stronger connections between stakeholders, resulted in improved water governance.
+Our analysis suggests that the 87-WAS unexpectedly increased water use by $5.75\%$, while the 98-UBR successfully reduced water use as anticipated.
+Our research highlights the role of institutional structures in governance policies, demonstrating that the mismatched structure of the 87-WAS led to increased competition and exploitation of water resources, while the 98-UBR, basin-wide authority and stronger connections between stakeholders, resulted in improved water governance.
      Our study underscores the importance of designing institutions that are consistent with the scale of the ecological system, promote cooperation among stakeholders, and adapt to changing social-ecological system (SES) contexts.
-As outdated and inflexible water quotas may no longer meet the demands of sustainable development in the YRB, governments and policymakers must consider the potential consequences of institutional shifts and their impact on water use and sustainability.
+As outdated and inflexible water quotas may no longer meet the demands of sustainable development in the YRB, policymakers must consider the potential consequences of institutional shifts and their impact on water use and sustainability.
 \end{abstract}
@@
 \textbf{Acknowledgments}\\
-This research has been supported by the National Natural Science Foundation of China (grant no. 42041007) and the Fundamental Research Funds for the Central Universities
+This research has been supported by the National Natural Science Foundation of China (grant no. 42041007) and the Fundamental Research Funds for the Central Universities.
 

### 2023-07-31 docs/papers/01_manuscript/06_methods.tex
docs(method): :memo: polish method description

@@
 
-In the methodology section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as organizational diagrams during different periods of time.
+In this section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as organizational diagrams during different periods of time.
 Next, we introduce the dataset we used here and employ the Principal Components Analysis (PCA) method to reduce the dimensionality of variables affecting the total water use.
 We then estimate the net effects of the two institutional shifts on total water use, changing trends, and differences in the YRB's provinces using the Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021}.
-Finally, we present the efficiency tests approach for the DSC model.
+Finally, we introduce the tests approach for validating efficiency of the DSC model.
 % Finally, for discussion, we developed a marginal benefit analysis based on identified SES structures to provide the observed pattern of water use changes with a theoretical interpretation.
@@
 We examined the official documents of the two institutional shifts (87-WAS and 98-UBR) to portray the organizational diagrams in this study~\cite{bodin2017a,kluger2020,guerrero2015}.
-It is important to note that it can result in very different structures when basin-scale regulatory entity (YRCC) is responsible for river reach regulation, or have direct authority to interact with provincial units.
+It is important to note that it can result in nuanced different structures when basin-scale regulatory entity (YRCC) is responsible for river reach regulation, or have direct authority to interact with provincial units.
 
@@
 The data of water consumption surveys conducted by the Ministry of Water Resources were taken as the observed values throughout the years.
-Then, to estimate the water use of the YRB by assuming there were no effects from institutional shifts, we focused on variables from five categories (environmental, economic, domestic, and technological) water use factors.
-Their specific items and origins are listed in~\ref{secS2}~Table~\ref{tab:variables}.
+Then, to estimate the water use of the YRB by assuming there were no effects from institutional shifts, we focused on $24$ variables from $5$ categories (environmental, economic, domestic, and technological) water use factors~(\textit{\ref{secS2}, Table~\ref{tab:variables}}).
 Among the total $31$ data-accessible provinces (or regions) assigned quotas in the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin and Beijing (together, Jinji) because of their trivial water use from the YRB (see Table~\ref{tab:quota}).
@@
 
-Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $D = 5$ principal components.
 Previous study has proved that combining PCA and DSC can lead to a more robust causal inference~\cite{bayani2021}.
 We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different.
-Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\ref{secS2}~Figure\ref{fig:elbow}}).
-Finally, we transform the dataset and input the dimensions-reduced output into the DSC model.
+Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components $D$ (\textit{Appendix~\ref{secS2}~Figure\ref{fig:elbow}}).
+Finally, all $24$ normalized variables were reduced into $D = 5$ primary components where $89.63\%$ variance was explained, and we use this transformed dataset as input of the DSC model.
 
@@
 Think of it as creating an alternate reality or a ``what-if'' scenario to compare with what actually happened~\cite{abadie2010, abadie2015, hill2021}.
-The key idea behind this method is to evaluate the effects of policy changes that mainly affect certain units (in this case, the institutional shifts in the Yellow River Basin or YRB).
+The key idea behind this method is to evaluate the effects of policy changes (in this case, the 87-WAS and the 98-UBR) that mainly affect certain units (the provinces in the YRB).
 The method creates a ``synthetic'' version of the affected units by combining information from other similar but unaffected units.
 This ``synthetic'' version serves as a control group, which we can compare with the actual affected units.
-The DSC method, therefore, is a powerful tool as it allows us to control for unobserved factors that can change over time, providing more robust results.
+The DSC method, therefore, is a powerful tool as it allows us to control for unobserved factors that can change over time.
 
-In practice, all treated units (i.e., provinces) were affected by institutional shifts in 1987 and 1998, each taken as the ``shifted'' time $T_0$ within two individually analyzed periods $1, 2, \dots, T_0, T_0 + 1, \dots, T$: from 1979 to 1998; from 1987 to 2008.
-We separately include each of the eight provinces in the YRB (see \textit{\nameref{sec:dataset}}) as individual treated units~\cite{abadie2021}.
-Then, we consider the $J+1$ units observed in time periods $1, \dots, T$ where the remaining $J=20$ units represent untreated provinces from outside the YRB.\
-% We define $T_0$ to represent the number of pre-treatment periods ($1,\ldots,t_0$) and $T_1$ the number post-treatment periods ($t_0, \ldots, T$), such that $T = T_0+ T_1$.
-The treated unit is exposed to the institutional shift in every post-treatment period $T_0 +1, \dots, T$, unaffected by the institutional shift in all preceding periods $1, 2, \dots, T_0$.
-Then, any weighted average of the control units is a synthetic control and can be represented by a ($J \times 1$) vector of weights $\mathbf{W} = (w_{1}, \ldots ,w_{J})$, with $w_j \in (0, 1)$ and $w_1 + \cdots  + w_{J} = 1$.
-We denote $k$ is $T * D$ number of covariates, in which $D$ is number of dimensions of the dataset (i.e., $D = 5$ in this case).
-Introducing a ($k \times 1$) non-negative vector $\mathbf{V}$ ($\mathbf{V} = v_{1}, \ldots ,v_{k}$) and $v_1 + \cdots  + v_{k} = 1$ that signifies the relative importance of each covariate.
-% 接下来的目标就是求一个权重矩阵W，让它来表示控制组各单位的权重，使这些权重构成我们需要的“合成”版本的控制组
-The next goal is finding the optimal synthetic control ($\mathbf{W}$) which represents the ``synthetic'' versions of the affected provinces in the YRB.\
+In practice, we consider two distinct institutional shifts that affected all treated units (i.e., provinces in the YRB) in 1987 and 1998.
+Each institutional shift (87-WAS or 98-UBR) is designated as the ``shifted'' time $T_0$, and we individually analyzed two periods: from 1979 to 1998; from 1987 to 2008.
+We include each of the eight provinces in the YRB as separate treated units~\cite{abadie2021} and define the $J+1$ units observed in a time period $1, 2, \dots, T_0, T_0 + 1, \dots, T$, where the remaining $J=20$ units represent untreated provinces outside the YRB.\
+
+The treated unit is exposed to the institutional shift in every post-treatment period $T_0 +1, \dots, T$, and unaffected by the institutional shift in preceding periods $1, 2, \dots, T_0$.
+Any weighted average of the control units is referred as a synthetic control and is denoted by a ($J \times 1$) vector of weights $\mathbf{W} = (w_{1}, \ldots ,w_{J})$, satisfying $w_j \in (0, 1)$ and $w_1 + \cdots  + w_{J} = 1$.
+We also introduce a a ($k \times 1$) non-negative vector $\mathbf{V} = v_{1}, \ldots ,v_{k}$ where $k$ is the product of $T$ and $D$, the number of years and dimensions in the dataset ($D = 5$ in this case).
+The vector $\mathbf{V}$ must fulfill $v_1 + \cdots  + v_{k} = 1$, reflecting the relative importance of each covariate.
+The next goal is finding the optimal $\mathbf{W}$ which represents the best ``synthetic'' versions of the affected provinces in the YRB:\
 
@@
 
-Here, $\mathbf{X_1}$ is the pre-treatment average of each variable in the dataset for the treated unit, while $\mathbf{X_0}$ is a ($k \times J$) matrix containing the pre-treatment characteristics for each of the $J$ control units; $\mathbf{W}^{*}(V)$ is the vector of weights $\mathbf{W}$ that minimizes the difference between the pre-treatment characteristics of the treated unit and the synthetic control, given $\mathbf{V}$.
+Here, matrix $\mathbf{X_1}$ represents the pre-treatment average of each dimension in the dataset for the treated unit, while $\mathbf{X_0}$ is a ($k \times J$) matrix containing the pre-treatment characteristics for each of the $J$ control units.
+We also define $\mathbf{W}^{*}(V)$ as the vector of weights $\mathbf{W}$ that minimizes the discrepancy between the pre-treatment characteristics of the treated unit and the synthetic control for a given $\mathbf{V}$.
 That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W^{*}(V)}$.
@@
 \begin{equation}
+    % https://github.com/OscarEngelbrektson/SyntheticControlMethods/issues/18 这里和README不一样，因为它有问题
     \mathbf{V}^{*}=\underset{\mathbf{V} \in \mathcal{V}}{\operatorname{argmin}}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)^{\prime}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)
@@
 
-That is the minimum difference between the water uses of treated units and the synthetic controls in the pre-treatment period, where $\mathbf{Z}_{1}$ is a matrix containing every observation of the water use for the treated unit in the pre-treatment period $T_0$.
-Similarly, $\mathbf{Z}_{0}$ is a ($J \times T_0$) matrix contains the water use for each control unit in the pre-treatment period.
-% https://github.com/OscarEngelbrektson/SyntheticControlMethods/issues/18 这里和README不一样，因为它有问题
+That is the minimum difference between the water uses of treated units and the synthetic controls in the pre-treatment period ($1, 2, \dots, T_0$), where $\mathbf{Z}_{1}$ is a matrix containing every observation of the water use for the treated unit.
+Similarly, $\mathbf{Z}_{0}$ is a ($J \times T_0$) matrix contains the water use for each control unit in this period.
 The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with better robustness~\cite{billmeier2013, smith2015}.
-In this study, we adopted the minimization by the ``Synthetic Control Methods'' Python library (version 1.1.17)~\cite{engelbrektson2023}.
+In this study, we adopted the algorithm by the ``Synthetic Control Methods'' Python library (version 1.1.17)~\cite{engelbrektson2023} for the minimization.
 
@@
 
-Two primary methods can be employed to validate the efficiency of the DSC approach.
+The efficiency of the DSC approach can be validated using two primary methods.
 
-Firstly, the reconstruction effect on inferred variables (water consumption here) before and after treatment (the interventions of 87-WAS and 98-UBR) can be compared.
-If there are small gaps between the predicted and observed values before treatment, and a large gap after treatment, it indicates that the policy intervention's effect is apparent.
-In this study, to determine whether the intervention effect is significant, the paired sample $T$ test is used to calculate statistics, comparing the model predictions and actual observation data in the periods before and after institutional interventions for both the 87-WAS in $1987$ and 98-UBR in $1998$.
-An effective result would be one where a significant difference is observed after treatment but not before treatment.
-If this is not the case, it implies that the institutional changes were ineffective for the treated units.
+The first method involves comparing the reconstruction effect on the inferred variables (in this case, water consumption) before and after the interventions of 87-WAS and 98-UBR.\
+Small gaps between predicted and observed values before treatment, coupled with a large gap after treatment, would signal the apparent effect of the policy intervention.
+Specifically, this study employs the paired sample T test to calculate statistics that compare model predictions and actual observation data in the periods before and after both institutional interventions in 1987 (87-WAS) and 1998 (98-UBR).
+A significant difference observed after treatment, but not before, indicates that the policy was effective.
+If this pattern is not found, it suggests that the institutional changes did not impact the treated units.
 
-Secondly, placebo tests are another common way to evaluate the effectiveness of synthetic control methods~\cite{abadie2010}.
-Placebo units are selected from the control unit pool and substituted for the treated unit, applying the synthetic control method to the placebo unit using the same data and parameters as the treated unit.
-If the synthetic control method is effective, there should be a clear difference between the placebo unit and the control unit since the placebo unit should not be affected by the intervention.
-% Placebo tests can be used to assess the effectiveness of the synthetic control method and detect any bias or confounding factors in the analysis.
-In this study, we adopt the placebo test step suggested by Abadie when proposing the synthetic control method~\cite{abadie2010} and utilize the Python library of the differential synthetic control method for the placebo test.
-If the ratio of the root mean square error (see Equation~\ref{ch5:eq:RMSE}) in the pre-synthesis period is significantly higher for most provinces (again using the $T$ test to determine the significance of the difference) than the results of other placebo units, the provinces in the YRB was more significantly affected than most other provinces during the treatment periods ($1987$ and $1998$), i.e., more effective.
+The second method involves using placebo tests, a standard procedure for assessing the effectiveness of synthetic control methods~\cite{abadie2010}.
+Placebo units are drawn from the control unit pool and substituted for the treated unit.
+The synthetic control method is then applied to the placebo unit using the same data and parameters as the treated unit.
+No significant difference between the placebo and control units, given that the placebo unit should not be influenced by the intervention, would demonstrate the method's effectiveness.
+In this study, we follow the placebo test approach suggested by Abadie~\cite{abadie2010} and utilize the same Python library~\cite{engelbrektson2023} to perform this.
+If the ratio of the Root Mean Square Error (RMSE) (see Equation~\ref{ch5:eq:RMSE}) in the post/pre -treated period is significantly higher for most treated provinces (using the T test to assess significance) compared to other placebo units, it implies that the provinces in the YRB were significantly affected during the treatment periods (1987 and 1998), thus indicating effectiveness.
 
@@
 
-Where $n$ is the observed number, $y_i$ is the actual value, and $\hat{y}_i$ is the predicted value.
+Where $n$ is the observed number, $y_i$ is the observed value, and $\hat{y}_i$ is the predicted value.

### 2023-07-31 docs/papers/01_manuscript/04_discussion.tex
docs(discussion): :memo: polish disscusion and conclusion

@@
 
-% \subsection{CAUSES OF INSTITUTIONAL IMPACTS}
-% \subsection{}
-% discussion-1:
-% 用水量的上升、下降-结果解读
-% 制度对社会生态系统的结果产生影响在世界范围内都很普遍，
 The impacts of institutional shifts on the governing effects of social-ecological systems (SESs) have attracted global attention, yet efforts to quantify their net effects remain sparse~\cite{cumming2020a}.
@@
 
-The above analysis with a real-world example underscores the crucial role of institutions in water governance by shaping SES structures.
-The structural pattern we depicted here (Figure~\ref{fig:structure}) has also been reported in other SESs worldwide~\cite{kluger2020,guerrero2015,bodin2012}.
-Before 98-UBR, fragmented ecological units were linked to separate social actors, which more likely led to lower effectiveness because isolated actors generally struggle to maintain interconnected ecosystems holistically~\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
-Institutional re-alignments since 98-UBR enhanced the responsibilities of the basin-scale authority (YRCC) and led to effectiveness in runoff restoration, which are usually named scale match or institutional match of SESs~\cite{cumming2020a,wang2019d}.
-Taken together, the comparison demonstrates the challenge of finding win-win situations in coupled social-ecological systems~\cite{hegwood2022} and the need to more deeply understand the role of institutions in water governance~\cite{bergsten2019, sayles2019}.
+The above analysis with a real-world example emphasizes the vital role of institutions in shaping the socio-ecological systems (SES) structures of water governance.
+The structural pattern we have depicted (Figure~\ref{fig:structure}), mirrored in other SESs worldwide~\cite{kluger2020,guerrero2015,bodin2012}, illustrates how fragmented ecological units linked to isolated social actors can lead to inefficiencies.
+Before the 98-UBR, this fragmentation resulted in lower effectiveness, as disconnected actors struggled to maintain holistic ecosystems~\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
+After the 98-UBR, institutional realignments enhanced basin-scale authority (YRCC), fostering effectiveness in runoff restoration—a phenomenon often termed scale or institutional match in SESs~\cite{cumming2020a,wang2019d}.
+This comparison underscores the complex challenges of crafting win-win scenarios in SES and accentuates the importance of understanding institutional roles in water governance~\cite{hegwood2022,bergsten2019, sayles2019}.
 
-Our approach has some inevitable limitations.
-First, the contributions of economic growth and institutional shifts are difficult to distinguish because of intertwined causality (institutional changes can also influence the relative economic variables);
-and second, when applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
-Our quasi-experiment approach nonetheless provides evidence supporting the view that there was a change in water use trajectory following the YRB's unique institutional shifts and offers insights into water governance (and particularly the importance of having a scale-matched, basin-wide authority for water allocation solutions~\cite{bodin2017b, ostrom2009, reyers2018}).
-Moreover, the ultimate success of the 98-UBR institutional shift theoretically and practically proved the importance of social-ecological fit.
-For sustainability in the future, it is necessary to emphasize the need to strengthen connections between stakeholders through agents consistent with the scale of the ecological system.
-For example, water rights transfers may be another way to build horizontal links between stakeholders that also have the potential to result in better water governance.
-In addition, policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to a changing SES context~\cite{reyers2018}.
+Our approach acknowledges certain limitations, such as the difficulty in quantifying contributions from economic growth, and challenges in isolating the effects from other concurrent policies in 1987 and 1998.
+Despite these constraints, our quasi-experimental methodology elucidates the change in water use following the YRB's unique institutional shifts.
+It offers critical insights into water governance, emphasizing scale-matched, basin-wide authority for water allocation solutions~\cite{bodin2017b, ostrom2009, reyers2018}.
+The success of the 98-UBR shift underscores the need for social-ecological alignment, fostering sustainable governance.
+Future endeavors must focus on strengthening stakeholder connections, exploring alternative solutions like water rights transfers, and embracing more dynamic and adaptable institutional frameworks to respond to evolving SES contexts~\cite{reyers2018}.
 
-The structural pattern that led to different effectiveness is widespread in global SESs, making our proposed mechanism crucial to governing such coupled systems.
-Our analysis suggests that these initiatives can lead to unexpected results because of mismatched structure when shifting to another institution~\cite{bodin2017b}.
-Better governance calls for more institutional analysis while China has embarked to redesign its decades-old water allocation scheme.
-Our research provides insights into how institutions can affect achieving successful river basin governance when socio-hydrological interplays frame SES structures~\cite{muneepeerakul2017, leslie2015, hegwood2022}.
+The diverse effectiveness of structural patterns, as observed in global SESs, underscores the necessity for nuanced governance in coupled systems.
+The potential for unexpected outcomes due to institutional mismatches calls for thorough institutional analysis.
+As China seeks to overhaul its water allocation schemes, our research serves as a timely beacon, highlighting how nuanced institutional interplays can shape successful river basin governance, resonating with the global challenge of socio-hydrological complexities~\cite{muneepeerakul2017, leslie2015, hegwood2022}.

### 2023-07-31 docs/papers/01_manuscript/05_conclusion.tex
docs(discussion): :memo: polish disscusion and conclusion

--- 2023-04-22 docs/papers/01_manuscript/05_conclusion.tex
@@
 %! Date = 2022/3/10
-Our study emphasizes the importance of social-ecological system (SES) structures in effective water resource management.
-By examining the Yellow River Basin (YRB) in China as a case study, we found that the 1987 Water Allocation Scheme (87-WAS) led to an 5.75\% increase in observed water use, while the 1998 Unified Basinal Regulation (98-UBR) effectively reduced total water use.
-Our findings highlight the critical role of well-designed SES structures in driving water resource management outcomes.
-To achieve sustainability, we recommend avoiding fragmented ecological units linked to separated social actors and underscore the need for a deeper understanding of the underlying processes and relationships in SES structures for effective water governance.
+
+In this investigation of the Yellow River Basin (YRB), we meticulously examined the impacts of two institutional shifts in water governance: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basin Regulation (98-UBR).
+Utilizing the Differenced Synthetic Control (DSC) approach, we were able to quantify the discrete effects of these transitions on water consumption within the basin.
+Our findings suggest a paradoxical increase in water use by 5.75\%, attributed to the 87-WAS, defying its original objectives.
+Conversely, the 98-UBR efficaciously diminished water usage in line with its intended outcomes.
+This analysis unearthed the pivotal role that institutional structural patterns play in determining their efficacy.
+Specifically, the misaligned structure of 87-WAS inadvertently fostered increased rivalry and exploitation of water resources.
+Meanwhile, the 98-UBR, characterized by its scale-matched, basin-wide coordination and reinforced stakeholder connections, fostered restoration of the Yellow River.
+
+In sum, our study sheds new light on the complex dynamics of institutions within socio-ecological systems (SES) governance, with an emphasis on water allocation.
+By unraveling the essential components that govern the triumph or downfall of institutional transformations, we furnish invaluable insights that can guide the crafting of sustainable water governance policies.
+These findings beckon further exploration into the multifaceted nature of institutional behavior in SES governance, and how future policy adjustments and institutional metamorphoses might sculpt the efficiency of water utilization and sustainability.

### 2023-07-31 docs/papers/04_response_letter/source/reviewer_1.tex
fix(project): :memo: update response linenos

@@
 
-\RC{} In Eq 1, $X_0$ and $X_1$ were never defined.
+\RC*{} In Eq 1, $X_0$ and $X_1$ were never defined.
 
-\RC{} Using ``$*$'' to denote the dimension of a matrix (e.g., $k*k$) is a bit odd; please consider using a multiplication symbol, e.g., $k \times k$.
+\RC*{} Using ``$*$'' to denote the dimension of a matrix (e.g., $k*k$) is a bit odd; please consider using a multiplication symbol, e.g., $k \times k$.
 
-\AR{} We have revised the description of the DSC method to make it clearer and more comprehensive.
+\AR{} [page 6 to 8, lines 124 to 185] We have revised the description of the DSC method to make it clearer and more comprehensive.
 We expanded on the purpose and process of the DSC method, provided more context on how it fits into our research, and clarified the mathematical notation.
@@
 
-\begin{quote}[page=5, sline=89, eline=91]
-    In the methodology section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as organizational diagrams during different periods of time.
+\begin{quote}[page=5, sline=90, eline=92]
+    In this section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as organizational diagrams during different periods of time.
 \end{quote}
 
-\begin{quote}[page=5, sline=98, eline=99]
+\begin{quote}[page=5, sline=99, eline=100]
     An organizational diagram is widely used to depict SES structures by abstracting links and nodes from the real-world interactions~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
@@
 
-\begin{quote}[page=5, sline=99, eline=103]
+\begin{quote}[page=5, sline=100, eline=105]
     We apply the analysis of the organizational diagrams~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit at the basin scale (the Yellow River Conservancy Commission) into structural patterns from official documents.
@@
 
-\begin{quote}[page=7, sline=162, eline=163]
-    Two primary methods can be employed to validate the efficiency of the DSC approach.
+\begin{quote}[page=7, sline=163]
+    The efficiency of the DSC approach can be validated using two primary methods.
 \end{quote}
 
-\begin{quote}[page=8, sline=169, eline=172]
-    An effective result would be one where a significant difference is observed after treatment but not before treatment.
-If this is not the case, it implies that the institutional changes were ineffective for the treated units.
+\begin{quote}[page=8, sline=170, eline=172]
+    A significant difference observed after treatment, but not before, indicates that the policy was effective.
+    If this pattern is not found, it suggests that the institutional changes did not impact the treated units.
 \end{quote}
@@
 \begin{quote}[page=8, sline=180, eline=184]
-    If the ratio of the root mean square error (see Equation~3) in the pre-synthesis period is significantly higher for most provinces (again using the $T$ test to determine the significance of the difference) than the results of other placebo units, the provinces in the YRB was more significantly affected than most other provinces during the treatment periods ($1987$ and $1998$), i.e., more effective.
+    If the ratio of the Root Mean Square Error (RMSE) (see Equation 3) in the post/pre -treated period is significantly higher for most treated provinces (using the T test to assess significance) compared to other placebo units, it implies that the provinces in the YRB were significantly affected during the treatment periods (1987 and 1998), thus indicating effectiveness.
 \end{quote}
@@
 \begin{quote}[page=8, sline=173, eline=174]
-    Secondly, placebo tests are another common way to evaluate the effectiveness of synthetic control methods~\cite{abadie2010}.
+    The second method involves using placebo tests, a standard procedure for assessing the effectiveness of synthetic control methods~\cite{abadie2010}.
 \end{quote}
@@
 
-\begin{quote}[page=4, sline=74, eline=75]
+\begin{quote}[page=4, sline=75, eline=76]
     In $1980s$, the central government proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019d, wang2019e}.
@@
 
-\begin{quote}[page=8, sline=169, eline=172]
-    An effective result would be one where a significant difference is observed after treatment but not before treatment.
-If this is not the case, it implies that the institutional changes were ineffective for the treated units.
+\begin{quote}[page=8, sline=170, eline=172]
+    A significant difference observed after treatment, but not before, indicates that the policy was effective.
+    If this pattern is not found, it suggests that the institutional changes did not impact the treated units.
 \end{quote}
@@
 
-\begin{quote}[page=10, sline=208, eline=210]
+\begin{quote}[page=10, sline=207, eline=209]
     From 1988 to 1998, on average, while the estimation of annual water use only suggests $887.05$ billion $m^3$, the observed water use of the YRB provinces reached $938.06$ billion $m^3$ (an increase of $5.75\%$).
@@
 
-\begin{quote}[page=14, sline=267, eline=270]
+\begin{quote}[page=14, sline=266, eline=269]
     Secondly, a theoretical marginal benefit analysis (see \textit{Appendix C}) suggests that this ``major users are effected more'' pattern can be inferred from a simple assumption that stakeholders anticipate future value in water quotas, thereby lending further support to the above hypothesis.
-.
 \end{quote}

### 2023-07-31 docs/papers/04_response_letter/source/reviewer_2.tex
fix(project): :memo: update response linenos

@@
 
-\begin{quote}[page=6, sline=124, eline=133]
+\begin{quote}[page=6, sline=124, eline=132]
     The Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021} is a tool we use to estimate how water use might have evolved if there had been no institutional shift.
     Think of it as creating an alternate reality or a ``what-if'' scenario to compare with what actually happened~\cite{abadie2010, abadie2015, hill2021}.
-    The key idea behind this method is to evaluate the effects of policy changes that mainly affect certain units (in this case, the institutional shifts in the Yellow River Basin or YRB).
+    The key idea behind this method is to evaluate the effects of policy changes (in this case, the 87-WAS and the 98-UBR) that mainly affect certain units (the provinces in the YRB).
     The method creates a ``synthetic'' version of the affected units by combining information from other similar but unaffected units.
 This ``synthetic'' version serves as a control group, which we can compare with the actual affected units.
-    The DSC method, therefore, is a powerful tool as it allows us to control for unobserved factors that can change over time, providing more robust results.
+    The DSC method, therefore, is a powerful tool as it allows us to control for unobserved factors that can change over time.
 \end{quote}
@@
 \AR{} We appreciate your thoughtful suggestion about additional checks for our Differenced Synthetic Control (DSC) method.
-We now revised the term from ``robustness'' to ``efficiency'' based on the comments from the reviewer \#1, so we basically kept the tests section without additional approach for the following reasons:
+We now revised the term from ``robustness'' to ``efficiency'' based on the comments from the reviewer \#1, so we basically kept the previous testing approaches for the following reasons:
 

### 2023-11-01 docs/papers/01_manuscript/manuscript_v-7.2.2.tex
fix(method): :memo: fixing submission problems

--- 2023-07-29 docs/papers/01_manuscript/manuscript_v-7.1.2.tex
@@
 
-\graphicspath{{../../../figs/}}
 \journal{Jounral of Hydrology}
@@
 
-Recent studies have explored diverse effects of institutions on river basin governance~\cite{bouckaert2022, vallury2022, loch2020, kirchhoff2016}, while the current analysis is more about interpreting outcomes after the institutional changes but cannot compare how scenarios would be without these institutional changes.
-Moreover, understanding how different SES structures influence institutional effectiveness is challenging due to the complexity and dynamics of socio-hydrological systems~\cite{bodin2017b}.
+Recent research has delved into the multifaceted effects of institutions on river basin governance, shedding light on diverse consequences and interactions~\cite{bouckaert2022, vallury2022, loch2020, kirchhoff2016}.
+Primarily due to the intricate dynamics within socio-hydrological systems, understanding the manner in which different SES structures influence institutional effectiveness remains a complex challenge~\cite{bodin2017b}.
+The current study contributes to this understanding by interpreting outcomes following institutional changes, though it does not explore hypothetical scenarios without such changes.
 Thus, knowledge gaps lie in the limited understanding of effective alignments between institutional shifts and SES structures, hindering the design of effective policies to promote sustainable river basin governance.
-To fill these knowledge gaps, we study the Yellow River basin, the fifth-largest river worldwide and one of the most anthropogenically altered river basins, to quantitatively measure the effects of changing SES structures.
+To fill these knowledge gaps, we study the fifth-largest river worldwide and one of the most anthropogenically altered river basins, the Yellow River Basin (YRB) in China, to quantitatively measure the effects of changing SES structures.
 
@@
 The YRB was the first basin in China for which water resource allocation institutions were created, and institutional shifts can be traced through several regulating documents released by the Chinese government (at the national level):
-(1) In $1980s$, proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019d, wang2019e}.
+(1) In $1980s$, the central government proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019d, wang2019e}.
 (2) In $1987$, the Water Allocation Scheme was implemented (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
@@
 
-In the methodology section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as point-axis networks during different periods of time.
+In this section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as organizational diagrams during different periods of time.
 Next, we introduce the dataset we used here and employ the Principal Components Analysis (PCA) method to reduce the dimensionality of variables affecting the total water use.
 We then estimate the net effects of the two institutional shifts on total water use, changing trends, and differences in the YRB's provinces using the Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021}.
-Finally, we present the robustness tests approach for the DSC model.
+Finally, we introduce the tests approach for validating efficiency of the DSC model.
 
 \subsection{Portraying structures}\label{sec:structures}
-A point-axis network type structure of SES is widely used to depict them by abstracting links and nodes~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
-We apply the network approach~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit at the basin scale (the Yellow River Conservancy Commission) into structural patterns from official documents.
-The network-based approach abstracts connections between entities into links according to their interactions~\cite{bodin2017a,kluger2020,guerrero2015}, so we examined the official documents of the two institutional shifts (87-WAS and 98-UBR) to portray these interactions in this study.
-It is important to note that it can result in very different structures when basin-scale regulatory entity (YRCC) is responsible for river reach regulation, or have direct authority to interact with provincial units.
+
+An organizational diagram is widely used to depict SES structures by abstracting links and nodes from the real-world interactions~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
+We apply the analysis of the organizational diagrams~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit at the basin scale (the Yellow River Conservancy Commission) into structural patterns from official documents.
+We examined the official documents of the two institutional shifts (87-WAS and 98-UBR) to portray the organizational diagrams in this study~\cite{bodin2017a,kluger2020,guerrero2015}.
+It is important to note that it can result in nuanced different structures when basin-scale regulatory entity (YRCC) is responsible for river reach regulation, or have direct authority to interact with provincial units.
 
@@
 The data of water consumption surveys conducted by the Ministry of Water Resources were taken as the observed values throughout the years.
-Then, to estimate the water use of the YRB by assuming there were no effects from institutional shifts, we focused on variables from five categories (environmental, economic, domestic, and technological) water use factors.
-Their specific items and origins are listed in~\ref{secS2}~Table~\ref{tab:variables}.
+Then, to estimate the water use of the YRB by assuming there were no effects from institutional shifts, we focused on $24$ variables from $5$ categories (environmental, economic, domestic, and technological) water use factors~(\textit{\ref{secS2}, Table~\ref{tab:variables}}).
 Among the total $31$ data-accessible provinces (or regions) assigned quotas in the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin and Beijing (together, Jinji) because of their trivial water use from the YRB (see Table~\ref{tab:quota}).
 
-Using the normalized data of all variables, we performed the PCA reduction to capture $89.63\%$ explained variance by $5$ principal components.
-Previous study has proved that combining PCA and DSC can raise the robustness of causal inference~\cite{bayani2021}.
+Previous study has proved that combining PCA and DSC can lead to a more robust causal inference~\cite{bayani2021}.
 We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different.
-Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components (\textit{Appendix~\nameref{secS2}~Figure\ref{fig:elbow}}).
-Finally, we transform the dataset and input the dimensions-reduced output into the DSC model.
+Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components $D$ (\textit{Appendix~\ref{secS2}~Figure\ref{fig:elbow}}).
+Finally, all $24$ normalized variables were reduced into $D = 5$ primary components where $89.63\%$ variance was explained, and we use this transformed dataset as input of the DSC model.
 
 \subsection{Differenced Synthetic Control}\label{sec:DSC}
-Using the Differenced Synthetic Control (DSC) method, we can estimate water use under the scenarios of no institutional shift.
-The DSC method is an effective identification strategy for estimating the net effect of historical events or policy interventions on aggregate units (such as cities, regions, and countries) by constructing a comparable control unit~\cite{abadie2010, abadie2015, hill2021}.
-This approach enables us to establish a counterfactual basis for exploring the consequences and incentives related to policy changes.
 
-This method aims to evaluate the effects of policy change that are not random across units but focuses on some of them (i.e., institutional shifts in the YRB here).
-By re-weighting units to match the pre-trend for the treated and control units, the DSC method imputes post-treatment control outcomes for the treated units by constructing a synthetic version of the treated units equal to a convex combination of control units.
-Therefore, the synthetic and actual version difference can be estimated as a net effect for a treated unit.
+The Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021} is a tool we use to estimate how water use might have evolved if there had been no institutional shift.
+Think of it as creating an alternate reality or a ``what-if'' scenario to compare with what actually happened~\cite{abadie2010, abadie2015, hill2021}.
+The key idea behind this method is to evaluate the effects of policy changes (in this case, the 87-WAS and the 98-UBR) that mainly affect certain units (the provinces in the YRB).
+The method creates a ``synthetic'' version of the affected units by combining information from other similar but unaffected units.
+This ``synthetic'' version serves as a control group, which we can compare with the actual affected units.
+The DSC method, therefore, is a powerful tool as it allows us to control for unobserved factors that can change over time.
 
-In practice, all treated units (i.e., provinces) were affected by institutional shifts in 1987 and 1998, each taken as the ``shifted'' time $t_0$ within two individually analyzed periods $T$: from 1979 to 1998; from 1987 to 2008.
-We include each province in the YRB ($n=8$, see \textit{\nameref{sec:dataset}}) as the treated unit separately, as multiple treated units approach had been widely applied~\cite{abadie2021}.
-Then, we consider the $J+1$ units observed in time periods $T = {1,2 \cdots , T}$ with the remaining $J=20$ units are untreated provinces from outside.
-We define $T_0$ to represent the number of pre-treatment periods ($1,\ldots,t_0$) and $T_1$ the number post-treatment periods ($t_0, \ldots, T$), such that $T = T_0+ T_1$.
-The treated unit is exposed to the institutional shift in every post-treatment period $T_0$, unaffected by the institutional shift in all preceding periods $T_1$.
-Then, any weighted average of the control units is a synthetic control and can be represented by a ($J * 1$) vector of weights $\mathbf{W} = (w_{1}, \ldots ,w_{J})$, with $w_j \in (0, 1)$.
-Among them, by introduce a ($k * k$) diagonal, matrix $\mathbf{V}$ that signifies the relative importance of each covariant, the DSC method procedure for finding the optimal synthetic control ($W$) is expressed as follows:
+In practice, we consider two distinct institutional shifts that affected all treated units (i.e., provinces in the YRB) in 1987 and 1998.
+Each institutional shift (87-WAS or 98-UBR) is designated as the ``shifted'' time $T_0$, and we individually analyzed two periods: from 1979 to 1998; from 1987 to 2008.
+We include each of the eight provinces in the YRB as separate treated units~\cite{abadie2021} and define the $J+1$ units observed in a time period $1, 2, \dots, T_0, T_0 + 1, \dots, T$, where the remaining $J=20$ units represent untreated provinces outside the YRB.\
+
+The treated unit is exposed to the institutional shift in every post-treatment period $T_0 +1, \dots, T$, and unaffected by the institutional shift in preceding periods $1, 2, \dots, T_0$.
+Any weighted average of the control units is referred as a synthetic control and is denoted by a ($J \times 1$) vector of weights $\mathbf{W} = (w_{1}, \ldots ,w_{J})$, satisfying $w_j \in (0, 1)$ and $w_1 + \cdots  + w_{J} = 1$.
+We also introduce a a ($k \times 1$) non-negative vector $\mathbf{V} = v_{1}, \ldots ,v_{k}$ where $k$ is the product of $T$ and $D$, the number of years and dimensions in the dataset ($D = 5$ in this case).
+The vector $\mathbf{V}$ must fulfill $v_1 + \cdots  + v_{k} = 1$, reflecting the relative importance of each covariate.
+The next goal is finding the optimal $\mathbf{W}$ which represents the best ``synthetic'' versions of the affected provinces in the YRB:\
 
 \begin{equation}
-    \mathbf{W^{*}(V)}=\underset{\mathbf{W} \in \mathcal{W}}{\operatorname{minimize}}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)^{\prime} \mathbf{V}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)
+    \mathbf{W^{*}(V)}=\underset{\mathbf{W} \in \mathcal{W}}{\operatorname{argmin}}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)^{\prime} \mathbf{V}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)
 \end{equation}
 
-where $\mathbf{W}^{*}(V)$ is the vector of weights $\mathbf{W}$ that minimizes the difference between the pre-treatment characteristics of the treated unit and the synthetic control, given $\mathbf{V}$.
-That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W*(V)}$.
-Therefore, we choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{W*(V)}$ that minimizes the following expression:
+Here, matrix $\mathbf{X_1}$ represents the pre-treatment average of each dimension in the dataset for the treated unit, while $\mathbf{X_0}$ is a ($k \times J$) matrix containing the pre-treatment characteristics for each of the $J$ control units.
+We also define $\mathbf{W}^{*}(V)$ as the vector of weights $\mathbf{W}$ that minimizes the discrepancy between the pre-treatment characteristics of the treated unit and the synthetic control for a given $\mathbf{V}$.
+That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W^{*}(V)}$.
+Therefore, we choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{{W}^{*}(V)}$ that minimizes the following expression:
 
@@
 
-That is the minimum difference between the outcome of the treated unit and the synthetic control in the pre-treatment period, where $\mathbf{Z}_{1}$ is a ($1*T_0$) matrix containing every observation of the outcome for the treated unit in the pre-treatment period.
-Similarly, let $\mathbf{Z}_{0}$ be a ($k * T_0$) matrix containing the outcome for each control unit in the pre-treatment period, and $k$ is the number of variables in the datasets.
-The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with double robustness properties~\cite{billmeier2013, smith2015}.
+That is the minimum difference between the water uses of treated units and the synthetic controls in the pre-treatment period ($1, 2, \dots, T_0$), where $\mathbf{Z}_{1}$ is a matrix containing every observation of the water use for the treated unit.
+Similarly, $\mathbf{Z}_{0}$ is a ($J \times T_0$) matrix contains the water use for each control unit in this period.
+The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with better robustness~\cite{billmeier2013, smith2015}.
+In this study, we adopted the algorithm by the ``Synthetic Control Methods'' Python library (version 1.1.17)~\cite{engelbrektson2023} for the minimization.
 
-\subsection{Robustness analysis}\label{sec:robustness}
+\subsection{Validating results}\label{sec:robustness}
 
-Two primary methods can be employed to test the robustness of the DSC approach.
+The efficiency of the DSC approach can be validated using two primary methods.
 
-Firstly, the reconstruction effect on inferred variables (water consumption here) before and after treatment (the interventions of 87-WAS and 98-UBR) can be compared.
-If there are small gaps between the predicted and observed values before treatment, and a large gap after treatment, it indicates that the policy intervention's effect is apparent.
-In this study, to determine whether the intervention effect is significant, the paired sample $T$ test is used to calculate statistics, comparing the model predictions and actual observation data in the periods before and after institutional interventions for both the 87-WAS in $1987$ and 98-UBR in $1998$.
-A robust synthetic control model will show a significant difference after treatment but not before treatment.
+The first method involves comparing the reconstruction effect on the inferred variables (in this case, water consumption) before and after the interventions of 87-WAS and 98-UBR.\
+Small gaps between predicted and observed values before treatment, coupled with a large gap after treatment, would signal the apparent effect of the policy intervention.
+Specifically, this study employs the paired sample T test to calculate statistics that compare model predictions and actual observation data in the periods before and after both institutional interventions in 1987 (87-WAS) and 1998 (98-UBR).
+A significant difference observed after treatment, but not before, indicates that the policy was effective.
+If this pattern is not found, it suggests that the institutional changes did not impact the treated units.
 
-Secondly, placebo experiments are another common way to evaluate the effectiveness of synthetic control methods.
-Placebo units are selected from the control unit pool and substituted for the treated unit, applying the synthetic control method to the placebo unit using the same data and parameters as the treated unit.
-If the synthetic control method is effective, there should be a clear difference between the placebo unit and the control unit since the placebo unit should not be affected by the intervention.
-In this study, we adopt the placebo test step suggested by Abadie when proposing the synthetic control method~\cite{abadie2010} and utilize the Python library of the differential synthetic control method for the placebo test.
-If the ratio of the root mean square error (see Equation~\ref{ch5:eq:RMSE}) in the pre-synthesis period is significantly higher for most provinces (again using the $T$ test to determine the significance of the difference) than the results of other placebo units, it would suggest that the Yellow River Basin was more significantly affected than most other provinces during the treatment periods ($1987$ and $1998$), i.e., the results are more robust.
+The second method involves using placebo tests, a standard procedure for assessing the effectiveness of synthetic control methods~\cite{abadie2010}.
+Placebo units are drawn from the control unit pool and substituted for the treated unit.
+The synthetic control method is then applied to the placebo unit using the same data and parameters as the treated unit.
+No significant difference between the placebo and control units, given that the placebo unit should not be influenced by the intervention, would demonstrate the method's effectiveness.
+In this study, we follow the placebo test approach suggested by Abadie~\cite{abadie2010} and utilize the same Python library~\cite{engelbrektson2023} to perform this.
+If the ratio of the Root Mean Square Error (RMSE) (see Equation~\ref{ch5:eq:RMSE}) in the post/pre -treated period is significantly higher for most treated provinces (using the T test to assess significance) compared to other placebo units, it implies that the provinces in the YRB were significantly affected during the treatment periods (1987 and 1998), thus indicating effectiveness.
 
@@
 
-Where $n$ is the observed number, $y_i$ is the actual value, and $\hat{y}_i$ is the predicted value.
+Where $n$ is the observed number, $y_i$ is the observed value, and $\hat{y}_i$ is the predicted value.
 
@@
 Consequently, the YRCC has been directly linked to the provinces since then (Figure~\ref{fig:structure}C).
-Key points of the official documents supporting the structural changes above can be found in supplementary material~\textit{\nameref{secS1}}.
+Key points of the official documents supporting the structural changes above can be found in supplementary material~\textit{\ref{secS1}}.
 
@@
 The total water use of the YRB exhibited a significant difference between the counterfactual prediction and the actual observed value after the two institutional shifts, while the difference was small and insignificant before (see Figures~\ref{fig:main_results}A and B).
-This indicates that the estimated reconstruction of water use change was robust.
+This indicates that the estimated reconstruction of water use change was effective.
 Figure~\ref{fig:main_results}A suggests that the 87-WAS prompted the provinces to withdraw even more water than would have been used without an institutional shift (Figure~\ref{fig:main_results}A).
-From 1988 to 1998, on average, while the estimation of annual water use only suggests $887.05~km^3$ billion $m^3$, the observed water use of the YRB provinces reached $938.06$ billion $m^3$ (an increase of $5.75\%$).
+From 1988 to 1998, on average, while the estimation of annual water use only suggests $887.05$ billion $m^3$, the observed water use of the YRB provinces reached $938.06$ billion $m^3$ (an increase of $5.75\%$).
 However, after the 98-UBR, trends of increasing water use appeared to be effectively suppressed.
@@
 The gray bar chart shows the ratio of actual water use by provinces to their total water use in the decade after the two changes; The triangle marks indicate the ratio of the theoretical water resource quota of the province to the total available water in the YRB.\
-In the ten years after the 87-WAS, the proportion of water consumption increase (or decrease) compared to that estimated by the DSC model was positively correlated with the proportion of water consumption taken from the YRB at present (partial correlation coefficient was $0.64$, Figure~\ref{fig:regulating}).
+In the ten years after the 87-WAS, the proportion of water consumption increase (or decrease) compared to that estimated by the DSC model was positively correlated with the proportion of water consumption taken from the YRB at present (partial correlation coefficient was $0.64$).
 From 1987 to 1998, some provinces with high water consumption (e.g., Inner Mongolia and Henan) also showed significant increases in water consumption (Figure~\ref{fig:regulating} and Table~\ref{tab:DSC_summary}), with the average water consumption in four major users (Shandong, Inner Mongolia, Henan, and Ningxia) exceeding the predicted value by $32.14\%$.
@@
 
-The impacts of institutional shifts on the governing effects of social-ecological systems (SESs) have been widely reported worldwide, but few attempts have been made to quantify their net effects~\cite{cumming2020a}.
-Our case study of the YRB's water governance suggests that while the 98-UBR decreased total water use as expected, the 87-WAS unexpectedly increased it by $5.75\%$, a comparison of which can yield insights into the effectiveness of governance.
-Firstly, the results challenge previous analyses (i.e., suggesting that 87-WAS ``had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present~\cite{abadie2015,hill2021}.
-However, the significant net effect indicated by our analysis suggests that the 87-WAS was followed by increased water use even after controlling for environmental and economic variables (see \textit{\nameref{secS2}} Table~\ref{tab:variables}).
-In contrast, the 98-UBR reduced surface water competition, so many studies attributed the streamflow restoration mainly to the successful introduction of this institution~\cite{chen2021,huangang2002,an2007}.
+The impacts of institutional shifts on the governing effects of social-ecological systems (SESs) have attracted global attention, yet efforts to quantify their net effects remain sparse~\cite{cumming2020a}.
+Our investigation of the YRB's water governance reveals vary effects of nuanced-differences institutional shifts: while the 98-UBR led to an expected decrease in total water use, the 87-WAS surprisingly increased it by $5.75\%$.
+This comparison offers insightful perspectives on the effectiveness of governance because it suggests a significant net effect on increased water use following the implementation of this policy, in addition to the previous reports and comments suggesting that the 87-WAS was ``out-of-control''~\cite{wang2019d, departmentofearthsciences1999}.
+In contrast, the 98-UBR reduced surface water competition, so many studies attributed the streamflow restoration mainly to the successful introduction of it~\cite{chen2021,huangang2002,an2007}.
 
-Examining the unexpected 87-WAS policy, we found it shared a similar structure with many other SES governance failures, supporting the hypothesis that specific mismatched structures can rapidly exhaust common resources~\cite{kellenberg2009,cai2016,barnes2019}.
-Generally, these structure-based failures occur when social actors freely access linked resource units (like the institution before 1987), while the monitoring duty of the YRCC after 87-WAS was a sign that water quota was valuable to pursue (between 1987 and 1998).
-This conjecture aligns with the increased water use after 87-WAS and the concerns about frequently scrambling for water in some provinces during this period~\cite{mao2000, bouckaert2022}.
-A previous study analyzed reasons for the non-ideal effect of 87-WAS~\cite{huangang2002}, where core concerns were the lack of enforcement and controlling approaches, while major stakeholders kept arguing they needed more quotas from 1983 to the 1990s.
-It indicates that it was reasonable for stakeholders to pursue more water quota by withdrawing more water, beyond their economic growth.
-Our results align with this hypothesis since the correlation between current water use and changed (increased or decreased) water use was significant after the 87-WAS but not after the 98-UBR (Figure~\ref{fig:regulating}).
-In addition, through a theoretically marginal benefit analysis, this ``major users use more'' pattern can be inferred from a simple assumption that stakeholders can expect water quota's value in the short future, also supporting the above hypothesis (see \textit{\nameref{secS4}}).
+The unanticipated consequence of the 87-WAS policy echoes the structural challenges reported in many other SES governance failures.
+This suggests a general pattern where specific misaligned structures can precipitate the rapid depletion of common resources~\cite{kellenberg2009,cai2016,barnes2019}.
+These structure-based failures often occur when social actors have unregulated access to linked resource units, a feature prevalent in the institution prior to 1987~\cite{wang2019c}.
+When the central government attempted to curtail this free access by introducing water quotas, they were met with water demands from stakeholders' proposals that far exceeded expectations (Table~\ref{tab:quota}).
+A previous study attributed the suboptimal effect of 87-WAS to the lack of enforcement and control mechanisms~\cite{huangang2002}.
+Taken together, it underpins a hypothesis that in the absence of enforcement, stakeholders might have exploited the system by increasing water withdrawals to secure more water quotas for their economic prospects.
 
-Besides our results, the above hypothesis also aligns with two reported facts:
-(1) The water quotas of 87-WAS (or the initial water rights) went through a stage of ``bargaining'' among stakeholders (from 1982 to 1987) and the bargaining arguments even persisted years after 1987~\cite{wang2019e, wang2019d}.
-During this process, each province attempted to demonstrate its development potential related to water use, to match water shares to their economy because the major water users (like Shandong and Henan) needed more water than their original quota (if only considering economic potentials when designing the institution)~\cite{zuo2020}.
-(2) During the ``bargaining'', more significant stakeholders had considerable
-incentives to pursue more water quotas, which aligned with the fact that major water users submitted appeals to the higher central government for larger shares~\cite{wang2019e, wang2019d}.
-This means provinces with higher current water use have greater bargaining power in water use allocation.
+This hypothesis can be further substantiated by two reported facts:
+(1) There were not only surges of total water uses following the 87-WAS, but also scrambles for water reported in several provinces during this period~\cite{mao2000, bouckaert2022}.
+(2) From 1983 to the 1990s, the stakeholders persistently argued for increased the water quotas, when is a stage of ``bargaining''~\cite{wang2019e, wang2019d};
+(3) During this ``bargaining'' stage, the stakeholders who had more economic profits submitted appeals to the higher central government for larger shares~\cite{wang2019e, wang2019d}.
 
-On the other hand, since the YRCC could coordinate stakeholders by water quota licenses according to water conditions for the entire YRB after 98-UBR, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)~\cite{krieger1955, ostrom1990}.
-Similar, proportional decreased water use of provinces and the theoretical minimal water use of marginal benefit model indicated this policy lead to successful governance as expected (see \nameref{result-3}).
-However, since the 98-UBR only regulated surface water use, many clues suggested the institution shift may cause broader influences, including estimated increased groundwater withdrawals after 98-UBR in many intensive water use regions~\cite{sun2022b}.
-With limited eligible data on groundwater use, related assessment is beyond the scope of this study but remains quite important, as similar water quota policies started to be implemented nationally since the 21st century.
+Our results also corroborate some intuitive deductions of the hypothesis.
+Firstly, we found significant correlations between current and changed water use after the 87-WAS, which suggests that the key stakeholders (such as Neimeng, Henan, and Shandong), were more likely to be affected by the institutional change.\
+Secondly, a theoretical marginal benefit analysis (see \textit{\ref{secS4}}) suggests that this ``major users are effected more'' pattern can be inferred from a simple assumption that stakeholders anticipate future value in water quotas, thereby lending further support to the above hypothesis.
+Finally, since the YRCC could forcibly coordinate stakeholders by water quota licenses for the entire YRB after 98-UBR, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)~\cite{krieger1955, ostrom1990}.
 
-The structural pattern we depicted here (Figure~\ref{fig:structure}) has also been reported in other SESs worldwide~\cite{kluger2020,guerrero2015,bodin2012}.
-Before 98-UBR, fragmented ecological units were linked to separate social actors, which more likely led to lower effectiveness because isolated actors generally struggle to maintain interconnected ecosystems holistically~\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
-Institutional re-alignments since 98-UBR enhanced the responsibilities of the basin-scale authority (YRCC) and led to effectiveness in runoff restoration, which are usually named scale match or institutional match of SESs~\cite{cumming2020a,wang2019d}.
-Taken together, the comparison demonstrates the challenge of finding win-win situations in coupled social-ecological systems~\cite{hegwood2022} and the need to more deeply understand the role of institutions in water governance~\cite{bergsten2019, sayles2019}.
+On the flip side, the apparent success of the 98-UBR institutional transformation has received consistent acclaim, particularly for its role in restoring the previously dry river~\cite{wang2019e, wang2019d}.
+Our findings suggest that the 98-UBR led to a proportional decrease in water use across provinces, indeed indicative of an immediate and tangible effect.
+However, it's essential to recognize that the 98-UBR focused solely on regulating surface water use, which hints at potential broader implications.
+Notably, some evidence suggests that this institutional shift might have resulted in increased groundwater withdrawals in regions with intensive water usage following the 98-UBR~\cite{sun2022b}.
+Unfortunately, the limited availability of eligible data on groundwater use constrains a comprehensive assessment, leaving this aspect beyond the scope of the current study.
+Nonetheless, this consideration remains highly relevant, especially as similar water quota policies have begun to be implemented nationally since the turn of the 21st century.
 
-Our approach has some inevitable limitations.
-First, the contributions of economic growth and institutional shifts are difficult to distinguish because of intertwined causality (institutional changes can also influence the relative economic variables);
-and second, when applying the DSC method, it is difficult to rule out the effects of other policies over the same time breakpoints (1987 and 1998).
-Our quasi-experiment approach nonetheless provides evidence supporting the view that there was a change in water use trajectory following the YRB's unique institutional shifts and offers insights into water governance (and particularly the importance of having a scale-matched, basin-wide authority for water allocation solutions~\cite{bodin2017b, ostrom2009, reyers2018}).
-Moreover, the ultimate success of the 98-UBR institutional shift theoretically and practically proved the importance of social-ecological fit.
-For sustainability in the future, it is necessary to emphasize the need to strengthen connections between stakeholders through agents consistent with the scale of the ecological system.
-For example, water rights transfers may be another way to build horizontal links between stakeholders that also have the potential to result in better water governance.
-In addition, policymakers can propose more dynamic and flexible institutions to increase the adaptation of stakeholders to a changing SES context~\cite{reyers2018}.
+To provide an intuitive understanding of the profound impact of the Institutional shifts, we can turn to the insights shared by a representative of the Hetao Irrigation District in Neimeng.
+As a primary stakeholder, the district's representative voiced the struggle to adapt under the 98-UBR policy which strictly enforced water quotas in our surveys.
+``The water allocated to us is far from enough'', he revealed with a desire on more water quota: ``And it's not like in the past when we could actually over use, it is very strictly controlled now.''
+``Under a limited quota, of course there are conflicts between users time to time, which depends on leaderships of the water-user associates'', he reflected: ``-farmers may have their own solutions, such as switching to sunflower, which is more water-efficient, or using shallow groundwater when is available.''
+Simultaneously, the district looked forward to future projects, such as the ``South-to-North Water Diversion'' Western Route Project, which they hoped would increase their water quotas and allow for expansion of their irrigation area.
+The desire of water in Neimeng wasn't without controversy. Stakeholders in other lower reaches argued that the Hetao Irrigation District was consuming too much water from the Yellow River.
 
-The structural pattern that led to different effectiveness is widespread in global SESs, making our proposed mechanism crucial to governing such coupled systems.
-Our analysis suggests that these initiatives can lead to unexpected results because of mismatched structure when shifting to another institution~\cite{bodin2017b}.
-Better governance calls for more institutional analysis while China has embarked to redesign its decades-old water allocation scheme.
-Our research provides insights into how institutions can affect achieving successful river basin governance when socio-hydrological interplays frame SES structures~\cite{muneepeerakul2017, leslie2015, hegwood2022}.
+The above analysis with a real-world example emphasizes the vital role of institutions in shaping the socio-ecological systems (SES) structures of water governance.
+The structural pattern we have depicted (Figure~\ref{fig:structure}), mirrored in other SESs worldwide~\cite{kluger2020,guerrero2015,bodin2012}, illustrates how fragmented ecological units linked to isolated social actors can lead to inefficiencies.
+Before the 98-UBR, this fragmentation resulted in lower effectiveness, as disconnected actors struggled to maintain holistic ecosystems~\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
+After the 98-UBR, institutional realignments enhanced basin-scale authority (YRCC), fostering effectiveness in runoff restoration—a phenomenon often termed scale or institutional match in SESs~\cite{cumming2020a,wang2019d}.
+This comparison underscores the complex challenges of crafting win-win scenarios in SES and accentuates the importance of understanding institutional roles in water governance~\cite{hegwood2022,bergsten2019, sayles2019}.
+
+Our approach acknowledges certain limitations, such as the difficulty in quantifying contributions from economic growth, and challenges in isolating the effects from other concurrent policies in 1987 and 1998.
+Despite these constraints, our quasi-experimental methodology elucidates the change in water use following the YRB's unique institutional shifts.
+It offers critical insights into water governance, emphasizing scale-matched, basin-wide authority for water allocation solutions~\cite{bodin2017b, ostrom2009, reyers2018}.
+The success of the 98-UBR shift underscores the need for social-ecological alignment, fostering sustainable governance.
+Future endeavors must focus on strengthening stakeholder connections, exploring alternative solutions like water rights transfers, and embracing more dynamic and adaptable institutional frameworks to respond to evolving SES contexts~\cite{reyers2018}.
+
+The diverse effectiveness of structural patterns, as observed in global SESs, underscores the necessity for nuanced governance in coupled systems.
+The potential for unexpected outcomes due to institutional mismatches calls for thorough institutional analysis.
+As China seeks to overhaul its water allocation schemes, our research serves as a timely beacon, highlighting how nuanced institutional interplays can shape successful river basin governance, resonating with the global challenge of socio-hydrological complexities~\cite{muneepeerakul2017, leslie2015, hegwood2022}.
 
@@
 
-In this study, we examined the effects of two major institutional shifts in water governance within the Yellow River Basin (YRB): the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basin Regulation (98-UBR).
-By employing a Difference-in-Differences approach with Synthetic Control, we quantified the net effects of these institutional shifts on water use within the YRB.\
-Our results showed that the 87-WAS unexpectedly increased water use by $5.75\%$, contrary to its intended goals, while the 98-UBR successfully reduced water use as anticipated.
-The analysis revealed that the structural patterns of the institutions played a critical role in their effectiveness.
-The mismatched structure of the 87-WAS led to increased competition and exploitation of water resources, while the 98-UBR, with its scale-matched, basin-wide authority and stronger connections between stakeholders, resulted in improved water governance.
+In this investigation of the Yellow River Basin (YRB), we meticulously examined the impacts of two institutional shifts in water governance: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basin Regulation (98-UBR).
+Utilizing the Differenced Synthetic Control (DSC) approach, we were able to quantify the discrete effects of these transitions on water consumption within the basin.
+Our findings suggest a paradoxical increase in water use by 5.75\%, attributed to the 87-WAS, defying its original objectives.
+Conversely, the 98-UBR efficaciously diminished water usage in line with its intended outcomes.
+This analysis unearthed the pivotal role that institutional structural patterns play in determining their efficacy.
+Specifically, the misaligned structure of 87-WAS inadvertently fostered increased rivalry and exploitation of water resources.
+Meanwhile, the 98-UBR, characterized by its scale-matched, basin-wide coordination and reinforced stakeholder connections, fostered restoration of the Yellow River.
 
-In conclusion, our research contributes to a better understanding of the role of institutions in SES governance, particularly in the context of water management.
-By identifying the key factors that influence the success or failure of institutional shifts, we provide valuable insights for the design of effective and sustainable water governance policies.
-Future research should continue to explore the intricacies of institutions in SES governance and investigate the potential impacts of additional policies and institutional shifts on water use and sustainability.
+In sum, our study sheds new light on the complex dynamics of institutions within socio-ecological systems (SES) governance, with an emphasis on water allocation.
+By unraveling the essential components that govern the triumph or downfall of institutional transformations, we furnish invaluable insights that can guide the crafting of sustainable water governance policies.
+These findings beckon further exploration into the multifaceted nature of institutional behavior in SES governance, and how future policy adjustments and institutional metamorphoses might sculpt the efficiency of water utilization and sustainability.
 
@@
 \textbf{Acknowledgments}\\
-This research has been supported by the National Natural Science Foundation of China (grant no. 42041007) and the Fundamental Research Funds for the Central Universities
+This research has been supported by the National Natural Science Foundation of China (grant no. 42041007) and the Fundamental Research Funds for the Central Universities.
+
+\textbf{Declaration of generative AI and AI-assisted technologies in the writing process}
+
+During the preparation of this work the authors used ChatGPT 4.0 in order to polish sentences.
+After using this tool/service, the authors reviewed and edited the content as needed and take full responsibility for the content of the publication.
 
@@
 As a benchmark, case 1 analogy to a decentralized stakeholders situation and lead to medium-level water use.
-In case 2, each stakeholder expects that current water use helps bargain for a favorable water quota in the face of institutional shift (see \textit{\nameref{secS4}}), which can intensify the incentive to use water, leading to higher water use.
+In case 2, each stakeholder expects that current water use helps bargain for a favorable water quota in the face of institutional shift (see \textit{\ref{secS4}}), which can intensify the incentive to use water, leading to higher water use.
 Furthermore, the water users with higher capability are more stimulated by the institutional shift and away from the theoretically optimal water use under a unified allocation.

### 2023-11-01 docs/papers/04_response_letter/source/editor.tex
fix(project): :memo: change nameref into ref
docs(project): :memo: update R2 reviewer's comment

--- 2023-07-28 docs/papers/04_response_letter/source/editor.tex
@@
 % chktex-file 46
-\section*{Associate Editor}\label{editor}
+\section*{Invited editorial team}\label{editor}
 
 \subsection*{General comments}
-\RC*{} Dear Author,
+\RC{} Dear Author,
 
-\RC*{} Two reviewers have assessed your paper and identified a good potential but some flaws, with which I concur.
-I would particularly insist on Reviewer 1's comment on DSC method description and wording.
+% 现在有两位审稿人对修订后的版本进行了评估。他们都赞赏为考虑到对他们两人都审查过的初次提交的意见所做的工作。对论文的技术方面不太了解的人仍然对方法的解释很恼火。请仔细修改这方面，以确保期刊读者能理解你的论文
+\RC*{} Two reviewers have now assessed the revised version.
+They both appreciate the work done to take in account the comments on the initial submission they had both reviewed.
+The one who is lcoser to the technical aspect of the paper is still quite annoyed though on the explanation of the method.
+Please revise carefully this aspect in order to ensure understandability of your paper by the journal readership
 
-% 除了审稿人的意见外，我还建议根据特刊主题加强讨论。你对制度变迁后果的分析，对于社会水文学来说，确实是重要而及时的。主要基于统计定量分析的方法选择是创新的，可以更好地描述社会水文系统的变化，这是好的。要深入社会水文学，需要更多背后的故事，对推动这些变化的社会和水文过程的解释。讨论在这个方向上开辟了一些途径，但在这方面过于薄弱。我漏了一些例子。1998年以后从地表水转移到地下水取水的事实)，引语(如:(关于讨价还价的论据)，谁是主要利益相关者的准确性以及他们如何影响社会水文过程。
-\RC*{} In addition to reviewers' comments, I would also recomment strengthening the discussion in light of the special issue topic.
-Your analysis of consequences of institutional shifts is indeed important and timely for grounded sociohydrology.
-The methodological choice mainly based on statistical quantitative analysis is innovative to better qualify changes in SocioHydrological systems, which is good.
-Going to grounded sociohydrology needs more of the story behind, explanation of the social and hydrological processes that drive these changes.
-The discussion opens some ways in this direction but is too weak on that regard.
-I missed examples (eg.\ facts describing the transfer from surface to groundwater withdrawal after 98), quotations (eg.\ on bargaining arguments), precisions of who are the dominant stakeholders and how they influence the sociohydrological process.
-
-\RC*{} I hope you will be able and keen on revising the manuscript with these directions.
-
-\RC*{} O. Barreteau in the name of invited editorial team
-
-\AR*{} We hope that these revisions address the concerns raised by both reviewers.
-We are confident that these changes have significantly improved the quality of our manuscript and made it more relevant and valuable to the scientific community.
-We look forward to your further feedback and the possibility of our manuscript being accepted for publication.
+% TODO \AR{} I am grateful for the encouragement and the direction provided to enhance our manuscript.
+It has been a privilege to contribute to this special issue, and I believe that the revisions made align with the expectations and vision set forth by the editorial team.

### 2023-11-01 docs/papers/04_response_letter/source/reviewer_1.tex
docs(project): :memo: update R2 reviewer's comment

@@
 
-% \RC{}本研究旨在利用差分综合控制(DSC)方法量化黄河流域(YRB)制度变迁(政策变化)和水资源利用的影响。这项研究在方法上似乎是合理的。这个话题很有趣:它以定量的方式将政策维度整合到对流域的评估中，可能会引起期刊读者的兴趣。也就是说，我认为手稿需要相当多的改进和仔细的修改。请参阅下文。
-\RC{} This study aimed at quantifying the effect of institution shifts (policy changes) and water usage in the Yellow River Basin (YRB), using the Differenced Synthetic Control (DSC) method.
-The study seemed methodologically sound.
-The topic is interesting: it integrated the policy dimension into an assessment of a river basin in a quantitative way and could be of interest to the journal's readership.
-That said, I believe the manuscript needs quite a few improvements and careful revisions.
-Please see below.
+% 在大多数情况下，作者已经解决了我在原始提交中关于单词选择和各种符号混淆的评论，我对此表示赞赏。然而，差分综合控制方法的描述，如果有什么的话，变得更让我困惑!
+\RC{} For the most part, the authors have addressed my comments regarding word choices and various notational confusion in the original submission, and I appreciate that.
+However, the description of the Differenced Synthetic Control method, if anything, becomes even more confusing to me!
 
-\AR{} Thank you for your valuable feedback and for acknowledging our novelty and reasonability.
-Your feedback greatly helps us improve the clarity and accessibility of our work.
-We sincerely appreciate your effort in reviewing our manuscript and providing these insightful comments.
-Below are point-to-point modification descriptions.
+% Eq 1: V怎么可能是一个向量，而不是一个矩阵?在Eq 1中的矩阵乘法只是不工作与指定的维度!X_1的维数是多少?作者指定W是一个(J x 1)向量，X_0是一个(k x J)矩阵。这意味着乘积(X_0 W)是一个(k x 1)向量，所以X_1也应该是一个(k x 1)向量。这意味着(X_1 - X_0 W)'和(X_1 - X_0 W)的维数应该是(1 × k)和(k × 1)。为了使方程1成立，V必须是一个(k × k)矩阵。我错过什么了吗?如果我误解了什么，请澄清。
+\RC{} Eq 1: How can V be a vector, not a matrix?
+The matrix multiplication in Eq 1 just doesn't work with the dimensions specified!
+And what is the dimension of X_1?
+The authors specified that W is a (J x 1) vector and X_0 is a (k x J) matrix.
+This implies that the product (X_0 W) is a (k x 1) vector, so X_1 should be a (k x 1) vector as well.
+Which means that (X_1 - X_0 W)' and (X_1 - X_0 W) should have dimensions of (1 x k) and (k x 1).
+For Eq 1 to work, V must be a (k x k) matrix.
+Did I miss something here?
+If I misunderstood anything here, please clarify.
 
-\subsection{CLEARER METHOD DESCRIPTION}\label{sec:1-1}
+% 加上，如何确定V的项的值?公式2表明需要W来确定V?但这不是循环逻辑吗?所以你需要最优的V来确定W，但你也需要最优的W来确定最优的V?哪些优化必须先做?
+\RC{} Plus, how does one determine the values of V's entries?
+Eq.
+2 suggests that one needs W to determine V?
+But isn't that circular logic?
+So you need the optimal V to determine W, but you also need the optimal W to determine the optimal V?
+Which optimization must be done first?
 
-\RC{} Section 3.3.
-Differenced Synthetic Control needs to be much clearer.
-For example, on lines 141-145, please double-check the description and symbols used in this passage.
-In particular, the multiple uses of capital letter T—as the duration of a period and as a time index—were quite confusing.
-Then, ``post-treatment period $T_0$.\ldots all preceding periods $T_1$'' - is this correct?
-Anyhow, please double-check and revise to make this passage clearer.
+% Z的维数不应该是(T_0 x J)，而不是(J x T_0)吗?否则，它就不能从右边乘以W, W的维数是(jx1)再说一遍，我漏了什么吗?如果我误解了什么，请澄清。
+\RC{} Eq.
+2: Shouldn't Z's dimension be (T_0 x J), not (J x T_0)?
+Otherwise, it cannot be multiplied from the right by W, which has the dimension of (J x 1).
+Again, did I miss something here?
+If I misunderstood anything here, please clarify.
 
-\RC*{} In Eq 1, $X_0$ and $X_1$ were never defined.
-
-\RC*{} Using ``$*$'' to denote the dimension of a matrix (e.g., $k*k$) is a bit odd; please consider using a multiplication symbol, e.g., $k \times k$.
-
-\AR{} [page 6 to 8, lines 124 to 185] We have revised the description of the DSC method to make it clearer and more comprehensive.
-We expanded on the purpose and process of the DSC method, provided more context on how it fits into our research, and clarified the mathematical notation.
-We also explained the specific variables used when we introduced $X_1, X_0, Z_1$, and $Z_0$, as well as mentioned the specific method used for minimization and the corresponding reference.
-We believe that these revisions have significantly improved the clarity of our method description.
-
-\subsection{BETTER WORD CHOICES}\label{sec:1-2}
-
-\RC{} I found some of the word choices a bit strange.
-For example, unless the term has been used this way in the literature, ``point-axis networks'' sounds strange.
-Otherwise, please consider alternatives like ``organizational charts'' or ``organizational diagrams'', which I believe is more appropriate.
-
-\AR{} Thank you once again for your valuable insights and suggestions.
-
-\AR*{} Regarding your comment on our use of the term ``point-axis networks'', we appreciate your feedback.
-The term was indeed referenced from a review article (\cite{kluger2020}), and we initially used it believing it was a common term in the literature.
-However, upon your suggestion and further consideration, we agree that the term may not be widely recognized across our readership.
-
-\AR*{} We have therefore revised the relevant sentence to use the term ``organizational diagram'', which is indeed more familiar and equally accurate. The sentence now reads:
-
-\begin{quote}[page=5, sline=90, eline=92]
-    In this section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as organizational diagrams during different periods of time.
-\end{quote}
-
-\begin{quote}[page=5, sline=99, eline=100]
-    An organizational diagram is widely used to depict SES structures by abstracting links and nodes from the real-world interactions~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
-\end{quote}
-
-\RC{} In a similar vein, I do not think that ``network approach'' or ``network-based approach'' is an appropriate description of what is being done here.
-Normally, network approaches involve concepts from complex network theories, which are not present here.
-Indeed, calling this a network approach may provoke unnecessary objections from network researchers.
-I would suggest the use of simpler terms like ``analysis of the organizational charts'' or something along that line.
-
-\AR{} Thank you for your thoughtful suggestion to use the term ``analysis of the organizational charts''.
-We agree that this term is clearer and more widely understood.
-We have incorporated your suggestion into our manuscript.
-We believe this modification has improved the clarity and readability of our manuscript, making it more accessible to our readers:
-
-\begin{quote}[page=5, sline=100, eline=105]
-    We apply the analysis of the organizational diagrams~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit at the basin scale (the Yellow River Conservancy Commission) into structural patterns from official documents.
-    We examined the official documents of the two institutional shifts (87-WAS and 98-UBR) to portray the organizational diagrams in this study~\cite{bodin2017a,kluger2020,guerrero2015}.
-\end{quote}
-
-\RC{} I disagree with how the term and concept of ``robustness'' is used here.
-Normally, a robust result is a result that holds even when the input variables and/or parameters are uncertain.
-What is being reported here seems to be the effectiveness or efficiency of the institutional shifts, not the robustness.
-If I misunderstood anything here, please clarify.
-As it is, I don't think that the use of the term ``robustness'' is appropriate here.
-
-\AR{} Regarding your suggestion on the usage of the term ``robustness'', we have reconsidered our choice of words and agree with your point.
-We understand that the term ``efficiency'' more accurately represents our intended meaning in this context.
-Therefore, we have revised our manuscript and replaced ``robustness'' with ``efficiency''.
-We believe this change improves the clarity and precision of our work:
-
-\begin{quote}[page=7, sline=163]
-    The efficiency of the DSC approach can be validated using two primary methods.
-\end{quote}
-
-\begin{quote}[page=8, sline=170, eline=172]
-    A significant difference observed after treatment, but not before, indicates that the policy was effective.
-    If this pattern is not found, it suggests that the institutional changes did not impact the treated units.
-\end{quote}
-
-\begin{quote}[page=8, sline=180, eline=184]
-    If the ratio of the Root Mean Square Error (RMSE) (see Equation 3) in the post/pre -treated period is significantly higher for most treated provinces (using the T test to assess significance) compared to other placebo units, it implies that the provinces in the YRB were significantly affected during the treatment periods (1987 and 1998), thus indicating effectiveness.
-\end{quote}
-
-\AR*{} Thank you once again for your valuable feedback, which has greatly contributed to the quality of our manuscript.
-
-\RC{} Is ``placebo experiments'' the term normally used in this way? If so, can you provide some references?
-
-\AR{} Basically, the term ``placebo'' is indeed used in this context in the literature, particularly in policy evaluation studies where the synthetic control method is used.
-It refers to the procedure of applying the synthetic control method to units that did not receive treatment to verify the significance of the estimated treatment effects.
-This procedure is called a ``placebo test'' or ``placebo experiment'' and is crucial for validating the results of synthetic control analyses.
-
-\AR*{} In light of your comment, we have revised our manuscript to consistently use the term ``placebo tests'' throughout, and we have added references that use this term in a similar context~\cite{abadie2010}.
-We hope this change addresses your concern and provides a clear explanation of the term's usage:
-
-\begin{quote}[page=8, sline=173, eline=174]
-    The second method involves using placebo tests, a standard procedure for assessing the effectiveness of synthetic control methods~\cite{abadie2010}.
-\end{quote}
-
-\subsection{Other comments}\label{sec:1-3}
-
-\RC{} I would change the first two key points into full sentences; as they are, they are only fragments, while the third and fourth points are full sentences.
-
-\AR{} Thank you for your valuable suggestion to rewrite the key points as full sentences.
-We appreciate your attention to detail and agree that full sentences are more informative and complete.
-We have revised the key points in our manuscript as follows:
-
-\begin{quote}[page=Key Points]
-    1.	We assess the impact of institutional shifts in water governance at basin scale.\\
-    2.	We conduct a quantitative analysis of Yellow River Basin's water management policies.\\
-    3.	Water Allocation Scheme in 1987 unexpectedly increased water use by 5.75\%.\\
-    4.	Unified Basin Regulation in 1998 successfully reduced water use as anticipated.\\
-\end{quote}
-
-\RC{} Lines 39-40: ``the 1987\ldots (98-UBR).'' is repeated -please remove.
-
-\AR{} Thank you for pointing out the repetition in lines 39-40 regarding ``the 1987\ldots (98-UBR).'' We appreciate your careful attention to detail.
-This repetition was indeed an oversight on our part.
-We have now corrected this error by removing the duplicate phrase in our manuscript.
-
-\RC{} Line 75: A subject is missing in front of ``proposed to\ldots '' Perhaps, ``the government''?
-
-\AR{} Thank you for your attentive reading of our manuscript and for pointing out the missing subject in line 75.
-Upon your suggestion, we have revised the sentence to specify the subject, now reading:
-
-\begin{quote}[page=4, sline=75, eline=76]
-    In $1980s$, the central government proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019d, wang2019e}.
-\end{quote}
-
-\RC{} Lines 169-171: ``A robust synthetic control model will show a significant difference after treatment, but not before treatment.'' Why?
-This statement assumes that the treatment must have an effect; what if the treatment has no effect?
-
-\AR{} Thank you for your valuable comment regarding the clarification needed for the statement in lines 169-171.
-Upon your suggestion, we have revised the sentence for better clarity, and it now reads:
-
-\begin{quote}[page=8, sline=170, eline=172]
-    A significant difference observed after treatment, but not before, indicates that the policy was effective.
-    If this pattern is not found, it suggests that the institutional changes did not impact the treated units.
-\end{quote}
-
-\RC{} Line 209: Are parentheses missing for ``$km^3 billion m^3$''?
-
-\AR{} Thank you for pointing out the typo in line 209 regarding units.
-Your careful attention to detail is greatly appreciated.
-We have now corrected this typographical error in our manuscript by deleting the redundant unit:
-
-\begin{quote}[page=10, sline=207, eline=209]
-    From 1988 to 1998, on average, while the estimation of annual water use only suggests $887.05$ billion $m^3$, the observed water use of the YRB provinces reached $938.06$ billion $m^3$ (an increase of $5.75\%$).
-\end{quote}
-
-\RC{} Lines 261-262: It's unclear to me how Fig. 4 supports the statement "the correlation between \dots 98-UBR (Figure 4)."
-
-\AR{} Thank you for pointing out the confusion in the reference to Figure 4 in lines 261-262.
-We have now deleted this not consistently reference.
-We value your insightful feedback and thank you for helping us improve the clarity and accuracy of our manuscript.
-
-\RC{} Somehow, I did not see Appendix C explicitly referred to in the main text. There is reference to "Marginal benefit model for water use" but this was not explicitly labeled as Appendix C.
-
-\AR{} Thank you for pointing out the missing reference to Appendix C in our manuscript.
-We appreciate your attention to detail.
-Upon revisiting the manuscript, we realized that Appendix C was indeed not explicitly referred to in the main text.
-We have now rectified this oversight by adding an explicit reference to Appendix C where the ``Marginal benefit model for water use'' is discussed:
-
-\begin{quote}[page=14, sline=266, eline=269]
-    Secondly, a theoretical marginal benefit analysis (see \textit{Appendix C}) suggests that this ``major users are effected more'' pattern can be inferred from a simple assumption that stakeholders anticipate future value in water quotas, thereby lending further support to the above hypothesis.
-\end{quote}
-
-\RC{} Line 280: from ``Similar'' to ``Similarly''
-
-\AR{} Thank you for pointing out the typographical error in line 280. We have eliminated the error in the revision.
-
-\RC{} Line 323-324: This is the first time you used the term ``difference-in-differences'' -so far, you have called your method ``Differenced Synthetic Control'' (DSC).
-Why different names?
-Likely a typo; please double-check.
-
-\AR{} Upon your suggestion, we have rectified the error and now consistently use the term ``Differenced Synthetic Control'' (DSC) throughout the manuscript, ensuring the consistency and clarity of our terminology.
-
-\RC{} Line 327: ``revealed'' is too strong; perhaps ``suggested''?
-
-\AR{} Thank you for pointing out the excessive use of the term ``revealed'' in line 327.
-We appreciate your thoughtful suggestion to soften the language.
-We have now replaced ``revealed'' with the more appropriate term ``suggested'' in our manuscript.
-
-\RC{} Line 437, Ref [30]: Pca should be all caps, PCA.\
-
-\AR{} Thank you for bringing to our attention the typographical error in line 437, reference [30].
-We appreciate your meticulous review of our manuscript.
-We have corrected the error by capitalizing the acronym "PCA".
-This has improved the accuracy and professionalism of our reference list.
+% 虽然我仍然认为这项研究可能会引起期刊读者的兴趣，正如我上面的沮丧所表明的那样，方法描述非常令人困惑，并且没有得到充分的解决。我强烈建议作者在下次修订时要非常小心。
+\RC{} While I still think that the study can be of interest to the journal's readership, as indicated by my frustration above, the method description is very confusing and has not been adequately addressed.
+I strongly suggest that the authors be VERY CAREFUL in the next revision.

### 2023-11-02 docs/papers/01_manuscript/06_methods.tex
fix(method): :bug: refine the expression of method by Yinan Xiao

@@
 The treated unit is exposed to the institutional shift in every post-treatment period $T_0 +1, \dots, T$, and unaffected by the institutional shift in preceding periods $1, 2, \dots, T_0$.
-Any weighted average of the control units is referred as a synthetic control and is denoted by a ($J \times 1$) vector of weights $\mathbf{W} = (w_{1}, \ldots ,w_{J})$, satisfying $w_j \in (0, 1)$ and $w_1 + \cdots  + w_{J} = 1$.
-We also introduce a a ($k \times 1$) non-negative vector $\mathbf{V} = v_{1}, \ldots ,v_{k}$ where $k$ is the product of $T$ and $D$, the number of years and dimensions in the dataset ($D = 5$ in this case).
-The vector $\mathbf{V}$ must fulfill $v_1 + \cdots  + v_{k} = 1$, reflecting the relative importance of each covariate.
-The next goal is finding the optimal $\mathbf{W}$ which represents the best ``synthetic'' versions of the affected provinces in the YRB:\
+Any weighted average of the control units is referred as a synthetic control and is denoted by a ($J \times 1$) vector of weights $\mathbf{w} = (w_{1}, \ldots ,w_{J})$, satisfying $w_j \in (0, 1)$ and $w_1 + \cdots  + w_{J} = 1$.
+We also introduce a ($k \times 1$) non-negative vector $\mathbf{v} = (v_{1}, \ldots ,v_{k}$) to weight the relative importance of each covariate, where $k$ is the product of $T$ and $D$, the number of years and dimensions in the dataset ($D = 5$ in this case).
+The vector $\mathbf{v}$ must fulfill $v_1 + \cdots  + v_{k} = 1$, and $\mathbf{diag(v)}$ represents the diagonal matrix formed by the vector $\mathbf{v}$.
+Then, the next goal is finding the optimal $\mathbf{w}$ which represents the best ``synthetic'' versions of the affected provinces in the YRB.\
+Given $\mathbf{v}$, we define $\mathbf{w^{*}(v)}$ as a function of $\mathbf{v}$ that minimizes the discrepancy between the pre-treatment characteristics of the treated unit and the synthetic control:
 
 \begin{equation}
-    \mathbf{W^{*}(V)}=\underset{\mathbf{W} \in \mathcal{W}}{\operatorname{argmin}}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)^{\prime} \mathbf{V}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)
+    \mathbf{w^{*}(v)}=\underset{\mathbf{w} \in \mathcal{W}}{\operatorname{argmin}}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{w}\right)^{\prime} \mathbf{diag(v)}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{w}\right)
 \end{equation}
@@
 Here, matrix $\mathbf{X_1}$ represents the pre-treatment average of each dimension in the dataset for the treated unit, while $\mathbf{X_0}$ is a ($k \times J$) matrix containing the pre-treatment characteristics for each of the $J$ control units.
-We also define $\mathbf{W}^{*}(V)$ as the vector of weights $\mathbf{W}$ that minimizes the discrepancy between the pre-treatment characteristics of the treated unit and the synthetic control for a given $\mathbf{V}$.
-That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W^{*}(V)}$.
-Therefore, we choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{{W}^{*}(V)}$ that minimizes the following expression:
+Finally, we choose $\mathbf{v^{*}}$ by minimizing difference between the water uses of treated units and the synthetic controls in the pre-treatment period ($1, 2, \dots, T_0$):
 
@@
     % https://github.com/OscarEngelbrektson/SyntheticControlMethods/issues/18 这里和README不一样，因为它有问题
-    \mathbf{V}^{*}=\underset{\mathbf{V} \in \mathcal{V}}{\operatorname{argmin}}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)^{\prime}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)
+    \mathbf{v}^{*}=\underset{\mathbf{v} \in \mathcal{V}}{\operatorname{argmin}}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{w}^{*}(\mathbf{v})\right)^{\prime}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{w}^{*}(\mathbf{v})\right)
 \end{equation}
 
-That is the minimum difference between the water uses of treated units and the synthetic controls in the pre-treatment period ($1, 2, \dots, T_0$), where $\mathbf{Z}_{1}$ is a matrix containing every observation of the water use for the treated unit.
-Similarly, $\mathbf{Z}_{0}$ is a ($J \times T_0$) matrix contains the water use for each control unit in this period.
+where $\mathbf{Z}_{1}$ is a matrix containing every observation of the water use for the treated unit, and $\mathbf{Z}_{0}$ is a ($T_0 \times J$) matrix contains the water use for each control unit in this period.
 The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with better robustness~\cite{billmeier2013, smith2015}.

### 2023-11-02 docs/papers/04_response_letter/source/editor.tex
fix(project): :memo: response letter

@@
 
-% TODO \AR{} I am grateful for the encouragement and the direction provided to enhance our manuscript.
-It has been a privilege to contribute to this special issue, and I believe that the revisions made align with the expectations and vision set forth by the editorial team.
+\AR{} We would like to express our sincere gratitude for the opportunity to revise our manuscript and for the constructive comments from the reviewers which have been instrumental in enhancing the quality of our paper.
+
+\AR*{} Following the guidance provided, we have meticulously revised the manuscript, paying particular attention to the clarity of the methodological section as suggested.
+We have addressed all the concerns raised by Reviewer 1, including the accurate representation of mathematical equations and the logical sequence of our methodology.
+
+\AR*{} We are confident that the changes made have significantly improved the manuscript, and we believe it is now ready for publication.
+We hope that the modifications meet the journal’s standards and look forward to the possibility of our study contributing to the journal's esteemed collection of research.
+
+\AR*{} Thank you once again for your assistance and the reviewers for their essential insights.

### 2023-11-02 docs/papers/04_response_letter/source/reviewer_1.tex
fix(project): :memo: response letter

@@
 
-% Eq 1: V怎么可能是一个向量，而不是一个矩阵?在Eq 1中的矩阵乘法只是不工作与指定的维度!X_1的维数是多少?作者指定W是一个(J x 1)向量，X_0是一个(k x J)矩阵。这意味着乘积(X_0 W)是一个(k x 1)向量，所以X_1也应该是一个(k x 1)向量。这意味着(X_1 - X_0 W)'和(X_1 - X_0 W)的维数应该是(1 × k)和(k × 1)。为了使方程1成立，V必须是一个(k × k)矩阵。我错过什么了吗?如果我误解了什么，请澄清。
+% 非常抱歉造成了新的困惑，我们承认之前在方法数学描述上的经验不足。现在，我们请了数学家帮我们矫正了方法表述，我希望您可以在本次修订中发现所有的步骤已得到清晰准确的描述。
+\AR{} We apologize for any new confusion because of our lack of experience in mathematical descriptions of this method.
+Now that we have had mathematicians help us correct the representation, I hope you will find that all the steps are clearly and accurately described in this revision.
+We are attaching the changes here and will respond to your specific comments later (\ref{specific_comments}).
+
+\begin{quote}[page=7, sline=139, eline=159]
+    The treated unit is exposed to the institutional shift in every post-treatment period $T_0 +1, \dots, T$, and unaffected by the institutional shift in preceding periods $1, 2, \dots, T_0$.
+    Any weighted average of the control units is referred as a synthetic control and is denoted by a ($J \times 1$) vector of weights $\mathbf{w} = (w_{1}, \ldots ,w_{J})$, satisfying $w_j \in (0, 1)$ and $w_1 + \cdots  + w_{J} = 1$.
+    We also introduce a ($k \times 1$) non-negative vector $\mathbf{v} = (v_{1}, \ldots ,v_{k}$) to weight the relative importance of each covariate, where $k$ is the product of $T$ and $D$, the number of years and dimensions in the dataset ($D = 5$ in this case).
+    The vector $\mathbf{v}$ must fulfill $v_1 + \cdots  + v_{k} = 1$, and $\mathbf{diag(v)}$ represents the diagonal matrix formed by the vector $\mathbf{v}$.
+    Then, the next goal is finding the optimal $\mathbf{w}$ which represents the best ``synthetic'' versions of the affected provinces in the YRB.\
+    Given $\mathbf{v}$, we define $\mathbf{w^{*}(v)}$ as a function of $\mathbf{v}$ that minimizes the discrepancy between the pre-treatment characteristics of the treated unit and the synthetic control:
+
+    \begin{equation}\label{eq1}
+        \mathbf{w^{*}(v)}=\underset{\mathbf{w} \in \mathcal{W}}{\operatorname{argmin}}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{w}\right)^{\prime} \mathbf{diag(v)}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{w}\right)
+    \end{equation}
+
+    Here, matrix $\mathbf{X_1}$ represents the pre-treatment average of each dimension in the dataset for the treated unit, while $\mathbf{X_0}$ is a ($k \times J$) matrix containing the pre-treatment characteristics for each of the $J$ control units.
+    Finally, we choose $\mathbf{v^{*}}$ by minimizing difference between the water uses of treated units and the synthetic controls in the pre-treatment period ($1, 2, \dots, T_0$):
+
+    \begin{equation}\label{eq2}
+        % https://github.com/OscarEngelbrektson/SyntheticControlMethods/issues/18 这里和README不一样，因为它有问题
+        \mathbf{v}^{*}=\underset{\mathbf{v} \in \mathcal{V}}{\operatorname{argmin}}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{w}^{*}(\mathbf{v})\right)^{\prime}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{w}^{*}(\mathbf{v})\right)
+    \end{equation}
+
+    where $\mathbf{Z}_{1}$ is a matrix containing every observation of the water use for the treated unit, and $\mathbf{Z}_{0}$ is a ($T_0 \times J$) matrix contains the water use for each control unit in this period.
+    The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with better robustness~\cite{billmeier2013, smith2015}.
+    In this study, we adopted the algorithm by the ``Synthetic Control Methods'' Python library (version 1.1.17)~\cite{engelbrektson2023} for the minimization.
+
+\end{quote}
+
+\subsection*{Specific comments}\label{specific_comments}
+
+% Eq 1: V怎么可能是一个向量，而不是一个矩阵?在Eq 1中的矩阵乘法只是不工作与指定的维度!X_1的维数是多少?作者指定W是一个(J \times 1)向量，X_0是一个(k \times J)矩阵。这意味着乘积(X_0 W)是一个(k \times 1)向量，所以X_1也应该是一个(k \times 1)向量。这意味着(X_1 - X_0 W)'和(X_1 - X_0 W)的维数应该是(1 × k)和(k × 1)。为了使方程1成立，V必须是一个(k × k)矩阵。我错过什么了吗?如果我误解了什么，请澄清。
 \RC{} Eq 1: How can V be a vector, not a matrix?
 The matrix multiplication in Eq 1 just doesn't work with the dimensions specified!
-And what is the dimension of X_1?
-The authors specified that W is a (J x 1) vector and X_0 is a (k x J) matrix.
-This implies that the product (X_0 W) is a (k x 1) vector, so X_1 should be a (k x 1) vector as well.
-Which means that (X_1 - X_0 W)' and (X_1 - X_0 W) should have dimensions of (1 x k) and (k x 1).
-For Eq 1 to work, V must be a (k x k) matrix.
+And what is the dimension of $X_1$?
+The authors specified that W is a $(J \times 1)$ vector and $X_0$ is a $(k \times J)$ matrix.
+This implies that the product $(X_0 W)$ is a $(k \times 1)$ vector, so $X_1$ should be a $(k \times 1)$ vector as well.
+Which means that $(X_1 - X_0 W)'$ and $(X_1 - X_0 W)$ should have dimensions of $(1 \times k)$ and $(k \times 1)$.
+For Eq 1 to work, V must be a $(k \times k)$ matrix.
 Did I miss something here?
 If I misunderstood anything here, please clarify.
+
+% 是的，非常抱歉之前因表述错误而造成的误解。V应该是一个向量构造的对角矩阵。这已经在修订后的段落中得到了说明
+\AR{} We apologize for the confusion caused by the erroneous description of $\mathbf{V}$ in the initial submission.
+Upon review, we acknowledge that it lacked clarity that $\mathbf{v}$ (lower case now) is indeed a vector, but used as a diagonal matrix in the equation.
+This correction is accompanied by a detailed explanation in the methodology section to avoid any future misunderstanding.
+
+\begin{quote}[page=7, sline=142, eline=149]
+    We also introduce a ($k \times 1$) non-negative vector $\mathbf{v} = (v_{1}, \ldots ,v_{k}$) to weight the relative importance of each covariate, where $k$ is the product of $T$ and $D$, the number of years and dimensions in the dataset ($D = 5$ in this case).
+    The vector $\mathbf{v}$ must fulfill $v_1 + \cdots  + v_{k} = 1$, and we introduce $\mathbf{diag(v)}$ as the diagonal matrix formed by the vector $\mathbf{v}$.
+\end{quote}
 
@@
 
-% Z的维数不应该是(T_0 x J)，而不是(J x T_0)吗?否则，它就不能从右边乘以W, W的维数是(jx1)再说一遍，我漏了什么吗?如果我误解了什么，请澄清。
+% 这个问题应该是之前不当表述所造成的误解。通过现在更清晰的表述中，我们的读者会发现这不是一个循环。在式子1可以理解为关于W*的定义，将其表达为向量v的函数。因此，式子2的右边也是v的函数，因此v*就是让这个函数取最小值的一个向量解。
+\AR{} The raised doubt of any circular logic in our methodological approach may be a result of an imprecise explanation in our initial submission.
+Actually, the Equation~\ref{eq1} is presented as the definition of $\mathbf{w^*}$ which is expressed as a function of the vector $\mathbf{v}$.
+Therefore, the right-hand side of Equation~\ref{eq2} can be also formulated as a function of the vector $\mathbf{v}$, leading to $\mathbf{v^*}$ representing the vector that minimizes this function.
+This approach ensures that the optimization process doesn't have any circularity.
+We trust that this revised mathematical descriptions will make the method's steps transparent and logical to our readers.
+
+% Z的维数不应该是(T_0 \times J)，而不是(J \times T_0)吗?否则，它就不能从右边乘以W, W的维数是(jx1)再说一遍，我漏了什么吗?如果我误解了什么，请澄清。
 \RC{} Eq.
-2: Shouldn't Z's dimension be (T_0 x J), not (J x T_0)?
-Otherwise, it cannot be multiplied from the right by W, which has the dimension of (J x 1).
+2: Shouldn't Z's dimension be $(T_0 \times J)$, not $(J \times T_0)$?
+Otherwise, it cannot be multiplied from the right by W, which has the dimension of $(J \times 1)$.
 Again, did I miss something here?
 If I misunderstood anything here, please clarify.
+
+% 抱歉，这是我们之前的错误，我们已经将维度表达修正了过来。
+\AR{} Sorry, it was our previous mistake, we have corrected the dimensional expression from $(T_0 \times J)$ to $(J \times T_0)$.
 
@@
 I strongly suggest that the authors be VERY CAREFUL in the next revision.
+
+% 非常感谢您对本研究意义的认可，我们相信，我们对该方法的应用识别并解释了一个非常有趣的现象。也非常抱歉之前的手稿造成困惑，我们希望新的手稿对读者来说表述足够清晰！
+\AR{} We are very grateful for your recognition of the significance of our research.
+We believe that the application of the method has identified and explained an intriguing phenomenon that will be of considerable interest to our readers.
+We also sincerely apologize for any confusion caused by our earlier manuscript.
+It has been our aim in this revision to present our methodology and findings with utmost clarity, and we hope that the readers will find the new manuscript to be lucid and straightforward.

### 2023-11-21 docs/papers/04_response_letter/source/reviewer_1.tex
fix(method): :bug: typo fix from T to T0

--- 2023-11-01 docs/papers/04_response_letter/source/reviewer_1.tex
@@
 
-% 在大多数情况下，作者已经解决了我在原始提交中关于单词选择和各种符号混淆的评论，我对此表示赞赏。然而，差分综合控制方法的描述，如果有什么的话，变得更让我困惑!
-\RC{} For the most part, the authors have addressed my comments regarding word choices and various notational confusion in the original submission, and I appreciate that.
-However, the description of the Differenced Synthetic Control method, if anything, becomes even more confusing to me!
+Reviewer \#1: I appreciate that the authors took my comments seriously and apparently invested efforts in improving the description of the method, which indeed has become clearer.
+That said, some confusing points remain.
+I will be specific here.
+Please clarify the following three points.
 
-% Eq 1: V怎么可能是一个向量，而不是一个矩阵?在Eq 1中的矩阵乘法只是不工作与指定的维度!X_1的维数是多少?作者指定W是一个(J x 1)向量，X_0是一个(k x J)矩阵。这意味着乘积(X_0 W)是一个(k x 1)向量，所以X_1也应该是一个(k x 1)向量。这意味着(X_1 - X_0 W)'和(X_1 - X_0 W)的维数应该是(1 × k)和(k × 1)。为了使方程1成立，V必须是一个(k × k)矩阵。我错过什么了吗?如果我误解了什么，请澄清。
-\RC{} Eq 1: How can V be a vector, not a matrix?
-The matrix multiplication in Eq 1 just doesn't work with the dimensions specified!
-And what is the dimension of X_1?
-The authors specified that W is a (J x 1) vector and X_0 is a (k x J) matrix.
-This implies that the product (X_0 W) is a (k x 1) vector, so X_1 should be a (k x 1) vector as well.
-Which means that (X_1 - X_0 W)' and (X_1 - X_0 W) should have dimensions of (1 x k) and (k x 1).
-For Eq 1 to work, V must be a (k x k) matrix.
-Did I miss something here?
-If I misunderstood anything here, please clarify.
+\RC{} Is $k = T x D$ or $T_0 x D$?
+Currently, it is stated that ``$k$ is the product of $T$ and $D$, the number of years and dimensions in the dataset.'' However, this portion of the method focuses on the PRE-TREATMENT characteristics, shouldn't we use only the data from the PRE-TREATMENT period, i.e., $T_0$ years?
+As such, shouldn't $k$ be ``the product of $T_0$ and $D$, the number of pre-treatment years and dimensions''?
 
-% 加上，如何确定V的项的值?公式2表明需要W来确定V?但这不是循环逻辑吗?所以你需要最优的V来确定W，但你也需要最优的W来确定最优的V?哪些优化必须先做?
-\RC{} Plus, how does one determine the values of V's entries?
-Eq.
-2 suggests that one needs W to determine V?
-But isn't that circular logic?
-So you need the optimal V to determine W, but you also need the optimal W to determine the optimal V?
-Which optimization must be done first?
+% 是的，您的理解是正确的，这里的数据集指的是pre-treatment的部分，抱歉这没有写得更清楚，T的符号是一个笔误，我们已经修改成T0.
+\AR{} Yes, your understanding is correct, the data set here refers to the part of pre-treatment, sorry it was not written more clearly, the symbol of $T$ is a clerical error, we have modified it to $T_0$.
+Thank you for your care to make all this sentence more clear:
 
-% Z的维数不应该是(T_0 x J)，而不是(J x T_0)吗?否则，它就不能从右边乘以W, W的维数是(jx1)再说一遍，我漏了什么吗?如果我误解了什么，请澄清。
-\RC{} Eq.
-2: Shouldn't Z's dimension be (T_0 x J), not (J x T_0)?
-Otherwise, it cannot be multiplied from the right by W, which has the dimension of (J x 1).
-Again, did I miss something here?
-If I misunderstood anything here, please clarify.
+\begin{quote}
+    $\dots$ where $k$ is the product of $T_0$ and $D$, the number of pre-treatment years and dimensions in the dataset ($D = 5$ in this case).
+\end{quote}
 
-% 虽然我仍然认为这项研究可能会引起期刊读者的兴趣，正如我上面的沮丧所表明的那样，方法描述非常令人困惑，并且没有得到充分的解决。我强烈建议作者在下次修订时要非常小心。
-\RC{} While I still think that the study can be of interest to the journal's readership, as indicated by my frustration above, the method description is very confusing and has not been adequately addressed.
-I strongly suggest that the authors be VERY CAREFUL in the next revision.
+\RC{} The authors still wrote ``matrix $X_1$'' -again, I don't see how the math would work if $X_1$ is a matrix.
+In Eq.
+1, $X_0$ is a ($k \times J$) matrix and $W$ is a ($J \times 1$) vector.
+This implies that the product ($X_0$, $W$) is a ($k \times 1$) vector, so $X_1$ should be a ($k \times 1$) vector as well, with each entry being the value of one the dimensions in one of the pre-treatment years.
+Please CLARIFY THE DEFINITION and EXPLICITLY INCLUDE THE DIMENSION OF $X_1$, which was one of the questions I previously asked.
+
+% 谢谢您指出这个问题，我们去除了容易让读者混淆的“矩阵”表述，并标明了其维度。
+\AR{} Thank you for pointing this out. We have removed the expression of ``matrix'', which is easy to confuse readers, and indicated its dimensions:
+
+\begin{quote}
+    $\mathbf{X_1}$ is a ($k \times 1$) vector containing the pre-treatment average of each dimension in the dataset for the treated unit $\dots$
+\end{quote}
+
+\RC{} Similarly, the authors wrote ``$Z_1$ is a matrix $\dots$'' -again, I don't see how the math would work if $Z_1$ is a matrix.
+In Eq.
+2, $Z_0$ is a ($T_0 \times J$) vector and $w*(v)$ is a $(J \times 1)$ matrix.
+This implies that the product ($Z_0 \times w*(v)$) is a ($T_0 \times 1$) vector, so $Z_1$ should be a ($T_0 \times 1$) vector as well, with each entry being the water use of the treated united in a given pre-treatment year.
+Please EXPLICITLY INCLUDE THE DIMENSION OF $Z_1$.
+
+\AR{} Similarly, we have removed the expression of ``matrix'' and introduced its dimensions directly:
+
+\begin{quote}
+    where $\mathbf{Z}_{1}$ is a ($T_0 \times 1$) vector containing every observation of the water use for the treated unit $\dots$
+\end{quote}
+
+As before, if I missed something or misunderstood anything here, please clarify.
+
+% 非常感谢您对本研究意义的认可，我们相信，我们对该方法的应用识别并解释了一个非常有趣的现象。也非常抱歉之前的手稿造成困惑，我们希望新的手稿对读者来说表述足够清晰！
+\AR{} We are very grateful for your recognition of our previous improvements of the manuscript.
+As you pointed out, we can indicate the dimensions for readers to understand better, and thanks to your valuable suggestions, we now fully follow them and further enhance the manuscript.

### 2025-02-11 docs/papers/01_manuscript/tab_rmse.tex
fix(project): :pencil2: Fix typo in paper for thesis

@@
 	  \midrule
-	  Qinghai & 5.26  & =     & FALSE & 5.89  & >     & TRUE \\
-	  Gansu & 10.37  & >     & TRUE  & 9.55  & >     & TRUE \\
-	  Ningxia & 5.81  & =     & FALSE & 6.83  & >     & TRUE \\
-	  Inner Mongolia & 7.11  & >     & TRUE  & 1.60  & <     & TRUE \\
-	  Shanxi & 1.72  & <     & TRUE  & 5.60  & >     & TRUE \\
-	  Shaanxi & 3.05  & <     & TRUE  & 3.01  & >     & TRUE \\
-	  Henan & 20.66  & >     & TRUE  & 1.18  & <     & TRUE \\
-	  Shandong & 4.54  & =     & FALSE & 4.14  & >     & TRUE \\
+	  Qinghai & 5.26  & $=$     & FALSE & 5.89  & $>$     & TRUE \\
+	  Gansu & 10.37  & $>$     & TRUE  & 9.55  & $>$     & TRUE \\
+	  Ningxia & 5.81  & $=$     & FALSE & 6.83  & $>$     & TRUE \\
+	  Inner Mongolia & 7.11  & $>$     & TRUE  & 1.60  & $<$     & TRUE \\
+	  Shanxi & 1.72  & $<$     & TRUE  & 5.60  & $>$     & TRUE \\
+	  Shaanxi & 3.05  & $<$     & TRUE  & 3.01  & $>$     & TRUE \\
+	  Henan & 20.66  & $>$     & TRUE  & 1.18  & $<$     & TRUE \\
+	  Shandong & 4.54  & $=$     & FALSE & 4.14  & $>$     & TRUE \\
 	  \bottomrule

### 2025-02-11 docs/papers/04_response_letter/source/reviewer_1.tex
fix(project): :pencil2: Fix typo in paper for thesis

@@
 
-\RC{} Is $k = T x D$ or $T_0 x D$?
+\RC{} Is $k = T \times D$ or $T_0 \times D$?
 Currently, it is stated that ``$k$ is the product of $T$ and $D$, the number of years and dimensions in the dataset.'' However, this portion of the method focuses on the PRE-TREATMENT characteristics, shouldn't we use only the data from the PRE-TREATMENT period, i.e., $T_0$ years?
@@
 
-\begin{quote}
+\begin{quote}[page=7, sline=144, eline=145]
     $\dots$ where $k$ is the product of $T_0$ and $D$, the number of pre-treatment years and dimensions in the dataset ($D = 5$ in this case).
@@
 
-\begin{quote}
+\begin{quote}[page=7, sline=150, eline=151]
     $\mathbf{X_1}$ is a ($k \times 1$) vector containing the pre-treatment average of each dimension in the dataset for the treated unit $\dots$
@@
 
-\begin{quote}
+\begin{quote}[page=7, sline=155, eline=156]
     where $\mathbf{Z}_{1}$ is a ($T_0 \times 1$) vector containing every observation of the water use for the treated unit $\dots$

### 2025-02-11 core/src/multi_synth.py
feat(method): :sparkles: Export fitted weight and updated the README.md file

@@ -422,3 +422,28 @@ class MultiSynth:
             if i not in [0, 4]:
                 ax.set_ylabel("")
         return fig
+
+    def export_weights(self):
+        """
+        合并多个处理单位的权重到一个宽格式数据框
+
+        参数:
+        weights_dict: 字典，键为处理单位名称，值为对应的权重数据框
+
+        返回:
+        pandas DataFrame: 宽格式的权重数据框，索引为控制单位，列为处理单位
+        """
+        # 创建一个空的列表来存储每个处理单位的权重
+        dfs = []
+
+        for treated_unit, model in self.units.items():
+            weight_df = model.model.original_data.weight_df
+            # 假设weight_df有'Unit'和'Weight'列
+            # 将权重序列重命名为处理单位名称
+            series = weight_df["Weight"]
+            series.name = treated_unit
+            dfs.append(series)
+
+        # 水平合并所有序列
+        combined_weights = pd.concat(dfs, axis=1)
+        return combined_weights

### 2025-02-11 docs/papers/00_cover_letter/abstract.tex

@@
 Our results suggest that two institutional shifts, the Water Allocation Scheme that began in 1987 (87-WAS) and the Unified Basinal Regulation that took over in 1998 (98-UBR), framed different social-ecological system (SES) structures.
-During the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $8.57\%$ more than expected while 98-UBR successfully decreased total water use, ultimately.
+During the decade following the introduction of the 87-WAS, observed water use of the YRB increased by $5.75\%$ more than expected while 98-UBR successfully decreased total water use, ultimately.
 Specifically, 87-WAS stimulated increased water use in some provinces (e.g., Inner Mongolia, Henan, and Shandong), but 98-UBR regulated nearly all provinces.

### 2025-02-11 docs/papers/01_manuscript/03_results.tex
fix(method): :memo: expression "robustness" and "placebo"

@@
 The total water use of the YRB exhibited a significant difference between the counterfactual prediction and the actual observed value after the two institutional shifts, while the difference was small and insignificant before (see Figures~\ref{fig:main_results}A and B).
-This indicates that the estimated reconstruction of water use change was robust.
+This indicates that the estimated reconstruction of water use change was effective.
 Figure~\ref{fig:main_results}A suggests that the 87-WAS prompted the provinces to withdraw even more water than would have been used without an institutional shift (Figure~\ref{fig:main_results}A).
-From 1988 to 1998, on average, while the estimation of annual water use only suggests $887.05~km^3$ billion $m^3$, the observed water use of the YRB provinces reached $938.06$ billion $m^3$ (an increase of $5.75\%$).
+% NOTE: 这里是每年 xxx 立方米
+From 1988 to 1998, on average, while the estimation of annual water use only suggests $887.05$ billion $m^3$, the observed water use of the YRB provinces reached $938.06$ billion $m^3$ (an increase of $5.75\%$).
 However, after the 98-UBR, trends of increasing water use appeared to be effectively suppressed.

### 2025-02-11 docs/papers/01_manuscript/06_methods.tex

@@
 Any weighted average of the control units is referred as a synthetic control and is denoted by a ($J \times 1$) vector of weights $\mathbf{w} = (w_{1}, \ldots ,w_{J})$, satisfying $w_j \in (0, 1)$ and $w_1 + \cdots  + w_{J} = 1$.
-We also introduce a ($k \times 1$) non-negative vector $\mathbf{v} = (v_{1}, \ldots ,v_{k}$) to weight the relative importance of each covariate, where $k$ is the product of $T$ and $D$, the number of years and dimensions in the dataset ($D = 5$ in this case).
+We also introduce a ($k \times 1$) non-negative vector $\mathbf{v} = (v_{1}, \ldots ,v_{k}$) to weight the relative importance of each covariate, where $k$ is the product of $T_0$ and $D$, the number of pre-treatment years and dimensions in the dataset ($D = 5$ in this case).
 The vector $\mathbf{v}$ must fulfill $v_1 + \cdots  + v_{k} = 1$, and $\mathbf{diag(v)}$ represents the diagonal matrix formed by the vector $\mathbf{v}$.
@@
 
-Here, matrix $\mathbf{X_1}$ represents the pre-treatment average of each dimension in the dataset for the treated unit, while $\mathbf{X_0}$ is a ($k \times J$) matrix containing the pre-treatment characteristics for each of the $J$ control units.
+Here, $\mathbf{X_1}$ is a ($k \times 1$) vector containing the pre-treatment average of each dimension in the dataset for the treated unit, while $\mathbf{X_0}$ is a ($k \times J$) matrix containing the pre-treatment characteristics for each of the $J$ control units.
 Finally, we choose $\mathbf{v^{*}}$ by minimizing difference between the water uses of treated units and the synthetic controls in the pre-treatment period ($1, 2, \dots, T_0$):
@@
 
-where $\mathbf{Z}_{1}$ is a matrix containing every observation of the water use for the treated unit, and $\mathbf{Z}_{0}$ is a ($T_0 \times J$) matrix contains the water use for each control unit in this period.
+where $\mathbf{Z}_{1}$ is a ($T_0 \times 1$) vector containing every observation of the water use for the treated unit, and $\mathbf{Z}_{0}$ is a ($T_0 \times J$) matrix containing the water use for each control unit in this period.
 The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with better robustness~\cite{billmeier2013, smith2015}.

### 2025-02-11 docs/papers/01_manuscript/elsarticle-template.tex

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\journal{Journal of \LaTeX\ Templates}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{2}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{Elsevier \LaTeX\ template\tnoteref{mytitlenote}}
\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

%% Group authors per affiliation:
\author{Elsevier\fnref{myfootnote}}
\address{Radarweg 29, Amsterdam}
\fntext[myfootnote]{Since 1880.}

%% or include affiliations in footnotes:
\author[mymainaddress,mysecondaryaddress]{Elsevier Inc}
\ead[url]{www.elsevier.com}

\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{support@elsevier.com}

\address[mymainaddress]{1600 John F Kennedy Boulevard, Philadelphia}
\address[mysecondaryaddress]{360 Park Avenue South, New York}

\begin{abstract}
This template helps you to create a properly formatted \LaTeX\ manuscript.
\end{abstract}

\begin{keyword}
\texttt{elsarticle.cls}\sep \LaTeX\sep Elsevier \sep template
\MSC[2010] 00-01\sep  99-00
\end{keyword}

\end{frontmatter}

\linenumbers

\section{The Elsevier article class}

\paragraph{Installation} If the document class \emph{elsarticle} is not available on your computer, you can download and install the system package \emph{texlive-publishers} (Linux) or install the \LaTeX\ package \emph{elsarticle} using the package manager of your \TeX\ installation, which is typically \TeX\ Live or Mik\TeX.

\paragraph{Usage} Once the package is properly installed, you can use the document class \emph{elsarticle} to create a manuscript. Please make sure that your manuscript follows the guidelines in the Guide for Authors of the relevant journal. It is not necessary to typeset your manuscript in exactly the same way as an article, unless you are submitting to a camera-ready copy (CRC) journal.

\paragraph{Functionality} The Elsevier article class is based on the standard article class and supports almost all of the functionality of that class. In addition, it features commands and options to format the
\begin{itemize}
\item document style
\item baselineskip
\item front matter
\item keywords and MSC codes
\item theorems, definitions and proofs
\item lables of enumerations
\item citation style and labeling.
\end{itemize}

\section{Front matter}

The author names and affiliations could be formatted in two ways:
\begin{enumerate}[(1)]
\item Group the authors per affiliation.
\item Use footnotes to indicate the affiliations.
\end{enumerate}
See the front matter of this document for examples. You are recommended to conform your choice to the journal you are submitting to.

\section{Bibliography styles}

There are various bibliography styles available. You can select the style of your choice in the preamble of this document. These styles are Elsevier styles based on standard styles like Harvard and Vancouver. Please use Bib\TeX\ to generate your bibliography and include DOIs whenever available.

Here are two sample references: \cite{Feynman1963118,Dirac1953888}.

\section*{References}

\bibliography{mybibfile}

\end{document}

### 2025-02-11 docs/papers/01_manuscript/out/manuscript_v-7.1.2.tex

--- 2023-07-29 docs/papers/01_manuscript/manuscript_v-7.1.2.tex
@@
 Firstly, the results challenge previous analyses (i.e., suggesting that 87-WAS ``had little practical effect'') because theoretically, there should be few gaps between actual and synthetic water use in the YRB if no effect is present~\cite{abadie2015,hill2021}.
-However, the significant net effect indicated by our analysis suggests that the 87-WAS was followed by increased water use even after controlling for environmental and economic variables (see \textit{\nameref{secS2}} Table~\ref{tab:variables}).
+However, the significant net effect indicated by our analysis suggests that the 87-WAS was followed by increased water use even after controlling for environmental and economic variables (see \textit{\ref{secS2}} Table~\ref{tab:variables}).
 In contrast, the 98-UBR reduced surface water competition, so many studies attributed the streamflow restoration mainly to the successful introduction of this institution~\cite{chen2021,huangang2002,an2007}.
@@
 Our results align with this hypothesis since the correlation between current water use and changed (increased or decreased) water use was significant after the 87-WAS but not after the 98-UBR (Figure~\ref{fig:regulating}).
-In addition, through a theoretically marginal benefit analysis, this ``major users use more'' pattern can be inferred from a simple assumption that stakeholders can expect water quota's value in the short future, also supporting the above hypothesis (see \textit{\nameref{secS4}}).
+In addition, through a theoretically marginal benefit analysis, this ``major users use more'' pattern can be inferred from a simple assumption that stakeholders can expect water quota's value in the short future, also supporting the above hypothesis (see \textit{\ref{secS4}}).
 

### 2025-02-11 docs/papers/01_manuscript/out/manuscript_v-7.3.0.tex

--- 2023-11-01 docs/papers/01_manuscript/manuscript_v-7.2.2.tex
@@
 
+\graphicspath{{../../../figs/}}
 \journal{Jounral of Hydrology}
@@
 Here, matrix $\mathbf{X_1}$ represents the pre-treatment average of each dimension in the dataset for the treated unit, while $\mathbf{X_0}$ is a ($k \times J$) matrix containing the pre-treatment characteristics for each of the $J$ control units.
-We also define $\mathbf{W}^{*}(V)$ as the vector of weights $\mathbf{W}$ that minimizes the discrepancy between the pre-treatment characteristics of the treated unit and the synthetic control for a given $\mathbf{V}$.
-That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W^{*}(V)}$.
-Therefore, we choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{{W}^{*}(V)}$ that minimizes the following expression:
+Finally, we choose $\mathbf{v^{*}}$ by minimizing difference between the water uses of treated units and the synthetic controls in the pre-treatment period ($1, 2, \dots, T_0$):
 
 \begin{equation}
-\mathbf{V}^{*}=\underset{\mathbf{V} \in \mathcal{V}}{\operatorname{argmin}}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)^{\prime}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)
+\mathbf{v}^{*}=\underset{\mathbf{v} \in \mathcal{V}}{\operatorname{argmin}}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{w}^{*}(\mathbf{v})\right)^{\prime}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{w}^{*}(\mathbf{v})\right)
 \end{equation}
 
-That is the minimum difference between the water uses of treated units and the synthetic controls in the pre-treatment period ($1, 2, \dots, T_0$), where $\mathbf{Z}_{1}$ is a matrix containing every observation of the water use for the treated unit.
-Similarly, $\mathbf{Z}_{0}$ is a ($J \times T_0$) matrix contains the water use for each control unit in this period.
+where $\mathbf{Z}_{1}$ is a matrix containing every observation of the water use for the treated unit, and $\mathbf{Z}_{0}$ is a ($T_0 \times J$) matrix contains the water use for each control unit in this period.
 The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with better robustness~\cite{billmeier2013, smith2015}.
@@
 \textbf{Acknowledgments}\\
-This research has been supported by the National Natural Science Foundation of China (grant no. 42041007) and the Fundamental Research Funds for the Central Universities.
+This research has been supported by the National Natural Science Foundation of China (grant no.
+42041007) and the Fundamental Research Funds for the Central Universities.
+Thanks to two anonymous reviewers for their comments, and Yinan Xiao from Peking University for his help in editing mathematical parts of the manuscript.
 

### 2025-02-11 docs/papers/01_manuscript/tab_data_source.tex

--- 2023-11-01 docs/papers/01_manuscript/manuscript_v-7.2.2.tex
@@
-\documentclass[preprint, 12pt]{elsarticle}
-
-\usepackage{amssymb}
-\usepackage{amsmath, graphicx, array}
-\usepackage{dcolumn, soul}\let\openbox\relax
-\usepackage{amsthm}
-\usepackage[figuresright]{rotating}\usepackage{algorithm, algorithmicx, algpseudocode}
-\usepackage{listings}\usepackage{hyperref}
-\usepackage{geometry}
-\usepackage{tabularx}
-
-\geometry{a4paper,left=2.0cm,right=2.0cm,top=2.5cm,bottom=2.5cm}
-\linespread{1.5}
-\newtheorem{defn}{Definition}
-\newtheorem{thm}{Theorem}
-\newtheorem{ass}{Assumption}
-\newtheorem{prop}{Proposition}
-\newtheorem{fig}{Fig.}
-\newtheorem{case}{Case}
-\newtheorem{case_appendix}{Case}
-\newtheorem{example}{Example}[section]
-\renewcommand{\proofname}{\textbf{Proof}}
-\newtheorem{property}{Property}
-\newtheorem{remark}{Remark}
-\usepackage{enumitem}
-\usepackage{float}
-\usepackage{multirow}
-\usepackage{lineno}
-\usepackage{booktabs}
-\usepackage{diagbox}
-
-\journal{Jounral of Hydrology}
-
-\begin{document}
-\begin{frontmatter}
-
-\title{Quantifying the Effects of Institutional Shifts on Water Governance in the Yellow River Basin: A Social-ecological System Perspective}
-
-\author[inst1]{Shuang Song}
-\author[inst2]{Huiyu Wen}
-\author[inst1]{*Shuai Wang}
-\author[inst1]{Xutong Wu}
-
-\author[inst3]{Graeme S. Cumming}
-\author[inst1]{Bojie Fu}
-
-\affiliation[inst1]{
-     State Key Laboratory of Earth Surface Processes and Resource Ecology,
-     Faculty of Geographical Science,
-     Beijing Normal University,
-     Beijing 100875,
-     P.R. China}
-
-\affiliation[inst2]{School of Finance,
-     Renmin University of China,
-     Beijing 100875,
-     P.R. China}
-
-\affiliation[inst3]{
-     ARC Centre of Excellence for Coral Reef Studies,
-     James Cook University,
-     Townsville 4811,
-     QLD, Australia}
-
-\begin{abstract}
-     Water governance in river basins worldwide faces challenges due to complex socio-economic and environmental factors.
-In the Yellow River Basin (YRB), two major institutional shifts, the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basin Regulation (98-UBR), aimed to address water allocation and usage issues.
-This study quantifies the net effects of these institutional shifts on water use within the YRB and analyzes the underlying reasons for their success or failure.
-     We employ a Differenced Synthetic Control method to assess the impacts of the institutional shifts.
-Our analysis suggests that the 87-WAS unexpectedly increased water use by $5.75\%$, while the 98-UBR successfully reduced water use as anticipated.
-Our research highlights the role of institutional structures in governance policies, demonstrating that the mismatched structure of the 87-WAS led to increased competition and exploitation of water resources, while the 98-UBR, basin-wide authority and stronger connections between stakeholders, resulted in improved water governance.
-     Our study underscores the importance of designing institutions that are consistent with the scale of the ecological system, promote cooperation among stakeholders, and adapt to changing social-ecological system (SES) contexts.
-As outdated and inflexible water quotas may no longer meet the demands of sustainable development in the YRB, policymakers must consider the potential consequences of institutional shifts and their impact on water use and sustainability.
-\end{abstract}
-
-\begin{keyword}
-     water use~\sep~water governance~\sep~social-ecological system~\sep~institutions~\sep~Yellow River
-\end{keyword}
-
-\end{frontmatter}
-\newpage
-\linenumbers
-\section{Introduction}\label{sec:introduction}
-Widespread freshwater scarcity and overuse challenge the sustainability of large river basins, resulting in systematic risks to economies, societies, and ecosystems globally~\cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
-Amidst climate change, mismatches between supply and demand for water resources are expected to become increasingly more prominent~\cite{florke2018, yoon2021}.
-Consequently, large river basins are progressively seeking effective water governance solutions by coordinating stakeholders, providing water resources, and ensuring the sustainable allocation of shared water resources~\cite{wang2019d}.
-In this way, hydrological processes are tightly intertwined with societies, forming a social-ecological system (SES) at a basin scale with complex socio-hydrological feedback.
-
-Institutions encompass the interplay between social actors, ecological units, and their interactions~\cite{young2008, lien2020, bodin2017b, wang2022g} (Figure~\ref{fig:framework}~a).
-These interactions constitute a type of SES structure, where effective institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different interactions, contributing to sustainability~\cite{epstein2015, wang2019d} (Figure~\ref{fig:framework}~b).
-While some institutional advances have led to effective water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China~\cite{wang2019d}, and collaborative water governance systems in Europe~\cite{green2013}), imposing institutional shifts may create or destroy connections and effectiveness is not ubiquitous~\cite{loos2022}.
-For example, the Colorado River once experienced severe water shortage, and institutions led to various shortage magnitudes for different stakeholders even under the same water demand levels~\cite{hadjimichael2020}.
-Therefore, examining when and how an institution leads to effective water governance can bring crucial insights for the sustainability of river basins.
-
-Recent research has delved into the multifaceted effects of institutions on river basin governance, shedding light on diverse consequences and interactions~\cite{bouckaert2022, vallury2022, loch2020, kirchhoff2016}.
-Primarily due to the intricate dynamics within socio-hydrological systems, understanding the manner in which different SES structures influence institutional effectiveness remains a complex challenge~\cite{bodin2017b}.
-The current study contributes to this understanding by interpreting outcomes following institutional changes, though it does not explore hypothetical scenarios without such changes.
-Thus, knowledge gaps lie in the limited understanding of effective alignments between institutional shifts and SES structures, hindering the design of effective policies to promote sustainable river basin governance.
-To fill these knowledge gaps, we study the fifth-largest river worldwide and one of the most anthropogenically altered river basins, the Yellow River Basin (YRB) in China, to quantitatively measure the effects of changing SES structures.
-
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[width=0.5\linewidth]{diagrams/framework.png}
-	\caption{
-		Illustration for understanding institutional shifts and SES structural changes.
-\textbf{a.} In the general framework for analyzing social-ecological systems (SESs), (Adapted from Ostrom, 2008~\cite{ostrom2009}).
-Institutional shifts can change interactions within the SES and reframe the structures.
-\textbf{b.} We aim to examine how institutional shifts effect river basin governance by structuring SES.}\label{fig:framework}
-\end{figure}
-
-In the 1980s, intense water use, accounting for about $80\%$ of the Yellow River surface water, caused consecutive drying-up crises of runoff, leading to wetland shrinkage, agriculture reduction, and scrambles for water~\cite{wohlfart2016}.
-To alleviate water stress, Chinese authorities implemented several ambitious water management policies in the Yellow River Basin (YRB), such as the South-to-North Water Diversion Project and the Water Resources Allocation Institutions~\cite{long2020, wang2019d}.
-In this study, we specifically examined two significant institutional shifts in water allocation of the YRB\: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulating (98-UBR).
-Instead of focusing on engineering and increasing water supply, the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, an authority at a basin level) mainly aimed to limit water demands~\cite{bouckaert2022, speed2013}.
-These institutional shifts can offer valuable insights for two main reasons:
-(1) the top-down institutional shifts suddenly led to transformations of SES structures, allowing us to quantitatively estimate their net effects; and (2) the two institutional shifts within the same river basin provide rare comparable quasi-natural experiments.
-
-In this study, we portrayed changes of SES structures throughout the YRB's institutional shifts (the 87-WAS and the 98-UBR) and quantitatively investigated their consequences, followed by a discussion on the effectiveness of institutional shifts.
-Specifically, we first used the descriptions of official documents following the two institutional shifts to abstract the interactions between main stakeholders and their river segment units for interpreting SES structure changes between 1979 and 2008.
-Next, and perhaps most importantly, we employed the ``Differenced Synthetic Control (DSC)'' method~\cite{arkhangelsky2021}, which accounts for economic growth and natural background, to estimate theoretical water use volumes under scenarios absent of institutional shifts.
-Finally, in the discussion, we linked the effectiveness of institutional shifts to the portrayed structures, by comparing the YRB's case to previous SES structure studies and developing a marginal benefits analysis.
-
-\section{Study area and institutional contexts}\label{sec:yrb}
-
-The YRB, cradle of Chinese civilization, is located in north-central China and spans ten province-level regions whose socio-economic development heavily depends on water from the Yellow River.
-As a semi-arid and arid region, the YRB's annual precipitation varies from about 100 to 1,000 mm and increases from the northwest to the southeast, while the annual pan evaporation varies from about 700 to 1,800 mm~\cite{wang2022e}.
-Together, the YRB supports $35.63\%$ of China's irrigation and $30\%$ of its population while containing only $2.66\%$ of its water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today).
-Hence, over-withdrawing water from the Yellow River became an urgent concern when the river began to dry up in the early 1970s.
-Among the policies proposed to address the problem, a series of water resource allocation institutions aimed to limit water use for each region with specific quotas, which were regarded as some of the most important solutions.
-However, few attempts have been made to quantitatively assess how the YRB's water allocation scheme contributed to water governance, while other engineering solutions have been carefully evaluated~\cite{long2020}.
-
-The YRB was the first basin in China for which water resource allocation institutions were created, and institutional shifts can be traced through several regulating documents released by the Chinese government (at the national level):
-(1) In $1980s$, the central government proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019d, wang2019e}.
-(2) In $1987$, the Water Allocation Scheme was implemented (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
-(3) In $1998$, the Unified Basinal Regulation was implemented (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
-(4) In $2008$, provinces were asked to draw up new water resources plans for the YRB to further refine water allocations~\cite{wang2019d,wang2019e}.
-(5) In $2021$, there was a call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
-
-Our study period therefore ranges from $1980$ (when water quotas were proposed) to $2008$, when a regulating system with quotas was fully established at basin, provincial, and district levels.
-During this period, two significant institutional shifts can be analyzed using documents from $1987$ (87-WAS) and $1998$ (98-UBR), which split the study period into three sections: from $1980$ to $1987$ (before 87-WAS), from $1988$ to $1997$ (after 87-WAS and before 98-UBR), and from $1998$ to $2007$ (after 98-UBR).
-
-\section{Methods}\label{sec:methods}
-
-In this section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as organizational diagrams during different periods of time.
-Next, we introduce the dataset we used here and employ the Principal Components Analysis (PCA) method to reduce the dimensionality of variables affecting the total water use.
-We then estimate the net effects of the two institutional shifts on total water use, changing trends, and differences in the YRB's provinces using the Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021}.
-Finally, we introduce the tests approach for validating efficiency of the DSC model.
-
-\subsection{Portraying structures}\label{sec:structures}
-
-An organizational diagram is widely used to depict SES structures by abstracting links and nodes from the real-world interactions~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
-We apply the analysis of the organizational diagrams~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit at the basin scale (the Yellow River Conservancy Commission) into structural patterns from official documents.
-We examined the official documents of the two institutional shifts (87-WAS and 98-UBR) to portray the organizational diagrams in this study~\cite{bodin2017a,kluger2020,guerrero2015}.
-It is important to note that it can result in nuanced different structures when basin-scale regulatory entity (YRCC) is responsible for river reach regulation, or have direct authority to interact with provincial units.
-
-\subsection{Dataset and preprocessing}\label{sec:dataset}
-The data of water consumption surveys conducted by the Ministry of Water Resources were taken as the observed values throughout the years.
-Then, to estimate the water use of the YRB by assuming there were no effects from institutional shifts, we focused on $24$ variables from $5$ categories (environmental, economic, domestic, and technological) water use factors~(\textit{\ref{secS2}, Table~\ref{tab:variables}}).
-Among the total $31$ data-accessible provinces (or regions) assigned quotas in the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin and Beijing (together, Jinji) because of their trivial water use from the YRB (see Table~\ref{tab:quota}).
-
-Previous study has proved that combining PCA and DSC can lead to a more robust causal inference~\cite{bayani2021}.
-We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different.
-Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components $D$ (\textit{Appendix~\ref{secS2}~Figure\ref{fig:elbow}}).
-Finally, all $24$ normalized variables were reduced into $D = 5$ primary components where $89.63\%$ variance was explained, and we use this transformed dataset as input of the DSC model.
-
-\subsection{Differenced Synthetic Control}\label{sec:DSC}
-
-The Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021} is a tool we use to estimate how water use might have evolved if there had been no institutional shift.
-Think of it as creating an alternate reality or a ``what-if'' scenario to compare with what actually happened~\cite{abadie2010, abadie2015, hill2021}.
-The key idea behind this method is to evaluate the effects of policy changes (in this case, the 87-WAS and the 98-UBR) that mainly affect certain units (the provinces in the YRB).
-The method creates a ``synthetic'' version of the affected units by combining information from other similar but unaffected units.
-This ``synthetic'' version serves as a control group, which we can compare with the actual affected units.
-The DSC method, therefore, is a powerful tool as it allows us to control for unobserved factors that can change over time.
-
-In practice, we consider two distinct institutional shifts that affected all treated units (i.e., provinces in the YRB) in 1987 and 1998.
-Each institutional shift (87-WAS or 98-UBR) is designated as the ``shifted'' time $T_0$, and we individually analyzed two periods: from 1979 to 1998; from 1987 to 2008.
-We include each of the eight provinces in the YRB as separate treated units~\cite{abadie2021} and define the $J+1$ units observed in a time period $1, 2, \dots, T_0, T_0 + 1, \dots, T$, where the remaining $J=20$ units represent untreated provinces outside the YRB.\
-
-The treated unit is exposed to the institutional shift in every post-treatment period $T_0 +1, \dots, T$, and unaffected by the institutional shift in preceding periods $1, 2, \dots, T_0$.
-Any weighted average of the control units is referred as a synthetic control and is denoted by a ($J \times 1$) vector of weights $\mathbf{W} = (w_{1}, \ldots ,w_{J})$, satisfying $w_j \in (0, 1)$ and $w_1 + \cdots  + w_{J} = 1$.
-We also introduce a a ($k \times 1$) non-negative vector $\mathbf{V} = v_{1}, \ldots ,v_{k}$ where $k$ is the product of $T$ and $D$, the number of years and dimensions in the dataset ($D = 5$ in this case).
-The vector $\mathbf{V}$ must fulfill $v_1 + \cdots  + v_{k} = 1$, reflecting the relative importance of each covariate.
-The next goal is finding the optimal $\mathbf{W}$ which represents the best ``synthetic'' versions of the affected provinces in the YRB:\
-
-\begin{equation}
-    \mathbf{W^{*}(V)}=\underset{\mathbf{W} \in \mathcal{W}}{\operatorname{argmin}}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)^{\prime} \mathbf{V}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)
-\end{equation}
-
-Here, matrix $\mathbf{X_1}$ represents the pre-treatment average of each dimension in the dataset for the treated unit, while $\mathbf{X_0}$ is a ($k \times J$) matrix containing the pre-treatment characteristics for each of the $J$ control units.
-We also define $\mathbf{W}^{*}(V)$ as the vector of weights $\mathbf{W}$ that minimizes the discrepancy between the pre-treatment characteristics of the treated unit and the synthetic control for a given $\mathbf{V}$.
-That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W^{*}(V)}$.
-Therefore, we choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{{W}^{*}(V)}$ that minimizes the following expression:
-
-\begin{equation}
-\mathbf{V}^{*}=\underset{\mathbf{V} \in \mathcal{V}}{\operatorname{argmin}}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)^{\prime}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)
-\end{equation}
-
-That is the minimum difference between the water uses of treated units and the synthetic controls in the pre-treatment period ($1, 2, \dots, T_0$), where $\mathbf{Z}_{1}$ is a matrix containing every observation of the water use for the treated unit.
-Similarly, $\mathbf{Z}_{0}$ is a ($J \times T_0$) matrix contains the water use for each control unit in this period.
-The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with better robustness~\cite{billmeier2013, smith2015}.
-In this study, we adopted the algorithm by the ``Synthetic Control Methods'' Python library (version 1.1.17)~\cite{engelbrektson2023} for the minimization.
-
-\subsection{Validating results}\label{sec:robustness}
-
-The efficiency of the DSC approach can be validated using two primary methods.
-
-The first method involves comparing the reconstruction effect on the inferred variables (in this case, water consumption) before and after the interventions of 87-WAS and 98-UBR.\
-Small gaps between predicted and observed values before treatment, coupled with a large gap after treatment, would signal the apparent effect of the policy intervention.
-Specifically, this study employs the paired sample T test to calculate statistics that compare model predictions and actual observation data in the periods before and after both institutional interventions in 1987 (87-WAS) and 1998 (98-UBR).
-A significant difference observed after treatment, but not before, indicates that the policy was effective.
-If this pattern is not found, it suggests that the institutional changes did not impact the treated units.
-
-The second method involves using placebo tests, a standard procedure for assessing the effectiveness of synthetic control methods~\cite{abadie2010}.
-Placebo units are drawn from the control unit pool and substituted for the treated unit.
-The synthetic control method is then applied to the placebo unit using the same data and parameters as the treated unit.
-No significant difference between the placebo and control units, given that the placebo unit should not be influenced by the intervention, would demonstrate the method's effectiveness.
-In this study, we follow the placebo test approach suggested by Abadie~\cite{abadie2010} and utilize the same Python library~\cite{engelbrektson2023} to perform this.
-If the ratio of the Root Mean Square Error (RMSE) (see Equation~\ref{ch5:eq:RMSE}) in the post/pre -treated period is significantly higher for most treated provinces (using the T test to assess significance) compared to other placebo units, it implies that the provinces in the YRB were significantly affected during the treatment periods (1987 and 1998), thus indicating effectiveness.
-
-\begin{equation}
-    \label{ch5:eq:RMSE}
-    \text{RMSE} = \sqrt{\frac{1}{n}\sum_{i=1}^{n}{(y_i-\hat{y}_i)}^2}
-\end{equation}
-
-Where $n$ is the observed number, $y_i$ is the observed value, and $\hat{y}_i$ is the predicted value.
-
-\section{Results}\label{sec:results}
-
-\subsection{Institutional shifts and structures}\label{results-1}
-
-\begin{figure*}[!t]
-	\includegraphics[width=\linewidth]{diagrams/diagram.pdf}
-	\caption{
-Institutional shifts and related SES structures in the Yellow River Basin (YRB).
-		\textbf{A.} The YRB crosses $10$ provinces or the same-level administrative regions, $8$ of which heavily rely on the water resources from the YRB (Table~\ref{tab:quota}).
-The national administrations hold ultimate authority in issuing water governance policies, which are often implemented by the basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
-		\textbf{B.} Provincial administrative agencies are the major stakeholders.
-Since the 87-WAS, with surface water withdrawal from the Yellow River restricted by specific quotas, each stakeholder plans and uses water resources for development.
-However, natural hydrological processes are interconnected.
-Although the institutions focus mainly on surface water (Sur.), they can also influence groundwater inside (Gro.) or water resources outside (Sur.\ and Gro.') through systematic socio-hydrological processes within the YRB.\\ The YRCC only monitors water withdrawals at that time.
-		\textbf{C.} Institutional shifts and subsequent structural changes (details in \textit{\nameref{sec:yrb}}).
-(1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from the connected ecological unit (the reach of the Yellow River, denoted by the blue circles).
-(2) After 1987-WAS, the YRCC (the yellow circles) monitored (the dot-line links) river reaches with water use quotas.
-(3) Since the 98-UBR, stakeholders have had to apply for water use licenses from the YRCC (the connections between the red and yellow circles).
-	}\label{fig:structure}
-\end{figure*}
-
-Until the 87-WAS, provincial regions in the YRB had unrestricted access to the Yellow River water resources for development, despite geographic and temporal differences between freshwater demand and availability.
-The YRCC had no links to the provinces regarding water use before 1987, and the provinces could connect directly to the Yellow River reaches (Figure~\ref{fig:structure}~C).
-Following the 87-WAS, national authorities proposed allocating specific water quotas among the provinces, and the YRCC's duty became to report actual water use volumes in each reach.
-As it was the first time the YRCC's responsibilities included water use, this introduced new links between the YRCC and the river (i.e., ecological nodes Figure~\ref{fig:structure}~C).
-The 98-UBR further reinforced the YRCC's responsibilities for integrated water use management.
-Since $1998$, provinces have been required to submit their annual water use plans for water use licenses to the YRCC instead of freely accessing the Yellow River water.
-Consequently, the YRCC has been directly linked to the provinces since then (Figure~\ref{fig:structure}C).
-Key points of the official documents supporting the structural changes above can be found in supplementary material~\textit{\ref{secS1}}.
-
-\begin{table}[htbp]\footnotesize
-	\centering
-	\caption{Water quotas assigned for provincial regions in the YRB}\label{tab:quota}
-	  \begin{tabularx}{\textwidth}{p{3cm}XXXXX}
-	  \toprule
-	  Provincial regions & \multicolumn{1}{l}{Water planning$^a$} & \multicolumn{1}{l}{Proposal in 1983$^b$} & \multicolumn{1}{l}{Scheme in 1987$^c$} & \multicolumn{1}{l}{Avg.
-WU$^d$} & \multicolumn{1}{l}{Ratio ($\%$)$^e$} \\
-	  \midrule
-	  Qinghai & 35.70  & 14.00  & 14.10  & 12.03  & 48.12  \\
-	  Sichuan & 0.00  & 0.00  & 0.40  & 0.25  & 0.10  \\
-	  Gansu & 73.50  & 30.00  & 30.40  & 25.80  & 30.79  \\
-	  Ningxia & 60.50  & 40.00  & 40.00  & 36.58  & 58.45  \\
-	  Inner Mongolia & 148.90  & 62.00  & 58.60  & 61.97  & 47.82  \\
-	  Shanxi & 115.00  & 43.00  & 38.00  & 21.16  & 73.55  \\
-	  Shaanxi & 60.80  & 52.00  & 43.10  & 11.97  & 44.39  \\
-	  Henan & 111.80  & 58.00  & 55.40  & 34.30  & 24.77  \\
-	  Shandong & 84.00  & 75.00  & 70.00  & 77.87  & 34.41  \\
-	  Jinji & 6.00  & 0.00  & 20.00  & 5.85  & 3.11  \\
-	  \bottomrule
-	  \multicolumn{6}{p{\textwidth}}{$^a$ In 1982, each provincial region proposed their water use plans.}\\
-	  \multicolumn{6}{p{\textwidth}}{$^b$ In 1983, the Yellow River Conservancy Commission (YRCC) proposed these initial water quotas.}\\
-	  \multicolumn{6}{p{\textwidth}}{$^c$ In 1987, the quotas agreed by state department (Ministry of Water Resources).}\\
-	  \multicolumn{6}{p{\textwidth}}{$^d$ Average water use (WU) from the Yellow River for each region. Because of missing data, Sichuan and Jinji were calculated by data from 2004 to 2017.}\\
-	  \multicolumn{6}{p{\textwidth}}{$^e$ Ratio of the average water use (WU) from the Yellow River to provincial total water uses.}\\
-	  \end{tabularx}\\
-\end{table}
-
-\subsection{Institutional shifts impact on water use}\label{result-2}
-
-\begin{figure*}[!htb]
-	\centering
-	\includegraphics[width=0.9\linewidth]{outputs/main_results2.pdf}
-	\caption{
-	Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
-	\textbf{A.} Water uses of the YRB before and after the institutional shift in 1987 (87-WAS);
-	\textbf{B.} Water uses of the YRB before and after the institutional shift in 1998 (98-UBR).
-Blue lines are statistics derived from water use data; grey lines are estimates from the Differenced Synthetic Control method with economic and environmental background controlled;
-	\textbf{C.} Drought intensity in the YRB and drying up events of the Yellow River. The size of the grey bubbles denotes the length of drying upstream.
-	}\label{fig:main_results}
-\end{figure*}
-
-The total water use of the YRB exhibited a significant difference between the counterfactual prediction and the actual observed value after the two institutional shifts, while the difference was small and insignificant before (see Figures~\ref{fig:main_results}A and B).
-This indicates that the estimated reconstruction of water use change was effective.
-Figure~\ref{fig:main_results}A suggests that the 87-WAS prompted the provinces to withdraw even more water than would have been used without an institutional shift (Figure~\ref{fig:main_results}A).
-From 1988 to 1998, on average, while the estimation of annual water use only suggests $887.05$ billion $m^3$, the observed water use of the YRB provinces reached $938.06$ billion $m^3$ (an increase of $5.75\%$).
-However, after the 98-UBR, trends of increasing water use appeared to be effectively suppressed.
-From 1998 to 2008, the total observed water use decreased by $6.6$ billion $m^3/yr$ per year, while the estimation of water use still suggests $5.5$ billion $m^3/yr$ increases (Figure~\ref{fig:main_results} B).
-The increased water uses after 87-WAS align with the severe dry-up of the surface streamflow from $1987$ to $1998$, a clear indicator of river degradation and environmental crisis (Figure~\ref{fig:main_results}C).
-On the other hand, the 98-UBR ended river depletion, despite subsequent increases in drought intensity (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{fig:main_results}C).
-
-\subsection{Heterogeneous effects and interpretation}\label{result-3}
-
-\begin{figure*}[!htb]
-	\centering
-	\includegraphics[width=0.9\linewidth]{outputs/fig3.pdf}
-	\caption{
-		Regulating differences for provinces in the YRB.\\
-		Red (the 87-WAS) and green (the 98-UBR) bars denote an increased or decreased ratio for actual water use relative to the estimate from the model in the decade after the institutional shift.
-		The grey bars indicate the proportions of actual water use for each province relative to their total water use in the decade after the institutional shift.
-		The triangles mark the water quotas assigned under the institution, converted to ratios by dividing by their sum.
-	}\label{fig:regulating}
-\end{figure*}
-
-Our results demonstrate that there are differences in the response patterns of the two changes in the water resources allocation system.
-In Figure~\ref{fig:regulating}, the red bar chart (87-WAS) and the green bar chart (98-UBR) respectively represent the increase or decrease ratio of actual water consumption compared to the estimated water use of the DSC model within ten years after the institutional shifts.
-The gray bar chart shows the ratio of actual water use by provinces to their total water use in the decade after the two changes; The triangle marks indicate the ratio of the theoretical water resource quota of the province to the total available water in the YRB.\
-In the ten years after the 87-WAS, the proportion of water consumption increase (or decrease) compared to that estimated by the DSC model was positively correlated with the proportion of water consumption taken from the YRB at present (partial correlation coefficient was $0.64$).
-From 1987 to 1998, some provinces with high water consumption (e.g., Inner Mongolia and Henan) also showed significant increases in water consumption (Figure~\ref{fig:regulating} and Table~\ref{tab:DSC_summary}), with the average water consumption in four major users (Shandong, Inner Mongolia, Henan, and Ningxia) exceeding the predicted value by $32.14\%$.
-However, from 1998 to 2008, almost all provinces experienced a decrease in water consumption (by an average of $16.54\%$).
-In addition, the water consumption of each province has a negative correlation with the proportion of water taken from the Yellow River Basin (partial correlation coefficient is $-0.51$).
-
-\begin{table}[!htbp]\footnotesize
-	\centering
-	\caption{Pre and post treatment root mean squared prediction error (RMSE) for YRB's provinces}\label{tab:DSC_summary}
-	\begin{tabularx}{0.8\textwidth}{XXXXXXX}
-	  \toprule
-			& \multicolumn{3}{c}{87-WAS} & \multicolumn{3}{c}{98-UBR} \\
-  \cmidrule{2-7}    province  & \multicolumn{1}{c}{post/pre} & To avg. & \multicolumn{1}{c}{sig.} & \multicolumn{1}{c}{post/pre} & To avg.   & \multicolumn{1}{c}{sig.} \\
-	  \midrule
-	  Qinghai & 5.26  & =     & FALSE & 5.89  & >     & TRUE \\
-	  Gansu & 10.37  & >     & TRUE  & 9.55  & >     & TRUE \\
-	  Ningxia & 5.81  & =     & FALSE & 6.83  & >     & TRUE \\
-	  Inner Mongolia & 7.11  & >     & TRUE  & 1.60  & <     & TRUE \\
-	  Shanxi & 1.72  & <     & TRUE  & 5.60  & >     & TRUE \\
-	  Shaanxi & 3.05  & <     & TRUE  & 3.01  & >     & TRUE \\
-	  Henan & 20.66  & >     & TRUE  & 1.18  & <     & TRUE \\
-	  Shandong & 4.54  & =     & FALSE & 4.14  & >     & TRUE \\
-	  \bottomrule
-	  \end{tabularx}\label{tab:addlabel}\end{table}
-\section{Discussion}\label{sec:discussion}
-
-The impacts of institutional shifts on the governing effects of social-ecological systems (SESs) have attracted global attention, yet efforts to quantify their net effects remain sparse~\cite{cumming2020a}.
-Our investigation of the YRB's water governance reveals vary effects of nuanced-differences institutional shifts: while the 98-UBR led to an expected decrease in total water use, the 87-WAS surprisingly increased it by $5.75\%$.
-This comparison offers insightful perspectives on the effectiveness of governance because it suggests a significant net effect on increased water use following the implementation of this policy, in addition to the previous reports and comments suggesting that the 87-WAS was ``out-of-control''~\cite{wang2019d, departmentofearthsciences1999}.
-In contrast, the 98-UBR reduced surface water competition, so many studies attributed the streamflow restoration mainly to the successful introduction of it~\cite{chen2021,huangang2002,an2007}.
-
-The unanticipated consequence of the 87-WAS policy echoes the structural challenges reported in many other SES governance failures.
-This suggests a general pattern where specific misaligned structures can precipitate the rapid depletion of common resources~\cite{kellenberg2009,cai2016,barnes2019}.
-These structure-based failures often occur when social actors have unregulated access to linked resource units, a feature prevalent in the institution prior to 1987~\cite{wang2019c}.
-When the central government attempted to curtail this free access by introducing water quotas, they were met with water demands from stakeholders' proposals that far exceeded expectations (Table~\ref{tab:quota}).
-A previous study attributed the suboptimal effect of 87-WAS to the lack of enforcement and control mechanisms~\cite{huangang2002}.
-Taken together, it underpins a hypothesis that in the absence of enforcement, stakeholders might have exploited the system by increasing water withdrawals to secure more water quotas for their economic prospects.
-
-This hypothesis can be further substantiated by two reported facts:
-(1) There were not only surges of total water uses following the 87-WAS, but also scrambles for water reported in several provinces during this period~\cite{mao2000, bouckaert2022}.
-(2) From 1983 to the 1990s, the stakeholders persistently argued for increased the water quotas, when is a stage of ``bargaining''~\cite{wang2019e, wang2019d};
-(3) During this ``bargaining'' stage, the stakeholders who had more economic profits submitted appeals to the higher central government for larger shares~\cite{wang2019e, wang2019d}.
-
-Our results also corroborate some intuitive deductions of the hypothesis.
-Firstly, we found significant correlations between current and changed water use after the 87-WAS, which suggests that the key stakeholders (such as Neimeng, Henan, and Shandong), were more likely to be affected by the institutional change.\
-Secondly, a theoretical marginal benefit analysis (see \textit{\ref{secS4}}) suggests that this ``major users are effected more'' pattern can be inferred from a simple assumption that stakeholders anticipate future value in water quotas, thereby lending further support to the above hypothesis.
-Finally, since the YRCC could forcibly coordinate stakeholders by water quota licenses for the entire YRB after 98-UBR, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)~\cite{krieger1955, ostrom1990}.
-
-On the flip side, the apparent success of the 98-UBR institutional transformation has received consistent acclaim, particularly for its role in restoring the previously dry river~\cite{wang2019e, wang2019d}.
-Our findings suggest that the 98-UBR led to a proportional decrease in water use across provinces, indeed indicative of an immediate and tangible effect.
-However, it's essential to recognize that the 98-UBR focused solely on regulating surface water use, which hints at potential broader implications.
-Notably, some evidence suggests that this institutional shift might have resulted in increased groundwater withdrawals in regions with intensive water usage following the 98-UBR~\cite{sun2022b}.
-Unfortunately, the limited availability of eligible data on groundwater use constrains a comprehensive assessment, leaving this aspect beyond the scope of the current study.
-Nonetheless, this consideration remains highly relevant, especially as similar water quota policies have begun to be implemented nationally since the turn of the 21st century.
-
-To provide an intuitive understanding of the profound impact of the Institutional shifts, we can turn to the insights shared by a representative of the Hetao Irrigation District in Neimeng.
-As a primary stakeholder, the district's representative voiced the struggle to adapt under the 98-UBR policy which strictly enforced water quotas in our surveys.
-``The water allocated to us is far from enough'', he revealed with a desire on more water quota: ``And it's not like in the past when we could actually over use, it is very strictly controlled now.''
-``Under a limited quota, of course there are conflicts between users time to time, which depends on leaderships of the water-user associates'', he reflected: ``-farmers may have their own solutions, such as switching to sunflower, which is more water-efficient, or using shallow groundwater when is available.''
-Simultaneously, the district looked forward to future projects, such as the ``South-to-North Water Diversion'' Western Route Project, which they hoped would increase their water quotas and allow for expansion of their irrigation area.
-The desire of water in Neimeng wasn't without controversy. Stakeholders in other lower reaches argued that the Hetao Irrigation District was consuming too much water from the Yellow River.
-
-The above analysis with a real-world example emphasizes the vital role of institutions in shaping the socio-ecological systems (SES) structures of water governance.
-The structural pattern we have depicted (Figure~\ref{fig:structure}), mirrored in other SESs worldwide~\cite{kluger2020,guerrero2015,bodin2012}, illustrates how fragmented ecological units linked to isolated social actors can lead to inefficiencies.
-Before the 98-UBR, this fragmentation resulted in lower effectiveness, as disconnected actors struggled to maintain holistic ecosystems~\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
-After the 98-UBR, institutional realignments enhanced basin-scale authority (YRCC), fostering effectiveness in runoff restoration—a phenomenon often termed scale or institutional match in SESs~\cite{cumming2020a,wang2019d}.
-This comparison underscores the complex challenges of crafting win-win scenarios in SES and accentuates the importance of understanding institutional roles in water governance~\cite{hegwood2022,bergsten2019, sayles2019}.
-
-Our approach acknowledges certain limitations, such as the difficulty in quantifying contributions from economic growth, and challenges in isolating the effects from other concurrent policies in 1987 and 1998.
-Despite these constraints, our quasi-experimental methodology elucidates the change in water use following the YRB's unique institutional shifts.
-It offers critical insights into water governance, emphasizing scale-matched, basin-wide authority for water allocation solutions~\cite{bodin2017b, ostrom2009, reyers2018}.
-The success of the 98-UBR shift underscores the need for social-ecological alignment, fostering sustainable governance.
-Future endeavors must focus on strengthening stakeholder connections, exploring alternative solutions like water rights transfers, and embracing more dynamic and adaptable institutional frameworks to respond to evolving SES contexts~\cite{reyers2018}.
-
-The diverse effectiveness of structural patterns, as observed in global SESs, underscores the necessity for nuanced governance in coupled systems.
-The potential for unexpected outcomes due to institutional mismatches calls for thorough institutional analysis.
-As China seeks to overhaul its water allocation schemes, our research serves as a timely beacon, highlighting how nuanced institutional interplays can shape successful river basin governance, resonating with the global challenge of socio-hydrological complexities~\cite{muneepeerakul2017, leslie2015, hegwood2022}.
-
-\section{Conclusion}\label{sec:conclusion}
-
-In this investigation of the Yellow River Basin (YRB), we meticulously examined the impacts of two institutional shifts in water governance: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basin Regulation (98-UBR).
-Utilizing the Differenced Synthetic Control (DSC) approach, we were able to quantify the discrete effects of these transitions on water consumption within the basin.
-Our findings suggest a paradoxical increase in water use by 5.75\%, attributed to the 87-WAS, defying its original objectives.
-Conversely, the 98-UBR efficaciously diminished water usage in line with its intended outcomes.
-This analysis unearthed the pivotal role that institutional structural patterns play in determining their efficacy.
-Specifically, the misaligned structure of 87-WAS inadvertently fostered increased rivalry and exploitation of water resources.
-Meanwhile, the 98-UBR, characterized by its scale-matched, basin-wide coordination and reinforced stakeholder connections, fostered restoration of the Yellow River.
-
-In sum, our study sheds new light on the complex dynamics of institutions within socio-ecological systems (SES) governance, with an emphasis on water allocation.
-By unraveling the essential components that govern the triumph or downfall of institutional transformations, we furnish invaluable insights that can guide the crafting of sustainable water governance policies.
-These findings beckon further exploration into the multifaceted nature of institutional behavior in SES governance, and how future policy adjustments and institutional metamorphoses might sculpt the efficiency of water utilization and sustainability.
-
-\textbf{Authors Contribution}\\
-Shuai Wang and BF designed this research.
-Shuang Song performed the study and analysed data.
-Shuang Song and Huiyu Wen wrote the paper.
-Xutong Wu, Cumming S.
-Graeme, and HW revised and polished the manuscript and gave significant advice.
-
-\textbf{Acknowledgments}\\
-This research has been supported by the National Natural Science Foundation of China (grant no. 42041007) and the Fundamental Research Funds for the Central Universities.
-
-\textbf{Declaration of generative AI and AI-assisted technologies in the writing process}
-
-During the preparation of this work the authors used ChatGPT 4.0 in order to polish sentences.
-After using this tool/service, the authors reviewed and edited the content as needed and take full responsibility for the content of the publication.
-
-\bibliography{../mybib}
-\bibliographystyle{elsarticle-num}\label{bib}
-
-\newpage
-\appendix\label{appendix}
-
-\section{Key points in the documents of 87-WAS and 98-UBR}\label{secS1}
-\renewcommand{\thefigure}{A\arabic{figure}}
-\renewcommand{\thetable}{A\arabic{table}}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-The official documents in 1987 (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today) convey the following key points:
-
-\begin{itemize}
-\item The policy is aimed at related provinces (or regions at the same administrative level).
-\item Depletion of the river is identified as the first consideration of this institution.
-\item Provinces are encouraged to develop their water use plans based on a quota system.
-\item Water in short supply is a common phenomenon in relevant provinces (regions).
-\end{itemize}
-
-The official documents in 1998
-(\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today) convey the following key points:
-
-\begin{itemize}
-\item The document points out that not only provinces and autonomous regions involved in water resources management (see \textit{Article 3}), the provinces’ and regions’ water use shall be declared, organized, and supervised by the YRCC (\textit{Article 11 and Chapter III to Chapter V, and Chapter VII}).
-\item Creating the overall plan of water use in the upper, middle, and lower reaches is identified as the first consideration of this institution (\textit{Article 1}).
-\item With the same quota as used in the 1987 policy, provinces were encouraged to further distribute their quota into lower-level administrations (see \textit{Article 6 and Article 41}).
-\item They emphasize that supply is determined by total quantity, and water use should not exceed the quota proposed in 1987 (see \textit{Article 2}).
-\end{itemize}
-
-\newpage
-\section{Data source and method details}\label{secS2}
-\renewcommand{\thefigure}{B\arabic{figure}}
-\renewcommand{\thetable}{B\arabic{table}}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
 \begin{table*}[!ht]
@@
 \end{table*}
-
-\begin{figure*}[!h]
-    \includegraphics[width=0.9\linewidth]{outputs/elbow.pdf}
-    \centering
-    \caption{Choose number of pricipal components by Elbow method, $5$ pricipal components already capture $89.63\%$ explained variance.}\label{fig:elbow}
-\end{figure*}
-
-\newpage
-\section{Marginal benefit model for water use}\label{secS4}
-\renewcommand{\thefigure}{C\arabic{figure}}
-\renewcommand{\thetable}{C\arabic{table}}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-For interpretation of the pattern of provincial water uses, we compared the theoretical marginal returns and optimal water use under three different structural cases (case 1 to case 3, corresponding to different SES structures in Figure~\ref{fig:structure}~C).
-
-Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.
-As a benchmark, case 1 analogy to a decentralized stakeholders situation and lead to medium-level water use.
-In case 2, each stakeholder expects that current water use helps bargain for a favorable water quota in the face of institutional shift (see \textit{\ref{secS4}}), which can intensify the incentive to use water, leading to higher water use.
-Furthermore, the water users with higher capability are more stimulated by the institutional shift and away from the theoretically optimal water use under a unified allocation.
-After water-use decisions are consolidated into unified management (case 3), marginal benefits analysis suggests the lowest water use among the cases.
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.6\linewidth]{outputs/economic_model.pdf}
-	\caption{
-		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}~C) Major water users' theoretically optimal water use is also larger (see the proofs below.)}
-\end{figure}
-
-Below are the detailed theoretical model derivation process, where we started from proposing three intuitive and general assumptions:
-
-\begin{ass}
-(Water-dependent production) Because of irreplaceability, water is assumed to be the only input of the production function with two types of production efficiency.
-The production function of a high-incentive province is $A_HF(x)$, and the production function of a low-incentive province is $A_LF(x)$ ($A_H>A_L$).
-F(x) is continuous, $F'(0)=\infty$, $ F'(\infty)=0$, $F'(x)>0$, and $F''(x)<0$.
-The production output is under perfect competition, with a constant unit price of $P$.
-\end{ass}
-
-\begin{ass}
- (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in $N$ provinces, the cost of water use is equally assigned to each province under any water use.
-The unit cost of water is a constant $C$.
-\end{ass}
-\begin{ass}
-(Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water use.
-\end{ass}
-
-Under the above assumptions, we can demonstrate three cases consisting of local governments in a whole basin to simulate their water use decision-making and water use patterns.
-
-\begin{case} before 1987: This case corresponds to a situation without any high-level water allocation institution.
-
-When each province independently decides on its water use, the optimal water use $x_i^*$ in province $i$ satisfies:
-
- $AF'(x)=\frac{C}{P}$,
-
- where $A_H$ and $A_L$ denote high-incentive and low-incentive provinces, respectively.
-
- When the decisions in different periods are independent, for $t$ = $0, 1, 2 \cdots$, then:
-
- $x_{it}^* = x_i^*$
-
- \end{case}
-
-\begin{case} from 1987 to 1998: This case corresponds to an SES structure where fragmented stakeholders are linked to unified river reaches.
-
- The water quota is determined at $t$=0 and imposed in $t$=1,2, \ldots Under the subjective expectation of each province that current water use may influence the future water allocation determined by high-level authorities, the total quota is a constant denoted as Q, and the quota for province $i$ is determined in a proportional form:
-
- $Q_i=Q \cdot \frac{x_i}{x_i + \begin{matrix}\sum{x_{-i}} \end{matrix}}$.
-
-Under a scenario with decentralized decision-making with a water quota, given other provinces' decisions on water use remain unchanged, the optimal water use of province $i$ at $t$=0 satisfies:
-
-$AF'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix})^2}$,
-
-where $A_H$ denotes a high-incentive province and $A_L$ denotes a low-incentive province.
-
-\end{case}
-
-\begin{case} after 1998: This case corresponds to the institution under which water use in a basin is centrally managed.
-
- When the $N$ provinces decide on water use as a unified whole (e.g., the central government completely decides and controls the water use in each province), the optimal water use $x_i^*$ of province $i$ satisfies:
-
-$F'(x)=\frac{C}{P}$.
-
-\end{case}
-
-We propose Proposition 1 and Proposition 2:
-
-Proposition 1: Compared with the decentralized institution, a institution with unified management decreases total water use.
-
-The optimal water use under the three cases implies that mismatched institutions cause incentive distortions and lead to resource overuse.
-
-Proposition 2: Water overuse is higher among provinces with high water use incentives than low- water use incentives under a mismatched institution.
-
-The intuition for this proposition is straightforward in that all provinces would use up their allocated quota under a relatively small $Q$.
-As production efficiency increases, the marginal benefits of a unit quota increase, and the quota would provide higher future benefits for a pre-emptive water use strategy.
-Provinces with high production efficiency have higher optimal water use values under the decentralized decision.
-The divergence in water use would be exaggerated when the water quota is expected to be implemented with greater competition.
-
-When the N provinces decide on water uses as a unity, the marginal cost is C, equal to its fixed unit cost.
-The water use of province $i$ aims to maximize $P\cdot A\cdot F(x)-C$.
-Hence, $x_i^*$ satisfies $P \cdot A\cdot F'(x)=C$, i.e., $AF'(x)=\frac{C}{P}$, where A denotes $A_H$ for a high-incentive province and $A_L$ for a low-incentive province.
-
-When each of the N provinces independently decides on its water use, the marginal cost of water use would be $\frac{C}{N}$ as a result of cost-sharing with others.
-Hence, the optimal water use in province i at period t, denoted as $\hat x_i^*$, satisfies $P \cdot A \cdot F'(x_{it})=\frac{C}{N}$, i.e., $A \cdot F'(x)=\frac{C}{P \cdot N}$.
-Since $F'$ is monotonically decreasing, $\hat x_{it}^*>x_i^*$.
-
-When the water quota would constrain future water use, the dynamic optimization problem of province i is shown as follows.
-In $t=1,2,\cdots$, there would be no relevant cost when the quota is bound that each province takes ongoing costs of $\frac{P \cdot Q}{N}$ regardless of the allocation.
-Therefore, it is sufficient to consider only the total water quota is less than total water use in Case 2 since a ``too large'' quota doesn't make sense for ecological policies.
-
-$max  \quad P \cdot A \cdot F(x_{i,0})-\frac{C \cdot \begin{matrix} \sum x_{i,0} + x_{-i,0} \end{matrix}}{N}+\beta P \cdot A \cdot F(x_{i,1})+\beta^2 P \cdot A \cdot F(x_{i,2})+...$
-
-$=P \cdot A \cdot F(x_{i,0})-C \cdot \frac{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}{N}+\frac{\beta}{1-\beta} P \cdot A \cdot F(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}})$
-
-First-order condition: $P \cdot A \cdot F'(x_{i,0})-\frac{C}{N}+\frac{\beta}{1-\beta}[P \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0}+\begin{matrix} \sum  x_{-i,0} \end{matrix})^2}]=0$
-
-where $f(\cdot)$ is the differential function of $F(\cdot)$.
-
-The optimal water use in province i at t=0 $\widetilde x_{i,0}^*$ satisfies $P \cdot A \cdot F'(x_{i,0})=\frac{C}{N}-\frac{\beta}{1-\beta} \cdot P \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$,
-i.e.,
-$A \cdot F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$.
-
-Since $F'>0$ and $F''<0$, $\widetilde x_i^*>\hat x_i^*>x_i^*$, taken others' water use $x_{-i,0}$ as given.
-Since the provincial water use decisions are exactly symmetric, total water use would increase when each province has higher incentives for current water use.
-
-Proof of Proposition 1:
-
-Because $F'>0$ and $F''(x)<0$ is monotonically decreasing, based on a comparison of costs and benefits for stakeholders (provinces) in the three cases,
-
-$\widetilde x_i^*>\hat x_i^*>x_i^*$.
-
-The result of $\hat x_i^*>x_i^*$ indicates that individual rationality would deviate from collective rationality under unclear property rights where a water user is fully responsible for the relevant costs.
-The result of $\hat x_i^*>x_i^*$
-
-The difference between $ x_i^*$ and $\hat x_i^*$ stems from two parts: the effect of the marginal returns and the effect of the marginal costs.
-First, the ``shadow value'' provides additional marginal returns of water use in $t$ = 0, which increases the incentives of water overuse by encouraging bargaining for a larger quota.
-Second, the future cost of water use would be degraded from $\frac{P}{N}$ to an irrelevant cost.
-
-Proof of Proposition 2:
-
-Since $A_H>A_L$, $F'(x_H)<F'(x_L)$,
-Eq.(xxx) implies a positive relation between $x_{i0}$ and A, when $\beta, P, C, Q$, and other provinces' water use are taken as given.
-
-The difference between $\widetilde x_i^*$ and $\hat x_i^*$ (i.e., $\frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$) represents the incentive of water overuse derived from an expectation of water quota allocation.
-The incentive of water overuse increases by A.
-
-\end{document}

### 2025-02-11 docs/papers/01_manuscript/tab_quotas.tex

--- 2023-11-01 docs/papers/01_manuscript/manuscript_v-7.2.2.tex
@@
-\documentclass[preprint, 12pt]{elsarticle}
-
-\usepackage{amssymb}
-\usepackage{amsmath, graphicx, array}
-\usepackage{dcolumn, soul}\let\openbox\relax
-\usepackage{amsthm}
-\usepackage[figuresright]{rotating}\usepackage{algorithm, algorithmicx, algpseudocode}
-\usepackage{listings}\usepackage{hyperref}
-\usepackage{geometry}
-\usepackage{tabularx}
-
-\geometry{a4paper,left=2.0cm,right=2.0cm,top=2.5cm,bottom=2.5cm}
-\linespread{1.5}
-\newtheorem{defn}{Definition}
-\newtheorem{thm}{Theorem}
-\newtheorem{ass}{Assumption}
-\newtheorem{prop}{Proposition}
-\newtheorem{fig}{Fig.}
-\newtheorem{case}{Case}
-\newtheorem{case_appendix}{Case}
-\newtheorem{example}{Example}[section]
-\renewcommand{\proofname}{\textbf{Proof}}
-\newtheorem{property}{Property}
-\newtheorem{remark}{Remark}
-\usepackage{enumitem}
-\usepackage{float}
-\usepackage{multirow}
-\usepackage{lineno}
-\usepackage{booktabs}
-\usepackage{diagbox}
-
-\journal{Jounral of Hydrology}
-
-\begin{document}
-\begin{frontmatter}
-
-\title{Quantifying the Effects of Institutional Shifts on Water Governance in the Yellow River Basin: A Social-ecological System Perspective}
-
-\author[inst1]{Shuang Song}
-\author[inst2]{Huiyu Wen}
-\author[inst1]{*Shuai Wang}
-\author[inst1]{Xutong Wu}
-
-\author[inst3]{Graeme S. Cumming}
-\author[inst1]{Bojie Fu}
-
-\affiliation[inst1]{
-     State Key Laboratory of Earth Surface Processes and Resource Ecology,
-     Faculty of Geographical Science,
-     Beijing Normal University,
-     Beijing 100875,
-     P.R. China}
-
-\affiliation[inst2]{School of Finance,
-     Renmin University of China,
-     Beijing 100875,
-     P.R. China}
-
-\affiliation[inst3]{
-     ARC Centre of Excellence for Coral Reef Studies,
-     James Cook University,
-     Townsville 4811,
-     QLD, Australia}
-
-\begin{abstract}
-     Water governance in river basins worldwide faces challenges due to complex socio-economic and environmental factors.
-In the Yellow River Basin (YRB), two major institutional shifts, the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basin Regulation (98-UBR), aimed to address water allocation and usage issues.
-This study quantifies the net effects of these institutional shifts on water use within the YRB and analyzes the underlying reasons for their success or failure.
-     We employ a Differenced Synthetic Control method to assess the impacts of the institutional shifts.
-Our analysis suggests that the 87-WAS unexpectedly increased water use by $5.75\%$, while the 98-UBR successfully reduced water use as anticipated.
-Our research highlights the role of institutional structures in governance policies, demonstrating that the mismatched structure of the 87-WAS led to increased competition and exploitation of water resources, while the 98-UBR, basin-wide authority and stronger connections between stakeholders, resulted in improved water governance.
-     Our study underscores the importance of designing institutions that are consistent with the scale of the ecological system, promote cooperation among stakeholders, and adapt to changing social-ecological system (SES) contexts.
-As outdated and inflexible water quotas may no longer meet the demands of sustainable development in the YRB, policymakers must consider the potential consequences of institutional shifts and their impact on water use and sustainability.
-\end{abstract}
-
-\begin{keyword}
-     water use~\sep~water governance~\sep~social-ecological system~\sep~institutions~\sep~Yellow River
-\end{keyword}
-
-\end{frontmatter}
-\newpage
-\linenumbers
-\section{Introduction}\label{sec:introduction}
-Widespread freshwater scarcity and overuse challenge the sustainability of large river basins, resulting in systematic risks to economies, societies, and ecosystems globally~\cite{distefano2017, dolan2021, xu2020b, mekonnen2016}.
-Amidst climate change, mismatches between supply and demand for water resources are expected to become increasingly more prominent~\cite{florke2018, yoon2021}.
-Consequently, large river basins are progressively seeking effective water governance solutions by coordinating stakeholders, providing water resources, and ensuring the sustainable allocation of shared water resources~\cite{wang2019d}.
-In this way, hydrological processes are tightly intertwined with societies, forming a social-ecological system (SES) at a basin scale with complex socio-hydrological feedback.
-
-Institutions encompass the interplay between social actors, ecological units, and their interactions~\cite{young2008, lien2020, bodin2017b, wang2022g} (Figure~\ref{fig:framework}~a).
-These interactions constitute a type of SES structure, where effective institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different interactions, contributing to sustainability~\cite{epstein2015, wang2019d} (Figure~\ref{fig:framework}~b).
-While some institutional advances have led to effective water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China~\cite{wang2019d}, and collaborative water governance systems in Europe~\cite{green2013}), imposing institutional shifts may create or destroy connections and effectiveness is not ubiquitous~\cite{loos2022}.
-For example, the Colorado River once experienced severe water shortage, and institutions led to various shortage magnitudes for different stakeholders even under the same water demand levels~\cite{hadjimichael2020}.
-Therefore, examining when and how an institution leads to effective water governance can bring crucial insights for the sustainability of river basins.
-
-Recent research has delved into the multifaceted effects of institutions on river basin governance, shedding light on diverse consequences and interactions~\cite{bouckaert2022, vallury2022, loch2020, kirchhoff2016}.
-Primarily due to the intricate dynamics within socio-hydrological systems, understanding the manner in which different SES structures influence institutional effectiveness remains a complex challenge~\cite{bodin2017b}.
-The current study contributes to this understanding by interpreting outcomes following institutional changes, though it does not explore hypothetical scenarios without such changes.
-Thus, knowledge gaps lie in the limited understanding of effective alignments between institutional shifts and SES structures, hindering the design of effective policies to promote sustainable river basin governance.
-To fill these knowledge gaps, we study the fifth-largest river worldwide and one of the most anthropogenically altered river basins, the Yellow River Basin (YRB) in China, to quantitatively measure the effects of changing SES structures.
-
-\begin{figure}[!ht]
-	\centering
-	\includegraphics[width=0.5\linewidth]{diagrams/framework.png}
-	\caption{
-		Illustration for understanding institutional shifts and SES structural changes.
-\textbf{a.} In the general framework for analyzing social-ecological systems (SESs), (Adapted from Ostrom, 2008~\cite{ostrom2009}).
-Institutional shifts can change interactions within the SES and reframe the structures.
-\textbf{b.} We aim to examine how institutional shifts effect river basin governance by structuring SES.}\label{fig:framework}
-\end{figure}
-
-In the 1980s, intense water use, accounting for about $80\%$ of the Yellow River surface water, caused consecutive drying-up crises of runoff, leading to wetland shrinkage, agriculture reduction, and scrambles for water~\cite{wohlfart2016}.
-To alleviate water stress, Chinese authorities implemented several ambitious water management policies in the Yellow River Basin (YRB), such as the South-to-North Water Diversion Project and the Water Resources Allocation Institutions~\cite{long2020, wang2019d}.
-In this study, we specifically examined two significant institutional shifts in water allocation of the YRB\: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basinal Regulating (98-UBR).
-Instead of focusing on engineering and increasing water supply, the 87-WAS (which assigned water quotas for provinces in the YRB) and the 98-UBR (under which provinces had to obtain permits from the Yellow River Conservancy Commission, YRCC, an authority at a basin level) mainly aimed to limit water demands~\cite{bouckaert2022, speed2013}.
-These institutional shifts can offer valuable insights for two main reasons:
-(1) the top-down institutional shifts suddenly led to transformations of SES structures, allowing us to quantitatively estimate their net effects; and (2) the two institutional shifts within the same river basin provide rare comparable quasi-natural experiments.
-
-In this study, we portrayed changes of SES structures throughout the YRB's institutional shifts (the 87-WAS and the 98-UBR) and quantitatively investigated their consequences, followed by a discussion on the effectiveness of institutional shifts.
-Specifically, we first used the descriptions of official documents following the two institutional shifts to abstract the interactions between main stakeholders and their river segment units for interpreting SES structure changes between 1979 and 2008.
-Next, and perhaps most importantly, we employed the ``Differenced Synthetic Control (DSC)'' method~\cite{arkhangelsky2021}, which accounts for economic growth and natural background, to estimate theoretical water use volumes under scenarios absent of institutional shifts.
-Finally, in the discussion, we linked the effectiveness of institutional shifts to the portrayed structures, by comparing the YRB's case to previous SES structure studies and developing a marginal benefits analysis.
-
-\section{Study area and institutional contexts}\label{sec:yrb}
-
-The YRB, cradle of Chinese civilization, is located in north-central China and spans ten province-level regions whose socio-economic development heavily depends on water from the Yellow River.
-As a semi-arid and arid region, the YRB's annual precipitation varies from about 100 to 1,000 mm and increases from the northwest to the southeast, while the annual pan evaporation varies from about 700 to 1,800 mm~\cite{wang2022e}.
-Together, the YRB supports $35.63\%$ of China's irrigation and $30\%$ of its population while containing only $2.66\%$ of its water resources (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today).
-Hence, over-withdrawing water from the Yellow River became an urgent concern when the river began to dry up in the early 1970s.
-Among the policies proposed to address the problem, a series of water resource allocation institutions aimed to limit water use for each region with specific quotas, which were regarded as some of the most important solutions.
-However, few attempts have been made to quantitatively assess how the YRB's water allocation scheme contributed to water governance, while other engineering solutions have been carefully evaluated~\cite{long2020}.
-
-The YRB was the first basin in China for which water resource allocation institutions were created, and institutional shifts can be traced through several regulating documents released by the Chinese government (at the national level):
-(1) In $1980s$, the central government proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019d, wang2019e}.
-(2) In $1987$, the Water Allocation Scheme was implemented (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
-(3) In $1998$, the Unified Basinal Regulation was implemented (\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today).
-(4) In $2008$, provinces were asked to draw up new water resources plans for the YRB to further refine water allocations~\cite{wang2019d,wang2019e}.
-(5) In $2021$, there was a call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
-
-Our study period therefore ranges from $1980$ (when water quotas were proposed) to $2008$, when a regulating system with quotas was fully established at basin, provincial, and district levels.
-During this period, two significant institutional shifts can be analyzed using documents from $1987$ (87-WAS) and $1998$ (98-UBR), which split the study period into three sections: from $1980$ to $1987$ (before 87-WAS), from $1988$ to $1997$ (after 87-WAS and before 98-UBR), and from $1998$ to $2007$ (after 98-UBR).
-
-\section{Methods}\label{sec:methods}
-
-In this section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as organizational diagrams during different periods of time.
-Next, we introduce the dataset we used here and employ the Principal Components Analysis (PCA) method to reduce the dimensionality of variables affecting the total water use.
-We then estimate the net effects of the two institutional shifts on total water use, changing trends, and differences in the YRB's provinces using the Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021}.
-Finally, we introduce the tests approach for validating efficiency of the DSC model.
-
-\subsection{Portraying structures}\label{sec:structures}
-
-An organizational diagram is widely used to depict SES structures by abstracting links and nodes from the real-world interactions~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
-We apply the analysis of the organizational diagrams~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit at the basin scale (the Yellow River Conservancy Commission) into structural patterns from official documents.
-We examined the official documents of the two institutional shifts (87-WAS and 98-UBR) to portray the organizational diagrams in this study~\cite{bodin2017a,kluger2020,guerrero2015}.
-It is important to note that it can result in nuanced different structures when basin-scale regulatory entity (YRCC) is responsible for river reach regulation, or have direct authority to interact with provincial units.
-
-\subsection{Dataset and preprocessing}\label{sec:dataset}
-The data of water consumption surveys conducted by the Ministry of Water Resources were taken as the observed values throughout the years.
-Then, to estimate the water use of the YRB by assuming there were no effects from institutional shifts, we focused on $24$ variables from $5$ categories (environmental, economic, domestic, and technological) water use factors~(\textit{\ref{secS2}, Table~\ref{tab:variables}}).
-Among the total $31$ data-accessible provinces (or regions) assigned quotas in the 87-WAS and the 98-UBR, we dropped Sichuan, Tianjin and Beijing (together, Jinji) because of their trivial water use from the YRB (see Table~\ref{tab:quota}).
-
-Previous study has proved that combining PCA and DSC can lead to a more robust causal inference~\cite{bayani2021}.
-We first applied the Zero-Mean normalization (unit variance), as the variables' units are far different.
-Then, we apply PCA to the multi-year average of each province, using the Elbow method to decide the number of the principal components $D$ (\textit{Appendix~\ref{secS2}~Figure\ref{fig:elbow}}).
-Finally, all $24$ normalized variables were reduced into $D = 5$ primary components where $89.63\%$ variance was explained, and we use this transformed dataset as input of the DSC model.
-
-\subsection{Differenced Synthetic Control}\label{sec:DSC}
-
-The Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021} is a tool we use to estimate how water use might have evolved if there had been no institutional shift.
-Think of it as creating an alternate reality or a ``what-if'' scenario to compare with what actually happened~\cite{abadie2010, abadie2015, hill2021}.
-The key idea behind this method is to evaluate the effects of policy changes (in this case, the 87-WAS and the 98-UBR) that mainly affect certain units (the provinces in the YRB).
-The method creates a ``synthetic'' version of the affected units by combining information from other similar but unaffected units.
-This ``synthetic'' version serves as a control group, which we can compare with the actual affected units.
-The DSC method, therefore, is a powerful tool as it allows us to control for unobserved factors that can change over time.
-
-In practice, we consider two distinct institutional shifts that affected all treated units (i.e., provinces in the YRB) in 1987 and 1998.
-Each institutional shift (87-WAS or 98-UBR) is designated as the ``shifted'' time $T_0$, and we individually analyzed two periods: from 1979 to 1998; from 1987 to 2008.
-We include each of the eight provinces in the YRB as separate treated units~\cite{abadie2021} and define the $J+1$ units observed in a time period $1, 2, \dots, T_0, T_0 + 1, \dots, T$, where the remaining $J=20$ units represent untreated provinces outside the YRB.\
-
-The treated unit is exposed to the institutional shift in every post-treatment period $T_0 +1, \dots, T$, and unaffected by the institutional shift in preceding periods $1, 2, \dots, T_0$.
-Any weighted average of the control units is referred as a synthetic control and is denoted by a ($J \times 1$) vector of weights $\mathbf{W} = (w_{1}, \ldots ,w_{J})$, satisfying $w_j \in (0, 1)$ and $w_1 + \cdots  + w_{J} = 1$.
-We also introduce a a ($k \times 1$) non-negative vector $\mathbf{V} = v_{1}, \ldots ,v_{k}$ where $k$ is the product of $T$ and $D$, the number of years and dimensions in the dataset ($D = 5$ in this case).
-The vector $\mathbf{V}$ must fulfill $v_1 + \cdots  + v_{k} = 1$, reflecting the relative importance of each covariate.
-The next goal is finding the optimal $\mathbf{W}$ which represents the best ``synthetic'' versions of the affected provinces in the YRB:\
-
-\begin{equation}
-    \mathbf{W^{*}(V)}=\underset{\mathbf{W} \in \mathcal{W}}{\operatorname{argmin}}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)^{\prime} \mathbf{V}\left(\mathbf{X}_{\mathbf{1}}-\mathbf{X}_{\mathbf{0}} \mathbf{W}\right)
-\end{equation}
-
-Here, matrix $\mathbf{X_1}$ represents the pre-treatment average of each dimension in the dataset for the treated unit, while $\mathbf{X_0}$ is a ($k \times J$) matrix containing the pre-treatment characteristics for each of the $J$ control units.
-We also define $\mathbf{W}^{*}(V)$ as the vector of weights $\mathbf{W}$ that minimizes the discrepancy between the pre-treatment characteristics of the treated unit and the synthetic control for a given $\mathbf{V}$.
-That is, $\mathbf{W^{*}}$ depends on the choice of $\mathbf{V}$ –hence the notation $\mathbf{W^{*}(V)}$.
-Therefore, we choose $\mathbf{V^{*}}$ to be the $\mathbf{V}$ that results in $\mathbf{{W}^{*}(V)}$ that minimizes the following expression:
-
-\begin{equation}
-\mathbf{V}^{*}=\underset{\mathbf{V} \in \mathcal{V}}{\operatorname{argmin}}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)^{\prime}\left(\mathbf{Z}_{1}-\mathbf{Z}_{0} \mathbf{W}^{*}(\mathbf{V})\right)
-\end{equation}
-
-That is the minimum difference between the water uses of treated units and the synthetic controls in the pre-treatment period ($1, 2, \dots, T_0$), where $\mathbf{Z}_{1}$ is a matrix containing every observation of the water use for the treated unit.
-Similarly, $\mathbf{Z}_{0}$ is a ($J \times T_0$) matrix contains the water use for each control unit in this period.
-The DSC method generalizes the difference-in-differences estimator and allows for time-varying individual-specific unobserved heterogeneity, with better robustness~\cite{billmeier2013, smith2015}.
-In this study, we adopted the algorithm by the ``Synthetic Control Methods'' Python library (version 1.1.17)~\cite{engelbrektson2023} for the minimization.
-
-\subsection{Validating results}\label{sec:robustness}
-
-The efficiency of the DSC approach can be validated using two primary methods.
-
-The first method involves comparing the reconstruction effect on the inferred variables (in this case, water consumption) before and after the interventions of 87-WAS and 98-UBR.\
-Small gaps between predicted and observed values before treatment, coupled with a large gap after treatment, would signal the apparent effect of the policy intervention.
-Specifically, this study employs the paired sample T test to calculate statistics that compare model predictions and actual observation data in the periods before and after both institutional interventions in 1987 (87-WAS) and 1998 (98-UBR).
-A significant difference observed after treatment, but not before, indicates that the policy was effective.
-If this pattern is not found, it suggests that the institutional changes did not impact the treated units.
-
-The second method involves using placebo tests, a standard procedure for assessing the effectiveness of synthetic control methods~\cite{abadie2010}.
-Placebo units are drawn from the control unit pool and substituted for the treated unit.
-The synthetic control method is then applied to the placebo unit using the same data and parameters as the treated unit.
-No significant difference between the placebo and control units, given that the placebo unit should not be influenced by the intervention, would demonstrate the method's effectiveness.
-In this study, we follow the placebo test approach suggested by Abadie~\cite{abadie2010} and utilize the same Python library~\cite{engelbrektson2023} to perform this.
-If the ratio of the Root Mean Square Error (RMSE) (see Equation~\ref{ch5:eq:RMSE}) in the post/pre -treated period is significantly higher for most treated provinces (using the T test to assess significance) compared to other placebo units, it implies that the provinces in the YRB were significantly affected during the treatment periods (1987 and 1998), thus indicating effectiveness.
-
-\begin{equation}
-    \label{ch5:eq:RMSE}
-    \text{RMSE} = \sqrt{\frac{1}{n}\sum_{i=1}^{n}{(y_i-\hat{y}_i)}^2}
-\end{equation}
-
-Where $n$ is the observed number, $y_i$ is the observed value, and $\hat{y}_i$ is the predicted value.
-
-\section{Results}\label{sec:results}
-
-\subsection{Institutional shifts and structures}\label{results-1}
-
-\begin{figure*}[!t]
-	\includegraphics[width=\linewidth]{diagrams/diagram.pdf}
-	\caption{
-Institutional shifts and related SES structures in the Yellow River Basin (YRB).
-		\textbf{A.} The YRB crosses $10$ provinces or the same-level administrative regions, $8$ of which heavily rely on the water resources from the YRB (Table~\ref{tab:quota}).
-The national administrations hold ultimate authority in issuing water governance policies, which are often implemented by the basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
-		\textbf{B.} Provincial administrative agencies are the major stakeholders.
-Since the 87-WAS, with surface water withdrawal from the Yellow River restricted by specific quotas, each stakeholder plans and uses water resources for development.
-However, natural hydrological processes are interconnected.
-Although the institutions focus mainly on surface water (Sur.), they can also influence groundwater inside (Gro.) or water resources outside (Sur.\ and Gro.') through systematic socio-hydrological processes within the YRB.\\ The YRCC only monitors water withdrawals at that time.
-		\textbf{C.} Institutional shifts and subsequent structural changes (details in \textit{\nameref{sec:yrb}}).
-(1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from the connected ecological unit (the reach of the Yellow River, denoted by the blue circles).
-(2) After 1987-WAS, the YRCC (the yellow circles) monitored (the dot-line links) river reaches with water use quotas.
-(3) Since the 98-UBR, stakeholders have had to apply for water use licenses from the YRCC (the connections between the red and yellow circles).
-	}\label{fig:structure}
-\end{figure*}
-
-Until the 87-WAS, provincial regions in the YRB had unrestricted access to the Yellow River water resources for development, despite geographic and temporal differences between freshwater demand and availability.
-The YRCC had no links to the provinces regarding water use before 1987, and the provinces could connect directly to the Yellow River reaches (Figure~\ref{fig:structure}~C).
-Following the 87-WAS, national authorities proposed allocating specific water quotas among the provinces, and the YRCC's duty became to report actual water use volumes in each reach.
-As it was the first time the YRCC's responsibilities included water use, this introduced new links between the YRCC and the river (i.e., ecological nodes Figure~\ref{fig:structure}~C).
-The 98-UBR further reinforced the YRCC's responsibilities for integrated water use management.
-Since $1998$, provinces have been required to submit their annual water use plans for water use licenses to the YRCC instead of freely accessing the Yellow River water.
-Consequently, the YRCC has been directly linked to the provinces since then (Figure~\ref{fig:structure}C).
-Key points of the official documents supporting the structural changes above can be found in supplementary material~\textit{\ref{secS1}}.
-
+% Table generated by Excel2LaTeX from sheet 'Sheet2'
 \begin{table}[htbp]\footnotesize
@@
 	  \end{tabularx}\\
-\end{table}
-
-\subsection{Institutional shifts impact on water use}\label{result-2}
-
-\begin{figure*}[!htb]
-	\centering
-	\includegraphics[width=0.9\linewidth]{outputs/main_results2.pdf}
-	\caption{
-	Effects of two institutional shifts on water resources use and allocation in the Yellow River Basin (YRB).
-	\textbf{A.} Water uses of the YRB before and after the institutional shift in 1987 (87-WAS);
-	\textbf{B.} Water uses of the YRB before and after the institutional shift in 1998 (98-UBR).
-Blue lines are statistics derived from water use data; grey lines are estimates from the Differenced Synthetic Control method with economic and environmental background controlled;
-	\textbf{C.} Drought intensity in the YRB and drying up events of the Yellow River. The size of the grey bubbles denotes the length of drying upstream.
-	}\label{fig:main_results}
-\end{figure*}
-
-The total water use of the YRB exhibited a significant difference between the counterfactual prediction and the actual observed value after the two institutional shifts, while the difference was small and insignificant before (see Figures~\ref{fig:main_results}A and B).
-This indicates that the estimated reconstruction of water use change was effective.
-Figure~\ref{fig:main_results}A suggests that the 87-WAS prompted the provinces to withdraw even more water than would have been used without an institutional shift (Figure~\ref{fig:main_results}A).
-From 1988 to 1998, on average, while the estimation of annual water use only suggests $887.05$ billion $m^3$, the observed water use of the YRB provinces reached $938.06$ billion $m^3$ (an increase of $5.75\%$).
-However, after the 98-UBR, trends of increasing water use appeared to be effectively suppressed.
-From 1998 to 2008, the total observed water use decreased by $6.6$ billion $m^3/yr$ per year, while the estimation of water use still suggests $5.5$ billion $m^3/yr$ increases (Figure~\ref{fig:main_results} B).
-The increased water uses after 87-WAS align with the severe dry-up of the surface streamflow from $1987$ to $1998$, a clear indicator of river degradation and environmental crisis (Figure~\ref{fig:main_results}C).
-On the other hand, the 98-UBR ended river depletion, despite subsequent increases in drought intensity (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{fig:main_results}C).
-
-\subsection{Heterogeneous effects and interpretation}\label{result-3}
-
-\begin{figure*}[!htb]
-	\centering
-	\includegraphics[width=0.9\linewidth]{outputs/fig3.pdf}
-	\caption{
-		Regulating differences for provinces in the YRB.\\
-		Red (the 87-WAS) and green (the 98-UBR) bars denote an increased or decreased ratio for actual water use relative to the estimate from the model in the decade after the institutional shift.
-		The grey bars indicate the proportions of actual water use for each province relative to their total water use in the decade after the institutional shift.
-		The triangles mark the water quotas assigned under the institution, converted to ratios by dividing by their sum.
-	}\label{fig:regulating}
-\end{figure*}
-
-Our results demonstrate that there are differences in the response patterns of the two changes in the water resources allocation system.
-In Figure~\ref{fig:regulating}, the red bar chart (87-WAS) and the green bar chart (98-UBR) respectively represent the increase or decrease ratio of actual water consumption compared to the estimated water use of the DSC model within ten years after the institutional shifts.
-The gray bar chart shows the ratio of actual water use by provinces to their total water use in the decade after the two changes; The triangle marks indicate the ratio of the theoretical water resource quota of the province to the total available water in the YRB.\
-In the ten years after the 87-WAS, the proportion of water consumption increase (or decrease) compared to that estimated by the DSC model was positively correlated with the proportion of water consumption taken from the YRB at present (partial correlation coefficient was $0.64$).
-From 1987 to 1998, some provinces with high water consumption (e.g., Inner Mongolia and Henan) also showed significant increases in water consumption (Figure~\ref{fig:regulating} and Table~\ref{tab:DSC_summary}), with the average water consumption in four major users (Shandong, Inner Mongolia, Henan, and Ningxia) exceeding the predicted value by $32.14\%$.
-However, from 1998 to 2008, almost all provinces experienced a decrease in water consumption (by an average of $16.54\%$).
-In addition, the water consumption of each province has a negative correlation with the proportion of water taken from the Yellow River Basin (partial correlation coefficient is $-0.51$).
-
-\begin{table}[!htbp]\footnotesize
-	\centering
-	\caption{Pre and post treatment root mean squared prediction error (RMSE) for YRB's provinces}\label{tab:DSC_summary}
-	\begin{tabularx}{0.8\textwidth}{XXXXXXX}
-	  \toprule
-			& \multicolumn{3}{c}{87-WAS} & \multicolumn{3}{c}{98-UBR} \\
-  \cmidrule{2-7}    province  & \multicolumn{1}{c}{post/pre} & To avg. & \multicolumn{1}{c}{sig.} & \multicolumn{1}{c}{post/pre} & To avg.   & \multicolumn{1}{c}{sig.} \\
-	  \midrule
-	  Qinghai & 5.26  & =     & FALSE & 5.89  & >     & TRUE \\
-	  Gansu & 10.37  & >     & TRUE  & 9.55  & >     & TRUE \\
-	  Ningxia & 5.81  & =     & FALSE & 6.83  & >     & TRUE \\
-	  Inner Mongolia & 7.11  & >     & TRUE  & 1.60  & <     & TRUE \\
-	  Shanxi & 1.72  & <     & TRUE  & 5.60  & >     & TRUE \\
-	  Shaanxi & 3.05  & <     & TRUE  & 3.01  & >     & TRUE \\
-	  Henan & 20.66  & >     & TRUE  & 1.18  & <     & TRUE \\
-	  Shandong & 4.54  & =     & FALSE & 4.14  & >     & TRUE \\
-	  \bottomrule
-	  \end{tabularx}\label{tab:addlabel}\end{table}
-\section{Discussion}\label{sec:discussion}
-
-The impacts of institutional shifts on the governing effects of social-ecological systems (SESs) have attracted global attention, yet efforts to quantify their net effects remain sparse~\cite{cumming2020a}.
-Our investigation of the YRB's water governance reveals vary effects of nuanced-differences institutional shifts: while the 98-UBR led to an expected decrease in total water use, the 87-WAS surprisingly increased it by $5.75\%$.
-This comparison offers insightful perspectives on the effectiveness of governance because it suggests a significant net effect on increased water use following the implementation of this policy, in addition to the previous reports and comments suggesting that the 87-WAS was ``out-of-control''~\cite{wang2019d, departmentofearthsciences1999}.
-In contrast, the 98-UBR reduced surface water competition, so many studies attributed the streamflow restoration mainly to the successful introduction of it~\cite{chen2021,huangang2002,an2007}.
-
-The unanticipated consequence of the 87-WAS policy echoes the structural challenges reported in many other SES governance failures.
-This suggests a general pattern where specific misaligned structures can precipitate the rapid depletion of common resources~\cite{kellenberg2009,cai2016,barnes2019}.
-These structure-based failures often occur when social actors have unregulated access to linked resource units, a feature prevalent in the institution prior to 1987~\cite{wang2019c}.
-When the central government attempted to curtail this free access by introducing water quotas, they were met with water demands from stakeholders' proposals that far exceeded expectations (Table~\ref{tab:quota}).
-A previous study attributed the suboptimal effect of 87-WAS to the lack of enforcement and control mechanisms~\cite{huangang2002}.
-Taken together, it underpins a hypothesis that in the absence of enforcement, stakeholders might have exploited the system by increasing water withdrawals to secure more water quotas for their economic prospects.
-
-This hypothesis can be further substantiated by two reported facts:
-(1) There were not only surges of total water uses following the 87-WAS, but also scrambles for water reported in several provinces during this period~\cite{mao2000, bouckaert2022}.
-(2) From 1983 to the 1990s, the stakeholders persistently argued for increased the water quotas, when is a stage of ``bargaining''~\cite{wang2019e, wang2019d};
-(3) During this ``bargaining'' stage, the stakeholders who had more economic profits submitted appeals to the higher central government for larger shares~\cite{wang2019e, wang2019d}.
-
-Our results also corroborate some intuitive deductions of the hypothesis.
-Firstly, we found significant correlations between current and changed water use after the 87-WAS, which suggests that the key stakeholders (such as Neimeng, Henan, and Shandong), were more likely to be affected by the institutional change.\
-Secondly, a theoretical marginal benefit analysis (see \textit{\ref{secS4}}) suggests that this ``major users are effected more'' pattern can be inferred from a simple assumption that stakeholders anticipate future value in water quotas, thereby lending further support to the above hypothesis.
-Finally, since the YRCC could forcibly coordinate stakeholders by water quota licenses for the entire YRB after 98-UBR, the external appeals of provinces for larger quotas turned into internal innovation to improve water efficiency (e.g., drastically increased water-conserving equipment)~\cite{krieger1955, ostrom1990}.
-
-On the flip side, the apparent success of the 98-UBR institutional transformation has received consistent acclaim, particularly for its role in restoring the previously dry river~\cite{wang2019e, wang2019d}.
-Our findings suggest that the 98-UBR led to a proportional decrease in water use across provinces, indeed indicative of an immediate and tangible effect.
-However, it's essential to recognize that the 98-UBR focused solely on regulating surface water use, which hints at potential broader implications.
-Notably, some evidence suggests that this institutional shift might have resulted in increased groundwater withdrawals in regions with intensive water usage following the 98-UBR~\cite{sun2022b}.
-Unfortunately, the limited availability of eligible data on groundwater use constrains a comprehensive assessment, leaving this aspect beyond the scope of the current study.
-Nonetheless, this consideration remains highly relevant, especially as similar water quota policies have begun to be implemented nationally since the turn of the 21st century.
-
-To provide an intuitive understanding of the profound impact of the Institutional shifts, we can turn to the insights shared by a representative of the Hetao Irrigation District in Neimeng.
-As a primary stakeholder, the district's representative voiced the struggle to adapt under the 98-UBR policy which strictly enforced water quotas in our surveys.
-``The water allocated to us is far from enough'', he revealed with a desire on more water quota: ``And it's not like in the past when we could actually over use, it is very strictly controlled now.''
-``Under a limited quota, of course there are conflicts between users time to time, which depends on leaderships of the water-user associates'', he reflected: ``-farmers may have their own solutions, such as switching to sunflower, which is more water-efficient, or using shallow groundwater when is available.''
-Simultaneously, the district looked forward to future projects, such as the ``South-to-North Water Diversion'' Western Route Project, which they hoped would increase their water quotas and allow for expansion of their irrigation area.
-The desire of water in Neimeng wasn't without controversy. Stakeholders in other lower reaches argued that the Hetao Irrigation District was consuming too much water from the Yellow River.
-
-The above analysis with a real-world example emphasizes the vital role of institutions in shaping the socio-ecological systems (SES) structures of water governance.
-The structural pattern we have depicted (Figure~\ref{fig:structure}), mirrored in other SESs worldwide~\cite{kluger2020,guerrero2015,bodin2012}, illustrates how fragmented ecological units linked to isolated social actors can lead to inefficiencies.
-Before the 98-UBR, this fragmentation resulted in lower effectiveness, as disconnected actors struggled to maintain holistic ecosystems~\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
-After the 98-UBR, institutional realignments enhanced basin-scale authority (YRCC), fostering effectiveness in runoff restoration—a phenomenon often termed scale or institutional match in SESs~\cite{cumming2020a,wang2019d}.
-This comparison underscores the complex challenges of crafting win-win scenarios in SES and accentuates the importance of understanding institutional roles in water governance~\cite{hegwood2022,bergsten2019, sayles2019}.
-
-Our approach acknowledges certain limitations, such as the difficulty in quantifying contributions from economic growth, and challenges in isolating the effects from other concurrent policies in 1987 and 1998.
-Despite these constraints, our quasi-experimental methodology elucidates the change in water use following the YRB's unique institutional shifts.
-It offers critical insights into water governance, emphasizing scale-matched, basin-wide authority for water allocation solutions~\cite{bodin2017b, ostrom2009, reyers2018}.
-The success of the 98-UBR shift underscores the need for social-ecological alignment, fostering sustainable governance.
-Future endeavors must focus on strengthening stakeholder connections, exploring alternative solutions like water rights transfers, and embracing more dynamic and adaptable institutional frameworks to respond to evolving SES contexts~\cite{reyers2018}.
-
-The diverse effectiveness of structural patterns, as observed in global SESs, underscores the necessity for nuanced governance in coupled systems.
-The potential for unexpected outcomes due to institutional mismatches calls for thorough institutional analysis.
-As China seeks to overhaul its water allocation schemes, our research serves as a timely beacon, highlighting how nuanced institutional interplays can shape successful river basin governance, resonating with the global challenge of socio-hydrological complexities~\cite{muneepeerakul2017, leslie2015, hegwood2022}.
-
-\section{Conclusion}\label{sec:conclusion}
-
-In this investigation of the Yellow River Basin (YRB), we meticulously examined the impacts of two institutional shifts in water governance: the 1987 Water Allocation Scheme (87-WAS) and the 1998 Unified Basin Regulation (98-UBR).
-Utilizing the Differenced Synthetic Control (DSC) approach, we were able to quantify the discrete effects of these transitions on water consumption within the basin.
-Our findings suggest a paradoxical increase in water use by 5.75\%, attributed to the 87-WAS, defying its original objectives.
-Conversely, the 98-UBR efficaciously diminished water usage in line with its intended outcomes.
-This analysis unearthed the pivotal role that institutional structural patterns play in determining their efficacy.
-Specifically, the misaligned structure of 87-WAS inadvertently fostered increased rivalry and exploitation of water resources.
-Meanwhile, the 98-UBR, characterized by its scale-matched, basin-wide coordination and reinforced stakeholder connections, fostered restoration of the Yellow River.
-
-In sum, our study sheds new light on the complex dynamics of institutions within socio-ecological systems (SES) governance, with an emphasis on water allocation.
-By unraveling the essential components that govern the triumph or downfall of institutional transformations, we furnish invaluable insights that can guide the crafting of sustainable water governance policies.
-These findings beckon further exploration into the multifaceted nature of institutional behavior in SES governance, and how future policy adjustments and institutional metamorphoses might sculpt the efficiency of water utilization and sustainability.
-
-\textbf{Authors Contribution}\\
-Shuai Wang and BF designed this research.
-Shuang Song performed the study and analysed data.
-Shuang Song and Huiyu Wen wrote the paper.
-Xutong Wu, Cumming S.
-Graeme, and HW revised and polished the manuscript and gave significant advice.
-
-\textbf{Acknowledgments}\\
-This research has been supported by the National Natural Science Foundation of China (grant no. 42041007) and the Fundamental Research Funds for the Central Universities.
-
-\textbf{Declaration of generative AI and AI-assisted technologies in the writing process}
-
-During the preparation of this work the authors used ChatGPT 4.0 in order to polish sentences.
-After using this tool/service, the authors reviewed and edited the content as needed and take full responsibility for the content of the publication.
-
-\bibliography{../mybib}
-\bibliographystyle{elsarticle-num}\label{bib}
-
-\newpage
-\appendix\label{appendix}
-
-\section{Key points in the documents of 87-WAS and 98-UBR}\label{secS1}
-\renewcommand{\thefigure}{A\arabic{figure}}
-\renewcommand{\thetable}{A\arabic{table}}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-The official documents in 1987 (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today) convey the following key points:
-
-\begin{itemize}
-\item The policy is aimed at related provinces (or regions at the same administrative level).
-\item Depletion of the river is identified as the first consideration of this institution.
-\item Provinces are encouraged to develop their water use plans based on a quota system.
-\item Water in short supply is a common phenomenon in relevant provinces (regions).
-\end{itemize}
-
-The official documents in 1998
-(\href{http://www.mwr.gov.cn/ztpd/2013ztbd/2013fxkh/fxkhswcbcs/cs/flfg/201304/t20130411_433489.html}{http://www.mwr.gov.cn}, last access: \today) convey the following key points:
-
-\begin{itemize}
-\item The document points out that not only provinces and autonomous regions involved in water resources management (see \textit{Article 3}), the provinces’ and regions’ water use shall be declared, organized, and supervised by the YRCC (\textit{Article 11 and Chapter III to Chapter V, and Chapter VII}).
-\item Creating the overall plan of water use in the upper, middle, and lower reaches is identified as the first consideration of this institution (\textit{Article 1}).
-\item With the same quota as used in the 1987 policy, provinces were encouraged to further distribute their quota into lower-level administrations (see \textit{Article 6 and Article 41}).
-\item They emphasize that supply is determined by total quantity, and water use should not exceed the quota proposed in 1987 (see \textit{Article 2}).
-\end{itemize}
-
-\newpage
-\section{Data source and method details}\label{secS2}
-\renewcommand{\thefigure}{B\arabic{figure}}
-\renewcommand{\thetable}{B\arabic{table}}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-\begin{table*}[!ht]
-	\caption{Variables and their categories for water use predictions}
-	\scriptsize
-	\label{tab:variables}
-	\resizebox{\linewidth}{!}{
-	\begin{tabular}{lllll}
-	\hline
-	Sector &
-	  Category &
-	  Unit &
-	  Description &
-	  Variables \\ \hline
-	Agriculture &
-	  Irrigation Area &
-	  thousand ha &
-	  \begin{tabular}[c]{@{}l@{}}Area equipped for irrgiation by different \\ crop:\end{tabular} &
-	  \begin{tabular}[c]{@{}l@{}}Rice, \\ Wheat, \\ Maize, \\ Fruits, \\ Others.\end{tabular} \\ \hline
-	Industry &
-	  \begin{tabular}[c]{@{}l@{}}Industrial gross \\ value added\end{tabular} &
-	  Billion Yuan &
-	  Industrial GVA by industries &
-	  \begin{tabular}[c]{@{}l@{}}Textile, \\ Papermaking, \\ Petrochemicals, \\ Metallurgy, \\ Mining, \\ Food, \\ Cements, \\ Machinery, \\ Electronics, \\ Thermal electrivity, \\ Others.\end{tabular} \\
-	 &
-	  \begin{tabular}[c]{@{}l@{}}Industrial water \\ use efficiency\end{tabular} &
-	  \% &
-	  \begin{tabular}[c]{@{}l@{}}The ratio of recycled water and evaporated \\ water to total industrial water use\end{tabular} &
-	  \begin{tabular}[c]{@{}l@{}}Ratio of industrial water recycling, \\ Ratio of industrial water evaporated.\end{tabular} \\ \hline
-	Services &
-	  \begin{tabular}[c]{@{}l@{}}Services gross \\ value added\end{tabular} &
-	  Billion Yuan &
-	  GVA of service activities &
-	  Services GVA \\ \hline
-	Domestic &
-	  Urban population &
-	  Million Capita &
-	  Population living in urban regions. &
-	  Urban pop \\
-	 &
-	  Rural population &
-	  Million Capita &
-	  Population living in rural regions. &
-	  Rural pop \\
-	 &
-	  Livestock population &
-	  Billion KJ &
-	  \begin{tabular}[c]{@{}l@{}}Livestock commodity calories summed from \\ 7 types of animal.\end{tabular} &
-	  Livestock \\ \hline
-	Environment &
-		  Temperature & $K$ & Near surface air temperature & Temperature \\
-			& Precipitation & $mm$ & Annual accumulated precipitation & Precipitation \\ \hline
-	\end{tabular}}
-\end{table*}
-
-\begin{figure*}[!h]
-    \includegraphics[width=0.9\linewidth]{outputs/elbow.pdf}
-    \centering
-    \caption{Choose number of pricipal components by Elbow method, $5$ pricipal components already capture $89.63\%$ explained variance.}\label{fig:elbow}
-\end{figure*}
-
-\newpage
-\section{Marginal benefit model for water use}\label{secS4}
-\renewcommand{\thefigure}{C\arabic{figure}}
-\renewcommand{\thetable}{C\arabic{table}}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-For interpretation of the pattern of provincial water uses, we compared the theoretical marginal returns and optimal water use under three different structural cases (case 1 to case 3, corresponding to different SES structures in Figure~\ref{fig:structure}~C).
-
-Assuming that water is the factor input with decreasing marginal output of each province, results show that varying incentives for water use in each province derive from the relationship between the benefits and costs of water use.
-As a benchmark, case 1 analogy to a decentralized stakeholders situation and lead to medium-level water use.
-In case 2, each stakeholder expects that current water use helps bargain for a favorable water quota in the face of institutional shift (see \textit{\ref{secS4}}), which can intensify the incentive to use water, leading to higher water use.
-Furthermore, the water users with higher capability are more stimulated by the institutional shift and away from the theoretically optimal water use under a unified allocation.
-After water-use decisions are consolidated into unified management (case 3), marginal benefits analysis suggests the lowest water use among the cases.
-
-\begin{figure}[!htb]
-	\centering
-	\includegraphics[width=0.6\linewidth]{outputs/economic_model.pdf}
-	\caption{
-		The proposed relationship of marginal benefits and water use of individual province under varying cases (case 1 to case 3, corresponding to the different SES structures in Figure~\ref{fig:structure}~C) Major water users' theoretically optimal water use is also larger (see the proofs below.)}
-\end{figure}
-
-Below are the detailed theoretical model derivation process, where we started from proposing three intuitive and general assumptions:
-
-\begin{ass}
-(Water-dependent production) Because of irreplaceability, water is assumed to be the only input of the production function with two types of production efficiency.
-The production function of a high-incentive province is $A_HF(x)$, and the production function of a low-incentive province is $A_LF(x)$ ($A_H>A_L$).
-F(x) is continuous, $F'(0)=\infty$, $ F'(\infty)=0$, $F'(x)>0$, and $F''(x)<0$.
-The production output is under perfect competition, with a constant unit price of $P$.
-\end{ass}
-
-\begin{ass}
- (Ecological cost allocation) Under the assumption that the ecology is a single entity for the whole basin involved in $N$ provinces, the cost of water use is equally assigned to each province under any water use.
-The unit cost of water is a constant $C$.
-\end{ass}
-\begin{ass}
-(Multi-period settings) There are infinite periods with a constant discount factor $\beta$ lying in (0,1). There is no cross-period smoothing in water use.
-\end{ass}
-
-Under the above assumptions, we can demonstrate three cases consisting of local governments in a whole basin to simulate their water use decision-making and water use patterns.
-
-\begin{case} before 1987: This case corresponds to a situation without any high-level water allocation institution.
-
-When each province independently decides on its water use, the optimal water use $x_i^*$ in province $i$ satisfies:
-
- $AF'(x)=\frac{C}{P}$,
-
- where $A_H$ and $A_L$ denote high-incentive and low-incentive provinces, respectively.
-
- When the decisions in different periods are independent, for $t$ = $0, 1, 2 \cdots$, then:
-
- $x_{it}^* = x_i^*$
-
- \end{case}
-
-\begin{case} from 1987 to 1998: This case corresponds to an SES structure where fragmented stakeholders are linked to unified river reaches.
-
- The water quota is determined at $t$=0 and imposed in $t$=1,2, \ldots Under the subjective expectation of each province that current water use may influence the future water allocation determined by high-level authorities, the total quota is a constant denoted as Q, and the quota for province $i$ is determined in a proportional form:
-
- $Q_i=Q \cdot \frac{x_i}{x_i + \begin{matrix}\sum{x_{-i}} \end{matrix}}$.
-
-Under a scenario with decentralized decision-making with a water quota, given other provinces' decisions on water use remain unchanged, the optimal water use of province $i$ at $t$=0 satisfies:
-
-$AF'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(\begin{matrix} x_{i,0} + \sum x_{-i,0} \end{matrix})^2}$,
-
-where $A_H$ denotes a high-incentive province and $A_L$ denotes a low-incentive province.
-
-\end{case}
-
-\begin{case} after 1998: This case corresponds to the institution under which water use in a basin is centrally managed.
-
- When the $N$ provinces decide on water use as a unified whole (e.g., the central government completely decides and controls the water use in each province), the optimal water use $x_i^*$ of province $i$ satisfies:
-
-$F'(x)=\frac{C}{P}$.
-
-\end{case}
-
-We propose Proposition 1 and Proposition 2:
-
-Proposition 1: Compared with the decentralized institution, a institution with unified management decreases total water use.
-
-The optimal water use under the three cases implies that mismatched institutions cause incentive distortions and lead to resource overuse.
-
-Proposition 2: Water overuse is higher among provinces with high water use incentives than low- water use incentives under a mismatched institution.
-
-The intuition for this proposition is straightforward in that all provinces would use up their allocated quota under a relatively small $Q$.
-As production efficiency increases, the marginal benefits of a unit quota increase, and the quota would provide higher future benefits for a pre-emptive water use strategy.
-Provinces with high production efficiency have higher optimal water use values under the decentralized decision.
-The divergence in water use would be exaggerated when the water quota is expected to be implemented with greater competition.
-
-When the N provinces decide on water uses as a unity, the marginal cost is C, equal to its fixed unit cost.
-The water use of province $i$ aims to maximize $P\cdot A\cdot F(x)-C$.
-Hence, $x_i^*$ satisfies $P \cdot A\cdot F'(x)=C$, i.e., $AF'(x)=\frac{C}{P}$, where A denotes $A_H$ for a high-incentive province and $A_L$ for a low-incentive province.
-
-When each of the N provinces independently decides on its water use, the marginal cost of water use would be $\frac{C}{N}$ as a result of cost-sharing with others.
-Hence, the optimal water use in province i at period t, denoted as $\hat x_i^*$, satisfies $P \cdot A \cdot F'(x_{it})=\frac{C}{N}$, i.e., $A \cdot F'(x)=\frac{C}{P \cdot N}$.
-Since $F'$ is monotonically decreasing, $\hat x_{it}^*>x_i^*$.
-
-When the water quota would constrain future water use, the dynamic optimization problem of province i is shown as follows.
-In $t=1,2,\cdots$, there would be no relevant cost when the quota is bound that each province takes ongoing costs of $\frac{P \cdot Q}{N}$ regardless of the allocation.
-Therefore, it is sufficient to consider only the total water quota is less than total water use in Case 2 since a ``too large'' quota doesn't make sense for ecological policies.
-
-$max  \quad P \cdot A \cdot F(x_{i,0})-\frac{C \cdot \begin{matrix} \sum x_{i,0} + x_{-i,0} \end{matrix}}{N}+\beta P \cdot A \cdot F(x_{i,1})+\beta^2 P \cdot A \cdot F(x_{i,2})+...$
-
-$=P \cdot A \cdot F(x_{i,0})-C \cdot \frac{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}{N}+\frac{\beta}{1-\beta} P \cdot A \cdot F(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}})$
-
-First-order condition: $P \cdot A \cdot F'(x_{i,0})-\frac{C}{N}+\frac{\beta}{1-\beta}[P \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0}+\begin{matrix} \sum  x_{-i,0} \end{matrix})^2}]=0$
-
-where $f(\cdot)$ is the differential function of $F(\cdot)$.
-
-The optimal water use in province i at t=0 $\widetilde x_{i,0}^*$ satisfies $P \cdot A \cdot F'(x_{i,0})=\frac{C}{N}-\frac{\beta}{1-\beta} \cdot P \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$,
-i.e.,
-$A \cdot F'(x_{i,0})=\frac{C}{P \cdot N} - \frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$.
-
-Since $F'>0$ and $F''<0$, $\widetilde x_i^*>\hat x_i^*>x_i^*$, taken others' water use $x_{-i,0}$ as given.
-Since the provincial water use decisions are exactly symmetric, total water use would increase when each province has higher incentives for current water use.
-
-Proof of Proposition 1:
-
-Because $F'>0$ and $F''(x)<0$ is monotonically decreasing, based on a comparison of costs and benefits for stakeholders (provinces) in the three cases,
-
-$\widetilde x_i^*>\hat x_i^*>x_i^*$.
-
-The result of $\hat x_i^*>x_i^*$ indicates that individual rationality would deviate from collective rationality under unclear property rights where a water user is fully responsible for the relevant costs.
-The result of $\hat x_i^*>x_i^*$
-
-The difference between $ x_i^*$ and $\hat x_i^*$ stems from two parts: the effect of the marginal returns and the effect of the marginal costs.
-First, the ``shadow value'' provides additional marginal returns of water use in $t$ = 0, which increases the incentives of water overuse by encouraging bargaining for a larger quota.
-Second, the future cost of water use would be degraded from $\frac{P}{N}$ to an irrelevant cost.
-
-Proof of Proposition 2:
-
-Since $A_H>A_L$, $F'(x_H)<F'(x_L)$,
-Eq.(xxx) implies a positive relation between $x_{i0}$ and A, when $\beta, P, C, Q$, and other provinces' water use are taken as given.
-
-The difference between $\widetilde x_i^*$ and $\hat x_i^*$ (i.e., $\frac{\beta}{1-\beta} \cdot A \cdot f(Q \cdot \frac{x_{i,0}}{x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix}}) \cdot Q \cdot \frac{\begin{matrix} \sum x_{-i,0} \end{matrix}}{(x_{i,0} + \begin{matrix} \sum x_{-i,0} \end{matrix})^2}$) represents the incentive of water overuse derived from an expectation of water quota allocation.
-The incentive of water overuse increases by A.
-
-\end{document}
+\end{table}%

### 2025-02-11 docs/papers/02_appendix/01_institution_context.tex

@@
 % Water allocation institutions are widespread in large river basin management programs throughout the world (see \textit{Appendix} Figure~\ref{fig:world})~\cite{speed2013}.
-% This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level)\cite{wang2019a}:
+% This was the first basin in China for which a water resource allocation institution was created, and institutional shifts can be traced through several documents released by the Chinese government (at the national level)\cite{wang2019e}:
 % \begin{itemize}
-%     \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wang2019, wang2019a}.
+%     \item \textbf{1982}: The provinces and the Yellow River Water Conservancy Commission (YRCC) are required to develop a water resource plan for the Yellow River \cite{wang2019d, wang2019e}.
 %     \item \textbf{1987}: Implementation of the Allocation Plan. (\href{http://www.gov.cn/zhengce/content/2011-03/30/content_3138.htm#}{http://www.mwr.gov.cn}, last access: \today).
@@
 %     % 各省按要求编制新的黄河流域水资源规划，将水资源额度分配进一步细化。
-%     \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wang2019,wang2019a}.
+%     \item \textbf{2008}: Provinces are asked to draw up new water resources plans for the YRB to further refine water allocations \cite{wang2019d,wang2019e}.
 %     \item \textbf{2021}: A call for redesigning the water allocation institution (\href{http://www.ccgp.gov.cn/cggg/zygg/gkzb/202107/t20210721_16591901.htm}{http://www.ccgp.gov.cn}, last access: \today).
@@
 
-\begin{figure*}[!htb]
-    \centering
-    \includegraphics[width=12cm]{diagrams/world_institutions.pdf}
-	\caption{
-		Overview of water allocation institutions.
-		% 世界已有水资源分配制度的大河流域，其中黄河流域最早于1987年提出资源分配方案，后于1998年更改为统一调度方案。
-		\textbf{A.} Major river basins in the world with water resource allocation systems (shaded red); the YRB first proposed a resource allocation scheme in 1987 (designed since 1983) and then changed to a unified regulation scheme in 1998 (designed in 1997 but implemented in 1998) \cite{speed2013}.
-		% 不同的水资源分配制度设计模式，中国黄河流域是典型的自上而下。
-		\textbf{B.} Different water resource allocation system design patterns; the YRB is typical of a top-down system.
-		% 流域分水制度的演化。这种多层次的制度设计有其历史变化过程。
-		\textbf{C.} The four periods of institutional evolution of water allocation of the YRB.
-	}
-    \label{fig:world}
-\end{figure*}
+% \begin{figure*}[!htb]
+%     \centering
+%     \includegraphics[width=12cm]{diagrams/world_institutions.pdf}
+% 	\caption{
+% 		Overview of water allocation institutions.
+% 		% 世界已有水资源分配制度的大河流域，其中黄河流域最早于1987年提出资源分配方案，后于1998年更改为统一调度方案。
+% 		\textbf{A.} Major river basins in the world with water resource allocation systems (shaded red); the YRB first proposed a resource allocation scheme in 1987 (designed since 1983) and then changed to a unified regulation scheme in 1998 (designed in 1997 but implemented in 1998) \cite{speed2013}.
+% 		% 不同的水资源分配制度设计模式，中国黄河流域是典型的自上而下。
+% 		\textbf{B.} Different water resource allocation system design patterns; the YRB is typical of a top-down system.
+% 		% 流域分水制度的演化。这种多层次的制度设计有其历史变化过程。
+% 		\textbf{C.} The four periods of institutional evolution of water allocation of the YRB.
+% 	}\label{fig:world}
+% \end{figure*}
 
 % 基于上述分析，我们抽象出了两次制度转变之后的SES结构变化如正文的图1C所示。
-Based on the above documents, we abstracted the structural changes of SES after the two institutional changes, as shown in the main text \textbf{Figure 2C}.
-
-\begin{table*}
-    \centering
-    \small
-    \caption{Water quotas assigned in the 87-WAS}\label{tab:quota}
-	\resizebox{\linewidth}{!}{
-    \begin{tabular}{p{0.24\linewidth}llllp{0.1\linewidth}lllll}
-	\hline
-	Items (water volume, billion $m^3$)                    & Qinghai & Sichuan & Gansu   & Ningxia & Inner Mongolia & Shanxi  & Shaanxi & Henan   & Shandong & Jinji  \\
-	\hline
-	Demands in water plan                                                & 35.7    & 0       & 73.5    & 60.5    & 148.9          & 115     & 60.8    & 111.8   & 84       & 6      \\
-	Quota designed in 1983                                               & 14      & 0       & 30      & 40      & 62             & 43      & 52      & 58      & 75       & 0      \\
-	Quota assigned in 1987                                               & 14.1    & 0.4     & 30.4    & 40.0    & 58.6           & 38.0    & 43.1    & 55.4    & 70.0     & 20     \\
-	Average water consumption from the Yellow River from 1987-2008       & 12.03   & 0.25$^a$   & 25.80   & 36.58   & 61.97          & 21.16   & 11.97   & 34.30   & 77.87    & 5.85$^a$  \\
-	Proportion of water from the Yellow River in total water consumption & 48.12\% & 0.10$^b$\%  & 30.79\% & 58.45\% & 47.82\%        & 73.55\% & 44.39\% & 24.77\% & 34.41\%  & 3.11\%$^b$ \\
-    \hline
-    \end{tabular}}
-	\footnotesize[a]\leftline{{Calculated by data from 2004 to 2017.}}\\
-	\footnotesize[b]{\leftline{The share is too small, thus the provinces (or region) Sichuan and Jinji not to be considered in this study.}}
-\end{table*}
+% Based on the above documents, we abstracted the structural changes of SES after the two institutional changes, as shown in the main text \textbf{Figure 2C}.

### 2025-02-11 docs/papers/02_appendix/02_method_details.tex
docs: plain text version
docs(appendix.tex): splitting into four sections

--- 2022-05-20 docs/papers/02_appendix/02_method_details.tex
@@
 
-There are two approaches in validity testing of the DSC: (1) comparing the post- and pre- period reconstructions, (2) testing robustness through placebo analysis.
+% % 找到具解释力的变量是构造合成控制法稳健的关键。
+% Explanatory variables are the key to constructing a robust synthetic control method.
+% % 我们共使用了用水量密切相关的26个变量，这些变量的数据集已在先前的研究中被用来解释中国的用水量变化
+% We used a total of $24$ variables related to water consumption Table~\ref{tab:variables}, which datasets have been used in previous studies to explain changes in water use in China \cite{zhou2020}.
+% % 由于这些变量间存在自相关，我们通过肘部法供选择了5个主成分作为DSC的输入，前人研究表明PCA方法的结合能够增强合成控制法的稳健性
 
-A good synthetic control will reconstruct (a) the outcome of the treated unit and (b) the covariates of the treated unit over the pre-treatment period.
-The plots and the Root Mean Square Percentage Error (RMSPE) help us evaluate (a), this table is meant to evaluate (b).
-If the synthetic control has good fit, the following things should be true:
+% In addition, we selected $5$ principal components as input by the elbow method because selection in autocorrelated variables reduces dimensions and then enhances the robustness of the DSC (Figure~\ref{fig:elbow}).
 
-Each row of the first two columns should be approximately equal. This means the synthetic control has reconstructed the treated unit values.
+% There are two approaches to validity testing of the DSC: (1) comparing the post-treated and pre-treated reconstructions and (2) testing robustness through placebo analysis.
+% For (1), differences between each province and their synthetic are significant in post-treated periods and small in pre-treated periods (Figure~\ref{fig:87panel} and figure~\ref{fig:98panel}), which show good reconstructions of their water use changes' estimation.
+% For (2), we applied the in-place placebo analysis described by \cite{abadie2010}.
+In most provinces, ratios of post-MSPE to pre-MSPE are higher than the median of other placebo units, which suggests the institutional shifts in treated time (1987 and 1998 here) influenced them more than most of the other provinces (figure~\ref{fig:87placebo}, figure~\ref{fig:98placebo}, Table~\ref{tab:DSC_summary}).
 
-Placebo analysis is another standard approach to.
+% \begin{figure*}[!bh]
+%     \includegraphics[width=0.9\linewidth]{outputs/87panel.pdf}
+%     \centering
+%     \caption{Comparations between YRB' provinces and their synthetic controls around the 87-WAS.}
+%     \label{fig:87panel}
+% \end{figure*}
+
+% \begin{figure*}
+%     \includegraphics[width=0.9\linewidth]{outputs/98panel.pdf}
+%     \centering
+%     \caption{Comparations between YRB' provinces and their synthetic controls around the 98-UBR.}
+%     \label{fig:98panel}
+% \end{figure*}
+
+% \begin{figure*}
+%     \includegraphics[width=0.9\linewidth]{outputs/87placebo.pdf}
+%     \centering
+%     \caption{Gaps in change in water use between provinces outside the YRB and their synthetic control, around the 87-WAS, excluding the provinces with high pre-treatment RMSPE (more than $3$ times of treated units' RMSPE).}
+%     \label{fig:87placebo}
+% \end{figure*}
+
+% \begin{figure*}
+%     \includegraphics[width=0.9\linewidth]{outputs/98placebo.pdf}
+%     \centering
+%     \caption{Gaps in change in water use between provinces outside the YRB and their synthetic control, around the 98-UBR, excluding the provinces with high pre-treatment RMSPE (more than $3$ times of treated units' RMSPE)}
+%     \label{fig:98placebo}
+% \end{figure*}
+
+\input{tab_data_source.tex}
+
+\begin{figure*}[!h]
+    \includegraphics[width=0.9\linewidth]{outputs/elbow.pdf}
+    \centering
+    \caption{Choose number of pricipal components by Elbow method, $5$ pricipal components already capture $89.63\%$ explained variance.}\label{fig:elbow}
+\end{figure*}

### 2025-02-11 docs/papers/02_appendix/03_results_appendix.tex

--- 2022-05-05 docs/papers/02_appendix/03_results_appendix.tex
@@
-\graphicspath{{../../../figs/}}
+% The Differenced Synthetic Control (DSC) method estimates water use $y'$ by assuming that the control group (provinces out of the YRB) and experiment group (provinces in the YRB) keep their changing trends after an institutional shift in $t_0$, i.e., $f_{t<t_0}(X) = f_{t>t_0}(X)$.
+% Therefore, when comparing the actual water use $y$ and the estimated water use $y'$ after institutional shifts, if $y'_{t<t_0} \approx y_{t<t_0}$ but $y'_{t>t_0} \neq y_{t>t_0}$, there are two cases: (1) changing trends of independent variables $X$ are different between control groups and experiment groups; (2) functions of variables are different between pre- and post- institutional shift periods i.e., $f_{t<t_0}(X) \neq f_{t>t_0}(X)$.
+% Corresponding to the problem of this study, they mean: (1) Institutional shift changes the trend of independent variables (environment, economy, technology); (2) Institutional shift makes difference of water use caused by the change of unit independent variable combination different.
 
-The Differenced Synthetic Control (DSC) method estimates water use $y'$ by assuming that the control group (provinces out of the YRB) and experiment group (provinces in the YRB) keep their changing trends after an institutional shift in $t_0$, i.e., $f_{t<t_0}(X) = f_{t>t_0}(X)$.
-Therefore, when comparing the actual water use $y$ and the estimated water use $y'$ after institutional shifts, if $y'_{t<t_0} \approx y_{t<t_0}$ but $y'_{t>t_0} \neq y_{t>t_0}$), there are two cases: (1) changing trends of independent variables $X$ are different between control groups and experiment groups; (2) functions of variables are different between pre- and post- institutional shift periods i.e., $f_{t<t_0}(X) \neq f_{t>t_0}(X)$.
-Corresponding to the problem of this study, they mean: (1) Institutional shift changes the trend of independent variables (environment, economy, technology); (2) Institutional shift makes difference of water use caused by the change of unit independent variable combination different.
+% In practice, both two factors may contribute simultaneously.
+% Here, we analyze the differences between the YRB (affecting the actual water consumption) and other provinces (used by DSC generating synthetic control group) for the representative independent variables in each category of Table~\ref{tab:variables} by calculating their differences in ratio $Diff_{ratio}$:
 
-In practice, both two factors may contribute simultaneously.
-Here, we analyze the differences between the YRB (affecting the actual water consumption) and other provinces (used by DSC generating synthetic control group) for the representative independent variables in each category of Table~\ref{tab:variables} by calculating their differences in ratio $Diff_{ratio}$:
+% \begin{equation}
+%     Diff_{ratio} = \frac{\vec{var}^{YRB}_{t} - \vec{var}^{others}_{t}}{\frac{1}{T} * \sum_{t}^T (var^{YRB}_{t} - var^{others}_{t})}
+% \end{equation}
 
-\begin{equation}
-    Diff_{ratio} = \frac{\vec{var}^{YRB}_{t} - \vec{var}^{others}_{t}}{\frac{1}{T} * \sum_{t}^T (var^{YRB}_{t} - var^{others}_{t})}
-\end{equation}
+% where $\vec{var}$ is a vector of specific independent variable in $X_{t, var}$, $t\in [1979, 2008]$.
 
-where $\vec{var}$ is a vector of specific independent variable in $X_{t, var}$, $t\in [1975, 2008]$.
-
-For the first case, in terms of environmental factors, the differences between provinces in the YRB and other Chinese provinces has not changed significantly throughout (i.e., kept parallel, Figure~\ref{fig:variables} A and B).
+% For the first case, in terms of environmental factors, the differences between provinces in the YRB and other Chinese provinces has not changed significantly throughout (i.e., kept parallel, Figure~\ref{fig:variables} A and B).
 However, the economic factors (both in agriculture, industry, and services) had significant changes after the first institutional shift (the 87-WAS) (Figure~\ref{fig:variables}~C, D and E), but not in population (Figure~\ref{fig:variables}~F).
 
-% 对第二种情况
-For the second case, since the production functions of water use are mainly dependent on its efficiency, which influenced by water-saving facilities a lot, we analyze the differences between water conservation infrastructures (WCI) ratio and industrial water recycling (IWR) ratio.
+% % 对第二种情况
+% For the second case, since water the production functions of water use are mainly dependent on its efficiency, which is influenced by water-saving facilities a lot, we analyze the differences between water conservation infrastructures (WCI) ratio and industrial water recycling (IWR) ratio.
 While an abruptly changing trend occurred after the 87-WAS for WCI, ratio of IWR rised its differences between the YRB provinces and other provinces (without abrupt change) until the 98-UBR (Figure~\ref{fig:variables}~G and H).
 
-As results, the differences between the DSC estimated YRB's water use and its actual water use are contributed by both abrupt changes of independent variables and functions.
+% As results, the differences between the DSC estimated YRB's water use and its actual water use are contributed by both abrupt changes of independent variables and functions.
 Furthermore, the economic variables (agriculture, industry, and services) contributed much more rather than environmental variables or population.
 
-\begin{figure*}
-    \includegraphics[width=0.9\linewidth]{outputs/variables.pdf}
-    \centering
-    \caption{Differences ratio of different variables: \textbf{A.} precipitation, \textbf{B.} temperature, \textbf{C.} total irrigated areas, \textbf{D.} industrial gross value added (industrial GVA), \textbf{E.} services GVA, \textbf{F.} population, \textbf{G.} water conservation irrigation (WCI) ratio, and \textbf{H.} industrial water recycling (IWR) ratio.}
-    \label{fig:variables}
-\end{figure*}
+% \begin{figure*}
+%     \includegraphics[width=0.9\linewidth]{outputs/variables.pdf}
+%     \centering
+%     \caption{Differences ratio of different variables: \textbf{A.} precipitation, \textbf{B.} temperature, \textbf{C.} total irrigated areas, \textbf{D.} industrial gross value added (industrial GVA), \textbf{E.} services GVA, \textbf{F.} population, \textbf{G.} water conservation irrigation (WCI) ratio, and \textbf{H.} industrial water recycling (IWR) ratio.}
+%     \label{fig:variables}
+% \end{figure*}
+
+% \begin{figure*}
+%     \includegraphics[width=0.9\linewidth]{outputs/elbow.pdf}
+%     \centering
+%     \caption{Choose number of pricipal components by Elbow method, $5$ pricipal components already capture $89.63\%$ explained variance.}
+%     \label{fig:elbow}
+% \end{figure*}
 

### 2025-02-11 docs/papers/04_response_letter/source/editor.tex

--- 2023-11-01 docs/papers/04_response_letter/source/editor.tex
@@
 
-% 现在有两位审稿人对修订后的版本进行了评估。他们都赞赏为考虑到对他们两人都审查过的初次提交的意见所做的工作。对论文的技术方面不太了解的人仍然对方法的解释很恼火。请仔细修改这方面，以确保期刊读者能理解你的论文
-\RC*{} Two reviewers have now assessed the revised version.
-They both appreciate the work done to take in account the comments on the initial submission they had both reviewed.
-The one who is lcoser to the technical aspect of the paper is still quite annoyed though on the explanation of the method.
-Please revise carefully this aspect in order to ensure understandability of your paper by the journal readership
+% 之前的审稿人现在已经审查了第二次修订版本。第一个审稿人仍然要求具体的澄清，下面有很好的解释。请务必考虑一下，我希望这将是一个最终的修订。
+\RC*{} Both previous reviewers have now reviewed this second revised version. The first reviewer is still asking for specific clarifications well explained below.
 
-% TODO \AR{} I am grateful for the encouragement and the direction provided to enhance our manuscript.
-It has been a privilege to contribute to this special issue, and I believe that the revisions made align with the expectations and vision set forth by the editorial team.
+\RC*{} Please do consider them in what I hope will be an ultimate revision.
+
+% 很感谢审稿人提出的宝贵建议，它们的确能够让读者更加易于理解我们应用的计量方法，我们已经完全遵照其建议作出了修改。
+\AR{} We are grateful to the reviewers for their valuable suggestions, which really make it easier for readers to understand the measurement methods we apply, and we have made changes in full compliance with their suggestions.

### 2025-02-11 docs/papers/04_response_letter/source/reviewer_2.tex

--- 2023-07-29 docs/papers/04_response_letter/source/reviewer_2.tex
@@
 
-\RC{} This study examines the effects of two institutional shifts in Water Governance for the Yellow River Basin - 87-WAS and 98-UBR.
-Results show that while 87-WAS led to an increased water use, 98 UBR successfully reduced it due to its basin wide authority and stronger connections between stakeholders.
-It is suggested that institutions should be designed according to ecological scale, promote cooperation with different parties involved, as well as adapting themselves accordingly.
-Governments and policymakers must analyze the effects of changes in policy on water usage and sustainability.
-The author adopted the newly developed Synthetic Difference-in-Differences published on AER.
-This paper is well written and strutured.
-However, this method is completely new to the researcher on water study.
-I have several suggestions wish the authors further consider them in the revised manuscript.
+\RC{} The authors have addressed my concerns. I have no further comments or suggestions on this paper. Thank you.
 
-\AR{} We appreciate your acknowledgement of the reasonable and adaptable methodology used in this study, as well as the useful insights provided by the case analysis.
-We agree that the discussion could be more supportive and solid in its content of the results and we will work to revise the manuscript accordingly.
-Please find our point-by-point response to your specific comments below.
-
-\subsection{\#1 Method}
-
-\RC{}  It is suggested that the principle behind Differenced Synthetic Control, as well as the process for selecting treatment and control groups and conducting synthetic control, be explained using more accessible language.
-Currently, the explanation is too abstract and may be difficult for most readers of the journal to understand.
-To further expand on the suggestion, using more accessible language would involve breaking down complex ideas and jargon into simpler terms that are easier for readers to understand.
-This could involve providing more concrete examples and explanations, and avoiding technical terminology that may not be familiar to a general audience.
-Additionally, it may be helpful to provide step-by-step instructions or diagrams to illustrate the process of selecting treatment and control groups and conducting synthetic control.
-By doing so, readers who may not be familiar with the topic can more easily understand and appreciate the content of the journal.
-
-\AR{} Thank you for your insightful suggestion on making the Differenced Synthetic Control (DSC) method explanation more accessible to a wider audience.
-We understand the importance of making our methodology clear to all readers, not just those with a strong background in statistical analysis.
-We have revised the section accordingly, breaking down complex ideas into simpler terms, providing concrete examples, and avoiding jargon.
-We believe these changes make the methodology more accessible to a broader audience.
-Your suggestion greatly helped us improve the clarity and accessibility of our methodology description:
-
-\begin{quote}[page=6, sline=124, eline=133]
-    The Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021} is a tool we use to estimate how water use might have evolved if there had been no institutional shift.
-    Think of it as creating an alternate reality or a ``what-if'' scenario to compare with what actually happened~\cite{abadie2010, abadie2015, hill2021}.
-    The key idea behind this method is to evaluate the effects of policy changes that mainly affect certain units (in this case, the institutional shifts in the Yellow River Basin or YRB).
-    The method creates a ``synthetic'' version of the affected units by combining information from other similar but unaffected units.
-This ``synthetic'' version serves as a control group, which we can compare with the actual affected units.
-    The DSC method, therefore, is a powerful tool as it allows us to control for unobserved factors that can change over time, providing more robust results.
-\end{quote}
-
-\subsection{\#2 Robustness}\label{sec:2-2}
-
-\RC{} I'm glad to see that you have included a couple of robustness checks.
-However, there are several more details related to Differenced Synthetic Control that need to be tested.
-These may include testing for the sensitivity of the results to changes in the choice of control group, the inclusion or exclusion of certain covariates, and the specification of the synthetic control model.
-Other possible robustness checks may involve testing for heterogeneity of treatment effects across different subgroups or time periods, and assessing the impact of outliers or influential observations on the results.
-
-\AR{} We appreciate your thoughtful suggestion about additional robustness checks for our Differenced Synthetic Control (DSC) method.
-However, we have chosen not to include further robustness checks in our revised manuscript for several reasons:
-
-\AR*{} Firstly, our primary objective in this paper is not to conduct a precisely quantitative assessment.
-Rather, we aim to uncover the interesting differential responses underlying the two different institutional shifts.
-As you pointed out, readers of our paper might not expect an overload of technical details.
-To maintain conciseness and avoid overwhelming our readers, we have chosen to limit the number of methodologies we include.
-
-\AR*{} Secondly, the two approaches we have employed were recommended by the developers of the DSC method~\cite{engelbrektson2023}.
-The corresponding algorithms have been provided and are consistent with the DSC method.
-If we were to introduce further tests, we might have to develop our own algorithms.
-This could potentially lead to inconsistencies and might confuse readers who wish to apply our methods in their own work.
-
-\AR*{} Lastly, in response to a suggestion from another reviewer, we have revised the terminology from ``robustness'' to ``efficiency''.
-We believe this terminology better communicates our intentions and the nature of our methodology to readers, reducing the need for additional emphasis on robustness.
-
-\AR*{} We believe these reasons justify our decision.
-However, we appreciate your suggestion and will certainly keep it in mind for future research where more extensive robustness checks may be more appropriate.
-
-\subsection{\#3 Results and discussion}\label{sec:2-3}
-
-\RC{} The results, discussion, and comparisons are comprehensive, and I have no further comments at this time.
-
-\AR{} Thank you for your positive feedback on the comprehensiveness of the results, discussion, and comparisons in our paper.
-We're delighted to hear that you found this section satisfactory.
-Your kind words are greatly encouraging and motivate us to continue to improve our work.
-We hope that the revisions we have made in response to your helpful suggestions have improved the manuscript.
+\AR{} We are immensely grateful for your assessment and pleased to hear that you have no further comments.
+Your feedback has been invaluable to the improvement of our manuscript.
+Thank you for your time and contribution to our work.
